### 2023-04-01 Data_Import.Rmd
Initial upload

---
title: "Data_Import"
output: html_document
date: "2023-04-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
```

## Import data
Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
Mothership<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
```
## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
Mothership2 <- mutate(Mothership, 
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                          "1"="Complete",
                                          "2"="Nearly Complete",
                                          "3"="Insurance",
                                          "4"="Nonatteneance",
                                          "5"="Inappropriate",
                                          "6"="Inpatient",
                                          "7"="Withdrew",
                                          "8"="Dissatisfaction",
                                          "9"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                          "1"="<Grade 12",
                                          "2"="HS Diploma",
                                          "3"="GED",
                                          "4"="Some College",
                                          "5"="Associates Degree",
                                          "6"="Bachelors Degree",
                                          "7"="Some Grad School",
                                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                                       "0"="Female",
                                       "1"="Male",
                                       "2"="Non-Binary",
                                       "3"="Other",
                                       "4"="Unknown"),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                                             "0"="Married",
                                             "1"="Cohabitating",
                                             "2"="Widowed",
                                             "3"="Separated",
                                             "4"="Divorced",
                                             "5"="Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                                          "1"="Straight",
                                          "2"="Gay",
                                          "3"="Bisexual",
                                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                                          "0"="General",
                                          "1"="Trauma",
                                          "2"="Young Adult",
                                          "3"="BPD"),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                      "0"="<Grade 6", 
                                      "1"="Grades 7-12",
                                      "2"="HS Diploma", 
                                      "3"="GED",
                                      "4"="Some College",
                                      "5"="Associates Degree",
                                      "6"="Bachelors Degree",
                                      "7"="Some Grad School",
                                      "8"="Grad Degree"))
```

## Pie Chart For Education Status 
```{r}
#Create Table and Data Frame
Education<-table(Mothership$Education_1)
Education_df<-as.data.frame(Education)
Education_df

str(Mothership$Education_1)

#Rename Columns
colnames(Education_df)[1]="Category"
colnames(Education_df)[2]="Frequency"

Education_df$Category=recode(Education_df$Category,
                             "0"="<Grade 6", 
                             "1"="Grades 7-12",
                             "2"="HS Diploma", 
                             "3"="GED",
                             "4"="Some College",
                             "5"="Associates Degree",
                             "6"="Bachelors Degree",
                             "7"="Some Grad School",
                             "8"="Grad Degree")

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  coord_polar("y",start=0)+
  theme_void()
```

### 2023-04-01 Doug_Stuff.R

@@ -1,0 +1,522 @@
+### SETUP ###
+
+setwd("~/Desktop/Coding/R working directory/Hospital_Visualizations")
+library(tidyverse)
+library(dplyr)
+library(haven)
+library(ggplot2)
+
+Mothership<-read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
+
+Mothership<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
+
+############################### Demographics ####################################
+
+### Bar Chart for Discharge Status ###
+
+ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
+  geom_bar(color = "black",fill="darkgreen")+
+  ggtitle("Treatment Discharge Status") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  scale_x_discrete(name = "Discharge Status")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,5000))
+
+### Bar Chart for Education Status ###
+
+ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
+  geom_bar(color = "black",fill="darkred")+
+  ggtitle("Education Level") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  scale_x_discrete(name = "Education Level")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,2500))
+
+### Pie Chart For Education Status ###
+
+#Create Table and Data Frame
+Education<-table(Mothership$Education_1)
+Education_df<-as.data.frame(Education)
+Education_df
+
+str(Mothership$Education_1)
+
+#Rename Columns
+colnames(Education_df)[1]="Category"
+colnames(Education_df)[2]="Frequency"
+
+
+Education_df$Category=recode(Education_df$Category,
+                             "0"="<Grade 6", 
+                             "1"="Grades 7-12",
+                             "2"="HS Diploma", 
+                             "3"="GED",
+                             "4"="Some College",
+                             "5"="Associates Degree",
+                             "6"="Bachelors Degree",
+                             "7"="Some Grad School",
+                             "8"="Grad Degree")
+
[…]

### 2023-04-02 Data_Import.Rmd
Duration depression figure

@@
 library(ggplot2)
+## long / wide data
+library(tidyr)
 ```
@@
 ```{r}
-Mothership <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
-Mothership<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
+df <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
+view(df)
+Mothership<-select(df,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
 ```
@@
 ```{r}
-Mothership2 <- mutate(Mothership, 
+#recode varaibles
+
+Mothership <- mutate(Mothership, 
                      DC_status_1 = as.factor(DC_status_1),
@@
                                       "7"="Some Grad School",
-                                      "8"="Grad Degree"))
+                                      "8"="Grad Degree"),
+
+       #Lets make some new variables 
+                     Duration = as.factor(
+                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1-5",
+                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "6-10",
+                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "11-15", "16+"
+                              )))))
+# Disorder subtypes 
+# Mood Disorders
+# Anxiety Disorders
+# Obsessive Compusive Disorders
+# Personality Disorders
+# Substance Use Disorders
+# Trauma related disorders
+# Psychotic Disorders
+# Eating Disorders
+
+#Extract Year From Intake Date
+#Convert to Date
+library("lubridate")
+Mothership$Intake_1<-mdy(Mothership$Intake_1,locale = "en_US.UTF-8")
+Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
+
+Mothership<-mutate(Mothership,
+                   TxYear = as.factor(TxYear),
+                   TxYear = recode(TxYear,
+                                   "1582"="2014",
+                                   "2021"="2020",
+                                   "2022"="2020"))
+
+```
+
+```{r}
+### Bar Chart for Discharge Status ###
+plot(Mothership2$DC_status_1)
+
+ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
+  geom_bar(color = "black",fill="darkgreen")+
+  ggtitle("Frequency of Treatment Discharge Status") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Discharge Status") +
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6000))
+
+### Bar Chart for Education Status ###
+
+ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
+  geom_bar(color = "black",fill="darkred")+
+  ggtitle("Frequency of Education Level") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Education Level")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,3000))
 ```
@@
 Education_df
-
-str(Mothership$Education_1)
 
@@
 ```
+
+## Depression Treatment Progress Charts
+
+```{r}
+Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
+Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]
+
+#Create a Time Variable
+Mothership_Long$TxDay <- NA
+Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
+Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
+Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
+Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
+Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
+Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
+Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
+Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
+Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
+Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
+Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
+Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
+Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
+Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
+Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
+Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
+Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
+Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
+Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
+Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20
+
+#Create a New Data Set with an Average Depression Variable
+Mothership_Mean_CUDOS<-Mothership_Long %>%
+  group_by(TxDay) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+```
+
+```{r}
+#Plot the Depression Mean for Full Sample
+ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
+  geom_line(size=1,color="#0065A3")+
+  geom_point(color="#0065A3")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  ggtitle("Mean Depression Severity During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
+  theme(panel.background=NULL) +
+  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
+  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
+  geom_vline(xintercept = 13, color = "red",alpha =.5)+
+  annotate("text", x = 5, y = 34, label = "Q1") +
+  annotate("text", x = 8, y = 34, label = "Mean") +
+  annotate("text", x = 13, y = 34, label = "Q3")
+
+ggplot(Mothership, aes(Days_complete_1))+
+  geom_density()+
+  scale_x_continuous(limits=c(0,20)) +
+  labs(
+    title="Quantity of discharges Per Treatment Day")
+
+```
+
+### plot means based upon duration group membership 
+```{r}
+ggplot(Mothership, aes(x = Duration, y = Days_complete_1)) +
+  geom_violin()+
+  geom_boxplot(width=0.1, color="blue", alpha=0.2)
+
+Mothership_duration_CUDOS<-Mothership_Long %>%
+  group_by(TxDay,Duration) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+```
+
+```{r}
+#plot depression mean with each group
+
+Mothership_Mean_CUDOS<-Mothership_Long %>%
+  group_by(Duration,TxDay) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+Mothership_duration_CUDOS<-Mothership_Mean_CUDOS[1:83,]
+#delete weird Na values and put NA for values
+Mothership_duration_CUDOS[6:20,3] = NA
+Mothership_duration_CUDOS[37:41,3] = NA
+Mothership_duration_CUDOS[74:83,3] = NA
+Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-21),]
+Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-41),]
+Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-61),]
+Mothership_duration_CUDOS
+
+ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
+  geom_line(size=1)+
+  geom_point()+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  ggtitle("Mean Depression Severity During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
+  scale_color_manual(values=c("#BB9D00","red",
+                              "darkred","orange"))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())+
+  geom_vline(xintercept = 5,alpha =.25)+
+  geom_vline(xintercept = 8,alpha =.25)+
+  geom_vline(xintercept = 13,alpha =.25)+
+  annotate("text", x = 5, y = 39, label = "Q1") +
+  annotate("text", x = 8, y = 39, label = "Mean") +
+  annotate("text", x = 13, y = 39, label = "Q3")
+
+```

### 2023-04-02 Doug_Stuff.R

@@ -203,6 +203,8 @@ Mothership_Mean_CUDOS_Gender<-Mothership_Long %>%
   group_by(TxDay,Gender_1) %>%
   summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
 
+Mothership_Mean_CUDOS_Gender
+
 #Create the Depression Line Graph by Gender
 ggplot(data=subset(Mothership_Mean_CUDOS_Gender,!is.na(Gender_1)),
        aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+

### 2023-04-03 Anxiety_Vis.Rmd
Creating new documents

---
title: "Anxiety_vis"
output: html_document
date: "2023-04-03"
---

```{r setup, include=FALSE}
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

#Data
Mothership<-read.csv("~/Desktop/Coding/data/Mothership_Vis.csv")
Mothership<-mutate(Mothership,
      DC_status_1 = as.factor(DC_status_1),
      Education_1 = as.factor(Education_1),
      Gender_1 = as.factor(Gender_1),
      Relationship_1 = as.factor(Relationship_1),
      Sexuality_1 = as.factor(Sexuality_1),
      IPT_track_1 = as.factor(IPT_track_1),
      Race_1 = as.factor(Race_1),
      Education_1 = as.factor(Education_1),
      Duration = as.factor(Duration),
      TxYear = as.factor(TxYear)
      )
```

### 2023-04-03 Depression_Vis.Rmd
Creating new documents

---
title: "Depression_Vis"
output: html_document
date: "2023-04-03"
---

```{r setup, include=FALSE}
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

#Data
Mothership<-read.csv("~/Desktop/Coding/data/Mothership_Vis.csv")
Mothership<-mutate(Mothership,
      DC_status_1 = as.factor(DC_status_1),
      Education_1 = as.factor(Education_1),
      Gender_1 = as.factor(Gender_1),
      Relationship_1 = as.factor(Relationship_1),
      Sexuality_1 = as.factor(Sexuality_1),
      IPT_track_1 = as.factor(IPT_track_1),
      Race_1 = as.factor(Race_1),
      Education_1 = as.factor(Education_1),
      Duration = as.factor(Duration),
      TxYear = as.factor(TxYear)
      )
```

## Depression Treatment Progress Charts

```{r}
Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]

#Create a Time Variable
Mothership_Long$TxDay <- NA
Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20

#Create a New Data Set with an Average Depression Variable
Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
```

```{r}
#Plot the Depression Mean for Full Sample
ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
  geom_line(size=1,color="#0065A3")+
  geom_point(color="#0065A3")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
  theme(panel.background=NULL) +
  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
  geom_vline(xintercept = 13, color = "red",alpha =.5)+
  annotate("text", x = 5, y = 34, label = "Q1") +
  annotate("text", x = 8, y = 34, label = "Mean") +
  annotate("text", x = 13, y = 34, label = "Q3")

ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20,by=1)) +
  labs(
    title="Quantity of discharges Per Treatment Day")
```

### plot means based upon duration group membership

```{r}
#plot depression mean with each group

# New dataset for the treatment duration depression plot
Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(Duration,TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

Mothership_duration_CUDOS<-Mothership_Mean_CUDOS[1:83,]
#delete weird Na values and put NA for values
Mothership_duration_CUDOS[6:20,3] = NA
Mothership_duration_CUDOS[37:41,3] = NA
Mothership_duration_CUDOS[74:83,3] = NA
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-21),]
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-41),]
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-61),]
Mothership_duration_CUDOS

ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
  scale_color_manual(values=c("#BB9D00","red",
                              "darkred","orange"))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())+
  geom_vline(xintercept = 5,alpha =.25)+
  geom_vline(xintercept = 8,alpha =.25)+
  geom_vline(xintercept = 13,alpha =.25)+
  annotate("text", x = 5, y = 39, label = "Q1") +
  annotate("text", x = 8, y = 39, label = "Mean") +
  annotate("text", x = 13, y = 39, label = "Q3") 
```

## Depression Treatment Progress by Characteristics

#### Race
Duration 1-5 days
```{r}

#Create a New Data Set with an Average Depression Variable and Race
Mothership_Mean_CUDOS_Race<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

RaceDF1<-Mothership_Mean_CUDOS_Race[1:34,]
# plot
Race1<-ggplot(data=subset(RaceDF1,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(
    title ="Depression Severity by Race During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

duration 6-10 days
```{r}

RaceDF2<-Mothership_Long %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

RaceDF2<-RaceDF2[1:70,]

# plot
Race2<-ggplot(data=subset(RaceDF2,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(
    title ="Depression Severity by Race During Partial Hospitalization",
    subtitle = "Patient discharge 6-10 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```
Discharge 10-15
```{r}
RaceDF3<-Mothership_Long %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

RaceDF3<-RaceDF3[1:105,]

# plot
Race3<-ggplot(data=subset(RaceDF3,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization",
    subtitle = "Patient discharge 11-15 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

```{r}
RaceDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

RaceDF4<-RaceDF4[1:140,]

# plot
Race4<-ggplot(data=subset(RaceDF4,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization",
    subtitle = "Patient discharge 16+ days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
Race4
```

#### putting them all together
```{r}
ggpubr::ggarrange(Race1,Race2,Race3,Race4,ncol=2,nrow=2)
```

## GENDER IDENTITY
Create a New Data Set with an Average Depression Variable and Gender
```{r}
#GENDER IDENTITY
#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

View(Mothership_Mean_CUDOS_Gender)

#Create the Depression Line Graph by Gender
ggplot(data=subset(Mothership_Mean_CUDOS_Gender,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Gender During Partial Hospitalization")+
    #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

Duration 1-5 days
```{r}

#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long %>%
  filter(Duration == "1-5") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
GenderDF1<-Mothership_Mean_CUDOS_Gender[1:30,]
# plot
Gender1<-ggplot(data=subset(GenderDF1,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  labs(
    title ="Depression Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 1-5 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

duration 6-10 days
```{r}

GenderDF2<-Mothership_Long %>%
  filter(Duration == "6-10") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

GenderDF2<-GenderDF2[1:59,]

# plot
Gender2<-ggplot(data=subset(GenderDF2,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  labs(
    title ="Depression Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 6-10 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```
Discharge 10-15
```{r}
GenderDF3<-Mothership_Long %>%
  filter(Duration == "11-15") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

GenderDF3<-GenderDF3[1:90,]

# plot
Gender3<-ggplot(data=subset(GenderDF3,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 11-15 days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

```{r}
GenderDF4<-Mothership_Long %>%
  filter(Duration == "16+") %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
View(GenderDF4)
GenderDF4<-GenderDF4[1:120,]

# plot
Gender4<-ggplot(data=subset(GenderDF4,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Gender During Partial Hospitalization",
    subtitle = "Patient discharge 16+ days")+
  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
Gender4
```

```{r}
ggpubr::ggarrange(Gender1,Gender2,Gender3,Gender4,ncol=2,nrow=2)
```

### 2023-04-03 Depression_Vis.Rmd
Depression visualizations by duration groups (4/3)

@@
       Duration = as.factor(Duration),
-      TxYear = as.factor(TxYear)
       )
+
+Mothership$Intake_1<-mdy(Mothership$Intake_1,locale = "en_US.UTF-8")
+Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
+
+Mothership<-mutate(Mothership,
+                   TxYear = as.factor(TxYear),
+                   TxYear = recode(TxYear,
+                                   "1582"="2014",
+                                   "2021"="2020",
+                                   "2022"="2020"))
+
 ```
@@
   labs(
-    title="Quantity of discharges Per Treatment Day")
+    title="Quantity of discharges Per Treatment Day")+
+  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
+  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
+  geom_vline(xintercept = 13, color = "red",alpha =.5)+
+  annotate("text", x = 5, y = .01, label = "Q1") +
+  annotate("text", x = 8, y = .01, label = "Mean") +
+  annotate("text", x = 13, y = .01, label = "Q3")
+
 ```
@@
 #### Race
-Duration 1-5 days
+Example of plot for 1-5 days discharge
 ```{r}
-
 #Create a New Data Set with an Average Depression Variable and Race
@@
        aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
-  geom_line(size=1)+
-  geom_point()+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
   labs(
@@
   #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
   scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
@@
 
-duration 6-10 days
-```{r}
+We are going to make seperate plots for the other duration groups (i.e., 6-10 days,11-15 days, 16+ days)
+```{r,include=FALSE}
 
+######## 6-10 days
 RaceDF2<-Mothership_Long %>%
@@
   theme(legend.title=element_blank())
-```
-Discharge 10-15
-```{r}
+
+######## 11-15 days
 RaceDF3<-Mothership_Long %>%
@@
        aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
-  geom_line(size=1)+
-  geom_point()+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
   labs(title ="Depression Severity by Race During Partial Hospitalization",
@@
   theme(legend.title=element_blank())
-```
 
-```{r}
+######## 16+ days
 RaceDF4<-Mothership_Long %>%
@@
   theme(legend.title=element_blank())
-Race4
 ```
@@
 ## GENDER IDENTITY
-Create a New Data Set with an Average Depression Variable and Gender
+Create a New Data Set with an Average Depression Variable and Gender, then plot it
 ```{r}
@@
 
-View(Mothership_Mean_CUDOS_Gender)
-
 #Create the Depression Line Graph by Gender
@@
   ggtitle("Depression Severity by Gender During Partial Hospitalization")+
-    #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
   scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
@@
   theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
+  theme(legend.title=element_blank())+geom_vline(xintercept = 5,alpha =.25)+
+  geom_vline(xintercept = 8,alpha =.25)+
+  geom_vline(xintercept = 13,alpha =.25)+
+  annotate("text", x = 5, y = 59, label = "Q1") +
+  annotate("text", x = 8, y = 59, label = "Mean") +
+  annotate("text", x = 13, y = 59, label = "Q3") 
 ```
 
-Duration 1-5 days
-```{r}
-
+Break it up by duration group 
+```{r, include= FALSE}
 #Create a New Data Set with an Average Depression Variable and Gender
@@
        aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
-  geom_line(size=1)+
-  geom_point()+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
   labs(
@@
   #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
+  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
   scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
@@
   theme(legend.title=element_blank())
-```
 
-duration 6-10 days
-```{r}
-
+##### 5-10 Days
 GenderDF2<-Mothership_Long %>%
@@
   theme(legend.title=element_blank())
-```
-Discharge 10-15
-```{r}
+
+##### 10-15 Days
 GenderDF3<-Mothership_Long %>%
@@
        aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
-  geom_line(size=1)+
-  geom_point()+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
   labs(title ="Depression Severity by Gender During Partial Hospitalization",
@@
   #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 16+ Days
+GenderDF4<-Mothership_Long %>%
+  filter(Duration == "16+") %>%
+  group_by(TxDay,Gender_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+GenderDF4<-GenderDF4[1:120,]
+
+# plot
+Gender4<-ggplot(data=subset(GenderDF4,!is.na(Gender_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Depression Severity by Gender During Partial Hospitalization",
+    subtitle = "Patient discharge 16+ days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
   scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
@@
 ```{r}
-GenderDF4<-Mothership_Long %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,Gender_1) %>%
+ggpubr::ggarrange(Gender1,Gender2,Gender3,Gender4,ncol=2,nrow=2)
+```
+
+#### TREATMENT TRACK
+```{r}
+#Create a New Data Set with an Average Depression Variable and Track
+Mothership_Mean_CUDOS_Track<-Mothership_Long %>%
+  group_by(TxDay,IPT_track_1) %>%
   summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-View(GenderDF4)
-GenderDF4<-GenderDF4[1:120,]
 
-# plot
-Gender4<-ggplot(data=subset(GenderDF4,!is.na(Gender_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
+#Create the Depression Line Graph by Treatment Track
+ggplot(data=subset(Mothership_Mean_CUDOS_Track,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
   geom_line(size=1)+
   geom_point()+
-  labs(title ="Depression Severity by Gender During Partial Hospitalization",
-    subtitle = "Patient discharge 16+ days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-  scale_x_continuous(name="Depression Severity",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
+  ggtitle("Depression Severity by Treatment Track During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#0065A3"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())+
+  geom_vline(xintercept = 5,alpha =.25)+
+  geom_vline(xintercept = 8,alpha =.25)+
+  geom_vline(xintercept = 13,alpha =.25)+
+  annotate("text", x = 5, y = 39, label = "Q1") +
+  annotate("text", x = 8, y = 39, label = "Mean") +
+  annotate("text", x = 13, y = 39, label = "Q3") 
+```
+
+Break it up by duration group (Treatment track)
+```{r, include= FALSE}
+#Create a New Data Set with an Average Depression Variable and Gender
+TrackDF1<-Mothership_Long %>%
+  filter(Duration == "1-5") %>%
+  group_by(TxDay,IPT_track_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+TrackDF1<-TrackDF1[1:20,]
+# plot
+Track1<-ggplot(data=subset(TrackDF1,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Depression Severity by Track During Partial Hospitalization",
+    subtitle = "Patient discharge 1-5 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
@@
   theme(legend.title=element_blank())
-Gender4
+
+##### 5-10 Days
+TrackDF2<-Mothership_Long %>%
+  filter(Duration == "6-10") %>%
+  group_by(TxDay,IPT_track_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+TrackDF2<-TrackDF2[1:40,]
+
+# plot
+Track2<-ggplot(data=subset(TrackDF2,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Depression Severity by Track During Partial Hospitalization",
+    subtitle = "Patient discharge 6-10 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 10-15 Days
+TrackDF3<-Mothership_Long %>%
+  filter(Duration == "11-15") %>%
+  group_by(TxDay,IPT_track_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+TrackDF3<-TrackDF3[1:60,]
+
+# plot
+Track3<-ggplot(data=subset(TrackDF3,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Depression Severity by Track During Partial Hospitalization",
+    subtitle = "Patient discharge 11-15 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 16+ Days
+TrackDF4<-Mothership_Long %>%
+  filter(Duration == "16+") %>%
+  group_by(TxDay,IPT_track_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+TrackDF4<-TrackDF4[1:80,]
+
+# plot
+Track4<-ggplot(data=subset(TrackDF4,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Depression Severity by Track During Partial Hospitalization",
+    subtitle = "Patient discharge 16+ days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
 ```
@@
 ```{r}
-ggpubr::ggarrange(Gender1,Gender2,Gender3,Gender4,ncol=2,nrow=2)
+ggpubr::ggarrange(Track1,Track2,Track3,Track4,ncol=2,nrow=2)
 ```
+### EDUCATION
+```{r}
+#Create a New Data Set with an Average Depression Variable and Education
+Mothership_Mean_CUDOS_Ed<-Mothership_Long %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+#Create the Depression Line Graph by Education
+ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())+
+  geom_vline(xintercept = 5,alpha =.25)+
+  geom_vline(xintercept = 8,alpha =.25)+
+  geom_vline(xintercept = 13,alpha =.25)+
+  annotate("text", x = 5, y = 39, label = "Q1") +
+  annotate("text", x = 8, y = 39, label = "Mean") +
+  annotate("text", x = 13, y = 39, label = "Q3") 
+```
+
+Break it up by duration group 
+```{r, include= FALSE}
+#Create a New Data Set with an Average Depression Variable and Gender
+EducationDF1<-Mothership_Long %>%
+  filter(Duration == "1-5") %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+EducationDF1<-EducationDF1[1:45,]
+# plot
+Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Depression Severity by Education Level During Partial Hospitalization",
+    subtitle = "Patient discharge 1-5 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 5-10 Days
+EducationDF2<-Mothership_Long %>%
+  filter(Duration == "6-10") %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+EducationDF2<-EducationDF2[1:90,]
+
+# plot
+Education2<-ggplot(data=subset(EducationDF2,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Depression Severity by Education Level During Partial Hospitalization",
+    subtitle = "Patient discharge 6-10 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 10-15 Days
+EducationDF3<-Mothership_Long %>%
+  filter(Duration == "11-15") %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+EducationDF3<-EducationDF3[1:135,]
+
+# plot
+Education3<-ggplot(data=subset(EducationDF3,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Depression Severity by Education Level During Partial Hospitalization",
+    subtitle = "Patient discharge 11-15 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 16+ Days
+EducationDF4<-Mothership_Long %>%
+  filter(Duration == "16+") %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+EducationDF4<-EducationDF4[1:180,]
+
+# plot
+Education4<-ggplot(data=subset(EducationDF4,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Depression Severity by Education Level During Partial Hospitalization",
+    subtitle = "Patient discharge 16+ days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,50,by=5))+
+   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+```{r}
+ggpubr::ggarrange(Education1,Education2,Education3,Education4, ncol=2,nrow=2)
+```
+### TREATMENT YEAR
+```{r}
+#Create a New Data Set with an Average Depression Variable and Year
+Mothership_Mean_CUDOS_Year<-Mothership_Long %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+str(Mothership_Long$TxYear)
+
+#Create the Depression Line Graph by Year
+ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,36,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559","#4B5D8E"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+Break it up by duration group (Year)
+```{r, include= FALSE}
+#Create a New Data Set with an Average Depression Variable and Gender
+YEARTXDF1<-Mothership_Long %>%
+  filter(Duration == "1-5") %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+YEARTXDF1<-YEARTXDF1[1:50,]
+# plot
+YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Depression Severity by YEARTX During Partial Hospitalization",
+    subtitle = "Patient discharge 1-5 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 5-10 Days
+YEARTXDF2<-Mothership_Long %>%
+  filter(Duration == "6-10") %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+YEARTXDF2<-YEARTXDF2[1:100,]
+
+# plot
+YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Depression Severity by YEARTX During Partial Hospitalization",
+    subtitle = "Patient discharge 6-10 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 10-15 Days
+YEARTXDF3<-Mothership_Long %>%
+  filter(Duration == "11-15") %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+YEARTXDF3<-YEARTXDF3[1:150,]
+
+# plot
+YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Depression Severity by YEARTX During Partial Hospitalization",
+    subtitle = "Patient discharge 11-15 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 16+ Days
+YEARTXDF4<-Mothership_Long %>%
+  filter(Duration == "16+") %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+YEARTXDF4<-YEARTXDF4[1:200,]
+
+# plot
+YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Depression Severity by YEARTX During Partial Hospitalization",
+    subtitle = "Patient discharge 16+ days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+```{r}
+ggpubr::ggarrange(YEARTX1,YEARTX2,YEARTX3,YEARTX4,ncol=2,nrow=2)
+```

### 2023-04-03 Data_Import.Rmd
Deleted depression stuff from the inport file

@@
 library(ggplot2)
-## long / wide data
 library(tidyr)
@@
 df <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
-view(df)
+#view(df)
 Mothership<-select(df,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
@@
 
+## Export as CSV
+```{r}
+write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Vis.csv")
+```
+
+# Background Statistics
 ```{r}
@@
 ```
-
-## Depression Treatment Progress Charts
-
-```{r}
-Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
-Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]
-
-#Create a Time Variable
-Mothership_Long$TxDay <- NA
-Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
-Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
-Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
-Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
-Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
-Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
-Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
-Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
-Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
-Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
-Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
-Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
-Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
-Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
-Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
-Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
-Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
-Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
-Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
-Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20
-
-#Create a New Data Set with an Average Depression Variable
-Mothership_Mean_CUDOS<-Mothership_Long %>%
-  group_by(TxDay) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-```
-
-```{r}
-#Plot the Depression Mean for Full Sample
-ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
-  geom_line(size=1,color="#0065A3")+
-  geom_point(color="#0065A3")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  ggtitle("Mean Depression Severity During Partial Hospitalization")+
-  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
-  theme(panel.background=NULL) +
-  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
-  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
-  geom_vline(xintercept = 13, color = "red",alpha =.5)+
-  annotate("text", x = 5, y = 34, label = "Q1") +
-  annotate("text", x = 8, y = 34, label = "Mean") +
-  annotate("text", x = 13, y = 34, label = "Q3")
-
-ggplot(Mothership, aes(Days_complete_1))+
-  geom_density()+
-  scale_x_continuous(limits=c(0,20)) +
-  labs(
-    title="Quantity of discharges Per Treatment Day")
-
-```
-
-### plot means based upon duration group membership 
-```{r}
-ggplot(Mothership, aes(x = Duration, y = Days_complete_1)) +
-  geom_violin()+
-  geom_boxplot(width=0.1, color="blue", alpha=0.2)
-
-Mothership_duration_CUDOS<-Mothership_Long %>%
-  group_by(TxDay,Duration) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-```
-
-```{r}
-#plot depression mean with each group
-
-Mothership_Mean_CUDOS<-Mothership_Long %>%
-  group_by(Duration,TxDay) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-Mothership_duration_CUDOS<-Mothership_Mean_CUDOS[1:83,]
-#delete weird Na values and put NA for values
-Mothership_duration_CUDOS[6:20,3] = NA
-Mothership_duration_CUDOS[37:41,3] = NA
-Mothership_duration_CUDOS[74:83,3] = NA
-Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-21),]
-Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-41),]
-Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-61),]
-Mothership_duration_CUDOS
-
-ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
-  geom_line(size=1)+
-  geom_point()+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  ggtitle("Mean Depression Severity During Partial Hospitalization")+
-  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
-  scale_color_manual(values=c("#BB9D00","red",
-                              "darkred","orange"))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+
-  geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 39, label = "Q1") +
-  annotate("text", x = 8, y = 39, label = "Mean") +
-  annotate("text", x = 13, y = 39, label = "Q3")
-
-```

### 2023-04-03 Anxiety_Vis.Rmd
Initial transfer of code from depression Rmd. pls double check code.

@@
       Duration = as.factor(Duration),
-      TxYear = as.factor(TxYear)
       )
+
+Mothership$Intake_1<-mdy(Mothership$Intake_1,locale = "en_US.UTF-8")
+Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
+
+Mothership<-mutate(Mothership,
+                   TxYear = as.factor(TxYear),
+                   TxYear = recode(TxYear,
+                                   "1582"="2014",
+                                   "2021"="2020",
+                                   "2022"="2020"))
+
 ```
+
+# Anxiety Treatment Progress Charts
+
+```{r}
+Mothership_Long <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
+Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]
+
+#Create a Time Variable
+Mothership_Long$TxDay <- NA
+Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUXOS"]<-1
+Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUXOS"]<-2
+Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUXOS"]<-3
+Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUXOS"]<-4
+Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUXOS"]<-5
+Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUXOS"]<-6
+Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUXOS"]<-7
+Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUXOS"]<-8
+Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUXOS"]<-9
+Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUXOS"]<-10
+Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUXOS"]<-11
+Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUXOS"]<-12
+Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUXOS"]<-13
+Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUXOS"]<-14
+Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUXOS"]<-15
+Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUXOS"]<-16
+Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUXOS"]<-17
+Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUXOS"]<-18
+Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUXOS"]<-19
+Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUXOS"]<-20
+
+#Create a New Data Set with an Average Anxiety Variable
+Mothership_Mean_CUXOS<-Mothership_Long %>%
+  group_by(TxDay) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+```
+
+```{r}
+#Plot the Anxiety Mean for Full Sample
+ggplot(data=Mothership_Mean_CUXOS,aes(x=TxDay,y=mean_CUXOS))+
+  geom_line(size=1,color="#0065A3")+
+  geom_point(color="#0065A3")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(20,40,by=5))+
+  theme(panel.background=NULL) +
+  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
+  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
+  geom_vline(xintercept = 13, color = "red",alpha =.5)+
+  annotate("text", x = 5, y = 39, label = "Q1") +
+  annotate("text", x = 8, y = 39, label = "Mean") +
+  annotate("text", x = 13, y = 39, label = "Q3")
+
+ggplot(Mothership, aes(Days_complete_1))+
+  geom_density()+
+  scale_x_continuous(limits=c(0,20,by=1)) +
+  labs(
+    title="Quantity of discharges Per Treatment Day")+
+  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
+  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
+  geom_vline(xintercept = 13, color = "red",alpha =.5)+
+  annotate("text", x = 5, y = .01, label = "Q1") +
+  annotate("text", x = 8, y = .01, label = "Mean") +
+  annotate("text", x = 13, y = .01, label = "Q3")
+
+```
+
+### plot means based upon duration group membership
+
+```{r}
+#plot Anxiety mean with each group
+
+# New dataset for the treatment duration Anxiety plot
+Mothership_Mean_CUXOS<-Mothership_Long %>%
+  group_by(Duration,TxDay) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
+#delete weird Na values and put NA for values
+Mothership_duration_CUXOS[6:20,3] = NA
+Mothership_duration_CUXOS[37:41,3] = NA
+Mothership_duration_CUXOS[74:83,3] = NA
+Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-21),]
+Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-41),]
+Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-61),]
+Mothership_duration_CUXOS
+
+ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration,color=Duration))+
+  geom_line(size=1)+
+  geom_point()+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(5,50,by=5))+
+  scale_color_manual(values=c("#BB9D00","red",
+                              "darkred","orange"))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())+
+  geom_vline(xintercept = 5,alpha =.25)+
+  geom_vline(xintercept = 8,alpha =.25)+
+  geom_vline(xintercept = 13,alpha =.25)+
+  annotate("text", x = 5, y = 49, label = "Q1") +
+  annotate("text", x = 8, y = 49, label = "Mean") +
+  annotate("text", x = 13, y = 49, label = "Q3") 
+```
+
+## Anxiety Treatment Progress by Characteristics
+
+#### Race
+Example of plot for 1-5 days discharge
+```{r}
+#Create a New Data Set with an Average Anxiety Variable and Race
+Mothership_Mean_CUXOS_Race<-Mothership_Long %>%
+  filter(Duration == "1-5") %>%
+  group_by(TxDay,Race_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+RaceDF1<-Mothership_Mean_CUXOS_Race[1:34,]
+# plot
+Race1<-ggplot(data=subset(RaceDF1,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Anxiety Severity by Race During Partial Hospitalization",
+    subtitle = "Patient discharge 1-5 days")+
+  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+We are going to make seperate plots for the other duration groups (i.e., 6-10 days,11-15 days, 16+ days)
+```{r,include=FALSE}
+
+######## 6-10 days
+RaceDF2<-Mothership_Long %>%
+  filter(Duration == "6-10") %>%
+  group_by(TxDay,Race_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+RaceDF2<-RaceDF2[1:70,]
+
+# plot
+Race2<-ggplot(data=subset(RaceDF2,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Anxiety Severity by Race During Partial Hospitalization",
+    subtitle = "Patient discharge 6-10 days")+
+  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+######## 11-15 days
+RaceDF3<-Mothership_Long %>%
+  filter(Duration == "11-15") %>%
+  group_by(TxDay,Race_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+RaceDF3<-RaceDF3[1:105,]
+
+# plot
+Race3<-ggplot(data=subset(RaceDF3,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by Race During Partial Hospitalization",
+    subtitle = "Patient discharge 11-15 days")+
+  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+######## 16+ days
+RaceDF4<-Mothership_Long %>%
+  filter(Duration == "16+") %>%
+  group_by(TxDay,Race_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+RaceDF4<-RaceDF4[1:150,]
+
+# plot
+Race4<-ggplot(data=subset(RaceDF4,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by Race During Partial Hospitalization",
+    subtitle = "Patient discharge 16+ days")+
+  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+#### putting them all together
+```{r}
+ggpubr::ggarrange(Race1,Race2,Race3,Race4,ncol=2,nrow=2)
+```
+
+## GENDER IDENTITY
+Create a New Data Set with an Average Anxiety Variable and Gender, then plot it
+```{r}
+#GENDER IDENTITY
+#Create a New Data Set with an Average Anxiety Variable and Gender
+Mothership_Mean_CUXOS_Gender<-Mothership_Long %>%
+  group_by(TxDay,Gender_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+#Create the Anxiety Line Graph by Gender
+ggplot(data=subset(Mothership_Mean_CUXOS_Gender,!is.na(Gender_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Anxiety Severity by Gender During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())+geom_vline(xintercept = 5,alpha =.25)+
+  geom_vline(xintercept = 8,alpha =.25)+
+  geom_vline(xintercept = 13,alpha =.25)+
+  annotate("text", x = 5, y = 59, label = "Q1") +
+  annotate("text", x = 8, y = 59, label = "Mean") +
+  annotate("text", x = 13, y = 59, label = "Q3") 
+```
+
+Break it up by duration group 
+```{r, include= FALSE}
+#Create a New Data Set with an Average Anxiety Variable and Gender
+Mothership_Mean_CUXOS_Gender<-Mothership_Long %>%
+  filter(Duration == "1-5") %>%
+  group_by(TxDay,Gender_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+GenderDF1<-Mothership_Mean_CUXOS_Gender[1:30,]
+# plot
+Gender1<-ggplot(data=subset(GenderDF1,!is.na(Gender_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Anxiety Severity by Gender During Partial Hospitalization",
+    subtitle = "Patient discharge 1-5 days")+
+  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 5-10 Days
+GenderDF2<-Mothership_Long %>%
+  filter(Duration == "6-10") %>%
+  group_by(TxDay,Gender_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+GenderDF2<-GenderDF2[1:59,]
+
+# plot
+Gender2<-ggplot(data=subset(GenderDF2,!is.na(Gender_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Anxiety Severity by Gender During Partial Hospitalization",
+    subtitle = "Patient discharge 6-10 days")+
+  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 10-15 Days
+GenderDF3<-Mothership_Long %>%
+  filter(Duration == "11-15") %>%
+  group_by(TxDay,Gender_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+GenderDF3<-GenderDF3[1:90,]
+
+# plot
+Gender3<-ggplot(data=subset(GenderDF3,!is.na(Gender_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by Gender During Partial Hospitalization",
+    subtitle = "Patient discharge 11-15 days")+
+  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 16+ Days
+GenderDF4<-Mothership_Long %>%
+  filter(Duration == "16+") %>%
+  group_by(TxDay,Gender_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+GenderDF4<-GenderDF4[1:120,]
+
+# plot
+Gender4<-ggplot(data=subset(GenderDF4,!is.na(Gender_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by Gender During Partial Hospitalization",
+    subtitle = "Patient discharge 16+ days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+```{r}
+ggpubr::ggarrange(Gender1,Gender2,Gender3,Gender4,ncol=2,nrow=2)
+```
+
+#### TREATMENT TRACK
+```{r}
+#Create a New Data Set with an Average Anxiety Variable and Track
+Mothership_Mean_CUXOS_Track<-Mothership_Long %>%
+  group_by(TxDay,IPT_track_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+#Create the Anxiety Line Graph by Treatment Track
+ggplot(data=subset(Mothership_Mean_CUXOS_Track,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Anxiety Severity by Treatment Track During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(20,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#0065A3"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())+
+  geom_vline(xintercept = 5,alpha =.25)+
+  geom_vline(xintercept = 8,alpha =.25)+
+  geom_vline(xintercept = 13,alpha =.25)+
+  annotate("text", x = 5, y = 39, label = "Q1") +
+  annotate("text", x = 8, y = 39, label = "Mean") +
+  annotate("text", x = 13, y = 39, label = "Q3") 
+```
+
+Break it up by duration group (Treatment track)
+```{r, include= FALSE}
+#Create a New Data Set with an Average Anxiety Variable and Gender
+TrackDF1<-Mothership_Long %>%
+  filter(Duration == "1-5") %>%
+  group_by(TxDay,IPT_track_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+TrackDF1<-TrackDF1[1:20,]
+# plot
+Track1<-ggplot(data=subset(TrackDF1,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Anxiety Severity by Track During Partial Hospitalization",
+    subtitle = "Patient discharge 1-5 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 5-10 Days
+TrackDF2<-Mothership_Long %>%
+  filter(Duration == "6-10") %>%
+  group_by(TxDay,IPT_track_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+TrackDF2<-TrackDF2[1:50,]
+
+# plot
+Track2<-ggplot(data=subset(TrackDF2,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Anxiety Severity by Track During Partial Hospitalization",
+    subtitle = "Patient discharge 6-10 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 10-15 Days
+TrackDF3<-Mothership_Long %>%
+  filter(Duration == "11-15") %>%
+  group_by(TxDay,IPT_track_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+TrackDF3<-TrackDF3[1:60,]
+
+# plot
+Track3<-ggplot(data=subset(TrackDF3,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by Track During Partial Hospitalization",
+    subtitle = "Patient discharge 11-15 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 16+ Days
+TrackDF4<-Mothership_Long %>%
+  filter(Duration == "16+") %>%
+  group_by(TxDay,IPT_track_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+TrackDF4<-TrackDF4[1:80,]
+
+# plot
+Track4<-ggplot(data=subset(TrackDF4,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by Track During Partial Hospitalization",
+    subtitle = "Patient discharge 16+ days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+```{r}
+ggpubr::ggarrange(Track1,Track2,Track3,Track4,ncol=2,nrow=2)
+```
+### EDUCATION
+```{r}
+#Create a New Data Set with an Average Anxiety Variable and Education
+Mothership_Mean_CUXOS_Ed<-Mothership_Long %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+#Create the Anxiety Line Graph by Education
+ggplot(data=subset(Mothership_Mean_CUXOS_Ed,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  ggtitle("Anxiety Severity by Education Level During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(20,38,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())+
+  geom_vline(xintercept = 5,alpha =.25)+
+  geom_vline(xintercept = 8,alpha =.25)+
+  geom_vline(xintercept = 13,alpha =.25)+
+  annotate("text", x = 5, y = 39, label = "Q1") +
+  annotate("text", x = 8, y = 39, label = "Mean") +
+  annotate("text", x = 13, y = 39, label = "Q3") 
+```
+
+Break it up by duration group 
+```{r, include= FALSE}
+#Create a New Data Set with an Average Anxiety Variable and Gender
+EducationDF1<-Mothership_Long %>%
+  filter(Duration == "1-5") %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+EducationDF1<-EducationDF1[1:45,]
+# plot
+Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by Education Level During Partial Hospitalization",
+    subtitle = "Patient discharge 1-5 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 5-10 Days
+EducationDF2<-Mothership_Long %>%
+  filter(Duration == "6-10") %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+EducationDF2<-EducationDF2[1:90,]
+
+# plot
+Education2<-ggplot(data=subset(EducationDF2,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by Education Level During Partial Hospitalization",
+    subtitle = "Patient discharge 6-10 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 10-15 Days
+EducationDF3<-Mothership_Long %>%
+  filter(Duration == "11-15") %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+EducationDF3<-EducationDF3[1:135,]
+
+# plot
+Education3<-ggplot(data=subset(EducationDF3,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by Education Level During Partial Hospitalization",
+    subtitle = "Patient discharge 11-15 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 16+ Days
+EducationDF4<-Mothership_Long %>%
+  filter(Duration == "16+") %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+EducationDF4<-EducationDF4[1:180,]
+
+# plot
+Education4<-ggplot(data=subset(EducationDF4,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by Education Level During Partial Hospitalization",
+    subtitle = "Patient discharge 16+ days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+```{r}
+ggpubr::ggarrange(Education1,Education2,Education3,Education4, ncol=2,nrow=2)
+```
+### TREATMENT YEAR
+```{r}
+#Create a New Data Set with an Average Anxiety Variable and Year
+Mothership_Mean_CUXOS_Year<-Mothership_Long %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+str(Mothership_Long$TxYear)
+
+#Create the Anxiety Line Graph by Year
+ggplot(data=subset(Mothership_Mean_CUXOS_Year,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUXOS,group=TxYear,color=TxYear))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Anxiety Severity by Treatment Year During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(20,36,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559","#4B5D8E"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+Break it up by duration group (Year)
+```{r, include= FALSE}
+#Create a New Data Set with an Average Anxiety Variable and Gender
+YEARTXDF1<-Mothership_Long %>%
+  filter(Duration == "1-5") %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+YEARTXDF1<-YEARTXDF1[1:50,]
+# plot
+YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUXOS,group=TxYear,color=TxYear))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Anxiety Severity by YEARTX During Partial Hospitalization",
+    subtitle = "Patient discharge 1-5 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 5-10 Days
+YEARTXDF2<-Mothership_Long %>%
+  filter(Duration == "6-10") %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+YEARTXDF2<-YEARTXDF2[1:100,]
+
+# plot
+YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUXOS,group=TxYear,color=TxYear))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(
+    title ="Anxiety Severity by YEARTX During Partial Hospitalization",
+    subtitle = "Patient discharge 6-10 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 10-15 Days
+YEARTXDF3<-Mothership_Long %>%
+  filter(Duration == "11-15") %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+YEARTXDF3<-YEARTXDF3[1:150,]
+
+# plot
+YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUXOS,group=TxYear,color=TxYear))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by YEARTX During Partial Hospitalization",
+    subtitle = "Patient discharge 11-15 days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+##### 16+ Days
+YEARTXDF4<-Mothership_Long %>%
+  filter(Duration == "16+") %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+YEARTXDF4<-YEARTXDF4[1:200,]
+
+# plot
+YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUXOS,group=TxYear,color=TxYear))+
+  geom_line(size=.5)+
+  geom_point(size=.5)+
+  labs(title ="Anxiety Severity by YEARTX During Partial Hospitalization",
+    subtitle = "Patient discharge 16+ days")+
+    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+```{r}
+ggpubr::ggarrange(YEARTX1,YEARTX2,YEARTX3,YEARTX4,ncol=2,nrow=2)
+```

### 2023-04-03 Anxiety_Vis.Rmd
Finalized anxiety visualizations by discharge

@@
 #### Race
+```{r}
+#Overall race
+Mothership_Mean_CUXOS_Race<-Mothership_Long %>%
+  group_by(TxDay,Race_1) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+# plot
+ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
+  geom_line(size=1)+
+  geom_point()+
+  labs(title ="Depression Severity by Race During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())+
+   geom_vline(xintercept = 5,alpha =.25)+
+  geom_vline(xintercept = 8,alpha =.25)+
+  geom_vline(xintercept = 13,alpha =.25)+
+  annotate("text", x = 5, y = 39, label = "Q1") +
+  annotate("text", x = 8, y = 39, label = "Mean") +
+  annotate("text", x = 13, y = 39, label = "Q3") 
+```
+
 Example of plot for 1-5 days discharge
@@
   scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(20,50,by=5))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(20,46,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#0065A3"))+
@@
   geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 39, label = "Q1") +
-  annotate("text", x = 8, y = 39, label = "Mean") +
-  annotate("text", x = 13, y = 39, label = "Q3") 
+  annotate("text", x = 5, y = 45, label = "Q1") +
+  annotate("text", x = 8, y = 45, label = "Mean") +
+  annotate("text", x = 13, y = 45, label = "Q3") 
 ```
@@
 
-TrackDF2<-TrackDF2[1:50,]
+TrackDF2<-TrackDF2[1:40,]
 
@@
        aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
+  geom_line(size=1)+
+  geom_point()+
   ggtitle("Anxiety Severity by Education Level During Partial Hospitalization")+
     scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(20,38,by=5))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(20,50,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
@@
   geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 39, label = "Q1") +
-  annotate("text", x = 8, y = 39, label = "Mean") +
-  annotate("text", x = 13, y = 39, label = "Q3") 
+  annotate("text", x = 5, y = 49, label = "Q1") +
+  annotate("text", x = 8, y = 49, label = "Mean") +
+  annotate("text", x = 13, y = 49, label = "Q3") 
 ```

### 2023-04-03 Depression_Vis.Rmd
Final depression visualizations by discharge

@@
 #### Race
+```{r}
+#Overall race
+Mothership_Mean_CUDOS_Race<-Mothership_Long %>%
+  group_by(TxDay,Race_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+# plot
+ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
+  geom_line(size=1)+
+  geom_point()+
+  labs(title ="Depression Severity by Race During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())+
+   geom_vline(xintercept = 5,alpha =.25)+
+  geom_vline(xintercept = 8,alpha =.25)+
+  geom_vline(xintercept = 13,alpha =.25)+
+  annotate("text", x = 5, y = 39, label = "Q1") +
+  annotate("text", x = 8, y = 39, label = "Mean") +
+  annotate("text", x = 13, y = 39, label = "Q3") 
+```
+
 Example of plot for 1-5 days discharge

### 2023-04-03 Data_Import.Rmd
Creating the disorder variables.

@@
 #Lets make some new variables 
+      #Duration of treatment
                      Duration = as.factor(
@@
                        ifelse(Days_complete_1>10 & Days_complete_1 <=15, "11-15", "16+"
-                              )))))
-# Disorder subtypes 
+                              )))),
+      #Disorder subtypes 
           # Mood Disorders
+                     Mood_D = as.factor(
+                      ifelse(
+                        MDD_C ==1 | AnyBipolar_C == 1 | Bipolar1_C == 1 | Dysthymia_C == 1 |
+                        OtherMood_C, 1, 0)),
           # Anxiety Disorders
+                    Anxiety_D = as.factor(
+                      ifelse(
+                        GAD_C ==1 | Panic_C == 1 | PanicAgor_C == 1 | Agoraphobia_C == 1 |
+                        Social_C == 1 | Specific_C == 1 | OtherAnx_C, 1, 0)),
           # Obsessive Compusive Disorders
+                #OCD_C is for current OCD
           # Personality Disorders
+                #BPD_C is for current BPD
           # Substance Use Disorders
-# Trauma related disorders
+                    Substance_D = as.factor(
+                      ifelse(
+                        Alcohol_C == 1 | Drug_C ==1, 1, 0)),
+          # Trauma or stresor related disorders
+                    Trauma_D = as.factor(
+                      ifelse(PTSD_C == 1 | Adjustment_C ==1, 1,0)),
           # Psychotic Disorders
+                    Psychotic_D = as.factor(
+                      ifelse(
+                        Schiz_C == 1 | Schizaff_C == 1 | AnyPsychotic_C ==1,1,0)),
             # Eating Disorders
+                    Eating_D = as.factor(
+                      ifelse(
+                        AnyEating_C ==1 | Anorex_C == 1 | Bulim_C == 1 | Binge_C == 1, 1,0))
+                    )
+                    Disorder_Type = as.factor(
+
+                    )
 
@@
 ```
+
+#### Amount of disorders treated
+```{r}
+
+```

### 2023-04-03 Data_Import.Rmd
Disorder_type variable

--- 2023-04-03 Data_Import.Rmd
@@
                        ifelse(Days_complete_1>10 & Days_complete_1 <=15, "11-15", "16+"
-                              )))))
-# Disorder subtypes 
+                              )))),
+      #Disorder subtypes 
           # Mood Disorders
+                     Mood_D = as.factor(
+                      ifelse(
+                        MDD_C ==1 | AnyBipolar_C == 1 | Bipolar1_C == 1 | Dysthymia_C == 1 |
+                        OtherMood_C, 1, 0)),
           # Anxiety Disorders
+                    Anxiety_D = as.factor(
+                      ifelse(
+                        GAD_C ==1 | Panic_C == 1 | PanicAgor_C == 1 | Agoraphobia_C == 1 |
+                        Social_C == 1 | Specific_C == 1 | OtherAnx_C, 1, 0)),
           # Obsessive Compusive Disorders
+                #OCD_C is for current OCD
           # Personality Disorders
+                #BPD_C is for current BPD
           # Substance Use Disorders
-# Trauma related disorders
+                    Substance_D = as.factor(
+                      ifelse(
+                        Alcohol_C == 1 | Drug_C ==1, 1, 0)),
+          # Trauma or stresor related disorders
+                    Trauma_D = as.factor(
+                      ifelse(PTSD_C == 1 | Adjustment_C ==1, 1,0)),
           # Psychotic Disorders
+                    Psychotic_D = as.factor(
+                      ifelse(
+                        Schiz_C == 1 | Schizaff_C == 1 | AnyPsychotic_C ==1,1,0)),
             # Eating Disorders
+                    Eating_D = as.factor(
+                      ifelse(
+                        AnyEating_C ==1 | Anorex_C == 1 | Bulim_C == 1 | Binge_C == 1, 1,0)),
+                    Disorder_Type = as.factor(
+                      ifelse(Anxiety_D == 1, "Anxiety",
+                      ifelse(Mood_D == 1, "Mood",
+                      ifelse(OCD_C ==1, "OCD",
+                      ifelse(BPD_C == 1, "Personality",
+                      ifelse(Substance_D == 1, "Substance Use",
+                      ifelse(Trauma_D == 1, "Trauma or Stressor",
+                      ifelse(Eating_D ==1, "Eating",
+                      ifelse(
+                        #Comorbid stuff
+                        Anxiety_D == 1 & Mood_D == 1 |
+                        Anxiety_D == 1 & OCD_C == 1 |
+                        Anxiety_D == 1 & BPD_C == 1 |
+                        Anxiety_D == 1 & Substance_D == 1 |
+                        Anxiety_D == 1 & Trauma_D == 1 | 
+                        Anxiety_D == 1 & Eating_D ==1 |
+                        Mood_D == 1 & OCD_C == 1 |
+                        Mood_D == 1 & BPD_C == 1 |
+                        Mood_D == 1 & Substance_D == 1 |
+                        Mood_D == 1 & Trauma_D == 1 | 
+                        Mood_D == 1 & Eating_D ==1 |
+                        OCD_C == 1 & BPD_C == 1 |
+                        OCD_C ==1 & Substance_D == 1 |
+                        OCD_C ==1 & Trauma_D == 1 |
+                        OCD_C ==1 & Eating_D ==1 |
+                        BPD_C == 1 & Substance_D == 1 |
+                        BPD_C == 1 & Trauma_D == 1 |
+                        BPD_C == 1 & Eating_D ==1 |
+                        Substance_D == 1 & Trauma_D == 1 |
+                        Substance_D == 1 & Eating_D ==1 |
+                        Trauma_D == 1 & Eating_D ==1, "Comorbid", "Other")
+                      )))))))))
 
@@
 ```
+
+#### Amount of disorders treated
+```{r}
+ggplot(data = subset(Mothership, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type))+
+  geom_bar()+
+  ggtitle("Frequency of Education Level") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Education Level")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,3000))
+```

### 2023-04-04 Data_Import.Rmd
Creating diagnosis variables, and initial visualization.

--- 2023-04-03 Data_Import.Rmd
@@
 df <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
-#view(df)
-Mothership<-select(df,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
+view(df)
+Mothership<-select(df,ID1:Sexuality_1,MDD_C:Day40_CUXOS,SUMdep_0:SUManx_1,SUMdep_DC,SUManx_DC,BL_CUDOS, BL_CUXOS)
 ```
@@
 #recode varaibles
-
+view(Mothership)
 Mothership <- mutate(Mothership, 
@@
                               )))))
-# Disorder subtypes 
-# Mood Disorders
-# Anxiety Disorders
-# Obsessive Compusive Disorders
-# Personality Disorders
-# Substance Use Disorders
-# Trauma related disorders
-# Psychotic Disorders
-# Eating Disorders
 

### 2023-04-04 Diagnosis_Vis.Rmd
Creating diagnosis variables, and initial visualization.

---
title: "Diagnosis_Vis"
output: html_document
date: "2023-04-04"
---

```{r setup, include=FALSE}
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

#Data
Mothership<-read.csv("~/Desktop/Coding/data/Mothership_Vis.csv")
Mothership<-mutate(Mothership,
      DC_status_1 = as.factor(DC_status_1),
      Education_1 = as.factor(Education_1),
      Gender_1 = as.factor(Gender_1),
      Relationship_1 = as.factor(Relationship_1),
      Sexuality_1 = as.factor(Sexuality_1),
      IPT_track_1 = as.factor(IPT_track_1),
      Race_1 = as.factor(Race_1),
      Education_1 = as.factor(Education_1),
      Duration = as.factor(Duration),
      )
```

## Create Diagnosis Variables 
```{r}
Mothership<-Mothership %>%
  mutate(
          # Mood Disorders
                     Mood_D = as.factor(
                      ifelse(
                        MDD_P ==1 | Bipolar1_P == 1 | Bipolar2_P == 1 | Dysthymia_P == 1, 1, 0)),
          # Anxiety Disorders
                    Anxiety_D = as.factor(
                      ifelse(
                        GAD_P ==1 | Panic_P == 1 | PanicAgor_P == 1 | Agoraphobia_P == 1 |
                        Social_P == 1 | Specific_P == 1, 1, 0)),
          # Obsessive Compusive Disorders
                #OCD_P is for current OCD
          # Personality Disorders
                #BPD_P is for current BPD
          # Substance Use Disorders
                    Substance_D = as.factor(
                      ifelse(
                        Alcohol_P == 1 | Drug_P ==1, 1, 0)),
          # Trauma or stresor related disorders
                    Trauma_D = as.factor(
                      ifelse(PTSD_P == 1 | Adjustment_P ==1, 1,0)),
          # Psychotic Disorders
                    Psychotic_D = as.factor(
                      ifelse(
                        Schiz_P == 1 | Schizaff_P == 1,1,0)),
            # Eating Disorders
                    Eating_D = as.factor(
                      ifelse(
                        Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1, 1,0)),
                    Disorder_Type = as.factor(
                      ifelse(Anxiety_D == 1, "Anxiety",
                      ifelse(OCD_P == 1, "OCD",
                      ifelse(BPD_P == 1, "BPD",
                      ifelse(Substance_D == 1, "Substance Use",
                      ifelse(Trauma_D == 1, "Stress and Trauma",
                      ifelse(Mood_D == 1, "Mood",
                      ifelse(Psychotic_D == 1, "Psychotic", "Eating")
                      ))))))))

                      # Comorbid_Anx = as.factor(
                      #   ifelse(Anxiety_D == 1 & Mood_D == 1 |
                      #           Anxiety_D == 1 & OCD_C == 1 |
                      #           Anxiety_D == 1 & BPD_C == 1 |
                      #           Anxiety_D == 1 & Substance_D == 1 |
                      #           Anxiety_D == 1 & Trauma_D == 1 | 
                      #           Anxiety_D == 1 & Eating_D ==1, 1, 0)),
                      # Comorbid_Mood = as.factor(
                      #   ifelse(Mood_D == 1 & Anxiety_D == 1 |
                      #           Mood_D == 1 & BPD_C == 1 |
                      #           Mood_D == 1 & BPD_C == 1 |
                      #           Mood_D == 1 & Substance_D == 1 |
                      #           Mood_D == 1 & Trauma_D == 1 | 
                      #           Mood_D == 1 & Eating_D ==1, 1, 0)),
                      # Comorbid_OCD = as.factor(
                      #   ifelse(OCD_C == 1 & Anxiety_D == 1 |
                      #           OCD_C == 1 & Mood_D == 1 |
                      #           OCD_C == 1 & BPD_C == 1 |
                      #           OCD_C == 1 & Substance_D == 1 |
                      #           OCD_C == 1 & Trauma_D == 1 | 
                      #           OCD_C == 1 & Eating_D ==1, 1, 0)),
                      # Comorbid_BPD = as.factor(
                      #   ifelse(BPD_C == 1 & Anxiety_D == 1 |
                      #           BPD_C == 1 & Mood_D == 1 |
                      #           BPD_C == 1 & OCD_C == 1 |
                      #           BPD_C == 1 & Substance_D == 1 |
                      #           BPD_C == 1 & Trauma_D == 1 | 
                      #           BPD_C == 1 & Eating_D ==1, 1, 0)),

```

#### Amount of disorders treated
```{r}
#overall psychiatric disorders
ggplot(data = subset(Mothership, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6000))+
  coord_flip()
```

### 2023-04-11 Data_Import.Rmd
YMD in lubridate code

@@
 #Convert to Date
+install.packages("lubridate")
 library("lubridate")
-Mothership$Intake_1<-mdy(Mothership$Intake_1,locale = "en_US.UTF-8")
+Mothership$Intake_1
+Mothership$Intake_1<-ymd(Mothership$Intake_1)
 Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
-
+Mothership$TxYear
 Mothership<-mutate(Mothership,

### 2023-04-11 Diagnosis_Vis.Rmd
YMD in lubridate code

@@
       )
+
+Mothership$Intake_1<-ymd(Mothership$Intake_1,locale = "en_US.UTF-8")
+Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
+Mothership<-mutate(Mothership,
+                   TxYear = as.factor(TxYear),
+                   TxYear = recode(TxYear,
+                                   "1582"="2014",
+                                   "2021"="2020",
+                                   "2022"="2020"))
 ```

### 2023-04-11 Doug_Stuff.R

@@ -7,8 +7,8 @@ library(haven)
 library(ggplot2)
 
 Mothership<-read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
-
-Mothership<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
+view(Mothership)
+Mothership<-select(Mothership,Intake_1,Days_complete_1,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
 
 ############################### Demographics ####################################
 
@@ -128,6 +128,7 @@ Mothership <- mutate(Mothership,
 #Extract Year From Intake Date
 #Convert to Date
 library("lubridate")
+
 Mothership$Intake_1<-mdy(Mothership$Intake_1,locale = "en_US.UTF-8")
 Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
 

### 2023-04-11 Depression_Vis.Rmd
ymd

@@
 
-Mothership$Intake_1<-mdy(Mothership$Intake_1,locale = "en_US.UTF-8")
+Mothership$Intake_1<-ymd(Mothership$Intake_1,locale = "en_US.UTF-8")
 Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
-
 Mothership<-mutate(Mothership,

### 2023-04-12 Anxiety_Vis.Rmd
YMD in lubridate code
changed date plots

@@
 
-Mothership$Intake_1<-mdy(Mothership$Intake_1,locale = "en_US.UTF-8")
-Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
-
-Mothership<-mutate(Mothership,
-                   TxYear = as.factor(TxYear),
-                   TxYear = recode(TxYear,
-                                   "1582"="2014",
-                                   "2021"="2020",
-                                   "2022"="2020"))
-
+Mothership$Intake_1<-ymd(Mothership$Intake_1,locale = "en_US.UTF-8")
 ```
@@
 
-str(Mothership_Long$TxYear)
-
 #Create the Anxiety Line Graph by Year
 ggplot(data=subset(Mothership_Mean_CUXOS_Year,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUXOS,group=TxYear,color=TxYear))+
+       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
   geom_line(size=1)+
@@
     scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(20,36,by=5))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(15,50,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                               "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559","#4B5D8E"))+
+                              "#91A9F1"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
@@
   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-YEARTXDF1<-YEARTXDF1[1:50,]
+YEARTXDF1<-YEARTXDF1[1:40,]
 # plot
 YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUXOS,group=TxYear,color=TxYear))+
+       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
   geom_line(size=.5)+
   geom_point(size=.5)+
-  labs(
-    title ="Anxiety Severity by YEARTX During Partial Hospitalization",
+  labs(title ="Anxiety Severity by YEARTX",
     subtitle = "Patient discharge 1-5 days")+
@@
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
@@
 
-YEARTXDF2<-YEARTXDF2[1:100,]
+YEARTXDF2<-YEARTXDF2[1:80,]
 
@@
 YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUXOS,group=TxYear,color=TxYear))+
+       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
   geom_line(size=.5)+
   geom_point(size=.5)+
-  labs(
-    title ="Anxiety Severity by YEARTX During Partial Hospitalization",
+    labs(title ="Anxiety Severity by YEARTX",
     subtitle = "Patient discharge 6-10 days")+
@@
 
-YEARTXDF3<-YEARTXDF3[1:150,]
+YEARTXDF3<-YEARTXDF3[1:120,]
 
@@
 YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUXOS,group=TxYear,color=TxYear))+
+       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
   geom_line(size=.5)+
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by YEARTX During Partial Hospitalization",
+  labs(title ="Anxiety Severity by YEARTX",
     subtitle = "Patient discharge 11-15 days")+
@@
   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-YEARTXDF4<-YEARTXDF4[1:200,]
+YEARTXDF4<-YEARTXDF4[1:160,]
 
@@
 YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUXOS,group=TxYear,color=TxYear))+
+       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
   geom_line(size=.5)+
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by YEARTX During Partial Hospitalization",
+  labs(title ="Anxiety Severity by YEARTX",
     subtitle = "Patient discharge 16+ days")+

### 2023-04-12 Data_Import.Rmd
changed date plots

--- 2023-04-04 Data_Import.Rmd
@@
 #recode varaibles
-view(Mothership)
 Mothership <- mutate(Mothership, 
@@
 library("lubridate")
-Mothership$Intake_1<-mdy(Mothership$Intake_1,locale = "en_US.UTF-8")
+Mothership$Intake_1<-ymd(Mothership$Intake_1)
 Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
-
+Mothership$TxYear
 Mothership<-mutate(Mothership,

### 2023-04-12 Depression_Vis.Rmd
date plots

@@
 ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
+       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
   geom_line(size=1)+
@@
   summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-YEARTXDF1<-YEARTXDF1[1:50,]
+YEARTXDF1<-YEARTXDF1[1:40,]
 # plot
 YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
+       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
   geom_line(size=.5)+
@@
 YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
+       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
   geom_line(size=.5)+
@@
 YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
+       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
   geom_line(size=.5)+
@@
   summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-YEARTXDF4<-YEARTXDF4[1:200,]
+YEARTXDF4<-YEARTXDF4[1:180,]
 
@@
 YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUDOS,group=TxYear,color=TxYear))+
+       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
   geom_line(size=.5)+

### 2023-04-12 Diagnosis_Vis.Rmd
Recodes

@@
                                    "2022"="2020"))
+
+s
 ```

### 2023-04-14 Data_Import.Rmd
Recodes
Created density plots per year!

--- 2023-04-04 Data_Import.Rmd
@@
 df <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
-view(df)
 Mothership<-select(df,ID1:Sexuality_1,MDD_C:Day40_CUXOS,SUMdep_0:SUManx_1,SUMdep_DC,SUManx_DC,BL_CUDOS, BL_CUXOS)
+view(Mothership)
 ```
@@
                                       "8"="Grad Degree"),
+                     DC_status_1 = as.factor(DC_status_1),
+                     DC_status_1 = recode(DC_status_1,
+                                      "1"="Treatment Complete",
+                                      "2"="Treatment Near Complete",
+                                      "3"="Insurance Stopped",
+                                      "4"="Nonattendence",
+                                      "5"="Inapproparite Language",
+                                      "6"="Transfered To Impatient",
+                                      "7"="Withdrew for External factors",
+                                      "8"="Withdrew (AMA)",
+                                      "9"="Other",
+                                      "10"="Other"),
+                    Referal_1 = as.factor(Referal_1),
+                    Referal_1 = recode(Referal_1,
+                                      "1"="Inpatient",
+                                      "2"="PHP",
+                                      "3"="APS",
+                                      "4"="Psychatrist",
+                                      "5"="PCP",
+                                      "6"="Another Physican",
+                                      "7"="Therapist",
+                                      "17"="Other"
+                    ),
 
@@
 library("lubridate")
-Mothership$Intake_1<-mdy(Mothership$Intake_1,locale = "en_US.UTF-8")
+Mothership$Intake_1<-ymd(Mothership$Intake_1)
 Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
-
 Mothership<-mutate(Mothership,

### 2023-04-14 Diagnosis_Vis.Rmd
Created density plots per year!

--- 2023-04-11 Diagnosis_Vis.Rmd
@@
                         Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1, 1,0)),
+            # Somatic Disroders
+                    Somatic_D = as.factor(
+                      ifelse(
+                        Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1,
+                        1,0)),
                     Disorder_Type = as.factor(
@@
                       ifelse(Mood_D == 1, "Mood",
-                      ifelse(Psychotic_D == 1, "Psychotic", "Eating")
-                      ))))))))
+                      ifelse(Psychotic_D == 1, "Psychotic", 
+                      ifelse(Eating_D == 1, "Eating", 
+                      ifelse(Somatic_D == 1, "Somatic", NA
+                      )))))))))),
 
+          #emotional disorders
+                  Emotional_dis = as.factor(
+                    ifelse(Anxiety_D == 1 | OCD_P == 1 | Trauma_D == 1 |
+                           Mood_D == 1, "Emotional Disorder", "Other Disorder"))
+                  )
  # Comorbid_Anx = as.factor(
@@
 
+##### df for plots
+
+# df without NAs in date and disorder type
+Mothership_Diag <- Mothership %>%
+  filter(!is.na(Disorder_Type))%>%
+  filter(!is.na(TxYear))
+
+# df with and without depression
+No_depressy <- Mothership_Diag %>%
+  filter(Disorder_Type != "Mood")
 ```
@@
 #overall psychiatric disorders
-ggplot(data = subset(Mothership, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type))+
+ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
   geom_bar()+
@@
   theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6000))+
+  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
   coord_flip()
 ```
+
+#### Number of disorders over time.
+```{r}
+# Libraries
+library(ggplot2)
+#install.packages("hrbrthemes")
+library(hrbrthemes)
+library(dplyr)
+library(tidyr)
+library(viridis)
+
+# Stacked
+ggplot(data=subset(Mothership_Diag, !is.na(Disorder_Type)), 
+       mapping= aes(x=TxYear, y = stat(count),
+                    group=Disorder_Type, fill=Disorder_Type)) +
+    geom_density(adjust=1.5,alpha=.4,position="fill") +
+    theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+     theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+     xlab("Treatment Year") +
+  theme(panel.background=NULL) +
+    facet_wrap(~Emotional_dis)+
+  labs(
+    title = "Type of Disorders Treated at the Hospital Per Year",
+    subtitle = "Broken Up By Disorder Types") +
+    xlab("Treatment Year") +
+    ylab("Percent of Patients With Disorder")
+
+# Broken up by disorder. 
+ggplot(data=subset(Mothership, !is.na(Disorder_Type)), 
+    mapping= aes(x=TxYear,y = stat(count),
+                 group=Disorder_Type, fill=Disorder_Type)) +
+  geom_density(adjust=1.5,alpha=.4) +
+  facet_wrap(~Disorder_Type)+
+  theme_classic()+
+    theme(
+      panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2),
+      axis.text.x = element_text(angle = 45,hjust = 1),
+      legend.position="none",
+      panel.spacing = unit(0.1, "lines"),
+      axis.ticks.x=element_blank(),
+      panel.background=NULL) +
+  labs(
+    title = "Type of Disorders Treated at the Hospital Per Year",
+    subtitle = "Broken Up By Dmotional vs Other Disorders") +
+    xlab("Treatment Year") +
+    ylab("Number of Patients With Disorder")
+
+```
+
+```{r}
+# without depression
+ggplot(data=subset(No_depressy, !is.na(Disorder_Type)), 
+    mapping= aes(x=TxYear,y = stat(count),
+                 group=Disorder_Type, fill=Disorder_Type)) +
+  geom_density(adjust=1.5,alpha=.4) +
+  facet_wrap(~Disorder_Type)+
+  theme_classic()+
+    theme(
+      panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2),
+      axis.text.x = element_text(angle = 45,hjust = 1),
+      legend.position="none",
+      panel.spacing = unit(0.1, "lines"),
+      axis.ticks.x=element_blank(),
+      panel.background=NULL) +
+  labs(
+    title = "Type of Disorders Treated at the Hospital Per Year",
+    subtitle = "Broken Up By Dmotional vs Other Disorders") +
+    xlab("Treatment Year") +
+    ylab("Number of Patients With Disorder")
+```

### 2023-04-15 Treatment_Outcomes.Rmd
Treatment outcomes - added RDQ plot and created variable with Post CUDOS/CUXOS scores.

---
title: "Treatment_Outcomes"
output: html_document
date: "2023-04-14"
---
```{r setup, include=FALSE}
# Libraries 
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
library("lubridate")

#Data
Mothership<-read.csv("~/Desktop/Coding/data/Mothership_Vis.csv")
Mothership<-mutate(Mothership,
      DC_status_1 = as.factor(DC_status_1),
      Education_1 = as.factor(Education_1),
      Gender_1 = as.factor(Gender_1),
      Relationship_1 = as.factor(Relationship_1),
      Sexuality_1 = as.factor(Sexuality_1),
      IPT_track_1 = as.factor(IPT_track_1),
      Race_1 = as.factor(Race_1),
      Education_1 = as.factor(Education_1),
      Duration = as.factor(Duration),
      )

Mothership$Intake_1<-ymd(Mothership$Intake_1,locale = "en_US.UTF-8")
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014",
                                   "2021"="2020",
                                   "2022"="2020"))
```

## RDQ stuff
```{r}

#Read in a New Data Set
Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))

#Make This Data Set Long Data
library(tidyr)
Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
                              factor_key = "T")
Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]

view(Mothership_Long_RDQ)

#Create a Time Variable
Mothership_Long_RDQ$PrePost <- NA
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_coping"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_pmh"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_func"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_wbs"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_sym"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_coping"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_pmh"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_func"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_wbs"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_sym"]<-"Post"

#Create a New Data Set with an Average Depression Variable and Race
Mothership_Mean_RDQ<-Mothership_Long_RDQ %>%
  group_by(rm,PrePost) %>%
  summarise(RDQ=mean(RDQ,na.rm=TRUE))

#Add a Paired Variable to the New Data Set
Mothership_Mean_RDQ<-mutate(Mothership_Mean_RDQ,
                            paired=case_when(rm=="rdqPRE_coping"~"1",
                                             rm=="rdqPOST_coping"~"1",
                                             rm=="rdqPRE_pmh"~"2",
                                             rm=="rdqPOST_pmh"~"2",
                                             rm=="rdqPRE_func"~"3",
                                             rm=="rdqPOST_func"~"3",
                                             rm=="rdqPRE_wbs"~"4",
                                             rm=="rdqPOST_wbs"~"4",
                                             rm=="rdqPRE_sym"~"5",
                                             rm=="rdqPOST_sym"~"5"))

#Pre Post RDQ Plot
ggplot(data=Mothership_Mean_RDQ,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
           group=rm,color=paired,!is.na(PrePost)))+
  geom_point(size=2.5)+
  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="RDQ Subscore")+
  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())+
  scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
                              "4"="#00BCA3","5"="#008570"),
                     labels=c("Coping Skills","Positive Mental Health",
                              "Functioning","Well-Being","Symptoms"))

```

## CUDOS and CUXOS over time.

```{r}
# Depression symptoms df
CUDOS_Score <- select(Mothership,
                      Days_complete_1,Day1_CUDOS:Day40_CUDOS)

# Anxiety symptoms df
CUXOS_Score <- select(Mothership,
                      Days_complete_1,Day1_CUXOS:Day40_CUXOS)

```

```{r}
#1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
Mothership_Pre_Post <- Mothership
  mutate(Mothership_Pre_Post, 
            Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
         )

  Mothership
#2. Then create df with CUDOS and CUXOS scores
  # Depression

    CUDOS_Score <- select(Mothership,
                      Day1_CUDOS:Day40_CUDOS)

  # Anxiety
    CUXOS_Score <- select(Mothership,
                      Day1_CUXOS:Day40_CUXOS)

#3. Extract the valeues for each patient at their last day (length of stay)
    # mutate(Mothership_Pre_Post, 
    #         CUDOS_post = CUDOS_Score[
    #           cbind(seq_along(Mothership_Pre_Post$Days_complete_W),
    #                 Mothership_Pre_Post$Days_complete_W)],
    #         CUXOS_post = CUXOS_Score[
    #           cbind(seq_along(Mothership_Pre_Post$Days_complete_W),
    #                 Mothership_Pre_Post$Days_complete_W)]
    #      )
```

```{r}
CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]
CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]

#4. Extract the value for their first day 
CUDOS_pre<-Mothership$Day1_CUDOS
CUXOS_pre<-Mothership$Day1_CUXOS
AnxDep_PrePost <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
AnxDep_PrePost

#5. Create long dataframe

###### This is where I am. I'm trying to figure out how to create the long dataset
AnxDep_PrePost_Long <- gather(AnxDep_PrePost,ID1:CUXOS_post)
                              factor_key = "T")

Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
                              factor_key = "T")
Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]

?gather()

```

### 2023-04-17 Anxiety_Vis.Rmd
Changes in dischage date / preparing for 2nd presentation.

@@
 ggplot(data=Mothership_Mean_CUXOS,aes(x=TxDay,y=mean_CUXOS))+
-  geom_line(size=1,color="#0065A3")+
-  geom_point(color="#0065A3")+
+  geom_line(size=1,color="red")+
+  geom_point(color="red")+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
@@
   theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+
+  labs(subtitle = "Broken up by Discharge Date")+
   geom_vline(xintercept = 5,alpha =.25)+
@@
   scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_y_continuous(name="Depression Severity",limits=c(0,40,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
@@
   labs(
-    title ="Anxiety Severity by Race During Partial Hospitalization",
+    #title ="Anxiety Severity by Race During Partial Hospitalization",
     subtitle = "Patient discharge 1-5 days")+
@@
   labs(
-    title ="Anxiety Severity by Race During Partial Hospitalization",
+    #title ="Anxiety Severity by Race During Partial Hospitalization",
     subtitle = "Patient discharge 6-10 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by Race During Partial Hospitalization",
+  labs(
+    #title ="Anxiety Severity by Race During Partial Hospitalization",
     subtitle = "Patient discharge 11-15 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by Race During Partial Hospitalization",
+  labs(
+    #title ="Anxiety Severity by Race During Partial Hospitalization",
     subtitle = "Patient discharge 16+ days")+
@@
 ggpubr::ggarrange(Race1,Race2,Race3,Race4,ncol=2,nrow=2)
+
 ```
@@
 TrackDF1<-TrackDF1[1:20,]
+
 # plot
@@
   labs(
-    title ="Anxiety Severity by Track During Partial Hospitalization",
+    title ="Treatment Track",
     subtitle = "Patient discharge 1-5 days")+
@@
   labs(
-    title ="Anxiety Severity by Track During Partial Hospitalization",
+    title ="Treatment Track",
     subtitle = "Patient discharge 6-10 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by Track During Partial Hospitalization",
+  labs(title ="Treatment Track",
     subtitle = "Patient discharge 11-15 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by Track During Partial Hospitalization",
+  labs(title ="Treatment Track",
     subtitle = "Patient discharge 16+ days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by Education Level During Partial Hospitalization",
+  labs(
+    title ="Education Level",
     subtitle = "Patient discharge 1-5 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by Education Level During Partial Hospitalization",
+  labs(
+    title ="Education Level",
     subtitle = "Patient discharge 6-10 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by Education Level During Partial Hospitalization",
+  labs(
+    title ="Education Level",
     subtitle = "Patient discharge 11-15 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by Education Level During Partial Hospitalization",
+  labs(title ="Education Level",
     subtitle = "Patient discharge 16+ days")+

### 2023-04-17 Depression_Vis.Rmd
Changes in dischage date / preparing for 2nd presentation.

@@
   ggtitle("Mean Depression Severity During Partial Hospitalization")+
+  labs(subtitle = "Broken up by Discharge Date")+
   scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
   scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
-  scale_color_manual(values=c("#BB9D00","red",
-                              "darkred","orange"))+
+  scale_color_manual(values=c("skyblue","#0065A3",
+                              "navy","blue"))+
   theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+
   geom_vline(xintercept = 5,alpha =.25)+
@@
   labs(
-    title ="Depression Severity by Race During Partial Hospitalization",
+    # title ="Depression Severity by Race During Partial Hospitalization",
     subtitle = "Patient discharge 1-5 days")+
@@
   labs(
-    title ="Depression Severity by Race During Partial Hospitalization",
+    # title ="Depression Severity by Race During Partial Hospitalization",
     subtitle = "Patient discharge 6-10 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by Race During Partial Hospitalization",
+  labs(
+    # title ="Depression Severity by Race During Partial Hospitalization",
     subtitle = "Patient discharge 11-15 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by Race During Partial Hospitalization",
+  labs(
+    # title ="Depression Severity by Race During Partial Hospitalization",
     subtitle = "Patient discharge 16+ days")+
@@
   labs(
-    title ="Depression Severity by Gender During Partial Hospitalization",
+    # title ="Depression Severity by Gender During Partial Hospitalization",
     subtitle = "Patient discharge 1-5 days")+
@@
   labs(
-    title ="Depression Severity by Gender During Partial Hospitalization",
+    # title ="Depression Severity by Gender During Partial Hospitalization",
     subtitle = "Patient discharge 6-10 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by Gender During Partial Hospitalization",
+  labs(
+    # title ="Depression Severity by Gender During Partial Hospitalization",
     subtitle = "Patient discharge 11-15 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by Gender During Partial Hospitalization",
+  labs(
+    # title ="Depression Severity by Gender During Partial Hospitalization",
     subtitle = "Patient discharge 16+ days")+
@@
   labs(
-    title ="Depression Severity by Track During Partial Hospitalization",
+    #title ="Depression Severity by Track During Partial Hospitalization",
     subtitle = "Patient discharge 1-5 days")+
@@
   labs(
-    title ="Depression Severity by Track During Partial Hospitalization",
+    #title ="Depression Severity by Track During Partial Hospitalization",
     subtitle = "Patient discharge 6-10 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by Track During Partial Hospitalization",
+  labs(
+    #title ="Depression Severity by Track During Partial Hospitalization",
     subtitle = "Patient discharge 11-15 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by Track During Partial Hospitalization",
+  labs(
+    #title ="Depression Severity by Track During Partial Hospitalization",
     subtitle = "Patient discharge 16+ days")+
@@
        aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
+  geom_line(size=.75)+
+  geom_point(size=.75)+
   ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by Education Level During Partial Hospitalization",
+  labs(
+    # title ="Depression Severity by Education Level During Partial Hospitalization",
     subtitle = "Patient discharge 1-5 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by Education Level During Partial Hospitalization",
+  labs(
+    # title ="Depression Severity by Education Level During Partial Hospitalization",
     subtitle = "Patient discharge 6-10 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by Education Level During Partial Hospitalization",
+  labs(
+    # title ="Depression Severity by Education Level During Partial Hospitalization",
     subtitle = "Patient discharge 11-15 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by Education Level During Partial Hospitalization",
+  labs(
+    # title ="Depression Severity by Education Level During Partial Hospitalization",
     subtitle = "Patient discharge 16+ days")+
@@
     scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Depression Severity",limits=c(20,36,by=5))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
@@
   labs(
-    title ="Depression Severity by YEARTX During Partial Hospitalization",
+    # title ="Depression Severity by YEARTX During Partial Hospitalization",
     subtitle = "Patient discharge 1-5 days")+
@@
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559","#4B5D8E"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
@@
   labs(
-    title ="Depression Severity by YEARTX During Partial Hospitalization",
+    # title ="Depression Severity by YEARTX During Partial Hospitalization",
     subtitle = "Patient discharge 6-10 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by YEARTX During Partial Hospitalization",
+  labs(
+    #title ="Depression Severity by TX",
     subtitle = "Patient discharge 11-15 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Depression Severity by YEARTX During Partial Hospitalization",
+  labs(
+    # title ="Depression Severity by YEARTX During Partial Hospitalization",
     subtitle = "Patient discharge 16+ days")+

### 2023-04-17 Diagnosis_Vis.Rmd
Changed alpha level & fixed NAs in plot

@@
 # Broken up by disorder. 
-ggplot(data=subset(Mothership, !is.na(Disorder_Type)), 
+ggplot(data=subset(Mothership_Diag, !is.na(Disorder_Type)), 
     mapping= aes(x=TxYear,y = stat(count),
                  group=Disorder_Type, fill=Disorder_Type)) +
-  geom_density(adjust=1.5,alpha=.4) +
+  geom_density(adjust=1.5,alpha=.6) +
   facet_wrap(~Disorder_Type)+
@@
                  group=Disorder_Type, fill=Disorder_Type)) +
-  geom_density(adjust=1.5,alpha=.4) +
+  geom_density(adjust=1.5,alpha=.6) +
   facet_wrap(~Disorder_Type)+

### 2023-04-17 Anxiety_Vis.Rmd
Made sociodem figs, and changed titles for anxiety figs

@@
   geom_point()+
-  labs(title ="Depression Severity by Race During Partial Hospitalization")+
+  labs(title ="Anxiety Severity by Race During Partial Hospitalization")+
   scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Depression Severity",limits=c(0,40,by=5))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(0,40,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
@@
   labs(
-    title ="Education Level",
+    # title ="Education Level",
     subtitle = "Patient discharge 1-5 days")+
@@
   labs(
-    title ="Education Level",
+    # title ="Education Level",
     subtitle = "Patient discharge 6-10 days")+
@@
   labs(
-    title ="Education Level",
+    # title ="Education Level",
     subtitle = "Patient discharge 11-15 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Education Level",
+  labs(
+    # title ="Education Level",
     subtitle = "Patient discharge 16+ days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by YEARTX",
+  labs(
+    # title ="Anxiety Severity by YEARTX",
     subtitle = "Patient discharge 1-5 days")+
@@
   geom_point(size=.5)+
-    labs(title ="Anxiety Severity by YEARTX",
+    labs(
+      # title ="Anxiety Severity by YEARTX",
     subtitle = "Patient discharge 6-10 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by YEARTX",
+  labs(
+    # title ="Anxiety Severity by YEARTX",
     subtitle = "Patient discharge 11-15 days")+
@@
   geom_point(size=.5)+
-  labs(title ="Anxiety Severity by YEARTX",
+  labs(
+    # title ="",
     subtitle = "Patient discharge 16+ days")+

### 2023-04-17 Data_Import.Rmd
Made sociodem figs, and changed titles for anxiety figs

@@
                                       "10"="Other"),
-                    Referal_1 = as.factor(Referal_1),
-                    Referal_1 = recode(Referal_1,
+                    DC_status_1 = as.factor(DC_status_1),
+                    DC_status_1 = recode(DC_status_1,
                                       "1"="Inpatient",
@@
   scale_y_continuous(name = "Frequency",limits=c(0,3000))
+
+### Bar chart for race ###
+ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
+  geom_bar(color = "black",fill="darkblue")+
+  ggtitle("Frequency of Race/Ethnicity") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Race")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+
+### Bar chart for gender###
+ggplot(data = subset(Mothership, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
+  geom_bar(color = "black",fill="darkorange")+
+  ggtitle("Frequency of Gender") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Gender")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+
+### Treatment Track ###
+
+ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
+  geom_bar(color = "black",fill="skyblue")+
+  ggtitle("Frequency of Treatment Type") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Treatment Type")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+
+### Treatment Year ###
+
+Mothership$TxYear
+
+ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
+  geom_bar(color = "black",fill="#9350C7")+
+  ggtitle("Frequency of Patients per Year") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Treatment Year")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+
+### Duration of Treatment ###
+ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
+  geom_bar(color = "black",fill="lightgreen")+
+  ggtitle("Frequency of Patients per Duration of Treatment") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Treatment Duration")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+
 ```
@@
   geom_bar(stat="Identity",width=1,color="white")+
+  ggtitle("Education Level of Patients") +
   coord_polar("y",start=0)+

### 2023-04-17 Treatment_Outcomes.Rmd
Got pre/post scores. Can't figure out long data.

@@
 #1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
-Mothership_Pre_Post <- Mothership
+Mothership_Pre_Post <- Mothership %>%
   mutate(Mothership_Pre_Post, 
@@
 
-  Mothership
+Mothership_Pre_Post$Days_complete_W
+
 #2. Then create df with CUDOS and CUXOS scores
@@
 #3. Extract the valeues for each patient at their last day (length of stay)
-    # mutate(Mothership_Pre_Post, 
-    #         CUDOS_post = CUDOS_Score[
-    #           cbind(seq_along(Mothership_Pre_Post$Days_complete_W),
-    #                 Mothership_Pre_Post$Days_complete_W)],
-    #         CUXOS_post = CUXOS_Score[
-    #           cbind(seq_along(Mothership_Pre_Post$Days_complete_W),
-    #                 Mothership_Pre_Post$Days_complete_W)]
-    #      )
-```
+# Mothership_Pre_Post <- mutate(Mothership_Pre_Post,
+#             CUDOS_post = CUDOS_post,
+#             CUXOS_post = CUXOS_post)
+    ##### Why is it not includeing NAs.
 
-```{r}
 CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]
@@
 CUXOS_pre<-Mothership$Day1_CUXOS
-AnxDep_PrePost <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
-AnxDep_PrePost
+AnxDep_PrePost_test <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
+AnxDep_PrePost_test
+colnames(AnxDep_PrePost)[1] = "ID1"
 
+## This is where I am Figure out where to go from here *******************
 #5. Create long dataframe
 
-###### This is where I am. I'm trying to figure out how to create the long dataset
-AnxDep_PrePost_Long <- gather(AnxDep_PrePost,ID1:CUXOS_post)
-                              factor_key = "T")
+AnxDep_PrePost_Lon <- gather(AnxDep_PrePost,ID1:CUXOS_post,factor_key = "T")
+
+AnxDep_PrePost_Long <- pivot_longer(AnxDep_PrePost,ID1:CUXOS_post)
+
+AnxDep_PrePost_Long
+?pivot_longer()
+
+AnxDep_PrePost_Long <- AnxDep_PrePost_Long[order(AnxDep_PrePost_Long$ID1),]
 
@@
                               factor_key = "T")
-Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]
-
-?gather()
+Mothership_Long_RDQ
 

### 2023-04-20 Anxiety_Vis.Rmd
Finalized code for final presentation.

@@
   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+# Mothership_Mean_CUXOS20<-Mothership_Long20 %>%
+#   group_by(TxDay) %>%
+#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
 ```
@@
     title="Quantity of discharges Per Treatment Day")+
-  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
-  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
-  geom_vline(xintercept = 13, color = "red",alpha =.5)+
-  annotate("text", x = 5, y = .01, label = "Q1") +
-  annotate("text", x = 8, y = .01, label = "Mean") +
-  annotate("text", x = 13, y = .01, label = "Q3")
+  theme_classic()
 
@@
   theme(panel.background=NULL)+
-  labs(subtitle = "Broken up by Discharge Date")+
-  geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 49, label = "Q1") +
-  annotate("text", x = 8, y = 49, label = "Mean") +
-  annotate("text", x = 13, y = 49, label = "Q3") 
+  labs(subtitle = "Broken up by Duration of Treatment")
+  #  +
+  # geom_vline(xintercept = 5,alpha =.25)+
+  # geom_vline(xintercept = 8,alpha =.25)+
+  # geom_vline(xintercept = 13,alpha =.25)+
+  # annotate("text", x = 5, y = 49, label = "Q1") +
+  # annotate("text", x = 8, y = 49, label = "Mean") +
+  # annotate("text", x = 13, y = 49, label = "Q3") 
 ```
@@
 ```{r}
+
+Mothership<-read.csv("~/Desktop/Coding/data/Mothership_Vis.csv")
+Mothership<-mutate(Mothership,
+      DC_status_1 = as.factor(DC_status_1),
+      Education_1 = as.factor(Education_1),
+      Gender_1 = as.factor(Gender_1),
+      Relationship_1 = as.factor(Relationship_1),
+      Sexuality_1 = as.factor(Sexuality_1),
+      IPT_track_1 = as.factor(IPT_track_1),
+      Race_1 = as.factor(Race_1),
+      Education_1 = as.factor(Education_1),
+      Duration = as.factor(Duration),
+      )
+
+Mothership$Intake_1<-ymd(Mothership$Intake_1,locale = "en_US.UTF-8")
+
+Mothership_Long_anx <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
+Mothership_Long_anx <- Mothership_Long_anx[order(Mothership_Long_anx$ID1),]
+
+#Create a Time Variable
+Mothership_Long_anx$TxDay <- NA
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day1_CUXOS"]<-1
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day2_CUXOS"]<-2
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day3_CUXOS"]<-3
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day4_CUXOS"]<-4
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day5_CUXOS"]<-5
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day6_CUXOS"]<-6
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day7_CUXOS"]<-7
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day8_CUXOS"]<-8
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day9_CUXOS"]<-9
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day10_CUXOS"]<-10
+
 #Overall race
-Mothership_Mean_CUXOS_Race<-Mothership_Long %>%
+Mothership_Mean_CUXOS_Race<-Mothership_Long_anx %>%
   group_by(TxDay,Race_1) %>%
   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+Mothership_Mean_CUXOS_Race<-Mothership_Mean_CUXOS_Race[1:70,]
+Mothership_Mean_CUXOS_Race
 # plot
-ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
+ggplot(data=subset(Mothership_Mean_CUXOS_Race,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
   geom_line(size=1)+
@@
   labs(title ="Anxiety Severity by Race During Partial Hospitalization")+
-  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(0,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(0,60,by=5))+
+  scale_color_manual(values=c("#DA2E2E","#57423E",
+                              "gold3","#3E8300",
+                              "#77B81C","darkorange2"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
   theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+
-   geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 39, label = "Q1") +
-  annotate("text", x = 8, y = 39, label = "Mean") +
-  annotate("text", x = 13, y = 39, label = "Q3") 
+  theme(legend.title=element_blank())
 ```
@@
 #Create a New Data Set with an Average Anxiety Variable and Race
-Mothership_Mean_CUXOS_Race<-Mothership_Long %>%
+Mothership_Mean_CUXOS_Race<-Mothership_Long_anx %>%
   filter(Duration == "1-5") %>%
@@
 ######## 6-10 days
-RaceDF2<-Mothership_Long %>%
+RaceDF2<-Mothership_Long_anx %>%
   filter(Duration == "6-10") %>%
@@
 ######## 11-15 days
-RaceDF3<-Mothership_Long %>%
+RaceDF3<-Mothership_Long_anx %>%
   filter(Duration == "11-15") %>%
@@
 ######## 16+ days
-RaceDF4<-Mothership_Long %>%
+RaceDF4<-Mothership_Long_anx %>%
   filter(Duration == "16+") %>%
@@
 #Create a New Data Set with an Average Anxiety Variable and Gender
-Mothership_Mean_CUXOS_Gender<-Mothership_Long %>%
+
+Mothership_Mean_CUXOS_Gender<-Mothership_Long_anx %>%
   group_by(TxDay,Gender_1) %>%
   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+Mothership_Mean_CUXOS_Gender <-filter(Mothership_Mean_CUXOS_Gender,
+                                      Gender_1 != "Unknown",
+                                      Gender_1 != "Non-Binary",
+                                      Gender_1 != "Other"
+                                        )
 
@@
   ggtitle("Anxiety Severity by Gender During Partial Hospitalization")+
-  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3"))+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(15,45,by=5))+
+  scale_color_manual(values=c("#DA2E2E","#57423E"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
   theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 59, label = "Q1") +
-  annotate("text", x = 8, y = 59, label = "Mean") +
-  annotate("text", x = 13, y = 59, label = "Q3") 
+  theme(legend.title=element_blank())
 ```
@@
 #Create a New Data Set with an Average Anxiety Variable and Gender
-Mothership_Mean_CUXOS_Gender<-Mothership_Long %>%
+Mothership_Mean_CUXOS_Gender<-Mothership_Long_anx %>%
   filter(Duration == "1-5") %>%
@@
 ##### 5-10 Days
-GenderDF2<-Mothership_Long %>%
+GenderDF2<-Mothership_Long_anx %>%
   filter(Duration == "6-10") %>%
@@
 ##### 10-15 Days
-GenderDF3<-Mothership_Long %>%
+GenderDF3<-Mothership_Long_anx %>%
   filter(Duration == "11-15") %>%
@@
 ##### 16+ Days
-GenderDF4<-Mothership_Long %>%
+GenderDF4<-Mothership_Long_anx %>%
   filter(Duration == "16+") %>%
@@
 #Create a New Data Set with an Average Anxiety Variable and Track
-Mothership_Mean_CUXOS_Track<-Mothership_Long %>%
+Mothership_Mean_CUXOS_Track<-Mothership_Long_anx %>%
   group_by(TxDay,IPT_track_1) %>%
@@
   ggtitle("Anxiety Severity by Treatment Track During Partial Hospitalization")+
-  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
   scale_y_continuous(name="Anxiety Severity",limits=c(20,46,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#0065A3"))+
+  scale_color_manual(values=c("#DA2E2E","#57423E","gold3"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
   theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+
-  geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 45, label = "Q1") +
-  annotate("text", x = 8, y = 45, label = "Mean") +
-  annotate("text", x = 13, y = 45, label = "Q3") 
+  theme(legend.title=element_blank())
 ```
@@
 #Create a New Data Set with an Average Anxiety Variable and Gender
-TrackDF1<-Mothership_Long %>%
+TrackDF1<-Mothership_Long_anx %>%
   filter(Duration == "1-5") %>%
@@
 ##### 5-10 Days
-TrackDF2<-Mothership_Long %>%
+TrackDF2<-Mothership_Long_anx %>%
   filter(Duration == "6-10") %>%
@@
 ##### 10-15 Days
-TrackDF3<-Mothership_Long %>%
+TrackDF3<-Mothership_Long_anx %>%
   filter(Duration == "11-15") %>%
@@
 ##### 16+ Days
-TrackDF4<-Mothership_Long %>%
+TrackDF4<-Mothership_Long_anx %>%
   filter(Duration == "16+") %>%
@@
 #Create a New Data Set with an Average Anxiety Variable and Education
-Mothership_Mean_CUXOS_Ed<-Mothership_Long %>%
+Mothership_Mean_CUXOS_Ed<-Mothership_Long_anx %>%
   group_by(TxDay,Education_1) %>%
@@
   ggtitle("Anxiety Severity by Education Level During Partial Hospitalization")+
-    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
   scale_y_continuous(name="Anxiety Severity",limits=c(20,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559"))+
+  scale_color_manual(values=c("#DA2E2E","#57423E",
+                              "gold3","#3E8300",
+                              "#77B81C","darkorange2",
+                              "#798897","#FD85AE"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+
-  geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 49, label = "Q1") +
-  annotate("text", x = 8, y = 49, label = "Mean") +
-  annotate("text", x = 13, y = 49, label = "Q3") 
+  theme(panel.background=NULL)
+
+ggplot(data=subset(Mothership_Mean_CUXOS_Ed,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Anxiety Severity by Education Level During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(20,50,by=5))+
+  scale_color_manual(values=c("#DA2E2E","lightgrey","lightgrey",
+                              "gold3","lightgrey","lightgrey",
+                              "lightgrey","lightgrey"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)
 ```
@@
 #Create a New Data Set with an Average Anxiety Variable and Gender
-EducationDF1<-Mothership_Long %>%
+EducationDF1<-Mothership_Long_anx %>%
   filter(Duration == "1-5") %>%
@@
 ##### 5-10 Days
-EducationDF2<-Mothership_Long %>%
+EducationDF2<-Mothership_Long_anx %>%
   filter(Duration == "6-10") %>%
@@
 ##### 10-15 Days
-EducationDF3<-Mothership_Long %>%
+EducationDF3<-Mothership_Long_anx %>%
   filter(Duration == "11-15") %>%
@@
 ##### 16+ Days
-EducationDF4<-Mothership_Long %>%
+EducationDF4<-Mothership_Long_anx %>%
   filter(Duration == "16+") %>%
@@
   scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559"))+
+  scale_color_manual(values=c("#DA2E2E","#57423E",
+                              "gold3","#3E8300",
+                              "#77B81C","darkorange2",
+                              "#798897","#FD85AE","firebrick4"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
@@
 #Create a New Data Set with an Average Anxiety Variable and Year
-Mothership_Mean_CUXOS_Year<-Mothership_Long %>%
+Mothership_Mean_CUXOS_Year<-Mothership_Long_anx %>%
   group_by(TxDay,TxYear) %>%
@@
   ggtitle("Anxiety Severity by Treatment Year During Partial Hospitalization")+
-    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
   scale_y_continuous(name="Anxiety Severity",limits=c(15,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1"))+
+  scale_color_manual(values=c("#DA2E2E","#57423E",
+                              "gold3","#3E8300",
+                              "#77B81C","darkorange2",
+                              "firebrick4","#FD85AE","#798897"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
@@
   theme(legend.title=element_blank())
+
+ggplot(data=subset(Mothership_Mean_CUXOS_Year,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Anxiety Severity by Treatment Year During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(15,50,by=5))+
+  scale_color_manual(values=c("lightgrey","lightgrey",
+                              "lightgrey","lightgrey",
+                              "lightgrey","lightgrey",
+                              "firebrick4","lightgrey","lightgrey"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
 ```
@@
 #Create a New Data Set with an Average Anxiety Variable and Gender
-YEARTXDF1<-Mothership_Long %>%
+YEARTXDF1<-Mothership_Long_anx %>%
   filter(Duration == "1-5") %>%
@@
 ##### 5-10 Days
-YEARTXDF2<-Mothership_Long %>%
+YEARTXDF2<-Mothership_Long_anx %>%
   filter(Duration == "6-10") %>%
@@
 ##### 10-15 Days
-YEARTXDF3<-Mothership_Long %>%
+YEARTXDF3<-Mothership_Long_anx %>%
   filter(Duration == "11-15") %>%
@@
 ##### 16+ Days
-YEARTXDF4<-Mothership_Long %>%
+YEARTXDF4<-Mothership_Long_anx %>%
   filter(Duration == "16+") %>%

### 2023-04-20 Data_Import.Rmd
Finalized code for final presentation.

@@
                      Duration = as.factor(
-                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1-5",
-                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "6-10",
-                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "11-15", "16+"
-                              )))))
+                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1",
+                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "2",
+                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "3", "4"
+                              )))),
+                    Duration = recode(Duration,
+                                      "1"="1-5",
+                                      "2"="6-10",
+                                      "3"="11-15",
+                                      "4"="16+"
+                                      ))
 
@@
   theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+  scale_y_continuous(name = "Frequency",limits=c(0,1500))
 

### 2023-04-20 Depression_Vis.Rmd
Finalized code for final presentation.

@@
 ```{r}
-Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
-Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]
-
-#Create a Time Variable
-Mothership_Long$TxDay <- NA
-Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
-Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
-Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
-Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
-Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
-Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
-Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
-Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
-Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
-Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
 Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
@@
 ```{r}
+Mothership_Long_dep <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
+Mothership_Long_dep <- Mothership_Long_dep[order(Mothership_Long_dep$ID1),]
+
+#Create a Time Variable
+Mothership_Long_dep$TxDay <- NA
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day1_CUDOS"]<-1
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day2_CUDOS"]<-2
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day3_CUDOS"]<-3
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day4_CUDOS"]<-4
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day5_CUDOS"]<-5
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day6_CUDOS"]<-6
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day7_CUDOS"]<-7
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day8_CUDOS"]<-8
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day9_CUDOS"]<-9
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day10_CUDOS"]<-10
+
 #Overall race
-Mothership_Mean_CUDOS_Race<-Mothership_Long %>%
+Mothership_Mean_CUDOS_Race<-Mothership_Long_dep %>%
   group_by(TxDay,Race_1) %>%
@@
   labs(title ="Depression Severity by Race During Partial Hospitalization")+
-  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
   scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
+  scale_color_manual(values=c("#209845","#3D4A3E","darkgreen",
+                              "#0098DB","#0065A3","#A0AFA1"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
   theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+
-   geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 39, label = "Q1") +
-  annotate("text", x = 8, y = 39, label = "Mean") +
-  annotate("text", x = 13, y = 39, label = "Q3") 
+  theme(legend.title=element_blank())
+
+ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
+  geom_line(size=1)+
+  geom_point()+
+  labs(title ="Depression Severity by Race During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","lightgrey","lightgrey",
+                              "lightgrey","lightgrey","lightgrey"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
+  geom_line(size=1)+
+  geom_point()+
+  labs(title ="Depression Severity by Race During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("lightgrey","lightgrey","darkgreen",
+                              "lightgrey","#0065A3","lightgrey"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
 ```
@@
 #Create a New Data Set with an Average Depression Variable and Gender
-Mothership_Mean_CUDOS_Gender<-Mothership_Long %>%
+Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
   group_by(TxDay,Gender_1) %>%
@@
 
+Mothership_Mean_CUDOS_Gender <-filter(Mothership_Mean_CUDOS_Gender,
+                                      Gender_1 != "Unknown",
+                                      Gender_1 != "Non-Binary",
+                                      Gender_1 != "Other"
+                                        )
 #Create the Depression Line Graph by Gender
@@
   ggtitle("Depression Severity by Gender During Partial Hospitalization")+
-  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(15,45,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
@@
   theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 59, label = "Q1") +
-  annotate("text", x = 8, y = 59, label = "Mean") +
-  annotate("text", x = 13, y = 59, label = "Q3") 
+  theme(legend.title=element_blank())
 ```
@@
 #Create a New Data Set with an Average Depression Variable and Gender
-Mothership_Mean_CUDOS_Gender<-Mothership_Long %>%
+Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
   filter(Duration == "1-5") %>%
@@
 ##### 5-10 Days
-GenderDF2<-Mothership_Long %>%
+GenderDF2<-Mothership_Long_dep %>%
   filter(Duration == "6-10") %>%
@@
 ##### 10-15 Days
-GenderDF3<-Mothership_Long %>%
+GenderDF3<-Mothership_Long_dep %>%
   filter(Duration == "11-15") %>%
@@
 ##### 16+ Days
-GenderDF4<-Mothership_Long %>%
+GenderDF4<-Mothership_Long_dep %>%
   filter(Duration == "16+") %>%
@@
 #Create a New Data Set with an Average Depression Variable and Track
-Mothership_Mean_CUDOS_Track<-Mothership_Long %>%
+Mothership_Mean_CUDOS_Track<-Mothership_Long_dep %>%
   group_by(TxDay,IPT_track_1) %>%
@@
   ggtitle("Depression Severity by Treatment Track During Partial Hospitalization")+
-  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
   scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
@@
   theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+
-  geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 39, label = "Q1") +
-  annotate("text", x = 8, y = 39, label = "Mean") +
-  annotate("text", x = 13, y = 39, label = "Q3") 
+  theme(legend.title=element_blank())
 ```
@@
 #Create a New Data Set with an Average Depression Variable and Gender
-TrackDF1<-Mothership_Long %>%
+TrackDF1<-Mothership_Long_dep %>%
   filter(Duration == "1-5") %>%
@@
 ##### 5-10 Days
-TrackDF2<-Mothership_Long %>%
+TrackDF2<-Mothership_Long_dep %>%
   filter(Duration == "6-10") %>%
@@
 ##### 10-15 Days
-TrackDF3<-Mothership_Long %>%
+TrackDF3<-Mothership_Long_dep %>%
   filter(Duration == "11-15") %>%
@@
 ##### 16+ Days
-TrackDF4<-Mothership_Long %>%
+TrackDF4<-Mothership_Long_dep %>%
   filter(Duration == "16+") %>%
@@
 #Create a New Data Set with an Average Depression Variable and Education
-Mothership_Mean_CUDOS_Ed<-Mothership_Long %>%
+Mothership_Mean_CUDOS_Ed<-Mothership_Long_dep %>%
   group_by(TxDay,Education_1) %>%
@@
   ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
-    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
   scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
@@
   theme(panel.background=NULL)+
-  theme(legend.title=element_blank())+
-  geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 39, label = "Q1") +
-  annotate("text", x = 8, y = 39, label = "Mean") +
-  annotate("text", x = 13, y = 39, label = "Q3") 
+  theme(legend.title=element_blank())
+
+ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
+  geom_line(size=.75)+
+  geom_point(size=.75)+
+  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
+  scale_color_manual(values=c("#209845","lightgrey","lightgrey",
+                              "#0098DB","lightgrey","lightgrey",
+                              "lightgrey","lightgrey"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
 ```
@@
 #Create a New Data Set with an Average Depression Variable and Gender
-EducationDF1<-Mothership_Long %>%
+EducationDF1<-Mothership_Long_dep %>%
   filter(Duration == "1-5") %>%
@@
 ##### 5-10 Days
-EducationDF2<-Mothership_Long %>%
+EducationDF2<-Mothership_Long_dep %>%
   filter(Duration == "6-10") %>%
@@
 ##### 10-15 Days
-EducationDF3<-Mothership_Long %>%
+EducationDF3<-Mothership_Long_dep %>%
   filter(Duration == "11-15") %>%
@@
 ##### 16+ Days
-EducationDF4<-Mothership_Long %>%
+EducationDF4<-Mothership_Long_dep %>%
   filter(Duration == "16+") %>%
@@
 #Create a New Data Set with an Average Depression Variable and Year
-Mothership_Mean_CUDOS_Year<-Mothership_Long %>%
+Mothership_Mean_CUDOS_Year<-Mothership_Long_dep %>%
   group_by(TxDay,TxYear) %>%
@@
 
-str(Mothership_Long$TxYear)
+str(Mothership_Long_dep$TxYear)
 
@@
   ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
-    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
   scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559","#4B5D8E"))+
+                              "#0098DB","#91A9F1","darkgreen",
+                              "#0065A3","#7F8559","#4B5D8E"))+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
@@
   theme(legend.title=element_blank())
+
+#Create the Depression Line Graph by Year
+ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
+  scale_color_manual(values=c("lightgrey","lightgrey","lightgrey",
+                              "lightgrey","lightgrey","lightgrey",
+                              "#0065A3","lightgrey","lightgrey"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+```
 ```
@@
 #Create a New Data Set with an Average Depression Variable and Gender
-YEARTXDF1<-Mothership_Long %>%
+YEARTXDF1<-Mothership_Long_dep %>%
   filter(Duration == "1-5") %>%
@@
 ##### 5-10 Days
-YEARTXDF2<-Mothership_Long %>%
+YEARTXDF2<-Mothership_Long_dep %>%
   filter(Duration == "6-10") %>%
@@
 ##### 10-15 Days
-YEARTXDF3<-Mothership_Long %>%
+YEARTXDF3<-Mothership_Long_dep %>%
   filter(Duration == "11-15") %>%
@@
 ##### 16+ Days
-YEARTXDF4<-Mothership_Long %>%
+YEARTXDF4<-Mothership_Long_dep %>%
   filter(Duration == "16+") %>%

### 2023-04-21 Anxiety_Vis.Rmd
Deleting all of my hard work :(

@@
   labs(subtitle = "Broken up by Duration of Treatment")
-  #  +
-  # geom_vline(xintercept = 5,alpha =.25)+
-  # geom_vline(xintercept = 8,alpha =.25)+
-  # geom_vline(xintercept = 13,alpha =.25)+
-  # annotate("text", x = 5, y = 49, label = "Q1") +
-  # annotate("text", x = 8, y = 49, label = "Mean") +
-  # annotate("text", x = 13, y = 49, label = "Q3") 
 ```
@@
 ```
-
-Example of plot for 1-5 days discharge
-```{r}
-#Create a New Data Set with an Average Anxiety Variable and Race
-Mothership_Mean_CUXOS_Race<-Mothership_Long_anx %>%
-  filter(Duration == "1-5") %>%
-  group_by(TxDay,Race_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-RaceDF1<-Mothership_Mean_CUXOS_Race[1:34,]
-# plot
-Race1<-ggplot(data=subset(RaceDF1,!is.na(Race_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    #title ="Anxiety Severity by Race During Partial Hospitalization",
-    subtitle = "Patient discharge 1-5 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-We are going to make seperate plots for the other duration groups (i.e., 6-10 days,11-15 days, 16+ days)
-```{r,include=FALSE}
-
-######## 6-10 days
-RaceDF2<-Mothership_Long_anx %>%
-  filter(Duration == "6-10") %>%
-  group_by(TxDay,Race_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-RaceDF2<-RaceDF2[1:70,]
-
-# plot
-Race2<-ggplot(data=subset(RaceDF2,!is.na(Race_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    #title ="Anxiety Severity by Race During Partial Hospitalization",
-    subtitle = "Patient discharge 6-10 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-######## 11-15 days
-RaceDF3<-Mothership_Long_anx %>%
-  filter(Duration == "11-15") %>%
-  group_by(TxDay,Race_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-RaceDF3<-RaceDF3[1:105,]
-
-# plot
-Race3<-ggplot(data=subset(RaceDF3,!is.na(Race_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    #title ="Anxiety Severity by Race During Partial Hospitalization",
-    subtitle = "Patient discharge 11-15 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-######## 16+ days
-RaceDF4<-Mothership_Long_anx %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,Race_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-RaceDF4<-RaceDF4[1:150,]
-
-# plot
-Race4<-ggplot(data=subset(RaceDF4,!is.na(Race_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    #title ="Anxiety Severity by Race During Partial Hospitalization",
-    subtitle = "Patient discharge 16+ days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-#### putting them all together
-```{r}
-ggpubr::ggarrange(Race1,Race2,Race3,Race4,ncol=2,nrow=2)
-
-```
-
 ## GENDER IDENTITY
@@
 
-Break it up by duration group 
-```{r, include= FALSE}
-#Create a New Data Set with an Average Anxiety Variable and Gender
-Mothership_Mean_CUXOS_Gender<-Mothership_Long_anx %>%
-  filter(Duration == "1-5") %>%
-  group_by(TxDay,Gender_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-GenderDF1<-Mothership_Mean_CUXOS_Gender[1:30,]
-# plot
-Gender1<-ggplot(data=subset(GenderDF1,!is.na(Gender_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    title ="Anxiety Severity by Gender During Partial Hospitalization",
-    subtitle = "Patient discharge 1-5 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 5-10 Days
-GenderDF2<-Mothership_Long_anx %>%
-  filter(Duration == "6-10") %>%
-  group_by(TxDay,Gender_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-GenderDF2<-GenderDF2[1:59,]
-
-# plot
-Gender2<-ggplot(data=subset(GenderDF2,!is.na(Gender_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    title ="Anxiety Severity by Gender During Partial Hospitalization",
-    subtitle = "Patient discharge 6-10 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 10-15 Days
-GenderDF3<-Mothership_Long_anx %>%
-  filter(Duration == "11-15") %>%
-  group_by(TxDay,Gender_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-GenderDF3<-GenderDF3[1:90,]
-
-# plot
-Gender3<-ggplot(data=subset(GenderDF3,!is.na(Gender_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(title ="Anxiety Severity by Gender During Partial Hospitalization",
-    subtitle = "Patient discharge 11-15 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 16+ Days
-GenderDF4<-Mothership_Long_anx %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,Gender_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-GenderDF4<-GenderDF4[1:120,]
-
-# plot
-Gender4<-ggplot(data=subset(GenderDF4,!is.na(Gender_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(title ="Anxiety Severity by Gender During Partial Hospitalization",
-    subtitle = "Patient discharge 16+ days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,60,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-```{r}
-ggpubr::ggarrange(Gender1,Gender2,Gender3,Gender4,ncol=2,nrow=2)
-```
-
 #### TREATMENT TRACK
@@
   theme(legend.title=element_blank())
-```
-
-Break it up by duration group (Treatment track)
-```{r, include= FALSE}
-#Create a New Data Set with an Average Anxiety Variable and Gender
-TrackDF1<-Mothership_Long_anx %>%
-  filter(Duration == "1-5") %>%
-  group_by(TxDay,IPT_track_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-TrackDF1<-TrackDF1[1:20,]
-
-# plot
-Track1<-ggplot(data=subset(TrackDF1,!is.na(IPT_track_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    title ="Treatment Track",
-    subtitle = "Patient discharge 1-5 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 5-10 Days
-TrackDF2<-Mothership_Long_anx %>%
-  filter(Duration == "6-10") %>%
-  group_by(TxDay,IPT_track_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-TrackDF2<-TrackDF2[1:40,]
-
-# plot
-Track2<-ggplot(data=subset(TrackDF2,!is.na(IPT_track_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    title ="Treatment Track",
-    subtitle = "Patient discharge 6-10 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 10-15 Days
-TrackDF3<-Mothership_Long_anx %>%
-  filter(Duration == "11-15") %>%
-  group_by(TxDay,IPT_track_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-TrackDF3<-TrackDF3[1:60,]
-
-# plot
-Track3<-ggplot(data=subset(TrackDF3,!is.na(IPT_track_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(title ="Treatment Track",
-    subtitle = "Patient discharge 11-15 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 16+ Days
-TrackDF4<-Mothership_Long_anx %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,IPT_track_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-TrackDF4<-TrackDF4[1:80,]
-
-# plot
-Track4<-ggplot(data=subset(TrackDF4,!is.na(IPT_track_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(title ="Treatment Track",
-    subtitle = "Patient discharge 16+ days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-```{r}
-ggpubr::ggarrange(Track1,Track2,Track3,Track4,ncol=2,nrow=2)
 ```
@@
 
-Break it up by duration group 
-```{r, include= FALSE}
-#Create a New Data Set with an Average Anxiety Variable and Gender
-EducationDF1<-Mothership_Long_anx %>%
-  filter(Duration == "1-5") %>%
-  group_by(TxDay,Education_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-EducationDF1<-EducationDF1[1:45,]
-# plot
-Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Education Level",
-    subtitle = "Patient discharge 1-5 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 5-10 Days
-EducationDF2<-Mothership_Long_anx %>%
-  filter(Duration == "6-10") %>%
-  group_by(TxDay,Education_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-EducationDF2<-EducationDF2[1:90,]
-
-# plot
-Education2<-ggplot(data=subset(EducationDF2,!is.na(Education_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Education Level",
-    subtitle = "Patient discharge 6-10 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 10-15 Days
-EducationDF3<-Mothership_Long_anx %>%
-  filter(Duration == "11-15") %>%
-  group_by(TxDay,Education_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-EducationDF3<-EducationDF3[1:135,]
-
-# plot
-Education3<-ggplot(data=subset(EducationDF3,!is.na(Education_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Education Level",
-    subtitle = "Patient discharge 11-15 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 16+ Days
-EducationDF4<-Mothership_Long_anx %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,Education_1) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-EducationDF4<-EducationDF4[1:180,]
-
-# plot
-Education4<-ggplot(data=subset(EducationDF4,!is.na(Education_1)),
-       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Education Level",
-    subtitle = "Patient discharge 16+ days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#DA2E2E","#57423E",
-                              "gold3","#3E8300",
-                              "#77B81C","darkorange2",
-                              "#798897","#FD85AE","firebrick4"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-```{r}
-ggpubr::ggarrange(Education1,Education2,Education3,Education4, ncol=2,nrow=2)
-```
 ### TREATMENT YEAR
@@
 ```
-
-Break it up by duration group (Year)
-```{r, include= FALSE}
-#Create a New Data Set with an Average Anxiety Variable and Gender
-YEARTXDF1<-Mothership_Long_anx %>%
-  filter(Duration == "1-5") %>%
-  group_by(TxDay,TxYear) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-YEARTXDF1<-YEARTXDF1[1:40,]
-# plot
-YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Anxiety Severity by YEARTX",
-    subtitle = "Patient discharge 1-5 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 5-10 Days
-YEARTXDF2<-Mothership_Long_anx %>%
-  filter(Duration == "6-10") %>%
-  group_by(TxDay,TxYear) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-YEARTXDF2<-YEARTXDF2[1:80,]
-
-# plot
-YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-    labs(
-      # title ="Anxiety Severity by YEARTX",
-    subtitle = "Patient discharge 6-10 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 10-15 Days
-YEARTXDF3<-Mothership_Long_anx %>%
-  filter(Duration == "11-15") %>%
-  group_by(TxDay,TxYear) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-YEARTXDF3<-YEARTXDF3[1:120,]
-
-# plot
-YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Anxiety Severity by YEARTX",
-    subtitle = "Patient discharge 11-15 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 16+ Days
-YEARTXDF4<-Mothership_Long_anx %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,TxYear) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-YEARTXDF4<-YEARTXDF4[1:160,]
-
-# plot
-YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="",
-    subtitle = "Patient discharge 16+ days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(10,50,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-```{r}
-ggpubr::ggarrange(YEARTX1,YEARTX2,YEARTX3,YEARTX4,ncol=2,nrow=2)
-```

### 2023-04-21 Depression_Vis.Rmd
Deleting all of my hard work :(

@@
   scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
-  theme(panel.background=NULL) +
-  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
-  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
-  geom_vline(xintercept = 13, color = "red",alpha =.5)+
-  annotate("text", x = 5, y = 34, label = "Q1") +
-  annotate("text", x = 8, y = 34, label = "Mean") +
-  annotate("text", x = 13, y = 34, label = "Q3")
+  theme(panel.background=NULL)
 
@@
   labs(
-    title="Quantity of discharges Per Treatment Day")+
-  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
-  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
-  geom_vline(xintercept = 13, color = "red",alpha =.5)+
-  annotate("text", x = 5, y = .01, label = "Q1") +
-  annotate("text", x = 8, y = .01, label = "Mean") +
-  annotate("text", x = 13, y = .01, label = "Q3")
+    title="Quantity of discharges Per Treatment Day")
 
@@
                               "navy","blue"))+
-  theme(panel.background=NULL)+
-  geom_vline(xintercept = 5,alpha =.25)+
-  geom_vline(xintercept = 8,alpha =.25)+
-  geom_vline(xintercept = 13,alpha =.25)+
-  annotate("text", x = 5, y = 39, label = "Q1") +
-  annotate("text", x = 8, y = 39, label = "Mean") +
-  annotate("text", x = 13, y = 39, label = "Q3") 
+  theme(panel.background=NULL)
 ```
@@
 
-Example of plot for 1-5 days discharge
-```{r}
-#Create a New Data Set with an Average Depression Variable and Race
-Mothership_Mean_CUDOS_Race<-Mothership_Long %>%
-  filter(Duration == "1-5") %>%
-  group_by(TxDay,Race_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-RaceDF1<-Mothership_Mean_CUDOS_Race[1:34,]
-# plot
-Race1<-ggplot(data=subset(RaceDF1,!is.na(Race_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Race During Partial Hospitalization",
-    subtitle = "Patient discharge 1-5 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-We are going to make seperate plots for the other duration groups (i.e., 6-10 days,11-15 days, 16+ days)
-```{r,include=FALSE}
-
-######## 6-10 days
-RaceDF2<-Mothership_Long %>%
-  filter(Duration == "6-10") %>%
-  group_by(TxDay,Race_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-RaceDF2<-RaceDF2[1:70,]
-
-# plot
-Race2<-ggplot(data=subset(RaceDF2,!is.na(Race_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Race During Partial Hospitalization",
-    subtitle = "Patient discharge 6-10 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-######## 11-15 days
-RaceDF3<-Mothership_Long %>%
-  filter(Duration == "11-15") %>%
-  group_by(TxDay,Race_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-RaceDF3<-RaceDF3[1:105,]
-
-# plot
-Race3<-ggplot(data=subset(RaceDF3,!is.na(Race_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Race During Partial Hospitalization",
-    subtitle = "Patient discharge 11-15 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-######## 16+ days
-RaceDF4<-Mothership_Long %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,Race_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-RaceDF4<-RaceDF4[1:140,]
-
-# plot
-Race4<-ggplot(data=subset(RaceDF4,!is.na(Race_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Race During Partial Hospitalization",
-    subtitle = "Patient discharge 16+ days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-#### putting them all together
-```{r}
-ggpubr::ggarrange(Race1,Race2,Race3,Race4,ncol=2,nrow=2)
-```
-
 ## GENDER IDENTITY
@@
 ```
-
-Break it up by duration group 
-```{r, include= FALSE}
-#Create a New Data Set with an Average Depression Variable and Gender
-Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
-  filter(Duration == "1-5") %>%
-  group_by(TxDay,Gender_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-GenderDF1<-Mothership_Mean_CUDOS_Gender[1:30,]
-# plot
-Gender1<-ggplot(data=subset(GenderDF1,!is.na(Gender_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Gender During Partial Hospitalization",
-    subtitle = "Patient discharge 1-5 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 5-10 Days
-GenderDF2<-Mothership_Long_dep %>%
-  filter(Duration == "6-10") %>%
-  group_by(TxDay,Gender_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-GenderDF2<-GenderDF2[1:59,]
-
-# plot
-Gender2<-ggplot(data=subset(GenderDF2,!is.na(Gender_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Gender During Partial Hospitalization",
-    subtitle = "Patient discharge 6-10 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-  scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 10-15 Days
-GenderDF3<-Mothership_Long_dep %>%
-  filter(Duration == "11-15") %>%
-  group_by(TxDay,Gender_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-GenderDF3<-GenderDF3[1:90,]
-
-# plot
-Gender3<-ggplot(data=subset(GenderDF3,!is.na(Gender_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Gender During Partial Hospitalization",
-    subtitle = "Patient discharge 11-15 days")+
-  #scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 16+ Days
-GenderDF4<-Mothership_Long_dep %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,Gender_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-GenderDF4<-GenderDF4[1:120,]
-
-# plot
-Gender4<-ggplot(data=subset(GenderDF4,!is.na(Gender_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Gender During Partial Hospitalization",
-    subtitle = "Patient discharge 16+ days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,60,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-```{r}
-ggpubr::ggarrange(Gender1,Gender2,Gender3,Gender4,ncol=2,nrow=2)
-```
-
 #### TREATMENT TRACK
@@
 
-Break it up by duration group (Treatment track)
-```{r, include= FALSE}
-#Create a New Data Set with an Average Depression Variable and Gender
-TrackDF1<-Mothership_Long_dep %>%
-  filter(Duration == "1-5") %>%
-  group_by(TxDay,IPT_track_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-TrackDF1<-TrackDF1[1:20,]
-# plot
-Track1<-ggplot(data=subset(TrackDF1,!is.na(IPT_track_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    #title ="Depression Severity by Track During Partial Hospitalization",
-    subtitle = "Patient discharge 1-5 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 5-10 Days
-TrackDF2<-Mothership_Long_dep %>%
-  filter(Duration == "6-10") %>%
-  group_by(TxDay,IPT_track_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-TrackDF2<-TrackDF2[1:40,]
-
-# plot
-Track2<-ggplot(data=subset(TrackDF2,!is.na(IPT_track_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    #title ="Depression Severity by Track During Partial Hospitalization",
-    subtitle = "Patient discharge 6-10 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 10-15 Days
-TrackDF3<-Mothership_Long_dep %>%
-  filter(Duration == "11-15") %>%
-  group_by(TxDay,IPT_track_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-TrackDF3<-TrackDF3[1:60,]
-
-# plot
-Track3<-ggplot(data=subset(TrackDF3,!is.na(IPT_track_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    #title ="Depression Severity by Track During Partial Hospitalization",
-    subtitle = "Patient discharge 11-15 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 16+ Days
-TrackDF4<-Mothership_Long_dep %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,IPT_track_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-TrackDF4<-TrackDF4[1:80,]
-
-# plot
-Track4<-ggplot(data=subset(TrackDF4,!is.na(IPT_track_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    #title ="Depression Severity by Track During Partial Hospitalization",
-    subtitle = "Patient discharge 16+ days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-```{r}
-ggpubr::ggarrange(Track1,Track2,Track3,Track4,ncol=2,nrow=2)
-```
 ### EDUCATION
@@
 
-Break it up by duration group 
-```{r, include= FALSE}
-#Create a New Data Set with an Average Depression Variable and Gender
-EducationDF1<-Mothership_Long_dep %>%
-  filter(Duration == "1-5") %>%
-  group_by(TxDay,Education_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-EducationDF1<-EducationDF1[1:45,]
-# plot
-Education1<-ggplot(data=subset(EducationDF1,!is.na(Education_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Education Level During Partial Hospitalization",
-    subtitle = "Patient discharge 1-5 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 5-10 Days
-EducationDF2<-Mothership_Long_dep %>%
-  filter(Duration == "6-10") %>%
-  group_by(TxDay,Education_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-EducationDF2<-EducationDF2[1:90,]
-
-# plot
-Education2<-ggplot(data=subset(EducationDF2,!is.na(Education_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Education Level During Partial Hospitalization",
-    subtitle = "Patient discharge 6-10 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 10-15 Days
-EducationDF3<-Mothership_Long_dep %>%
-  filter(Duration == "11-15") %>%
-  group_by(TxDay,Education_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-EducationDF3<-EducationDF3[1:135,]
-
-# plot
-Education3<-ggplot(data=subset(EducationDF3,!is.na(Education_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Education Level During Partial Hospitalization",
-    subtitle = "Patient discharge 11-15 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 16+ Days
-EducationDF4<-Mothership_Long_dep %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,Education_1) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-EducationDF4<-EducationDF4[1:180,]
-
-# plot
-Education4<-ggplot(data=subset(EducationDF4,!is.na(Education_1)),
-       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by Education Level During Partial Hospitalization",
-    subtitle = "Patient discharge 16+ days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,50,by=5))+
-   scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-```{r}
-ggpubr::ggarrange(Education1,Education2,Education3,Education4, ncol=2,nrow=2)
-```
 ### TREATMENT YEAR
@@
 ```
-```
-
-Break it up by duration group (Year)
-```{r, include= FALSE}
-#Create a New Data Set with an Average Depression Variable and Gender
-YEARTXDF1<-Mothership_Long_dep %>%
-  filter(Duration == "1-5") %>%
-  group_by(TxDay,TxYear) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-YEARTXDF1<-YEARTXDF1[1:40,]
-# plot
-YEARTX1<-ggplot(data=subset(YEARTXDF1,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by YEARTX During Partial Hospitalization",
-    subtitle = "Patient discharge 1-5 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559","#4B5D8E"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 5-10 Days
-YEARTXDF2<-Mothership_Long_dep %>%
-  filter(Duration == "6-10") %>%
-  group_by(TxDay,TxYear) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-YEARTXDF2<-YEARTXDF2[1:80,]
-
-# plot
-YEARTX2<-ggplot(data=subset(YEARTXDF2,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by YEARTX During Partial Hospitalization",
-    subtitle = "Patient discharge 6-10 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559","#4B5D8E"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 10-15 Days
-YEARTXDF3<-Mothership_Long_dep %>%
-  filter(Duration == "11-15") %>%
-  group_by(TxDay,TxYear) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-YEARTXDF3<-YEARTXDF3[1:120,]
-
-# plot
-YEARTX3<-ggplot(data=subset(YEARTXDF3,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    #title ="Depression Severity by TX",
-    subtitle = "Patient discharge 11-15 days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559","#4B5D8E"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-
-##### 16+ Days
-YEARTXDF4<-Mothership_Long_dep %>%
-  filter(Duration == "16+") %>%
-  group_by(TxDay,TxYear) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-YEARTXDF4<-YEARTXDF4[1:180,]
-
-# plot
-YEARTX4<-ggplot(data=subset(YEARTXDF4,!is.na(TxYear)),
-       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
-  geom_line(size=.5)+
-  geom_point(size=.5)+
-  labs(
-    # title ="Depression Severity by YEARTX During Partial Hospitalization",
-    subtitle = "Patient discharge 16+ days")+
-    scale_x_continuous(name="Treatment Day",limits=c(0,20,by=1))+
-  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
-  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
-                              "#0098DB","#0065A3","darkgreen",
-                              "#91A9F1","#7F8559","#4B5D8E"))+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title=element_blank())
-```
-
-```{r}
-ggpubr::ggarrange(YEARTX1,YEARTX2,YEARTX3,YEARTX4,ncol=2,nrow=2)
-```

### 2023-04-21 Anxiety_Vis.Rmd
deleting all my hard work :/

@@
   scale_y_continuous(name="Anxiety Severity",limits=c(20,40,by=5))+
-  theme(panel.background=NULL) +
-  geom_vline(xintercept = 5, color = "#BB9D00",alpha =.5)+
-  geom_vline(xintercept = 8, color = "orange",alpha =.5)+
-  geom_vline(xintercept = 13, color = "red",alpha =.5)+
-  annotate("text", x = 5, y = 39, label = "Q1") +
-  annotate("text", x = 8, y = 39, label = "Mean") +
-  annotate("text", x = 13, y = 39, label = "Q3")
+  theme(panel.background=NULL)
 

### 2023-04-21 Data_Import.Rmd
Added legend title.

@@
   ggtitle("Education Level of Patients") +
+  scale_fill_discrete(name = "Education") +
   coord_polar("y",start=0)+

### 2023-04-21 Diagnosis_Vis.Rmd
Added comorbid stuff. Can't figure out CODUS/COXUS post scores.

@@
                       )))))))))),
-
+                  Anxiety_C =  as.factor(
+                    ifelse(  GAD_C ==1 | Panic_C == 1 | PanicAgor_C == 1 | Agoraphobia_C == 1 |
+                        Social_C == 1 | Specific_C == 1, 1, 0)),
+                  Mood_C =  as.factor(
+                    ifelse(MDD_C ==1 | Bipolar1_C == 1 | Bipolar2_C == 1 | Dysthymia_C == 1, 1, 0)),
+                  Substance_C = as.factor(
+                    ifelse(Alcohol_C == 1 | Drug_C ==1, 1, 0)),
+                  Trauma_C = as.factor(
+                    ifelse(PTSD_C == 1 | Adjustment_C ==1, 1,0)),
+                  Psychotic_C = as.factor(
+                    ifelse(Schiz_C == 1 | Schizaff_C == 1,1,0)),
+                  Eating_C = as.factor(
+                    ifelse(Anorex_C == 1 | Bulim_C == 1 | Binge_C == 1, 1,0)),
+                  Somatic_C = as.factor(
+                    ifelse(Somat_C == 1 | UndiffSoma_C == 1| Hypochondriasis_C ==1, 1,0)),
           #emotional disorders
@@
                     ifelse(Anxiety_D == 1 | OCD_P == 1 | Trauma_D == 1 |
-                           Mood_D == 1, "Emotional Disorder", "Other Disorder"))
-                  )
- # Comorbid_Anx = as.factor(
-                      #   ifelse(Anxiety_D == 1 & Mood_D == 1 |
-                      #           Anxiety_D == 1 & OCD_C == 1 |
-                      #           Anxiety_D == 1 & BPD_C == 1 |
-                      #           Anxiety_D == 1 & Substance_D == 1 |
-                      #           Anxiety_D == 1 & Trauma_D == 1 | 
-                      #           Anxiety_D == 1 & Eating_D ==1, 1, 0)),
-                      # Comorbid_Mood = as.factor(
-                      #   ifelse(Mood_D == 1 & Anxiety_D == 1 |
-                      #           Mood_D == 1 & BPD_C == 1 |
-                      #           Mood_D == 1 & BPD_C == 1 |
-                      #           Mood_D == 1 & Substance_D == 1 |
-                      #           Mood_D == 1 & Trauma_D == 1 | 
-                      #           Mood_D == 1 & Eating_D ==1, 1, 0)),
-                      # Comorbid_OCD = as.factor(
-                      #   ifelse(OCD_C == 1 & Anxiety_D == 1 |
-                      #           OCD_C == 1 & Mood_D == 1 |
-                      #           OCD_C == 1 & BPD_C == 1 |
-                      #           OCD_C == 1 & Substance_D == 1 |
-                      #           OCD_C == 1 & Trauma_D == 1 | 
-                      #           OCD_C == 1 & Eating_D ==1, 1, 0)),
-                      # Comorbid_BPD = as.factor(
-                      #   ifelse(BPD_C == 1 & Anxiety_D == 1 |
-                      #           BPD_C == 1 & Mood_D == 1 |
-                      #           BPD_C == 1 & OCD_C == 1 |
-                      #           BPD_C == 1 & Substance_D == 1 |
-                      #           BPD_C == 1 & Trauma_D == 1 | 
-                      #           BPD_C == 1 & Eating_D ==1, 1, 0)),
+                           Mood_D == 1, "Emotional Disorder", "Other Disorder")),
+                  Co_Anx = as.factor(
+                        ifelse(Anxiety_D == 1 & Mood_C == 1 |
+                                Anxiety_D == 1 & OCD_C == 1 |
+                                Anxiety_D == 1 & BPD_C == 1 |
+                                Anxiety_D == 1 & Substance_C == 1 |
+                                Anxiety_D == 1 & Trauma_C == 1 |
+                                Anxiety_D == 1 & Eating_C ==1 |
+                                Anxiety_D == 1 & Psychotic_C ==1 |
+                                Anxiety_D == 1 & Somatic_C ==1, 1, 0)),
+                  Co_Mood = as.factor(
+                        ifelse(Mood_D == 1 & Anxiety_C == 1 |
+                                Mood_D == 1 & OCD_C == 1 |
+                                Mood_D == 1 & BPD_C == 1 |
+                                Mood_D == 1 & Substance_C == 1 |
+                                Mood_D == 1 & Trauma_C == 1 |
+                                Mood_D == 1 & Eating_C ==1 |
+                                Mood_D == 1 & Psychotic_C ==1 |
+                                Mood_D == 1 & Somatic_C ==1 , 1, 0)),
+                  Co_OCD = as.factor(
+                        ifelse(OCD_C == 1 & Anxiety_C == 1 |
+                                OCD_C == 1 & Mood_C == 1 |
+                                OCD_C == 1 & BPD_C == 1 |
+                                OCD_C == 1 & Substance_C == 1 |
+                                OCD_C == 1 & Trauma_C == 1 |
+                                OCD_C == 1 & Eating_C ==1 |
+                                OCD_C == 1 & Psychotic_C ==1 |
+                                OCD_C == 1 & Somatic_C ==1, 1, 0)),
+                  CO_BPD = as.factor(
+                        ifelse(BPD_C == 1 & Anxiety_C == 1 |
+                                BPD_C == 1 & Mood_C == 1 |
+                                BPD_C == 1 & OCD_C == 1 |
+                                BPD_C == 1 & Substance_C == 1 |
+                                BPD_C == 1 & Trauma_C == 1 |
+                                BPD_C == 1 & Eating_C ==1 |
+                                BPD_C == 1 & Psychotic_C ==1 |
+                                BPD_C == 1 & Somatic_C ==1 , 1, 0)),
+                  CO_Psychotic = as.factor(
+                       ifelse(Psychotic_D == 1 & Mood_C == 1 |
+                                Psychotic_D == 1 & OCD_C == 1 |
+                                Psychotic_D == 1 & BPD_C == 1 |
+                                Psychotic_D == 1 & Substance_C == 1 |
+                                Psychotic_D == 1 & Trauma_C == 1 |
+                                Psychotic_D == 1 & Eating_C ==1 |
+                                Psychotic_D == 1 & Anxiety_C ==1 |
+                                Psychotic_D == 1 & Somatic_C ==1, 1, 0)),
+                  CO_Eating = as.factor(
+                      ifelse(Eating_D == 1 & Mood_C == 1 |
+                                Eating_D == 1 & OCD_C == 1 |
+                                Eating_D == 1 & BPD_C == 1 |
+                                Eating_D == 1 & Substance_C == 1 |
+                                Eating_D == 1 & Trauma_C == 1 |
+                                Eating_D == 1 & Psychotic_C ==1 |
+                                Eating_D == 1 & Anxiety_C ==1 |
+                                Eating_D == 1 & Somatic_C ==1, 1, 0)),
+                  CO_Somatic =  as.factor(
+                       ifelse(Somatic_D == 1 & Mood_C == 1 |
+                                Somatic_D == 1 & OCD_C == 1 |
+                                Somatic_D == 1 & BPD_C == 1 |
+                                Somatic_D == 1 & Substance_C == 1 |
+                                Somatic_D == 1 & Trauma_C == 1 |
+                                Somatic_D == 1 & Eating_C ==1 |
+                                Somatic_D == 1 & Anxiety_C ==1 |
+                                Somatic_D == 1 & Psychotic_C ==1, 1, 0)))
 

### 2023-04-21 Treatment_Outcomes.Rmd
Added comorbid stuff. Can't figure out CODUS/COXUS post scores.

@@
 #1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
-Mothership_Pre_Post <- Mothership %>%
+Mothership <- Mothership %>%
   mutate(Mothership_Pre_Post, 
@@
 
-Mothership_Pre_Post$Days_complete_W
+Mothership$Days_complete_W
 
@@
 
+#### Figure out how to:
+    #1. write a for /while loop to get a final value. 
+    #2. get values for NAs for days attended, 
+    #3. get values so this can go into the whole mothership dataset.
+
 #3. Extract the valeues for each patient at their last day (length of stay)
-# Mothership_Pre_Post <- mutate(Mothership_Pre_Post,
-#             CUDOS_post = CUDOS_post,
-#             CUXOS_post = CUXOS_post)
+ Mothership <- mutate(Mothership,
+            # CUDOS_post = CUDOS_post)
+            CUXOS_post = CUXOS_post)
     ##### Why is it not includeing NAs.
 
-CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]
-CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]
+CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
+CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
 
+CUDOS_post
+Mothership %>%
+  mutate(Dep_post = CUDOS_post)
+
+CUDOS_post
 #4. Extract the value for their first day 
@@
 
+AnxDep_PrePost_test
 ## This is where I am Figure out where to go from here *******************

### 2023-04-25 Anxiety_Vis.Rmd
prepped everything for markdowns.

@@
 ```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
 # Libraries 

### 2023-04-25 Data_Import.Rmd
prepped everything for markdowns.

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
 
@@
 ### Bar Chart for Discharge Status ###
-plot(Mothership2$DC_status_1)
 

### 2023-04-25 Depression_Vis.Rmd
prepped everything for markdowns.

@@
 ```{r}
+Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
+Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]
+
+#Create a Time Variable
+Mothership_Long$TxDay <- NA
+Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
+Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
+Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
+Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
+Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
+Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
+Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
+Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
+Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
+Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
 Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
@@
 
-#Create a New Data Set with an Average Depression Variable
+#Create a New Data Set with an Average Anxiety Variable
 Mothership_Mean_CUDOS<-Mothership_Long %>%
@@
   theme(panel.background=NULL) 
-
-ggplot(Mothership, aes(Days_complete_1))+
-  geom_density()+
-  scale_x_continuous(limits=c(0,20,by=1)) +
-  labs(
-    title="Quantity of discharges Per Treatment Day")
-
 ```

### 2023-04-25 Treatment_Outcomes.Rmd
prepped everything for markdowns.

--- 2023-04-15 Treatment_Outcomes.Rmd
@@
 
-## CUDOS and CUXOS over time.
-
-```{r}
-# Depression symptoms df
-CUDOS_Score <- select(Mothership,
-                      Days_complete_1,Day1_CUDOS:Day40_CUDOS)
-
-# Anxiety symptoms df
-CUXOS_Score <- select(Mothership,
-                      Days_complete_1,Day1_CUXOS:Day40_CUXOS)
+```{r, include=FALSE}
+# # Depression symptoms df
+# CUDOS_Score <- select(Mothership,
+#                       Days_complete_1,Day1_CUDOS:Day40_CUDOS)
+# 
+# # Anxiety symptoms df
+# CUXOS_Score <- select(Mothership,
+#                       Days_complete_1,Day1_CUXOS:Day40_CUXOS)
 
@@
 
-```{r}
+```{r, include=FALSE}
 #1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
-Mothership_Pre_Post <- Mothership
-  mutate(Mothership_Pre_Post, 
-            Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
-         )
-
-  Mothership
-#2. Then create df with CUDOS and CUXOS scores
-  # Depression
-
-    CUDOS_Score <- select(Mothership,
-                      Day1_CUDOS:Day40_CUDOS)
-
-  # Anxiety
-    CUXOS_Score <- select(Mothership,
-                      Day1_CUXOS:Day40_CUXOS)
-
-#3. Extract the valeues for each patient at their last day (length of stay)
+# Mothership <- Mothership %>%
 #   mutate(Mothership_Pre_Post, 
-    #         CUDOS_post = CUDOS_Score[
-    #           cbind(seq_along(Mothership_Pre_Post$Days_complete_W),
-    #                 Mothership_Pre_Post$Days_complete_W)],
-    #         CUXOS_post = CUXOS_Score[
-    #           cbind(seq_along(Mothership_Pre_Post$Days_complete_W),
-    #                 Mothership_Pre_Post$Days_complete_W)]
+#             Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
 #          )
-```
-
-```{r}
-CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]
-CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$ Days_complete_W),Mothership$ Days_complete_W)]
-
-#4. Extract the value for their first day 
-CUDOS_pre<-Mothership$Day1_CUDOS
-CUXOS_pre<-Mothership$Day1_CUXOS
-AnxDep_PrePost <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
-AnxDep_PrePost
-
-#5. Create long dataframe
-
-###### This is where I am. I'm trying to figure out how to create the long dataset
-AnxDep_PrePost_Long <- gather(AnxDep_PrePost,ID1:CUXOS_post)
-                              factor_key = "T")
-
-Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
-                              factor_key = "T")
-Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]
-
-?gather()
+# 
+# Mothership$Days_complete_W
+# 
+# #2. Then create df with CUDOS and CUXOS scores
+#   # Depression 
+#   
+#     CUDOS_Score <- select(Mothership,
+#                       Day1_CUDOS:Day40_CUDOS)
+# 
+#   # Anxiety
+#     CUXOS_Score <- select(Mothership,
+#                       Day1_CUXOS:Day40_CUXOS)
+#     
+# #### Figure out how to:
+#     #1. write a for /while loop to get a final value. 
+#     #2. get values for NAs for days attended, 
+#     #3. get values so this can go into the whole mothership dataset. 
+#     
+#     
+#     
+#     
+# #3. Extract the valeues for each patient at their last day (length of stay)
+#  Mothership <- mutate(Mothership,
+#             # CUDOS_post = CUDOS_post)
+#             CUXOS_post = CUXOS_post)
+#     ##### Why is it not includeing NAs.
+# 
+# CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
+# CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
+# 
+# CUDOS_post
+# Mothership %>%
+#   mutate(Dep_post = CUDOS_post)
+# 
+# CUDOS_post
+# #4. Extract the value for their first day 
+# CUDOS_pre<-Mothership$Day1_CUDOS
+# CUXOS_pre<-Mothership$Day1_CUXOS
+# AnxDep_PrePost_test <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
+# AnxDep_PrePost_test
+# colnames(AnxDep_PrePost)[1] = "ID1"
+# 
+# AnxDep_PrePost_test
+# ## This is where I am Figure out where to go from here *******************
+# #5. Create long dataframe
+# 
+# AnxDep_PrePost_Lon <- gather(AnxDep_PrePost,ID1:CUXOS_post,factor_key = "T")
+# 
+# AnxDep_PrePost_Long <- pivot_longer(AnxDep_PrePost,ID1:CUXOS_post)
+# 
+# 
+# AnxDep_PrePost_Long
+# ?pivot_longer()
+# 
+# AnxDep_PrePost_Long <- AnxDep_PrePost_Long[order(AnxDep_PrePost_Long$ID1),]
+# 
+# Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
+#                               factor_key = "T")
+# Mothership_Long_RDQ
 

### 2023-04-29 Diagnosis_Vis.Rmd
Figured out how to make long data for diagnosis!

@@
 ```
+
+```{r}
+ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
+  geom_bar()+
+  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Psychiatric Disorder Subtype")+
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
+  coord_flip()
+```
+
+```{r}
+library(dplyr)
+library(tidyr)
+
+Mothership_Current_Long <- Mothership_Diag %>%
+  pivot_longer(
+    cols=c(Anxiety_C, Mood_C, Substance_C, Trauma_C, Psychotic_C, Eating_C,  Somatic_C),
+    names_to = 'disorder_present'
+  ) %>%
+  filter(value != 0) %>%
+  select(!value) %>%
+  pivot_longer(
+    cols=c(Co_Anx, Co_Mood, Co_OCD, CO_BPD, CO_Psychotic, CO_Eating, CO_Somatic),
+    names_to = 'Co_Occuring'
+  )%>%
+  filter(value != 0) %>%
+  select(!value) 
+  ## pick back up here!!
+    #filter out disorders that are co occuring the same (e.g. anxiety and anxiety)
+    #maybe figure out to make a variable that is co-occuring for primary and secondary same thing (e.g. GAD and panic)
+  # mutate(
+
+view(Mothership_Current_Long)
+
+```
+
+                     Mood_D 
+                    Anxiety_D 
+                #OCD_P is for current OCD
+                #BPD_P is for current BPD
+                    Substance_D 
+                    Trauma_D 
+                    Psychotic_D 
+                    Eating_D 
+                    Somatic_D 
+                    Disorder_Type = primary diag 
+                  Anxiety_C 
+                  Mood_C 
+                  Substance_C
+                  Trauma_C 
+                  Psychotic_C
+                  Eating_C 
+                  Somatic_C 
+                  Emotional_dis 
+                  Co_Anx 
+                  Co_Mood 
+                  Co_OCD
+                  CO_BPD 
+                  CO_Psychotic
+                  CO_Eating 
+                  CO_Somatic

### 2023-04-30 Diagnosis_Vis.Rmd
Co-occuring disorders plot!

--- 2023-04-25 Diagnosis_Vis.Rmd
@@
                       ifelse(Substance_D == 1, "Substance Use",
-                      ifelse(Trauma_D == 1, "Stress and Trauma",
+                      ifelse(Trauma_D == 1, "Trauma",
                       ifelse(Mood_D == 1, "Mood",
@@
                   Anxiety_C =  as.factor(
-                    ifelse(  GAD_C ==1 | Panic_C == 1 | PanicAgor_C == 1 | Agoraphobia_C == 1 |
-                        Social_C == 1 | Specific_C == 1, 1, 0)),
+                    ifelse( GAD_P !=1 & GAD_C ==1 | 
+                        Panic_P != 1 & Panic_C == 1 | 
+                        PanicAgor_P != 1 & PanicAgor_C == 1 | 
+                        Agoraphobia_P != 1 & Agoraphobia_C == 1 |
+                        Social_P != 1 & Social_C == 1 | 
+                        Specific_P != 1 & Specific_C == 1, 1, 0)),
                   Mood_C =  as.factor(
-                    ifelse(MDD_C ==1 | Bipolar1_C == 1 | Bipolar2_C == 1 | Dysthymia_C == 1, 1, 0)),
+                    ifelse( MDD_P != 1 & MDD_C == 1 |
+                        Bipolar1_P != 1 & Bipolar1_C == 1 | 
+                        Bipolar2_P != 1 &  Bipolar2_C == 1 | 
+                        Dysthymia_P != 1 & Dysthymia_C == 1 , 1, 0)),
                   Substance_C = as.factor(
-                    ifelse(Alcohol_C == 1 | Drug_C ==1, 1, 0)),
+                    ifelse(Alcohol_P != 1 & Alcohol_C == 1 | 
+                        Drug_P != 1 & Drug_C ==1, 1, 0)),
                   Trauma_C = as.factor(
-                    ifelse(PTSD_C == 1 | Adjustment_C ==1, 1,0)),
+                    ifelse(PTSD_P != 1 & PTSD_C == 1 | 
+                        Adjustment_P != 1 & Adjustment_C ==1, 1,0)),
                   Psychotic_C = as.factor(
-                    ifelse(Schiz_C == 1 | Schizaff_C == 1,1,0)),
+                    ifelse(Schiz_P != 1 & Schiz_C == 1 | 
+                        Schizaff_P != 1 & Schizaff_C == 1,1,0)),
                   Eating_C = as.factor(
-                    ifelse(Anorex_C == 1 | Bulim_C == 1 | Binge_C == 1, 1,0)),
+                    ifelse(Anorex_P != 1 & Anorex_C == 1 | 
+                        Bulim_P != 1 & Bulim_C == 1 | 
+                        Binge_P != 1 & Binge_C == 1, 1,0)),
                   Somatic_C = as.factor(
-                    ifelse(Somat_C == 1 | UndiffSoma_C == 1| Hypochondriasis_C ==1, 1,0)),
+                    ifelse(Somat_P != 1 & Somat_C == 1 | 
+                        UndiffSoma_P != 1 & UndiffSoma_C == 1 | 
+                        Hypochondriasis_P != 1 &  Hypochondriasis_C == 1, 1,0)),
+                  OCD_Co_C = as.factor(
+                    ifelse(OCD_P != 1 & OCD_C == 1,1,0)),
+                  BPD_Co_C = as.factor(
+                    ifelse(BPD_P != 1 & BPD_C ==1,1,0)),
           #emotional disorders
@@
                                 Somatic_D == 1 & Psychotic_C ==1, 1, 0)))
+
+view(Mothership)
 
@@
 ```
+
+```{r}
+ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
+  geom_bar()+
+  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Psychiatric Disorder Subtype")+
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
+  coord_flip()
+```
+
+```{r}
+library(dplyr)
+library(tidyr)
+
+Mothership_Current_Long <- Mothership %>%
+  pivot_longer(
+    cols=c(Anxiety_C, Mood_C, Substance_C, Trauma_C, Psychotic_C, Eating_C,  Somatic_C, OCD_Co_C, BPD_Co_C),
+    names_to = 'Disorder_Present'
+  ) %>%
+  filter(value != 0) %>%
+  select(!value)  %>%
+  filter(!is.na(Disorder_Present))%>%
+  filter(!is.na(Disorder_Type))
+
+## Figure out how to plot these two
+
+Mothership_Current_Long %>%
+  ggplot(aes(x = Disorder_Type, y = Disorder_Present, color = Disorder_Type)) +
+  geom_count(alpha = .5)+
+  scale_size_area(max_size = 20) +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+    legend.position = "none") +
+  scale_y_discrete(labels=c("Trauma_C" = "Co Trauma", 
+                            "Substance_C" = "Co Substance Use",
+                            "Somatic_C" = "Co Somatic",
+                            "Psychotic_C" = "Co Psychotic",
+                            "OCD_Co_C" = "Co OCD",
+                            "Mood_C" = "Co Mood",
+                            "Eating_C" = "Co Eating",
+                            "BPD_Co_C" = "Co BPD",
+                            "Anxiety_C" = "Co Anxiety")) +
+  labs(
+    title = "Number of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
+    subtitle = "Grouped into subtypes of DSM diagonsis",
+    y = "Co-Occuring Psychiatric Disorder",
+    x = "Primary Psychiatric Diagnosis"
+  )
+
+```

### 2023-05-05 Anxiety_Vis.Rmd
Adding Website to repo

@@
 ---
-title: "Anxiety_vis"
-output: html_document
-date: "2023-04-03"
+title: "Treatment Progression Visualizations"
+output:
+  html_document:
+    toc: true
+    toc_float: true
+    collapsed: false
+    number_sections: false
+    toc_depth: 1
+    #code_folding: hide
 ---
@@
 
-# Anxiety Treatment Progress Charts
+The following code visualizes how patients scores on anxiety and depression measures change over the duration of treatment based upon sociodemographics and treatment information.
 
+# Average Symptom Severity Treatment Progress Charts
+
+## {.tabset}
+
+### Create Data Frames
 ```{r}
+
 Mothership_Long <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
@@
 
-# Mothership_Mean_CUXOS20<-Mothership_Long20 %>%
-#   group_by(TxDay) %>%
-#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+# data frame by druation
+Mothership_Mean_CUXOS_duration<-Mothership_Long %>%
+  group_by(Duration,TxDay) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+Mothership_duration_CUXOS<-Mothership_Mean_CUXOS_duration[1:83,]
+
+Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
+Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]
+
+#Create a Time Variable
+Mothership_Long$TxDay <- NA
+Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
+Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
+Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
+Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
+Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
+Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
+Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
+Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
+Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
+Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
+Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
+Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
+Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
+Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
+Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
+Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
+Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
+Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
+Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
+Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20
+
+#Create a New Data Set with an Average Anxiety Variable
+Mothership_Mean_CUDOS<-Mothership_Long %>%
+  group_by(TxDay) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
 
@@
 
+### Anxiety
 ```{r}
@@
   theme(panel.background=NULL)
+```
 
+```{r,include=FALSE}
 ggplot(Mothership, aes(Days_complete_1))+
@@
   theme_classic()
-
 ```
 
-### plot means based upon duration group membership
+This visualization suggests that some patients get better quickly, while those that stay in treatment longer have higher anxiety.
+
+#### Plot means based upon duration of treatment
 
 ```{r}
-#plot Anxiety mean with each group
-
 # New dataset for the treatment duration Anxiety plot
-Mothership_Mean_CUXOS<-Mothership_Long %>%
-  group_by(Duration,TxDay) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
+# Mothership_Mean_CUXOS<-Mothership_Long %>%
+#   group_by(Duration,TxDay) %>%
+#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+# 
+# Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
 #delete weird Na values and put NA for values
@@
 
-## Anxiety Treatment Progress by Characteristics
+This shows that those who are in treatment longer tend to have higher anxiety than those who are in treatment for less time.
 
-#### Race
+### Depression
+
+```{r}
+#Plot the Depression Mean for Full Sample
+ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
+  geom_line(size=1,color="#0065A3")+
+  geom_point(color="#0065A3")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  ggtitle("Mean Depression Severity During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
+  theme(panel.background=NULL) 
+```
+
+#### Plot means based upon duration of treatment
+
+```{r}
+#plot depression mean with each group
+
+# New dataset for the treatment duration depression plot
+Mothership_Mean_CUDOS<-Mothership_Long %>%
+  group_by(Duration,TxDay) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+Mothership_duration_CUDOS<-Mothership_Mean_CUDOS[1:83,]
+#delete weird Na values and put NA for values
+Mothership_duration_CUDOS[6:20,3] = NA
+Mothership_duration_CUDOS[37:41,3] = NA
+Mothership_duration_CUDOS[74:83,3] = NA
+Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-21),]
+Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-41),]
+Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-61),]
+Mothership_duration_CUDOS
+
+ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
+  geom_line(size=1)+
+  geom_point()+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  ggtitle("Mean Depression Severity During Partial Hospitalization")+
+  labs(subtitle = "Broken up by Discharge Date")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
+  scale_color_manual(values=c("skyblue","#0065A3",
+                              "navy","blue"))+
+  theme(panel.background=NULL)
+```
+
+# Treatment Progress by Race
+
+## {.tabset}
+
+### Anxiety
 ```{r}
@@
 ```
-## GENDER IDENTITY
-Create a New Data Set with an Average Anxiety Variable and Gender, then plot it
+
+### Depression
+```{r}
+Mothership_Long_dep <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
+Mothership_Long_dep <- Mothership_Long_dep[order(Mothership_Long_dep$ID1),]
+
+#Create a Time Variable
+Mothership_Long_dep$TxDay <- NA
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day1_CUDOS"]<-1
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day2_CUDOS"]<-2
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day3_CUDOS"]<-3
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day4_CUDOS"]<-4
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day5_CUDOS"]<-5
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day6_CUDOS"]<-6
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day7_CUDOS"]<-7
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day8_CUDOS"]<-8
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day9_CUDOS"]<-9
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day10_CUDOS"]<-10
+
+#Overall race
+Mothership_Mean_CUDOS_Race<-Mothership_Long_dep %>%
+  group_by(TxDay,Race_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+# plot
+ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
+  geom_line(size=1)+
+  geom_point()+
+  labs(title ="Depression Severity by Race During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","darkgreen",
+                              "#0098DB","#0065A3","#A0AFA1"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
+  geom_line(size=1)+
+  geom_point()+
+  labs(title ="Depression Severity by Race During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("#209845","lightgrey","lightgrey",
+                              "lightgrey","lightgrey","lightgrey"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
+  geom_line(size=1)+
+  geom_point()+
+  labs(title ="Depression Severity by Race During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
+  scale_color_manual(values=c("lightgrey","lightgrey","darkgreen",
+                              "lightgrey","#0065A3","lightgrey"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+# Treatment Progress by Gender Idenitity
+
+## {.tabset}
+
+### Anxiety
 ```{r}
@@
 
-#### TREATMENT TRACK
+### Depression
+```{r}
+#Create a New Data Set with an Average Depression Variable and Gender
+Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
+  group_by(TxDay,Gender_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+Mothership_Mean_CUDOS_Gender <-filter(Mothership_Mean_CUDOS_Gender,
+                                      Gender_1 != "Unknown",
+                                      Gender_1 != "Non-Binary",
+                                      Gender_1 != "Other"
+                                        )
+#Create the Depression Line Graph by Gender
+ggplot(data=subset(Mothership_Mean_CUDOS_Gender,!is.na(Gender_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Depression Severity by Gender During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(15,45,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+# Treatment Progress by Treatment Track
+
+## {.tabset}
+
+### Anxiety
 ```{r}
@@
 ```
-### EDUCATION
+
+### Depression
+```{r}
+#Create a New Data Set with an Average Depression Variable and Track
+Mothership_Mean_CUDOS_Track<-Mothership_Long_dep %>%
+  group_by(TxDay,IPT_track_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+#Create the Depression Line Graph by Treatment Track
+ggplot(data=subset(Mothership_Mean_CUDOS_Track,!is.na(IPT_track_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Depression Severity by Treatment Track During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#0065A3"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+# Treatment progress by Education
+
+## {.tabset}
+
+### Anxiety
 ```{r}
@@
 
-### TREATMENT YEAR
+### Depression
+```{r}
+#Create a New Data Set with an Average Depression Variable and Education
+Mothership_Mean_CUDOS_Ed<-Mothership_Long_dep %>%
+  group_by(TxDay,Education_1) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+#Create the Depression Line Graph by Education
+ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
+  geom_line(size=.75)+
+  geom_point(size=.75)+
+  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#0065A3","darkgreen",
+                              "#91A9F1","#7F8559"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
+       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
+  geom_line(size=.75)+
+  geom_point(size=.75)+
+  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
+  scale_color_manual(values=c("#209845","lightgrey","lightgrey",
+                              "#0098DB","lightgrey","lightgrey",
+                              "lightgrey","lightgrey"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+```
+
+# Treatment Progress by Treatment Year
+
+## {.tabset}
+
+### Anxiety
 ```{r}
@@
 ```
+
+### Depresssion
+
+```{r}
+#Create a New Data Set with an Average Depression Variable and Year
+Mothership_Mean_CUDOS_Year<-Mothership_Long_dep %>%
+  group_by(TxDay,TxYear) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+str(Mothership_Long_dep$TxYear)
+
+#Create the Depression Line Graph by Year
+ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
+  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
+                              "#0098DB","#91A9F1","darkgreen",
+                              "#0065A3","#7F8559","#4B5D8E"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+#Create the Depression Line Graph by Year
+ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
+       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
+  geom_line(size=1)+
+  geom_point()+
+  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
+    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
+  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
+  scale_color_manual(values=c("lightgrey","lightgrey","lightgrey",
+                              "lightgrey","lightgrey","lightgrey",
+                              "#0065A3","lightgrey","lightgrey"))+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title=element_blank())
+
+```

### 2023-05-05 Data_Import.Rmd
Adding Website to repo

--- 2023-04-21 Data_Import.Rmd
@@
 ---
-title: "Data_Import"
-output: html_document
-date: "2023-04-01"
+title: "Background on Patients"
+output:
+  html_document:
+    toc: true
+    toc_float: true
+    collapsed: false
+    number_sections: false
+    toc_depth: 1
+    #code_folding: hide
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r setup}
+knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
 
@@
 
-## Import data
+# Import data
+
 Read in the dataset. 
@@
 
-# Background Statistics
+# Sociodemographic Visualizations
+
+## {.tabset}
+
+### Education Status
 ```{r}
-### Bar Chart for Discharge Status ###
-plot(Mothership2$DC_status_1)
-
-ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
-  geom_bar(color = "black",fill="darkgreen")+
-  ggtitle("Frequency of Treatment Discharge Status") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Discharge Status") +
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6000))
-
-### Bar Chart for Education Status ###
-
 ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
@@
   scale_y_continuous(name = "Frequency",limits=c(0,3000))
+```
 
-### Bar chart for race ###
+### Race
+```{r}
 ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
@@
   scale_y_continuous(name = "Frequency",limits=c(0,6500))
+```
 
-### Bar chart for gender###
+### Gender
+```{r}
 ggplot(data = subset(Mothership, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
@@
   scale_y_continuous(name = "Frequency",limits=c(0,6500))
-
-### Treatment Track ###
-
-ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
-  geom_bar(color = "black",fill="skyblue")+
-  ggtitle("Frequency of Treatment Type") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Treatment Type")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6500))
-
-### Treatment Year ###
-
-Mothership$TxYear
-
-ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
-  geom_bar(color = "black",fill="#9350C7")+
-  ggtitle("Frequency of Patients per Year") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Treatment Year")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,1500))
-
-### Duration of Treatment ###
-ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
-  geom_bar(color = "black",fill="lightgreen")+
-  ggtitle("Frequency of Patients per Duration of Treatment") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Treatment Duration")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6500))
-
 ```
 
-## Pie Chart For Education Status 
+# Pie Chart For Education Status 
+We wanted to learn how to make a pie chart in R so here is one!
 ```{r}
@@
 ```
+
+# Treatment Related Visualizations
+
+## {.tabset}
+
+### Discharge Status
+```{r}
+### Bar Chart for Discharge Status ###
+
+ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
+  geom_bar(color = "black",fill="darkgreen")+
+  ggtitle("Frequency of Treatment Discharge Status") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Discharge Status") +
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6000))
+```
+
+### Treatment Track
+```{r}
+### Treatment Track ###
+
+ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
+  geom_bar(color = "black",fill="skyblue")+
+  ggtitle("Frequency of Treatment Type") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Treatment Type")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+```
+
+### Treatment Year
+```{r}
+### Treatment Year ###
+
+ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
+  geom_bar(color = "black",fill="#9350C7")+
+  ggtitle("Frequency of Patients per Year") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Treatment Year")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,1500))
+```
+
+### Duration of Treatment
+```{r}
+### Duration of Treatment ###
+ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
+  geom_bar(color = "black",fill="lightgreen")+
+  ggtitle("Frequency of Patients per Duration of Treatment") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Treatment Duration")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+
+```

### 2023-05-05 Depression_Vis.Rmd
Adding Website to repo

@@
 
-### plot means based upon duration group membership
+### Plot means based upon duration of treatment
 
@@
 ```{r}
-#GENDER IDENTITY
 #Create a New Data Set with an Average Depression Variable and Gender

### 2023-05-05 Diagnosis_Vis.Rmd
Adding Website to repo

--- 2023-04-25 Diagnosis_Vis.Rmd
@@
 ---
-title: "Diagnosis_Vis"
-output: html_document
-date: "2023-04-04"
+title: "Diagnosis Visualizations"
+output:
+  html_document:
+    toc: true
+    toc_float: true
+    collapsed: false
+    number_sections: false
+    toc_depth: 1
+    #code_folding: hide
 ---
@@
 
-## Create Diagnosis Variables 
+The following code creates visualizations for diagnostic related information.
+The main difficulty of these visualizations was getting diagnostic variables correctly coded so there was not overlap or double acounting for conditions.
+
+# Create Diagnosis Variables 
 ```{r}
@@
 
-#### Amount of disorders treated
-```{r}
-#overall psychiatric disorders
-ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
-  geom_bar()+
-  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Psychiatric Disorder Subtype")+
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
-  coord_flip()
-```
+# Number of Disorders Treated Over Time
 
-#### Number of disorders over time.
+## {.tabset}
+
+### All Disorders
 ```{r}
@@
 ```
+### Excluding Mood Disorders
 
@@
 ```
+
+# Amount of Disorder Type Treated 
+Grouped into DSM chapter subtypes (e.g., Mood Disorder = Major Depressive Disorder, Bipolar 1 & 2, etc.)
+
+### Amount of Primary Diagnoses
+```{r}
+# Disorder Type 
+ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
+  geom_bar()+
+  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+        legend.position = "none")+
+  xlab("Psychiatric Disorder Subtype")+
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
+  coord_flip()
+```
+
+As you can see, the main disorder type in the hospital is mood realted disorders.
+This shouldn't be supprising as many indiviudals with suicidality (A common hospitalization issue) will meet criteria for a mood disorder.
+
+### Excluding Mood Disorders
+```{r}
+# Disorder Type (Without Depression)
+ggplot(data = subset(No_depressy, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
+  geom_bar()+
+  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+        legend.position = "none")+
+  xlab("Psychiatric Disorder Subtype")+
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
+  coord_flip()
+```
+
+### Number of Co-occuring Disorders
+The following visualization looks at the number of disorders people had, but wasn't the main reason they attended the hospital, or their "main" diagnosis.
+```{r}
+Mothership_Current_Long <- Mothership %>%
+  pivot_longer(
+    cols=c(Anxiety_C, Mood_C, Substance_C, Trauma_C, Psychotic_C, Eating_C,  Somatic_C, OCD_Co_C, BPD_Co_C),
+    names_to = 'Disorder_Present') %>%
+  filter(value != 0) %>%
+  select(!value)  %>%
+  filter(!is.na(Disorder_Present))%>%
+  filter(!is.na(Disorder_Type))
+
+ggplot(data = subset(Mothership_Current_Long, !is.na(Disorder_Present)),mapping = aes(x = Disorder_Present, fill=Disorder_Present))+
+  geom_bar()+
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+        legend.position = "none") +
+  labs(title = "Number of Co Occuring Psychiatric Diosrders",
+    subtitle = "In Addition to the Primary Diagnosis",
+    x = "Co-Occuring Psychiatric Disorder") +
+    scale_x_discrete(labels=c("Trauma_C" = "Trauma", 
+                            "Substance_C" = "Substance Use",
+                            "Somatic_C" = "Somatic",
+                            "Psychotic_C" = "Psychotic",
+                            "OCD_Co_C" = "OCD",
+                            "Mood_C" = "Mood",
+                            "Eating_C" = "Eating",
+                            "BPD_Co_C" = "BPD",
+                            "Anxiety_C" = "Anxiety")) +
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
+  coord_flip()
+```
+
+# Primary and Co-occuring Disorders.
+
+The following visualization shows which disorders are co-occurring with which types of primary diagnoses. 
+```{r}
+library(dplyr)
+library(tidyr)
+
+Mothership_Current_Long %>%
+  ggplot(aes(x = Disorder_Type, y = Disorder_Present, color = Disorder_Type)) +
+  geom_count(alpha = .5)+
+  scale_size_area(max_size = 20) +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+    legend.position = "none") +
+  scale_y_discrete(labels=c("Trauma_C" = "Co Trauma", 
+                            "Substance_C" = "Co Substance Use",
+                            "Somatic_C" = "Co Somatic",
+                            "Psychotic_C" = "Co Psychotic",
+                            "OCD_Co_C" = "Co OCD",
+                            "Mood_C" = "Co Mood",
+                            "Eating_C" = "Co Eating",
+                            "BPD_Co_C" = "Co BPD",
+                            "Anxiety_C" = "Co Anxiety")) +
+  labs(title = "Number of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
+    subtitle = "Grouped into subtypes of DSM diagonsis",
+    y = "Co-Occuring Psychiatric Disorder",
+    x = "Primary Psychiatric Diagnosis") 
+```

### 2023-05-05 Treatment_Outcomes.Rmd
Adding Website to repo

@@
 ---
-title: "Treatment_Outcomes"
-output: html_document
-date: "2023-04-14"
+title: "Treatment Outcome Visualization"
+output:
+  html_document:
+    toc: true
+    toc_float: true
+    collapsed: false
+    number_sections: false
+    toc_depth: 1
+    #code_folding: hide
 ---
@@
 
-## RDQ stuff
+# Remission from Depression Questionnaire (RDQ)
+
+The following code visualizes the outcomes from the RDQ. The RDQ is broken up into the following categories:
+
+1. Coping Skills: (higher score = more coping skills)
+2. Positive Mental Health: (higher score = more positive mental health)
+3. Functioning: (higher score = better functioning)
+4. Well Being: (higher score = better overall well being)
+5. Symptoms: (higher score = more severe depression symptoms)
+
 ```{r}
-
 #Read in a New Data Set
@@
 Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]
-
-view(Mothership_Long_RDQ)
 
@@
 ```{r, include=FALSE}
-# # Depression symptoms df
+# Depression symptoms df
 # CUDOS_Score <- select(Mothership,
@@
 #1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
+# 
+# 
+# Mothership_post <- Mothership %>%
+#   mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1))
+# 
+# 
+# 
 # Mothership <- Mothership %>%
-#   mutate(Mothership_Pre_Post, 
-#             Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)
-#          )
+#   mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1))
 #          
+# 
+# Mothership$Day1_CUDOS
+# Mothership$Days_complete_1
 # Mothership$Days_complete_W
 # 
+# view(Mothership)
 # #2. Then create df with CUDOS and CUXOS scores
@@
 # 
-# #### Figure out how to:
-#     #1. write a for /while loop to get a final value. 
-#     #2. get values for NAs for days attended, 
-#     #3. get values so this can go into the whole mothership dataset. 
+# 
+# #3. Extract the valeues for each patient at their last day (length of stay)
+#     ##### Why is it not includeing NAs.
 #     
 # 
+# CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
+# CUXOS_post = CUXOS_Score[cbind(1:length(Mothership$Days_complete_W),Mothership$Days_complete_W)]
+# 
+# seq_along(Mothership$Days_complete_W)
+# Mothership$Days_complete_W
+# CUDOS_post
+# 
+# Mothership %>%
+#   mutate(Dep_post = CUDOS_post)
 # 
 # 
-# #3. Extract the valeues for each patient at their last day (length of stay)
-#  Mothership <- mutate(Mothership,
-#             # CUDOS_post = CUDOS_post)
-#             CUXOS_post = CUXOS_post)
-#     ##### Why is it not includeing NAs.
-# 
-# CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
-# CUXOS_post = CUXOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
-# 
-# CUDOS_post
 # Mothership %>%
@@
 ```
+
+```{r, include=FALSE}
+# Mothership_Post <- Mothership %>%
+#   filter(!is.na(Days_complete_1)) %>%
+#   mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)) 
+#   
+# 
+# Mothership_Post$Days_complete_W
+# 1:length(Mothership_Post$Days_complete_W)
+# 
+# # Depression
+# CUDOS_Score <- select(Mothership_Post, Day1_CUDOS:Day40_CUDOS)
+# 
+# CUDOS_Score
+# 
+# 1:length(Mothership_Post$Days_complete_W)
+# 
+# # Anxiety
+# CUXOS_Score <- select(Mothership_Post, Day1_CUXOS:Day40_CUXOS)
+# 
+# values <- cbind(seq_along(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W[1:8610])
+# values
+# CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership_Post$Days_complete_W)[1:8610],Mothership_Post$Days_complete_W[1:8610])]
+# CUDOS_post
+# 
+# 
+# CUDOS_post = CUDOS_Score[cbind(1:length(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W)]
+# CUXOS_post = CUXOS_Score[cbind(1:length(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W)]
+# 
+# CUDOS_post
+# 
+# values <- cbind(1:length(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W)
+# values
+# Mothership_Post<- Mothership_Post %>%
+#   mutate(Dep_post = CUDOS_post)
+```

### 2023-05-05 Whole_thing.Rmd
Adding Website to repo

---
title: "Whole thing"
output: html_document
date: "2023-04-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
```

```{r}
# Libraries
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
```

## Import data
Read in the dataset. 
```{r}
df <- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
Mothership<-select(df,ID1:Sexuality_1,MDD_C:Day40_CUXOS,SUMdep_0:SUManx_1,SUMdep_DC,SUManx_DC,BL_CUDOS, BL_CUXOS)
view(Mothership)
```
#### Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles
Mothership <- mutate(Mothership, 
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                          "1"="Complete",
                                          "2"="Nearly Complete",
                                          "3"="Insurance",
                                          "4"="Nonatteneance",
                                          "5"="Inappropriate",
                                          "6"="Inpatient",
                                          "7"="Withdrew",
                                          "8"="Dissatisfaction",
                                          "9"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                          "1"="<Grade 12",
                                          "2"="HS Diploma",
                                          "3"="GED",
                                          "4"="Some College",
                                          "5"="Associates Degree",
                                          "6"="Bachelors Degree",
                                          "7"="Some Grad School",
                                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                                       "0"="Female",
                                       "1"="Male",
                                       "2"="Non-Binary",
                                       "3"="Other",
                                       "4"="Unknown"),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                                             "0"="Married",
                                             "1"="Cohabitating",
                                             "2"="Widowed",
                                             "3"="Separated",
                                             "4"="Divorced",
                                             "5"="Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                                          "1"="Straight",
                                          "2"="Gay",
                                          "3"="Bisexual",
                                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                                          "0"="General",
                                          "1"="Trauma",
                                          "2"="Young Adult",
                                          "3"="BPD"),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                      "0"="<Grade 6", 
                                      "1"="Grades 7-12",
                                      "2"="HS Diploma", 
                                      "3"="GED",
                                      "4"="Some College",
                                      "5"="Associates Degree",
                                      "6"="Bachelors Degree",
                                      "7"="Some Grad School",
                                      "8"="Grad Degree"),
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                      "1"="Treatment Complete",
                                      "2"="Treatment Near Complete",
                                      "3"="Insurance Stopped",
                                      "4"="Nonattendence",
                                      "5"="Inapproparite Language",
                                      "6"="Transfered To Impatient",
                                      "7"="Withdrew for External factors",
                                      "8"="Withdrew (AMA)",
                                      "9"="Other",
                                      "10"="Other"),
                    DC_status_1 = as.factor(DC_status_1),
                    DC_status_1 = recode(DC_status_1,
                                      "1"="Inpatient",
                                      "2"="PHP",
                                      "3"="APS",
                                      "4"="Psychatrist",
                                      "5"="PCP",
                                      "6"="Another Physican",
                                      "7"="Therapist",
                                      "17"="Other"
                    ),

#Lets make some new variables 
      #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "2",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "3", "4"
                              )))),
                    Duration = recode(Duration,
                                      "1"="1-5",
                                      "2"="6-10",
                                      "3"="11-15",
                                      "4"="16+"
                                      ))

#Extract Year From Intake Date
#Convert to Date
library("lubridate")
Mothership$Intake_1<-ymd(Mothership$Intake_1)
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014",
                                   "2021"="2020",
                                   "2022"="2020"))

```

### Export as CSV
```{r}
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Vis.csv")
```

# Background Statistics
```{r}
### Bar Chart for Discharge Status ###

ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
  geom_bar(color = "black",fill="darkgreen")+
  ggtitle("Frequency of Treatment Discharge Status") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Discharge Status") +
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6000))

### Bar Chart for Education Status ###

ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))

### Bar chart for race ###
ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
  geom_bar(color = "black",fill="darkblue")+
  ggtitle("Frequency of Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Race")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

### Bar chart for gender###
ggplot(data = subset(Mothership, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
  geom_bar(color = "black",fill="darkorange")+
  ggtitle("Frequency of Gender") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Gender")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

### Treatment Track ###

ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

### Treatment Year ###

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1500))

### Duration of Treatment ###
ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
  geom_bar(color = "black",fill="lightgreen")+
  ggtitle("Frequency of Patients per Duration of Treatment") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Duration")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

```

## Pie Chart For Education Status 
```{r}
#Create Table and Data Frame
Education<-table(Mothership$Education_1)
Education_df<-as.data.frame(Education)
Education_df

#Rename Columns
colnames(Education_df)[1]="Category"
colnames(Education_df)[2]="Frequency"

Education_df$Category=recode(Education_df$Category,
                             "0"="<Grade 6", 
                             "1"="Grades 7-12",
                             "2"="HS Diploma", 
                             "3"="GED",
                             "4"="Some College",
                             "5"="Associates Degree",
                             "6"="Bachelors Degree",
                             "7"="Some Grad School",
                             "8"="Grad Degree")

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  ggtitle("Education Level of Patients") +
  scale_fill_discrete(name = "Education") +
  coord_polar("y",start=0)+
  theme_void()
```

## Visualizing disorders

#### Create Diagnosis Variables 
```{r}
Mothership<-Mothership %>%
  mutate(
          # Mood Disorders
                     Mood_D = as.factor(
                      ifelse(
                        MDD_P ==1 | Bipolar1_P == 1 | Bipolar2_P == 1 | Dysthymia_P == 1, 1, 0)),
          # Anxiety Disorders
                    Anxiety_D = as.factor(
                      ifelse(
                        GAD_P ==1 | Panic_P == 1 | PanicAgor_P == 1 | Agoraphobia_P == 1 |
                        Social_P == 1 | Specific_P == 1, 1, 0)),
          # Obsessive Compusive Disorders
                #OCD_P is for current OCD
          # Personality Disorders
                #BPD_P is for current BPD
          # Substance Use Disorders
                    Substance_D = as.factor(
                      ifelse(
                        Alcohol_P == 1 | Drug_P ==1, 1, 0)),
          # Trauma or stresor related disorders
                    Trauma_D = as.factor(
                      ifelse(PTSD_P == 1 | Adjustment_P ==1, 1,0)),
          # Psychotic Disorders
                    Psychotic_D = as.factor(
                      ifelse(
                        Schiz_P == 1 | Schizaff_P == 1,1,0)),
            # Eating Disorders
                    Eating_D = as.factor(
                      ifelse(
                        Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1, 1,0)),
            # Somatic Disroders
                    Somatic_D = as.factor(
                      ifelse(
                        Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1,
                        1,0)),
                    Disorder_Type = as.factor(
                      ifelse(Anxiety_D == 1, "Anxiety",
                      ifelse(OCD_P == 1, "OCD",
                      ifelse(BPD_P == 1, "BPD",
                      ifelse(Substance_D == 1, "Substance Use",
                      ifelse(Trauma_D == 1, "Stress and Trauma",
                      ifelse(Mood_D == 1, "Mood",
                      ifelse(Psychotic_D == 1, "Psychotic", 
                      ifelse(Eating_D == 1, "Eating", 
                      ifelse(Somatic_D == 1, "Somatic", NA
                      )))))))))),
                  Anxiety_C =  as.factor(
                    ifelse(  GAD_C ==1 | Panic_C == 1 | PanicAgor_C == 1 | Agoraphobia_C == 1 |
                        Social_C == 1 | Specific_C == 1, 1, 0)),
                  Mood_C =  as.factor(
                    ifelse(MDD_C ==1 | Bipolar1_C == 1 | Bipolar2_C == 1 | Dysthymia_C == 1, 1, 0)),
                  Substance_C = as.factor(
                    ifelse(Alcohol_C == 1 | Drug_C ==1, 1, 0)),
                  Trauma_C = as.factor(
                    ifelse(PTSD_C == 1 | Adjustment_C ==1, 1,0)),
                  Psychotic_C = as.factor(
                    ifelse(Schiz_C == 1 | Schizaff_C == 1,1,0)),
                  Eating_C = as.factor(
                    ifelse(Anorex_C == 1 | Bulim_C == 1 | Binge_C == 1, 1,0)),
                  Somatic_C = as.factor(
                    ifelse(Somat_C == 1 | UndiffSoma_C == 1| Hypochondriasis_C ==1, 1,0)),
          #emotional disorders
                  Emotional_dis = as.factor(
                    ifelse(Anxiety_D == 1 | OCD_P == 1 | Trauma_D == 1 |
                           Mood_D == 1, "Emotional Disorder", "Other Disorder")),
                  Co_Anx = as.factor(
                        ifelse(Anxiety_D == 1 & Mood_C == 1 |
                                Anxiety_D == 1 & OCD_C == 1 |
                                Anxiety_D == 1 & BPD_C == 1 |
                                Anxiety_D == 1 & Substance_C == 1 |
                                Anxiety_D == 1 & Trauma_C == 1 |
                                Anxiety_D == 1 & Eating_C ==1 |
                                Anxiety_D == 1 & Psychotic_C ==1 |
                                Anxiety_D == 1 & Somatic_C ==1, 1, 0)),
                  Co_Mood = as.factor(
                        ifelse(Mood_D == 1 & Anxiety_C == 1 |
                                Mood_D == 1 & OCD_C == 1 |
                                Mood_D == 1 & BPD_C == 1 |
                                Mood_D == 1 & Substance_C == 1 |
                                Mood_D == 1 & Trauma_C == 1 |
                                Mood_D == 1 & Eating_C ==1 |
                                Mood_D == 1 & Psychotic_C ==1 |
                                Mood_D == 1 & Somatic_C ==1 , 1, 0)),
                  Co_OCD = as.factor(
                        ifelse(OCD_C == 1 & Anxiety_C == 1 |
                                OCD_C == 1 & Mood_C == 1 |
                                OCD_C == 1 & BPD_C == 1 |
                                OCD_C == 1 & Substance_C == 1 |
                                OCD_C == 1 & Trauma_C == 1 |
                                OCD_C == 1 & Eating_C ==1 |
                                OCD_C == 1 & Psychotic_C ==1 |
                                OCD_C == 1 & Somatic_C ==1, 1, 0)),
                  CO_BPD = as.factor(
                        ifelse(BPD_C == 1 & Anxiety_C == 1 |
                                BPD_C == 1 & Mood_C == 1 |
                                BPD_C == 1 & OCD_C == 1 |
                                BPD_C == 1 & Substance_C == 1 |
                                BPD_C == 1 & Trauma_C == 1 |
                                BPD_C == 1 & Eating_C ==1 |
                                BPD_C == 1 & Psychotic_C ==1 |
                                BPD_C == 1 & Somatic_C ==1 , 1, 0)),
                  CO_Psychotic = as.factor(
                       ifelse(Psychotic_D == 1 & Mood_C == 1 |
                                Psychotic_D == 1 & OCD_C == 1 |
                                Psychotic_D == 1 & BPD_C == 1 |
                                Psychotic_D == 1 & Substance_C == 1 |
                                Psychotic_D == 1 & Trauma_C == 1 |
                                Psychotic_D == 1 & Eating_C ==1 |
                                Psychotic_D == 1 & Anxiety_C ==1 |
                                Psychotic_D == 1 & Somatic_C ==1, 1, 0)),
                  CO_Eating = as.factor(
                      ifelse(Eating_D == 1 & Mood_C == 1 |
                                Eating_D == 1 & OCD_C == 1 |
                                Eating_D == 1 & BPD_C == 1 |
                                Eating_D == 1 & Substance_C == 1 |
                                Eating_D == 1 & Trauma_C == 1 |
                                Eating_D == 1 & Psychotic_C ==1 |
                                Eating_D == 1 & Anxiety_C ==1 |
                                Eating_D == 1 & Somatic_C ==1, 1, 0)),
                  CO_Somatic =  as.factor(
                       ifelse(Somatic_D == 1 & Mood_C == 1 |
                                Somatic_D == 1 & OCD_C == 1 |
                                Somatic_D == 1 & BPD_C == 1 |
                                Somatic_D == 1 & Substance_C == 1 |
                                Somatic_D == 1 & Trauma_C == 1 |
                                Somatic_D == 1 & Eating_C ==1 |
                                Somatic_D == 1 & Anxiety_C ==1 |
                                Somatic_D == 1 & Psychotic_C ==1, 1, 0)))

##### df for plots

# df without NAs in date and disorder type
Mothership_Diag <- Mothership %>%
  filter(!is.na(Disorder_Type))%>%
  filter(!is.na(TxYear))

# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")
```

#### Amount of disorders treated
```{r}
#overall psychiatric disorders
ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3500))+
  coord_flip()
```

#### Number of disorders over time.
```{r}
# Libraries
library(ggplot2)
#install.packages("hrbrthemes")
library(hrbrthemes)
library(dplyr)
library(tidyr)
library(viridis)

# Stacked
ggplot(data=subset(Mothership_Diag, !is.na(Disorder_Type)), 
       mapping= aes(x=TxYear, y = stat(count),
                    group=Disorder_Type, fill=Disorder_Type)) +
    geom_density(adjust=1.5,alpha=.4,position="fill") +
    theme(axis.text.x = element_text(angle = 45,hjust = 1))+
     theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
     xlab("Treatment Year") +
  theme(panel.background=NULL) +
    facet_wrap(~Emotional_dis)+
  labs(
    title = "Type of Disorders Treated at the Hospital Per Year",
    subtitle = "Broken Up By Disorder Types") +
    xlab("Treatment Year") +
    ylab("Percent of Patients With Disorder")

# Broken up by disorder. 
ggplot(data=subset(Mothership_Diag, !is.na(Disorder_Type)), 
    mapping= aes(x=TxYear,y = stat(count),
                 group=Disorder_Type, fill=Disorder_Type)) +
  geom_density(adjust=1.5,alpha=.6) +
  facet_wrap(~Disorder_Type)+
  theme_classic()+
    theme(
      panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2),
      axis.text.x = element_text(angle = 45,hjust = 1),
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      axis.ticks.x=element_blank(),
      panel.background=NULL) +
  labs(
    title = "Type of Disorders Treated at the Hospital Per Year",
    subtitle = "Broken Up By Dmotional vs Other Disorders") +
    xlab("Treatment Year") +
    ylab("Number of Patients With Disorder")

```

```{r}
# without depression
ggplot(data=subset(No_depressy, !is.na(Disorder_Type)), 
    mapping= aes(x=TxYear,y = stat(count),
                 group=Disorder_Type, fill=Disorder_Type)) +
  geom_density(adjust=1.5,alpha=.6) +
  facet_wrap(~Disorder_Type)+
  theme_classic()+
    theme(
      panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2),
      axis.text.x = element_text(angle = 45,hjust = 1),
      legend.position="none",
      panel.spacing = unit(0.1, "lines"),
      axis.ticks.x=element_blank(),
      panel.background=NULL) +
  labs(
    title = "Type of Disorders Treated at the Hospital Per Year",
    subtitle = "Broken Up By Dmotional vs Other Disorders") +
    xlab("Treatment Year") +
    ylab("Number of Patients With Disorder")
```

## Depression Treatment Progress Charts

```{r}
Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]

#Create a Time Variable
Mothership_Long$TxDay <- NA
Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20

#Create a New Data Set with an Average Anxiety Variable
Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
```

```{r}
#Plot the Depression Mean for Full Sample
ggplot(data=Mothership_Mean_CUDOS,aes(x=TxDay,y=mean_CUDOS))+
  geom_line(size=1,color="#0065A3")+
  geom_point(color="#0065A3")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(20,35,by=5))+
  theme(panel.background=NULL)

ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20,by=1)) +
  labs(
    title="Quantity of discharges Per Treatment Day")

```

### plot means based upon duration group membership

```{r}
#plot depression mean with each group

# New dataset for the treatment duration depression plot
Mothership_Mean_CUDOS<-Mothership_Long %>%
  group_by(Duration,TxDay) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

Mothership_duration_CUDOS<-Mothership_Mean_CUDOS[1:83,]
#delete weird Na values and put NA for values
Mothership_duration_CUDOS[6:20,3] = NA
Mothership_duration_CUDOS[37:41,3] = NA
Mothership_duration_CUDOS[74:83,3] = NA
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-21),]
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-41),]
Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-61),]
Mothership_duration_CUDOS

ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Depression Severity During Partial Hospitalization")+
  labs(subtitle = "Broken up by Discharge Date")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
  scale_color_manual(values=c("skyblue","#0065A3",
                              "navy","blue"))+
  theme(panel.background=NULL)
```

## Depression Treatment Progress by Characteristics

#### Race
```{r}
Mothership_Long_dep <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
Mothership_Long_dep <- Mothership_Long_dep[order(Mothership_Long_dep$ID1),]

#Create a Time Variable
Mothership_Long_dep$TxDay <- NA
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day1_CUDOS"]<-1
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day2_CUDOS"]<-2
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day3_CUDOS"]<-3
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day4_CUDOS"]<-4
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day5_CUDOS"]<-5
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day6_CUDOS"]<-6
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day7_CUDOS"]<-7
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day8_CUDOS"]<-8
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day9_CUDOS"]<-9
Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day10_CUDOS"]<-10

#Overall race
Mothership_Mean_CUDOS_Race<-Mothership_Long_dep %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
# plot
ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","darkgreen",
                              "#0098DB","#0065A3","#A0AFA1"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("#209845","lightgrey","lightgrey",
                              "lightgrey","lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

ggplot(data=subset(Mothership_Mean_CUDOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Depression Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(10,40,by=5))+
  scale_color_manual(values=c("lightgrey","lightgrey","darkgreen",
                              "lightgrey","#0065A3","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

## GENDER IDENTITY
Create a New Data Set with an Average Depression Variable and Gender, then plot it
```{r}
#GENDER IDENTITY
#Create a New Data Set with an Average Depression Variable and Gender
Mothership_Mean_CUDOS_Gender<-Mothership_Long_dep %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

Mothership_Mean_CUDOS_Gender <-filter(Mothership_Mean_CUDOS_Gender,
                                      Gender_1 != "Unknown",
                                      Gender_1 != "Non-Binary",
                                      Gender_1 != "Other"
                                        )
#Create the Depression Line Graph by Gender
ggplot(data=subset(Mothership_Mean_CUDOS_Gender,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Gender During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(15,45,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```
#### TREATMENT TRACK
```{r}
#Create a New Data Set with an Average Depression Variable and Track
Mothership_Mean_CUDOS_Track<-Mothership_Long_dep %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

#Create the Depression Line Graph by Treatment Track
ggplot(data=subset(Mothership_Mean_CUDOS_Track,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUDOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Track During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#0065A3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

### EDUCATION
```{r}
#Create a New Data Set with an Average Depression Variable and Education
Mothership_Mean_CUDOS_Ed<-Mothership_Long_dep %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

#Create the Depression Line Graph by Education
ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.75)+
  geom_point(size=.75)+
  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#0065A3","darkgreen",
                              "#91A9F1","#7F8559"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

ggplot(data=subset(Mothership_Mean_CUDOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUDOS,group=Education_1,color=Education_1))+
  geom_line(size=.75)+
  geom_point(size=.75)+
  ggtitle("Depression Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,38,by=5))+
  scale_color_manual(values=c("#209845","lightgrey","lightgrey",
                              "#0098DB","lightgrey","lightgrey",
                              "lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

### TREATMENT YEAR
```{r}
#Create a New Data Set with an Average Depression Variable and Year
Mothership_Mean_CUDOS_Year<-Mothership_Long_dep %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))

str(Mothership_Long_dep$TxYear)

#Create the Depression Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("#209845","#3D4A3E","#A0AFA1",
                              "#0098DB","#91A9F1","darkgreen",
                              "#0065A3","#7F8559","#4B5D8E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

#Create the Depression Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUDOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUDOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Depression Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Depression Severity",limits=c(20,40,by=5))+
  scale_color_manual(values=c("lightgrey","lightgrey","lightgrey",
                              "lightgrey","lightgrey","lightgrey",
                              "#0065A3","lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

```

## Anxiety Treatment Progress Charts

```{r}
Mothership_Long <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]

#Create a Time Variable
Mothership_Long$TxDay <- NA
Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUXOS"]<-1
Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUXOS"]<-2
Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUXOS"]<-3
Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUXOS"]<-4
Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUXOS"]<-5
Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUXOS"]<-6
Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUXOS"]<-7
Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUXOS"]<-8
Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUXOS"]<-9
Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUXOS"]<-10
Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUXOS"]<-11
Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUXOS"]<-12
Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUXOS"]<-13
Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUXOS"]<-14
Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUXOS"]<-15
Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUXOS"]<-16
Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUXOS"]<-17
Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUXOS"]<-18
Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUXOS"]<-19
Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUXOS"]<-20

#Create a New Data Set with an Average Anxiety Variable
Mothership_Mean_CUXOS<-Mothership_Long %>%
  group_by(TxDay) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

# Mothership_Mean_CUXOS20<-Mothership_Long20 %>%
#   group_by(TxDay) %>%
#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

```

```{r}
#Plot the Anxiety Mean for Full Sample
ggplot(data=Mothership_Mean_CUXOS,aes(x=TxDay,y=mean_CUXOS))+
  geom_line(size=1,color="red")+
  geom_point(color="red")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,40,by=5))+
  theme(panel.background=NULL)

ggplot(Mothership, aes(Days_complete_1))+
  geom_density()+
  scale_x_continuous(limits=c(0,20,by=1)) +
  labs(
    title="Quantity of discharges Per Treatment Day")+
  theme_classic()

```

### plot means based upon duration group membership

```{r}
#plot Anxiety mean with each group

# New dataset for the treatment duration Anxiety plot
Mothership_Mean_CUXOS<-Mothership_Long %>%
  group_by(Duration,TxDay) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
#delete weird Na values and put NA for values
Mothership_duration_CUXOS[6:20,3] = NA
Mothership_duration_CUXOS[37:41,3] = NA
Mothership_duration_CUXOS[74:83,3] = NA
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-21),]
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-41),]
Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-61),]
Mothership_duration_CUXOS

ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration,color=Duration))+
  geom_line(size=1)+
  geom_point()+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
  scale_y_continuous(name="Anxiety Severity",limits=c(5,50,by=5))+
  scale_color_manual(values=c("#BB9D00","red",
                              "darkred","orange"))+
  theme(panel.background=NULL)+
  labs(subtitle = "Broken up by Duration of Treatment")
```

## Anxiety Treatment Progress by Characteristics

#### Race
```{r}

Mothership<-read.csv("~/Desktop/Coding/data/Mothership_Vis.csv")
Mothership<-mutate(Mothership,
      DC_status_1 = as.factor(DC_status_1),
      Education_1 = as.factor(Education_1),
      Gender_1 = as.factor(Gender_1),
      Relationship_1 = as.factor(Relationship_1),
      Sexuality_1 = as.factor(Sexuality_1),
      IPT_track_1 = as.factor(IPT_track_1),
      Race_1 = as.factor(Race_1),
      Education_1 = as.factor(Education_1),
      Duration = as.factor(Duration),
      )

Mothership$Intake_1<-ymd(Mothership$Intake_1,locale = "en_US.UTF-8")

Mothership_Long_anx <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
Mothership_Long_anx <- Mothership_Long_anx[order(Mothership_Long_anx$ID1),]

#Create a Time Variable
Mothership_Long_anx$TxDay <- NA
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day1_CUXOS"]<-1
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day2_CUXOS"]<-2
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day3_CUXOS"]<-3
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day4_CUXOS"]<-4
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day5_CUXOS"]<-5
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day6_CUXOS"]<-6
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day7_CUXOS"]<-7
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day8_CUXOS"]<-8
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day9_CUXOS"]<-9
Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day10_CUXOS"]<-10

#Overall race
Mothership_Mean_CUXOS_Race<-Mothership_Long_anx %>%
  group_by(TxDay,Race_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

Mothership_Mean_CUXOS_Race<-Mothership_Mean_CUXOS_Race[1:70,]
Mothership_Mean_CUXOS_Race
# plot
ggplot(data=subset(Mothership_Mean_CUXOS_Race,!is.na(Race_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Race_1,color=Race_1))+
  geom_line(size=1)+
  geom_point()+
  labs(title ="Anxiety Severity by Race During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(0,60,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E",
                              "gold3","#3E8300",
                              "#77B81C","darkorange2"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```
## GENDER IDENTITY
Create a New Data Set with an Average Anxiety Variable and Gender, then plot it
```{r}
#GENDER IDENTITY
#Create a New Data Set with an Average Anxiety Variable and Gender

Mothership_Mean_CUXOS_Gender<-Mothership_Long_anx %>%
  group_by(TxDay,Gender_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

Mothership_Mean_CUXOS_Gender <-filter(Mothership_Mean_CUXOS_Gender,
                                      Gender_1 != "Unknown",
                                      Gender_1 != "Non-Binary",
                                      Gender_1 != "Other"
                                        )

#Create the Anxiety Line Graph by Gender
ggplot(data=subset(Mothership_Mean_CUXOS_Gender,!is.na(Gender_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Gender_1,color=Gender_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Gender During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(15,45,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

#### TREATMENT TRACK
```{r}
#Create a New Data Set with an Average Anxiety Variable and Track
Mothership_Mean_CUXOS_Track<-Mothership_Long_anx %>%
  group_by(TxDay,IPT_track_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Treatment Track
ggplot(data=subset(Mothership_Mean_CUXOS_Track,!is.na(IPT_track_1)),
       aes(x=TxDay,y=mean_CUXOS,group=IPT_track_1,color=IPT_track_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Treatment Track During Partial Hospitalization")+
  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,46,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E","gold3"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```
### EDUCATION
```{r}
#Create a New Data Set with an Average Anxiety Variable and Education
Mothership_Mean_CUXOS_Ed<-Mothership_Long_anx %>%
  group_by(TxDay,Education_1) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Education
ggplot(data=subset(Mothership_Mean_CUXOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,50,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E",
                              "gold3","#3E8300",
                              "#77B81C","darkorange2",
                              "#798897","#FD85AE"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)

ggplot(data=subset(Mothership_Mean_CUXOS_Ed,!is.na(Education_1)),
       aes(x=TxDay,y=mean_CUXOS,group=Education_1,color=Education_1))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Education Level During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(20,50,by=5))+
  scale_color_manual(values=c("#DA2E2E","lightgrey","lightgrey",
                              "gold3","lightgrey","lightgrey",
                              "lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)
```

### TREATMENT YEAR
```{r}
#Create a New Data Set with an Average Anxiety Variable and Year
Mothership_Mean_CUXOS_Year<-Mothership_Long_anx %>%
  group_by(TxDay,TxYear) %>%
  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))

#Create the Anxiety Line Graph by Year
ggplot(data=subset(Mothership_Mean_CUXOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(15,50,by=5))+
  scale_color_manual(values=c("#DA2E2E","#57423E",
                              "gold3","#3E8300",
                              "#77B81C","darkorange2",
                              "firebrick4","#FD85AE","#798897"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())

ggplot(data=subset(Mothership_Mean_CUXOS_Year,!is.na(TxYear)),
       aes(x=TxDay,y=mean_CUXOS,group=as.factor(TxYear),color=as.factor(TxYear)))+
  geom_line(size=1)+
  geom_point()+
  ggtitle("Anxiety Severity by Treatment Year During Partial Hospitalization")+
    scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10))+
  scale_y_continuous(name="Anxiety Severity",limits=c(15,50,by=5))+
  scale_color_manual(values=c("lightgrey","lightgrey",
                              "lightgrey","lightgrey",
                              "lightgrey","lightgrey",
                              "firebrick4","lightgrey","lightgrey"))+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title=element_blank())
```

## RDQ stuff
```{r}

#Read in a New Data Set
Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))

#Make This Data Set Long Data
library(tidyr)
Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
                              factor_key = "T")
Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]

view(Mothership_Long_RDQ)

#Create a Time Variable
Mothership_Long_RDQ$PrePost <- NA
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_coping"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_pmh"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_func"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_wbs"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_sym"]<-"Pre"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_coping"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_pmh"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_func"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_wbs"]<-"Post"
Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_sym"]<-"Post"

#Create a New Data Set with an Average Depression Variable and Race
Mothership_Mean_RDQ<-Mothership_Long_RDQ %>%
  group_by(rm,PrePost) %>%
  summarise(RDQ=mean(RDQ,na.rm=TRUE))

#Add a Paired Variable to the New Data Set
Mothership_Mean_RDQ<-mutate(Mothership_Mean_RDQ,
                            paired=case_when(rm=="rdqPRE_coping"~"1",
                                             rm=="rdqPOST_coping"~"1",
                                             rm=="rdqPRE_pmh"~"2",
                                             rm=="rdqPOST_pmh"~"2",
                                             rm=="rdqPRE_func"~"3",
                                             rm=="rdqPOST_func"~"3",
                                             rm=="rdqPRE_wbs"~"4",
                                             rm=="rdqPOST_wbs"~"4",
                                             rm=="rdqPRE_sym"~"5",
                                             rm=="rdqPOST_sym"~"5"))

#Pre Post RDQ Plot
ggplot(data=Mothership_Mean_RDQ,
       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
           group=rm,color=paired,!is.na(PrePost)))+
  geom_point(size=2.5)+
  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5)+
  scale_x_discrete(name="Time Point")+
  scale_y_continuous(name="RDQ Subscore")+
  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  theme(legend.title = element_blank())+
  scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
                              "4"="#00BCA3","5"="#008570"),
                     labels=c("Coping Skills","Positive Mental Health",
                              "Functioning","Well-Being","Symptoms"))

```

### 2023-05-05 index.Rmd
Adding Website to repo

---
title: "Home"
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visualizing Mental Health Treatment.

This is a series of R Markdowns dipicting code used for a final project in a Design for Data Visualization course BMI 787.

---

## Background on project:

#### Partial hospitalization is a useful and effective treatment option for mental health

- Partial hospitalization refers to intensive mental health treatment that is considered a higher level of care than outpatient weekly therapy, but a lower level of care than inpatient treatment.
- Partial hospital programs generally involve daily therapy in different forms for about half a day, before patients return home to practice skills used in therapy in their lives.
-Empirical evidence shows that these programs are effective in reducing symptoms of common mental health conditions (Price, 2022; Murphy et al., 2022).

#### Partial hospitalization settings are understudied in the field of clinical psychology

- Despite their usefulness and relative ubiquity, relatively little research is conducted or reported in partial hospital program patients, leaving providers in this setting without a solid empirical basis from which to draw (Morgan et al., 2021).
- Therefore, the purpose of this project is to help fill this gap in research by visualizing demographic and clinical variables from a partial hospitalization program. 
    + Who attends this program?
    + Do patients improve during treatment? Which patients? On what measures?
    + At what point in treatment do patients improve?

#### Data for this project comes from a longstanding partial hospital program at a public hospital in New England

- Data comes from the Methods to Improve Diagnostic Assessment and Services (MIDAS) project – a longitudinal project that collects psychiatric patient data from outpatient and partial hospital settings.
- Patients at the partial hospital program attend multiple group therapies each day, as well as individual meeting with a therapist and psychiatrist. 
- Treatment is based in Acceptance and Commitment Therapy (ACT), an empirically-supported psychotherapy (Hayes et al., 2006).
---
The following visualizations are broken up into 4 sections:
1. [Sociodemographic and Treatment Characteristics]
2. [Diagnosis Visualizations]
3. [Treatment Progression Visualizations]
4. [Treatment Outcome Visualization]

---
### References

Hayes, S. C., Luoma, J. B., Bond, F. W., Masuda, A., & Lillis, J. (2006). Acceptance and commitment therapy: model, processes and outcomes. Behaviour research and therapy, 44(1), 1–25. https://doi.org/10.1016/j.brat.2005.06.006

Price, C. M. (2022). Participants’ experiences of group therapy in a partial hospitalization program: “It was impactful” ProQuest Information & Learning. In Dissertation Abstracts International Section A: Humanities and Social Sciences (Vol. 83, Issue 8–A).

Morgan, T. A., Dalrymple, K., D’Avanzato, C., Zimage, S., Balling, C., Ward, M., & Zimmerman, M. (2021). Conducting outcomes research in a clinical practice setting: 
The effectiveness and acceptability of acceptance and commitment therapy (ACT) in a partial hospital program. Behavior Therapy, 52(2), 272–285. https://doi-org.ezproxy.uky.edu/10.1016/j.beth.2020.08.004

Murphy, J. W., Corey, L. C., & Sturgeon, M. J. (2022). Evaluation of outcomes for military mental health partial hospitalization program. Military Psychology, 34(1), 91–97. https://doi-org.ezproxy.uky.edu/10.1080/08995605.2021.1971939

### 2023-05-05 index.Rmd
Added links

@@
 - Treatment is based in Acceptance and Commitment Therapy (ACT), an empirically-supported psychotherapy (Hayes et al., 2006).
----
-The following visualizations are broken up into 4 sections:
-1. [Sociodemographic and Treatment Characteristics]
-2. [Diagnosis Visualizations]
-3. [Treatment Progression Visualizations]
-4. [Treatment Outcome Visualization]
+
+#### The following visualizations are broken up into 4 sections:
+
+1. [Sociodemographic and Treatment Characteristics](https://troy-hubert.github.io/Hospital_Visualizations/Data_Import.html)
+2. [Diagnosis Visualizations](https://troy-hubert.github.io/Hospital_Visualizations/Diagnosis_Vis.html)
+3. [Treatment Progression Visualizations](https://troy-hubert.github.io/Hospital_Visualizations/Anxiety_Vis.html)
+4. [Treatment Outcome Visualization](https://troy-hubert.github.io/Hospital_Visualizations/Treatment_Outcomes.html)
 

### 2023-05-24 Diagnosis_Vis.Rmd
treatment duration boxplot

@@
   filter(Disorder_Type != "Mood")
+
+view(Mothership)
 ```
@@
 ```
+
+# Duration of treatment based upon disorder
+
+Source for [Data_Vis](https://twitter.com/nrennie35/status/1655911610618114052)
+```{r}
+library(tidyverse)
+#install.packages("showtext")
+library(showtext)
+# install.packages("camcorder")
+library(camcorder)
+# install.packages("ggtext")
+library(ggtext)
+library(glue)
+# install.packages("nrbrand")
+#require(nrBrand)
+    #what the fuck is this?
+# install.packages("ggmagnify")
+#library(ggmagnify)
+
+font_add_google("Fredericka the Great", "fred")
+showtext_auto()
+
+# gg_record(
+#   dir = file.path("~/Desktop/Coding/R working directory/plots/Recording"), # where to save the recording
+#   device = "png", # device to use to save images
+#   width = 8, # width of saved image
+#   height = 6.5, # height of saved image
+#   units = "in", # units for width and height
+#   dpi = 300 # dpi to use when saving image
+# )
+
+bg_col <- "#F9FBF2"
+# highlight_col <- "#FFAD05"
+# highlight_col <- "FF52825"
+highlight_col <- "#02d46e"
+outline_col <- "darkblue"
+dark_col <- "#333333"
+
+title = "Length of Treatment for Different Disorders"
+st = "The partial hospitalization program at the Rhode Island Hospital consists of a variety of treatment modalities for psychiatric disorders, but mainly consists of mindfulness based psychotherapies (e.g., ACT).
+Patients come for treatment during the day from 9-5 and do not stay overnight in the hospital.
+Patient discharge is agreed between psychiatrist, therapist, and patient."
+
+cap = "**Source:**: Methods to Improve Diagnostic Assessment and Services (MIDAS) project <br> "
+
+set.seed(12345)
+ggplot(
+  data = Mothership_Current_Long,
+  mapping = aes(
+    x = Days_complete_1,
+    y = Disorder_Type,
+    group = Disorder_Type)
+  )+
+  geom_jitter(
+    size = 0.6,
+    alpha = .5,
+    colour = highlight_col
+    )+
+  geom_boxplot(
+    outlier.shape = NA,
+    colour = outline_col,
+    fill = highlight_col,
+    alpha = 0.3) +
+  scale_x_continuous(
+   breaks = c(0, 15, 30, 45, 60),
+    limits = c(0.00, 60)
+  ) +
+  labs(
+    x = "Number of Days In Partial Hospitalization Program",
+    y = "DSM-5 Disorder Subtype",
+    title = title,
+    subtitle = st,
+    caption = cap
+    ) +
+  theme_minimal(
+    base_size = 30,
+    base_family = "Commissioner"
+    ) +
+  theme(
+    axis.ticks = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.major.x = element_line(
+       linewidth = 0.4,
+       colour = alpha(dark_col, 0.2),
+    ),
+    plot.background = element_rect(
+      fill = bg_col,
+      colour = bg_col
+    ),
+    panel.background = element_rect(
+      fill = bg_col,
+      colour = bg_col
+    ),
+    plot.title = element_text(
+      family = "Commissioner",
+        #this is the font
+      margin = margin(b = 20),
+      colour = dark_col,
+      size = 70
+    ),
+    plot.subtitle = element_textbox_simple(
+      lineheight = 0.55,
+      colour = dark_col,
+      family = "Commissioner",
+      hjust = 0,
+      margin = margin(b = 20),
+      halign = 0,
+      size = 28
+    ),
+    plot.caption = element_textbox_simple(
+      lineheight = 0.55,
+      colour = dark_col,
+      margin = margin(t = 10)
+    ),
+    axis.text = element_text(colour = dark_col),
+    axis.title = element_text(colour = dark_col),
+    legend.position = "none",
+    plot.margin = margin(15, 15, 10, 10)
+  )
+
+```

### 2023-05-24 Diagnosis_Vis.Rmd
Ridgeline plots!

@@
 
-cap = "**Source:**: Methods to Improve Diagnostic Assessment and Services (MIDAS) project <br> "
+cap = "**Source:** Methods to Improve Diagnostic Assessment and Services (MIDAS) project <br> "
 
@@
   theme_minimal(
-    base_size = 30,
+    base_size = 10,
     base_family = "Commissioner"
@@
         #this is the font
-      margin = margin(b = 20),
+      margin = margin(b = 10),
       colour = dark_col,
-      size = 70
+      size = 17
     ),
@@
       hjust = 0,
-      margin = margin(b = 20),
+      margin = margin(b = 10),
       halign = 0,
-      size = 28
+      size = 8
     ),
@@
 ```
+
+# CUXOS by Diagnosis
+
+## {.tabset}
+
+### Code
+```{r}
+# install.packages("ggridges")
+library(ggridges)
+library(ggplot2)
+library(forcats)
+```
+
+```{r}
+bg_col <- "#F9FBF2"
+dark_col <- "#333333"
+
+title = "Baseline Anxiety for Patients By Disorder Type"
+subtitle = "Upon entrence of the partial hospitalization program, scores of anxiety are reported from the _Clinically Useful Anxiety Outcome Scale_ (CUXOS).
+The CUXOS is a 20 item measure used to assess symptoms of anxiety; a cutoff score of 20 suggests a possitive screen for a probable anxiety disorder.
+Mean CUXOS scores are reported for each disorder type below (i.e., _the black line_)."
+cap = "**Symptom severity:** 0-10 (non-anxiety), 11-20 (minimal anxiety), 21-30 (mild anxiety), 31-40 (moderate anxiety), 41+ (severe anxiety) <br> <br> **Source:**: Methods to Improve Diagnostic Assessment and Services (MIDAS) project"
+
+p <- ggplot(Mothership_Current_Long, aes(
+  x = BL_CUXOS,
+  y = Disorder_Type,
+  fill = Disorder_Type)) +
+  # geom_density_ridges(alpha=0.6,
+  #                     rel_min_height = 0.05, 
+  #                     scale = 2)+
+   stat_density_ridges(quantile_lines = TRUE, alpha = 0.6, quantiles = 2, rel_min_height = 0.05, scale = 1.5) +
+   scale_x_continuous(
+   breaks = c(0, 20, 40, 60, 80),
+   limits = c(0, 80)) +
+  #theme_ridges() + 
+  labs(
+    x = "Baseline Score on CUXOS",
+    #y = "DSM-5 Disorder Subtype",
+    title = title,
+    subtitle = subtitle,
+    caption = cap) +
+   theme_minimal(
+    base_size = 10,
+    base_family = "Commissioner"
+    ) + 
+    theme(legend.position = "none",
+          axis.ticks = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.major.x = element_line(
+       linewidth = 0.4), 
+    axis.title.y= element_blank(),
+    plot.background = element_rect(
+      fill = bg_col,
+      colour = bg_col
+    ),    
+    panel.background = element_rect(
+      fill = bg_col,
+      colour = bg_col
+    ),
+    plot.title = element_text(
+      family = "Commissioner",
+        #this is the font
+      margin = margin(b = 5),
+      colour = dark_col,
+      size = 15
+    ),
+    plot.subtitle = element_textbox_simple(
+      lineheight = 0.55,
+      colour = dark_col,
+      family = "Commissioner",
+      hjust = 0,
+      margin = margin(b = 6),
+      halign = 0,
+      size = 8
+    ),
+     plot.caption = element_textbox_simple(
+      lineheight = 0.55,
+      colour = dark_col,
+      margin = margin(t = 10),
+      size = 7))
+```
+
+### Plot
+
+```{r}
+p
+```
+
+# Depression by disorder type
+
+## {.tabset}
+
+### Code
+```{r}
+bg_col <- "#F9FBF2"
+dark_col <- "#333333"
+
+title = "Baseline Depression for Patients By Disorder Type"
+subtitle = "Upon entrence of the partial hospitalization program, scores of anxiety are reported from the _Clinically Useful Depression Outcome Scale_ (CUDOS).
+The CUXOS is a 18 item measure used to assess different symptoms of depression; A cut off score of 20 suggests a positive screen for probable major depression.
+Mean CUDOS scores are reported for each disorder type below (i.e., _the black line_)."
+cap = "**Symptom severity:** 0-10 (non-depression), 11-20 (minimal depression), 21-30 (mild anxiety), 31-45 (moderate depression), 41+ (severe depression) <br><br> **Source:**: Methods to Improve Diagnostic Assessment and Services (MIDAS) project"
+
+q <- ggplot(Mothership_Current_Long, aes(
+  x = BL_CUDOS,
+  y = Disorder_Type,
+  fill = Disorder_Type)) +
+  # geom_density_ridges(alpha=0.6,
+  #                     rel_min_height = 0.05, 
+  #                     scale = 2)+
+   stat_density_ridges(quantile_lines = TRUE, alpha = 0.6, quantiles = 2, rel_min_height = 0.05, scale = 1.5) +
+   scale_x_continuous(
+   breaks = c(0, 20, 40, 60),
+   limits = c(0, 64)) +
+  #theme_ridges() + 
+  labs(
+    x = "Baseline Score on CUXOS",
+    #y = "DSM-5 Disorder Subtype",
+    title = title,
+    subtitle = subtitle,
+    caption = cap) +
+   theme_minimal(
+    base_size = 10,
+    base_family = "Commissioner"
+    ) + 
+    theme(legend.position = "none",
+          axis.ticks = element_blank(),
+    panel.grid.minor = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.major.x = element_line(
+       linewidth = 0.4), 
+    axis.title.y= element_blank(),
+    plot.background = element_rect(
+      fill = bg_col,
+      colour = bg_col
+    ),    
+    panel.background = element_rect(
+      fill = bg_col,
+      colour = bg_col
+    ),
+    plot.title = element_text(
+      family = "Commissioner",
+        #this is the font
+      margin = margin(b = 5),
+      colour = dark_col,
+      size = 15
+    ),
+    plot.subtitle = element_textbox_simple(
+      lineheight = 0.55,
+      colour = dark_col,
+      family = "Commissioner",
+      hjust = 0,
+      margin = margin(b = 5),
+      halign = 0,
+      size = 8
+    ),
+     plot.caption = element_textbox_simple(
+      lineheight = 0.55,
+      colour = dark_col,
+      margin = margin(t = 10),
+      size = 8))
+```
+
+### plot
+```{r}
+q
+```

### 2023-06-07 Diagnosis_Vis.Rmd
Made geom_count with less variables

@@
                       )))))))))),
+                    Disorder_treat = as.factor(
+                      ifelse(Anxiety_D == 1, "Anxiety",
+                      ifelse(BPD_P == 1, "BPD",
+                      ifelse(Trauma_D == 1, "Trauma",
+                      ifelse(Mood_D == 1, "Mood",
+                      NA
+                      ))))),
                   Anxiety_C =  as.factor(
@@
                     ifelse(BPD_P != 1 & BPD_C ==1,1,0)),
+                  No_Co = as.factor(
+                    ifelse(BPD_Co_C == 0 &
+                           OCD_Co_C == 0 &
+                           Somatic_C == 0 & 
+                           Eating_C == 0 &
+                           Psychotic_C == 0 &
+                           Trauma_C == 0 & 
+                           Substance_C == 0 &
+                           Mood_C == 0 &
+                           Anxiety_C == 0, 1,0)),
+                  Other_Co = as.factor(
+                    ifelse(OCD_Co_C == 1 & 
+                           Somatic_C == 0 & 
+                           Eating_C == 0 &
+                           Psychotic_C == 0,1,0)),
+
           #emotional disorders
@@
 
+Mothership_Diag_treat <- Mothership %>%
+  filter(!is.na(Disorder_treat))%>%
+  filter(!is.na(TxYear))
 # df with and without depression
@@
   ggplot(aes(x = Disorder_Type, y = Disorder_Present, color = Disorder_Type)) +
-  geom_count(alpha = .5)+
-  scale_size_area(max_size = 20) +
+  geom_count(aes(size = after_stat(prop),group = Disorder_Type),alpha = .5)+
+  scale_size_area(max_size = 25) +
   theme_classic() +
@@
   labs(title = "Number of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
+    subtitle = "Grouped into subtypes of DSM diagonsis",
+    y = "Co-Occuring Psychiatric Disorder",
+    x = "Primary Psychiatric Diagnosis") 
+```
+
+```{r}
+
+Mothership_current_Imp <- Mothership %>%
+  pivot_longer(
+    cols=c(Anxiety_C, Mood_C, Substance_C, Trauma_C, BPD_Co_C,Other_Co,No_Co),
+    names_to = 'Disorder_Present') %>%
+  filter(value != 0) %>%
+  select(!value)  %>%
+  filter(!is.na(Disorder_Present))%>%
+  filter(!is.na(Disorder_treat))
+
+tabs<-as.data.frame.matrix(xtabs(~Disorder_treat + Disorder_Present, data = Mothership_current_Imp))
+
+anx<-sum(tabs[1,])
+bpd<-sum(tabs[2,])
+mood<-sum(tabs[3,])
+trauma<-sum(tabs[4,])
+
+tabs[1,] <- (tabs[1,] /anx)*100
+tabs[2,] <- (tabs[2,] /bpd)*100
+tabs[3,] <- (tabs[3,] /mood)*100
+tabs[4,] <- (tabs[4,] /trauma)*100
+
+tabs
+```
+
+```{r}
+Mothership_current_Imp$Disorder_Present
+Mothership_current_Imp %>%
+  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
+  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .5)+
+  scale_size_area(max_size = 30) +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+    legend.position = "none") +
+  scale_y_discrete(labels=c("Trauma_C" = "Trauma", 
+                            "Substance_C" = "Substance Use",
+                            "Other_Co" = "Other",
+                            "No_Co" = "None",
+                            "Mood_C" = "Mood",
+                            "BPD_Co_C" = "BPD",
+                            "Anxiety_C" = "Anxiety")) +
+  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
     subtitle = "Grouped into subtypes of DSM diagonsis",
@@
   labs(
-    x = "Baseline Score on CUXOS",
+    x = "Baseline Score on CUDOS",
     #y = "DSM-5 Disorder Subtype",

### 2023-06-07 Diagnosis_Vis.Rmd
Got perportions of disorders correct.

@@
                 #OCD_P is for current OCD
+                OCD_P = as.factor(OCD_P),
           # Personality Disorders
                 #BPD_P is for current BPD
+                BPD_P = as.factor(BPD_P),
           # Substance Use Disorders
@@
 
-tabs<-as.data.frame.matrix(xtabs(~Disorder_treat + Disorder_Present, data = Mothership_current_Imp))
+tabs<-as.data.frame.matrix(xtabs(~ Disorder_Present + Disorder_treat, data = Mothership_current_Imp))
 
-anx<-sum(tabs[1,])
-bpd<-sum(tabs[2,])
-mood<-sum(tabs[3,])
-trauma<-sum(tabs[4,])
+anx<-summary(Mothership$Anxiety_D)[2]
+bpd<-summary(Mothership$BPD_P)[2]
+mood<-summary(Mothership$Mood_D)[2]
+trauma<-summary(Mothership$Trauma_D)[2]
 
-tabs[1,] <- (tabs[1,] /anx)*100
-tabs[2,] <- (tabs[2,] /bpd)*100
-tabs[3,] <- (tabs[3,] /mood)*100
-tabs[4,] <- (tabs[4,] /trauma)*100
+tabs[,1] <- (tabs[,1] / anx)*100
+tabs[,2] <- (tabs[,2] /bpd)*100
+tabs[,3] <- (tabs[,3] /mood)*100
+tabs[,4] <- (tabs[,4] /trauma)*100
 
@@
 Mothership_current_Imp$Disorder_Present
-Mothership_current_Imp %>%
+CO_OC<- Mothership_current_Imp %>%
   ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
@@
     x = "Primary Psychiatric Diagnosis")
+
+CO_OC
 ```

### 2023-06-08 Diagnosis_Vis.Rmd
Final co-occuring image

@@
 
+tabs[,5] <- c("Anxiety","BPD","Mood","None","Other","Substance","Trauma")
+colnames(tabs)[5] = "Disorder"
 tabs
@@
 ```{r}
-Mothership_current_Imp$Disorder_Present
-CO_OC<- Mothership_current_Imp %>%
+Mothership_current_Imp %>%
   ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
-  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .5)+
-  scale_size_area(max_size = 30) +
+  geom_point(aes(size = ..count..),stat = "bin2d")+
+  #scale_size_area(max_size = 30)+
+  scale_colour_manual(values = c( "#F4B393","#FC60A8","#7A28CB","#494368"))+
+  #scale_size_continuous(range = c(10, 30)) +
   theme_classic() +
@@
 
-CO_OC
+ "#CEEC97"
+ "#F4B393"
+ "#FC60A8"
+ "#7A28CB"
+ "#494368"
+
+```
+
+```{r}
+Mothership_current_Imp %>%
+  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
+  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .75)+
+ scale_size_area(max_size = 40)+
+  scale_colour_manual(values = c("#FE6CAA","#f7a174","#B1D4E0","#A06CFE"))+
+  #scale_size_continuous(range = c(10, 30)) +
+  theme_classic() +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+    legend.position = "none") +
+  scale_y_discrete(labels=c("Other_Co" = "Other",
+                            "No_Co" = "None",
+                            "BPD_Co_C" = "BPD",
+                            "Trauma_C" = "Trauma", 
+                            "Substance_C" = "Substance Use",
+                            "Mood_C" = "Mood",
+                            "Anxiety_C" = "Anxiety")) +
+  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
+    subtitle = "Grouped into subtypes of DSM diagonsis",
+    y = "Co-Occuring Psychiatric Disorder",
+    x = "Primary Psychiatric Diagnosis") 
 ```

### 2023-06-08 Diagnosis_Vis.Rmd
final final

@@
 
+While very pretty, this visualization is hard to interpret as.
+It may be easier to focus on the disorders most treated at the hospital (i.e., Anxiety, BPD, Mood, Trauma), and compare those across treatments.
+
+I first wanted to find out the percentages of patients with one diagnoses that also had another diagnosis. The following code:
+1. Creates a cross tabs of the number of people with each disorder / co occuring disorders
+2. Sums the number of people with a primary diagnosis of anxiety, mood, trauma, and BPD
+2. creates a value with the % of people that also have co-occuring disorders. 
 ```{r}
@@
 
-```{r}
-Mothership_current_Imp %>%
-  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
-  geom_point(aes(size = ..count..),stat = "bin2d")+
-  #scale_size_area(max_size = 30)+
-  scale_colour_manual(values = c( "#F4B393","#FC60A8","#7A28CB","#494368"))+
-  #scale_size_continuous(range = c(10, 30)) +
-  theme_classic() +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1),
-    legend.position = "none") +
-  scale_y_discrete(labels=c("Trauma_C" = "Trauma", 
-                            "Substance_C" = "Substance Use",
-                            "Other_Co" = "Other",
-                            "No_Co" = "None",
-                            "Mood_C" = "Mood",
-                            "BPD_Co_C" = "BPD",
-                            "Anxiety_C" = "Anxiety")) +
-  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
-    subtitle = "Grouped into subtypes of DSM diagonsis",
-    y = "Co-Occuring Psychiatric Disorder",
-    x = "Primary Psychiatric Diagnosis")
+### Plot the thing
 
- "#CEEC97"
- "#F4B393"
- "#FC60A8"
- "#7A28CB"
- "#494368"
-
-```
-
+Now that we have the percentages we will need to plot it. This figure plots the proportion of co-occuring disorders (y-axis) by the main diagnoses treated (x axis).
 ```{r}
@@
 ```
+
+While this figure is more clear, I wanted to add numbers to it. I popped this over to illustrator and made things a bit better. You can see the final figure below:
+
+![Note. Other = OCD, Eating Disorders, Somatic Disorders, and Psychotic Disorders; None = No other co-occuring disorder.](images/Co_occuring.png)
 

### 2023-06-18 Diagnosis_Vis.Rmd
Pre/Post Plots

@@
                                 Somatic_D == 1 & Psychotic_C ==1, 1, 0)))
+
+### Export as CSV
+write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag.csv")
 
@@
 Mean CUDOS scores are reported for each disorder type below (i.e., _the black line_)."
-cap = "**Symptom severity:** 0-10 (non-depression), 11-20 (minimal depression), 21-30 (mild anxiety), 31-45 (moderate depression), 41+ (severe depression) <br><br> **Source:**: Methods to Improve Diagnostic Assessment and Services (MIDAS) project"
+cap = "**Symptom severity:** 0-10 (non-depression), 11-20 (minimal depression), 21-30 (mild depression), 31-45 (moderate depression), 46+ (severe depression) <br><br> **Source:**: Methods to Improve Diagnostic Assessment and Services (MIDAS) project"
 

### 2023-06-18 Treatment_Outcomes.Rmd
Pre/Post Plots

@@
 #Data
-Mothership<-read.csv("~/Desktop/Coding/data/Mothership_Vis.csv")
+Mothership<-read.csv("~/Desktop/Coding/data/Mothership_Diag.csv")
 Mothership<-mutate(Mothership,
@@
 
+Mothership_Mean_RDQ
+
 #Pre Post RDQ Plot
@@
 ```{r, include=FALSE}
-# Depression symptoms df
-# CUDOS_Score <- select(Mothership,
-#                       Days_complete_1,Day1_CUDOS:Day40_CUDOS)
-# 
-# # Anxiety symptoms df
-# CUXOS_Score <- select(Mothership,
-#                       Days_complete_1,Day1_CUXOS:Day40_CUXOS)
+# 1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
+
+Mothership_post <- Mothership %>%
+  mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1),
+
+#2. Create pre_scores
+      CUXOS_pre = Day1_CUXOS,
+      CUDOX_pre = Day1_CUDOS
+      )
+
+#3. Then create df with CUDOS and CUXOS scores
+  # Depression
+
+    CUDOS_Score <- select(Mothership,
+                      Day1_CUDOS:Day40_CUDOS)
+    CUDOS_Score <- data.frame(CUDOS_Score)
+
+  # Anxiety
+    CUXOS_Score <- select(Mothership,
+                      Day1_CUXOS:Day40_CUXOS)
+    CUXOS_Score <- data.frame(CUDOS_Score)
+
+    view(Mothership)
+
+#4. Extract the valeues for each patient at their last day (length of stay), and create a CUDOS and CUXOS post score.
+
+Mothership <- Mothership %>%
+  mutate(
+    CUDOS_post = CUDOS_Score[cbind(seq_along(1:8667),CUDOS_Score$Days_complete_W)],
+    CUXOS_post = CUXOS_Score[cbind(seq_along(1:8667),CUDOS_Score$Days_complete_W)]
+  )
+
+#5. create new DF with Varaibles we want
+
+AnxDep_PrePost<- data.frame(cbind(Mothership$ID1,Mothership$Disorder_Type,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post)) %>%
+  filter(!is.na(Mothership$Disorder_Type))
+colnames(AnxDep_PrePost)[1:2] = c("ID1","Disorder_Type")
+
+#6. Create long data frame
+
+AnxDep_PrePost_Long <- AnxDep_PrePost %>% 
+  pivot_longer(
+    cols = CUDOS_pre:CUXOS_post, 
+    names_to = "Test",
+    values_to = "Score"
+  )
+AnxDep_PrePost_Long <-AnxDep_PrePost_Long %>%
+  mutate(
+    PrePost = ifelse(
+      Test == "CUDOS_pre", "Pre",
+      ifelse(Test == "CUXOS_pre" , "Pre", "Post"
+    )),
+    Score = as.integer(Score),
+    Test = as.factor(Test),
+    Test = as.factor(ifelse(Test == "CUDOS_pre",  "CUDOS",
+                     ifelse(Test == "CUDOS_post", "CUDOS", "CUXOS"
+                     ))))
+
+#7. Convert to data frame with means of values to be plotted
+AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
+  group_by(Test,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+#8. Pre Post CUDOS/CUXOS Plot
+ggplot(data=AnxDep_PrePost_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Test,color=Test))+
+  geom_point(size=2.5)+
+  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS/CUXOS Score")+
+  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank())
+ # scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
+                             # "4"="#00BCA3","5"="#008570"),
+                     #labels=c("Coping Skills","Positive Mental Health",
+                             # "Functioning","Well-Being","Symptoms"))
 
 ```
+Anxiety / Depression Pre_Post by disorder - line plot
+```{r}
+#1. Creaate new datasets with only anxiety / depresssion
 
-```{r, include=FALSE}
-#1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
-# 
-# 
-# Mothership_post <- Mothership %>%
-#   mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1))
-# 
-# 
-# 
-# Mothership <- Mothership %>%
-#   mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1))
-#          
-# 
-# Mothership$Day1_CUDOS
-# Mothership$Days_complete_1
-# Mothership$Days_complete_W
-# 
-# view(Mothership)
-# #2. Then create df with CUDOS and CUXOS scores
-#   # Depression
-# 
-#     CUDOS_Score <- select(Mothership,
-#                       Day1_CUDOS:Day40_CUDOS)
-# 
-#   # Anxiety
-#     CUXOS_Score <- select(Mothership,
-#                       Day1_CUXOS:Day40_CUXOS)
-# 
-# 
-# #3. Extract the valeues for each patient at their last day (length of stay)
-#     ##### Why is it not includeing NAs.
-#     
-# 
-# CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership$Days_complete_W),Mothership$Days_complete_W)]
-# CUXOS_post = CUXOS_Score[cbind(1:length(Mothership$Days_complete_W),Mothership$Days_complete_W)]
-# 
-# seq_along(Mothership$Days_complete_W)
-# Mothership$Days_complete_W
-# CUDOS_post
-# 
-# Mothership %>%
-#   mutate(Dep_post = CUDOS_post)
-# 
-# 
-# Mothership %>%
-#   mutate(Dep_post = CUDOS_post)
-# 
-# CUDOS_post
-# #4. Extract the value for their first day
-# CUDOS_pre<-Mothership$Day1_CUDOS
-# CUXOS_pre<-Mothership$Day1_CUXOS
-# AnxDep_PrePost_test <- data.frame(cbind(Mothership$ID1,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post))
-# AnxDep_PrePost_test
-# colnames(AnxDep_PrePost)[1] = "ID1"
-# 
-# AnxDep_PrePost_test
-# ## This is where I am Figure out where to go from here *******************
-# #5. Create long dataframe
-# 
-# AnxDep_PrePost_Lon <- gather(AnxDep_PrePost,ID1:CUXOS_post,factor_key = "T")
-# 
-# AnxDep_PrePost_Long <- pivot_longer(AnxDep_PrePost,ID1:CUXOS_post)
-# 
-# 
-# AnxDep_PrePost_Long
-# ?pivot_longer()
-# 
-# AnxDep_PrePost_Long <- AnxDep_PrePost_Long[order(AnxDep_PrePost_Long$ID1),]
-# 
-# Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
-#                               factor_key = "T")
-# Mothership_Long_RDQ
+ANX_PrePost<- AnxDep_PrePost_Long %>%
+  filter(Test == "CUXOS")
 
+DEP_PrePost<- AnxDep_PrePost_Long %>%
+  filter(Test == "CUDOS")
+
+#2. Create DF grouped buy disorder type
+ANX_PrePost_mean<-ANX_PrePost %>%
+  group_by(Disorder_Type,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+DEP_PrePost_mean<-DEP_PrePost %>%
+  group_by(Disorder_Type,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+#3. Plot em
+
+#### ANX
+ggplot(data=ANX_PrePost_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_point(size=2.5)+
+  geom_line(size=1)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUXOS Score")+
+  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUXOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank())
+
+#### DEP
+ggplot(data=DEP_PrePost_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_point(size=2.5)+
+  geom_line(size=1)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS Score")+
+  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
+       subtitle = "Self report depression was assessed using the CUDOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank())
 ```
 
-```{r, include=FALSE}
-# Mothership_Post <- Mothership %>%
-#   filter(!is.na(Days_complete_1)) %>%
-#   mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1)) 
-#   
-# 
-# Mothership_Post$Days_complete_W
-# 1:length(Mothership_Post$Days_complete_W)
-# 
-# # Depression
-# CUDOS_Score <- select(Mothership_Post, Day1_CUDOS:Day40_CUDOS)
-# 
-# CUDOS_Score
-# 
-# 1:length(Mothership_Post$Days_complete_W)
-# 
-# # Anxiety
-# CUXOS_Score <- select(Mothership_Post, Day1_CUXOS:Day40_CUXOS)
-# 
-# values <- cbind(seq_along(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W[1:8610])
-# values
-# CUDOS_post = CUDOS_Score[cbind(seq_along(Mothership_Post$Days_complete_W)[1:8610],Mothership_Post$Days_complete_W[1:8610])]
-# CUDOS_post
-# 
-# 
-# CUDOS_post = CUDOS_Score[cbind(1:length(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W)]
-# CUXOS_post = CUXOS_Score[cbind(1:length(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W)]
-# 
-# CUDOS_post
-# 
-# values <- cbind(1:length(Mothership_Post$Days_complete_W),Mothership_Post$Days_complete_W)
-# values
-# Mothership_Post<- Mothership_Post %>%
-#   mutate(Dep_post = CUDOS_post)
+Depression/ Anxiety pre/ post Dumbell plots
+```{r}
+Pre_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
+Plot_Text
+
+ggplot(data=Pre_ANX,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#aeb6bf",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUXOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
+  scale_y_reverse()+
+  # limits = c(10, 50))+
+  coord_flip() +
+  theme_classic()+
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+
+sum(as.factor(ANX_PrePost$Disorder_Type))
+
+Pre_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+ggplot(data=Pre_DEP,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#aeb6bf",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUDOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
+  scale_y_reverse()+
+  # limits = c(10, 50))+
+  coord_flip() +
+  theme_classic()+
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
 ```

### 2023-06-23 Treatment_Outcomes.Rmd
IT WORKED

@@
 knitr::opts_chunk$set(echo = TRUE, message=FALSE,warning = FALSE)
+getOption("max.print")
 # Libraries 
@@
 
-```{r, include=FALSE}
+# Pre and Post Scores
+
+## {.tabset}
+
+### Extract pre/post scores
+```{r}
 # 1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
@@
 Mothership_post <- Mothership %>%
-  mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40,Days_complete_1),
+  mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
 
@@
       CUXOS_pre = Day1_CUXOS,
-      CUDOX_pre = Day1_CUDOS
-      )
+      CUDOS_pre = Day1_CUDOS
+      ) %>%
+  filter(!is.na(Days_complete_W)) %>%
+  filter(!Days_complete_W == 0)
+
+sum(is.na(Mothership_post$Days_complete_W))
 
@@
 
-    CUDOS_Score <- select(Mothership,
+    CUDOS_Score <- select(Mothership_post,
                       Day1_CUDOS:Day40_CUDOS)
@@
   # Anxiety
-    CUXOS_Score <- select(Mothership,
-                      Day1_CUXOS:Day40_CUXOS)
-    CUXOS_Score <- data.frame(CUDOS_Score)
+    CUXOS_Score <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS)
+    CUXOS_Score <- data.frame(CUXOS_Score)
 
-    view(Mothership)
+length(Mothership_post$Days_complete_W)
 
@@
 
-Mothership <- Mothership %>%
+# Mothership_post2 <- Mothership_post %>%
+#   mutate(
+#     CUDOS_post = CUDOS_Score[cbind(seq_along(1:8610),CUDOS_Score$Days_complete_W)],
+#     CUXOS_post = CUXOS_Score[cbind(seq_along(1:8610),CUXOS_Score$Days_complete_W)]
+#   )
+
+# CUDOS_Score2=CUDOS_Score[,2:41]
+# CUXOS_Score2=CUXOS_Score[,2:41]
+
+Mothership_post <- Mothership_post %>%
   mutate(
-    CUDOS_post = CUDOS_Score[cbind(seq_along(1:8667),CUDOS_Score$Days_complete_W)],
-    CUXOS_post = CUXOS_Score[cbind(seq_along(1:8667),CUDOS_Score$Days_complete_W)]
+    CUDOS_post = CUDOS_Score[cbind(c(1:8367),Mothership_post$Days_complete_W)],
+    CUXOS_post = CUXOS_Score[cbind(c(1:8367),Mothership_post$Days_complete_W)]
   )
 
+####WTF
+```
+
+```{r}
 #5. create new DF with Varaibles we want
 
-AnxDep_PrePost<- data.frame(cbind(Mothership$ID1,Mothership$Disorder_Type,CUDOS_pre,CUDOS_post,CUXOS_pre,CUXOS_post)) %>%
-  filter(!is.na(Mothership$Disorder_Type))
-colnames(AnxDep_PrePost)[1:2] = c("ID1","Disorder_Type")
+AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
+                                  Mothership_post$Disorder_Type,
+                                  Mothership_post$CUDOS_pre,
+                                  Mothership_post$CUDOS_post,
+                                  Mothership_post$CUXOS_pre,
+                                  Mothership_post$CUXOS_post)) %>%
+  filter(!is.na(Mothership_post$Disorder_Type))
+
+colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post")
 
@@
 
-#8. Pre Post CUDOS/CUXOS Plot
+```
+
+### Overall Plot
+```{r}
+# Pre Post CUDOS/CUXOS Plot
 ggplot(data=AnxDep_PrePost_mean,
@@
   theme(legend.title = element_blank())
- # scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
-                             # "4"="#00BCA3","5"="#008570"),
-                     #labels=c("Coping Skills","Positive Mental Health",
-                             # "Functioning","Well-Being","Symptoms"))
 
 ```
-Anxiety / Depression Pre_Post by disorder - line plot
+
+### Line Plot By Disorder
 ```{r}
@@
 
-Depression/ Anxiety pre/ post Dumbell plots
+### Dumbell Plot by Disorder
 ```{r}
@@
 
-sum(as.factor(ANX_PrePost$Disorder_Type))
+#sum(as.factor(ANX_PrePost$Disorder_Type))
 
@@
        subtitle = "Self Report anxiety was assessed using the CUDOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
+       ylab = "Disorder Type")+
   scale_y_reverse()+

### 2023-06-23 index.Rmd
IT WORKED

@@
 
+#### Enjoy my favorite visualizations from the project!
+
+![](images/Treatment_duration.png)
+
+![Note. Other = OCD, Eating Disorders, Somatic Disorders, and Psychotic Disorders; None = No other co-occuring disorder.](images/Co_occuring.png)
+
+![Pre (red) and Post (green) scores of depression via self report for different DSM diagnoses.](images/Pre_post.png)
+
 ---

### 2023-06-25 Treatment_Outcomes.Rmd
Crack at while loop.

@@
       ) %>%
+
+#4. Filter out scores for people not in the program / don't have dataa
   filter(!is.na(Days_complete_W)) %>%
+    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
+  filter(!Days_complete_1 > 40) %>%
   filter(!Days_complete_W == 0)
 
-sum(is.na(Mothership_post$Days_complete_W))
+dim(Mothership_post)
 
-#3. Then create df with CUDOS and CUXOS scores
+#5. Then create df with CUDOS and CUXOS scores
   # Depression
@@
 
-length(Mothership_post$Days_complete_W)
-
-#4. Extract the valeues for each patient at their last day (length of stay), and create a CUDOS and CUXOS post score.
-
-# Mothership_post2 <- Mothership_post %>%
-#   mutate(
-#     CUDOS_post = CUDOS_Score[cbind(seq_along(1:8610),CUDOS_Score$Days_complete_W)],
-#     CUXOS_post = CUXOS_Score[cbind(seq_along(1:8610),CUXOS_Score$Days_complete_W)]
-#   )
-
-# CUDOS_Score2=CUDOS_Score[,2:41]
-# CUXOS_Score2=CUXOS_Score[,2:41]
+#6. Using incidences to extract values
 
@@
   mutate(
-    CUDOS_post = CUDOS_Score[cbind(c(1:8367),Mothership_post$Days_complete_W)],
-    CUXOS_post = CUXOS_Score[cbind(c(1:8367),Mothership_post$Days_complete_W)]
+    CUDOS_post = CUDOS_Score[cbind(c(1:8343),Mothership_post$Days_complete_W)],
+    CUXOS_post = CUXOS_Score[cbind(c(1:8343),Mothership_post$Days_complete_W)]
   )
 
-####WTF
-```
-
-```{r}
-#5. create new DF with Varaibles we want
+#7. create new DF with Varaibles we want
 
@@
 
-#6. Create long data frame
+#8. Create long data frame
 
@@
 
-#7. Convert to data frame with means of values to be plotted
+#9. Convert to data frame with means of values to be plotted
 AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
@@
 
+```
+
+```{r, include=FALSE}
+# Try to extract values using a while loop?
+
+for (i in 1:nrow(CUDOS_Score)){
+  while(is.na(CUDOS_Score[i,CUDOS_Score$Days_complete_W])){
+    x = Days_complete_W -1
+    post_days <- CUDOS_Score[i,(x)]
+  }
+}
 ```
@@
   summarise(Score=mean(Score,na.rm=TRUE))
-
-#3. Plot em
 

### 2023-09-13 Paper_stuff.Rmd
PAPER TIME

---
title: "Paper_stuff"
output: html_document
date: "2023-09-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries
library(tidyverse)
library(dplyr)
library(haven)
library(ggplot2)
library(tidyr)
```

# Import data

Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
View(df)
```

## Rename and Recode variables 
We can change the current variables to make them easier to interpret. 
```{r}
#recode varaibles
Mothership <- mutate(Mothership, 
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                          "1"="Complete",
                                          "2"="Nearly Complete",
                                          "3"="Insurance",
                                          "4"="Nonatteneance",
                                          "5"="Inappropriate",
                                          "6"="Inpatient",
                                          "7"="Withdrew",
                                          "8"="Dissatisfaction",
                                          "9"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                          "1"="<Grade 12",
                                          "2"="HS Diploma",
                                          "3"="GED",
                                          "4"="Some College",
                                          "5"="Associates Degree",
                                          "6"="Bachelors Degree",
                                          "7"="Some Grad School",
                                          "8"="Grad Degree"),
                     Gender_1 = as.factor(Gender_1),
                     Gender_1 = recode(Gender_1,
                                       "0"="Female",
                                       "1"="Male",
                                       "2"="Non-Binary",
                                       "3"="Other",
                                       "4"="Unknown"),
                     Relationship_1 = as.factor(Relationship_1),
                     Relationship_1 = recode(Relationship_1,
                                             "0"="Married",
                                             "1"="Cohabitating",
                                             "2"="Widowed",
                                             "3"="Separated",
                                             "4"="Divorced",
                                             "5"="Never Married"),
                     Sexuality_1 = as.factor(Sexuality_1),
                     Sexuality_1 = recode(Sexuality_1,
                                          "1"="Straight",
                                          "2"="Gay",
                                          "3"="Bisexual",
                                          "4"="Other"),
                     IPT_track_1 = as.factor(IPT_track_1),
                     IPT_track_1 = recode(IPT_track_1,
                                          "0"="General",
                                          "1"="Trauma",
                                          "2"="Young Adult",
                                          "3"="BPD"),
                     Race_1 = as.factor(Race_1),
                     Race_1 = recode(Race_1,
                                     "0"="White",
                                     "1"="Black",
                                     "2"="Hispanic",
                                     "3"="Asian",
                                     "4"="Portugese",
                                     "5"="Other"),
                     Education_1 = as.factor(Education_1),
                     Education_1 = recode(Education_1,
                                      "0"="<Grade 6", 
                                      "1"="Grades 7-12",
                                      "2"="HS Diploma", 
                                      "3"="GED",
                                      "4"="Some College",
                                      "5"="Associates Degree",
                                      "6"="Bachelors Degree",
                                      "7"="Some Grad School",
                                      "8"="Grad Degree"),
                     DC_status_1 = as.factor(DC_status_1),
                     DC_status_1 = recode(DC_status_1,
                                      "1"="Treatment Complete",
                                      "2"="Treatment Near Complete",
                                      "3"="Insurance Stopped",
                                      "4"="Nonattendence",
                                      "5"="Inapproparite Language",
                                      "6"="Transfered To Impatient",
                                      "7"="Withdrew for External factors",
                                      "8"="Withdrew (AMA)",
                                      "9"="Other",
                                      "10"="Other"),
                    DC_status_1 = as.factor(DC_status_1),
                    DC_status_1 = recode(DC_status_1,
                                      "1"="Inpatient",
                                      "2"="PHP",
                                      "3"="APS",
                                      "4"="Psychatrist",
                                      "5"="PCP",
                                      "6"="Another Physican",
                                      "7"="Therapist",
                                      "17"="Other"
                    ),

#Lets make some new variables 
      #Duration of treatment
                     Duration = as.factor(
                       ifelse(Days_complete_1>0 & Days_complete_1 <=5, "1",
                       ifelse(Days_complete_1>5 & Days_complete_1 <=10, "2",
                       ifelse(Days_complete_1>10 & Days_complete_1 <=15, "3",
                       ifelse(is.na(Days_complete_1), NA, "4"
                              ))))),
                    Duration = as.factor(recode(Duration,
                                      "1"="1-5",
                                      "2"="6-10",
                                      "3"="11-15",
                                      "4"="16+"
                                      )))

#Extract Year From Intake Date
#Convert to Date
library("lubridate")
Mothership$Intake_1<-ymd(Mothership$Intake_1)
Mothership$TxYear<-as.numeric(format(Mothership$Intake_1,"%Y"))
Mothership<-mutate(Mothership,
                   TxYear = as.factor(TxYear),
                   TxYear = recode(TxYear,
                                   "1582"="2014"))
```

## Export as CSV
```{r}
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_paper")
```

```{r}
Mothership<-Mothership %>%
  mutate(
          # Mood Disorders
                     Mood_D = as.factor(
                      ifelse(
                        MDD_P ==1 | Bipolar1_P == 1 | Bipolar2_P == 1 | Dysthymia_P == 1, 1, 0)),
          # Anxiety Disorders
                    Anxiety_D = as.factor(
                      ifelse(
                        GAD_P ==1 | Panic_P == 1 | PanicAgor_P == 1 | Agoraphobia_P == 1 |
                        Social_P == 1 | Specific_P == 1, 1, 0)),
          # Obsessive Compusive Disorders
                #OCD_P is for current OCD
                OCD_P = as.factor(OCD_P),
          # Personality Disorders
                #BPD_P is for current BPD
                BPD_P = as.factor(BPD_P),
          # Substance Use Disorders
                    Substance_D = as.factor(
                      ifelse(
                        Alcohol_P == 1 | Drug_P ==1, 1, 0)),
          # Trauma or stresor related disorders
                    Trauma_D = as.factor(
                      ifelse(PTSD_P == 1 | Adjustment_P ==1, 1,0)),
          # Psychotic Disorders
                    Psychotic_D = as.factor(
                      ifelse(
                        Schiz_P == 1 | Schizaff_P == 1,1,0)),
            # Eating Disorders
                    Eating_D = as.factor(
                      ifelse(
                        Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1, 1,0)),
            # Somatic Disroders
                    Somatic_D = as.factor(
                      ifelse(
                        Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1,
                        1,0)),
                    Other = as.factor(
                        ifelse(
                        Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1 |
                        Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1 | Schiz_P == 1 | 
                        Schizaff_P == 1 | Alcohol_P == 1 | Drug_P ==1 | OCD_P ==1,
                        1,0)),
                    Disorder_Type = as.factor(
                      ifelse(Anxiety_D == 1, "Anxiety",
                      ifelse(OCD_P == 1, "OCD",
                      ifelse(BPD_P == 1, "BPD",
                      ifelse(Substance_D == 1, "Substance Use",
                      ifelse(Trauma_D == 1, "Trauma",
                      ifelse(Mood_D == 1, "Mood",
                      ifelse(Psychotic_D == 1, "Psychotic", 
                      ifelse(Eating_D == 1, "Eating", 
                      ifelse(Somatic_D == 1, "Somatic", NA
                      )))))))))),
                    Disorder_treat = as.factor(
                      ifelse(Anxiety_D == 1, "Anxiety",
                      ifelse(BPD_P == 1, "BPD",
                      ifelse(Trauma_D == 1, "Trauma",
                      ifelse(Mood_D == 1, "Mood",
                      ifelse(OCD_P == 1, "Other",
                      ifelse(Substance_D == 1, "Other",
                      ifelse(Psychotic_D == 1, "Other", 
                      ifelse(Eating_D == 1, "Other", NA
                      ))))))))),
                  Anxiety_C =  as.factor(
                    ifelse( GAD_P !=1 & GAD_C ==1 | 
                        Panic_P != 1 & Panic_C == 1 | 
                        PanicAgor_P != 1 & PanicAgor_C == 1 | 
                        Agoraphobia_P != 1 & Agoraphobia_C == 1 |
                        Social_P != 1 & Social_C == 1 | 
                        Specific_P != 1 & Specific_C == 1, 1, 0)),
                  Mood_C =  as.factor(
                    ifelse( MDD_P != 1 & MDD_C == 1 |
                        Bipolar1_P != 1 & Bipolar1_C == 1 | 
                        Bipolar2_P != 1 &  Bipolar2_C == 1 | 
                        Dysthymia_P != 1 & Dysthymia_C == 1 , 1, 0)),
                  Substance_C = as.factor(
                    ifelse(Alcohol_P != 1 & Alcohol_C == 1 | 
                        Drug_P != 1 & Drug_C ==1, 1, 0)),
                  Trauma_C = as.factor(
                    ifelse(PTSD_P != 1 & PTSD_C == 1 | 
                        Adjustment_P != 1 & Adjustment_C ==1, 1,0)),
                  Psychotic_C = as.factor(
                    ifelse(Schiz_P != 1 & Schiz_C == 1 | 
                        Schizaff_P != 1 & Schizaff_C == 1,1,0)),
                  Eating_C = as.factor(
                    ifelse(Anorex_P != 1 & Anorex_C == 1 | 
                        Bulim_P != 1 & Bulim_C == 1 | 
                        Binge_P != 1 & Binge_C == 1, 1,0)),
                  Somatic_C = as.factor(
                    ifelse(Somat_P != 1 & Somat_C == 1 | 
                        UndiffSoma_P != 1 & UndiffSoma_C == 1 | 
                        Hypochondriasis_P != 1 &  Hypochondriasis_C == 1, 1,0)),
                  OCD_Co_C = as.factor(
                    ifelse(OCD_P != 1 & OCD_C == 1,1,0)),
                  BPD_Co_C = as.factor(
                    ifelse(BPD_P != 1 & BPD_C ==1,1,0)),
                  No_Co = as.factor(
                    ifelse(BPD_Co_C == 0 &
                           OCD_Co_C == 0 &
                           Somatic_C == 0 & 
                           Eating_C == 0 &
                           Psychotic_C == 0 &
                           Trauma_C == 0 & 
                           Substance_C == 0 &
                           Mood_C == 0 &
                           Anxiety_C == 0, 1,0)),
                  Other_Co = as.factor(
                    ifelse(OCD_Co_C == 1 & 
                           Somatic_C == 1 & 
                           Eating_C == 1 &
                           Psychotic_C == 1,1,0)),

          #emotional disorders
                  Emotional_dis = as.factor(
                    ifelse(Anxiety_D == 1 | OCD_P == 1 | Trauma_D == 1 |
                           Mood_D == 1, "Emotional Disorder", "Other Disorder")),

          # co occuring disorders
                  Co_Anx = as.factor(
                        ifelse(Anxiety_C == 1 & Mood_D == 1 |
                                Anxiety_C == 1 & OCD_P == 1 |
                                Anxiety_C == 1 & BPD_P == 1 |
                                Anxiety_C == 1 & Substance_D == 1 |
                                Anxiety_C == 1 & Trauma_D == 1 |
                                Anxiety_C == 1 & Eating_D ==1 |
                                Anxiety_C == 1 & Psychotic_D ==1 |
                                Anxiety_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_Mood = as.factor(
                        ifelse(Mood_C == 1 & Anxiety_D == 1 |
                                Mood_C == 1 & OCD_P == 1 |
                                Mood_C == 1 & BPD_P == 1 |
                                Mood_C == 1 & Substance_D == 1 |
                                Mood_C == 1 & Trauma_D == 1 |
                                Mood_C == 1 & Eating_D ==1 |
                                Mood_C == 1 & Psychotic_D ==1 |
                                Mood_C == 1 & Somatic_D==1 , 1, 0)),
                  Co_OCD = as.factor(
                        ifelse(OCD_C == 1 & Anxiety_D == 1 |
                                OCD_C == 1 & Mood_D == 1 |
                                OCD_C == 1 & BPD_P== 1 |
                                OCD_C == 1 & Substance_D == 1 |
                                OCD_C == 1 & Trauma_D == 1 |
                                OCD_C == 1 & Eating_D ==1 |
                                OCD_C == 1 & Psychotic_D ==1 |
                                OCD_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_BPD = as.factor(
                        ifelse(BPD_C == 1 & Anxiety_D == 1 |
                                BPD_C == 1 & Mood_D == 1 |
                                BPD_C == 1 & OCD_P== 1 |
                                BPD_C == 1 & Substance_D == 1 |
                                BPD_C == 1 & Trauma_D == 1 |
                                BPD_C == 1 & Eating_D ==1 |
                                BPD_C == 1 & Psychotic_D ==1 |
                                BPD_C == 1 & Somatic_D ==1 , 1, 0)),
                  Co_Psychotic = as.factor(
                       ifelse(Psychotic_C == 1 & Mood_D == 1 |
                                Psychotic_C == 1 & OCD_P == 1 |
                                Psychotic_C == 1 & BPD_P == 1 |
                                Psychotic_C == 1 & Substance_D == 1 |
                                Psychotic_C == 1 & Trauma_D == 1 |
                                Psychotic_C == 1 & Eating_D ==1 |
                                Psychotic_C == 1 & Anxiety_D ==1 |
                                Psychotic_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_Eating = as.factor(
                      ifelse(Eating_C == 1 & Mood_D == 1 |
                                Eating_C == 1 & OCD_P == 1 |
                                Eating_C == 1 & BPD_P == 1 |
                                Eating_C == 1 & Substance_D == 1 |
                                Eating_C == 1 & Trauma_D == 1 |
                                Eating_C == 1 & Psychotic_D ==1 |
                                Eating_C == 1 & Anxiety_D ==1 |
                                Eating_C == 1 & Somatic_D ==1, 1, 0)),
                  Co_Somatic =  as.factor(
                       ifelse(Somatic_C == 1 & Mood_D == 1 |
                                Somatic_C == 1 & OCD_P == 1 |
                                Somatic_C == 1 & BPD_P == 1 |
                                Somatic_C == 1 & Substance_D == 1 |
                                Somatic_C == 1 & Trauma_D == 1 |
                                Somatic_C == 1 & Eating_D ==1 |
                                Somatic_C == 1 & Anxiety_D ==1 |
                                Somatic_C == 1 & Substance_D ==1 |
                                Somatic_C == 1 & Psychotic_D ==1, 1, 0)),
                  Co_Substance = as.factor(
                      ifelse(Substance_C == 1 & Mood_D == 1 |
                                Substance_C == 1 & OCD_P == 1 |
                                Substance_C == 1 & BPD_P == 1 |
                                Substance_C == 1 & Substance_D == 1 |
                                Substance_C == 1 & Trauma_D == 1 |
                                Substance_C == 1 & Eating_D ==1 |
                                Substance_C == 1 & Anxiety_D ==1 |
                                Substance_C == 1 & Somatic_D ==1 |
                                Substance_C == 1 & Psychotic_D ==1, 1, 0)),
                 Co_Trauma = as.factor(
                    ifelse(Trauma_C == 1 & Mood_D == 1 |
                                Trauma_C == 1 & OCD_P == 1 |
                                Trauma_C == 1 & BPD_P == 1 |
                                Trauma_C == 1 & Substance_D == 1 |
                                Trauma_C == 1 & Eating_D ==1 |
                                Trauma_C == 1 & Anxiety_D ==1 |
                                Trauma_C == 1 & Somatic_D ==1 |
                                Trauma_C == 1 & Psychotic_D ==1, 1, 0))
  )

### Export as CSV
write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag.csv")

##### df for plots

# df without NAs in date and disorder type
Mothership_Diag <- Mothership %>%
  filter(!is.na(Disorder_Type))%>%
  filter(!is.na(TxYear))

Mothership_Diag_treat <- Mothership %>%
  filter(!is.na(Disorder_treat),
         !is.na(TxYear),
         !is.na(Duration))

# df with and without depression
No_depressy <- Mothership_Diag %>%
  filter(Disorder_Type != "Mood")
```

What Doug Wants

# Results
### The overall breakdown of patients’ demographics and diagnoses.
###	The trajectories of depression and anxiety for all patients (both numerical – pre/post scores, overall slope, and visual – graphs). Numerical results are in text, visual results presented to supplement.
- Broken down by treatment duration, treatment track, most common primary diagnoses.
###	The pre-post scores (numerical and visual) for RDQ subscales.
###	Reasons for discharge (numerical and visual).

# Visualizations
### Table – Demographics
### Table – Diagnoses
```{r}
#Demographics Table
Demo_tab_df <- Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1),

        )

Demo_tab<-data.frame(table1::table1(~Age_1+Education_1+Race_1+Gender_1+Relationship_1, data=Demo_tab_df))
colnames(Demo_tab) <- c("Variable","Total Sample")
Demo_tab

#Disorder Table
Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_Diag_treat))
colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
Dis_tab
```
### Visualization – most common diagnoses.
```{r}
#frequency

ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
  geom_bar()+
  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
        legend.position = "none")+
  xlab("Psychiatric Disorder Subtype")+
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,4300))+
  coord_flip()
```

```{r}
# Visualization of percent

Mothership_current_Imp <- Mothership_Diag_treat %>%
  pivot_longer(
    cols=c("Co_Anx","Co_Mood","Co_OCD","CO_BPD","CO_Psychotic","CO_Eating","CO_Somatic", "CO_Substance","CO_Trauma", "No_Co"),
    names_to = 'Disorder_Present') %>%
  filter(value != 0) %>%
  select(!value)  %>%
  filter(!is.na(Disorder_Present))%>%
  filter(!is.na(Disorder_treat))

co_dis_tab <- Mothership_Diag_treat |>
  pivot_longer(
    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "CO_Substance","Co_Trauma", "No_Co"),
    names_to = 'Co Occuring',
    values_to = "Number"
  ) |>
  select(Disorder_treat, `Co Occuring`, Number) |>
  filter(Number != 0,
         !is.na(`Co Occuring`),
         !is.na(Disorder_treat))

tabs<-as.data.frame.matrix(xtabs(~ Disorder_Present + Disorder_treat, data = Mothership_current_Imp))

anx<-summary(Mothership_Diag_treat$Anxiety_D)[2]
bpd<-summary(Mothership_Diag_treat$BPD_P)[2]
mood<-summary(Mothership_Diag_treat$Mood_D)[2]
trauma<-summary(Mothership_Diag_treat$Trauma_D)[2]
other<-summary(Mothership_Diag_treat$Other)[2]

tabs[,1] <- (tabs[,1] / anx)*100
tabs[,2] <- (tabs[,2] /bpd)*100
tabs[,3] <- (tabs[,3] /mood)*100
tabs[,4] <- (tabs[,4] /other)*100
tabs[,5] <- (tabs[,5] /trauma)*100
tabs[,6] <- c("Anxiety","BPD","Eating","Mood","OCD","Psychotic","Somatic", "Substance","Trauma", "None")
colnames(tabs)[6] = "Disorder"
tabs

CODis_tab<-data.frame(table1::table1(~`Co Occuring` | Disorder_treat, data = co_dis_tab))
CODis_tab

p <- Mothership_current_Imp %>%
  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .75)+
 scale_size_area(max_size = 30)+
  scale_colour_manual(values = c("#FE6CAA","#f7a174","#B1D4E0","#A06CFE","red"))+
  #scale_size_continuous(range = c(10, 30)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Other_Co" = "Other",
                            "No_Co" = "None",
                            "BPD_Co_C" = "BPD",
                            "Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Mood_C" = "Mood",
                            "Anxiety_C" = "Anxiety")) +
  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis")

```

•	Visualizations – CUDOS and CUXOS trajectories by treatment duration, treatment track, most common diagnoses. 
•	Visualization – RDQ pre and post change.
•	Table or Visualization – Reasons for discharge results.

# Sociodemographic Visualizations

## {.tabset}

### Education Status
```{r}
ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
  geom_bar(color = "black",fill="darkred")+
  ggtitle("Frequency of Education Level") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Education Level")+
  theme(panel.grid.major.y = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,3000))
```

### Race
```{r}
ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
  geom_bar(color = "black",fill="darkblue")+
  ggtitle("Frequency of Race/Ethnicity") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Race")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

### Gender
```{r}
ggplot(data = subset(Mothership, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
  geom_bar(color = "black",fill="darkorange")+
  ggtitle("Frequency of Gender") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Gender")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  coord_flip()+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

# Pie Chart For Education Status 
We wanted to learn how to make a pie chart in R so here is one!
```{r}
#Create Table and Data Frame
Education<-table(Mothership$Education_1)
Education_df<-as.data.frame(Education)
Education_df

#Rename Columns
colnames(Education_df)[1]="Category"
colnames(Education_df)[2]="Frequency"

Education_df$Category=recode(Education_df$Category,
                             "0"="<Grade 6", 
                             "1"="Grades 7-12",
                             "2"="HS Diploma", 
                             "3"="GED",
                             "4"="Some College",
                             "5"="Associates Degree",
                             "6"="Bachelors Degree",
                             "7"="Some Grad School",
                             "8"="Grad Degree")

ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
  geom_bar(stat="Identity",width=1,color="white")+
  ggtitle("Education Level of Patients") +
  scale_fill_discrete(name = "Education") +
  coord_polar("y",start=0)+
  theme_void()
```

# Treatment Related Visualizations

## {.tabset}

### Discharge Status
```{r}
### Bar Chart for Discharge Status ###

ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
  geom_bar(color = "black",fill="darkgreen")+
  ggtitle("Frequency of Treatment Discharge Status") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Discharge Status") +
  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6000)) +
  coord_flip()
```

### Treatment Track
```{r}
### Treatment Track ###

ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
  geom_bar(color = "black",fill="skyblue")+
  ggtitle("Frequency of Treatment Type") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Type")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))
```

### Treatment Year
```{r}
### Treatment Year ###

ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
  geom_bar(color = "black",fill="#9350C7")+
  ggtitle("Frequency of Patients per Year") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Year")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,1500))
```

### Duration of Treatment
```{r}
### Duration of Treatment ###
ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
  geom_bar(color = "black",fill="lightgreen")+
  ggtitle("Frequency of Patients per Duration of Treatment") +
  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
  xlab("Treatment Duration")+
  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
  theme(panel.background=NULL)+
  scale_y_continuous(name = "Frequency",limits=c(0,6500))

```

### 2023-09-13 Treatment_Outcomes.Rmd
PAPER TIME

@@
        caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
-  scale_y_reverse()+
-  # limits = c(10, 50))+
+  scale_y_reverse(limits = c(45,15)) +
   coord_flip() +
@@
        ylab = "Disorder Type")+
-  scale_y_reverse()+
-  # limits = c(10, 50))+
+  scale_y_reverse(limits = c(45,15)) +
   coord_flip() +

### 2023-09-14 Depression_Vis.Rmd
Adding anxiety / depression by duration

@@
 ```{r}
-Mothership_Long <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
-Mothership_Long <- Mothership_Long[order(Mothership_Long$ID1),]
+Mothership_Long_dep <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
+Mothership_Long_dep <- Mothership_Long_dep[order(Mothership_Long_dep$ID1),]
 
 #Create a Time Variable
-Mothership_Long$TxDay <- NA
-Mothership_Long$TxDay[Mothership_Long$rm=="Day1_CUDOS"]<-1
-Mothership_Long$TxDay[Mothership_Long$rm=="Day2_CUDOS"]<-2
-Mothership_Long$TxDay[Mothership_Long$rm=="Day3_CUDOS"]<-3
-Mothership_Long$TxDay[Mothership_Long$rm=="Day4_CUDOS"]<-4
-Mothership_Long$TxDay[Mothership_Long$rm=="Day5_CUDOS"]<-5
-Mothership_Long$TxDay[Mothership_Long$rm=="Day6_CUDOS"]<-6
-Mothership_Long$TxDay[Mothership_Long$rm=="Day7_CUDOS"]<-7
-Mothership_Long$TxDay[Mothership_Long$rm=="Day8_CUDOS"]<-8
-Mothership_Long$TxDay[Mothership_Long$rm=="Day9_CUDOS"]<-9
-Mothership_Long$TxDay[Mothership_Long$rm=="Day10_CUDOS"]<-10
-Mothership_Long$TxDay[Mothership_Long$rm=="Day11_CUDOS"]<-11
-Mothership_Long$TxDay[Mothership_Long$rm=="Day12_CUDOS"]<-12
-Mothership_Long$TxDay[Mothership_Long$rm=="Day13_CUDOS"]<-13
-Mothership_Long$TxDay[Mothership_Long$rm=="Day14_CUDOS"]<-14
-Mothership_Long$TxDay[Mothership_Long$rm=="Day15_CUDOS"]<-15
-Mothership_Long$TxDay[Mothership_Long$rm=="Day16_CUDOS"]<-16
-Mothership_Long$TxDay[Mothership_Long$rm=="Day17_CUDOS"]<-17
-Mothership_Long$TxDay[Mothership_Long$rm=="Day18_CUDOS"]<-18
-Mothership_Long$TxDay[Mothership_Long$rm=="Day19_CUDOS"]<-19
-Mothership_Long$TxDay[Mothership_Long$rm=="Day20_CUDOS"]<-20
+Mothership_Long_dep$TxDay <- NA
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day1_CUDOS"]<-1
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day2_CUDOS"]<-2
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day3_CUDOS"]<-3
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day4_CUDOS"]<-4
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day5_CUDOS"]<-5
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day6_CUDOS"]<-6
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day7_CUDOS"]<-7
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day8_CUDOS"]<-8
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day9_CUDOS"]<-9
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day10_CUDOS"]<-10
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day11_CUDOS"]<-11
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day12_CUDOS"]<-12
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day13_CUDOS"]<-13
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day14_CUDOS"]<-14
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day15_CUDOS"]<-15
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day16_CUDOS"]<-16
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day17_CUDOS"]<-17
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day18_CUDOS"]<-18
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day19_CUDOS"]<-19
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day20_CUDOS"]<-20
 
 #Create a New Data Set with an Average Anxiety Variable
-Mothership_Mean_CUDOS<-Mothership_Long %>%
+Mothership_Mean_CUDOS<-Mothership_Long_dep %>%
   group_by(TxDay) %>%

### 2023-09-14 Paper_stuff.Rmd
Adding anxiety / depression by duration

@@
   coord_flip()
+
+ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
+  geom_bar()+
+  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+        legend.position = "none")+
+  xlab("Psychiatric Disorder Subtype")+
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,2000))+
+  coord_flip()+
+  facet_wrap(~Duration)
 ```
@@
   pivot_longer(
-    cols=c("Co_Anx","Co_Mood","Co_OCD","CO_BPD","CO_Psychotic","CO_Eating","CO_Somatic", "CO_Substance","CO_Trauma", "No_Co"),
+    cols=c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
     names_to = 'Disorder_Present') %>%
@@
   pivot_longer(
-    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "CO_Substance","Co_Trauma", "No_Co"),
+    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
     names_to = 'Co Occuring',
@@
  scale_size_area(max_size = 30)+
-  scale_colour_manual(values = c("#FE6CAA","#f7a174","#B1D4E0","#A06CFE","red"))+
+  scale_colour_manual(values = c("#ffa600","#ff6361","#bc5090","#58508d","#003f5c"))+
   #scale_size_continuous(range = c(10, 30)) +
@@
 
+p
 ```
@@
 •	Visualizations – CUDOS and CUXOS trajectories by treatment duration, treatment track, most common diagnoses.
+
+### plot means based upon duration group membership 
 •	Visualization – RDQ pre and post change.

### 2023-09-14 Paper_stuff.Rmd
Duration categories aren't working as they are suppsoed to.

@@
 
-ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
-  geom_bar()+
-  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1),
-        legend.position = "none")+
-  xlab("Psychiatric Disorder Subtype")+
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,2000))+
-  coord_flip()+
-  facet_wrap(~Duration)
+# ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
+#   geom_bar()+
+#   ggtitle("Frequency of Psychiatric Disorder Subtypes") +
+#   theme(axis.text.x = element_text(angle = 45,hjust = 1),
+#         legend.position = "none")+
+#   xlab("Psychiatric Disorder Subtype")+
+#   theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+#   theme(panel.background=NULL)+
+#   scale_y_continuous(name = "Frequency",limits=c(0,2000))+
+#   coord_flip()+
+#   facet_wrap(~Duration)
 ```
@@
 ### plot means based upon duration group membership
+
 •	Visualization – RDQ pre and post change.

### 2023-09-16 Paper_stuff.Rmd
Trying to figure out treatment responders

@@
                     DC_status_1 = recode(DC_status_1,
-                                      "1"="Inpatient",
-                                      "2"="PHP",
-                                      "3"="APS",
-                                      "4"="Psychatrist",
-                                      "5"="PCP",
-                                      "6"="Another Physican",
-                                      "7"="Therapist",
-                                      "17"="Other"
+                                      "1" ="Inpatient",
+                                      "2" ="PHP",
+                                      "3" ="APS",
+                                      "4" ="Psychatrist",
+                                      "5" ="PCP",
+                                      "6" ="Another Physican",
+                                      "7" ="Therapist",
+                                      "17"="Other",
+                                      "11"="Other",
+                                      "0" ="Other"
                     ),
@@
                               ))))),
-                    Duration = as.factor(recode(Duration,
+                    Duration_lab = as.factor(recode(Duration,
                                       "1"="1-5",
@@
                                       "4"="16+"
+                                      )),
+                    Duration_10 = as.factor(
+                      ifelse(Duration == 1 | Duration == 2, "1",
+                      ifelse(Duration == 3 | Duration == 4, "2", NA)
                       )))
@@
 
+Disorder_varaibles
 ```{r}
@@
 
-### Export as CSV
-write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag.csv")
-
 ##### df for plots
@@
 # df without NAs in date and disorder type
-Mothership_Diag <- Mothership %>%
-  filter(!is.na(Disorder_Type))%>%
+Mothership_Diag <- Mothership |>
+  filter(!is.na(Disorder_Type)) |>
   filter(!is.na(TxYear))
 
-Mothership_Diag_treat <- Mothership %>%
+Mothership_Diag_treat <- Mothership |>
   filter(!is.na(Disorder_treat),
@@
 
+Main_Treat <- Mothership |>
+
+### Export as CSV
+write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag.csv")
+
 # df with and without depression
@@
   filter(Disorder_Type != "Mood")
+```
+
+Pre_Post
+```{r}
+Mothership_post <- Mothership |>
+  #1. Filter out scores for people not in the program / don't have dataa
+  filter(!is.na(Days_complete_1)) |>
+    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
+  filter(!Days_complete_1 > 40,
+         !Days_complete_1 == 0,
+         !is.na(BL_CUXOS),
+         !is.na(SUManx_DC),
+         BL_CUXOS > 1,
+         SUManx_DC > 0,
+         !is.na(BL_CUDOS),
+         !is.na(SUMdep_DC),
+         BL_CUDOS > 1,
+         SUMdep_DC > 0
+         ) |>
+  mutate(
+    Delta_Anx_DC = BL_CUXOS - SUManx_DC,
+    Delta_Dep_DC = BL_CUDOS - SUMdep_DC,
+    Percent_anx_change = SUManx_DC - BL_CUXOS/BL_CUXOS,
+    Percent_Dep_Dchange = SUMdep_DC - BL_CUDOS/BL_CUDOS,
+    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
+    Anx_Responder = as.factor(
+      ifelse(BL_CUXOS > 10 &(Delta_Anx_DC/BL_CUXOS) <= .5 & (Delta_Anx_DC/BL_CUXOS) >= 0, "Anx Responder",
+      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 0, "Anx Worse", 
+      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS > .5,  "Unresponders", "Low BL Anx"      
+      )))),
+    Dep_Responder = as.factor(
+      ifelse(BL_CUDOS > 10 & (Delta_Dep_DC/BL_CUDOS) <= .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Dep Responder",
+      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 0, "Dep Worse", 
+      ifelse(BL_CUDOS > 10 & Delta_Anx_DC/BL_CUXOS <= 1 & Delta_Anx_DC/BL_CUXOS > .5,  "Unresponders", "Low BL Dep" 
+      )))),
+    Treatment_Responder = as.factor(
+      ifelse(BL_CUXOS > 10 & (Delta_Anx_DC/BL_CUXOS) < .5 & (Delta_Anx_DC/BL_CUXOS) >= 0, "Anx Responder",
+      ifelse((Delta_Dep_DC/BL_CUDOS) < .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Dep Responder",
+      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 &(Delta_Anx_DC/BL_CUXOS) < .5 & (Delta_Anx_DC/BL_CUXOS) >= 0 & (Delta_Dep_DC/BL_CUDOS) < .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Both_Responder", 
+      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 0, "Anx Worse",
+      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 0, "Dep Worse",
+      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS >= .5 & Delta_Dep_DC/BL_CUDOS < 1 & Delta_Dep_DC/BL_CUDOS >= .5, "Both Unresponder",
+      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 1 & Delta_Dep_DC/BL_CUDOS >= .5, "Dep Unresponders", 
+      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS >= .5, "Anx Unresponders", "Low Baseline"
+      ))))))))))
+
+summary(Mothership_post$Treatment_Responder)
+summary(Mothership_post$Anx_Responder)
+summary(Mothership_post$Dep_Responder)
+
+ggplot(Mothership_post, aes(x = Treatment_Responder)) +
+  geom_bar() +
+  coord_flip() +
+  labs(
+    title = "Treatment response of Anxiety and Depression",
+    subtitle = "Response = 50% reduciton in scores if BL score > 10")
+
+ggplot(Mothership_post, aes(x = Anx_Responder)) +
+  geom_bar() +
+  coord_flip() +
+    labs(
+    title = "Treatment response of Anxiety",
+    subtitle = "Response = 50% reduciton in scores if BL score > 10")
+
+ggplot(Mothership_post, aes(x = Dep_Responder)) +
+  geom_bar() +
+  coord_flip() +
+    labs(
+    title = "Treatment response of Depression",
+    subtitle = "Response = 50% reduciton in scores if BL score > 10")
+
+mean(Mothership_post$Percent_anx_change)
+ggplot(Mothership_post,aes(x = Anx_Responder, y = Percent_anx_change)) +
+         geom_boxplot()
+#2. Create pre_scores
+      # CUXOS_pre = Day1_CUXOS,
+      # CUDOS_pre = Day1_CUDOS
+      # )
+
+sum(Mothership_post$SUManx_DC < 0)
+
 ```
@@
 
+#Demographic tab
 Demo_tab<-data.frame(table1::table1(~Age_1+Education_1+Race_1+Gender_1+Relationship_1, data=Demo_tab_df))
@@
 
-#Disorder Table
+#Disorder Table - duratin
 Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_Diag_treat))
@@
 Dis_tab
+
+#Disorder Tab by 10 days
+Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_Diag_treat))
+colnames(Dis_tab_10) <- c("Primary Diagnosis","1-10 Days", "10+ Days", "Total Sample")
+Dis_tab_10
+
 ```
@@
 
-ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
+ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping =  aes(x = fct_rev(fct_infreq(Disorder_Type))))+
+  geom_bar(fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"
+                               ))+
+  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1),
+        legend.position = "none")+
+  xlab("Psychiatric Disorder Subtype")+
+  #scale_fill_manual(values = c("#003f5c","#2f4b7c","#665191", "#a05195", "#d45087", "#f95d6a", "#ff7c43", "#ffa600", "#EBC500")) +
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,4300))+
+  coord_flip()
+
+ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping =  aes(x = fct_rev(fct_infreq(Disorder_Type)),fill= Disorder_Type))+
   geom_bar()+
@@
   theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,4300))+
-  coord_flip()
-
-# ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping = aes(x = Disorder_Type, fill=Disorder_Type))+
-#   geom_bar()+
-#   ggtitle("Frequency of Psychiatric Disorder Subtypes") +
-#   theme(axis.text.x = element_text(angle = 45,hjust = 1),
-#         legend.position = "none")+
-#   xlab("Psychiatric Disorder Subtype")+
-#   theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-#   theme(panel.background=NULL)+
-#   scale_y_continuous(name = "Frequency",limits=c(0,2000))+
-#   coord_flip()+
-#   facet_wrap(~Duration)
+  scale_y_continuous(name = "Frequency",limits=c(0,1750))+
+  scale_fill_manual(values = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"
+                               )) +
+  coord_flip()+
+  facet_wrap(~Duration,labeller = labeller(Duration =
+      c("1" = "1-5 Days", 
+        "2" = "6-10 Days", 
+        "3" = "11-15 Days",
+        "4" = "16+ Days")
+      ))
 ```
 
+# Most co-ocurring diagnoses
 ```{r}
@@
 •	Visualization – RDQ pre and post change.
+
+```{r}
+#Read in a New Data Set
+Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
+Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
+Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))
+
+#Make This Data Set Long Data
+library(tidyr)
+Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
+                              factor_key = "T")
+Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]
+
+#Create a Time Variable
+Mothership_Long_RDQ$PrePost <- NA
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_coping"]<-"Pre"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_pmh"]<-"Pre"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_func"]<-"Pre"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_wbs"]<-"Pre"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_sym"]<-"Pre"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_coping"]<-"Post"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_pmh"]<-"Post"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_func"]<-"Post"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_wbs"]<-"Post"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_sym"]<-"Post"
+
+#Create a New Data Set with an Average Depression Variable and Race
+Mothership_Mean_RDQ<-Mothership_Long_RDQ %>%
+  group_by(rm,PrePost) %>%
+  summarise(RDQ=mean(RDQ,na.rm=TRUE))
+
+#Add a Paired Variable to the New Data Set
+Mothership_Mean_RDQ<-mutate(Mothership_Mean_RDQ,
+                            paired=case_when(rm=="rdqPRE_coping"~"1",
+                                             rm=="rdqPOST_coping"~"1",
+                                             rm=="rdqPRE_pmh"~"2",
+                                             rm=="rdqPOST_pmh"~"2",
+                                             rm=="rdqPRE_func"~"3",
+                                             rm=="rdqPOST_func"~"3",
+                                             rm=="rdqPRE_wbs"~"4",
+                                             rm=="rdqPOST_wbs"~"4",
+                                             rm=="rdqPRE_sym"~"5",
+                                             rm=="rdqPOST_sym"~"5"))
+
+#Pre Post RDQ Plot - combined 
+ggplot(data=Mothership_Mean_RDQ,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
+           group=rm,color=paired,!is.na(PrePost)))+
+  geom_point(size=2.5)+
+  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="RDQ Subscore")+
+  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank())+
+  # scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
+  #                              "4"="#00BCA3","5"="#008570"),
+  scale_colour_manual(values = c("#ffa600","#ff6361","#bc5090","#58508d","#003f5c"),
+                     labels=c("Coping Skills","Positive Mental Health",
+                              "Functioning","Well-Being","Symptoms"))
+
+# pre post RDQ Plot - facet wrap
+ggplot(data=Mothership_Mean_RDQ,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
+           group=rm,color=paired,!is.na(PrePost))) +
+  geom_point(size=2.5) +
+  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5) +
+  scale_x_discrete(name="Time Point") +
+  scale_y_continuous(name="RDQ Subscore",limits = c(0, 40)) +
+  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire") +
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2)) +
+  theme(panel.background=NULL) +
+  theme(legend.position="none") +
+  # scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
+  #                              "4"="#00BCA3","5"="#008570")) +
+  scale_colour_manual(values = c("#ffa600","#ff6361","#bc5090","#58508d","#003f5c"))+
+  facet_wrap(~paired, labeller = labeller(paired =
+    c("1" = "Coping Skills",
+      "2"="Positive Mental Health",
+      "3"="Functioning",
+      "4"="Well-Being",
+      "5"="Symptoms")))
+
+```
+
 •	Table or Visualization – Reasons for discharge results.
+
+### Discharge Status
+```{r}
+### Bar Chart for Discharge Status ###
+
+ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = fct_rev(fct_infreq(DC_status_1))))+
+  geom_bar(fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"
+                               ))+
+  ggtitle("Frequency of Treatment Discharge Status") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Discharge Status") +
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6000)) +
+  coord_flip()
+
+ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = fct_rev(fct_infreq(DC_status_1))))+
+  geom_bar()+ #fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"))+
+  ggtitle("Frequency of Treatment Discharge Status") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Discharge Status") +
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,2100)) +
+  #scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
+  coord_flip() +
+  facet_wrap(~Duration,labeller = labeller(Duration =
+      c("1" = "1-5 Days", 
+        "2" = "6-10 Days", 
+        "3" = "11-15 Days",
+        "4" = "16+ Days")
+      ))
+
+```
 
@@
   xlab("Education Level")+
-  theme(panel.grid.major.y = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
+  theme(panel.grid.major.x = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
   theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,3000))
+  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
+  coord_flip()
 ```
@@
   theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+  scale_y_continuous(name = "Frequency",limits=c(0,6500)) +
+  coord_flip()
 ```
@@
 
-### Discharge Status
-```{r}
-### Bar Chart for Discharge Status ###
-
-ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = DC_status_1))+
-  geom_bar(color = "black",fill="darkgreen")+
-  ggtitle("Frequency of Treatment Discharge Status") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Discharge Status") +
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6000)) +
-  coord_flip()
-```
-
 ### Treatment Track
@@
   xlab("Treatment Type")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.grid.major.x= element_line(color = "grey",size = 0.5,linetype = 2))+
   theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+  scale_y_continuous(name = "Frequency",limits=c(0,4200))+
+  coord_flip()
 ```
@@
   xlab("Treatment Year")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
   theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,1500))
+  scale_y_continuous(name = "Frequency",limits=c(0,1500)) +
+  coord_flip()
 ```
@@
   xlab("Treatment Duration")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
   theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
+  coord_flip()
 

### 2023-09-16 Treatment_Outcomes.Rmd
Trying to figure out treatment responders

@@
 
-#Pre Post RDQ Plot
+str(Mothership_Mean_RDQ$rm)
+
+#Pre Post RDQ Plot - combined 
 ggplot(data=Mothership_Mean_RDQ,
@@
 
+# pre post RDQ Plot - facet wrap
+ggplot(data=Mothership_Mean_RDQ,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
+           group=rm,color=paired,!is.na(PrePost))) +
+  geom_point(size=2.5) +
+  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5) +
+  scale_x_discrete(name="Time Point") +
+  scale_y_continuous(name="RDQ Subscore",limits = c(0, 40)) +
+  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire") +
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2)) +
+  theme(panel.background=NULL) +
+  theme(legend.position="none") +
+  scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
+                               "4"="#00BCA3","5"="#008570")) +
+  facet_wrap(~paired, labeller = labeller(paired =
+    c("1" = "Coping Skills",
+      "2"="Positive Mental Health",
+      "3"="Functioning",
+      "4"="Well-Being",
+      "5"="Symptoms")))
 ```

### 2023-09-16 Paper_stuff.Rmd
Updated Tx responders varaibles

@@
   mutate(
-    Delta_Anx_DC = BL_CUXOS - SUManx_DC,
-    Delta_Dep_DC = BL_CUDOS - SUMdep_DC,
-    Percent_anx_change = SUManx_DC - BL_CUXOS/BL_CUXOS,
-    Percent_Dep_Dchange = SUMdep_DC - BL_CUDOS/BL_CUDOS,
+    Delta_Anx_DC =  SUManx_DC - BL_CUXOS,
+    Delta_Dep_DC = SUMdep_DC - BL_CUDOS,
+    Percent_Anx_change = (Delta_Anx_DC/BL_CUXOS)*100,
+    Percent_Dep_Dchange = (Delta_Dep_DC/BL_CUDOS)*100,
     #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
     Anx_Responder = as.factor(
-      ifelse(BL_CUXOS > 10 &(Delta_Anx_DC/BL_CUXOS) <= .5 & (Delta_Anx_DC/BL_CUXOS) >= 0, "Anx Responder",
-      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 0, "Anx Worse", 
-      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS > .5,  "Unresponders", "Low BL Anx"      
+      ifelse(BL_CUXOS > 10 & Percent_Anx_change  <= -50, "Anx Responder",
+      ifelse(BL_CUXOS > 10 & Percent_Anx_change > 0, "Anx Worse", 
+      ifelse(BL_CUXOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50,  "Unresponders", "Low BL Anx"      
       )))),
     Dep_Responder = as.factor(
-      ifelse(BL_CUDOS > 10 & (Delta_Dep_DC/BL_CUDOS) <= .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Dep Responder",
-      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 0, "Dep Worse", 
-      ifelse(BL_CUDOS > 10 & Delta_Anx_DC/BL_CUXOS <= 1 & Delta_Anx_DC/BL_CUXOS > .5,  "Unresponders", "Low BL Dep" 
+      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
+      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0, "Dep Worse", 
+      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50,  "Unresponders", "Low BL Dep" 
       )))),
     Treatment_Responder = as.factor(
-      ifelse(BL_CUXOS > 10 & (Delta_Anx_DC/BL_CUXOS) < .5 & (Delta_Anx_DC/BL_CUXOS) >= 0, "Anx Responder",
-      ifelse((Delta_Dep_DC/BL_CUDOS) < .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Dep Responder",
-      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 &(Delta_Anx_DC/BL_CUXOS) < .5 & (Delta_Anx_DC/BL_CUXOS) >= 0 & (Delta_Dep_DC/BL_CUDOS) < .5 & (Delta_Dep_DC/BL_CUDOS) >= 0, "Both_Responder", 
-      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 0, "Anx Worse",
-      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 0, "Dep Worse",
-      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS >= .5 & Delta_Dep_DC/BL_CUDOS < 1 & Delta_Dep_DC/BL_CUDOS >= .5, "Both Unresponder",
-      ifelse(BL_CUDOS > 10 & Delta_Dep_DC/BL_CUDOS < 1 & Delta_Dep_DC/BL_CUDOS >= .5, "Dep Unresponders", 
-      ifelse(BL_CUXOS > 10 & Delta_Anx_DC/BL_CUXOS < 1 & Delta_Anx_DC/BL_CUXOS >= .5, "Anx Unresponders", "Low Baseline"
-      ))))))))))
+      ifelse(BL_CUXOS > 10 & BL_CUXOS > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
+      ifelse(BL_CUXOS > 10 & Percent_Anx_change  <= -50, "Anx Responder",
+      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
+      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0 & BL_CUXOS > 10 & Percent_Anx_change > 0, "Both Worse",
+      ifelse(BL_CUXOS > 10 & Percent_Anx_change > 0, "Anx Worse",
+      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
+      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
+      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
+      ifelse(BL_CUXOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
+      )))))))))))
 
@@
   coord_flip() +
+  scale_x_discrete(limits =c("Low Baseline", "Both Worse", "Dep Worse", "Anx Worse","Both Unresponder","Dep Unresponders", "Anx Unresponders","Both_Responder", "Anx Responder","Dep Responder"))+
   labs(
@@
 mean(Mothership_post$Percent_anx_change)
-ggplot(Mothership_post,aes(x = Anx_Responder, y = Percent_anx_change)) +
-         geom_boxplot()
+ggplot(Mothership_post,aes(x = Anx_Responder, y = Percent_Anx_change)) +
+         geom_boxplot() +
+         ylim(-50,500) + 
+  scale_x_discrete(limits = c(
+    ""
+  ))
+
 #2. Create pre_scores
@@
 
+(40-50)/50
 ```

### 2023-09-20 Treatment_Outcomes.Rmd
POST SCORES!

@@
       CUXOS_pre = Day1_CUXOS,
-      CUDOS_pre = Day1_CUDOS
+      CUDOS_pre = Day1_CUDOS,
+      dummy = -99
       ) %>%
@@
   # Depression
-
-    CUDOS_Score <- select(Mothership_post,
+Mothership_post
+    CUDOS_Score <-    
+                      select(Mothership_post,
                       Day1_CUDOS:Day40_CUDOS)
@@
   # Anxiety
-    CUXOS_Score <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS)
+    CUDOS_Score <- select(Mothership_post, dummy,Day1_CUXOS:Day40_CUXOS)
     CUXOS_Score <- data.frame(CUXOS_Score)
@@
   summarise(Score=mean(Score,na.rm=TRUE))
+```
+
+```{r}
+#load DF
+nrow(CUDOS_Score)
+CUDOS_Score
+
+CUDOS_Score_Test <- CUDOS_Score[1:20,]
+CUDOS_Score_Test
+
+new_var <- NA
+data <- NA
+# new_var <- data.frame(new_var)
+for(i in 1:nrow(CUDOS_Score)){
+data <- unname(unlist(CUDOS_Score[i,]))
+data <- data[!is.na(data)]
+data <- tail(data, n=1)
+new_var <- rbind(new_var,data)
+}
+
+new_var
+
+first_var <-rbind(first_var,first)
+last_var
+
+pre_post <-data.frame(first_var,last_var)
+
+pre_post
+
+new_var
+nrow(new_var)
+
+Mothership_post <- mutate(Mothership_post,
+
+                          )
+
+# Mothership_post$Days_complete_W
 

### 2023-09-20 Paper_stuff.Rmd
Pre/Post Scores!!

@@
 
+# only include people that attend treatment & its thier first time attending
+Mothership <- Mothership |>
+        filter(
+          is.na(Prev_AdmitID_1),
+          C_Admit_1 == 1
+          ) |>
+        mutate(
+          dummy = -99
+        )
+
 # df without NAs in date and disorder type
@@
 
-Main_Treat <- Mothership |>
-
 ### Export as CSV
@@
 Pre_Post
+### Extract pre/post scores
 ```{r}
-Mothership_post <- Mothership |>
+#1. load DF
+    Mothership_post <- Mothership_Diag_treat
+
+    # Depressiopn
+    CUDOS_Score_post <-  select(Mothership_post, dummy,Day1_CUDOS:Day40_CUDOS)
+    # Anxiety
+    CUXOS_Score_post <- select(Mothership_post, dummy,Day1_CUXOS:Day40_CUXOS)
+
+#2. Getting post scores for people who have NA for post
+
+    # Depression
+    Post_DEP <- NA
+    PD_df <- NA
+    for(i in 1:nrow(CUDOS_Score_post)){
+    PD_df <- unname(unlist(CUDOS_Score_post[i,]))
+    PD_df <- PD_df[!is.na(PD_df)]
+    PD_df <- tail(PD_df, n=1)
+    Post_DEP <- rbind(Post_DEP,PD_df)
+    }
+    Post_Dep <- Post_DEP[-1]
+
+    # Anxiety
+    Post_ANX <- NA
+    PA_df <- NA
+    for(i in 1:nrow(CUXOS_Score_post)){
+    PA_df <- unname(unlist(CUXOS_Score_post[i,]))
+    PA_df <- PA_df[!is.na(PA_df)]
+    PA_df <- tail(PA_df, n=1)
+    Post_ANX <- rbind(Post_ANX,PA_df)
+    }
+    Post_anx <- Post_ANX[-1]
+
+# 3. Getting BL scores for people who have NA at Baseline
+
+    # Depression / Anxiety Dummy variable
+    CUDOS_Score_pre <-  select(Mothership_post, Day1_CUDOS:Day40_CUDOS,dummy)
+    CUXOS_Score_pre <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS,dummy)
+
+    # Depression
+    Pre_DEP <- NA
+    PD_df <- NA
+    for(i in 1:nrow(CUDOS_Score_pre)){
+    PD_df <- unname(unlist(CUDOS_Score_pre[i,]))
+    PD_df <- PD_df[!is.na(PD_df)]
+    PD_df <- head(PD_df, n=1)
+    Pre_DEP <- rbind(Pre_DEP,PD_df)
+    }
+    Pre_dep <- Pre_DEP[-1]
+
+    # Anxiety
+    Pre_ANX <- NA
+    PA_df <- NA
+    for(i in 1:nrow(CUXOS_Score_pre)){
+    PA_df <- unname(unlist(CUXOS_Score_pre[i,]))
+    PA_df <- PA_df[!is.na(PA_df)]
+    PA_df <- head(PA_df, n=1)
+    Pre_ANX <- rbind(Pre_ANX,PA_df)
+    }
+    Pre_anx <- Pre_ANX[-1]
+
+#4 Adding it back to mother ship
+    Mothership_post <- Mothership_post |>
+      mutate(
+        CUDOS_pre = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
+          CUDOS_pre = ifelse(CUDOS_pre < 0, NA, CUDOS_pre),
+        CUXOS_pre = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
+          CUXOS_pre = ifelse(CUXOS_pre < 0, NA, CUXOS_pre),
+        CUDOS_post = ifelse(Post_Dep < 0, NA, Post_Dep),
+        CUXOS_post = ifelse(Post_anx < 0, NA, Post_anx)
+      )
+
+#7. create new DF with Varaibles we want
+
+AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
+                                  Mothership_post$Disorder_treat,
+                                  Mothership_post$CUDOS_pre,
+                                  Mothership_post$CUDOS_post,
+                                  Mothership_post$CUXOS_pre,
+                                  Mothership_post$CUXOS_post)) %>%
+  filter(!is.na(Mothership_post$Disorder_Type))
+
+colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post")
+
+#8. Create long data frame
+
+AnxDep_PrePost_Long <- AnxDep_PrePost %>% 
+  pivot_longer(
+    cols = CUDOS_pre:CUXOS_post, 
+    names_to = "Test",
+    values_to = "Score"
+  )
+AnxDep_PrePost_Long <-AnxDep_PrePost_Long %>%
+  mutate(
+    PrePost = ifelse(
+      Test == "CUDOS_pre", "Pre",
+      ifelse(Test == "CUXOS_pre" , "Pre", "Post"
+    )),
+    Score = as.integer(Score),
+    Test = as.factor(Test),
+    Test = as.factor(ifelse(Test == "CUDOS_pre",  "CUDOS",
+                     ifelse(Test == "CUDOS_post", "CUDOS", "CUXOS"
+                     ))))
+
+#9. Convert to data frame with means of values to be plotted
+AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
+  group_by(Test,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+```
+
+### Overall Plot
+```{r}
+# Pre Post CUDOS/CUXOS Plot
+ggplot(data=AnxDep_PrePost_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Test,color=Test))+
+  geom_point(size=2.5)+
+  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS/CUXOS Score")+
+  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank())
+
+```
+
+### Line Plot By Disorder
+```{r}
+#1. Creaate new datasets with only anxiety / depresssion
+
+ANX_PrePost<- AnxDep_PrePost_Long %>%
+  filter(Test == "CUXOS")
+
+DEP_PrePost<- AnxDep_PrePost_Long %>%
+  filter(Test == "CUDOS")
+
+#2. Create DF grouped buy disorder type
+ANX_PrePost_mean<-ANX_PrePost %>%
+  group_by(Disorder_Type,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+DEP_PrePost_mean<-DEP_PrePost %>%
+  group_by(Disorder_Type,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+#### ANX
+ggplot(data=ANX_PrePost_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_point(size=2.5)+
+  geom_line(size=1)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUXOS Score")+
+  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUXOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank())
+
+#### DEP
+ggplot(data=DEP_PrePost_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_point(size=2.5)+
+  geom_line(size=1)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS Score")+
+  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
+       subtitle = "Self report depression was assessed using the CUDOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank())
+```
+
+### Dumbell Plot by Disorder
+```{r}
+Pre_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
+Plot_Text
+
+"#aeb6bf"
+
+ggplot(data=Pre_ANX,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUXOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
+  scale_y_reverse(limits = c(45,15)) +
+  coord_flip() +
+  theme_classic()+
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+
+#sum(as.factor(ANX_PrePost$Disorder_Type))
+
+Pre_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+ggplot(data=Pre_DEP,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUDOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
+       ylab = "Disorder Type")+
+  scale_y_reverse(limits = c(45,15)) +
+  coord_flip() +
+  theme_classic()+
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+```
+
+```{r}
+Mothership_post <- Mothership_post |>
   #1. Filter out scores for people not in the program / don't have dataa
@@
     #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
-  filter(!Days_complete_1 > 40,
-         !Days_complete_1 == 0,
-         !is.na(BL_CUXOS),
-         !is.na(SUManx_DC),
-         BL_CUXOS > 1,
-         SUManx_DC > 0,
-         !is.na(BL_CUDOS),
-         !is.na(SUMdep_DC),
-         BL_CUDOS > 1,
-         SUMdep_DC > 0
+  filter(!is.na(CUXOS_pre),
+         !is.na(CUXOS_post),
+         CUXOS_pre > 0,
+         CUXOS_post >= 0,
+         !is.na(CUDOS_pre),
+         !is.na(CUDOS_post),
+         CUDOS_pre > 0,
+         CUDOS_post> 0
          ) |>
   mutate(
-    Delta_Anx_DC =  SUManx_DC - BL_CUXOS,
-    Delta_Dep_DC = SUMdep_DC - BL_CUDOS,
-    Percent_Anx_change = (Delta_Anx_DC/BL_CUXOS)*100,
-    Percent_Dep_Dchange = (Delta_Dep_DC/BL_CUDOS)*100,
+    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
+    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
+    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
+    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
     #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
     Anx_Responder = as.factor(
-      ifelse(BL_CUXOS > 10 & Percent_Anx_change  <= -50, "Anx Responder",
-      ifelse(BL_CUXOS > 10 & Percent_Anx_change > 0, "Anx Worse", 
-      ifelse(BL_CUXOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50,  "Unresponders", "Low BL Anx"      
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse", 
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50,  "Unresponders", "Low BL Anx"      
       )))),
     Dep_Responder = as.factor(
-      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
-      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0, "Dep Worse", 
-      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50,  "Unresponders", "Low BL Dep" 
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse", 
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50,  "Unresponders", "Low BL Dep" 
       )))),
     Treatment_Responder = as.factor(
-      ifelse(BL_CUXOS > 10 & BL_CUXOS > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
-      ifelse(BL_CUXOS > 10 & Percent_Anx_change  <= -50, "Anx Responder",
-      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
-      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0 & BL_CUXOS > 10 & Percent_Anx_change > 0, "Both Worse",
-      ifelse(BL_CUXOS > 10 & Percent_Anx_change > 0, "Anx Worse",
-      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
-      ifelse(BL_CUXOS > 10 & BL_CUDOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
-      ifelse(BL_CUDOS > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
-      ifelse(BL_CUXOS > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
+      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
+      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
       )))))))))))
@@
     subtitle = "Response = 50% reduciton in scores if BL score > 10")
-
-mean(Mothership_post$Percent_anx_change)
-ggplot(Mothership_post,aes(x = Anx_Responder, y = Percent_Anx_change)) +
-         geom_boxplot() +
-         ylim(-50,500) + 
-  scale_x_discrete(limits = c(
-    ""
-  ))
-
-#2. Create pre_scores
-      # CUXOS_pre = Day1_CUXOS,
-      # CUDOS_pre = Day1_CUDOS
-      # )
-
-sum(Mothership_post$SUManx_DC < 0)
-
-(40-50)/50
 ```

### 2023-09-20 Treatment_Outcomes.Rmd
Pre/Post Scores!!
extra pre/post

--- 2023-09-16 Treatment_Outcomes.Rmd
@@
 ```{r}
-# 1. First adjust the their values for length of stay above 40 to 40, because the measures don't go above 40 days.
+#1. load DF
 
-Mothership_post <- Mothership %>%
-  mutate(Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
+Mothership
 
-#2. Create pre_scores
-      CUXOS_pre = Day1_CUXOS,
-      CUDOS_pre = Day1_CUDOS
-      ) %>%
+    Mothership_post <- Mothership |>
+        filter(
+          is.na(Prev_AdmitID_1),
+          C_Admit_1 == 1
+          ) |>
+        mutate(
+          dummy = -99
+        )
 
-#4. Filter out scores for people not in the program / don't have dataa
-  filter(!is.na(Days_complete_W)) %>%
-    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
-  filter(!Days_complete_1 > 40) %>%
-  filter(!Days_complete_W == 0)
+    # Depressiopn
+    CUDOS_Score_post <-  select(Mothership_post, dummy,Day1_CUDOS:Day40_CUDOS)
+    # Anxiety
+    CUXOS_Score_post <- select(Mothership_post, dummy,Day1_CUXOS:Day40_CUXOS)
 
-dim(Mothership_post)
+#2. Getting post scores for people who have NA for post
 
-#5. Then create df with CUDOS and CUXOS scores
     # Depression
-
-    CUDOS_Score <- select(Mothership_post,
-                      Day1_CUDOS:Day40_CUDOS)
-    CUDOS_Score <- data.frame(CUDOS_Score)
+    Post_DEP <- NA
+    PD_df <- NA
+    for(i in 1:nrow(CUDOS_Score_post)){
+    PD_df <- unname(unlist(CUDOS_Score_post[i,]))
+    PD_df <- PD_df[!is.na(PD_df)]
+    PD_df <- tail(PD_df, n=1)
+    Post_DEP <- rbind(Post_DEP,PD_df)
+    }
+    Post_DEP
+    Post_Dep <- Post_DEP[-1]
 
     # Anxiety
-    CUXOS_Score <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS)
-    CUXOS_Score <- data.frame(CUXOS_Score)
+    Post_ANX <- NA
+    PA_df <- NA
+    for(i in 1:nrow(CUXOS_Score_post)){
+    PA_df <- unname(unlist(CUXOS_Score_post[i,]))
+    PA_df <- PA_df[!is.na(PA_df)]
+    PA_df <- tail(PA_df, n=1)
+    Post_ANX <- rbind(Post_ANX,PA_df)
+    }
 
-#6. Using incidences to extract values
+    Post_ANX
+    Post_anx <- Post_ANX[-1]
 
-Mothership_post <- Mothership_post %>%
+# 3. Getting BL scores for people who have NA at Baseline
+
+    # Depression / Anxiety Dummy variable
+    CUDOS_Score_pre <-  select(Mothership_post, Day1_CUDOS:Day40_CUDOS,dummy)
+    CUXOS_Score_pre <- select(Mothership_post, Day1_CUXOS:Day40_CUXOS,dummy)
+
+    # Depression
+    Pre_DEP <- NA
+    PD_df <- NA
+    for(i in 1:nrow(CUDOS_Score_pre)){
+    PD_df <- unname(unlist(CUDOS_Score_pre[i,]))
+    PD_df <- PD_df[!is.na(PD_df)]
+    PD_df <- head(PD_df, n=1)
+    Pre_DEP <- rbind(Pre_DEP,PD_df)
+    }
+    Pre_dep <- Pre_DEP[-1]
+
+    # Anxiety
+    Pre_ANX <- NA
+    PA_df <- NA
+    for(i in 1:nrow(CUXOS_Score_pre)){
+    PA_df <- unname(unlist(CUXOS_Score_pre[i,]))
+    PA_df <- PA_df[!is.na(PA_df)]
+    PA_df <- head(PA_df, n=1)
+    Pre_ANX <- rbind(Pre_ANX,PA_df)
+    }
+    Pre_anx <- Pre_ANX[-1]
+
+#4 Adding it back to mother ship
+    Mothership_post <- Mothership_post |>
       mutate(
-    CUDOS_post = CUDOS_Score[cbind(c(1:8343),Mothership_post$Days_complete_W)],
-    CUXOS_post = CUXOS_Score[cbind(c(1:8343),Mothership_post$Days_complete_W)]
+        CUDOS_pre = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
+          CUDOS_pre = ifelse(CUDOS_pre < 0, NA, CUDOS_pre),
+        CUXOS_pre = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
+          CUXOS_pre = ifelse(CUXOS_pre < 0, NA, CUXOS_pre),
+        CUDOS_post = ifelse(Post_Dep < 0, NA, Post_Dep),
+        CUXOS_post = ifelse(Post_anx < 0, NA, Post_anx)
       )
@@
 
-```
-
-```{r, include=FALSE}
-# Try to extract values using a while loop?
-
-for (i in 1:nrow(CUDOS_Score)){
-  while(is.na(CUDOS_Score[i,CUDOS_Score$Days_complete_W])){
-    x = Days_complete_W -1
-    post_days <- CUDOS_Score[i,(x)]
-  }
-}
 ```
@@
 
+"#aeb6bf"
+
 ggplot(data=Pre_ANX,
@@
            group=Disorder_Type,color=Disorder_Type))+
-  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#aeb6bf",
+  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
               size = 4, #Note that I sized the segment to fit the points
@@
            group=Disorder_Type,color=Disorder_Type))+
-  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#aeb6bf",
+  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
               size = 4, #Note that I sized the segment to fit the points

### 2023-09-23 Paper_stuff.Rmd
made treatment response factors

@@
 
+    dim(CUDOS_Score_pre)
+    dim(Mothership_post)
+    length(Mothership_post$BL_CUDOS)
+    length(Pre_dep)
 #4 Adding it back to mother ship
@@
       mutate(
-        CUDOS_pre = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
-          CUDOS_pre = ifelse(CUDOS_pre < 0, NA, CUDOS_pre),
-        CUXOS_pre = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
-          CUXOS_pre = ifelse(CUXOS_pre < 0, NA, CUXOS_pre),
+        CUDOS_first = ifelse(is.na(BL_CUDOS),Pre_dep,BL_CUDOS),
+           CUDOS_first = ifelse(CUDOS_first < 0, NA, CUDOS_first),
+        CUXOS_first = ifelse(is.na(BL_CUXOS),Pre_anx,BL_CUXOS),
+           CUXOS_first = ifelse(CUXOS_first < 0, NA, CUXOS_first),
+        CUDOS_pre = BL_CUDOS,
+        CUXOS_pre = BL_CUXOS,
         CUDOS_post = ifelse(Post_Dep < 0, NA, Post_Dep),
-        CUXOS_post = ifelse(Post_anx < 0, NA, Post_anx)
+        CUXOS_post = ifelse(Post_anx < 0, NA, Post_anx),
+        BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
+                               ifelse(is.na(BL_CUDOS), "Dep Missing", "Not Missing"
+                                      ))),
+        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
+                           ifelse(BL_CUXOS > 20, "Sig Anx",
+                           ifelse(BL_CUDOS > 20, "Sig Dep",
+                           ifelse(is.na(BL_CUXOS),NA,
+                           ifelse(is.na(BL_CUDOS),NA, "Sub Both"
+                        )))))),
+        Sig_BL_Anx = as.factor(ifelse(BL_CUXOS > 20, "Significant",
+                               ifelse(is.na(BL_CUXOS),NA, "Subclinical"
+                              ))),
+        Sig_BL_Dep = as.factor(ifelse(BL_CUDOS > 20, "Significant",
+                               ifelse(is.na(BL_CUDOS),NA, "Subclinical"
+                              ))),
+        Sig_Post_Anx = as.factor(ifelse(CUXOS_post > 20, "Significant",
+                               ifelse(is.na(CUXOS_post),NA, "Subclinical"
+                              ))),
+        Sig_Post_Dep = as.factor(ifelse(CUDOS_post > 20, "Significant",
+                               ifelse(is.na(CUDOS_post),NA, "Subclinical"
+                              ))),
+        Any_Sig_BL = as.factor(ifelse(BL_CUXOS > 20 | BL_CUDOS > 20, "Sig",
+                               ifelse(is.na(BL_CUXOS),NA,
+                               ifelse(is.na(BL_CUDOS),NA, "Sub"
+                               )))),
+        Any_Sig_Post = as.factor(ifelse(CUXOS_post > 20 | CUDOS_post > 20, "Sig",
+                               ifelse(is.na(CUXOS_post),NA,
+                               ifelse(is.na(CUDOS_post),NA, "Sub"
+                               )))),
+        Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
+                 ifelse(BL_CUXOS > 20, "Sig Anx",
+                 ifelse(BL_CUDOS > 20, "Sig Dep",
+                 ifelse(is.na(BL_CUDOS), NA,
+                 ifelse(is.na(BL_CUXOS), NA, "Subclinical"
+                        )))))),
+        Sig_Post = as.factor(ifelse(CUXOS_post > 20 & CUDOS_post > 20, "Sig Both",
+                 ifelse(CUXOS_post > 20, "Sig Anx",
+                 ifelse(CUDOS_post > 20, "Sig Dep",
+                 ifelse(is.na(CUDOS_post), NA,
+                 ifelse(is.na(CUXOS_post), NA, "Subclinical"
+                        )))))),
+        Sig_unresponse = as.factor(ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post == "Subclinical", "Responder",
+                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Both", "Non-responder",
+                            ifelse(Sig_BL == "Sig Anx" & Sig_Post == "Sig Anx", "Non-responder",
+                            ifelse(Sig_BL == "Sig Dep" & Sig_Post == "Sig Dep", "Non-responder",
+                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Anx", "Dep gone Anx not",
+                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Dep", "Anx gone Dep not", NA
+                            ))))))))
+
+  # checking for pre scores
+   (grepl("Sig Both",Mothership_post$Sig_pre) | grepl("Sig Anx",Mothership_post$Sig_pre) | grepl("Sig Anx",Mothership_post$Sig_pre))
+    &
+  # Checking psot scores
+  (grepl("Sig Both",Mothership_post$Sig_Post) | grepl("Sig Anx",Mothership_post$Sig_Post) | grepl("Sig Anx",Mothership_post$Sig_Post))
+
+        ))
+              #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
+        BL_Dep_level = as.factor(ifelse(BL_CUDOS > 10 & BL_CUDOS <= 20, "Minimal",
+                                 ifelse(BL_CUDOS > 20 & BL_CUDOS <= 30, "Mild",
+                                 ifelse(BL_CUDOS > 10 & BL_CUDOS <= 45, "Moderate",
+                                 ifelse(BL_CUDOS > 45, "Severe",
+                                 ifelse(is.na(BL_CUDOS), NA, "Remission"
+                                )))))),
+        BL_Anx_level = as.factor(ifelse(BL_CUXOS > 10 & BL_CUXOS <= 20, "Minimal",
+                                 ifelse(BL_CUXOS > 20 & BL_CUXOS <= 30, "Mild",
+                                 ifelse(BL_CUXOS > 10 & BL_CUXOS <= 45, "Moderate",
+                                 ifelse(BL_CUXOS > 45, "Severe",
+                                 ifelse(is.na(BL_CUXOS), NA, "Remission"
+                                )))))),
+        Post_Dep_level = as.factor(ifelse(CUDOS_post > 10 & CUDOS_post <= 20, "Minimal",
+                                 ifelse(CUDOS_post > 20 & CUDOS_post <= 30, "Mild",
+                                 ifelse(CUDOS_post > 10 & CUDOS_post <= 45, "Moderate",
+                                 ifelse(CUDOS_post > 45, "Severe",
+                                 ifelse(is.na(CUDOS_post), NA, "Remission"
+                                )))))),
+        Post_Anx_level = as.factor(ifelse(CUXOS_post > 10 & CUXOS_post <= 20, "Minimal",
+                                 ifelse(CUXOS_post > 20 & CUXOS_post <= 30, "Mild",
+                                 ifelse(CUXOS_post > 10 & CUXOS_post <= 45, "Moderate",
+                                 ifelse(CUXOS_post > 45, "Severe",
+                                 ifelse(is.na(CUXOS_post), NA, "Remission"
+                                )))))))
+
       )
-
 #7. create new DF with Varaibles we want
@@
                                   Mothership_post$Disorder_treat,
+                                  Mothership_post$BL_CUDOS,
+                                  Mothership_post$BL_CUXOS,
                                   Mothership_post$CUDOS_pre,
@@
                                   Mothership_post$CUXOS_pre,
-                                  Mothership_post$CUXOS_post)) %>%
+                                  Mothership_post$CUXOS_post,
+                                  #Extra stuff?
+                                  Mothership_post$BL_Missing,
+                                  Sig_BL_Anx,
+                                  Sig_unresponse
+
+                                  )) %>%
   filter(!is.na(Mothership_post$Disorder_Type))
@@
   theme(legend.title = element_blank())
+
+ggplot(data=AnxDep_PrePost_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Test,color=Test))+
+  geom_point(size=2.5)+
+  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS/CUXOS Score")+
+  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank()) +
+  facet_wrap(~Sig_)
 
@@
     Anx_Responder = as.factor(
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50 | CUXOS_post < 20, "Anx Responder",
       ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse", 
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50,  "Unresponders", "Low BL Anx"      
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & CUXOS_post < 20,  "Unresponders", "Low BL Anx"      
       )))),
@@
       )))))))))))
+
+ CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))
+ CUXOS_post
 

### 2023-09-24 Paper_stuff.Rmd
New figs, and breakdown of missing data

@@
     Pre_anx <- Pre_ANX[-1]
-
-    dim(CUDOS_Score_pre)
-    dim(Mothership_post)
-    length(Mothership_post$BL_CUDOS)
-    length(Pre_dep)
 #4 Adding it back to mother ship
@@
         CUXOS_pre = BL_CUXOS,
-        CUDOS_post = ifelse(Post_Dep < 0, NA, Post_Dep),
-        CUXOS_post = ifelse(Post_anx < 0, NA, Post_anx),
+        CUDOS_post = ifelse(!is.na(SUMdep_DC), SUMdep_DC,Post_Dep),
+            CUDOS_post = ifelse(CUDOS_post < 0, NA, CUDOS_post),
+        CUXOS_post = ifelse(!is.na(SUManx_DC), SUManx_DC,Post_anx),
+            CUXOS_post = ifelse(CUXOS_post < 0, NA, CUXOS_post),
         BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
@@
                         )))))),
-        Sig_unresponse = as.factor(ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post == "Subclinical", "Responder",
+        Sig_unresponse_type = as.factor(ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post == "Subclinical", "Responder",
                             ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Both", "Non-responder",
@@
                             ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Anx", "Dep gone Anx not",
-                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Dep", "Anx gone Dep not", NA
-                            ))))))))
-
-  # checking for pre scores
-   (grepl("Sig Both",Mothership_post$Sig_pre) | grepl("Sig Anx",Mothership_post$Sig_pre) | grepl("Sig Anx",Mothership_post$Sig_pre))
-    &
-  # Checking psot scores
-  (grepl("Sig Both",Mothership_post$Sig_Post) | grepl("Sig Anx",Mothership_post$Sig_Post) | grepl("Sig Anx",Mothership_post$Sig_Post))
-
-        ))
+                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Dep", "Anx gone Dep not", 
+                            ifelse(ifelse(Sig_BL == "Subclinical" & Sig_Post == "Subclinical", "Low_BL",       
+                                   NA
+                            ))))))))),
+        Sig_unresponse = as.factor(ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post == "Subclinical", "Responder",
+                                        ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post %in% c("Sig Both","Sig Anx","Sig Dep"), "Non-responder",
+                                        ifelse(ifelse(Sig_BL == "Subclinical" & Sig_Post == "Subclinical", "Low_BL",       
+                                   NA
+                                   ))))),
+
               #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
@@
 
-      )
 #7. create new DF with Varaibles we want
@@
                                   Mothership_post$BL_Missing,
-                                  Sig_BL_Anx,
-                                  Sig_unresponse
-
-                                  )) %>%
-  filter(!is.na(Mothership_post$Disorder_Type))
-
-colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post")
+                                  Mothership_post$Sig_BL,
+                                  Mothership_post$Sig_Post,
+                                  Mothership_post$Sig_unresponse,
+                                  Mothership_post$Sig_unresponse_type
+                                  )) #%>%
+  #filter(!is.na(Mothership_post$Disorder_treat))
+
+colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","BL_Missing",
+                             "Sig_BL", "Sig_Post","Sig_unresponse", "Sig_unresponse_type")
 
@@
 
+view(data.frame(table1::table1(~BL_CUXOS + BL_CUDOS + SUManx_DC + SUMdep_DC + CUDOS_post +CUXOS_post, data = Mothership_post)))
+
 ```
@@
        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Test,color=Test))+
+           group=Test,color=fct_rev(Test)))+
   geom_point(size=2.5)+
@@
 
-ggplot(data=AnxDep_PrePost_mean,
+AnxDep_response_mean<-AnxDep_PrePost_Long %>%
+  filter(!is.na(Sig_unresponse)) |>
+  group_by(Test,Sig_unresponse,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+ggplot(data=AnxDep_response_mean,
        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Test,color=Test))+
-  geom_point(size=2.5)+
-  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
+           group=Test,color=fct_rev(Test)))+
+  geom_point(size=2.5) +
+  geom_line(group=AnxDep_response_mean$PrePost,size=1.5)+
   scale_x_discrete(name="Time Point")+
@@
   theme(legend.title = element_blank()) +
-  facet_wrap(~Sig_)
-
+  facet_wrap(~Sig_unresponse,labeller = labeller(Sig_unresponse =
+      c("1" = "Non-responders", 
+        "2" = "Responders")
+      ))
 ```
@@
   theme(legend.title = element_blank())
+
+### FACAT WRAP
+
+AnxDep_Treat_mean<-AnxDep_PrePost_Long %>%
+  filter(!is.na(Sig_unresponse),
+         !is.na(Disorder_Type)) |>
+  group_by(Test,Disorder_Type,Sig_unresponse,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+p <- ggplot(data=AnxDep_Treat_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Test,color=fct_rev(Test)))+
+  geom_point(size=2.5) +
+  geom_line(group=AnxDep_Treat_mean$PrePost,size=1.5)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS/CUXOS Score")+
+  labs(
+    title = "Mean Pre and Post Scores of the Anxiety and Depression",
+    subtitle = "Treatment response based upon Disorder")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank()) +
+  facet_grid(Sig_unresponse~Disorder_Type,
+             labeller = labeller(
+               Sig_unresponse = c("1" = "Non-responders", "2" = "Responders"),
+               Disorder_Type = c("1" = "Anxiety", "2" = "BPD", "3" = "Mood", "4" ="Other", "5" = "Trauma")
+      ))
+
+#Anxiety     BPD    Mood   Other  Trauma
 ```
@@
  CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))
- CUXOS_post
 

### 2023-09-29 Paper_stuff.Rmd
JT PLOTS: Its gonna be ME

@@
 
-summary(Mothership_post$Treatment_Responder)
-summary(Mothership_post$Anx_Responder)
-summary(Mothership_post$Dep_Responder)
-
 ggplot(Mothership_post, aes(x = Treatment_Responder)) +
@@
     subtitle = "Response = 50% reduciton in scores if BL score > 10")
+```
+
+```{r}
+devtools::install_github("AWKruijt/JT-RCI")
+library(JTRCI)
+
+# generate some random data:
+df <- cbind.data.frame("ppid" = seq(1:64), 
+                       "pre" = rnorm(64, 65, 8), 
+                       "post" = c(rnorm(32, 40, 8), rnorm(32, 45, 8)),
+                       "group" = rep(c("treatment", "control"), each = 32))
+
+# The function will determine which criterion to use based on the available information 
+# f.i. when no (healthy or dysfunctional) norm values are provided, the function will  
+# return criterion A using the baseline distribution as the 'dysfunctional distribution':
+
+JTRCI(data = df, 
+      ppid = "ppid", 
+      pre = "pre", 
+      post = "post",  
+      reliability = .8, 
+      indextype = "JT", 
+      JTcrit = "auto")
+
+df
+
+Mothership_post$ID1
+RCI_df_dep <- Mothership_post |>
+  mutate(
+    ID1  = as.integer(ID1),
+    pre  = as.numeric(CUDOS_pre),
+    post = as.numeric(CUDOS_post),
+    Disorder = Disorder_treat
+  ) |>
+  select(
+    ID1,pre,post,Disorder
+  ) |>
+  filter(!is.na(pre),
+         !is.na(post))
+
+RCI_df_anx <- Mothership_post |>
+  mutate(
+    ID1  = as.integer(ID1),
+    pre  = as.numeric(CUXOS_pre),
+    post = as.numeric(CUXOS_post),
+    Disorder = Disorder_treat
+  ) |>
+  select(
+    ID1,pre,post,Disorder
+  ) |>
+  filter(!is.na(pre),
+         !is.na(post))
+
+RCI_df_dep <- data.frame(RCI_df_dep)
+RCI_df_anx <- data.frame(RCI_df_anx)
+
+JTRCI (data = RCI_df_anx, 
+       pre = "pre", 
+       post = "post", 
+       ppid = "ID1", 
+       reliability = .9, 
+       indextype = "JT", 
+       JTcrit = 20,
+       group = "Disorder",
+       facetplot = T,
+       plottitle = "Anxeity: JT indices by disorder")
+
+JTRCI(data = df, pre = "pre", post = "post",  group = "group", ppid = "ppid",
+      reliability = .8, indextype = "JT", JTcrit = "C",
+       normM = 30, normSD = 5, dysfM = 60, dysfSD = 5, 
+      facetplot = T, plottitle = "JT indices by group:")
 ```

### 2023-09-30 Paper_stuff.Rmd
filter pre > 20

@@
 
-df
-
-Mothership_post$ID1
 RCI_df_dep <- Mothership_post |>
@@
   filter(!is.na(pre),
-         !is.na(post))
+         !is.na(post),
+         pre > 20)
 

### 2023-10-03 Paper_stuff.Rmd
Figuring out RCI vs. JT plot

@@
 ```{r}
-devtools::install_github("AWKruijt/JT-RCI")
+#devtools::install_github("AWKruijt/JT-RCI")
+
 library(JTRCI)
 
+devtools::install_github("zieglema/ClinicalSig")
+library(ClinicalSig)
 # generate some random data:
@@
 # return criterion A using the baseline distribution as the 'dysfunctional distribution':
-
-JTRCI(data = df, 
-      ppid = "ppid", 
-      pre = "pre", 
-      post = "post",  
-      reliability = .8, 
-      indextype = "JT", 
-      JTcrit = "auto")
 
@@
 
-JTRCI (data = RCI_df_anx, 
+https://awkruijt.netlify.app/plotposts/longitudinaljtrci
+
+dataRci <- rci(pre="pre", post="post", data=RCI_df_anx, rtt=.74, sdNorm=19.5)
+ggplot(dataRci, aes(x = rci)) +
+  geom_histogram(fill = "blue", alpha = .5) +
+  labs(
+    title = "Histogram of RCI",
+    xlab = "RCI",
+    ylab = "Quanity of patients"
+  )
+
+dataRci
+
+```
+
+```{r}
+
+JTRCI(data = RCI_df_dep, 
       pre = "pre", 
@@
       reliability = .9, 
-       indextype = "JT", 
-       JTcrit = 20,
-       group = "Disorder",
-       facetplot = T,
+      indextype = "RCI",  
+      table = F, 
+      plot = F)
+
+scores
+
+RCI_df_anx1<-RCI_df_anx |>
+  select(ID1,pre,post)
+
+JTRCI (data = RCI_df_dep, 
+       pre = "pre", 
+       post = "post", 
+       ppid = "ID1", 
+       reliability = .74, 
+       indextype = "RCI", 
+       #JTcrit = "auto",
        plottitle = "Anxeity: JT indices by disorder")
@@
       facetplot = T, plottitle = "JT indices by group:")
-```
+
+JTRCI(data = df, 
+      ppid = "ppid", 
+      pre = "pre", 
+      post = "post",  
+      reliability = .8, 
+      indextype = "JT", 
+      JTcrit = "auto")
+```
+
+The mean total score on the CUXOS was 25.8 (SD = 19.5).
+The mean scores on the 6-item psychic anxiety subscale and 14-item somatic anxiety subscale were 10.6 (SD = 7.1) and 15.3 (SD = 13.7), respectively.
+
+A factor analysis yielded 2 factors with eigenvalues greater than 1.
+The 2 factors accounted for 58.7% of the total variance.
+On the first factor, the 14 somatic anxiety items had the highest loadings, each item with a loading ≥ 0.49.
+On the second factor, the 6 psychic anxiety items had the highest loadings with each item loading ≥ 0.68.
+
+The internal consistency of the CUXOS total scale score and the psychic and somatic anxiety subscales was examined in the entire sample who completed the scale at the initial evaluation and a sample of 120 patients who completed it at a follow-up appointment.
+The CUXOS demonstrated excellent internal consistency (baseline: Cronbach α = .95 for the total scale, .90 for the psychic anxiety subscale, and .93 for the somatic anxiety subscale; follow-up: α = .95 for the total scale, .94 for the psychic anxiety subscale, and .91 for the somatic anxiety subscale).
+The data in Table 2 show the correlation between each item and the total scale score.
+All item-scale correlations were statistically significant at baseline (median = 0.68) and at follow-up (median = 0.68).
+
+The test-retest reliability of the CUXOS was examined in 216 subjects who completed the scale at the time of their initial appointment.
+The test-retest reliability of the total scale and the psychic and somatic anxiety subscales was high (r = 0.90, 0.86, 0.88, respectively), and the test-retest reliability of each item was statistically significant (median r = 0.75) (Table 2).
 

### 2023-10-12 Paper_stuff.Rmd
RCI treatment response figures.

--- 2023-09-30 Paper_stuff.Rmd
@@
                                 )))))))
-
-#7. create new DF with Varaibles we want
-
-AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
-                                  Mothership_post$Disorder_treat,
-                                  Mothership_post$BL_CUDOS,
-                                  Mothership_post$BL_CUXOS,
-                                  Mothership_post$CUDOS_pre,
-                                  Mothership_post$CUDOS_post,
-                                  Mothership_post$CUXOS_pre,
-                                  Mothership_post$CUXOS_post,
-                                  #Extra stuff?
-                                  Mothership_post$BL_Missing,
-                                  Mothership_post$Sig_BL,
-                                  Mothership_post$Sig_Post,
-                                  Mothership_post$Sig_unresponse,
-                                  Mothership_post$Sig_unresponse_type
-                                  )) #%>%
-  #filter(!is.na(Mothership_post$Disorder_treat))
-
-colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","BL_Missing",
-                             "Sig_BL", "Sig_Post","Sig_unresponse", "Sig_unresponse_type")
-
-#8. Create long data frame
-
-AnxDep_PrePost_Long <- AnxDep_PrePost %>% 
-  pivot_longer(
-    cols = CUDOS_pre:CUXOS_post, 
-    names_to = "Test",
-    values_to = "Score"
-  )
-AnxDep_PrePost_Long <-AnxDep_PrePost_Long %>%
+    ```
+    ```{r}
+#devtools::install_github("AWKruijt/JT-RCI")
+
+library(JTRCI)
+
+#devtools::install_github("zieglema/ClinicalSig")
+library(ClinicalSig)
+# generate some random data:
+
+RCI_df_dep <- Mothership_post |>
   mutate(
-    PrePost = ifelse(
-      Test == "CUDOS_pre", "Pre",
-      ifelse(Test == "CUXOS_pre" , "Pre", "Post"
-    )),
-    Score = as.integer(Score),
-    Test = as.factor(Test),
-    Test = as.factor(ifelse(Test == "CUDOS_pre",  "CUDOS",
-                     ifelse(Test == "CUDOS_post", "CUDOS", "CUXOS"
-                     ))))
-
-#9. Convert to data frame with means of values to be plotted
-AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
-  group_by(Test,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
-
-view(data.frame(table1::table1(~BL_CUXOS + BL_CUDOS + SUManx_DC + SUMdep_DC + CUDOS_post +CUXOS_post, data = Mothership_post)))
-
-```
-
-### Overall Plot
-```{r}
-# Pre Post CUDOS/CUXOS Plot
-ggplot(data=AnxDep_PrePost_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Test,color=fct_rev(Test)))+
-  geom_point(size=2.5)+
-  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUDOS/CUXOS Score")+
-  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank())
-
-AnxDep_response_mean<-AnxDep_PrePost_Long %>%
-  filter(!is.na(Sig_unresponse)) |>
-  group_by(Test,Sig_unresponse,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
-
-ggplot(data=AnxDep_response_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Test,color=fct_rev(Test)))+
-  geom_point(size=2.5) +
-  geom_line(group=AnxDep_response_mean$PrePost,size=1.5)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUDOS/CUXOS Score")+
-  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank()) +
-  facet_wrap(~Sig_unresponse,labeller = labeller(Sig_unresponse =
-      c("1" = "Non-responders", 
-        "2" = "Responders")
-      ))
-```
-
-### Line Plot By Disorder
-```{r}
-#1. Creaate new datasets with only anxiety / depresssion
-
-ANX_PrePost<- AnxDep_PrePost_Long %>%
-  filter(Test == "CUXOS")
-
-DEP_PrePost<- AnxDep_PrePost_Long %>%
-  filter(Test == "CUDOS")
-
-#2. Create DF grouped buy disorder type
-ANX_PrePost_mean<-ANX_PrePost %>%
-  group_by(Disorder_Type,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
-
-DEP_PrePost_mean<-DEP_PrePost %>%
-  group_by(Disorder_Type,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
-
-#### ANX
-ggplot(data=ANX_PrePost_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_point(size=2.5)+
-  geom_line(size=1)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUXOS Score")+
-  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUXOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank())
-
-#### DEP
-ggplot(data=DEP_PrePost_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_point(size=2.5)+
-  geom_line(size=1)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUDOS Score")+
-  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
-       subtitle = "Self report depression was assessed using the CUDOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank())
-
-### FACAT WRAP
-
-AnxDep_Treat_mean<-AnxDep_PrePost_Long %>%
-  filter(!is.na(Sig_unresponse),
-         !is.na(Disorder_Type)) |>
-  group_by(Test,Disorder_Type,Sig_unresponse,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
-
-p <- ggplot(data=AnxDep_Treat_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Test,color=fct_rev(Test)))+
-  geom_point(size=2.5) +
-  geom_line(group=AnxDep_Treat_mean$PrePost,size=1.5)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUDOS/CUXOS Score")+
-  labs(
-    title = "Mean Pre and Post Scores of the Anxiety and Depression",
-    subtitle = "Treatment response based upon Disorder")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank()) +
-  facet_grid(Sig_unresponse~Disorder_Type,
-             labeller = labeller(
-               Sig_unresponse = c("1" = "Non-responders", "2" = "Responders"),
-               Disorder_Type = c("1" = "Anxiety", "2" = "BPD", "3" = "Mood", "4" ="Other", "5" = "Trauma")
-      ))
-
-#Anxiety     BPD    Mood   Other  Trauma
-```
-
-### Dumbell Plot by Disorder
-```{r}
-Pre_ANX<-ANX_PrePost_mean %>%
-  filter(PrePost == "Pre")
-
-Post_ANX<-ANX_PrePost_mean %>%
-  filter(PrePost == "Post")
-
-Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
-Plot_Text
-
-"#aeb6bf"
-
-ggplot(data=Pre_ANX,
-       aes(x=Disorder_Type,y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
-              size = 4, #Note that I sized the segment to fit the points
-              alpha = .5) +
-  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
-  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
-  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUXOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
-  scale_y_reverse(limits = c(45,15)) +
-  coord_flip() +
-  theme_classic()+
-  theme(#legend.position = "none",
-         plot.background = element_rect(
-      fill = "white",
-      colour = "white"))
-
-#sum(as.factor(ANX_PrePost$Disorder_Type))
-
-Pre_DEP<-DEP_PrePost_mean %>%
-  filter(PrePost == "Pre")
-
-Post_DEP<-DEP_PrePost_mean %>%
-  filter(PrePost == "Post")
-
-ggplot(data=Pre_DEP,
-       aes(x=Disorder_Type,y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
-              size = 4, #Note that I sized the segment to fit the points
-              alpha = .5) +
-  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
-  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
-  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUDOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
-       ylab = "Disorder Type")+
-  scale_y_reverse(limits = c(45,15)) +
-  coord_flip() +
-  theme_classic()+
-  theme(#legend.position = "none",
-         plot.background = element_rect(
-      fill = "white",
-      colour = "white"))
+    ID1  = as.integer(ID1),
+    pre  = as.numeric(CUDOS_pre),
+    post = as.numeric(CUDOS_post),
+    Disorder = Disorder_treat
+  ) |>
+  select(
+    ID1,pre,post,Disorder
+  ) |>
+  filter(!is.na(pre),
+         !is.na(post),
+         pre > 20)
+
+RCI_df_anx <- Mothership_post |>
+  mutate(
+    ID1  = as.integer(ID1),
+    pre  = as.numeric(CUXOS_pre),
+    post = as.numeric(CUXOS_post),
+    Disorder = Disorder_treat
+  ) |>
+  select(
+    ID1,pre,post,Disorder
+  ) |>
+  filter(!is.na(pre),
+         !is.na(post),
+         pre > 20)
+
+RCI_df_dep <- data.frame(RCI_df_dep)
+RCI_df_anx <- data.frame(RCI_df_anx)
+
+# https://awkruijt.netlify.app/plotposts/longitudinaljtrci
+
+RCI_df_anx1<-RCI_df_anx |>
+  select(ID1,pre,post)
+
+DEP_RCI <- JTRCI (data = RCI_df_dep, 
+       pre = "pre", 
+       post = "post", 
+       ppid = "ID1", 
+       reliability = .74, 
+       indextype = "RCI", 
+       #JTcrit = "auto",
+       plottitle = "Anxeity: JT indices by disorder")
+
+ANX_RCI <- JTRCI (data = RCI_df_anx, 
+       pre = "pre", 
+       post = "post", 
+       ppid = "ID1", 
+       reliability = .74, 
+       indextype = "RCI", 
+       #JTcrit = "auto",
+       plottitle = "Anxeity: JT indices by disorder")
+
+RCI_DF<- ANX_RCI$data
+colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")
+
+RCI_DF2<- DEP_RCI$data
+colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")
+
+RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
+colnames(RCI_DF)[1] = "ID1"
+
+RCI_DF
 ```
@@
     Anx_Responder = as.factor(
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50 | CUXOS_post < 20, "Anx Responder",
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse", 
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & CUXOS_post < 20,  "Unresponders", "Low BL Anx"      
-      )))),
+      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
+      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
+      )),
     Dep_Responder = as.factor(
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse", 
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50,  "Unresponders", "Low BL Dep" 
-      )))),
+      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
+      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
+      )),
     Treatment_Responder = as.factor(
@@
 
- CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))
+Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1)) |>
+  mutate(
+    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
+      Depression_Responder = as.factor(recode(Depression_Responder,
+         "1" = "2",
+         "2" = "2",
+         "3" = "1"
+      )),
+    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
+         Depression_Responder = as.factor(recode(Depression_Responder,
+          "2" = "Non-Responder",
+          "1" = "Responder"
+      )),
+    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
+      Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+         "1" = "2",
+         "2" = "2",
+         "3" = "1"
+      )),
+    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
+         Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+          "2" = "Non-Responder",
+          "1" = "Responder"
+      )),
+    RESPONDER_FIGS = as.factor(
+        ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
+        ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
+        )))
+
+# View(Mothership_joined)
+```
+
+    ```{r}
+#7. create new DF with Varaibles we want
+
+AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
+                                  Mothership_post$Disorder_treat,
+                                  Mothership_post$BL_CUDOS,
+                                  Mothership_post$BL_CUXOS,
+                                  Mothership_post$CUDOS_pre,
+                                  Mothership_post$CUDOS_post,
+                                  Mothership_post$CUXOS_pre,
+                                  Mothership_post$CUXOS_post,
+                                  #Extra stuff?
+                                  Mothership_post$Depression_Responder,
+                                  Mothership_post$Anxiety_Responder,
+                                  Mothership_post$RESPONDER_FIGS
+                                  )) #%>%
+  #filter(!is.na(Mothership_post$Disorder_treat))
+
+colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","Depression_Responder",
+                             "Anxiety_Responder", "RESPONDER_FIGS")
+
+#8. Create long data frame
+
+AnxDep_PrePost_Long <- AnxDep_PrePost %>% 
+  pivot_longer(
+    cols = CUDOS_pre:CUXOS_post, 
+    names_to = "Test",
+    values_to = "Score"
+  )
+AnxDep_PrePost_Long <-AnxDep_PrePost_Long %>%
+  mutate(
+    PrePost = ifelse(
+      Test == "CUDOS_pre", "Pre",
+      ifelse(Test == "CUXOS_pre" , "Pre", "Post"
+    )),
+    Score = as.integer(Score),
+    Test = as.factor(Test),
+    Test = as.factor(ifelse(Test == "CUDOS_pre",  "CUDOS",
+                     ifelse(Test == "CUDOS_post", "CUDOS", "CUXOS"
+                     ))))
+
+#9. Convert to data frame with means of values to be plotted
+AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
+  group_by(Test,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+#table1::table1(~BL_CUXOS + BL_CUDOS + SUManx_DC + SUMdep_DC + CUDOS_post +CUXOS_post, data = Mothership_post)
+
+```
+
+### Dumbell Plot by Disorder
+```{r}
+Pre_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
+Plot_Text
+
+"#aeb6bf"
+
+ggplot(data=Pre_ANX,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUXOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
+  scale_y_reverse(limits = c(45,15)) +
+  coord_flip() +
+  theme_classic()+
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+
+#sum(as.factor(ANX_PrePost$Disorder_Type))
+
+Pre_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+ggplot(data=Pre_DEP,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUDOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
+       ylab = "Disorder Type")+
+  scale_y_reverse(limits = c(45,15)) +
+  coord_flip() +
+  theme_classic()+
+
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+```
+
+```{r}
+Mothership_post <- Mothership_post |>
+  #1. Filter out scores for people not in the program / don't have dataa
+  filter(!is.na(Days_complete_1)) |>
+    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
+  filter(!is.na(CUXOS_pre),
+         !is.na(CUXOS_post),
+         CUXOS_pre > 0,
+         CUXOS_post >= 0,
+         !is.na(CUDOS_pre),
+         !is.na(CUDOS_post),
+         CUDOS_pre > 0,
+         CUDOS_post> 0
+         ) |>
+  mutate(
+    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
+    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
+    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
+    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
+    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
+    Anx_Responder = as.factor(
+      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
+      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
+      )),
+    Dep_Responder = as.factor(
+      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
+      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
+      )),
+    Treatment_Responder = as.factor(
+      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
+      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
+      )))))))))))
+
+ #CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))
 
@@
 
-```{r}
-devtools::install_github("AWKruijt/JT-RCI")
-library(JTRCI)
-
-# generate some random data:
-df <- cbind.data.frame("ppid" = seq(1:64), 
-                       "pre" = rnorm(64, 65, 8), 
-                       "post" = c(rnorm(32, 40, 8), rnorm(32, 45, 8)),
-                       "group" = rep(c("treatment", "control"), each = 32))
-
-# The function will determine which criterion to use based on the available information 
-# f.i. when no (healthy or dysfunctional) norm values are provided, the function will  
-# return criterion A using the baseline distribution as the 'dysfunctional distribution':
-
-JTRCI(data = df, 
-      ppid = "ppid", 
-      pre = "pre", 
-      post = "post",  
-      reliability = .8, 
-      indextype = "JT", 
-      JTcrit = "auto")
-
-RCI_df_dep <- Mothership_post |>
-  mutate(
-    ID1  = as.integer(ID1),
-    pre  = as.numeric(CUDOS_pre),
-    post = as.numeric(CUDOS_post),
-    Disorder = Disorder_treat
-  ) |>
-  select(
-    ID1,pre,post,Disorder
-  ) |>
-  filter(!is.na(pre),
-         !is.na(post),
-         pre > 20)
-
-RCI_df_anx <- Mothership_post |>
-  mutate(
-    ID1  = as.integer(ID1),
-    pre  = as.numeric(CUXOS_pre),
-    post = as.numeric(CUXOS_post),
-    Disorder = Disorder_treat
-  ) |>
-  select(
-    ID1,pre,post,Disorder
-  ) |>
-  filter(!is.na(pre),
-         !is.na(post),
-         pre > 20)
-
-RCI_df_dep <- data.frame(RCI_df_dep)
-RCI_df_anx <- data.frame(RCI_df_anx)
-
-JTRCI (data = RCI_df_anx, 
-       pre = "pre", 
-       post = "post", 
-       ppid = "ID1", 
-       reliability = .9, 
-       indextype = "JT", 
-       JTcrit = 20,
-       group = "Disorder",
-       facetplot = T,
-       plottitle = "Anxeity: JT indices by disorder")
-
-JTRCI(data = df, pre = "pre", post = "post",  group = "group", ppid = "ppid",
-      reliability = .8, indextype = "JT", JTcrit = "C",
-       normM = 30, normSD = 5, dysfM = 60, dysfSD = 5, 
-      facetplot = T, plottitle = "JT indices by group:")
-```
-
 What Doug Wants
@@
 ### The overall breakdown of patients’ demographics and diagnoses. 
-###	The trajectories of depression and anxiety for all patients (both numerical – pre/post scores, overall slope, and visual – graphs).
-Numerical results are in text, visual results presented to supplement.
-- Broken down by treatment duration, treatment track, most common primary diagnoses.
-###	The pre-post scores (numerical and visual) for RDQ subscales.
-###	Reasons for discharge (numerical and visual).
-
-# Visualizations
-### Table – Demographics
-### Table – Diagnoses
+Table – Demographics
+Table – Diagnoses
 ```{r}
@@
          !is.na(Disorder_Type),
-         !is.na(Relationship_1),
-
+         !is.na(Relationship_1)
         )
@@
 ```
+
+###	The trajectories of depression and anxiety for all patients (both numerical – pre/post scores, overall slope, and visual – graphs).
+Numerical results are in text, visual results presented to supplement.
+
+Dumbell Plot by Disorder
+```{r}
+AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
+                                  Mothership_post$Disorder_Type,
+                                  Mothership_post$pre_anx,
+                                  Mothership_post$post_anx,
+                                  Mothership_post$pre_dep,
+                                  Mothership_post$post_dep)) 
+  # filter(!is.na(Mothership_post$Disorder_Type))
+colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post")
+
+Pre_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
+Plot_Text
+
+"#aeb6bf"
+
+ggplot(data=Pre_ANX,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUXOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
+  scale_y_reverse(limits = c(45,15)) +
+  coord_flip() +
+  theme_classic()+
+  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
+      c("1" = "Non-Responders", 
+        "2" = "Responders")
+  ))
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+
+#sum(as.factor(ANX_PrePost$Disorder_Type))
+
+Pre_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+ggplot(data=Pre_DEP,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUDOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
+       ylab = "Disorder Type")+
+  scale_y_reverse(limits = c(45,15)) +
+  coord_flip() +
+  theme_classic()+
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+```
+
+### Overall Plot
+```{r}
+# Pre Post CUDOS/CUXOS Plot
+ggplot(data=AnxDep_PrePost_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Test,color=fct_rev(Test)))+
+  geom_point(size=2.5)+
+  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS/CUXOS Score")+
+  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank())
+
+AnxDep_response_mean<-AnxDep_PrePost_Long %>%
+  filter(!is.na(RESPONDER_FIGS)) |>
+  group_by(Test,RESPONDER_FIGS,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+ggplot(data=AnxDep_response_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Test,color=fct_rev(Test)))+
+  geom_point(size=2.5) +
+  geom_line(group=AnxDep_response_mean$PrePost,size=1.5)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS/CUXOS Score")+
+  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank()) +
+  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
+      c("1" = "Non-Responders", 
+        "2" = "Responders")
+      ))
+```
+
+### Line Plot By Disorder
+```{r}
+#1. Creaate new datasets with only anxiety / depresssion
+
+ANX_PrePost<- AnxDep_PrePost_Long %>%
+  filter(Test == "CUXOS")
+
+DEP_PrePost<- AnxDep_PrePost_Long %>%
+  filter(Test == "CUDOS")
+
+#2. Create DF grouped buy disorder type
+ANX_PrePost_mean<-ANX_PrePost %>%
+  group_by(Disorder_Type,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+DEP_PrePost_mean<-DEP_PrePost %>%
+  group_by(Disorder_Type,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+#### ANX
+ggplot(data=ANX_PrePost_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_point(size=2.5)+
+  geom_line(size=1)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUXOS Score")+
+  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUXOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank())
+
+#### DEP
+ggplot(data=DEP_PrePost_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_point(size=2.5)+
+  geom_line(size=1)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS Score")+
+  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
+       subtitle = "Self report depression was assessed using the CUDOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank())
+
+### FACAT WRAP
+
+AnxDep_Treat_mean<-AnxDep_PrePost_Long %>%
+  filter(!is.na(Sig_unresponse),
+         !is.na(Disorder_Type)) |>
+  group_by(Test,Disorder_Type,Sig_unresponse,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+p <- ggplot(data=AnxDep_Treat_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Test,color=fct_rev(Test)))+
+  geom_point(size=2.5) +
+  geom_line(group=AnxDep_Treat_mean$PrePost,size=1.5)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS/CUXOS Score")+
+  labs(
+    title = "Mean Pre and Post Scores of the Anxiety and Depression",
+    subtitle = "Treatment response based upon Disorder")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank()) +
+  facet_grid(Sig_unresponse~Disorder_Type,
+             labeller = labeller(
+               Sig_unresponse = c("1" = "Non-responders", "2" = "Responders"),
+               Disorder_Type = c("1" = "Anxiety", "2" = "BPD", "3" = "Mood", "4" ="Other", "5" = "Trauma")
+      ))
+p 
+#Anxiety     BPD    Mood   Other  Trauma
+```
+
+- Broken down by treatment duration, treatment track, most common primary diagnoses.
+###	The pre-post scores (numerical and visual) for RDQ subscales.
+###	Reasons for discharge (numerical and visual).
+
+# Visualizations
+
 ### Visualization – most common diagnoses.
@@
 
+```{r}
+Mothership_Long_anx <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
+Mothership_Long_anx <- Mothership_Long_anx[order(Mothership_Long_anx$ID1),]
+
+#Create a Time Variable
+Mothership_Long_anx$TxDay <- NA
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day1_CUXOS"]<-1
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day2_CUXOS"]<-2
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day3_CUXOS"]<-3
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day4_CUXOS"]<-4
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day5_CUXOS"]<-5
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day6_CUXOS"]<-6
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day7_CUXOS"]<-7
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day8_CUXOS"]<-8
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day9_CUXOS"]<-9
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day10_CUXOS"]<-10
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day11_CUXOS"]<-11
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day12_CUXOS"]<-12
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day13_CUXOS"]<-13
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day14_CUXOS"]<-14
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day15_CUXOS"]<-15
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day16_CUXOS"]<-16
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day17_CUXOS"]<-17
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day18_CUXOS"]<-18
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day19_CUXOS"]<-19
+Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day20_CUXOS"]<-20
+
+# #Create a New Data Set with an Average Anxiety Variable
+# Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
+#   group_by(TxDay) %>%
+#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+#plot Anxiety mean with each group
+
+# New dataset for the treatment duration Anxiety plot
+Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
+  group_by(Duration,TxDay) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
+#delete weird Na values and put NA for values
+Mothership_duration_CUXOS[6:20,3] = NA
+Mothership_duration_CUXOS[37:41,3] = NA
+Mothership_duration_CUXOS[74:83,3] = NA
+Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-21),]
+Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-41),]
+Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-61),]
+Mothership_duration_CUXOS
+
+ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration,color=Duration))+
+  geom_line(size=1)+
+  geom_point()+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(5,50,by=5))+
+  scale_color_manual(values=c("#BB9D00","red",
+                              "darkred","orange"))+
+  theme(panel.background=NULL)+
+  labs(subtitle = "Broken up by Duration of Treatment")
+```
+
+```{r}
+Mothership_Long_dep <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
+Mothership_Long_dep <- Mothership_Long_dep[order(Mothership_Long_dep$ID1),]
+
+Mothership_Long_dep
+#Create a Time Variable
+Mothership_Long_dep$TxDay <- NA
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day1_CUDOS"]<-1
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day2_CUDOS"]<-2
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day3_CUDOS"]<-3
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day4_CUDOS"]<-4
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day5_CUDOS"]<-5
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day6_CUDOS"]<-6
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day7_CUDOS"]<-7
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day8_CUDOS"]<-8
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day9_CUDOS"]<-9
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day10_CUDOS"]<-10
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day11_CUDOS"]<-11
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day12_CUDOS"]<-12
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day13_CUDOS"]<-13
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day14_CUDOS"]<-14
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day15_CUDOS"]<-15
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day16_CUDOS"]<-16
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day17_CUDOS"]<-17
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day18_CUDOS"]<-18
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day19_CUDOS"]<-19
+Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day20_CUDOS"]<-20
+
+# #Create a New Data Set with an Average Anxiety Variable
+# Mothership_Mean_CUDOS<-Mothership_Long_dep %>%
+#   group_by(TxDay) %>%
+#   summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+#plot depression mean with each group
+
+# New dataset for the treatment duration depression plot
+Mothership_Mean_CUDOS<-Mothership_Long_dep %>%
+  group_by(Duration,TxDay) %>%
+  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
+
+Mothership_duration_CUDOS<-Mothership_Mean_CUDOS[1:83,]
+#delete weird Na values and put NA for values
+Mothership_duration_CUDOS[6:20,3] = NA
+Mothership_duration_CUDOS[37:41,3] = NA
+Mothership_duration_CUDOS[74:83,3] = NA
+Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-21),]
+Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-41),]
+Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-61),]
+Mothership_duration_CUDOS
+
+ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
+  geom_line(size=1)+
+  geom_point()+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  ggtitle("Mean Depression Severity During Partial Hospitalization")+
+  labs(subtitle = "Broken up by Discharge Date")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
+  scale_color_manual(values=c("skyblue","#0065A3",
+                              "navy","blue"))+
+  theme(panel.background=NULL)
+```
+
 •	Visualization – RDQ pre and post change.
@@
 library(tidyr)
-Mothership_Long_RDQ <- gather(Mothership_RDQ,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
+Mothership_Long_RDQ <- gather(Mothership_Diag_treat,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
                               factor_key = "T")
@@
 
+Mothership_Mean_RDQ[,1] = c("Coping","PMH","Functioning","WBS","Symptoms","Coping","PMH","Functioning","WBS","Symptoms")
+
+wide_rdq <- Mothership_Mean_RDQ |>
+  pivot_wider(
+    names_from = PrePost, values_from = RDQ
+  ) |>
+  select(
+    rm,Pre,Post
+  )
+
+#Table
+wide_rdq
+```
+
+```{r}
 #Pre Post RDQ Plot - combined 

### 2023-10-12 Treatment_Outcomes.Rmd
RCI treatment response figures.

@@
                                   Mothership_post$Disorder_Type,
-                                  Mothership_post$CUDOS_pre,
-                                  Mothership_post$CUDOS_post,
-                                  Mothership_post$CUXOS_pre,
-                                  Mothership_post$CUXOS_post)) %>%
+                                  Mothership_post$pre_anx,
+                                  Mothership_post$post_anx,
+                                  Mothership_post$pre_dep,
+                                  Mothership_post$post_dep)) %>%
   filter(!is.na(Mothership_post$Disorder_Type))

### 2023-11-12 Paper_stuff.Rmd
Domographic variables coding

@@
 Mothership <- mutate(Mothership, 
-                     DC_status_1 = as.factor(DC_status_1),
-                     DC_status_1 = recode(DC_status_1,
-                                          "1"="Complete",
-                                          "2"="Nearly Complete",
-                                          "3"="Insurance",
-                                          "4"="Nonatteneance",
-                                          "5"="Inappropriate",
-                                          "6"="Inpatient",
-                                          "7"="Withdrew",
-                                          "8"="Dissatisfaction",
-                                          "9"="Other"),
                      Education_1 = as.factor(Education_1),
@@
                           "1"="<Grade 12",
-                                          "2"="HS Diploma",
-                                          "3"="GED",
-                                          "4"="Some College",
-                                          "5"="Associates Degree",
+                          "2"="HS Diploma or GED",
+                          "3"="HS Diploma or GED",
+                          "4"="Some College/Associates Degree",
+                          "5"="Some College/Associates Degree",
                           "6"="Bachelors Degree",
-                                          "7"="Some Grad School",
+                          "7"="Bachelors Degree",
                           "8"="Grad Degree"),
@@
                           "3"="Other",
-                                       "4"="Unknown"),
+                          "4"="Other"),
                      Relationship_1 = as.factor(Relationship_1),
                      Relationship_1 = recode(Relationship_1,
-                                             "0"="Married",
-                                             "1"="Cohabitating",
-                                             "2"="Widowed",
-                                             "3"="Separated",
+                          "0"="Married or Cohabitating",
+                          "1"="Married or Cohabitating",
+                          "2"="Widowed or Seperated",
+                          "3"="Widowed or Separated",
                           "4"="Divorced",
-                                             "5"="Never Married"),
+                          "5"="Single or Never Married"),
                      Sexuality_1 = as.factor(Sexuality_1),
@@
                                      "5"="Other"),
-                     Education_1 = as.factor(Education_1),
-                     Education_1 = recode(Education_1,
-                                      "0"="<Grade 6", 
-                                      "1"="Grades 7-12",
-                                      "2"="HS Diploma", 
-                                      "3"="GED",
-                                      "4"="Some College",
-                                      "5"="Associates Degree",
-                                      "6"="Bachelors Degree",
-                                      "7"="Some Grad School",
-                                      "8"="Grad Degree"),
-                     DC_status_1 = as.factor(DC_status_1),
-                     DC_status_1 = recode(DC_status_1,
-                                      "1"="Treatment Complete",
-                                      "2"="Treatment Near Complete",
-                                      "3"="Insurance Stopped",
-                                      "4"="Nonattendence",
-                                      "5"="Inapproparite Language",
-                                      "6"="Transfered To Impatient",
-                                      "7"="Withdrew for External factors",
-                                      "8"="Withdrew (AMA)",
-                                      "9"="Other",
-                                      "10"="Other"),
                     DC_status_1 = as.factor(DC_status_1),
@@
                                       "7" ="Therapist",
+                                      "8"="Withdrew (AMA)",
+                                      "9"="Other",
+                                      "10"="Other",
+                                      "11"="Other",
                                       "17"="Other",
-                                      "11"="Other",
-                                      "0" ="Other"
-                    ),
+                                      "0" ="Other"),
 
@@
                                    "1582"="2014"))
+
+str(Mothership$Education_1)
 ```
@@
 #Demographic tab
-Demo_tab<-data.frame(table1::table1(~Age_1+Education_1+Race_1+Gender_1+Relationship_1, data=Demo_tab_df))
-colnames(Demo_tab) <- c("Variable","Total Sample")
+Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1, data=Demo_tab_df))
+colnames(Demo_tab) <- c("Demographic","Total Sample")
 Demo_tab
@@
        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
+           group=as.factor(Disorder_Type),color=as.factor(Disorder_Type)))+
   geom_point(size=2.5)+
@@
 AnxDep_Treat_mean<-AnxDep_PrePost_Long %>%
-  filter(!is.na(Sig_unresponse),
+  filter(!is.na(RESPONDER_FIGS),
          !is.na(Disorder_Type)) |>
-  group_by(Test,Disorder_Type,Sig_unresponse,PrePost) %>%
+  group_by(Test,Disorder_Type,RESPONDER_FIGS,PrePost) %>%
   summarise(Score=mean(Score,na.rm=TRUE))
@@
   theme(legend.title = element_blank()) +
-  facet_grid(Sig_unresponse~Disorder_Type,
+  facet_grid(RESPONDER_FIGS~Disorder_Type,
              labeller = labeller(
-               Sig_unresponse = c("1" = "Non-responders", "2" = "Responders"),
+               RESPONDER_FIGS = c("1" = "Non-responders", "2" = "Responders"),
                Disorder_Type = c("1" = "Anxiety", "2" = "BPD", "3" = "Mood", "4" ="Other", "5" = "Trauma")
@@
 ```{r}
-Mothership_Long_anx <- gather(Mothership,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
+Mothership_Long_anx <- gather(Mothership_post,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
 Mothership_Long_anx <- Mothership_Long_anx[order(Mothership_Long_anx$ID1),]
@@
   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+
+Mothership_Mean_CUXOS2 <- Mothership_Long_anx %>%
+  group_by(Duration,RESPONDER_FIGS,TxDay) %>%
+  summarise(Score=mean(CUXOS,na.rm=TRUE))
+
+View(Mothership_Mean_CUXOS2)
 
@@
 
+length of treatment based upon response?
+```{r}
+
+bg_col <- "#F9FBF2"
+# highlight_col <- "#FFAD05"
+# highlight_col <- "FF52825"
+highlight_col <- "#02d46e"
+outline_col <- "darkblue"
+dark_col <- "#333333"
+
+str(Mothership_post$Days_complete_1)
+subset(Mothership, !is.na(Gender_1))
+ggplot(
+  data = subset(Mothership_post, !is.na(RESPONDER_FIGS)),
+  mapping = aes(
+    x = Days_complete_1,
+    y = Disorder_treat,
+    group = Disorder_treat)
+  )+
+  geom_jitter(
+    size = 0.6,
+    alpha = .5,
+   colour = highlight_col
+    )+
+  geom_boxplot(
+    outlier.shape = NA,
+   colour = outline_col,
+   fill = highlight_col,
+    alpha = 0.3) +
+  scale_x_continuous(
+   breaks = c(0, 15, 30, 45, 60),
+    limits = c(0.00, 60)
+  ) +
+  facet_wrap(~RESPONDER_FIGS)
+
+      #        labeller = labeller(RESPONDER_FIGS =
+      # c("1" = "Non-Responders", 
+      #   "2" = "Responders"))
+
+summary(Mothership_post$Days_complete_1)
+
+table1(Days_complete_1, data = Mothership_post)
+#####W WHY ARE DAYS COMPLETE NOT SHOWING UP???
+
+```
+
 # Sociodemographic Visualizations

### 2023-12-29 Paper_stuff.Rmd
Updated demographic table.

@@
                      Education_1 = recode(Education_1,
+                          "0"="<Grade 12",
                           "1"="<Grade 12",
@@
                           "4"="Other"),
+                     Relationship_1 = ifelse(Relationship_1 == 8, NA, Relationship_1),
                      Relationship_1 = as.factor(Relationship_1),
@@
                           "1"="Married or Cohabitating",
-                          "2"="Widowed or Seperated",
+                          "2"="Widowed or Separated",
                           "3"="Widowed or Separated",
@@
                           "3"="BPD"),
+                     Race_1 = ifelse(Race_1 == 6, NA, Race_1),
                      Race_1 = as.factor(Race_1),
@@
 
-str(Mothership$Education_1)
 ```
@@
     ```
+
+Responders
 ```{r}
@@
 
+RCI
     ```{r}
@@
 
+AnxDep_PrePost
     ```{r}
@@
 colnames(Demo_tab) <- c("Demographic","Total Sample")
-Demo_tab
+view(Demo_tab)
 

### 2024-01-24 Paper_stuff.Rmd
Restarting paper

@@
 
-# Import data
+# Prep data for analysis
 
@@
 Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
-View(df)
+head(df)
 ```
@@
 
-```
-
-## Export as CSV
-```{r}
+####  Export as CSV
 write.csv(Mothership,"~/Desktop/Coding/data/Mothership_paper")
-```
-
-Disorder_varaibles
-```{r}
+
+####. Disorder_variables
+
 Mothership<-Mothership %>%
@@
   filter(Disorder_Type != "Mood")
-```
-
-Pre_Post
-### Extract pre/post scores
-```{r}
+
+############.          Extract pre/post scores.   ######################
+
 #1. load DF
@@
     Pre_anx <- Pre_ANX[-1]
+
     #4 Adding it back to mother ship
@@
                                 )))))))
-    ```
-
-Responders
-```{r}
+
+############                       Responder                   ############ 
 #devtools::install_github("AWKruijt/JT-RCI")
@@
 library(JTRCI)
+library(ClinicalSig)
 
 #devtools::install_github("zieglema/ClinicalSig")
-library(ClinicalSig)
-# generate some random data:
 
@@
 RCI_DF
-```
-
-RCI
-    ```{r}
+
+###############          Adding RCI to dataset       ####################
+
 Mothership_post <- Mothership_post |>
@@
 
-Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1)) |>
+RCI_DF
+
+Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
   mutate(
@@
 
-# View(Mothership_joined)
-```
-
-AnxDep_PrePost
-    ```{r}
+#############            AnxDep_PrePost                 ##################
+
 #7. create new DF with Varaibles we want
@@
 
-### Dumbell Plot by Disorder
-```{r}
-Pre_ANX<-ANX_PrePost_mean %>%
-  filter(PrePost == "Pre")
-
-Post_ANX<-ANX_PrePost_mean %>%
-  filter(PrePost == "Post")
-
-Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
-Plot_Text
-
-"#aeb6bf"
-
-ggplot(data=Pre_ANX,
-       aes(x=Disorder_Type,y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
-              size = 4, #Note that I sized the segment to fit the points
-              alpha = .5) +
-  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
-  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
-  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUXOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
-  scale_y_reverse(limits = c(45,15)) +
-  coord_flip() +
-  theme_classic()+
-  theme(#legend.position = "none",
-         plot.background = element_rect(
-      fill = "white",
-      colour = "white"))
-
-#sum(as.factor(ANX_PrePost$Disorder_Type))
-
-Pre_DEP<-DEP_PrePost_mean %>%
-  filter(PrePost == "Pre")
-
-Post_DEP<-DEP_PrePost_mean %>%
-  filter(PrePost == "Post")
-
-ggplot(data=Pre_DEP,
-       aes(x=Disorder_Type,y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
-              size = 4, #Note that I sized the segment to fit the points
-              alpha = .5) +
-  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
-  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
-  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUDOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
-       ylab = "Disorder Type")+
-  scale_y_reverse(limits = c(45,15)) +
-  coord_flip() +
-  theme_classic()+
-
-  theme(#legend.position = "none",
-         plot.background = element_rect(
-      fill = "white",
-      colour = "white"))
-```
-
-```{r}
-Mothership_post <- Mothership_post |>
-  #1. Filter out scores for people not in the program / don't have dataa
-  filter(!is.na(Days_complete_1)) |>
-    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
-  filter(!is.na(CUXOS_pre),
-         !is.na(CUXOS_post),
-         CUXOS_pre > 0,
-         CUXOS_post >= 0,
-         !is.na(CUDOS_pre),
-         !is.na(CUDOS_post),
-         CUDOS_pre > 0,
-         CUDOS_post> 0
-         ) |>
-  mutate(
-    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
-    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
-    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
-    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
-    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
-    Anx_Responder = as.factor(
-      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
-      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
-      )),
-    Dep_Responder = as.factor(
-      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
-      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
-      )),
-    Treatment_Responder = as.factor(
-      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
-      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
-      )))))))))))
-
- #CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))
-
-ggplot(Mothership_post, aes(x = Treatment_Responder)) +
-  geom_bar() +
-  coord_flip() +
-  scale_x_discrete(limits =c("Low Baseline", "Both Worse", "Dep Worse", "Anx Worse","Both Unresponder","Dep Unresponders", "Anx Unresponders","Both_Responder", "Anx Responder","Dep Responder"))+
-  labs(
-    title = "Treatment response of Anxiety and Depression",
-    subtitle = "Response = 50% reduciton in scores if BL score > 10")
-
-ggplot(Mothership_post, aes(x = Anx_Responder)) +
-  geom_bar() +
-  coord_flip() +
-    labs(
-    title = "Treatment response of Anxiety",
-    subtitle = "Response = 50% reduciton in scores if BL score > 10")
-
-ggplot(Mothership_post, aes(x = Dep_Responder)) +
-  geom_bar() +
-  coord_flip() +
-    labs(
-    title = "Treatment response of Depression",
-    subtitle = "Response = 50% reduciton in scores if BL score > 10")
-```
-
-What Doug Wants
+What I Want
 
@@
 #Demographics Table
-Demo_tab_df <- Mothership_Diag_treat |>
+Demo_tab_df <- Mothership_post |>
+  #Mothership_Diag_treat |>
   filter(!is.na(Education_1),
@@
 #Disorder Table - duratin
-Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_Diag_treat))
+Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_post))
+                                       #Mothership_Diag_treat))
 colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
@@
 #Disorder Tab by 10 days
-Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_Diag_treat))
+Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_post))
+                                      #Mothership_Diag_treat))
 colnames(Dis_tab_10) <- c("Primary Diagnosis","1-10 Days", "10+ Days", "Total Sample")
 Dis_tab_10
+
+##### Add other demographic information here
 
@@
                                   Mothership_post$pre_dep,
-                                  Mothership_post$post_dep)) 
+                                  Mothership_post$post_dep,
+                                  Mothership_post$RESPONDER_FIGS)) 
   # filter(!is.na(Mothership_post$Disorder_Type))
-colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post")
+colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","RESPONDER_FIGS)")
 
@@
 
-ggplot(data=Pre_ANX,
+ggplot(data=AnxDep_PrePost,
        aes(x=Disorder_Type,y=Score,
@@
 ```{r}
-ggplot(data = subset(Mothership, !is.na(Education_1)),mapping = aes(x = Education_1))+
+ggplot(data = subset(Mothership_post, !is.na(Education_1)),mapping = aes(x = Education_1))+
   geom_bar(color = "black",fill="darkred")+
@@
 ```{r}
-ggplot(data = subset(Mothership, !is.na(Race_1)),mapping = aes(x = Race_1))+
+ggplot(data = subset(Mothership_post, !is.na(Race_1)),mapping = aes(x = Race_1))+
   geom_bar(color = "black",fill="darkblue")+
@@
 ```{r}
-ggplot(data = subset(Mothership, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
+ggplot(data = subset(Mothership_post, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
   geom_bar(color = "black",fill="darkorange")+
@@
 
-# Pie Chart For Education Status 
-We wanted to learn how to make a pie chart in R so here is one!
-```{r}
-#Create Table and Data Frame
-Education<-table(Mothership$Education_1)
-Education_df<-as.data.frame(Education)
-Education_df
-
-#Rename Columns
-colnames(Education_df)[1]="Category"
-colnames(Education_df)[2]="Frequency"
-
-Education_df$Category=recode(Education_df$Category,
-                             "0"="<Grade 6", 
-                             "1"="Grades 7-12",
-                             "2"="HS Diploma", 
-                             "3"="GED",
-                             "4"="Some College",
-                             "5"="Associates Degree",
-                             "6"="Bachelors Degree",
-                             "7"="Some Grad School",
-                             "8"="Grad Degree")
-
-ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
-  geom_bar(stat="Identity",width=1,color="white")+
-  ggtitle("Education Level of Patients") +
-  scale_fill_discrete(name = "Education") +
-  coord_polar("y",start=0)+
-  theme_void()
-```
-
 # Treatment Related Visualizations
@@
 
-ggplot(data = subset(Mothership, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
+ggplot(data = subset(Mothership_post, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
   geom_bar(color = "black",fill="skyblue")+
@@
 
-ggplot(data = subset(Mothership, !is.na(TxYear)),mapping = aes(x = TxYear))+
+ggplot(data = subset(Mothership_post, !is.na(TxYear)),mapping = aes(x = TxYear))+
   geom_bar(color = "black",fill="#9350C7")+
@@
 ### Duration of Treatment ###
-ggplot(data = subset(Mothership, !is.na(Duration)),mapping = aes(x = Duration))+
+ggplot(data = subset(Mothership_post, !is.na(Duration)),mapping = aes(x = Duration))+
   geom_bar(color = "black",fill="lightgreen")+

### 2024-01-30 Lasso_RCI_Response.Rmd
Adding new RMD with stuff just for LAsso responder paper

--- 2024-01-24 Paper_stuff.Rmd
@@
 ---
-title: "Paper_stuff"
+title: "Lasso_RCI_Response"
+author: Troy Hubert
 output: html_document
-date: "2023-09-12"
+date: "2024-01-28"
 ---
@@
 
-Read in the dataset. 
+## Read in the dataset. 
 ```{r}
@@
 head(df)
-```
-
-## Rename and Recode variables 
-We can change the current variables to make them easier to interpret. 
-```{r}
+
+# source("~/Desktop/Coding/R working directory/Hospital_Visualizations/Lasso_RCI_Source.R")
+```
+
+## Clean, update, and wrangle data
+
+The code below reads in the data frame, and prepares df for analysis.
+
+this includes:
+  1 Re-coding / Renaming variables
+  2 Creating new Diagnostic variables 
+  3 Functions to create Pre - post scores 
+  4 RCI Analysis categorization
+  5 Pre - Post long data sets
+
+```{r}
+# 1. Re-coding / Renaming variables ------------------------------------------
+# We can change the current variables to make them easier to interpret.
+
 #recode varaibles
@@
                      DC_status_1 = recode(DC_status_1,
+                                          "1" ="Treatment Complete",
+                                          "2" ="Treatment nearly complete",
+                                          "3" ="Insurance no longer covering",
+                                          "4" ="Nonattendance",
+                                          "5" ="Inappropriate (language)/Referred to another tx setting",
+                                          "6" ="Transferred to inpatient",
+                                          "7" ="Withdrew due to external limitations",
+                                          "8"= "Withdrew AMA",
+                                          "9"= "Other",
+                                          "10"="Other",
+                                          "0" ="Other"),
+                     Referral_1 = as.factor(Referral_1),
+                     Referral_1 = recode(Referral_1,
                                          "1" ="Inpatient",
@@
                                          "7" ="Therapist",
-                                      "8"="Withdrew (AMA)",
-                                      "9"="Other",
-                                      "10"="Other",
-                                      "11"="Other",
                                          "17"="Other",
@@
 
-####. Disorder_variables
+# 2. Creating new diagnostic variables  -----------------------------------
 
@@
                Trauma_C == 1 & Somatic_D ==1 |
-                                Trauma_C == 1 & Psychotic_D ==1, 1, 0))
+               Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
   )
@@
 
-# df with and without depression
-No_depressy <- Mothership_Diag %>%
-  filter(Disorder_Type != "Mood")
-
-############.          Extract pre/post scores.   ######################
+# 3. Functions to create Pre - post scores -----------------------------------
 
@@
 
-    # Depressiopn
+  # Depression
     CUDOS_Score_post <-  select(Mothership_post, dummy,Day1_CUDOS:Day40_CUDOS)
@@
         CUXOS_post = ifelse(CUXOS_post < 0, NA, CUXOS_post),
+#5 Making some other varaibles
         BL_Missing = as.factor(ifelse(is.na(BL_CUXOS), "Anx Missing",
@@
                                              )))),
-        Any_Sig_Post = as.factor(ifelse(CUXOS_post > 20 | CUDOS_post > 20, "Sig",
-                               ifelse(is.na(CUXOS_post),NA,
-                               ifelse(is.na(CUDOS_post),NA, "Sub"
-                               )))),
         Sig_BL = as.factor(ifelse(BL_CUXOS > 20 & BL_CUDOS > 20, "Sig Both",
@@
                                                        ifelse(is.na(BL_CUXOS), NA, "Subclinical"
-                        )))))),
-        Sig_Post = as.factor(ifelse(CUXOS_post > 20 & CUDOS_post > 20, "Sig Both",
-                 ifelse(CUXOS_post > 20, "Sig Anx",
-                 ifelse(CUDOS_post > 20, "Sig Dep",
-                 ifelse(is.na(CUDOS_post), NA,
-                 ifelse(is.na(CUXOS_post), NA, "Subclinical"
-                        )))))),
-        Sig_unresponse_type = as.factor(ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post == "Subclinical", "Responder",
-                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Both", "Non-responder",
-                            ifelse(Sig_BL == "Sig Anx" & Sig_Post == "Sig Anx", "Non-responder",
-                            ifelse(Sig_BL == "Sig Dep" & Sig_Post == "Sig Dep", "Non-responder",
-                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Anx", "Dep gone Anx not",
-                            ifelse(Sig_BL == "Sig Both" & Sig_Post == "Sig Dep", "Anx gone Dep not", 
-                            ifelse(ifelse(Sig_BL == "Subclinical" & Sig_Post == "Subclinical", "Low_BL",       
-                                   NA
-                            ))))))))),
-        Sig_unresponse = as.factor(ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post == "Subclinical", "Responder",
-                                        ifelse(Sig_BL %in% c("Sig Both","Sig Anx","Sig Dep") & Sig_Post %in% c("Sig Both","Sig Anx","Sig Dep"), "Non-responder",
-                                        ifelse(ifelse(Sig_BL == "Subclinical" & Sig_Post == "Subclinical", "Low_BL",       
-                                   NA
-                                   ))))),
-
-              #deprssion values Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)"
-        BL_Dep_level = as.factor(ifelse(BL_CUDOS > 10 & BL_CUDOS <= 20, "Minimal",
-                                 ifelse(BL_CUDOS > 20 & BL_CUDOS <= 30, "Mild",
-                                 ifelse(BL_CUDOS > 10 & BL_CUDOS <= 45, "Moderate",
-                                 ifelse(BL_CUDOS > 45, "Severe",
-                                 ifelse(is.na(BL_CUDOS), NA, "Remission"
-                                )))))),
-        BL_Anx_level = as.factor(ifelse(BL_CUXOS > 10 & BL_CUXOS <= 20, "Minimal",
-                                 ifelse(BL_CUXOS > 20 & BL_CUXOS <= 30, "Mild",
-                                 ifelse(BL_CUXOS > 10 & BL_CUXOS <= 45, "Moderate",
-                                 ifelse(BL_CUXOS > 45, "Severe",
-                                 ifelse(is.na(BL_CUXOS), NA, "Remission"
-                                )))))),
-        Post_Dep_level = as.factor(ifelse(CUDOS_post > 10 & CUDOS_post <= 20, "Minimal",
-                                 ifelse(CUDOS_post > 20 & CUDOS_post <= 30, "Mild",
-                                 ifelse(CUDOS_post > 10 & CUDOS_post <= 45, "Moderate",
-                                 ifelse(CUDOS_post > 45, "Severe",
-                                 ifelse(is.na(CUDOS_post), NA, "Remission"
-                                )))))),
-        Post_Anx_level = as.factor(ifelse(CUXOS_post > 10 & CUXOS_post <= 20, "Minimal",
-                                 ifelse(CUXOS_post > 20 & CUXOS_post <= 30, "Mild",
-                                 ifelse(CUXOS_post > 10 & CUXOS_post <= 45, "Moderate",
-                                 ifelse(CUXOS_post > 45, "Severe",
-                                 ifelse(is.na(CUXOS_post), NA, "Remission"
-                                )))))))
-
-############                       Responder                   ############ 
+                                                       ))))))
+)
+
+# 4. RCI Analysis categorization ------------------------------------------
+
 #devtools::install_github("AWKruijt/JT-RCI")
@@
 #devtools::install_github("zieglema/ClinicalSig")
-
+#1. Create df for RCI
 RCI_df_dep <- Mothership_post |>
@@
 Mothership_post <- Mothership_post |>
-  #1. Filter out scores for people not in the program / don't have dataa
+  #1. Filter out scores for people not in the program / don't have data
   filter(!is.na(Days_complete_1)) |>
@@
 
-RCI_DF
-
+#2. Left join data from the RCI dataset into the Mothership_post df
 Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
@@
              ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
-        )))
+      ))) |>
+  filter(!is.na(RESPONDER_FIGS))
 
@@
   summarise(Score=mean(Score,na.rm=TRUE))
-
-#table1::table1(~BL_CUXOS + BL_CUDOS + SUManx_DC + SUMdep_DC + CUDOS_post +CUXOS_post, data = Mothership_post)
-
-```
-
-What I Want
-
-# Results
-### The overall breakdown of patients’ demographics and diagnoses. 
-Table – Demographics
-Table – Diagnoses
+```
+
+## Part 1: Who is attending?
+- Table 1 Demographics By Response
+- Table 2: Treatment information - What did treatment look like?
+- Table 3: Scores on measures pre post change? 
+    + I want to show the figure of prepost change???
+- Table 4: demographic breakdown
 ```{r}
@@
          !is.na(Disorder_Type),
-         !is.na(Relationship_1)
+         !is.na(Relationship_1),
+         !is.na(RESPONDER_FIGS)
         )
@@
 #Demographic tab
-Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1, data=Demo_tab_df))
-colnames(Demo_tab) <- c("Demographic","Total Sample")
-view(Demo_tab)
-
-#Disorder Table - duratin
-Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_post))
-                                       #Mothership_Diag_treat))
-colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
+Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
+colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
+Demo_tab
+
+# Treatment info
+resp_tab <- data.frame(table1::table1(
+  ~Referral_1 + DC_status_1 + RIPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
+  data = Mothership_post))
+colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
+resp_tab
+
+# Disorders by treatment response
+Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | RESPONDER_FIGS, 
+                                     data = Mothership_post))
 Dis_tab
 
-#Disorder Tab by 10 days
-Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_post))
-                                      #Mothership_Diag_treat))
-colnames(Dis_tab_10) <- c("Primary Diagnosis","1-10 Days", "10+ Days", "Total Sample")
-Dis_tab_10
-
-##### Add other demographic information here
-
-```
-
-###	The trajectories of depression and anxiety for all patients (both numerical – pre/post scores, overall slope, and visual – graphs).
-Numerical results are in text, visual results presented to supplement.
-
-Dumbell Plot by Disorder
-```{r}
-AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
-                                  Mothership_post$Disorder_Type,
-                                  Mothership_post$pre_anx,
-                                  Mothership_post$post_anx,
-                                  Mothership_post$pre_dep,
-                                  Mothership_post$post_dep,
-                                  Mothership_post$RESPONDER_FIGS)) 
-  # filter(!is.na(Mothership_post$Disorder_Type))
-colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","RESPONDER_FIGS)")
-
-Pre_ANX<-ANX_PrePost_mean %>%
-  filter(PrePost == "Pre")
-
-Post_ANX<-ANX_PrePost_mean %>%
-  filter(PrePost == "Post")
-
-Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
-Plot_Text
-
-"#aeb6bf"
-
-ggplot(data=AnxDep_PrePost,
-       aes(x=Disorder_Type,y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
-              size = 4, #Note that I sized the segment to fit the points
-              alpha = .5) +
-  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
-  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
-  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUXOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
-  scale_y_reverse(limits = c(45,15)) +
-  coord_flip() +
-  theme_classic()+
-  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
-      c("1" = "Non-Responders", 
-        "2" = "Responders")
-  ))
-  theme(#legend.position = "none",
-         plot.background = element_rect(
-      fill = "white",
-      colour = "white"))
-
-#sum(as.factor(ANX_PrePost$Disorder_Type))
-
-Pre_DEP<-DEP_PrePost_mean %>%
-  filter(PrePost == "Pre")
-
-Post_DEP<-DEP_PrePost_mean %>%
-  filter(PrePost == "Post")
-
-ggplot(data=Pre_DEP,
-       aes(x=Disorder_Type,y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
-              size = 4, #Note that I sized the segment to fit the points
-              alpha = .5) +
-  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
-  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
-  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUDOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
-       ylab = "Disorder Type")+
-  scale_y_reverse(limits = c(45,15)) +
-  coord_flip() +
-  theme_classic()+
-  theme(#legend.position = "none",
-         plot.background = element_rect(
-      fill = "white",
-      colour = "white"))
-```
-
-### Overall Plot
-```{r}
-# Pre Post CUDOS/CUXOS Plot
-ggplot(data=AnxDep_PrePost_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Test,color=fct_rev(Test)))+
-  geom_point(size=2.5)+
-  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUDOS/CUXOS Score")+
-  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank())
+#Full demographic break down.
+CODis_tab<-data.frame(table1::table1(~`Co Occuring` | Disorder_treat, data = co_dis_tab))
+CODis_tab
+
+Mothership_post$Current_Dx
+```
+
+```{r}
+#Treatment Scores
+
+  # I'm imagining a table that has all of the averages under 3 columns 
+      # Pre, post, delta | (mean, SD)
+  # variables involved = 
+      # CUXOS, CUDOS, RDQ, 
+  # can I make this break up by treatment response?
+
+resp_tab <- data.frame(table1::table1(
+  ~CUXOS_pre + CUXOS_post + Delta_Anx_DC + CUXOS_pre + CUXOS_post + Delta_Anx_DC +   | RESPONDER_FIGS, 
+  data = Mothership_post))
+colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
+resp_tab
+
+View(Mothership_post)
+
+#Read in a New Data Set
+Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
+Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
+Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))
+
+#Make This Data Set Long Data
+library(tidyr)
+Mothership_Long_RDQ <- gather(Mothership_Diag_treat,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
+                              factor_key = "T")
+Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]
+
+#Create a Time Variable
+Mothership_Long_RDQ$PrePost <- NA
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_coping"]<-"Pre"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_pmh"]<-"Pre"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_func"]<-"Pre"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_wbs"]<-"Pre"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_sym"]<-"Pre"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_coping"]<-"Post"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_pmh"]<-"Post"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_func"]<-"Post"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_wbs"]<-"Post"
+Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_sym"]<-"Post"
+
+#Create a New Data Set with an Average Depression Variable and Race
+Mothership_Mean_RDQ<-Mothership_Long_RDQ %>%
+  group_by(rm,PrePost) %>%
+  summarise(RDQ=mean(RDQ,na.rm=TRUE))
+
+#Add a Paired Variable to the New Data Set
+Mothership_Mean_RDQ<-mutate(Mothership_Mean_RDQ,
+                            paired=case_when(rm=="rdqPRE_coping"~"1",
+                                             rm=="rdqPOST_coping"~"1",
+                                             rm=="rdqPRE_pmh"~"2",
+                                             rm=="rdqPOST_pmh"~"2",
+                                             rm=="rdqPRE_func"~"3",
+                                             rm=="rdqPOST_func"~"3",
+                                             rm=="rdqPRE_wbs"~"4",
+                                             rm=="rdqPOST_wbs"~"4",
+                                             rm=="rdqPRE_sym"~"5",
+                                             rm=="rdqPOST_sym"~"5"))
+
+Mothership_Mean_RDQ[,1] = c("Coping","PMH","Functioning","WBS","Symptoms","Coping","PMH","Functioning","WBS","Symptoms")
+
+wide_rdq <- Mothership_Mean_RDQ |>
+  pivot_wider(
+    names_from = PrePost, values_from = RDQ
+  ) |>
+  select(
+    rm,Pre,Post
+  )
+
+#Table
+wide_rdq
+
+```
+
+Figure 1: Pre-post Line Plot
+```{r}
 
@@
 
-### Line Plot By Disorder
-```{r}
-#1. Creaate new datasets with only anxiety / depresssion
-
-ANX_PrePost<- AnxDep_PrePost_Long %>%
-  filter(Test == "CUXOS")
-
-DEP_PrePost<- AnxDep_PrePost_Long %>%
-  filter(Test == "CUDOS")
-
-#2. Create DF grouped buy disorder type
-ANX_PrePost_mean<-ANX_PrePost %>%
-  group_by(Disorder_Type,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
-
-DEP_PrePost_mean<-DEP_PrePost %>%
-  group_by(Disorder_Type,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
-
-#### ANX
-ggplot(data=ANX_PrePost_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_point(size=2.5)+
-  geom_line(size=1)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUXOS Score")+
-  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUXOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank())
-
-#### DEP
-ggplot(data=DEP_PrePost_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=as.factor(Disorder_Type),color=as.factor(Disorder_Type)))+
-  geom_point(size=2.5)+
-  geom_line(size=1)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUDOS Score")+
-  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
-       subtitle = "Self report depression was assessed using the CUDOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank())
-
-### FACAT WRAP
-
-AnxDep_Treat_mean<-AnxDep_PrePost_Long %>%
-  filter(!is.na(RESPONDER_FIGS),
-         !is.na(Disorder_Type)) |>
-  group_by(Test,Disorder_Type,RESPONDER_FIGS,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
-
-p <- ggplot(data=AnxDep_Treat_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Test,color=fct_rev(Test)))+
-  geom_point(size=2.5) +
-  geom_line(group=AnxDep_Treat_mean$PrePost,size=1.5)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUDOS/CUXOS Score")+
-  labs(
-    title = "Mean Pre and Post Scores of the Anxiety and Depression",
-    subtitle = "Treatment response based upon Disorder")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank()) +
-  facet_grid(RESPONDER_FIGS~Disorder_Type,
-             labeller = labeller(
-               RESPONDER_FIGS = c("1" = "Non-responders", "2" = "Responders"),
-               Disorder_Type = c("1" = "Anxiety", "2" = "BPD", "3" = "Mood", "4" ="Other", "5" = "Trauma")
-      ))
-p 
-#Anxiety     BPD    Mood   Other  Trauma
-```
-
-- Broken down by treatment duration, treatment track, most common primary diagnoses.
-###	The pre-post scores (numerical and visual) for RDQ subscales.
-###	Reasons for discharge (numerical and visual).
-
-# Visualizations
-
-### Visualization – most common diagnoses.
-```{r}
-#frequency
-
-ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping =  aes(x = fct_rev(fct_infreq(Disorder_Type))))+
-  geom_bar(fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"
-                               ))+
-  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1),
-        legend.position = "none")+
-  xlab("Psychiatric Disorder Subtype")+
-  #scale_fill_manual(values = c("#003f5c","#2f4b7c","#665191", "#a05195", "#d45087", "#f95d6a", "#ff7c43", "#ffa600", "#EBC500")) +
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,4300))+
-  coord_flip()
-
-ggplot(data = subset(Mothership_Diag, !is.na(Disorder_Type)),mapping =  aes(x = fct_rev(fct_infreq(Disorder_Type)),fill= Disorder_Type))+
-  geom_bar()+
-  ggtitle("Frequency of Psychiatric Disorder Subtypes") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1),
-        legend.position = "none")+
-  xlab("Psychiatric Disorder Subtype")+
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,1750))+
-  scale_fill_manual(values = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"
-                               )) +
-  coord_flip()+
-  facet_wrap(~Duration,labeller = labeller(Duration =
-      c("1" = "1-5 Days", 
-        "2" = "6-10 Days", 
-        "3" = "11-15 Days",
-        "4" = "16+ Days")
-      ))
-```
-
-# Most co-ocurring diagnoses
-```{r}
-# Visualization of percent
-
-Mothership_current_Imp <- Mothership_Diag_treat %>%
-  pivot_longer(
-    cols=c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
-    names_to = 'Disorder_Present') %>%
-  filter(value != 0) %>%
-  select(!value)  %>%
-  filter(!is.na(Disorder_Present))%>%
-  filter(!is.na(Disorder_treat))
-
-co_dis_tab <- Mothership_Diag_treat |>
-  pivot_longer(
-    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
-    names_to = 'Co Occuring',
-    values_to = "Number"
-  ) |>
-  select(Disorder_treat, `Co Occuring`, Number) |>
-  filter(Number != 0,
-         !is.na(`Co Occuring`),
-         !is.na(Disorder_treat))
-
-tabs<-as.data.frame.matrix(xtabs(~ Disorder_Present + Disorder_treat, data = Mothership_current_Imp))
-
-anx<-summary(Mothership_Diag_treat$Anxiety_D)[2]
-bpd<-summary(Mothership_Diag_treat$BPD_P)[2]
-mood<-summary(Mothership_Diag_treat$Mood_D)[2]
-trauma<-summary(Mothership_Diag_treat$Trauma_D)[2]
-other<-summary(Mothership_Diag_treat$Other)[2]
-
-tabs[,1] <- (tabs[,1] / anx)*100
-tabs[,2] <- (tabs[,2] /bpd)*100
-tabs[,3] <- (tabs[,3] /mood)*100
-tabs[,4] <- (tabs[,4] /other)*100
-tabs[,5] <- (tabs[,5] /trauma)*100
-tabs[,6] <- c("Anxiety","BPD","Eating","Mood","OCD","Psychotic","Somatic", "Substance","Trauma", "None")
-colnames(tabs)[6] = "Disorder"
-tabs
-
-CODis_tab<-data.frame(table1::table1(~`Co Occuring` | Disorder_treat, data = co_dis_tab))
-CODis_tab
-
-p <- Mothership_current_Imp %>%
-  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
-  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .75)+
- scale_size_area(max_size = 30)+
-  scale_colour_manual(values = c("#ffa600","#ff6361","#bc5090","#58508d","#003f5c"))+
-  #scale_size_continuous(range = c(10, 30)) +
-  theme_classic() +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1),
-    legend.position = "none") +
-  scale_y_discrete(labels=c("Other_Co" = "Other",
-                            "No_Co" = "None",
-                            "BPD_Co_C" = "BPD",
-                            "Trauma_C" = "Trauma", 
-                            "Substance_C" = "Substance Use",
-                            "Mood_C" = "Mood",
-                            "Anxiety_C" = "Anxiety")) +
-  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
-    subtitle = "Grouped into subtypes of DSM diagonsis",
-    y = "Co-Occuring Psychiatric Disorder",
-    x = "Primary Psychiatric Diagnosis")
-
-p
-```
-
-•	Visualizations – CUDOS and CUXOS trajectories by treatment duration, treatment track, most common diagnoses.
-
-### plot means based upon duration group membership
-
-```{r}
-Mothership_Long_anx <- gather(Mothership_post,rm,CUXOS,Day1_CUXOS:Day40_CUXOS,factor_key = "T")
-Mothership_Long_anx <- Mothership_Long_anx[order(Mothership_Long_anx$ID1),]
-
-#Create a Time Variable
-Mothership_Long_anx$TxDay <- NA
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day1_CUXOS"]<-1
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day2_CUXOS"]<-2
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day3_CUXOS"]<-3
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day4_CUXOS"]<-4
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day5_CUXOS"]<-5
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day6_CUXOS"]<-6
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day7_CUXOS"]<-7
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day8_CUXOS"]<-8
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day9_CUXOS"]<-9
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day10_CUXOS"]<-10
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day11_CUXOS"]<-11
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day12_CUXOS"]<-12
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day13_CUXOS"]<-13
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day14_CUXOS"]<-14
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day15_CUXOS"]<-15
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day16_CUXOS"]<-16
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day17_CUXOS"]<-17
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day18_CUXOS"]<-18
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day19_CUXOS"]<-19
-Mothership_Long_anx$TxDay[Mothership_Long_anx$rm=="Day20_CUXOS"]<-20
-
-# #Create a New Data Set with an Average Anxiety Variable
-# Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
-#   group_by(TxDay) %>%
-#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-#plot Anxiety mean with each group
-
-# New dataset for the treatment duration Anxiety plot
-Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
-  group_by(Duration,TxDay) %>%
-  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-Mothership_Mean_CUXOS2 <- Mothership_Long_anx %>%
-  group_by(Duration,RESPONDER_FIGS,TxDay) %>%
-  summarise(Score=mean(CUXOS,na.rm=TRUE))
-
-View(Mothership_Mean_CUXOS2)
-
-Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
-#delete weird Na values and put NA for values
-Mothership_duration_CUXOS[6:20,3] = NA
-Mothership_duration_CUXOS[37:41,3] = NA
-Mothership_duration_CUXOS[74:83,3] = NA
-Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-21),]
-Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-41),]
-Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-61),]
-Mothership_duration_CUXOS
-
-ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration,color=Duration))+
-  geom_line(size=1)+
-  geom_point()+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
-  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Anxiety Severity",limits=c(5,50,by=5))+
-  scale_color_manual(values=c("#BB9D00","red",
-                              "darkred","orange"))+
-  theme(panel.background=NULL)+
-  labs(subtitle = "Broken up by Duration of Treatment")
-```
-
-```{r}
-Mothership_Long_dep <- gather(Mothership,rm,CUDOS,Day1_CUDOS:Day40_CUDOS,factor_key = "T")
-Mothership_Long_dep <- Mothership_Long_dep[order(Mothership_Long_dep$ID1),]
-
-Mothership_Long_dep
-#Create a Time Variable
-Mothership_Long_dep$TxDay <- NA
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day1_CUDOS"]<-1
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day2_CUDOS"]<-2
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day3_CUDOS"]<-3
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day4_CUDOS"]<-4
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day5_CUDOS"]<-5
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day6_CUDOS"]<-6
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day7_CUDOS"]<-7
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day8_CUDOS"]<-8
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day9_CUDOS"]<-9
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day10_CUDOS"]<-10
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day11_CUDOS"]<-11
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day12_CUDOS"]<-12
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day13_CUDOS"]<-13
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day14_CUDOS"]<-14
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day15_CUDOS"]<-15
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day16_CUDOS"]<-16
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day17_CUDOS"]<-17
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day18_CUDOS"]<-18
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day19_CUDOS"]<-19
-Mothership_Long_dep$TxDay[Mothership_Long_dep$rm=="Day20_CUDOS"]<-20
-
-# #Create a New Data Set with an Average Anxiety Variable
-# Mothership_Mean_CUDOS<-Mothership_Long_dep %>%
-#   group_by(TxDay) %>%
-#   summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-#plot depression mean with each group
-
-# New dataset for the treatment duration depression plot
-Mothership_Mean_CUDOS<-Mothership_Long_dep %>%
-  group_by(Duration,TxDay) %>%
-  summarise(mean_CUDOS=mean(CUDOS,na.rm=TRUE))
-
-Mothership_duration_CUDOS<-Mothership_Mean_CUDOS[1:83,]
-#delete weird Na values and put NA for values
-Mothership_duration_CUDOS[6:20,3] = NA
-Mothership_duration_CUDOS[37:41,3] = NA
-Mothership_duration_CUDOS[74:83,3] = NA
-Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-21),]
-Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-41),]
-Mothership_duration_CUDOS<-Mothership_duration_CUDOS[(-61),]
-Mothership_duration_CUDOS
-
-ggplot(data=Mothership_duration_CUDOS,aes(x=TxDay,y=mean_CUDOS,group=Duration,color=Duration))+
-  geom_line(size=1)+
-  geom_point()+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  ggtitle("Mean Depression Severity During Partial Hospitalization")+
-  labs(subtitle = "Broken up by Discharge Date")+
-  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
-  scale_y_continuous(name="Depression Severity",limits=c(15,40,by=5))+
-  scale_color_manual(values=c("skyblue","#0065A3",
-                              "navy","blue"))+
-  theme(panel.background=NULL)
-```
-
-•	Visualization – RDQ pre and post change.
-
-```{r}
-#Read in a New Data Set
-Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
-Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
-Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))
-
-#Make This Data Set Long Data
-library(tidyr)
-Mothership_Long_RDQ <- gather(Mothership_Diag_treat,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
-                              factor_key = "T")
-Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]
-
-#Create a Time Variable
-Mothership_Long_RDQ$PrePost <- NA
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_coping"]<-"Pre"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_pmh"]<-"Pre"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_func"]<-"Pre"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_wbs"]<-"Pre"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_sym"]<-"Pre"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_coping"]<-"Post"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_pmh"]<-"Post"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_func"]<-"Post"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_wbs"]<-"Post"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_sym"]<-"Post"
-
-#Create a New Data Set with an Average Depression Variable and Race
-Mothership_Mean_RDQ<-Mothership_Long_RDQ %>%
-  group_by(rm,PrePost) %>%
-  summarise(RDQ=mean(RDQ,na.rm=TRUE))
-
-#Add a Paired Variable to the New Data Set
-Mothership_Mean_RDQ<-mutate(Mothership_Mean_RDQ,
-                            paired=case_when(rm=="rdqPRE_coping"~"1",
-                                             rm=="rdqPOST_coping"~"1",
-                                             rm=="rdqPRE_pmh"~"2",
-                                             rm=="rdqPOST_pmh"~"2",
-                                             rm=="rdqPRE_func"~"3",
-                                             rm=="rdqPOST_func"~"3",
-                                             rm=="rdqPRE_wbs"~"4",
-                                             rm=="rdqPOST_wbs"~"4",
-                                             rm=="rdqPRE_sym"~"5",
-                                             rm=="rdqPOST_sym"~"5"))
-
-Mothership_Mean_RDQ[,1] = c("Coping","PMH","Functioning","WBS","Symptoms","Coping","PMH","Functioning","WBS","Symptoms")
-
-wide_rdq <- Mothership_Mean_RDQ |>
-  pivot_wider(
-    names_from = PrePost, values_from = RDQ
-  ) |>
-  select(
-    rm,Pre,Post
-  )
-
-#Table
-wide_rdq
-```
-
-```{r}
-#Pre Post RDQ Plot - combined 
-ggplot(data=Mothership_Mean_RDQ,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
-           group=rm,color=paired,!is.na(PrePost)))+
-  geom_point(size=2.5)+
-  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="RDQ Subscore")+
-  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank())+
-  # scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
-  #                              "4"="#00BCA3","5"="#008570"),
-  scale_colour_manual(values = c("#ffa600","#ff6361","#bc5090","#58508d","#003f5c"),
-                     labels=c("Coping Skills","Positive Mental Health",
-                              "Functioning","Well-Being","Symptoms"))
-
-# pre post RDQ Plot - facet wrap
-ggplot(data=Mothership_Mean_RDQ,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=RDQ,
-           group=rm,color=paired,!is.na(PrePost))) +
-  geom_point(size=2.5) +
-  geom_line(group=Mothership_Mean_RDQ$paired,size=1.5) +
-  scale_x_discrete(name="Time Point") +
-  scale_y_continuous(name="RDQ Subscore",limits = c(0, 40)) +
-  ggtitle("Mean Pre and Post Scores of the Remission from Depression Questionnaire") +
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2)) +
-  theme(panel.background=NULL) +
-  theme(legend.position="none") +
-  # scale_color_manual(values=c("1"="#8956BB","2"="#4C4452","3"="#B1A8B9",
-  #                              "4"="#00BCA3","5"="#008570")) +
-  scale_colour_manual(values = c("#ffa600","#ff6361","#bc5090","#58508d","#003f5c"))+
-  facet_wrap(~paired, labeller = labeller(paired =
-    c("1" = "Coping Skills",
-      "2"="Positive Mental Health",
-      "3"="Functioning",
-      "4"="Well-Being",
-      "5"="Symptoms")))
-
-```
-
-•	Table or Visualization – Reasons for discharge results.
-
-### Discharge Status
-```{r}
-### Bar Chart for Discharge Status ###
-
-ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = fct_rev(fct_infreq(DC_status_1))))+
-  geom_bar(fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"
-                               ))+
-  ggtitle("Frequency of Treatment Discharge Status") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Discharge Status") +
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6000)) +
-  coord_flip()
-
-ggplot(data = subset(Mothership, !is.na(DC_status_1)), mapping = aes(x = fct_rev(fct_infreq(DC_status_1))))+
-  geom_bar()+ #fill = c("#EBC500", "#ffa600", "#ff7c43", "#f95d6a", "#d45087","#a05195","#665191","#2f4b7c","#003f5c"))+
-  ggtitle("Frequency of Treatment Discharge Status") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Discharge Status") +
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,2100)) +
-  #scale_fill_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) +
-  coord_flip() +
-  facet_wrap(~Duration,labeller = labeller(Duration =
-      c("1" = "1-5 Days", 
-        "2" = "6-10 Days", 
-        "3" = "11-15 Days",
-        "4" = "16+ Days")
-      ))
-
-```
-
-length of treatment based upon response?
-```{r}
-
-bg_col <- "#F9FBF2"
-# highlight_col <- "#FFAD05"
-# highlight_col <- "FF52825"
-highlight_col <- "#02d46e"
-outline_col <- "darkblue"
-dark_col <- "#333333"
-
-str(Mothership_post$Days_complete_1)
-subset(Mothership, !is.na(Gender_1))
-ggplot(
-  data = subset(Mothership_post, !is.na(RESPONDER_FIGS)),
-  mapping = aes(
-    x = Days_complete_1,
-    y = Disorder_treat,
-    group = Disorder_treat)
-  )+
-  geom_jitter(
-    size = 0.6,
-    alpha = .5,
-   colour = highlight_col
-    )+
-  geom_boxplot(
-    outlier.shape = NA,
-   colour = outline_col,
-   fill = highlight_col,
-    alpha = 0.3) +
-  scale_x_continuous(
-   breaks = c(0, 15, 30, 45, 60),
-    limits = c(0.00, 60)
-  ) +
-  facet_wrap(~RESPONDER_FIGS)
-
-      #        labeller = labeller(RESPONDER_FIGS =
-      # c("1" = "Non-Responders", 
-      #   "2" = "Responders"))
-
-summary(Mothership_post$Days_complete_1)
-
-table1(Days_complete_1, data = Mothership_post)
-#####W WHY ARE DAYS COMPLETE NOT SHOWING UP???
-
-```
-
-# Sociodemographic Visualizations
-
-## {.tabset}
-
-### Education Status
-```{r}
-ggplot(data = subset(Mothership_post, !is.na(Education_1)),mapping = aes(x = Education_1))+
-  geom_bar(color = "black",fill="darkred")+
-  ggtitle("Frequency of Education Level") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Education Level")+
-  theme(panel.grid.major.x = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
-  coord_flip()
-```
-
-### Race
-```{r}
-ggplot(data = subset(Mothership_post, !is.na(Race_1)),mapping = aes(x = Race_1))+
-  geom_bar(color = "black",fill="darkblue")+
-  ggtitle("Frequency of Race/Ethnicity") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Race")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6500)) +
-  coord_flip()
-```
-
-### Gender
-```{r}
-ggplot(data = subset(Mothership_post, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
-  geom_bar(color = "black",fill="darkorange")+
-  ggtitle("Frequency of Gender") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Gender")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  coord_flip()+
-  scale_y_continuous(name = "Frequency",limits=c(0,6500))
-```
-
-# Treatment Related Visualizations
-
-## {.tabset}
-
-### Treatment Track
-```{r}
-### Treatment Track ###
-
-ggplot(data = subset(Mothership_post, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
-  geom_bar(color = "black",fill="skyblue")+
-  ggtitle("Frequency of Treatment Type") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Treatment Type")+
-  theme(panel.grid.major.x= element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,4200))+
-  coord_flip()
-```
-
-### Treatment Year
-```{r}
-### Treatment Year ###
-
-ggplot(data = subset(Mothership_post, !is.na(TxYear)),mapping = aes(x = TxYear))+
-  geom_bar(color = "black",fill="#9350C7")+
-  ggtitle("Frequency of Patients per Year") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Treatment Year")+
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,1500)) +
-  coord_flip()
-```
-
-### Duration of Treatment
-```{r}
-### Duration of Treatment ###
-ggplot(data = subset(Mothership_post, !is.na(Duration)),mapping = aes(x = Duration))+
-  geom_bar(color = "black",fill="lightgreen")+
-  ggtitle("Frequency of Patients per Duration of Treatment") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Treatment Duration")+
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
-  coord_flip()
-
-```
+- Table 3: Correlation table?
+- supplemental table 1: Full diagnostic breakdown of sample 
+  + (co-occuring by Disorder)
+```{r}
+
+```
+
+## Part 2: RCI ANALYSIS - Treatment Response
+Anxiety & Depression = Total response
+- Table 4: RCI Analsyis results
+  + Anxiety, Depression, Total response
+- Figure 2 / Supplimetal 2: RCI Analysis figs 
+  + Anxeity & Depression
+```{r}
+
+```
+
+## Part 3
+Logistic lasso
+
+### Lasso Regression
+https://glmnet.stanford.edu/articles/glmnet.html
+https://www.mygreatlearning.com/blog/understanding-of-lasso-regression/
+https://bookdown.org/tpinto_home/Regularisation/lasso-regression.html
+
+\scriptsize
+```{r, warning=FALSE, message=FALSE}
+library(glmnet)
+ecls2$preds = as.matrix(ecls2[ ,c(1:8,14:22)])
+
+# lambda = 0
+lasso1 = glmnet(ecls2$preds, ecls2$g8_sci_tht, alpha=1, lambda=0, 
+                standardize=TRUE, intercept=TRUE)
+lasso1
+
+coef(lasso1)
+```
+
+### Lasso Regression
+\scriptsize
+```{r}
+## lambda = .1
+lasso2 = glmnet(ecls2$preds, ecls2$g8_sci_tht, alpha=1, lambda=.1,
+                standardize=TRUE, intercept=TRUE)
+lasso2
+
+coef(lasso2)
+```
+
+### $k$-fold Cross Validation
+\scriptsize
+```{r, warning=FALSE, message=FALSE}
+#1. set seed
+set.seed(19860608)
+#2. sample data from the number of rows in els2
+ecls2 = ecls2[sample(nrow(ecls2)),]
+#3. convert ecls2a a new datafraame that is scaled and mean centered.
+ecls2a = as.data.frame(scale(ecls2, center=TRUE, scale=TRUE))
+#4. create a new column of values with predictors
+ecls2a$pred = as.matrix(ecls2a[,c(1:8,14:22)])
+
+#5. define the number of folds: cut a sequence from 1-num rows in ecls2a, broken into 10 equal parts, without labels)
+folds = cut(seq(1,nrow(ecls2a)), breaks=10, labels=FALSE)
+
+#6. create a grid (Sequence) from 0 - 1 increasing by .001
+grid = seq(0, 1, by=.001)
+#.7 make a matrix full of NAs that is 10 columns wide and the length of grid long? 
+    # I think MSE = mean squared error?
+mse  = matrix(NA, 10, length(grid))
+
+#8. create a for loop (for each row in the number of columns (1-10))
+for(i in 1:10){
+  #9. the test cases are the first number for each fold
+  testCases = which(folds==i,arr.ind=TRUE)
+  test      = ecls2a[testCases, ]
+  #10. the train cases are the valeus not the test cases
+  train     = ecls2a[-testCases, ]
+
+  #11. another for loop for each value in 1 - length of grid)
+  for (j in 1:length(grid)){
+    #12. k lambda = the index of grid[j]
+    klambda = grid[j]
+    #13. run a fit train regression model with predictors, for train$g8_Sci_tht.
+    fitTrain = glmnet(train$pred, train$g8_sci_tht, 
+                      alpha=1, lambda=klambda,
+                      standardize=FALSE, intercept=TRUE)
+    #14. predict the test values using predict using the fitTrain model, and using the new x values as test$pred
+    fit_test = predict(fitTrain, newx=test$pred)
+    #15. at each index of mse, take the mean of the differnece between the test value, and the fit test values and square them
+    mse[i,j] = mean((test$g8_sci_tht - fit_test)^2)
+  }
+}
+
+# 16. load matrixStats
+library(matrixStats)
+
+#17. assign a varaible that is column means of mse
+mseMeans = colMeans(mse, na.rm=TRUE)
+#18. assign column sd
+mseSds = colSds(mse, na.rm=TRUE)
+
+# Find minimum - find the one which has the minimum mean square error 
+best = which.min(mseMeans)
+grid[best]
+
+# Find simplest model within 1 Standard Error - best close 
+maxMse = mseMeans[best] + mseSds[best]/sqrt(10)
+bestClose = max(which(mseMeans<maxMse))
+grid[bestClose]
+```
+
+K-fold cross-validation can be performed using the cv.glmnet function.
+In addition to all the glmnet parameters, cv.glmnet has its special parameters including nfolds (the number of folds), foldid (user-supplied folds), and type.measure(the loss used for cross-validation):
+
+“deviance” or “mse” for squared loss, MSE = mean squared loss
+
+### Lasso Regression
+\scriptsize
+```{r}
+lasso3 = glmnet(ecls2a$pred, ecls2a$g8_sci_tht, alpha=1, lambda=grid[best],
+                standardize=FALSE, intercept=TRUE)
+coef(lasso3)
+```
+
+### Lasso Regression
+\scriptsize
+```{r}
+lasso4 = glmnet(ecls2a$pred, ecls2a$g8_sci_tht, alpha=1, lambda=grid[bestClose],
+                standardize=FALSE, intercept=TRUE)
+coef(lasso4)
+```
+
+### Relaxed Lasso
+\scriptsize
+```{r}
+rlasso4 = lm(g8_sci_tht~gender+kage+k_math_tht+k_gk_tht+f_mtr+
+             poor, data=ecls2)
+summary(rlasso4)
+```
+
+*Relaxed Lasso*
+- I After variable selection using the lasso, an OLS regression model is fit with only the variables selected
+- The estimates for retained variables are not shrunken
+
+*Cautions*
+- When performing cross validation, it’s important to standardize
+variables before creating folds
+- Similarly, when creating the final prediction model, it is important for the standardization process to be the same across datasets
+    + Same means and standard deviations are used across datasets
+- Relaxed lasso avoids the standardization process when creating
+final model
+- Built in k-fold cross-validation using glmnet:
+
+### $\mathtt{cv.glmnet}$ function in $\mathtt{glmnet}$
+ - Built in $k$-fold cross-validation using $\text{glmnet}$
+
+\scriptsize
+```{r}
+cvGlmnet = cv.glmnet(ecls2a$pred, ecls2a$g8_sci_tht, 
+                     alpha=1, type.measure='mse', 
+                     nfolds=10)
+cvGlmnet$lambda.min
+cvGlmnet$lambda.1se
+
+plot(cvGlmnet)
+```

### 2024-01-30 Paper_stuff.Rmd
Adding new RMD with stuff just for LAsso responder paper

@@
                     DC_status_1 = recode(DC_status_1,
+                                      "1" ="Treatment Complete",
+                                      "2" ="Treatment nearly complete",
+                                      "3" ="Insurance no longer covering",
+                                      "4" ="Nonattendance",
+                                      "5" ="Inappropriate (language)/Referred to another tx setting",
+                                      "6" ="Transferred to inpatient",
+                                      "7" ="Withdrew due to external limitations",
+                                      "8"= "Withdrew AMA",
+                                      "9"= "Other",
+                                      "10"="Other",
+                                      "0" ="Other"),
+                    Referral_1 = as.factor(Referral_1),
+                    Referral_1 = recode(Referral_1,
                                       "1" ="Inpatient",
@@
                                       "7" ="Therapist",
-                                      "8"="Withdrew (AMA)",
-                                      "9"="Other",
-                                      "10"="Other",
-                                      "11"="Other",
                                       "17"="Other",
@@
                                 Trauma_C == 1 & Somatic_D ==1 |
-                                Trauma_C == 1 & Psychotic_D ==1, 1, 0))
+                                Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
+
+          #this isn't working???
+                  # Sum_DX = #Primary
+                  #       as.integer(Mood_D) + as.integer(Anxiety_D) +as.integer(OCD_P) + 
+                  #       as.integer(BPD_P) + as.integer(Substance_D) + as.integer(Trauma_D) + 
+                  #       as.integer(Psychotic_D) + as.integer(Eating_D) + as.integer(Somatic_D) + as.integer(Other) +
+                  #          #Co-Occurring
+                  #       as.integer(GAD_C) + as.integer(Panic_C) + as.integer(PanicAgor_C) + as.integer(Agoraphobia_C) + 
+                  #       as.integer(Social_C) + as.integer(Specific_C) + as.integer(MDD_C) + as.integer(Bipolar1_C) + as.integer(Bipolar2_C) + 
+                  #       as.integer(Dysthymia_C) + as.integer(Alcohol_C) + as.integer(Drug_C) + as.integer(PTSD_C) + 
+                  #       as.integer(Adjustment_C) + as.integer(Schiz_C) + as.integer(Schizaff_C) + as.integer(Anorex_C) + as.integer(Bulim_C) + 
+                  #       as.integer(Binge_C) + as.integer(Somat_C) + as.integer(UndiffSoma_C) + as.integer(Hypochondriasis_C) + as.integer(OCD_Co_C) + 
+                  #       as.integer(BPD_Co_C)
                       )
+
+View(Mothership)
 
@@
 write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag.csv")
-
-# df with and without depression
-No_depressy <- Mothership_Diag %>%
-  filter(Disorder_Type != "Mood")
 
@@
 
-RCI_DF
-
 Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
@@
         ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
-        )))
+        ))) |>
+  filter(!is.na(RESPONDER_FIGS))
 
@@
 # Results
+
+Part 1 - treatment information
+
+- demographics breakdown
+- treatment breakdown
+    - duration of stay based upon disorder?
+    - mean anx / depression based upon stay
+- Treatment discharge?
+- pre post by responder non responder
+
 ### The overall breakdown of patients’ demographics and diagnoses. 
@@
 Table – Diagnoses
+Table - Treatment information
 ```{r}
@@
 #Demographic tab
-Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1, data=Demo_tab_df))
-colnames(Demo_tab) <- c("Demographic","Total Sample")
-view(Demo_tab)
-
-#Disorder Table - duratin
-Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_post))
-                                       #Mothership_Diag_treat))
-colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
-Dis_tab
-
-#Disorder Tab by 10 days
-Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_post))
-                                      #Mothership_Diag_treat))
-colnames(Dis_tab_10) <- c("Primary Diagnosis","1-10 Days", "10+ Days", "Total Sample")
-Dis_tab_10
-
-##### Add other demographic information here
-
+Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
+colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
+Demo_tab
+
+# Treatment info
+resp_tab <- data.frame(table1::table1(
+  ~IPT_track_1 + Days_complete_1 + DC_status_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 + Current_Dx | RESPONDER_FIGS, 
+  data = Mothership_post))
+colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
+resp_tab
 ```
@@
 
-Dumbell Plot by Disorder
-```{r}
-AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
-                                  Mothership_post$Disorder_Type,
-                                  Mothership_post$pre_anx,
-                                  Mothership_post$post_anx,
-                                  Mothership_post$pre_dep,
-                                  Mothership_post$post_dep,
-                                  Mothership_post$RESPONDER_FIGS)) 
-  # filter(!is.na(Mothership_post$Disorder_Type))
-colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","RESPONDER_FIGS)")
-
-Pre_ANX<-ANX_PrePost_mean %>%
-  filter(PrePost == "Pre")
-
-Post_ANX<-ANX_PrePost_mean %>%
-  filter(PrePost == "Post")
-
-Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
-Plot_Text
-
-"#aeb6bf"
-
-ggplot(data=AnxDep_PrePost,
-       aes(x=Disorder_Type,y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
-              size = 4, #Note that I sized the segment to fit the points
-              alpha = .5) +
-  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
-  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
-  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUXOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
-  scale_y_reverse(limits = c(45,15)) +
-  coord_flip() +
-  theme_classic()+
-  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
-      c("1" = "Non-Responders", 
-        "2" = "Responders")
-  ))
-  theme(#legend.position = "none",
-         plot.background = element_rect(
-      fill = "white",
-      colour = "white"))
-
-#sum(as.factor(ANX_PrePost$Disorder_Type))
-
-Pre_DEP<-DEP_PrePost_mean %>%
-  filter(PrePost == "Pre")
-
-Post_DEP<-DEP_PrePost_mean %>%
-  filter(PrePost == "Post")
-
-ggplot(data=Pre_DEP,
-       aes(x=Disorder_Type,y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
-              size = 4, #Note that I sized the segment to fit the points
-              alpha = .5) +
-  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
-  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
-  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUDOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
-       ylab = "Disorder Type")+
-  scale_y_reverse(limits = c(45,15)) +
-  coord_flip() +
-  theme_classic()+
-  theme(#legend.position = "none",
-         plot.background = element_rect(
-      fill = "white",
-      colour = "white"))
-```
-
-### Overall Plot
-```{r}
-# Pre Post CUDOS/CUXOS Plot
-ggplot(data=AnxDep_PrePost_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Test,color=fct_rev(Test)))+
-  geom_point(size=2.5)+
-  geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUDOS/CUXOS Score")+
-  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank())
+## Pre Post
+### table - prepost
+```{r}
+
+```
+
+### Pre-post Line Plot
+```{r}
 
@@
 
-#### ANX
-ggplot(data=ANX_PrePost_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Disorder_Type,color=Disorder_Type))+
-  geom_point(size=2.5)+
-  geom_line(size=1)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUXOS Score")+
-  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
-       subtitle = "Self Report anxiety was assessed using the CUXOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank())
-
-#### DEP
-ggplot(data=DEP_PrePost_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=as.factor(Disorder_Type),color=as.factor(Disorder_Type)))+
-  geom_point(size=2.5)+
-  geom_line(size=1)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUDOS Score")+
-  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
-       subtitle = "Self report depression was assessed using the CUDOS",
-       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank())
-
-### FACAT WRAP
+#3. Create a combined dataset
 
@@
 Mothership_Long_anx <- Mothership_Long_anx[order(Mothership_Long_anx$ID1),]
+
+summary(Mothership_post$Duration_lab)
+test <- Mothership_post |>
+  filter(
+Duration == 2
+)
 
@@
 # #Create a New Data Set with an Average Anxiety Variable
-# Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
-#   group_by(TxDay) %>%
-#   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
-
-#plot Anxiety mean with each group
-
-# New dataset for the treatment duration Anxiety plot
 Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
@@
   summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
+```
+
+FIGURE OUT WHY THIS SHIT ISN'T WORKING IT IS GRABBING VALUES THAT DOEN'T EXIST
+ITS GRABBING VALUES (CUXOS) FOR PEOPLE THAT DISCHARGED. I DON'T UNDERSTAND HOW THIS WORKS
+```{r}
+Mothership_duration_CUXOS<-Mothership_Mean_CUXOS[1:83,]
+View(Mothership_duration_CUXOS)
+
+Mothership_duration_CUXOS[6:20,3] = NA
+Mothership_duration_CUXOS[37:41,3] = NA
+Mothership_duration_CUXOS[74:83,3] = NA
+Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-21),]
+Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-41),]
+Mothership_duration_CUXOS<-Mothership_duration_CUXOS[(-61),]
+Mothership_duration_CUXOS
+
+ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration,color=Duration))+
+  geom_line(size=1)+
+  geom_point()+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  ggtitle("Mean Anxiety Severity During Partial Hospitalization")+
+  scale_x_discrete(name="Treatment Day",limits=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18,19,20))+
+  scale_y_continuous(name="Anxiety Severity",limits=c(5,50,by=5))+
+  scale_color_manual(values=c("#BB9D00","red",
+                              "darkred","orange"))+
+  theme(panel.background=NULL)+
+  labs(subtitle = "Broken up by Duration of Treatment")
+```
+
+```{r}
+#plot Anxiety mean with each group
+
+Mothership_Long_anx$Duration_lab
+
+# New dataset for the treatment duration Anxiety plot
+Mothership_Mean_CUXOS<-Mothership_Long_anx %>%
+  group_by(Duration_lab,TxDay) %>%
+  summarise(mean_CUXOS=mean(CUXOS,na.rm=TRUE))
 
 Mothership_Mean_CUXOS2 <- Mothership_Long_anx %>%
-  group_by(Duration,RESPONDER_FIGS,TxDay) %>%
+  group_by(Duration_lab,RESPONDER_FIGS,TxDay) %>%
   summarise(Score=mean(CUXOS,na.rm=TRUE))
@@
 View(Mothership_Mean_CUXOS2)
+
+View(Mothership_Mean_CUXOS)
 
@@
 
-ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration,color=Duration))+
+ggplot(data=Mothership_duration_CUXOS,aes(x=TxDay,y=mean_CUXOS,group=Duration_lab,color=Duration_lab))+
   geom_line(size=1)+
@@
 
+# Sociodemographic Visualizations
+
+## {.tabset}
+
+### Education Status
+```{r}
+ggplot(data = subset(Mothership_post, !is.na(Education_1)),mapping = aes(x = Education_1))+
+  geom_bar(color = "black",fill="darkred")+
+  ggtitle("Frequency of Education Level") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Education Level")+
+  theme(panel.grid.major.x = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
+  coord_flip()
+```
+
+### Race
+```{r}
+ggplot(data = subset(Mothership_post, !is.na(Race_1)),mapping = aes(x = Race_1))+
+  geom_bar(color = "black",fill="darkblue")+
+  ggtitle("Frequency of Race/Ethnicity") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Race")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500)) +
+  coord_flip()
+```
+
+### Gender
+```{r}
+ggplot(data = subset(Mothership_post, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
+  geom_bar(color = "black",fill="darkorange")+
+  ggtitle("Frequency of Gender") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Gender")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  coord_flip()+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+```
+
+# Treatment Related Visualizations
+
+## {.tabset}
+
+### Treatment Track
+```{r}
+### Treatment Track ###
+
+ggplot(data = subset(Mothership_post, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
+  geom_bar(color = "black",fill="skyblue")+
+  ggtitle("Frequency of Treatment Type") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Treatment Type")+
+  theme(panel.grid.major.x= element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,4200))+
+  coord_flip()
+
+```
+
+### Treatment Year
+```{r}
+### Treatment Year ###
+
+ggplot(data = subset(Mothership_post, !is.na(TxYear)),mapping = aes(x = TxYear))+
+  geom_bar(color = "black",fill="#9350C7")+
+  ggtitle("Frequency of Patients per Year") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Treatment Year")+
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,1500)) +
+  coord_flip()
+```
+
+### Duration of Treatment
+```{r}
+### Duration of Treatment ###
+ggplot(data = subset(Mothership_post, !is.na(Duration)),mapping = aes(x = Duration))+
+  geom_bar(color = "black",fill="lightgreen")+
+  ggtitle("Frequency of Patients per Duration of Treatment") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Treatment Duration")+
+  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
+  coord_flip()
+
+```
+
+tables
+```{r}
+  ### To univariate tests with these???
+
+#Disorder Table - duratin
+# Dis_tab <- data.frame(table1::table1(~Disorder_Type | Duration, data = Mothership_post))
+#                                  #Mothership_Diag_treat))
+# colnames(Dis_tab) <- c("Primary Diagnosis","1-5 Days", "6-10 Days", "11-15 Days","16+ Days", "Total Sample")
+# Dis_tab
+
+#Disorder Tab by 10 days
+# Dis_tab_10 <- data.frame(table1::table1(~Disorder_Type | Duration_10, data = Mothership_post))
+# colnames(Dis_tab_10) <- c("Primary Diagnosis","1-10 Days", "10+ Days", "Total Sample")
+# Dis_tab_10
+
+# Disorder by responder
+```
+
+Dumbell Plot by Disorder - Pre and Post
+```{r}
+AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
+                                  Mothership_post$Disorder_Type,
+                                  Mothership_post$pre_anx,
+                                  Mothership_post$post_anx,
+                                  Mothership_post$pre_dep,
+                                  Mothership_post$post_dep,
+                                  Mothership_post$RESPONDER_FIGS)) 
+  # filter(!is.na(Mothership_post$Disorder_Type))
+colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","RESPONDER_FIGS)")
+
+Pre_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
+Plot_Text
+
+"#aeb6bf"
+
+ggplot(data=AnxDep_PrePost,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUXOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
+  scale_y_reverse(limits = c(45,15)) +
+  coord_flip() +
+  theme_classic()+
+  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
+      c("1" = "Non-Responders", 
+        "2" = "Responders")
+  ))
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+
+#sum(as.factor(ANX_PrePost$Disorder_Type))
+
+Pre_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+ggplot(data=Pre_DEP,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUDOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
+       ylab = "Disorder Type")+
+  scale_y_reverse(limits = c(45,15)) +
+  coord_flip() +
+  theme_classic()+
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+```
+
+### Dumbell Plot by Disorder
+```{r}
+Pre_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_ANX<-ANX_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+Plot_Text<- dplyr::count(ANX_PrePost, Disorder_Type)
+Plot_Text
+
+"#aeb6bf"
+
+ggplot(data=Pre_ANX,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_ANX$Disorder_Type, y=Score, yend=Post_ANX$Score),color = "#ad3e4f",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_ANX$Disorder_Type, y=Post_ANX$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUXOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
+  scale_y_reverse(limits = c(45,15)) +
+  coord_flip() +
+  theme_classic()+
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+
+#sum(as.factor(ANX_PrePost$Disorder_Type))
+
+Pre_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Pre")
+
+Post_DEP<-DEP_PrePost_mean %>%
+  filter(PrePost == "Post")
+
+ggplot(data=Pre_DEP,
+       aes(x=Disorder_Type,y=Score,
+           group=Disorder_Type,color=Disorder_Type))+
+  geom_segment(aes(x=Disorder_Type, xend=Post_DEP$Disorder_Type, y=Score, yend=Post_DEP$Score),color = "#4068a8",
+              size = 4, #Note that I sized the segment to fit the points
+              alpha = .5) +
+  geom_point( aes(x=Disorder_Type, y=Score), color= "#F90000", size=3.5) +
+  geom_point( aes(x=Post_DEP$Disorder_Type, y=Post_DEP$Score), color= "#0CC541", size=3.5) +
+  labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
+       subtitle = "Self Report anxiety was assessed using the CUDOS",
+       caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)",
+       ylab = "Disorder Type")+
+  scale_y_reverse(limits = c(45,15)) +
+  coord_flip() +
+  theme_classic()+
+
+  theme(#legend.position = "none",
+         plot.background = element_rect(
+      fill = "white",
+      colour = "white"))
+```
+
+Overall plot - pre post
+```{r}
+# Pre Post CUDOS/CUXOS Plot
+# ggplot(data=AnxDep_PrePost_mean,
+#        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+#            group=Test,color=fct_rev(Test)))+
+#   geom_point(size=2.5)+
+#   geom_line(group=AnxDep_PrePost_mean$PrePost,size=1.5)+
+#   scale_x_discrete(name="Time Point")+
+#   scale_y_continuous(name="CUDOS/CUXOS Score")+
+#   ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
+#   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+#   theme(panel.background=NULL)+
+#   theme(legend.title = element_blank())
+```
+
+pre post disorder
+```{r}
+#### ANX
+# ggplot(data=ANX_PrePost_mean,
+#        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+#            group=Disorder_Type,color=Disorder_Type))+
+#   geom_point(size=2.5)+
+#   geom_line(size=1)+
+#   scale_x_discrete(name="Time Point")+
+#   scale_y_continuous(name="CUXOS Score")+
+#   labs(title = "Mean Pre and Post Anxiety Scores By Disorder Type",
+#        subtitle = "Self Report anxiety was assessed using the CUXOS",
+#        caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-40 (moderate), 41+ (severe)")+
+#   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+#   theme(panel.background=NULL)+
+#   theme(legend.title = element_blank())
+
+#### DEP
+# ggplot(data=DEP_PrePost_mean,
+#        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+#            group=as.factor(Disorder_Type),color=as.factor(Disorder_Type)))+
+#   geom_point(size=2.5)+
+#   geom_line(size=1)+
+#   scale_x_discrete(name="Time Point")+
+#   scale_y_continuous(name="CUDOS Score")+
+#   labs(title = "Mean Pre and Post Depression Scores By Disorder Type",
+#        subtitle = "Self report depression was assessed using the CUDOS",
+#        caption = "Symptom severity: 0-10 (remission), 11-20 (minimal), 21-30 (mild), 31-45 (moderate), 46+ (severe)")+
+#   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+#   theme(panel.background=NULL)+
+#   theme(legend.title = element_blank())
+```
+
+```{r}
+Mothership_post <- Mothership_post |>
+  #1. Filter out scores for people not in the program / don't have dataa
+  filter(!is.na(Days_complete_1)) |>
+    #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
+  filter(!is.na(CUXOS_pre),
+         !is.na(CUXOS_post),
+         CUXOS_pre > 0,
+         CUXOS_post >= 0,
+         !is.na(CUDOS_pre),
+         !is.na(CUDOS_post),
+         CUDOS_pre > 0,
+         CUDOS_post> 0
+         ) |>
+  mutate(
+    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
+    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
+    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
+    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
+    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
+    Anx_Responder = as.factor(
+      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
+      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
+      )),
+    Dep_Responder = as.factor(
+      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
+      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
+      )),
+    Treatment_Responder = as.factor(
+      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
+      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
+      )))))))))))
+
+ #CUXOS_post == !(CUXOS_post %in% c(seq(1,9,1)))
+
+ggplot(Mothership_post, aes(x = Treatment_Responder)) +
+  geom_bar() +
+  coord_flip() +
+  scale_x_discrete(limits =c("Low Baseline", "Both Worse", "Dep Worse", "Anx Worse","Both Unresponder","Dep Unresponders", "Anx Unresponders","Both_Responder", "Anx Responder","Dep Responder"))+
+  labs(
+    title = "Treatment response of Anxiety and Depression",
+    subtitle = "Response = 50% reduciton in scores if BL score > 10")
+
+ggplot(Mothership_post, aes(x = Anx_Responder)) +
+  geom_bar() +
+  coord_flip() +
+    labs(
+    title = "Treatment response of Anxiety",
+    subtitle = "Response = 50% reduciton in scores if BL score > 10")
+
+ggplot(Mothership_post, aes(x = Dep_Responder)) +
+  geom_bar() +
+  coord_flip() +
+    labs(
+    title = "Treatment response of Depression",
+    subtitle = "Response = 50% reduciton in scores if BL score > 10")
+```
+
+# Pie Chart For Education Status 
+We wanted to learn how to make a pie chart in R so here is one!
+```{r}
+#Create Table and Data Frame
+Education<-table(Mothership_post$Education_1)
+Education_df<-as.data.frame(Education)
+Education_df
+
+#Rename Columns
+colnames(Education_df)[1]="Category"
+colnames(Education_df)[2]="Frequency"
+
+Education_df$Category=recode(Education_df$Category,
+                             "0"="<Grade 6", 
+                             "1"="Grades 7-12",
+                             "2"="HS Diploma", 
+                             "3"="GED",
+                             "4"="Some College",
+                             "5"="Associates Degree",
+                             "6"="Bachelors Degree",
+                             "7"="Some Grad School",
+                             "8"="Grad Degree")
+
+ggplot(data = Education_df, mapping = aes(x="", y=Frequency, fill=Category))+
+  geom_bar(stat="Identity",width=1,color="white")+
+  ggtitle("Education Level of Patients") +
+  scale_fill_discrete(name = "Education") +
+  coord_polar("y",start=0)+
+  theme_void()
+```
+
 •	Table or Visualization – Reasons for discharge results.
@@
       ))
-
 ```
@@
 ```
-
-# Sociodemographic Visualizations
-
-## {.tabset}
-
-### Education Status
-```{r}
-ggplot(data = subset(Mothership_post, !is.na(Education_1)),mapping = aes(x = Education_1))+
-  geom_bar(color = "black",fill="darkred")+
-  ggtitle("Frequency of Education Level") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Education Level")+
-  theme(panel.grid.major.x = element_line(color = "grey",linewidth = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
-  coord_flip()
-```
-
-### Race
-```{r}
-ggplot(data = subset(Mothership_post, !is.na(Race_1)),mapping = aes(x = Race_1))+
-  geom_bar(color = "black",fill="darkblue")+
-  ggtitle("Frequency of Race/Ethnicity") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Race")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,6500)) +
-  coord_flip()
-```
-
-### Gender
-```{r}
-ggplot(data = subset(Mothership_post, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
-  geom_bar(color = "black",fill="darkorange")+
-  ggtitle("Frequency of Gender") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Gender")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  coord_flip()+
-  scale_y_continuous(name = "Frequency",limits=c(0,6500))
-```
-
-# Treatment Related Visualizations
-
-## {.tabset}
-
-### Treatment Track
-```{r}
-### Treatment Track ###
-
-ggplot(data = subset(Mothership_post, !is.na(IPT_track_1)),mapping = aes(x = IPT_track_1))+
-  geom_bar(color = "black",fill="skyblue")+
-  ggtitle("Frequency of Treatment Type") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Treatment Type")+
-  theme(panel.grid.major.x= element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,4200))+
-  coord_flip()
-```
-
-### Treatment Year
-```{r}
-### Treatment Year ###
-
-ggplot(data = subset(Mothership_post, !is.na(TxYear)),mapping = aes(x = TxYear))+
-  geom_bar(color = "black",fill="#9350C7")+
-  ggtitle("Frequency of Patients per Year") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Treatment Year")+
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,1500)) +
-  coord_flip()
-```
-
-### Duration of Treatment
-```{r}
-### Duration of Treatment ###
-ggplot(data = subset(Mothership_post, !is.na(Duration)),mapping = aes(x = Duration))+
-  geom_bar(color = "black",fill="lightgreen")+
-  ggtitle("Frequency of Patients per Duration of Treatment") +
-  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
-  xlab("Treatment Duration")+
-  theme(panel.grid.major.x = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  scale_y_continuous(name = "Frequency",limits=c(0,3000))+
-  coord_flip()
-
-```

### 2024-01-30 Lasso_RCI_Response.Rmd
Updated Tables

@@
 ## Part 1: Who is attending?
+
+### Demographics information
 - Table 1 Demographics By Response
@@
 Demo_tab
-
-# Treatment info
+```
+
+### Treatment information
+```{r}
+# PHP Treatment information
 resp_tab <- data.frame(table1::table1(
@@
 
+# Treatment scores 
+Scores_tab <- data.frame(matrix(nrow = 8,ncol=4))
+colnames(Scores_tab) = c("Variables", "Pre M(SD)", "Post M(SD)", "Change M(SD)")
+
+    #CUXOS
+      Scores_tab[1,] = 
+        c("CUXOS",
+          paste0(round(mean(Mothership_post$CUXOS_pre),2), " (", round(sd(Mothership_post$CUXOS_pre),2),")"),
+          paste0(round(mean(Mothership_post$CUXOS_post),2), " (", round(sd(Mothership_post$CUXOS_post),2),")"),
+          paste0(round(mean(Mothership_post$Delta_Anx_DC),2), "(",round(sd(Mothership_post$Delta_Anx_DC),2),")")
+        )
+
+    #CUDOS
+      Scores_tab[2,] = 
+        c("CUDOS",
+          paste0(round(mean(Mothership_post$CUDOS_pre),2), " (", round(sd(Mothership_post$CUDOS_pre),2),")"),
+          paste0(round(mean(Mothership_post$CUDOS_post),2), " (", round(sd(Mothership_post$CUDOS_post),2),")"),
+          paste0(round(mean(Mothership_post$Delta_Dep_DC),2), "(",round(sd(Mothership_post$Delta_Dep_DC),2),")")
+        )
+
+    #RDQ total
+      # Scores_tab[3,] = 
+      #    c("RDQ Total",
+      #     paste0(round(mean(Mothership_post$RDQ_Pre_Total),2), " (", round(sd(Mothership_post$RDQ_Pre_Total),2),")"),
+      #     paste0(round(mean(Mothership_post$RDQ_Post_Total),2), " (", round(sd(Mothership_post$RDQ_Post_Total),2),")"),
+      #     paste0(round(mean(Mothership_post$RDQ_Change_Total),2), "(",round(sd(Mothership_post$RDQ_Change_Total),2),")")
+      #    )
+
+    #RDQ Subscales
+      Scores_tab[3,] = c ("RDQ Subscales", NA, NA, NA)
+
+    #Coping
+      Scores_tab[4,] = 
+        c("Coping ability",
+          paste0(round(mean(Mothership_post$rdqPRE_coping, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPRE_coping, na.rm = TRUE),2),")"),
+          paste0(round(mean(Mothership_post$rdqPOST_coping, na.rm = TRUE),2), " (",round(sd(Mothership_post$rdqPOST_coping, na.rm = TRUE),2),")"),
+          paste0(round(mean(Mothership_post$rdq_coping_change, na.rm = TRUE),2),"(",round(sd(Mothership_post$rdq_coping_change, na.rm = TRUE),2),")")
+        )
+
+    #"PMH"
+        Scores_tab[5,] = 
+        c("Positive mental health",
+          paste0(round(mean(Mothership_post$rdqPRE_coping, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPRE_coping, na.rm = TRUE),2),")"),
+          paste0(round(mean(Mothership_post$rdqPOST_coping, na.rm = TRUE),2), " (",round(sd(Mothership_post$rdqPOST_coping, na.rm = TRUE),2),")"),
+          paste0(round(mean(Mothership_post$rdq_coping_change, na.rm = TRUE),2),"(",round(sd(Mothership_post$rdq_coping_change, na.rm = TRUE),2),")")
+        )
+
+    # functioning
+            Scores_tab[6,] = 
+        c("Functioning",
+          paste0(round(mean(Mothership_post$rdqPRE_func, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPRE_func, na.rm = TRUE),2),")"),
+          paste0(round(mean(Mothership_post$rdqPOST_func, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPOST_func, na.rm = TRUE),2),")"),
+          paste0(round(mean(Mothership_post$rdq_func_change, na.rm = TRUE),2), "(",round(sd(Mothership_post$rdq_func_change, na.rm = TRUE),2),")")
+        )
+
+    # General sense of wellbeing
+            Scores_tab[7,] = 
+        c("General sense of wellbeing",
+          paste0(round(mean(Mothership_post$rdqPRE_wbs, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPRE_wbs, na.rm = TRUE),2),")"),
+          paste0(round(mean(Mothership_post$rdqPOST_wbs, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPOST_wbs, na.rm = TRUE),2),")"),
+          paste0(round(mean(Mothership_post$rdq_wbs_change, na.rm = TRUE),2), "(",round(sd(Mothership_post$rdq_wbs_change, na.rm = TRUE),2),")")
+        )
+
+    #Symptoms"
+            Scores_tab[8,] = 
+        c("Symptoms",
+          paste0(round(mean(Mothership_post$rdqPRE_sym, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPRE_sym, na.rm = TRUE),2),")"),
+          paste0(round(mean(Mothership_post$rdqPOST_sym, na.rm = TRUE),2), " (", round(sd(Mothership_post$rdqPOST_sym, na.rm = TRUE),2),")"),
+          paste0(round(mean(Mothership_post$rdq_sym_change, na.rm = TRUE),2), "(",round(sd(Mothership_post$rdq_sym_change, na.rm = TRUE),2),")")
+        )
+
+ Scores_tab
+```
+
+### Disorder Breakdowns
+Here are some tables displaying info on the psychiatric disorders treated at the PHP
+```{r}
 # Disorders by treatment response
@@
                                      data = Mothership_post))
+colnames(Dis_tab) = c("Variables","Non Responder", "Responder", "Total")
 Dis_tab
 
-#Full demographic break down.
+#Full demographic break down
+co_dis_tab <- Mothership_Diag_treat |>
+  pivot_longer(
+    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
+    names_to = 'Co Occuring',
+    values_to = "Number"
+  ) |>
+  select(Disorder_treat, `Co Occuring`, Number) |>
+  filter(Number != 0,
+         !is.na(`Co Occuring`),
+         !is.na(Disorder_treat))
+
 CODis_tab<-data.frame(table1::table1(~`Co Occuring` | Disorder_treat, data = co_dis_tab))
+colnames(CODis_tab)[1] = c("Variables")
 CODis_tab
-
-Mothership_post$Current_Dx
 ```

### 2024-02-05 Lasso_RCI_Response.Rmd
Correlation table

--- 2024-01-30 Lasso_RCI_Response.Rmd
@@
 Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
-head(df)
-
-# source("~/Desktop/Coding/R working directory/Hospital_Visualizations/Lasso_RCI_Source.R")
+DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
+
 ```
@@
 # We can change the current variables to make them easier to interpret.
+str(Mothership_post$Education_1)
 
@@
                                           "8"="Grad Degree"),
+                     Some_College = Education_1,
+                     Some_College = recode(Education_1,
+                                          "<Grade 12" = "No College",
+                                          "<Grade 12" = "No College",
+                                          "HS Diploma or GED" = "No College",
+                                          "HS Diploma or GED" = "No College",
+                                          "Some College/Associates Degree" = "Some College",
+                                          "Some College/Associates Degree" = "Some College",
+                                          "Bachelors Degree" = "Some College",
+                                          "Bachelors Degree" = "Some College",
+                                          "Grad Degree" ="Some College"),
                      Gender_1 = as.factor(Gender_1),
@@
                                        "4"="Other"),
+                     Female = Gender_1,
+                     Female= recode(Gender_1,
+                                       "Female" = "Female",
+                                       "Male" = "Not",
+                                       "Non-Binary" = "Not",
+                                       "Other" = "Not",
+                                       "Other" = "Not"),
                       Relationship_1 = ifelse(Relationship_1 == 8, NA, Relationship_1),
@@
                                              "5"="Single or Never Married"),
+                     Married = recode(Relationship_1,
+                                             "Married or Cohabitating" = "Married or Cohabitating",
+                                             "Widowed or Separated" = "Not",
+                                             "Divorced" = "Not",
+                                             "Single or Never Married" = "Not"),
                      Sexuality_1 = as.factor(Sexuality_1),
@@
                                           "4"="Other"),
+                     Straight = recode(Sexuality_1,
+                                         "Straight" = "Straight",
+                                          "Gay" = "Not Straight",
+                                          "Bisexual" = "Not Straight",
+                                          "Other" = "Not Straight"),
                      IPT_track_1 = as.factor(IPT_track_1),
@@
                                      "5"="Other"),
+                     White = recode(Race_1,
+                                     "White" = "White",
+                                     "Black" = "Not White",
+                                     "Hispanic"="Not White",
+                                     "Asian"="Not White",
+                                     "Portugese"="Not White",
+                                     "Other"="Not White"),
                      DC_status_1 = as.factor(DC_status_1),
@@
                                           "0" ="Other"),
-                     Referral_1 = as.factor(Referral_1),
-                     Referral_1 = recode(Referral_1,
-                                         "1" ="Inpatient",
-                                         "2" ="PHP",
-                                         "3" ="APS",
-                                         "4" ="Psychatrist",
-                                         "5" ="PCP",
-                                         "6" ="Another Physican",
-                                         "7" ="Therapist",
-                                         "17"="Other",
-                                         "0" ="Other"),
-
+                     Discharge = recode(DC_status_1,
+                                          "Treatment Complete" = "Treatment Successful",
+                                          "Treatment nearly complete" = "Treatment Successful",
+                                          "Insurance no longer covering" = "Other",
+                                          "Nonattendance" = "Other",
+                                          "Inappropriate (language)/Referred to another tx setting" ="Other",
+                                          "Transferred to inpatient"="Other",
+                                          "Withdrew due to external limitations"="Other",
+                                          "Withdrew AMA"="Other",
+                                          "Other"="Other",
+                                          "Other"="Other",
+                                          "Other"="Other"),
 #Lets make some new variables 
@@
                                                      "3"="11-15",
-                                                     "4"="16+"
-                     )),
+                                                     "4"="16+")),
                      Duration_10 = as.factor(
@@
 
-Mothership_Diag_treat <- Mothership |>
-  filter(!is.na(Disorder_treat),
-         !is.na(TxYear),
-         !is.na(Duration))
+# Mothership_Diag_treat <- Mothership |>
+#   filter(!is.na(Disorder_treat),
+#          !is.na(TxYear),
+#          !is.na(Duration))
 
@@
 library(JTRCI)
-library(ClinicalSig)
-
-#devtools::install_github("zieglema/ClinicalSig")
+# library(ClinicalSig)
+# 
+# #devtools::install_github("zieglema/ClinicalSig")
 #1. Create df for RCI
@@
 - Table 3: Scores on measures pre post change? 
-    + I want to show the figure of prepost change???
+    + I want to show the figure of pre-post change???
 - Table 4: demographic breakdown
@@
 
-# Treatment info
+Simple_Demo_tab <-data.frame(table1::table1(~Age_1 + White +IPT_track_1 + Straight + Married + Female +  Some_College + Discharge | RESPONDER_FIGS, data=Demo_tab_df))
+colnames(Simple_Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
+Simple_Demo_tab
+```
+
+### Treatment information
+Overal look at treatment varaibles by treatment response
+```{r}
+# PHP Treatment information
 resp_tab <- data.frame(table1::table1(
-  ~Referral_1 + DC_status_1 + RIPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
+   ~ DC_status_1 + IPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
   data = Mothership_post))
@@
 resp_tab
-
+```
+
+pre-post scores by treatment response
+```{r}
+# Treatment scores
+#1. Make DF + name columns
+Scores_tab <- data.frame(matrix(nrow = 9 ,ncol=7))
+colnames(Scores_tab) = c("Variables", "N_Pre M(SD)", "N_Post M(SD)", "N_Change M(SD)","R_Pre M(SD)", "R_Post M(SD)", "R_Change M(SD)")
+
+#2. Row 1 - responders
+Scores_tab[1,] = c(NA,"Non-responder","Non-responder","Non-responder","Responder","Responder","Responder")
+
+#3. Get statistics for variables + Assign to table
+  # Anxiety - CUXOS
+    #make df
+      anx_rep_tab <- Mothership_post |>
+        group_by(RESPONDER_FIGS) |>
+        summarize(pre_anx = round(mean(CUXOS_pre, na.rm = TRUE),2),
+                  pre_anx_sd = round(sd(CUXOS_pre, na.rm = TRUE),2),
+                  post_anx = round( mean(CUXOS_post,na.rm = TRUE),2),
+                  post_anx_sd = round( sd(CUXOS_post,na.rm = TRUE),2),
+                  delta_anx = round( mean(Delta_Anx_DC,na.rm = TRUE),2),
+                  delta_anx_sd = round( sd(Delta_Anx_DC, na.rm = TRUE),2)
+                  )
+# add to scores tab
+        Scores_tab[2,] = c(
+          "CUXOS",
+          #Non-responder scores
+          paste0(anx_rep_tab$pre_anx[[1]]," (",anx_rep_tab$pre_anx_sd[[1]],")"),
+          paste0(anx_rep_tab$post_anx[[1]]," (",anx_rep_tab$post_anx_sd[[1]],")"),
+          paste0(anx_rep_tab$delta_anx[[1]]," (",anx_rep_tab$delta_anx_sd[[1]],")"),
+          #responder scores
+          paste0(anx_rep_tab$pre_anx[[2]]," (",anx_rep_tab$pre_anx_sd[[2]],")"),
+          paste0(anx_rep_tab$post_anx[[2]]," (",anx_rep_tab$post_anx_sd[[2]],")"),
+          paste0(anx_rep_tab$delta_anx[[2]]," (",anx_rep_tab$delta_anx_sd[[2]],")")
+        )
+
+  # Depression - CUDOS
+  #Make df
+    dep_rep_tab <- Mothership_post |>
+      group_by(RESPONDER_FIGS) |>
+      summarize(pre_dep = round( mean(CUDOS_pre, na.rm = TRUE),2),
+                pre_dep_sd = round( sd(CUDOS_pre, na.rm = TRUE),2),
+                post_dep = round( mean(CUDOS_post, na.rm = TRUE),2),
+                post_dep_sd = round( sd(CUDOS_post, na.rm = TRUE),2),
+                delta_dep = round( mean(Delta_Dep_DC, na.rm = TRUE),2),
+                delta_dep_sd = round( sd(Delta_Dep_DC, na.rm = TRUE),2)
+                )
+    #Add to Scores_tab
+       Scores_tab[3,] = c(
+        "CUDOS",
+        #Non-responder scores
+        paste0(dep_rep_tab$pre_dep[[1]]," (",dep_rep_tab$pre_dep_sd[[1]],")"),
+        paste0(dep_rep_tab$post_dep[[1]]," (",dep_rep_tab$post_dep_sd[[1]],")"),
+        paste0(dep_rep_tab$delta_dep[[1]]," (",dep_rep_tab$delta_dep_sd[[1]],")"),
+        #responder scores
+        paste0(dep_rep_tab$pre_dep[[2]]," (",dep_rep_tab$pre_dep_sd[[2]],")"),
+        paste0(dep_rep_tab$post_dep[[2]]," (",dep_rep_tab$post_dep_sd[[2]],")"),
+        paste0(dep_rep_tab$delta_dep[[2]]," (",dep_rep_tab$delta_dep_sd[[2]],")")
+      )
+
+  #RDQ subscales
+       Scores_tab[4,1] = "RDQ Subscales"
+
+  # Coping
+      cope_rep_tab <- Mothership_post |>
+        group_by(RESPONDER_FIGS) |>
+        summarize(pre_cope = round( mean(rdqPRE_coping, na.rm = TRUE),2),
+                  pre_cope_sd = round( sd(rdqPRE_coping, na.rm = TRUE),2),
+                  post_cope = round( mean(rdqPOST_coping, na.rm = TRUE),2),
+                  post_cope_sd = round( sd(rdqPOST_coping, na.rm = TRUE),2),
+                  delta_cope = round( mean(rdq_coping_change, na.rm = TRUE),2),
+                  delta_cope_sd = round( sd(rdq_coping_change, na.rm = TRUE),2)
+              )
+      Scores_tab[5,] = c(
+        "Coping",
+        #Non-responder scores
+        paste0(cope_rep_tab$pre_cope[[1]]," (",cope_rep_tab$pre_cope_sd[[1]],")"),
+        paste0(cope_rep_tab$post_cope[[1]]," (",cope_rep_tab$post_cope_sd[[1]],")"),
+        paste0(cope_rep_tab$delta_cope[[1]]," (",cope_rep_tab$delta_cope_sd[[1]],")"),
+        #responder scores
+        paste0(cope_rep_tab$pre_cope[[2]]," (",cope_rep_tab$pre_cope_sd[[2]],")"),
+        paste0(cope_rep_tab$post_cope[[2]]," (",cope_rep_tab$post_cope_sd[[2]],")"),
+        paste0(cope_rep_tab$delta_cope[[2]]," (",cope_rep_tab$delta_cope_sd[[2]],")")
+      )
+   # Positive mental health
+  pmh_rep_tab <- Mothership_post |>
+    group_by(RESPONDER_FIGS) |>
+    summarize(pre_pmh = round( mean(rdqPRE_pmh, na.rm = TRUE),2),
+              pre_pmh_sd = round( sd(rdqPRE_pmh, na.rm = TRUE),2),
+              post_pmh = round( mean(rdqPOST_pmh, na.rm = TRUE),2),
+              post_pmh_sd = round( sd(rdqPOST_pmh, na.rm = TRUE),2),
+              delta_pmh = round( mean(rdq_pmh_change, na.rm = TRUE),2),
+              delta_pmh_sd = round( sd(rdq_pmh_change, na.rm = TRUE),2)
+              )
+         Scores_tab[6,] = c(
+              "Positive Mental Health",
+              #Non-responder scores
+              paste0(pmh_rep_tab$pre_pmh[[1]]," (",pmh_rep_tab$pre_pmh_sd[[1]],")"),
+              paste0(pmh_rep_tab$post_pmh[[1]]," (",pmh_rep_tab$post_pmh_sd[[1]],")"),
+              paste0(pmh_rep_tab$delta_pmh[[1]]," (",pmh_rep_tab$delta_pmh_sd[[1]],")"),
+              #responder scores
+              paste0(pmh_rep_tab$pre_pmh[[2]]," (",pmh_rep_tab$pre_pmh_sd[[2]],")"),
+              paste0(pmh_rep_tab$post_pmh[[2]]," (",pmh_rep_tab$post_pmh_sd[[2]],")"),
+              paste0(pmh_rep_tab$delta_pmh[[2]]," (",pmh_rep_tab$delta_pmh_sd[[2]],")")
+            )
+   # Functioning
+  func_rep_tab <- Mothership_post |>
+    group_by(RESPONDER_FIGS) |>
+    summarize(pre_func = round( mean(rdqPRE_func, na.rm = TRUE),2),
+              pre_func_sd = round( sd(rdqPRE_func, na.rm = TRUE),2),
+              post_func = round( mean(rdqPOST_func, na.rm = TRUE),2),
+              post_func_sd = round( sd(rdqPOST_func, na.rm = TRUE),2),
+              delta_func = round( mean(rdq_func_change, na.rm = TRUE),2),
+              delta_func_sd = round( sd(rdq_func_change, na.rm = TRUE),2)
+              )    
+         Scores_tab[7,] = c(
+              "Functioning",
+              #Non-responder scores
+              paste0(func_rep_tab$pre_func[[1]]," (",func_rep_tab$pre_func_sd[[1]],")"),
+              paste0(func_rep_tab$post_func[[1]]," (",func_rep_tab$post_func_sd[[1]],")"),
+              paste0(func_rep_tab$delta_func[[1]]," (",func_rep_tab$delta_func_sd[[1]],")"),
+              #responder scores
+              paste0(func_rep_tab$pre_func[[2]]," (",func_rep_tab$pre_func_sd[[2]],")"),
+              paste0(func_rep_tab$post_func[[2]]," (",func_rep_tab$post_func_sd[[2]],")"),
+              paste0(func_rep_tab$delta_func[[2]]," (",func_rep_tab$delta_func_sd[[2]],")")
+            )
+
+    # General sense of wellbeing
+    wbs_rep_tab <- Mothership_post |>
+    group_by(RESPONDER_FIGS) |>
+    summarize(pre_wbs = round( mean(rdqPRE_wbs, na.rm = TRUE),2),
+              pre_wbs_sd = round( sd(rdqPRE_wbs, na.rm = TRUE),2),
+              post_wbs = round( mean(rdqPOST_wbs, na.rm = TRUE),2),
+              post_wbs_sd = round( sd(rdqPOST_wbs, na.rm = TRUE),2),
+              delta_wbs = round( mean(rdq_wbs_change, na.rm = TRUE),2),
+              delta_wbs_sd = round( sd(rdq_wbs_change, na.rm = TRUE),2)
+              )
+
+     Scores_tab[8,] = c(
+              "General sense of wellbeing",
+              #Non-responder scores
+              paste0(wbs_rep_tab$pre_wbs[[1]]," (",wbs_rep_tab$pre_wbs_sd[[1]],")"),
+              paste0(wbs_rep_tab$post_wbs[[1]]," (",wbs_rep_tab$post_wbs_sd[[1]],")"),
+              paste0(wbs_rep_tab$delta_wbs[[1]]," (",wbs_rep_tab$delta_wbs_sd[[1]],")"),
+              #responder scores
+              paste0(wbs_rep_tab$pre_wbs[[2]]," (",wbs_rep_tab$pre_wbs_sd[[2]],")"),
+              paste0(wbs_rep_tab$post_wbs[[2]]," (",wbs_rep_tab$post_wbs_sd[[2]],")"),
+              paste0(wbs_rep_tab$delta_wbs[[2]]," (",wbs_rep_tab$delta_wbs_sd[[2]],")")
+            )
+
+    #Symptoms
+    sym_rep_tab <- Mothership_post |>
+    group_by(RESPONDER_FIGS) |>
+    summarize(pre_sym = round( mean(rdqPRE_sym, na.rm = TRUE),2),
+              pre_sym_sd = round( sd(rdqPRE_sym, na.rm = TRUE),2),
+              post_sym = round( mean(rdqPOST_sym, na.rm = TRUE),2),
+              post_sym_sd = round( sd(rdqPOST_sym, na.rm = TRUE),2),
+              delta_sym = round( mean(rdq_sym_change, na.rm = TRUE),2),
+              delta_sym_sd = round( sd(rdq_sym_change, na.rm = TRUE),2)
+              )
+
+      Scores_tab[9,] = c(
+              "Symptoms",
+              #Non-responder scores
+              paste0(sym_rep_tab$pre_sym[[1]]," (",sym_rep_tab$pre_sym_sd[[1]],")"),
+              paste0(sym_rep_tab$post_sym[[1]]," (",sym_rep_tab$post_sym_sd[[1]],")"),
+              paste0(sym_rep_tab$delta_sym[[1]]," (",sym_rep_tab$delta_sym_sd[[1]],")"),
+              #responder scores
+              paste0(sym_rep_tab$pre_sym[[2]]," (",sym_rep_tab$pre_sym_sd[[2]],")"),
+              paste0(sym_rep_tab$post_sym[[2]]," (",sym_rep_tab$post_sym_sd[[2]],")"),
+              paste0(sym_rep_tab$delta_sym[[2]]," (",sym_rep_tab$delta_sym_sd[[2]],")")
+            )
+Scores_tab
+```
+
+### Disorder Breakdowns
+Here are some tables displaying info on the psychiatric disorders treated at the PHP
+```{r}
 # Disorders by treatment response
@@
                                      data = Mothership_post))
+colnames(Dis_tab) = c("Variables","Non Responder", "Responder", "Total")
 Dis_tab
 
-#Full demographic break down.
+#Full demographic break down
+co_dis_tab <- Mothership_Diag_treat |>
+  pivot_longer(
+    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
+    names_to = 'Co Occuring',
+    values_to = "Number"
+  ) |>
+  select(Disorder_treat, `Co Occuring`, Number) |>
+  filter(Number != 0,
+         !is.na(`Co Occuring`),
+         !is.na(Disorder_treat))
+
 CODis_tab<-data.frame(table1::table1(~`Co Occuring` | Disorder_treat, data = co_dis_tab))
+colnames(CODis_tab)[1] = c("Variables")
 CODis_tab
-
-Mothership_post$Current_Dx
-```
-
-```{r}
-#Treatment Scores
-
-  # I'm imagining a table that has all of the averages under 3 columns 
-      # Pre, post, delta | (mean, SD)
-  # variables involved = 
-      # CUXOS, CUDOS, RDQ, 
-  # can I make this break up by treatment response?
-
-resp_tab <- data.frame(table1::table1(
-  ~CUXOS_pre + CUXOS_post + Delta_Anx_DC + CUXOS_pre + CUXOS_post + Delta_Anx_DC +   | RESPONDER_FIGS, 
-  data = Mothership_post))
-colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
-resp_tab
-
-View(Mothership_post)
-
-#Read in a New Data Set
-Mothership_RDQ<- read_sav("~/Desktop/Coding/data/Mothership_DV.sav")
-Mothership_RDQ<-select(Mothership,ID1:Sexuality_1,MDD_C:Day40_CUXOS)
-Mothership_RDQ<-data.frame(sapply(Mothership_RDQ,FUN=as.numeric))
-
-#Make This Data Set Long Data
-library(tidyr)
-Mothership_Long_RDQ <- gather(Mothership_Diag_treat,rm,RDQ,rdqPRE_coping:rdqPOST_sym,
-                              factor_key = "T")
-Mothership_Long_RDQ <- Mothership_Long_RDQ[order(Mothership_Long_RDQ$ID1),]
-
-#Create a Time Variable
-Mothership_Long_RDQ$PrePost <- NA
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_coping"]<-"Pre"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_pmh"]<-"Pre"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_func"]<-"Pre"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_wbs"]<-"Pre"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPRE_sym"]<-"Pre"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_coping"]<-"Post"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_pmh"]<-"Post"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_func"]<-"Post"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_wbs"]<-"Post"
-Mothership_Long_RDQ$PrePost[Mothership_Long_RDQ$rm=="rdqPOST_sym"]<-"Post"
-
-#Create a New Data Set with an Average Depression Variable and Race
-Mothership_Mean_RDQ<-Mothership_Long_RDQ %>%
-  group_by(rm,PrePost) %>%
-  summarise(RDQ=mean(RDQ,na.rm=TRUE))
-
-#Add a Paired Variable to the New Data Set
-Mothership_Mean_RDQ<-mutate(Mothership_Mean_RDQ,
-                            paired=case_when(rm=="rdqPRE_coping"~"1",
-                                             rm=="rdqPOST_coping"~"1",
-                                             rm=="rdqPRE_pmh"~"2",
-                                             rm=="rdqPOST_pmh"~"2",
-                                             rm=="rdqPRE_func"~"3",
-                                             rm=="rdqPOST_func"~"3",
-                                             rm=="rdqPRE_wbs"~"4",
-                                             rm=="rdqPOST_wbs"~"4",
-                                             rm=="rdqPRE_sym"~"5",
-                                             rm=="rdqPOST_sym"~"5"))
-
-Mothership_Mean_RDQ[,1] = c("Coping","PMH","Functioning","WBS","Symptoms","Coping","PMH","Functioning","WBS","Symptoms")
-
-wide_rdq <- Mothership_Mean_RDQ |>
-  pivot_wider(
-    names_from = PrePost, values_from = RDQ
-  ) |>
-  select(
-    rm,Pre,Post
-  )
-
-#Table
-wide_rdq
-
 ```
@@
 ```{r}
+cor_tab<- Mothership_post |>
+  select( c(
+    # Demographics
+    Age_1,Some_College:Discharge,
+    # Treatment info
+    IPT_track_1, Days_complete_1, # Days_noshow_1, Days_not_attended_1, Days_cancel_1,
+    # Disorders
+    Mood_D:Other,Co_Anx:Co_Trauma,Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    # RDQ
+    rdq_coping_change:rdq_sym_change
+
+  ))
+
+#comments about what I should do
+      #Should I make a level of anxiety / depression - cuxos cut offs?
+      # should I use the first score or the pre score?
+      # Should I do each individual disorder, or just the overarching classes (i.e., depression)?
+      # should I include co_occuring even if there is a lot of overlap (i.e., depressive P and Co)
+
+# View(cor_tab)
+# View(Mothership_post)
+
+# install.packages("ggcorrplot")
+# library(ggcorrplot)
+model.matrix(~0+., data=cor_tab) %>% 
+  cor(use="pairwise.complete.obs") %>% 
+  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
 
@@
 ```{r}
+DEP_RCI <- JTRCI (data = RCI_df_dep, 
+                  pre = "pre", 
+                  post = "post", 
+                  ppid = "ID1", 
+                  reliability = .74, 
+                  indextype = "RCI", 
+                  #JTcrit = "auto",
+                  plottitle = "Anxeity: JT indices by disorder")
+
+ANX_RCI <- JTRCI (data = RCI_df_anx, 
+                  pre = "pre", 
+                  post = "post", 
+                  ppid = "ID1", 
+                  reliability = .74, 
+                  indextype = "RCI", 
+                  #JTcrit = "auto",
+                  plottitle = "Anxeity: JT indices by disorder")
+
+RCI_DF<- ANX_RCI$data
+colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")
+
+RCI_DF2<- DEP_RCI$data
+colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")
+
+RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
+colnames(RCI_DF)[1] = "ID1"
+
+RCI_DF
+
+###############          Adding RCI to dataset       ####################
+
+Mothership_post <- Mothership_post |>
+  #1. Filter out scores for people not in the program / don't have data
+  filter(!is.na(Days_complete_1)) |>
+  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
+  filter(!is.na(CUXOS_pre),
+         !is.na(CUXOS_post),
+         CUXOS_pre > 0,
+         CUXOS_post >= 0,
+         !is.na(CUDOS_pre),
+         !is.na(CUDOS_post),
+         CUDOS_pre > 0,
+         CUDOS_post> 0
+         ) |>
+  mutate(
+    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
+    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
+    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
+    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
+    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
+    Anx_Responder = as.factor(
+      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
+      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
+      )),
+    Dep_Responder = as.factor(
+      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
+      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
+      )),
+    Treatment_Responder = as.factor(
+      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
+      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
+      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
+      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
+      )))))))))))
+
+#2. Left join data from the RCI dataset into the Mothership_post df
+Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
+  mutate(
+    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
+    Depression_Responder = as.factor(recode(Depression_Responder,
+                                            "1" = "2",
+                                            "2" = "2",
+                                            "3" = "1"
+    )),
+    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
+    Depression_Responder = as.factor(recode(Depression_Responder,
+                                            "2" = "Non-Responder",
+                                            "1" = "Responder"
+    )),
+    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
+    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+                                         "1" = "2",
+                                         "2" = "2",
+                                         "3" = "1"
+    )),
+    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
+    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+                                         "2" = "Non-Responder",
+                                         "1" = "Responder"
+    )),
+    RESPONDER_FIGS = as.factor(
+      ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
+             ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
+      ))) |>
+  filter(!is.na(RESPONDER_FIGS))
 

### 2024-02-18 Lasso_RCI_Response.Rmd
I DID THE THING!!!

@@
 Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
-DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
+#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
 
@@
 # We can change the current variables to make them easier to interpret.
-str(Mothership_post$Education_1)
 
@@
                      Some_College = recode(Education_1,
-                                          "<Grade 12" = "No College",
-                                          "<Grade 12" = "No College",
-                                          "HS Diploma or GED" = "No College",
-                                          "HS Diploma or GED" = "No College",
-                                          "Some College/Associates Degree" = "Some College",
-                                          "Some College/Associates Degree" = "Some College",
-                                          "Bachelors Degree" = "Some College",
-                                          "Bachelors Degree" = "Some College",
-                                          "Grad Degree" ="Some College"),
+                                          "<Grade 12" = "0",
+                                          "<Grade 12" = "0",
+                                          "HS Diploma or GED" = "0",
+                                          "HS Diploma or GED" = "0",
+                                          "Some College/Associates Degree" = "1",
+                                          "Some College/Associates Degree" = "1",
+                                          "Bachelors Degree" = "1",
+                                          "Bachelors Degree" = "1",
+                                          "Grad Degree" ="1"),
                      Gender_1 = as.factor(Gender_1),
@@
                      Female= recode(Gender_1,
-                                       "Female" = "Female",
-                                       "Male" = "Not",
-                                       "Non-Binary" = "Not",
-                                       "Other" = "Not",
-                                       "Other" = "Not"),
+                                       "Female" = "1",
+                                       "Male" = "0",
+                                       "Non-Binary" = "0",
+                                       "Other" = "0",
+                                       "Other" = "0"),
                       Relationship_1 = ifelse(Relationship_1 == 8, NA, Relationship_1),
@@
                      Married = recode(Relationship_1,
-                                             "Married or Cohabitating" = "Married or Cohabitating",
-                                             "Widowed or Separated" = "Not",
-                                             "Divorced" = "Not",
-                                             "Single or Never Married" = "Not"),
+                                             "Married or Cohabitating" = "1",
+                                             "Widowed or Separated" = "0",
+                                             "Divorced" = "0",
+                                             "Single or Never Married" = "0"),
                      Sexuality_1 = as.factor(Sexuality_1),
@@
                      Straight = recode(Sexuality_1,
-                                         "Straight" = "Straight",
-                                          "Gay" = "Not Straight",
-                                          "Bisexual" = "Not Straight",
-                                          "Other" = "Not Straight"),
+                                         "Straight" = "1",
+                                          "Gay" = "0",
+                                          "Bisexual" = "0",
+                                          "Other" = "0"),
                      IPT_track_1 = as.factor(IPT_track_1),
@@
                      White = recode(Race_1,
-                                     "White" = "White",
-                                     "Black" = "Not White",
-                                     "Hispanic"="Not White",
-                                     "Asian"="Not White",
-                                     "Portugese"="Not White",
-                                     "Other"="Not White"),
+                                     "White" = "1",
+                                     "Black" = "0",
+                                     "Hispanic"="0",
+                                     "Asian"="0",
+                                     "Portugese"="0",
+                                     "Other"="0"),
                      DC_status_1 = as.factor(DC_status_1),
@@
                      Discharge = recode(DC_status_1,
-                                          "Treatment Complete" = "Treatment Successful",
-                                          "Treatment nearly complete" = "Treatment Successful",
-                                          "Insurance no longer covering" = "Other",
-                                          "Nonattendance" = "Other",
-                                          "Inappropriate (language)/Referred to another tx setting" ="Other",
-                                          "Transferred to inpatient"="Other",
-                                          "Withdrew due to external limitations"="Other",
-                                          "Withdrew AMA"="Other",
-                                          "Other"="Other",
-                                          "Other"="Other",
-                                          "Other"="Other"),
+                                          "Treatment Complete" = "1",
+                                          "Treatment nearly complete" = "1",
+                                          "Insurance no longer covering" = "0",
+                                          "Nonattendance" = "0",
+                                          "Inappropriate (language)/Referred to another tx setting" ="0",
+                                          "Transferred to inpatient"="0",
+                                          "Withdrew due to external limitations"="0",
+                                          "Withdrew AMA"="0",
+                                          "Other"="0",
+                                          "Other"="0",
+                                          "Other"="0"),
 #Lets make some new variables 
@@
         GAD_P ==1 | Panic_P == 1 | PanicAgor_P == 1 | Agoraphobia_P == 1 |
-          Social_P == 1 | Specific_P == 1, 1, 0)),
+          Social_P == 1 | Specific_P == 1 | OCD_P == 1, 1, 0)),
     # Obsessive Compusive Disorders
     #OCD_P is for current OCD
-    OCD_P = as.factor(OCD_P),
+        #OCD_P = as.factor(OCD_P),
     # Personality Disorders
@@
         Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1 |
-          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1 | Schiz_P == 1 | 
-          Schizaff_P == 1 | Alcohol_P == 1 | Drug_P ==1 | OCD_P ==1,
+          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1 | 
+          Schiz_P == 1 |  Schizaff_P == 1,  
         1,0)),
@@
       ifelse(Anxiety_D == 1, "Anxiety",
-             ifelse(OCD_P == 1, "OCD",
                     ifelse(BPD_P == 1, "BPD",
@@
                                                               ifelse(Somatic_D == 1, "Somatic", NA
-                                                              )))))))))),
+                                                              ))))))))),
     Disorder_treat = as.factor(
@@
                            ifelse(Mood_D == 1, "Mood",
-                                  ifelse(OCD_P == 1, "Other",
+                                  #ifelse(OCD_P == 1, "Anxiety",
+                                     #felse(OCD_P == 1, "Other",
                                          ifelse(Substance_D == 1, "Other",
                                                 ifelse(Psychotic_D == 1, "Other", 
-                                                       ifelse(Eating_D == 1, "Other", NA
+                                                       ifelse(Eating_D == 1, "Other",
+                                                          ifelse(Somatic_D == 1, "Other",NA
                                                        ))))))))),
@@
                 Social_P != 1 & Social_C == 1 | 
+                #OCD_P != 1 & OCD_C == 1 |
                 Specific_P != 1 & Specific_C == 1, 1, 0)),
@@
                Hypochondriasis_P != 1 &  Hypochondriasis_C == 1, 1,0)),
-    OCD_Co_C = as.factor(
-      ifelse(OCD_P != 1 & OCD_C == 1,1,0)),
+    Other_C = as.factor(
+      ifelse(
+        Somatic_C == 1 | Eating_C == 1 | Psychotic_C == 1, 1, 0)),
+
+    #OCD_Co_C = as.factor(
+     # ifelse(OCD_P != 1 & OCD_C == 1,1,0)),
     BPD_Co_C = as.factor(
@@
       ifelse(BPD_Co_C == 0 &
-               OCD_Co_C == 0 &
                Somatic_C == 0 & 
@@
     Other_Co = as.factor(
-      ifelse(OCD_Co_C == 1 & 
-               Somatic_C == 1 & 
+      ifelse(  Somatic_C == 1 & 
                Eating_C == 1 &
@@
       ifelse(Anxiety_C == 1 & Mood_D == 1 |
-               Anxiety_C == 1 & OCD_P == 1 |
                Anxiety_C == 1 & BPD_P == 1 |
@@
       ifelse(Mood_C == 1 & Anxiety_D == 1 |
-               Mood_C == 1 & OCD_P == 1 |
                Mood_C == 1 & BPD_P == 1 |
@@
                Mood_C == 1 & Somatic_D==1 , 1, 0)),
-    Co_OCD = as.factor(
-      ifelse(OCD_C == 1 & Anxiety_D == 1 |
-               OCD_C == 1 & Mood_D == 1 |
-               OCD_C == 1 & BPD_P== 1 |
-               OCD_C == 1 & Substance_D == 1 |
-               OCD_C == 1 & Trauma_D == 1 |
-               OCD_C == 1 & Eating_D ==1 |
-               OCD_C == 1 & Psychotic_D ==1 |
-               OCD_C == 1 & Somatic_D ==1, 1, 0)),
     Co_BPD = as.factor(
-      ifelse(BPD_C == 1 & Anxiety_D == 1 |
-               BPD_C == 1 & Mood_D == 1 |
-               BPD_C == 1 & OCD_P== 1 |
-               BPD_C == 1 & Substance_D == 1 |
-               BPD_C == 1 & Trauma_D == 1 |
-               BPD_C == 1 & Eating_D ==1 |
-               BPD_C == 1 & Psychotic_D ==1 |
-               BPD_C == 1 & Somatic_D ==1 , 1, 0)),
+      ifelse(BPD_Co_C == 1 & Anxiety_D == 1 |
+               BPD_Co_C == 1 & Mood_D == 1 |
+               BPD_Co_C == 1 & Substance_D == 1 |
+               BPD_Co_C == 1 & Trauma_D == 1 |
+               BPD_Co_C == 1 & Eating_D ==1 |
+               BPD_Co_C == 1 & Psychotic_D ==1 |
+               BPD_Co_C == 1 & !BPD_P == 
+               BPD_Co_C == 1 & Somatic_D ==1 , 1, 0)),
     Co_Psychotic = as.factor(
       ifelse(Psychotic_C == 1 & Mood_D == 1 |
-               Psychotic_C == 1 & OCD_P == 1 |
                Psychotic_C == 1 & BPD_P == 1 |
@@
       ifelse(Eating_C == 1 & Mood_D == 1 |
-               Eating_C == 1 & OCD_P == 1 |
                Eating_C == 1 & BPD_P == 1 |
@@
       ifelse(Somatic_C == 1 & Mood_D == 1 |
-               Somatic_C == 1 & OCD_P == 1 |
                Somatic_C == 1 & BPD_P == 1 |
@@
       ifelse(Substance_C == 1 & Mood_D == 1 |
-               Substance_C == 1 & OCD_P == 1 |
                Substance_C == 1 & BPD_P == 1 |
@@
       ifelse(Trauma_C == 1 & Mood_D == 1 |
-               Trauma_C == 1 & OCD_P == 1 |
                Trauma_C == 1 & BPD_P == 1 |
@@
                Trauma_C == 1 & Psychotic_D ==1, 1, 0)),
-  )
-
+    Co_Other = as.factor(
+      ifelse(
+        Co_Substance == 1 |
+        Co_Somatic == 1 |
+        Co_Eating == 1 |
+        Co_Psychotic == 1, 1, 0))
+      )
+
+summary(Mothership$Co_Anx)
+table(Mothership$Anxiety_D, Mothership$Co_Anx)
 ##### df for plots
@@
     dummy = -99
-  )
+  ) |>
+  filter(!is.na(Disorder_treat),
+         !is.na(TxYear),
+         !is.na(Duration))
 
 # df without NAs in date and disorder type
-Mothership_Diag <- Mothership |>
-  filter(!is.na(Disorder_Type)) |>
-  filter(!is.na(TxYear))
-
-# Mothership_Diag_treat <- Mothership |>
-#   filter(!is.na(Disorder_treat),
-#          !is.na(TxYear),
-#          !is.na(Duration))
+
+Mothership_Diag_treat <- Mothership |>
+  filter(!is.na(Disorder_treat),
+         !is.na(TxYear),
+         !is.na(Duration))
 
 ### Export as CSV
-write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag.csv")
+write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag_treat.csv")
 
@@
 #1. load DF
-  Mothership_post <- Mothership_Diag_treat
+  Mothership_post <- Mothership
 
@@
 RCI_DF
-
+```
+
+```{r}
 ###############          Adding RCI to dataset       ####################
@@
 
+# Data analysis 
 ## Part 1: Who is attending?
@@
 #Full demographic break down
-co_dis_tab <- Mothership_Diag_treat |>
+
+co_dis_tab <- Mothership_post |>
+  filter(
+      !is.na(rdq_func_change),
+      !is.na(rdq_pmh_change),
+      !is.na(rdq_coping_change),
+      !is.na(rdq_wbs_change)
+  ) |>
   pivot_longer(
-    cols = c("Co_Anx","Co_Mood","Co_OCD","Co_BPD","Co_Psychotic","Co_Eating","Co_Somatic", "Co_Substance","Co_Trauma", "No_Co"),
+    cols = c("Anxiety_C","Mood_C","BPD_Co_C","Other_C", "Substance_C","Trauma_C", "No_Co"),
     names_to = 'Co Occuring',
@@
          !is.na(`Co Occuring`),
-         !is.na(Disorder_treat))
+         !is.na(Disorder_treat),
+         )
 
@@
 ```{r}
-cor_tab<- Mothership_post |>
+Vars_FULL <- Mothership_lasso |>
   select( c(
+    RESPONDER_FIGS,
     # Demographics
-    Age_1,Some_College:Discharge,
+    Age_1,Some_College:Married,White, #Discharge,
     # Treatment info
-    IPT_track_1, Days_complete_1, # Days_noshow_1, Days_not_attended_1, Days_cancel_1,
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
     # Disorders
-    Mood_D:Other,Co_Anx:Co_Trauma,Current_Dx,
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
+    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
+    Current_Dx,
     # Pre-Post stuff
@@
     # RDQ
-    rdq_coping_change:rdq_sym_change
-
+    rdq_coping_change:rdq_wbs_change
   ))
-
-#comments about what I should do
-      #Should I make a level of anxiety / depression - cuxos cut offs?
-      # should I use the first score or the pre score?
-      # Should I do each individual disorder, or just the overarching classes (i.e., depression)?
-      # should I include co_occuring even if there is a lot of overlap (i.e., depressive P and Co)
-
-# View(cor_tab)
-# View(Mothership_post)
+Vars_FULL <- na.omit(Vars_FULL)
 
 # install.packages("ggcorrplot")
-# library(ggcorrplot)
-model.matrix(~0+., data=cor_tab) %>% 
+library(ggcorrplot)
+model.matrix(~0+., data=Vars_FULL) %>% 
   cor(use="pairwise.complete.obs") %>% 
   ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
-
 ```
@@
 ```{r}
-DEP_RCI <- JTRCI (data = RCI_df_dep, 
-                  pre = "pre", 
-                  post = "post", 
-                  ppid = "ID1", 
-                  reliability = .74, 
-                  indextype = "RCI", 
-                  #JTcrit = "auto",
-                  plottitle = "Anxeity: JT indices by disorder")
-
-ANX_RCI <- JTRCI (data = RCI_df_anx, 
-                  pre = "pre", 
-                  post = "post", 
-                  ppid = "ID1", 
-                  reliability = .74, 
-                  indextype = "RCI", 
-                  #JTcrit = "auto",
-                  plottitle = "Anxeity: JT indices by disorder")
-
-RCI_DF<- ANX_RCI$data
-colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")
-
-RCI_DF2<- DEP_RCI$data
-colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")
-
-RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
-colnames(RCI_DF)[1] = "ID1"
-
-RCI_DF
-
-###############          Adding RCI to dataset       ####################
-
-Mothership_post <- Mothership_post |>
-  #1. Filter out scores for people not in the program / don't have data
-  filter(!is.na(Days_complete_1)) |>
-  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
-  filter(!is.na(CUXOS_pre),
-         !is.na(CUXOS_post),
-         CUXOS_pre > 0,
-         CUXOS_post >= 0,
-         !is.na(CUDOS_pre),
-         !is.na(CUDOS_post),
-         CUDOS_pre > 0,
-         CUDOS_post> 0
-         ) |>
-  mutate(
-    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
-    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
-    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
-    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
-    #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
-    Anx_Responder = as.factor(
-      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
-      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
-      )),
-    Dep_Responder = as.factor(
-      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
-      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
-      )),
-    Treatment_Responder = as.factor(
-      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
-      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
-      )))))))))))
-
-#2. Left join data from the RCI dataset into the Mothership_post df
-Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
-  mutate(
-    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
-    Depression_Responder = as.factor(recode(Depression_Responder,
-                                            "1" = "2",
-                                            "2" = "2",
-                                            "3" = "1"
-    )),
-    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
-    Depression_Responder = as.factor(recode(Depression_Responder,
-                                            "2" = "Non-Responder",
-                                            "1" = "Responder"
-    )),
-    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
-    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
-                                         "1" = "2",
-                                         "2" = "2",
-                                         "3" = "1"
-    )),
-    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
-    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
-                                         "2" = "Non-Responder",
-                                         "1" = "Responder"
-    )),
-    RESPONDER_FIGS = as.factor(
-      ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
-             ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
-      ))) |>
-  filter(!is.na(RESPONDER_FIGS))
-
-```
-
-## Part 3
-Logistic lasso
+
+RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
+colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
+#anxiety 
+RCI_table[1,] = c("CUXOS", unlist(summary(Mothership_post$Anxiety_Responder)))
+# Depresssion
+RCI_table[2,] = c("CUDOS", unlist(summary(Mothership_post$Depression_Responder)))
+#Total
+RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
+
+RCI_table
+```
+
+## Part 3 Logistic lasso
 
@@
 
+https://github.com/sydeaka/Using-Elastic-net-for-model-Selection-with-missing-data/blob/master/model_selection_missing_data-example.R
+http://www.sthda.com/english/articles/36-classification-methods-essentials/149-penalized-logistic-regression-essentials-in-r-ridge-lasso-and-elastic-net/
+
+Preparing data for Lasso
 \scriptsize
@@
 library(glmnet)
-ecls2$preds = as.matrix(ecls2[ ,c(1:8,14:22)])
-
-# lambda = 0
-lasso1 = glmnet(ecls2$preds, ecls2$g8_sci_tht, alpha=1, lambda=0, 
-                standardize=TRUE, intercept=TRUE)
-lasso1
-
-coef(lasso1)
-```
-
-### Lasso Regression
-\scriptsize
-```{r}
-## lambda = .1
-lasso2 = glmnet(ecls2$preds, ecls2$g8_sci_tht, alpha=1, lambda=.1,
-                standardize=TRUE, intercept=TRUE)
-lasso2
-
-coef(lasso2)
-```
-
-### $k$-fold Cross Validation
-\scriptsize
+library(caret)
+#Make sure there are no NAs within the dataset
+Mothership_lasso <- Mothership_post |>
+    filter(
+    !is.na(Some_College),
+    !is.na(Female),
+    !is.na(IPT_track_1),
+    !is.na(White),
+    !is.na(RESPONDER_FIGS)
+  )
+
+# View(Mothership_lasso)
+
+Vars <- Mothership_lasso |>
+  select( c(
+    RESPONDER_FIGS,
+    # Demographics
+    Age_1,Some_College:Married,White,
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, 
+    # Disorders
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
+    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
+    Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, 
+  ))
+
+```
+
 ```{r, warning=FALSE, message=FALSE}
-#1. set seed
-set.seed(19860608)
-#2. sample data from the number of rows in els2
-ecls2 = ecls2[sample(nrow(ecls2)),]
-#3. convert ecls2a a new datafraame that is scaled and mean centered.
-ecls2a = as.data.frame(scale(ecls2, center=TRUE, scale=TRUE))
-#4. create a new column of values with predictors
-ecls2a$pred = as.matrix(ecls2a[,c(1:8,14:22)])
-
-#5. define the number of folds: cut a sequence from 1-num rows in ecls2a, broken into 10 equal parts, without labels)
-folds = cut(seq(1,nrow(ecls2a)), breaks=10, labels=FALSE)
-
-#6. create a grid (Sequence) from 0 - 1 increasing by .001
-grid = seq(0, 1, by=.001)
-#.7 make a matrix full of NAs that is 10 columns wide and the length of grid long? 
-    # I think MSE = mean squared error?
-mse  = matrix(NA, 10, length(grid))
-
-#8. create a for loop (for each row in the number of columns (1-10))
-for(i in 1:10){
-  #9. the test cases are the first number for each fold
-  testCases = which(folds==i,arr.ind=TRUE)
-  test      = ecls2a[testCases, ]
-  #10. the train cases are the valeus not the test cases
-  train     = ecls2a[-testCases, ]
-
-  #11. another for loop for each value in 1 - length of grid)
-  for (j in 1:length(grid)){
-    #12. k lambda = the index of grid[j]
-    klambda = grid[j]
-    #13. run a fit train regression model with predictors, for train$g8_Sci_tht.
-    fitTrain = glmnet(train$pred, train$g8_sci_tht, 
-                      alpha=1, lambda=klambda,
-                      standardize=FALSE, intercept=TRUE)
-    #14. predict the test values using predict using the fitTrain model, and using the new x values as test$pred
-    fit_test = predict(fitTrain, newx=test$pred)
-    #15. at each index of mse, take the mean of the differnece between the test value, and the fit test values and square them
-    mse[i,j] = mean((test$g8_sci_tht - fit_test)^2)
-  }
-}
-
-# 16. load matrixStats
-library(matrixStats)
-
-#17. assign a varaible that is column means of mse
-mseMeans = colMeans(mse, na.rm=TRUE)
-#18. assign column sd
-mseSds = colSds(mse, na.rm=TRUE)
-
-# Find minimum - find the one which has the minimum mean square error 
-best = which.min(mseMeans)
-grid[best]
-
-# Find simplest model within 1 Standard Error - best close 
-maxMse = mseMeans[best] + mseSds[best]/sqrt(10)
-bestClose = max(which(mseMeans<maxMse))
-grid[bestClose]
-```
-
-K-fold cross-validation can be performed using the cv.glmnet function.
-In addition to all the glmnet parameters, cv.glmnet has its special parameters including nfolds (the number of folds), foldid (user-supplied folds), and type.measure(the loss used for cross-validation):
-
-“deviance” or “mse” for squared loss, MSE = mean squared loss
-
-### Lasso Regression
-\scriptsize
-```{r}
-lasso3 = glmnet(ecls2a$pred, ecls2a$g8_sci_tht, alpha=1, lambda=grid[best],
-                standardize=FALSE, intercept=TRUE)
-coef(lasso3)
-```
-
-### Lasso Regression
-\scriptsize
-```{r}
-lasso4 = glmnet(ecls2a$pred, ecls2a$g8_sci_tht, alpha=1, lambda=grid[bestClose],
-                standardize=FALSE, intercept=TRUE)
-coef(lasso4)
-```
-
-### Relaxed Lasso
-\scriptsize
-```{r}
-rlasso4 = lm(g8_sci_tht~gender+kage+k_math_tht+k_gk_tht+f_mtr+
-             poor, data=ecls2)
-summary(rlasso4)
-```
-
-*Relaxed Lasso*
-- I After variable selection using the lasso, an OLS regression model is fit with only the variables selected
-- The estimates for retained variables are not shrunken
-
-*Cautions*
-- When performing cross validation, it’s important to standardize
-variables before creating folds
-- Similarly, when creating the final prediction model, it is important for the standardization process to be the same across datasets
-    + Same means and standard deviations are used across datasets
-- Relaxed lasso avoids the standardization process when creating
-final model
-- Built in k-fold cross-validation using glmnet:
-
-### $\mathtt{cv.glmnet}$ function in $\mathtt{glmnet}$
- - Built in $k$-fold cross-validation using $\text{glmnet}$
-
-\scriptsize
-```{r}
-cvGlmnet = cv.glmnet(ecls2a$pred, ecls2a$g8_sci_tht, 
-                     alpha=1, type.measure='mse', 
-                     nfolds=10)
-cvGlmnet$lambda.min
-cvGlmnet$lambda.1se
-
-plot(cvGlmnet)
-```
+# View(Mothership_lasso)
+# head(Vars)
+# sum(is.na(Vars))
+Vars_FULL <- Mothership_lasso |>
+  select( c(
+    RESPONDER_FIGS,
+    # Demographics
+    Age_1,Some_College:Married,White, #Discharge,
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    # Disorders
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
+    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
+    Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    # RDQ
+    rdq_coping_change:rdq_wbs_change
+  ))
+
+Vars_FULL <- na.omit(Vars_FULL)
+```
+# with RDQ
+```{r}
+# Create Training and testing data
+set.seed(123) 
+training.samples <- Vars_FULL$RESPONDER_FIGS %>% 
+  createDataPartition(p = 0.8, list = FALSE)
+train.data  <- Vars_FULL[training.samples, ]
+test.data <- Vars_FULL[-training.samples, ]
+
+# Dumy code categorical predictor variables
+x <- model.matrix(RESPONDER_FIGS~., train.data)[,-1]
+# Convert the outcome (class) to a numerical variable
+y <- ifelse(train.data$RESPONDER_FIGS == "Responder", 1, 0)
+
+#Simplified lasso
+lasso1 <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)
+plot(lasso1, "lambda", label = TRUE)
+```
+
+Find coefficients using cv.lasso
+```{r}
+# Find the best lambda using cross-validation
+set.seed(123) 
+cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
+
+#The exact value of lambda can be viewed as follow:
+print(paste0("This is the minimum lambda value: ", round(cv.lasso$lambda.min,5)))
+
+#This value is called lambda.1se.
+print(paste0("This is the 1 standard error lambda value: ", round(cv.lasso$lambda.1se,5)))
+
+# Fit the final model on the training data
+model <- glmnet(x, y, alpha = 1, family = "binomial",
+                lambda = cv.lasso$lambda.min)
+# Display regression coefficients
+coef(model)
+# Make predictions on the test data
+x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
+probabilities <- model %>% predict(newx = x.test)
+predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
+# Model accuracy
+observed.classes <- test.data$RESPONDER_FIGS
+mean(predicted.classes == observed.classes)
+
+#Using lambda.min as the best lambda, gives the following regression coefficients:
+coef(cv.lasso, cv.lasso$lambda.min)
+
+#Using lambda.1se as the best lambda, gives the following regression coefficients:
+coef(cv.lasso, cv.lasso$lambda.1se)
+```
+
+Evaluating if we should use Lasso min or 1SE
+```{r}
+####  Using Min
+# Final model with lambda.min
+lasso.model.min <- glmnet(x, y, alpha = 1, family = "binomial",
+                      lambda = cv.lasso$lambda.min)
+
+coef(lasso.model.min)
+# Make prediction on test data
+x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
+probabilities <- lasso.model.min %>% predict(newx = x.test)
+predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
+# Model accuracy
+observed.classes <- test.data$RESPONDER_FIGS
+Mean.predict.min <- mean(predicted.classes == observed.classes)
+
+#####  using 1se
+# Final model with lambda.1se
+lasso.model.1se <- glmnet(x, y, alpha = 1, family = "binomial",
+                      lambda = cv.lasso$lambda.1se)
+coef(lasso.model.1se)
+# Make prediction on test data
+x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
+probabilities <- lasso.model.1se %>% predict(newx = x.test)
+predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
+
+# Model accuracy rate
+observed.classes <- test.data$RESPONDER_FIGS
+Mean.predict.1se <- mean(predicted.classes == observed.classes)
+
+#### full model
+# Fit the model
+full.model <- glm(RESPONDER_FIGS ~ ., data = train.data, family = "binomial")
+
+# Make predictions
+probabilities <- full.model %>% predict(test.data, type = "response")
+predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
+# Model accuracy
+observed.classes <- test.data$RESPONDER_FIGS
+Mean.predict.full.model <- mean(predicted.classes == observed.classes)
+
+predict.df <- data.frame(
+  model = c("Min", "1se", "Full"),
+  values = c(Mean.predict.min,Mean.predict.1se,Mean.predict.full.model)
+)
+predict.df
+```
+plot the lassos
+If We want to do lasso in ggplot
+https://stackoverflow.com/questions/48978179/plotting-lasso-beta-coefficients
+
+```{r}
+##plot the lambda
+plot(lasso1, "lambda", label = TRUE)
+## Fancy plot
+library(lars)
+lasso_FULL = lars(x, y, type='lasso', 
+              trace=TRUE, normalize=FALSE, intercept=TRUE)
+plot(lasso_FULL, xvar='norm', breaks = FALSE, 
+     plottype = 'coefficients', omit.zeros = TRUE)
+
+#CV k folds cross validation
+plot(cv.lasso)
+```
+
+### Final relaxed lasso
+Minimum
+```{r}
+## install.packages("fuzzySim")
+library(fuzzySim) ## For FDR adjusted p values
+FDR(pvalues = p_values.min)
+
+library(broom)
+# https://cran.r-project.org/web/packages/broom/vignettes/broom.html
+
+## min model
+  glm_min <-  
+      glm(
+      #Outcome varaible
+        RESPONDER_FIGS ~ 
+      # predictors
+        Days_not_attended_1 + Anxiety_D + Mood_D + Substance_C + 
+        rdq_coping_change + rdq_pmh_change + rdq_func_change + rdq_wbs_change,
+      #data
+      data = Vars_FULL, 
+      # type of regression : logistic = binary / binomial
+      family = "binomial")
+# Summary of the model
+  summary.min      <- summary(glm_min)
+
+  tidy.summary.min <- tidy(glm_min)
+
+# Coefficients
+  coefs.min <- abs(coef(glm_min))
+
+# Odds ratio
+  OR.min <- exp(coef(glm_min))
+
+# OR 95% CI
+  CI.min <- data.frame(exp(confint(glm_min)))
+
+# P values
+  p.values.min <- data.frame(cbind(tidy.summary.min$term,tidy.summary.min$p.value))
+  # FDR Adjusted P Values
+    adj.p.min <- FDR(pvalues = p_values.min)
+    ADJ.p.values.min <- data.frame(rbind(adj.p.min$exclude, adj.p.min$select))
+
+# R^2 values  
+   R2.min <- performance::r2(glm_min)
+
+# df for Forrest plots
+FP.min <- data.frame(cbind(
+  Variable = tidy.summary.min$term[2:length(tidy.summary.min$term)],
+  OR = OR.min[2:length(OR.min)],
+  OR_low  = CI.min[2:length(CI.min$X2.5..),1],
+  OR_high = CI.min[2:length(CI.min$X97.5..),2],
+  p.values = p.values.min$X2[2:length(p.values.min$X2)]
+                    ))
+
+# Left join the FDR adjusted p.value
+FP.min <- left_join(FP.min,ADJ.p.values.min, by = join_by(p.values == p.value))
+FP.min
+```
+
+1se
+```{r}
+glm_1se <-  
+      glm(
+      #Outcome varaible
+        RESPONDER_FIGS ~ 
+      # predictors
+        Days_not_attended_1 + rdq_coping_change + rdq_pmh_change + rdq_func_change +
+        rdq_wbs_change,
+      #data
+      data = Vars_FULL, 
+      # type of regression : logistic = binary / binomial
+      family = "binomial")
+
+summary(glm_1se)
+
+# Summary of the model
+  summary.1se      <- summary(glm_1se)
+
+  tidy.summary.1se <- tidy(glm_1se)
+
+# Coefficients
+  coefs.1se <- abs(coef(glm_1se))
+
+# Odds ratio
+  OR.1se <- exp(coef(glm_1se))
+
+# OR 95% CI
+  CI.1se <- data.frame(exp(confint(glm_1se)))
+
+# P values
+  p.values.1se <- data.frame(cbind(tidy.summary.1se$term,tidy.summary.1se$p.value))
+
+  # FDR Adjusted P Values
+    adj.p.1se <- FDR(pvalues = p.values.1se)
+    ADJ.p.values.1se <- data.frame(rbind(adj.p.1se$exclude, adj.p.1se$select))
+
+# R^2 values  
+   R2.1se <- performance::r2(glm_1se)
+
+# df for Forrest plots
+FP.1se <- data.frame(cbind(
+  Variable = tidy.summary.1se$term[2:length(tidy.summary.1se$term)],
+  OR = OR.1se[2:length(OR.1se)],
+  OR_low  = CI.1se[2:length(CI.1se$X2.5..),1],
+  OR_high = CI.1se[2:length(CI.1se$X97.5..),2],
+  p.values = p.values.1se$X2[2:length(p.values.1se$X2)]
+                    ))
+
+# Left join the FDR adjusted p.value
+FP.1se <- left_join(FP.1se,ADJ.p.values.1se, by = join_by(p.values == p.value))
+FP.1se
+```
+
+# Without RDQ
+Evaluating Methods of Assessing “Optimism”  in Regression Models Daniel Thoya1,*, Antony Waititu1, Thomas Magheto1, Antony Ngunyi2 
+- chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/http://article.sciappliedmathematics.com/pdf/ajams-6-4-2.pdf
+
+Validation of prediction models based on lasso regression with multiply imputed data
+- https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/1471-2288-14-116#Sec18
+
+Penalized Logistic Regression Essentials in R: Ridge, Lasso and Elastic Net
+http://www.sthda.com/english/articles/36-classification-methods-essentials/149-penalized-logistic-regression-essentials-in-r-ridge-lasso-and-elastic-net/
+
+### Lasso regression - set variables
+```{r}
+# Create Training and testing data
+set.seed(123) 
+training.samples <- Vars_full$RESPONDER_FIGS %>% 
+  createDataPartition(p = 0.8, list = FALSE)
+train.data  <- Vars[training.samples, ]
+test.data <- Vars[-training.samples, ]
+
+# Dumy code categorical predictor variables
+x <- model.matrix(RESPONDER_FIGS~., train.data)[,-1]
+# Convert the outcome (class) to a numerical variable
+y <- ifelse(train.data$RESPONDER_FIGS == "Responder", 1, 0)
+
+#Simplified lasso
+lasso1 <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)
+
+plot(lasso1, "lambda", label = TRUE)
+```
+
+Find coefficients using cv.lasso
+```{r}
+# Find the best lambda using cross-validation
+cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
+# Fit the final model on the training data
+model <- glmnet(x, y, alpha = 1, family = "binomial",
+                lambda = cv.lasso$lambda.min)
+# Display regression coefficients
+coef(model)
+# Make predictions on the test data
+x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
+probabilities <- model %>% predict(newx = x.test)
+predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
+# Model accuracy
+observed.classes <- test.data$RESPONDER_FIGS
+mean(predicted.classes == observed.classes)
+
+### Compute lasso regression
+#Find the optimal value of lambda that minimizes the cross-validation error:
+set.seed(123)
+cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
+
+#The exact value of lambda can be viewed as follow:
+cv.lasso$lambda.min
+
+#This value is called lambda.1se.
+cv.lasso$lambda.1se
+
+#Using lambda.min as the best lambda, gives the following regression coefficients:
+coef(cv.lasso, cv.lasso$lambda.min)
+
+#Using lambda.1se as the best lambda, gives the following regression coefficients:
+coef(cv.lasso, cv.lasso$lambda.1se)
+```
+
+Evaluating if we should use Lasso min or SE
+```{r}
+#### Compute the final lasso model:
+# Final model with lambda.min
+lasso.model.min <- glmnet(x, y, alpha = 1, family = "binomial",
+                      lambda = cv.lasso$lambda.min)
+
+coef(lasso.model.min)
+# Make prediction on test data
+x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
+probabilities <- lasso.model.min %>% predict(newx = x.test)
+predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
+# Model accuracy
+observed.classes <- test.data$RESPONDER_FIGS
+mean(predicted.classes == observed.classes)
+
+#####  using 1se
+# Final model with lambda.1se
+lasso.model.1se <- glmnet(x, y, alpha = 1, family = "binomial",
+                      lambda = cv.lasso$lambda.1se)
+
+# Make prediction on test data
+x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
+probabilities <- lasso.model.1se %>% predict(newx = x.test)
+predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
+
+# Model accuracy rate
+observed.classes <- test.data$RESPONDER_FIGS
+mean(predicted.classes == observed.classes)
+
+#### full model
+# Fit the model
+full.model <- glm(RESPONDER_FIGS ~ ., data = train.data, family = "binomial")
+
+# Make predictions
+probabilities <- full.model %>% predict(test.data, type = "response")
+predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
+# Model accuracy
+observed.classes <- test.data$RESPONDER_FIGS
+mean(predicted.classes == observed.classes)
+```
+
+Visualizing it
+```{r}
+library(lars)
+
+lasso5 = lars(x, y, type='lasso', 
+              trace=TRUE, normalize=FALSE, intercept=TRUE)
+
+plot(lasso5, xvar='norm', breaks = FALSE, 
+     plottype = 'coefficients', omit.zeros = TRUE)
+```
+
+### Final relaxed lasso
+```{r}
+## min model
+  glm_1se <-  
+      glm(RESPONDER_FIGS ~ 
+      Days_complete_1 + Days_not_attended_1,
+      data = Vars, family = "binomial")
+# Summary of the model
+  summary.1se      <- summary(glm_1se)
+      library(broom)
+          # https://cran.r-project.org/web/packages/broom/vignettes/broom.html
+  tidy.summary.1se <- tidy(glm_1se)
+
+# Coefficients
+  coefs.1se <- abs(coef(glm_1se))
+
+# Odds ratio
+  OR.1se <- exp(coef(glm_1se))
+
+# OR 95% CI
+  CI.1se <- data.frame(exp(confint(glm_1se)))
+
+# P values
+  p.values.1se <- tidy.summary.1se$p.value
+
+# R^2 values  
+   R2.1se <- performance::r2(glm_1se)
+
+# df for Forrest plots
+
+FP.1se <- data.frame(cbind(
+  Variable = tidy.summary.1se$term[2:length(tidy.summary.1se$term)],
+  OR = OR.1se[2:length(OR.1se)],
+  OR_low  = CI.1se[2:length(CI.1se$X2.5..),1],
+  OR_high = CI.1se[2:length(CI.1se$X97.5..),2],
+  p.values = p.values.1se[2:length(p.values.1se)]
+                    ))
+
+FP.1se
+```
+
+```{r}
+### min model
+  glm_min <-  
+      glm(RESPONDER_FIGS ~ 
+      Age_1 + Some_College + Married + Days_complete_1 + Days_not_attended_1 + 
+      Psychotic_D + Co_Substance + Co_Trauma + CUDOS_pre,
+      data = Vars, family = "binomial")
+# Summary of the model
+  summary.min      <- summary(glm_min)
+      library(broom)
+          # https://cran.r-project.org/web/packages/broom/vignettes/broom.html
+  tidy.summary.min <- tidy(glm_min)
+
+# Coefficients
+  coefs.min <- abs(coef(glm_min))
+
+# Odds ratio
+  OR.min <- exp(coef(glm_min))
+
+# OR 95% CI
+  CI.min <- data.frame(exp(confint(glm_min)))
+
+# P values
+  p.values.min <- tidy.summary.min$p.value
+
+# R^2 values  
+   R2.min <- performance::r2(glm_min)
+
+# df for Forrest plots
+
+FP.min <- data.frame(cbind(
+  Variable = tidy.summary.min$term[2:length(tidy.summary.min$term)],
+  OR = OR.min[2:length(OR.min)],
+  OR_low  = CI.min[2:length(CI.min$X2.5..),1],
+  OR_high = CI.min[2:length(CI.min$X97.5..),2],
+  p.values = p.values.min[2:length(p.values.min)]
+                    ))
+
+FP.min
+```

### 2024-02-19 Lasso_RCI_Response.Rmd
Anxiety & Depression seperate LASSO

@@
 ```{r}
-Vars_FULL <- Mothership_lasso |>
+Vars_dep <- Mothership_post |>
   select( c(
-    RESPONDER_FIGS,
+    Depression_Responder,
     # Demographics
@@
   ))
-Vars_FULL <- na.omit(Vars_FULL)
-
-# install.packages("ggcorrplot")
-library(ggcorrplot)
-model.matrix(~0+., data=Vars_FULL) %>% 
-  cor(use="pairwise.complete.obs") %>% 
-  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
-```
-
-## Part 2: RCI ANALYSIS - Treatment Response
-Anxiety & Depression = Total response
-- Table 4: RCI Analsyis results
-  + Anxiety, Depression, Total response
-- Figure 2 / Supplimetal 2: RCI Analysis figs 
-  + Anxeity & Depression
-```{r}
-
-RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
-colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
-#anxiety 
-RCI_table[1,] = c("CUXOS", unlist(summary(Mothership_post$Anxiety_Responder)))
-# Depresssion
-RCI_table[2,] = c("CUDOS", unlist(summary(Mothership_post$Depression_Responder)))
-#Total
-RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
-
-RCI_table
-```
-
-## Part 3 Logistic lasso
-
-### Lasso Regression
-https://glmnet.stanford.edu/articles/glmnet.html
-https://www.mygreatlearning.com/blog/understanding-of-lasso-regression/
-https://bookdown.org/tpinto_home/Regularisation/lasso-regression.html
-
-https://github.com/sydeaka/Using-Elastic-net-for-model-Selection-with-missing-data/blob/master/model_selection_missing_data-example.R
-http://www.sthda.com/english/articles/36-classification-methods-essentials/149-penalized-logistic-regression-essentials-in-r-ridge-lasso-and-elastic-net/
-
-Preparing data for Lasso
-\scriptsize
-```{r, warning=FALSE, message=FALSE}
-library(glmnet)
-library(caret)
-#Make sure there are no NAs within the dataset
-Mothership_lasso <- Mothership_post |>
-    filter(
-    !is.na(Some_College),
-    !is.na(Female),
-    !is.na(IPT_track_1),
-    !is.na(White),
-    !is.na(RESPONDER_FIGS)
-  )
-
-# View(Mothership_lasso)
-
-Vars <- Mothership_lasso |>
+
+Vars_anx <- Mothership_post |>
   select( c(
-    RESPONDER_FIGS,
-    # Demographics
-    Age_1,Some_College:Married,White,
-    # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, 
-    # Disorders
-    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
-    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
-    Current_Dx,
-    # Pre-Post stuff
-    CUDOS_pre,CUXOS_pre, 
-  ))
-
-```
-
-```{r, warning=FALSE, message=FALSE}
-# View(Mothership_lasso)
-# head(Vars)
-# sum(is.na(Vars))
-Vars_FULL <- Mothership_lasso |>
-  select( c(
-    RESPONDER_FIGS,
+    Anxiety_Responder,
     # Demographics
@@
 
-Vars_FULL <- na.omit(Vars_FULL)
-```
-# with RDQ
+Vars_FULL <- na.omit(Vars_dep)
+
+# install.packages("ggcorrplot")
+library(ggcorrplot)
+model.matrix(~0+., data=Vars_dep) %>% 
+  cor(use="pairwise.complete.obs") %>% 
+  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
+
+model.matrix(~0+., data=Vars_anx) %>% 
+  cor(use="pairwise.complete.obs") %>% 
+  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
+
+```
+
+## Part 2: RCI ANALYSIS - Treatment Response
+Anxiety & Depression = Total response
+- Table 4: RCI Analsyis results
+  + Anxiety, Depression, Total response
+- Figure 2 / Supplimetal 2: RCI Analysis figs 
+  + Anxeity & Depression
+```{r}
+
+RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
+colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
+#anxiety 
+RCI_table[1,] = c("CUXOS", unlist(summary(Mothership_post$Anxiety_Responder)))
+# Depresssion
+RCI_table[2,] = c("CUDOS", unlist(summary(Mothership_post$Depression_Responder)))
+#Total
+RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
+
+RCI_table
+```
+
+## Part 3 Logistic lasso
+
+### Lasso Regression
+https://glmnet.stanford.edu/articles/glmnet.html
+https://www.mygreatlearning.com/blog/understanding-of-lasso-regression/
+https://bookdown.org/tpinto_home/Regularisation/lasso-regression.html
+
+https://github.com/sydeaka/Using-Elastic-net-for-model-Selection-with-missing-data/blob/master/model_selection_missing_data-example.R
+http://www.sthda.com/english/articles/36-classification-methods-essentials/149-penalized-logistic-regression-essentials-in-r-ridge-lasso-and-elastic-net/
+
+# Depression Lasso 
+Preparing data for lasso - Anxiety
+```{r}
+Mothership_lasso_dep <- Mothership_post |>
+    filter(
+    !is.na(Some_College),
+    !is.na(Female),
+    !is.na(IPT_track_1),
+    !is.na(White),
+    !is.na(Depression_Responder)
+  )
+
+Vars_dep <- Mothership_lasso_dep |>
+  select( c(
+    Depression_Responder,
+    # Demographics
+    Age_1,Some_College:Married,White, #Discharge,
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    # Disorders
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
+    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
+    Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    # RDQ
+    rdq_coping_change:rdq_wbs_change
+  ))
+
+Vars_dep <- na.omit(Vars_dep)
+
+```
+
+Create test and train data - Depression
 ```{r}
@@
 set.seed(123) 
-training.samples <- Vars_FULL$RESPONDER_FIGS %>% 
+training.samples <- Vars_dep$Depression_Responder %>% 
   createDataPartition(p = 0.8, list = FALSE)
-train.data  <- Vars_FULL[training.samples, ]
-test.data <- Vars_FULL[-training.samples, ]
+train.data  <- Vars_dep[training.samples, ]
+test.data <- Vars_dep[-training.samples, ]
 
 # Dumy code categorical predictor variables
-x <- model.matrix(RESPONDER_FIGS~., train.data)[,-1]
+x.dep <- model.matrix(Depression_Responder~., train.data)[,-1]
 # Convert the outcome (class) to a numerical variable
-y <- ifelse(train.data$RESPONDER_FIGS == "Responder", 1, 0)
+y.dep <- ifelse(train.data$Depression_Responder == "Responder", 1, 0)
 
 #Simplified lasso
-lasso1 <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)
-plot(lasso1, "lambda", label = TRUE)
-```
-
-Find coefficients using cv.lasso
+lasso1_dep <- glmnet(x.dep, y.dep,family = "binomial", alpha = 1, lambda = NULL)
+plot(lasso1_dep, "lambda", label = TRUE)
+```
+
+Find coefficients using cv.lasso- Depression
 ```{r}
@@
 set.seed(123) 
-cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
+cv.lasso.dep <- cv.glmnet(x.dep, y.dep, alpha = 1, family = "binomial")
 
 #The exact value of lambda can be viewed as follow:
-print(paste0("This is the minimum lambda value: ", round(cv.lasso$lambda.min,5)))
+print(paste0("This is the minimum lambda value: ", round(cv.lasso.dep$lambda.min,5)))
 
 #This value is called lambda.1se.
-print(paste0("This is the 1 standard error lambda value: ", round(cv.lasso$lambda.1se,5)))
+print(paste0("This is the 1 standard error lambda value: ", round(cv.lasso.dep$lambda.1se,5)))
 
 # Fit the final model on the training data
-model <- glmnet(x, y, alpha = 1, family = "binomial",
-                lambda = cv.lasso$lambda.min)
+model <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
+                lambda = cv.lasso.dep$lambda.min)
 # Display regression coefficients
@@
 # Make predictions on the test data
-x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
+x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
 probabilities <- model %>% predict(newx = x.test)
@@
 # Model accuracy
-observed.classes <- test.data$RESPONDER_FIGS
+observed.classes <- test.data$Depression_Responder
 mean(predicted.classes == observed.classes)
@@
 #Using lambda.min as the best lambda, gives the following regression coefficients:
-coef(cv.lasso, cv.lasso$lambda.min)
+coef(cv.lasso.dep, cv.lasso.dep$lambda.min)
 
 #Using lambda.1se as the best lambda, gives the following regression coefficients:
-coef(cv.lasso, cv.lasso$lambda.1se)
-```
-
-Evaluating if we should use Lasso min or 1SE
+coef(cv.lasso.dep, cv.lasso.dep$lambda.1se)
+```
+
+Evaluating if we should use Lasso min or 1SE- Depression
 ```{r}
@@
 # Final model with lambda.min
-lasso.model.min <- glmnet(x, y, alpha = 1, family = "binomial",
+lasso.model.min.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                       lambda = cv.lasso$lambda.min)
 
-coef(lasso.model.min)
+coef(lasso.model.min.dep)
 # Make prediction on test data
-x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
-probabilities <- lasso.model.min %>% predict(newx = x.test)
+x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
+probabilities <- lasso.model.min.dep %>% predict(newx = x.test)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
 # Model accuracy
-observed.classes <- test.data$RESPONDER_FIGS
-Mean.predict.min <- mean(predicted.classes == observed.classes)
+observed.classes <- test.data$Depression_Responder
+Mean.predict.min.dep <- mean(predicted.classes == observed.classes)
 
@@
 # Final model with lambda.1se
-lasso.model.1se <- glmnet(x, y, alpha = 1, family = "binomial",
+lasso.model.1se.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                       lambda = cv.lasso$lambda.1se)
-coef(lasso.model.1se)
+coef(lasso.model.1se.dep)
 # Make prediction on test data
-x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
-probabilities <- lasso.model.1se %>% predict(newx = x.test)
+x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
+probabilities <- lasso.model.1se.dep %>% predict(newx = x.test)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 # Model accuracy rate
-observed.classes <- test.data$RESPONDER_FIGS
-Mean.predict.1se <- mean(predicted.classes == observed.classes)
+observed.classes <- test.data$Depression_Responder
+Mean.predict.1se.dep <- mean(predicted.classes == observed.classes)
 
@@
 # Fit the model
-full.model <- glm(RESPONDER_FIGS ~ ., data = train.data, family = "binomial")
+full.model.dep <- glm(Depression_Responder ~ ., data = train.data, family = "binomial")
 
@@
 # Model accuracy
-observed.classes <- test.data$RESPONDER_FIGS
-Mean.predict.full.model <- mean(predicted.classes == observed.classes)
+observed.classes <- test.data$Depression_Responder
+Mean.predict.full.model.dep <- mean(predicted.classes == observed.classes)
 
@@
   model = c("Min", "1se", "Full"),
-  values = c(Mean.predict.min,Mean.predict.1se,Mean.predict.full.model)
+  values = c(Mean.predict.min.dep,Mean.predict.1se.dep,Mean.predict.full.model.dep)
 )
@@
 ```
-plot the lassos
+
+plot the lassos- Depression
 If We want to do lasso in ggplot
 https://stackoverflow.com/questions/48978179/plotting-lasso-beta-coefficients
-
 ```{r}
 ##plot the lambda
-plot(lasso1, "lambda", label = TRUE)
+plot(lasso1_dep, "lambda", label = TRUE)
 ## Fancy plot
 library(lars)
-lasso_FULL = lars(x, y, type='lasso', 
+lasso_FULL_dep = lars(x.dep, y.dep, type='lasso', 
               trace=TRUE, normalize=FALSE, intercept=TRUE)
-plot(lasso_FULL, xvar='norm', breaks = FALSE, 
+plot(lasso_FULL_dep, xvar='norm', breaks = FALSE, 
      plottype = 'coefficients', omit.zeros = TRUE)
@@
 #CV k folds cross validation
-plot(cv.lasso)
-```
-
-### Final relaxed lasso
-Minimum
+plot(cv.lasso.dep)
+```
+
+### Final relaxed lasso- Depression
+Minimum- 
 ```{r}
@@
 library(fuzzySim) ## For FDR adjusted p values
-FDR(pvalues = p_values.min)
-
-library(broom)
-# https://cran.r-project.org/web/packages/broom/vignettes/broom.html
+library(broom) # for tidy regression output
 
 ## min model
-  glm_min <-  
+  glm_min_dep <-  
       glm(
       #Outcome varaible
-        RESPONDER_FIGS ~ 
+        Depression_Responder ~ 
       # predictors
-        Days_not_attended_1 + Anxiety_D + Mood_D + Substance_C + 
-        rdq_coping_change + rdq_pmh_change + rdq_func_change + rdq_wbs_change,
+        Married + Days_not_attended_1 + Mood_D + Anxiety_C + Substance_C +
+        CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + 
+        rdq_func_change,
       #data
-      data = Vars_FULL, 
+      data = Vars_dep, 
       # type of regression : logistic = binary / binomial
@@
 # Summary of the model
-  summary.min      <- summary(glm_min)
-
-  tidy.summary.min <- tidy(glm_min)
-
+  summary.min.dep      <- summary(glm_min_dep)
+
+  tidy.summary.min.dep <- tidy(glm_min_dep)
+tidy.summary.min
 # Coefficients
-  coefs.min <- abs(coef(glm_min))
+  coefs.min.dep <- abs(coef(glm_min_dep))
 
 # Odds ratio
-  OR.min <- exp(coef(glm_min))
+  OR.min.dep <- exp(coef(glm_min_dep))
 
 # OR 95% CI
-  CI.min <- data.frame(exp(confint(glm_min)))
+  CI.min.dep <- data.frame(exp(confint(glm_min_dep)))
 
 # P values
-  p.values.min <- data.frame(cbind(tidy.summary.min$term,tidy.summary.min$p.value))
+  p.values.min.dep <- data.frame(cbind(tidy.summary.min.dep$term,tidy.summary.min.dep$p.value))
   # FDR Adjusted P Values
-    adj.p.min <- FDR(pvalues = p_values.min)
-    ADJ.p.values.min <- data.frame(rbind(adj.p.min$exclude, adj.p.min$select))
+    adj.p.min.dep <- FDR(pvalues = p.values.min.dep)
+    ADJ.p.values.min.dep <- data.frame(rbind(adj.p.min.dep$exclude, adj.p.min.dep$select))
 
 # R^2 values  
-   R2.min <- performance::r2(glm_min)
+   R2.min.dep <- performance::r2(glm_min_dep)
 
 # df for Forrest plots
-FP.min <- data.frame(cbind(
-  Variable = tidy.summary.min$term[2:length(tidy.summary.min$term)],
-  OR = OR.min[2:length(OR.min)],
-  OR_low  = CI.min[2:length(CI.min$X2.5..),1],
-  OR_high = CI.min[2:length(CI.min$X97.5..),2],
-  p.values = p.values.min$X2[2:length(p.values.min$X2)]
+FP.min.dep <- data.frame(cbind(
+  Variable = tidy.summary.min.dep$term[2:length(tidy.summary.min.dep$term)],
+  OR = OR.min.dep [2:length(OR.min.dep)],
+  OR_low  = CI.min.dep [2:length(CI.min.dep$X2.5..),1],
+  OR_high = CI.min.dep [2:length(CI.min.dep$X97.5..),2],
+  p.values = p.values.min.dep $X2[2:length(p.values.min.dep$X2)]
                     ))
@@
 # Left join the FDR adjusted p.value
-FP.min <- left_join(FP.min,ADJ.p.values.min, by = join_by(p.values == p.value))
-FP.min
-```
-
-1se
-```{r}
-glm_1se <-  
+FP.min.dep <- left_join(FP.min.dep,ADJ.p.values.min.dep, by = join_by(p.values == p.value))
+FP.min.dep
+```
+1se -
+```{r}
+
+## 1se model
+  glm_1se_dep <-  
       glm(
       #Outcome varaible
-        RESPONDER_FIGS ~ 
+        Depression_Responder ~ 
       # predictors
-        Days_not_attended_1 + rdq_coping_change + rdq_pmh_change + rdq_func_change +
-        rdq_wbs_change,
+        rdq_coping_change + rdq_pmh_change + rdq_func_change + rdq_wbs_change,
       #data
-      data = Vars_FULL, 
+      data = Vars_dep, 
       # type of regression : logistic = binary / binomial
       family = "binomial")
-
-summary(glm_1se)
-
 # Summary of the model
-  summary.1se      <- summary(glm_1se)
-
-  tidy.summary.1se <- tidy(glm_1se)
-
+  summary.1se.dep      <- summary(glm_1se_dep)
+
+  tidy.summary.1se.dep <- tidy(glm_1se_dep)
+  tidy.summary.1se.dep
 # Coefficients
-  coefs.1se <- abs(coef(glm_1se))
+  coefs.1se.dep <- abs(coef(glm_1se_dep))
 
 # Odds ratio
-  OR.1se <- exp(coef(glm_1se))
+  OR.1se.dep <- exp(coef(glm_1se_dep))
 
 # OR 95% CI
-  CI.1se <- data.frame(exp(confint(glm_1se)))
+  CI.1se.dep <- data.frame(exp(confint(glm_1se_dep)))
 
 # P values
-  p.values.1se <- data.frame(cbind(tidy.summary.1se$term,tidy.summary.1se$p.value))
-
+  p.values.1se.dep <- data.frame(cbind(tidy.summary.1se.dep$term,tidy.summary.1se.dep$p.value))
   # FDR Adjusted P Values
-    adj.p.1se <- FDR(pvalues = p.values.1se)
-    ADJ.p.values.1se <- data.frame(rbind(adj.p.1se$exclude, adj.p.1se$select))
+    adj.p.1se.dep <- FDR(pvalues = p.values.1se.dep)
+    ADJ.p.values.1se.dep <- data.frame(rbind(adj.p.1se.dep$exclude, adj.p.1se.dep$select))
 
 # R^2 values  
-   R2.1se <- performance::r2(glm_1se)
+   R2.1se.dep <- performance::r2(glm_1se_dep)
 
 # df for Forrest plots
-FP.1se <- data.frame(cbind(
-  Variable = tidy.summary.1se$term[2:length(tidy.summary.1se$term)],
-  OR = OR.1se[2:length(OR.1se)],
-  OR_low  = CI.1se[2:length(CI.1se$X2.5..),1],
-  OR_high = CI.1se[2:length(CI.1se$X97.5..),2],
-  p.values = p.values.1se$X2[2:length(p.values.1se$X2)]
+FP.1se.dep <- data.frame(cbind(
+  Variable = tidy.summary.1se.dep$term[2:length(tidy.summary.1se.dep$term)],
+  OR = OR.1se.dep [2:length(OR.1se.dep)],
+  OR_low  = CI.1se.dep [2:length(CI.1se.dep$X2.5..),1],
+  OR_high = CI.1se.dep [2:length(CI.1se.dep$X97.5..),2],
+  p.values = p.values.1se.dep$X2[2:length(p.values.1se.dep$X2)]
                     ))
@@
 # Left join the FDR adjusted p.value
-FP.1se <- left_join(FP.1se,ADJ.p.values.1se, by = join_by(p.values == p.value))
-FP.1se
-```
-
-# Without RDQ
-Evaluating Methods of Assessing “Optimism”  in Regression Models Daniel Thoya1,*, Antony Waititu1, Thomas Magheto1, Antony Ngunyi2 
-- chrome-extension://efaidnbmnnnibpcajpcglclefindmkaj/http://article.sciappliedmathematics.com/pdf/ajams-6-4-2.pdf
-
-Validation of prediction models based on lasso regression with multiply imputed data
-- https://bmcmedresmethodol.biomedcentral.com/articles/10.1186/1471-2288-14-116#Sec18
-
-Penalized Logistic Regression Essentials in R: Ridge, Lasso and Elastic Net
-http://www.sthda.com/english/articles/36-classification-methods-essentials/149-penalized-logistic-regression-essentials-in-r-ridge-lasso-and-elastic-net/
-
-### Lasso regression - set variables
+FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
+FP.1se.dep
+```
+
+# Anxiety Lasso 
+Preparing data for lasso - Anxiety
+```{r}
+Mothership_lasso_anx <- Mothership_post |>
+    filter(
+    !is.na(Some_College),
+    !is.na(Female),
+    !is.na(IPT_track_1),
+    !is.na(White),
+    !is.na(Anxiety_Responder)
+  )
+
+Vars_anx <- Mothership_lasso_anx |>
+  select( c(
+    Anxiety_Responder,
+    # Demographics
+    Age_1,Some_College:Married,White, #Discharge,
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    # Disorders
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
+    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
+    Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    # RDQ
+    rdq_coping_change:rdq_wbs_change
+  ))
+
+Vars_anx <- na.omit(Vars_anx)
+```
+
+Create test and train data - ANX
 ```{r}
@@
 set.seed(123) 
-training.samples <- Vars_full$RESPONDER_FIGS %>% 
+training.samples <- Vars_anx$Anxiety_Responder %>% 
   createDataPartition(p = 0.8, list = FALSE)
-train.data  <- Vars[training.samples, ]
-test.data <- Vars[-training.samples, ]
+train.data  <- Vars_anx[training.samples, ]
+test.data <- Vars_anx[-training.samples, ]
 
 # Dumy code categorical predictor variables
-x <- model.matrix(RESPONDER_FIGS~., train.data)[,-1]
+x <- model.matrix(Anxiety_Responder~., train.data)[,-1]
 # Convert the outcome (class) to a numerical variable
-y <- ifelse(train.data$RESPONDER_FIGS == "Responder", 1, 0)
+y <- ifelse(train.data$Anxiety_Responder == "Responder", 1, 0)
 
 #Simplified lasso
-lasso1 <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)
-
-plot(lasso1, "lambda", label = TRUE)
-```
-
-Find coefficients using cv.lasso
+lasso1_anx <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)
+plot(lasso1_anx, "lambda", label = TRUE)
+```
+
+Find coefficients using cv.lasso- ANX
 ```{r}
 # Find the best lambda using cross-validation
-cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
+set.seed(123) 
+cv.lasso.anx <- cv.glmnet(x, y, alpha = 1, family = "binomial")
+
+#The exact value of lambda can be viewed as follow:
+print(paste0("This is the minimum lambda value: ", round(cv.lasso.anx$lambda.min,5)))
+
+#This value is called lambda.1se.
+print(paste0("This is the 1 standard error lambda value: ", round(cv.lasso.anx$lambda.1se,5)))
+
 # Fit the final model on the training data
 model <- glmnet(x, y, alpha = 1, family = "binomial",
-                lambda = cv.lasso$lambda.min)
+                lambda = cv.lasso.anx$lambda.min)
 # Display regression coefficients
@@
 # Make predictions on the test data
-x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
+x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
 probabilities <- model %>% predict(newx = x.test)
@@
 # Model accuracy
-observed.classes <- test.data$RESPONDER_FIGS
+observed.classes <- test.data$Anxiety_Responder
 mean(predicted.classes == observed.classes)
 
-### Compute lasso regression
-#Find the optimal value of lambda that minimizes the cross-validation error:
-set.seed(123)
-cv.lasso <- cv.glmnet(x, y, alpha = 1, family = "binomial")
-
-#The exact value of lambda can be viewed as follow:
-cv.lasso$lambda.min
-
-#This value is called lambda.1se.
-cv.lasso$lambda.1se
-
 #Using lambda.min as the best lambda, gives the following regression coefficients:
-coef(cv.lasso, cv.lasso$lambda.min)
+coef(cv.lasso.anx, cv.lasso.anx$lambda.min)
 
 #Using lambda.1se as the best lambda, gives the following regression coefficients:
-coef(cv.lasso, cv.lasso$lambda.1se)
-```
-
-Evaluating if we should use Lasso min or SE
-```{r}
-#### Compute the final lasso model:
+coef(cv.lasso.anx, cv.lasso.anx$lambda.1se)
+```
+
+Evaluating if we should use Lasso min or 1SE- ANX
+```{r}
+####  Using Min
 # Final model with lambda.min
-lasso.model.min <- glmnet(x, y, alpha = 1, family = "binomial",
+lasso.model.min.anx <- glmnet(x, y, alpha = 1, family = "binomial",
                       lambda = cv.lasso$lambda.min)
 
-coef(lasso.model.min)
+coef(lasso.model.min.anx)
 # Make prediction on test data
-x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
-probabilities <- lasso.model.min %>% predict(newx = x.test)
+x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
+probabilities <- lasso.model.min.anx %>% predict(newx = x.test)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
 # Model accuracy
-observed.classes <- test.data$RESPONDER_FIGS
-mean(predicted.classes == observed.classes)
+observed.classes <- test.data$Anxiety_Responder
+Mean.predict.min.anx <- mean(predicted.classes == observed.classes)
 
@@
 # Final model with lambda.1se
-lasso.model.1se <- glmnet(x, y, alpha = 1, family = "binomial",
+lasso.model.1se.anx <- glmnet(x, y, alpha = 1, family = "binomial",
                       lambda = cv.lasso$lambda.1se)
-
+coef(lasso.model.1se.anx)
 # Make prediction on test data
-x.test <- model.matrix(RESPONDER_FIGS ~., test.data)[,-1]
-probabilities <- lasso.model.1se %>% predict(newx = x.test)
+x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
+probabilities <- lasso.model.1se.anx %>% predict(newx = x.test)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 # Model accuracy rate
-observed.classes <- test.data$RESPONDER_FIGS
-mean(predicted.classes == observed.classes)
+observed.classes <- test.data$Anxiety_Responder
+Mean.predict.1se.anx <- mean(predicted.classes == observed.classes)
 
@@
 # Fit the model
-full.model <- glm(RESPONDER_FIGS ~ ., data = train.data, family = "binomial")
+full.model.anx <- glm(Anxiety_Responder ~ ., data = train.data, family = "binomial")
 
@@
 # Model accuracy
-observed.classes <- test.data$RESPONDER_FIGS
-mean(predicted.classes == observed.classes)
-```
-
-Visualizing it
-```{r}
+observed.classes <- test.data$Anxiety_Responder
+Mean.predict.full.model.anx <- mean(predicted.classes == observed.classes)
+
+predict.df <- data.frame(
+  model = c("Min", "1se", "Full"),
+  values = c(Mean.predict.min.anx,Mean.predict.1se.anx,Mean.predict.full.model.anx)
+)
+predict.df
+```
+
+plot the lassos- Anx
+If We want to do lasso in ggplot
+https://stackoverflow.com/questions/48978179/plotting-lasso-beta-coefficients
+```{r}
+##plot the lambda
+plot(lasso1_anx, "lambda", label = TRUE)
+## Fancy plot
 library(lars)
-
-lasso5 = lars(x, y, type='lasso', 
+lasso_FULL_anx = lars(x, y, type='lasso', 
               trace=TRUE, normalize=FALSE, intercept=TRUE)
-
-plot(lasso5, xvar='norm', breaks = FALSE, 
+plot(lasso_FULL_anx, xvar='norm', breaks = FALSE, 
      plottype = 'coefficients', omit.zeros = TRUE)
-```
-
-### Final relaxed lasso
-```{r}
+
+#CV k folds cross validation
+plot(cv.lasso.anx)
+```
+
+### Final relaxed lasso- anx
+Minimum- 
+```{r}
+## install.packages("fuzzySim")
+library(fuzzySim) ## For FDR adjusted p values
+library(broom) # for tidy regression output
+
 ## min model
-  glm_1se <-  
-      glm(RESPONDER_FIGS ~ 
-      Days_complete_1 + Days_not_attended_1,
-      data = Vars, family = "binomial")
+  glm_min_anx <-  
+      glm(
+      #Outcome varaible
+        Anxiety_Responder ~ 
+      # predictors
+        Some_College + Married + White + Days_complete_1 + Days_not_attended_1 + 
+        Anxiety_D + Other + Mood_C + BPD_Co_C + Substance_C + Trauma_C + Current_Dx +
+        CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
+      #data
+      data = Vars_anx, 
+      # type of regression : logistic = binary / binomial
+      family = "binomial")
 # Summary of the model
-  summary.1se      <- summary(glm_1se)
-      library(broom)
-          # https://cran.r-project.org/web/packages/broom/vignettes/broom.html
-  tidy.summary.1se <- tidy(glm_1se)
-
+  summary.min.anx      <- summary(glm_min_anx)
+
+  tidy.summary.min.anx <- tidy(glm_min_anx)
+  tidy.summary.min.anx
 # Coefficients
-  coefs.1se <- abs(coef(glm_1se))
+  coefs.min.anx <- abs(coef(glm_min_anx))
 
 # Odds ratio
-  OR.1se <- exp(coef(glm_1se))
+  OR.min.anx <- exp(coef(glm_min_anx))
 
 # OR 95% CI
-  CI.1se <- data.frame(exp(confint(glm_1se)))
+  CI.min.anx <- data.frame(exp(confint(glm_min_anx)))
 
 # P values
-  p.values.1se <- tidy.summary.1se$p.value
+  p.values.min.anx <- data.frame(cbind(tidy.summary.min.anx$term,tidy.summary.min.anx$p.value))
+  # FDR Adjusted P Values
+    adj.p.min.anx <- FDR(pvalues = p.values.min.anx)
+    ADJ.p.values.min.anx <- data.frame(rbind(adj.p.min.anx$exclude, adj.p.min.anx$select))
 
 # R^2 values  
-   R2.1se <- performance::r2(glm_1se)
+   R2.min.anx <- performance::r2(glm_min_anx)
 
 # df for Forrest plots
-
-FP.1se <- data.frame(cbind(
-  Variable = tidy.summary.1se$term[2:length(tidy.summary.1se$term)],
-  OR = OR.1se[2:length(OR.1se)],
-  OR_low  = CI.1se[2:length(CI.1se$X2.5..),1],
-  OR_high = CI.1se[2:length(CI.1se$X97.5..),2],
-  p.values = p.values.1se[2:length(p.values.1se)]
+FP.min.anx <- data.frame(cbind(
+  Variable = tidy.summary.min.anx$term[2:length(tidy.summary.min.anx$term)],
+  OR = OR.min.anx [2:length(OR.min.anx)],
+  OR_low  = CI.min.anx [2:length(CI.min.anx$X2.5..),1],
+  OR_high = CI.min.anx [2:length(CI.min.anx$X97.5..),2],
+  p.values = p.values.min.anx$X2[2:length(p.values.min.anx$X2)]
                     ))
 
-FP.1se
-```
-
-```{r}
-### min model
-  glm_min <-  
-      glm(RESPONDER_FIGS ~ 
-      Age_1 + Some_College + Married + Days_complete_1 + Days_not_attended_1 + 
-      Psychotic_D + Co_Substance + Co_Trauma + CUDOS_pre,
-      data = Vars, family = "binomial")
+# Left join the FDR adjusted p.value
+FP.min.anx <- left_join(FP.min.anx,ADJ.p.values.min.anx, by = join_by(p.values == p.value))
+FP.min.anx
+```
+1se -
+```{r}
+
+## 1se model
+  glm_1se_anx <-  
+      glm(
+      #Outcome varaible
+        Anxiety_Responder ~ 
+      # predictors
+         Days_not_attended_1 + rdq_coping_change + rdq_pmh_change + rdq_func_change,
+      #data
+      data = Vars_anx, 
+      # type of regression : logistic = binary / binomial
+      family = "binomial")
 # Summary of the model
-  summary.min      <- summary(glm_min)
-      library(broom)
-          # https://cran.r-project.org/web/packages/broom/vignettes/broom.html
-  tidy.summary.min <- tidy(glm_min)
-
+  summary.1se.anx      <- summary(glm_1se_anx)
+
+  tidy.summary.1se.anx <- tidy(glm_1se_anx)
+  tidy.summary.1se.anx
 # Coefficients
-  coefs.min <- abs(coef(glm_min))
+  coefs.1se.anx <- abs(coef(glm_1se_anx))
 
 # Odds ratio
-  OR.min <- exp(coef(glm_min))
+  OR.1se.anx <- exp(coef(glm_1se_anx))
 
 # OR 95% CI
-  CI.min <- data.frame(exp(confint(glm_min)))
+  CI.1se.anx <- data.frame(exp(confint(glm_1se_anx)))
 
 # P values
-  p.values.min <- tidy.summary.min$p.value
+  p.values.1se.anx <- data.frame(cbind(tidy.summary.1se.anx$term,tidy.summary.1se.anx$p.value))
+  # FDR Adjusted P Values
+    adj.p.1se.anx <- FDR(pvalues = p.values.1se.anx)
+    ADJ.p.values.1se.anx <- data.frame(rbind(adj.p.1se.anx$exclude, adj.p.1se.anx$select))
 
 # R^2 values  
-   R2.min <- performance::r2(glm_min)
+   R2.1se.anx <- performance::r2(glm_1se_anx)
 
 # df for Forrest plots
-
-FP.min <- data.frame(cbind(
-  Variable = tidy.summary.min$term[2:length(tidy.summary.min$term)],
-  OR = OR.min[2:length(OR.min)],
-  OR_low  = CI.min[2:length(CI.min$X2.5..),1],
-  OR_high = CI.min[2:length(CI.min$X97.5..),2],
-  p.values = p.values.min[2:length(p.values.min)]
+FP.1se.anx <- data.frame(cbind(
+  Variable = tidy.summary.1se.anx$term[2:length(tidy.summary.1se.anx$term)],
+  OR = OR.1se.anx [2:length(OR.1se.anx)],
+  OR_low  = CI.1se.anx [2:length(CI.1se.anx$X2.5..),1],
+  OR_high = CI.1se.anx [2:length(CI.1se.anx$X97.5..),2],
+  p.values = p.values.1se.anx$X2[2:length(p.values.1se.anx$X2)]
                     ))
 
-FP.min
-```
+# Left join the FDR adjusted p.value
+FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
+FP.1se.anx
+```

### 2024-02-19 Paper_stuff.Rmd
Anxiety & Depression seperate LASSO

@@
 ```{r}
-Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
+Mothership1 <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
 head(df)
+mode(Mothership1$Relationship_1)
 ```
@@
 
+relationship
+```{r}
+ggplot(data = subset(Mothership_post, !is.na(Gender_1)),mapping = aes(x = Gender_1))+
+  geom_bar(color = "black",fill="darkorange")+
+  ggtitle("Frequency of Gender") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("Gender")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  coord_flip()+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+
+Mothership_post$Relationship_1
+
+ggplot(data = subset(Mothership_post, !is.na(Relationship_1)),mapping = aes(x = Relationship_1))+
+  geom_bar(color = "black",fill="darkorange")+
+  ggtitle("Frequency of Relationship") +
+  theme(axis.text.x = element_text(angle = 45,hjust = 1))+
+  xlab("relationshipr")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  coord_flip()+
+  scale_y_continuous(name = "Frequency",limits=c(0,6500))
+
+summary(Mothership_post$Relationship_1)
+
+```
+
 # Treatment Related Visualizations
@@
   theme_void()
+
+Mothership_post
 ```

### 2024-02-19 Lasso_RCI_Response.Rmd
Updated peramiters (added substance use)

@@
         Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1 |
-          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1 | 
-          Schiz_P == 1 |  Schizaff_P == 1,  
+          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1,
         1,0)),
@@
       ifelse(  Somatic_C == 1 & 
-               Eating_C == 1 &
-               Psychotic_C == 1,1,0)),
+               Eating_C == 1, 1,0)),
 
@@
                BPD_Co_C == 1 & Psychotic_D ==1 |
-               BPD_Co_C == 1 & !BPD_P == 
+               BPD_Co_C == 1 & !BPD_P == 1 |
                BPD_Co_C == 1 & Somatic_D ==1 , 1, 0)),
@@
 
-pre-post scores by treatment response
+pre-post scores by treatment response - TOGETHER
 ```{r}
@@
   select( c(
-    Depression_Responder,
     # Demographics
@@
     # Disorders
-    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
-    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
+    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
     Current_Dx,
@@
   ))
+
+str(Vars_dep)
 
@@
     # Demographics
-    Age_1,Some_College:Married,White, #Discharge,
+    Age_1,Some_College:Married,White, 
     # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    IPT_track_1, Days_complete_1, Days_not_attended_1, 
     # Disorders
-    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
-    Anxiety_C,Mood_C,BPD_Co_C,Other_C, Substance_C, Trauma_C, No_Co,
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
+    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
     Current_Dx,
     # Pre-Post stuff
-    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    CUDOS_pre,CUXOS_pre,
     # RDQ
@@
   ))
+
+old model
+# Anxiety_D, Mood_D, BPD_P,    Trauma_D,  Other,
+#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+#     Current_Dx,
 
@@
   model = c("Min", "1se", "Full"),
-  values = c(Mean.predict.min.dep,Mean.predict.1se.dep,Mean.predict.full.model.dep)
+  Mean_Predict = c(Mean.predict.min.dep,Mean.predict.1se.dep,Mean.predict.full.model.dep)
 )
@@
 library(broom) # for tidy regression output
-
+# Old model
+# ## min model
+#   glm_min_dep <-  
+#       glm(
+#       #Outcome varaible
+#         Depression_Responder ~ 
+#       # predictors
+#         Married + Days_not_attended_1 + Mood_D + Anxiety_C + Substance_C +
+#         CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + 
+#         rdq_func_change,
+#       #data
+#       data = Vars_dep, 
+#       # type of regression : logistic = binary / binomial
+#       family = "binomial")
+```
+
+```{r}
 ## min model
@@
       # predictors
-        Married + Days_not_attended_1 + Mood_D + Anxiety_C + Substance_C +
-        CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + 
-        rdq_func_change,
+        Married + Days_not_attended_1 + Mood_D + Substance_D + Anxiety_C +
+        Substance_C + CUDOS_pre + CUXOS_pre + rdq_coping_change + 
+        rdq_pmh_change + rdq_func_change,
       #data
@@
         family = "binomial")
+
 # Summary of the model
   summary.min.dep      <- summary(glm_min_dep)
+  summary.min.dep
 
   tidy.summary.min.dep <- tidy(glm_min_dep)
-tidy.summary.min
+
 # Coefficients
@@
 
+# Some_College + Married + White + Days_complete_1 + Days_not_attended_1 + 
+#         Anxiety_D + Other + Mood_C + BPD_Co_C + Substance_C + Trauma_C + Current_Dx +
+#         CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
+
 ## min model
@@
       # predictors
-        Some_College + Married + White + Days_complete_1 + Days_not_attended_1 + 
-        Anxiety_D + Other + Mood_C + BPD_Co_C + Substance_C + Trauma_C + Current_Dx +
-        CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
+        Married + White + Days_complete_1 + Days_not_attended_1 + 
+        Anxiety_D + Mood_C + Substance_C + Trauma_C +  CUDOS_pre + CUXOS_pre + 
+        rdq_coping_change + rdq_pmh_change + rdq_func_change,
       #data
@@
       # predictors
-         Days_not_attended_1 + rdq_coping_change + rdq_pmh_change + rdq_func_change,
+         CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
       #data

### 2024-02-20 Lasso_RCI_Response.Rmd
FP has identity issues

@@
 FP.min.dep <- left_join(FP.min.dep,ADJ.p.values.min.dep, by = join_by(p.values == p.value))
+FP.min.dep$type = c("Depression")
 FP.min.dep
@@
 FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
+FP.1se.dep$type = c("Depression")
 FP.1se.dep
@@
 # Coefficients
-  coefs.min.anx <- abs(coef(glm_min_anx))
+  coefs.min.anx <- round(abs(coef(glm_min_anx)),3)
 
 # Odds ratio
-  OR.min.anx <- exp(coef(glm_min_anx))
-
+  OR.min.anx <- round(exp(coef(glm_min_anx)),3)
 # OR 95% CI
   CI.min.anx <- data.frame(exp(confint(glm_min_anx)))
-
+  CI.min.anx[,1] = round(CI.min.anx[,1],3)
+  CI.min.anx[,2] = round(CI.min.anx[,2],3)
 # P values
@@
     ADJ.p.values.min.anx <- data.frame(rbind(adj.p.min.anx$exclude, adj.p.min.anx$select))
-
+    ADJ.p.values.min.anx
 # R^2 values  
@@
 FP.min.anx <- left_join(FP.min.anx,ADJ.p.values.min.anx, by = join_by(p.values == p.value))
+FP.min.anx$p.values = round(as.numeric(FP.min.anx$p.values),3)
+FP.min.anx$p.adjusted = round(as.numeric(FP.min.anx$p.adjusted),3)
+FP.min.anx$type = c("Anxiety")
 FP.min.anx
+
 ```
@@
 FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
-FP.1se.anx
-```
+FP.1se.anx$type = c("Anxiety")
+```
+
+# Forrest Plot
+
+```{r}
+#Create order varaible in dataset to keep it the same as the regression
+FP.min.anx$order = c(rev(seq(length(FP.min.anx$Variable),1)))
+FP.min.anx
+
+```
+
+```{r}
+FP.min.anx |>
+  ggplot(aes(y = reorder(Variable, -order))) +
+  #take away background
+  theme_classic() +
+  #make the forrest plot
+  geom_point(aes(x=OR), shape=10, size=2.5,show.legend = FALSE) +
+    geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
+  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
+  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.5)+
+  #change x axis name
+  labs(
+    x="Odds Ratio",
+    # title = "Odds of Reporting Medical Conditions",
+    # subtitle = "Based Upon Probable TBI/concussion") +
+       ) 
+  #adjust the dimentions. 
+  #coord_cartesian(ylim = c(1,length(FP.min.anx$Variable))) +
+  #add a line at 0 for reference
+
+  #add anotations to help suggests what each side means.
+  # annotate("text", x = .5, y = 14, label = "Less Likely", size= 3) +
+  # annotate("text", x = 1.5, y = 14, label = "More Likely",size= 3) +
+  #Git rid of the Y - Axis
+    theme(axis.line.y = element_blank(),
+        axis.ticks.y= element_blank(),
+        axis.text.y= element_blank(),
+        axis.title.y= element_blank())
+
+```

### 2024-02-21 Lasso_RCI_Response.Rmd
Created table one

@@
 library(JTRCI)
-# library(ClinicalSig)
+citation("JTRCI")
+
 # 
@@
 ```{r}
-#Demographics Table
-Demo_tab_df <- Mothership_post |>
-  #Mothership_Diag_treat |>
-  filter(!is.na(Education_1),
-         !is.na(Race_1),
-         !is.na(Gender_1),
-         !is.na(Disorder_Type),
-         !is.na(Relationship_1),
-         !is.na(RESPONDER_FIGS)
-        )
-
-#Demographic tab
-Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
-colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
-Demo_tab
-
-Simple_Demo_tab <-data.frame(table1::table1(~Age_1 + White +IPT_track_1 + Straight + Married + Female +  Some_College + Discharge | RESPONDER_FIGS, data=Demo_tab_df))
-colnames(Simple_Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
-Simple_Demo_tab
+# #Demographics Table
+# Demo_tab_df <- Mothership_post |>
+#   #Mothership_Diag_treat |>
+#   filter(!is.na(Education_1),
+#          !is.na(Race_1),
+#          !is.na(Gender_1),
+#          !is.na(Disorder_Type),
+#          !is.na(Relationship_1),
+#          !is.na(RESPONDER_FIGS)
+#         )
+
+# #Demographic tab
+# Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
+# colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
+# Demo_tab
+# 
+# Simple_Demo_tab <-data.frame(table1::table1(~Age_1 + White +IPT_track_1 + Straight + Married + Female +  Some_College + Discharge | RESPONDER_FIGS, data=Demo_tab_df))
+# colnames(Simple_Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
+# Simple_Demo_tab
+# 
+# Table
+
+library(tableone)
+
+### first gather information based upon anxiety
+
+## Vector of variables to summarize
+table1_vars_anx <- c(colnames(Vars_anx)[-1])
+
+## Vector of categorical variables that need transformation
+catVars <- c("Some_College", "Female" , "Married", "White",
+             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
+             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
+             "Substance_C", "Other_C" , "No_Co"
+             )
+## Create a TableOne object
+table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Vars_anx,strata ="Anxiety_Responder",  factorVars = catVars)
+table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
+tab1_df_anx <- data.frame(table1_tab_anx)
+
+### next gather info based upon depression
+
+## Vector of variables to summarize
+table1_vars_dep <- c(colnames(Vars_dep)[-1])
+
+## Vector of categorical variables that need transformation
+catVars <- c("Some_College", "Female" , "Married", "White",
+             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
+             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
+             "Substance_C", "Other_C" , "No_Co"
+             )
+## Create a TableOne object
+table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Vars_dep,strata ="Depression_Responder",  factorVars = catVars)
+table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
+table1_tab_dep <-data.frame(table1_tab_dep)
+table1_tab_dep
+
+## lastly get the overal treatment breakdown
+table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso_anx,  factorVars = catVars)
+table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
+table1_gen <-data.frame(table1_gen)
+table1_gen 
 ```
@@
 resp_tab <- data.frame(table1::table1(
-   ~ DC_status_1 + IPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
+   ~IPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
   data = Mothership_post))
@@
     # RDQ
-    rdq_coping_change:rdq_wbs_change
+    rdqPOST_coping:rdqPOST_wbs
   ))
 
-old model
+# old model
 # Anxiety_D, Mood_D, BPD_P,    Trauma_D,  Other,
@@
 ```{r}
+library(glmnet)
+library(caret)
 # Create Training and testing data
@@
 # Fit the final model on the training data
-model <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
+model.min <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                 lambda = cv.lasso.dep$lambda.min)
 # Display regression coefficients
-coef(model)
+coef(model.min)
+
 # Make predictions on the test data
@@
 # Make predictions
-probabilities <- full.model %>% predict(test.data, type = "response")
+probabilities <- full.model.dep %>% predict(test.data, type = "response")
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
       # predictors
-        Married + Days_not_attended_1 + Mood_D + Substance_D + Anxiety_C +
-        Substance_C + CUDOS_pre + CUXOS_pre + rdq_coping_change + 
-        rdq_pmh_change + rdq_func_change,
+        White + Days_complete_1 + Days_not_attended_1 + Mood_D + Substance_D + 
+        Other + Anxiety_C + Mood_C + Substance_C + CUDOS_pre + CUXOS_pre + 
+        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
       # predictors
-        rdq_coping_change + rdq_pmh_change + rdq_func_change + rdq_wbs_change,
+        Days_not_attended_1+ rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + 
+        rdqPOST_wbs,
       #data
@@
     # RDQ
-    rdq_coping_change:rdq_wbs_change
+    rdqPOST_coping:rdqPOST_wbs
   ))
@@
 Vars_anx <- na.omit(Vars_anx)
+
+citation("glmnet")
 ```
@@
 # Display regression coefficients
-coef(model)
+# coef(model)
 # Make predictions on the test data
@@
 # Make predictions
-probabilities <- full.model %>% predict(test.data, type = "response")
+probabilities <- full.model.anx %>% predict(test.data, type = "response")
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
       # predictors
-         CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
+        Days_not_attended_1 + CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_wbs,
       #data
@@
 FP.1se.anx$type = c("Anxiety")
+FP.1se.anx
 ```

### 2024-02-27 Lasso_RCI_Response.Rmd
Updated CUXOS / CUDOS > 20

@@
                   indextype = "RCI", 
-                  #JTcrit = "auto",
-                  plottitle = "Anxeity: JT indices by disorder")
+                  JTcrit = "auto",
+                  plottitle = "JT indices for anxiety")
 
@@
                   #JTcrit = "auto",
-                  plottitle = "Anxeity: JT indices by disorder")
+                  plottitle = "JT indices for depression")
 
@@
     Anx_Responder = as.factor(
-      ifelse(CUXOS_pre < 20 & Percent_Anx_change  <= -50, "Responder",
-      ifelse(CUXOS_pre < 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
+      ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
+      ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
       )),
     Dep_Responder = as.factor(
-      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange <= -50, "Responder",
-      ifelse(CUDOS_pre < 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
+      ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
+      ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
       )),
@@
 
+Mothership_lasso <- Mothership_post |>
+    filter(
+    !is.na(Some_College),
+    !is.na(Female),
+    !is.na(IPT_track_1),
+    !is.na(White),
+    !is.na(Anxiety_Responder),
+    !is.na(Depression_Responder),
+    CUXOS_pre >= 20,
+    CUDOS_pre >= 20
+  )
+
+Vars_anx <- Mothership_lasso |>
+  select( c(
+    Anxiety_Responder,
+    # Demographics
+    Age_1,Some_College:Married,White, #Discharge,
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    # Disorders
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
+    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+    Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    # RDQ
+    rdqPOST_coping:rdqPOST_wbs
+  ))
+
+# Mothership_lasso_dep <- Mothership_post |>
+#     filter(
+#     !is.na(Some_College),
+#     !is.na(Female),
+#     !is.na(IPT_track_1),
+#     !is.na(White),
+#     !is.na(Depression_Responder),
+#     CUXOS_pre >= 20,
+#     CUDOS_pre >= 20
+#   )
+
+Vars_dep <- Mothership_lasso |>
+  select( c(
+    Depression_Responder,
+    # Demographics
+    Age_1,Some_College:Married,White, 
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, 
+    # Disorders
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
+    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+    Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre,
+    # RDQ
+    rdqPOST_coping:rdqPOST_wbs
+  ))
+
+Vars_anx <- na.omit(Vars_anx)
+Vars_dep <- na.omit(Vars_dep)
+
 library(tableone)
@@
 tab1_df_anx <- data.frame(table1_tab_anx)
-
+tab1_df_anx
 ### next gather info based upon depression
@@
 ## lastly get the overal treatment breakdown
-table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso_anx,  factorVars = catVars)
+table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,  factorVars = catVars)
 table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
@@
 table1_gen
+
+summary(Mothership_lasso$Depression_Responder)
+
 ```
@@
 # PHP Treatment information
-resp_tab <- data.frame(table1::table1(
-   ~IPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
-  data = Mothership_post))
-colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
-resp_tab
-```
-
-pre-post scores by treatment response - TOGETHER
+# resp_tab <- data.frame(table1::table1(
+#    ~IPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
+#   data = Mothership_post))
+# colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
+# resp_tab
+```
+
+# RCI analysis Table
+pre-post scores by treatment response, cut off, and RCI threshold
 ```{r}
@@
 #1. Make DF + name columns
-Scores_tab <- data.frame(matrix(nrow = 9 ,ncol=7))
-colnames(Scores_tab) = c("Variables", "N_Pre M(SD)", "N_Post M(SD)", "N_Change M(SD)","R_Pre M(SD)", "R_Post M(SD)", "R_Change M(SD)")
+Scores_tab <- data.frame(matrix(nrow = 2 ,ncol=9))
+colnames(Scores_tab) = c("Instrument", "N_Pre M(SD)", "N_Post M(SD)", "N_Change M(SD)","R_Pre M(SD)", "R_Post M(SD)", "R_Change M(SD)", "Cut Off", "RCI")
 
 #2. Row 1 - responders
-Scores_tab[1,] = c(NA,"Non-responder","Non-responder","Non-responder","Responder","Responder","Responder")
+Scores_tab[1,] = c(NA,"M (sd)","M (sd)","M (sd)","M (sd)","M (sd)","M (sd)",NA,NA)
 
@@
       anx_rep_tab <- Mothership_post |>
-        group_by(RESPONDER_FIGS) |>
+        group_by(Anxiety_Responder) |>
         summarize(pre_anx = round(mean(CUXOS_pre, na.rm = TRUE),2),
@@
           #Non-responder scores
+          paste0(anx_rep_tab$pre_anx[[2]]," (",anx_rep_tab$pre_anx_sd[[2]],")"),
+          paste0(anx_rep_tab$post_anx[[2]]," (",anx_rep_tab$post_anx_sd[[2]],")"),
+          paste0(anx_rep_tab$delta_anx[[2]]," (",anx_rep_tab$delta_anx_sd[[2]],")"),
+          #responder scores
           paste0(anx_rep_tab$pre_anx[[1]]," (",anx_rep_tab$pre_anx_sd[[1]],")"),
@@
           paste0(anx_rep_tab$delta_anx[[1]]," (",anx_rep_tab$delta_anx_sd[[1]],")"),
-          #responder scores
-          paste0(anx_rep_tab$pre_anx[[2]]," (",anx_rep_tab$pre_anx_sd[[2]],")"),
-          paste0(anx_rep_tab$post_anx[[2]]," (",anx_rep_tab$post_anx_sd[[2]],")"),
-          paste0(anx_rep_tab$delta_anx[[2]]," (",anx_rep_tab$delta_anx_sd[[2]],")")
+          20,
+          20
         )
@@
     dep_rep_tab <- Mothership_post |>
-      group_by(RESPONDER_FIGS) |>
+      group_by(Depression_Responder) |>
       summarize(pre_dep = round( mean(CUDOS_pre, na.rm = TRUE),2),
@@
         #Non-responder scores
+        paste0(dep_rep_tab$pre_dep[[2]]," (",dep_rep_tab$pre_dep_sd[[2]],")"),
+        paste0(dep_rep_tab$post_dep[[2]]," (",dep_rep_tab$post_dep_sd[[2]],")"),
+        paste0(dep_rep_tab$delta_dep[[2]]," (",dep_rep_tab$delta_dep_sd[[2]],")"),
+        #responder scores
         paste0(dep_rep_tab$pre_dep[[1]]," (",dep_rep_tab$pre_dep_sd[[1]],")"),
@@
         paste0(dep_rep_tab$delta_dep[[1]]," (",dep_rep_tab$delta_dep_sd[[1]],")"),
-        #responder scores
-        paste0(dep_rep_tab$pre_dep[[2]]," (",dep_rep_tab$pre_dep_sd[[2]],")"),
-        paste0(dep_rep_tab$post_dep[[2]]," (",dep_rep_tab$post_dep_sd[[2]],")"),
-        paste0(dep_rep_tab$delta_dep[[2]]," (",dep_rep_tab$delta_dep_sd[[2]],")")
+        20,
+        13
       )
 
-  #RDQ subscales
-       Scores_tab[4,1] = "RDQ Subscales"
-
-  # Coping
-      cope_rep_tab <- Mothership_post |>
-        group_by(RESPONDER_FIGS) |>
-        summarize(pre_cope = round( mean(rdqPRE_coping, na.rm = TRUE),2),
-                  pre_cope_sd = round( sd(rdqPRE_coping, na.rm = TRUE),2),
-                  post_cope = round( mean(rdqPOST_coping, na.rm = TRUE),2),
-                  post_cope_sd = round( sd(rdqPOST_coping, na.rm = TRUE),2),
-                  delta_cope = round( mean(rdq_coping_change, na.rm = TRUE),2),
-                  delta_cope_sd = round( sd(rdq_coping_change, na.rm = TRUE),2)
-              )
-      Scores_tab[5,] = c(
-        "Coping",
-        #Non-responder scores
-        paste0(cope_rep_tab$pre_cope[[1]]," (",cope_rep_tab$pre_cope_sd[[1]],")"),
-        paste0(cope_rep_tab$post_cope[[1]]," (",cope_rep_tab$post_cope_sd[[1]],")"),
-        paste0(cope_rep_tab$delta_cope[[1]]," (",cope_rep_tab$delta_cope_sd[[1]],")"),
-        #responder scores
-        paste0(cope_rep_tab$pre_cope[[2]]," (",cope_rep_tab$pre_cope_sd[[2]],")"),
-        paste0(cope_rep_tab$post_cope[[2]]," (",cope_rep_tab$post_cope_sd[[2]],")"),
-        paste0(cope_rep_tab$delta_cope[[2]]," (",cope_rep_tab$delta_cope_sd[[2]],")")
-      )
-   # Positive mental health
-  pmh_rep_tab <- Mothership_post |>
-    group_by(RESPONDER_FIGS) |>
-    summarize(pre_pmh = round( mean(rdqPRE_pmh, na.rm = TRUE),2),
-              pre_pmh_sd = round( sd(rdqPRE_pmh, na.rm = TRUE),2),
-              post_pmh = round( mean(rdqPOST_pmh, na.rm = TRUE),2),
-              post_pmh_sd = round( sd(rdqPOST_pmh, na.rm = TRUE),2),
-              delta_pmh = round( mean(rdq_pmh_change, na.rm = TRUE),2),
-              delta_pmh_sd = round( sd(rdq_pmh_change, na.rm = TRUE),2)
-              )
-         Scores_tab[6,] = c(
-              "Positive Mental Health",
-              #Non-responder scores
-              paste0(pmh_rep_tab$pre_pmh[[1]]," (",pmh_rep_tab$pre_pmh_sd[[1]],")"),
-              paste0(pmh_rep_tab$post_pmh[[1]]," (",pmh_rep_tab$post_pmh_sd[[1]],")"),
-              paste0(pmh_rep_tab$delta_pmh[[1]]," (",pmh_rep_tab$delta_pmh_sd[[1]],")"),
-              #responder scores
-              paste0(pmh_rep_tab$pre_pmh[[2]]," (",pmh_rep_tab$pre_pmh_sd[[2]],")"),
-              paste0(pmh_rep_tab$post_pmh[[2]]," (",pmh_rep_tab$post_pmh_sd[[2]],")"),
-              paste0(pmh_rep_tab$delta_pmh[[2]]," (",pmh_rep_tab$delta_pmh_sd[[2]],")")
-            )
-   # Functioning
-  func_rep_tab <- Mothership_post |>
-    group_by(RESPONDER_FIGS) |>
-    summarize(pre_func = round( mean(rdqPRE_func, na.rm = TRUE),2),
-              pre_func_sd = round( sd(rdqPRE_func, na.rm = TRUE),2),
-              post_func = round( mean(rdqPOST_func, na.rm = TRUE),2),
-              post_func_sd = round( sd(rdqPOST_func, na.rm = TRUE),2),
-              delta_func = round( mean(rdq_func_change, na.rm = TRUE),2),
-              delta_func_sd = round( sd(rdq_func_change, na.rm = TRUE),2)
-              )    
-         Scores_tab[7,] = c(
-              "Functioning",
-              #Non-responder scores
-              paste0(func_rep_tab$pre_func[[1]]," (",func_rep_tab$pre_func_sd[[1]],")"),
-              paste0(func_rep_tab$post_func[[1]]," (",func_rep_tab$post_func_sd[[1]],")"),
-              paste0(func_rep_tab$delta_func[[1]]," (",func_rep_tab$delta_func_sd[[1]],")"),
-              #responder scores
-              paste0(func_rep_tab$pre_func[[2]]," (",func_rep_tab$pre_func_sd[[2]],")"),
-              paste0(func_rep_tab$post_func[[2]]," (",func_rep_tab$post_func_sd[[2]],")"),
-              paste0(func_rep_tab$delta_func[[2]]," (",func_rep_tab$delta_func_sd[[2]],")")
-            )
-
-    # General sense of wellbeing
-    wbs_rep_tab <- Mothership_post |>
-    group_by(RESPONDER_FIGS) |>
-    summarize(pre_wbs = round( mean(rdqPRE_wbs, na.rm = TRUE),2),
-              pre_wbs_sd = round( sd(rdqPRE_wbs, na.rm = TRUE),2),
-              post_wbs = round( mean(rdqPOST_wbs, na.rm = TRUE),2),
-              post_wbs_sd = round( sd(rdqPOST_wbs, na.rm = TRUE),2),
-              delta_wbs = round( mean(rdq_wbs_change, na.rm = TRUE),2),
-              delta_wbs_sd = round( sd(rdq_wbs_change, na.rm = TRUE),2)
-              )
-
-     Scores_tab[8,] = c(
-              "General sense of wellbeing",
-              #Non-responder scores
-              paste0(wbs_rep_tab$pre_wbs[[1]]," (",wbs_rep_tab$pre_wbs_sd[[1]],")"),
-              paste0(wbs_rep_tab$post_wbs[[1]]," (",wbs_rep_tab$post_wbs_sd[[1]],")"),
-              paste0(wbs_rep_tab$delta_wbs[[1]]," (",wbs_rep_tab$delta_wbs_sd[[1]],")"),
-              #responder scores
-              paste0(wbs_rep_tab$pre_wbs[[2]]," (",wbs_rep_tab$pre_wbs_sd[[2]],")"),
-              paste0(wbs_rep_tab$post_wbs[[2]]," (",wbs_rep_tab$post_wbs_sd[[2]],")"),
-              paste0(wbs_rep_tab$delta_wbs[[2]]," (",wbs_rep_tab$delta_wbs_sd[[2]],")")
-            )
-
-    #Symptoms
-    sym_rep_tab <- Mothership_post |>
-    group_by(RESPONDER_FIGS) |>
-    summarize(pre_sym = round( mean(rdqPRE_sym, na.rm = TRUE),2),
-              pre_sym_sd = round( sd(rdqPRE_sym, na.rm = TRUE),2),
-              post_sym = round( mean(rdqPOST_sym, na.rm = TRUE),2),
-              post_sym_sd = round( sd(rdqPOST_sym, na.rm = TRUE),2),
-              delta_sym = round( mean(rdq_sym_change, na.rm = TRUE),2),
-              delta_sym_sd = round( sd(rdq_sym_change, na.rm = TRUE),2)
-              )
-
-      Scores_tab[9,] = c(
-              "Symptoms",
-              #Non-responder scores
-              paste0(sym_rep_tab$pre_sym[[1]]," (",sym_rep_tab$pre_sym_sd[[1]],")"),
-              paste0(sym_rep_tab$post_sym[[1]]," (",sym_rep_tab$post_sym_sd[[1]],")"),
-              paste0(sym_rep_tab$delta_sym[[1]]," (",sym_rep_tab$delta_sym_sd[[1]],")"),
-              #responder scores
-              paste0(sym_rep_tab$pre_sym[[2]]," (",sym_rep_tab$pre_sym_sd[[2]],")"),
-              paste0(sym_rep_tab$post_sym[[2]]," (",sym_rep_tab$post_sym_sd[[2]],")"),
-              paste0(sym_rep_tab$delta_sym[[2]]," (",sym_rep_tab$delta_sym_sd[[2]],")")
-            )
 Scores_tab
+```
+
+Figure 1: Pre-post Line Plot
+```{r}
+#### Redo and recreate dataset for Anxiety or depression response.
+AnxDep_response_mean<-AnxDep_PrePost_Long %>%
+  filter(!is.na(RESPONDER_FIGS)) |>
+  group_by(Test,RESPONDER_FIGS,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
+
+ggplot(data=AnxDep_response_mean,
+       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
+           group=Test,color=fct_rev(Test)))+
+  geom_point(size=2.5) +
+  geom_line(group=AnxDep_response_mean$PrePost,size=1.5)+
+  scale_x_discrete(name="Time Point")+
+  scale_y_continuous(name="CUDOS/CUXOS Score")+
+  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
+  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+  theme(panel.background=NULL)+
+  theme(legend.title = element_blank()) +
+  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
+      c("1" = "Non-Responders", 
+        "2" = "Responders")
+      ))
 ```
@@
 #anxiety
-RCI_table[1,] = c("CUXOS", unlist(summary(Mothership_post$Anxiety_Responder)))
+
+RCI_table[,1] = c("CUXOS", unlist(summary(Mothership_post$Anxiety_Responder)))
 # Depresssion
-RCI_table[2,] = c("CUDOS", unlist(summary(Mothership_post$Depression_Responder)))
-#Total
-RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
+RCI_table[,2] = c("CUDOS", unlist(summary(Mothership_post$Depression_Responder)))
+# #Total
+# RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
 

### 2024-03-17 Lasso_RCI_Response.Rmd
Changed to JT plot/classification

@@
         Somat_P == 1 | UndiffSoma_P == 1| Hypochondriasis_P ==1 |
-          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1,
+          Anorex_P == 1 | Bulim_P == 1 | Binge_P == 1 |
+            Schiz_P == 1 | Schizaff_P == 1 |
+              Alcohol_P == 1 | Drug_P ==1,
         1,0)),
@@
 
-summary(Mothership$Co_Anx)
-table(Mothership$Anxiety_D, Mothership$Co_Anx)
 ##### df for plots
@@
 
+## Using RCI only (respond/nonrespond/deteriorated)
 DEP_RCI <- JTRCI (data = RCI_df_dep, 
@@
                   plottitle = "JT indices for depression")
-
 RCI_DF<- ANX_RCI$data
@@
 RCI_DF
+```
+
+```{r}
+#Using JT citeria (recovered/improved/nonresponse/deteriorated)
+
+#1. JT classification for depression
+JTRCI (data = RCI_df_dep, 
+                  pre = "pre", 
+                  post = "post", 
+                  ppid = "ID1", 
+                  reliability = .74, 
+                  indextype = "JT", 
+                  JTcrit = "auto",
+                  plottitle = "JT indices for anxiety")
+
+DEP_JT <- JTRCIdf
+
+#2. JT classification for anxiety
+JTRCI (data = RCI_df_anx, 
+                  pre = "pre", 
+                  post = "post", 
+                  ppid = "ID1", 
+                  reliability = .74, 
+                  indextype = "JT", 
+                  #JTcrit = "auto",
+                  plottitle = "JT indices for depression")
+
+ANX_JT<- JTRCIdf
+
+#3. Make combined JT table for anxiety and depression
+
+JT_DF<- ANX_JT
+
+colnames(JT_DF) <- paste0(colnames(JT_DF),"_anx")
+
+JT_DF2<- DEP_JT
+colnames(JT_DF2) <- paste0(colnames(JT_DF2),"_dep")
+
+JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
+colnames(JT_DF)[1] = "ID1"
+
+JT_DF
+
 ```
@@
 #2. Left join data from the RCI dataset into the Mothership_post df
-Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
+# Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
+#   mutate(
+#     Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
+#     Depression_Responder = as.factor(recode(Depression_Responder,
+#                                             "1" = "2",
+#                                             "2" = "2",
+#                                             "3" = "1"
+#     )),
+#     Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
+#     Depression_Responder = as.factor(recode(Depression_Responder,
+#                                             "2" = "Non-Responder",
+#                                             "1" = "Responder"
+#     )),
+#     Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
+#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+#                                          "1" = "2",
+#                                          "2" = "2",
+#                                          "3" = "1"
+#     )),
+#     Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
+#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+#                                          "2" = "Non-Responder",
+#                                          "1" = "Responder"
+#     )),
+#     RESPONDER_FIGS = as.factor(
+#       ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
+#              ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
+#       ))) |>
+#   filter(!is.na(RESPONDER_FIGS))
+
+Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
   mutate(
-    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
+    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
     Depression_Responder = as.factor(recode(Depression_Responder,
@@
                                             "2" = "2",
-                                            "3" = "1"
+                                            "3" = "1",
+                                            "4" = "1",
+                                            "5" = "1"
     )),
@@
     )),
-    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
+    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
@@
                                          "2" = "2",
-                                         "3" = "1"
+                                         "3" = "1",
+                                         "4" = "1",
+                                         "5" = "1"
     )),
@@
                                          "1" = "Responder"
-    )),
-    RESPONDER_FIGS = as.factor(
-      ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
-             ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
     ))) |>
-  filter(!is.na(RESPONDER_FIGS))
-
+  filter(
+    !is.na(Anxiety_Responder),
+    !is.na(Depression_Responder)
+    )
+```
+
+```{r}
 #############            AnxDep_PrePost                 ##################
@@
                                    Mothership_post$Depression_Responder,
-                                   Mothership_post$Anxiety_Responder,
-                                   Mothership_post$RESPONDER_FIGS
+                                   Mothership_post$Anxiety_Responder
+                                   #Mothership_post$RESPONDER_FIGS
 )) #%>%
@@
 colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","Depression_Responder",
-                             "Anxiety_Responder", "RESPONDER_FIGS")
+                             "Anxiety_Responder")
+#, "RESPONDER_FIGS")
 
@@
 
-summary(Mothership_lasso$Depression_Responder)
-
 ```
@@
     #make df
-      anx_rep_tab <- Mothership_post |>
+      anx_rep_tab <- Mothership_lasso |>
         group_by(Anxiety_Responder) |>
@@
   #Make df
-    dep_rep_tab <- Mothership_post |>
+    dep_rep_tab <- Mothership_lasso |>
       group_by(Depression_Responder) |>
@@
 ```{r}
-#### Redo and recreate dataset for Anxiety or depression response.
-AnxDep_response_mean<-AnxDep_PrePost_Long %>%
-  filter(!is.na(RESPONDER_FIGS)) |>
-  group_by(Test,RESPONDER_FIGS,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
-
-ggplot(data=AnxDep_response_mean,
+#1. Create long data frame for pre/post depression
+dep_prepost <- dep_rep_tab |>
+  pivot_longer(
+    cols = c("pre_dep", "post_dep"),
+    names_to = "PrePost",
+    values_to = "Score"
+  ) |>
+  select(Depression_Responder,PrePost,Score) |>
+  mutate(
+    Test = "CUDOS",
+    PrePost = ifelse(PrePost == "pre_dep", "Pre", "Post")
+  )
+colnames(dep_prepost)[1] = "Responder"
+
+#2. Create long data frame for pre/post anxiety
+anx_prepost <- anx_rep_tab |>
+  pivot_longer(
+    cols = c("pre_anx", "post_anx"),
+    names_to = "PrePost",
+    values_to = "Score"
+  ) |>
+  select(Anxiety_Responder,PrePost,Score) |>
+  mutate(
+    Test = "CUXOS",
+    PrePost = ifelse(PrePost == "pre_anx", "Pre", "Post"),
+  )
+colnames(anx_prepost)[1] = "Responder"
+
+#3. Combine dataset
+AnxDep_fig_response <- rbind(dep_prepost,anx_prepost)
+
+#4. Plot pre post scores by treatment response
+ggplot(data=AnxDep_fig_response,
        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
@@
   geom_point(size=2.5) +
-  geom_line(group=AnxDep_response_mean$PrePost,size=1.5)+
+  geom_line(group=AnxDep_fig_response$PrePost,size=1.5)+
+  ### ADD confidience intervals??
   scale_x_discrete(name="Time Point")+
   scale_y_continuous(name="CUDOS/CUXOS Score")+
-  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
+  ggtitle("Mean Pre and Post Scores of Anxiety and Depression")+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
@@
   theme(legend.title = element_blank()) +
-  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
-      c("1" = "Non-Responders", 
-        "2" = "Responders")
-      ))
+  facet_wrap(~Responder)
 ```
@@
 # Disorders by treatment response
-Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | RESPONDER_FIGS, 
-                                     data = Mothership_post))
-colnames(Dis_tab) = c("Variables","Non Responder", "Responder", "Total")
+Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | Anxiety_Responder, 
+                                     data = Mothership_lasso))
+colnames(Dis_tab) = c("Variables","Anxiety Non Responder", "Anxiety Responder", "Total")
+
+Dis_tab1 <- data.frame(table1::table1(~Disorder_Type + Current_Dx | Depression_Responder, 
+                                     data = Mothership_lasso))
+colnames(Dis_tab1) = c("Variables","Depression Non Responder", "Depression Responder", "Total")
+Dis_tab <- cbind(Dis_tab1[,1:3],Dis_tab[,2:4])
 Dis_tab
@@
 
-co_dis_tab <- Mothership_post |>
+co_dis_tab <- Mothership_lasso |>
   filter(
@@
 
-Figure 1: Pre-post Line Plot
-```{r}
-
-AnxDep_response_mean<-AnxDep_PrePost_Long %>%
-  filter(!is.na(RESPONDER_FIGS)) |>
-  group_by(Test,RESPONDER_FIGS,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
-
-ggplot(data=AnxDep_response_mean,
-       aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
-           group=Test,color=fct_rev(Test)))+
-  geom_point(size=2.5) +
-  geom_line(group=AnxDep_response_mean$PrePost,size=1.5)+
-  scale_x_discrete(name="Time Point")+
-  scale_y_continuous(name="CUDOS/CUXOS Score")+
-  ggtitle("Mean Pre and Post Scores of the Anxiety and Depression")+
-  theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-  theme(panel.background=NULL)+
-  theme(legend.title = element_blank()) +
-  facet_wrap(~RESPONDER_FIGS,labeller = labeller(RESPONDER_FIGS =
-      c("1" = "Non-Responders", 
-        "2" = "Responders")
-      ))
-```
-
-- Table 3: Correlation table?
+Table 3: Correlation table?
 - supplemental table 1: Full diagnostic breakdown of sample 
@@
 ```{r}
-Vars_dep <- Mothership_post |>
-  select( c(
-    # Demographics
-    Age_1,Some_College:Married,White, #Discharge,
-    # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
-    # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
-    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
-    Current_Dx,
-    # Pre-Post stuff
-    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
-    # RDQ
-    rdq_coping_change:rdq_wbs_change
-  ))
-
-str(Vars_dep)
-
-Vars_anx <- Mothership_post |>
-  select( c(
-    Anxiety_Responder,
-    # Demographics
-    Age_1,Some_College:Married,White, #Discharge,
-    # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
-    # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
-    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
-    Current_Dx,
-    # Pre-Post stuff
-    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
-    # RDQ
-    rdq_coping_change:rdq_wbs_change
-  ))
+# Vars_dep <- Mothership_post |>
+#   select( c(
+#     # Demographics
+#     Age_1,Some_College:Married,White, #Discharge,
+#     # Treatment info
+#     IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+#     # Disorders
+#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
+#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+#     Current_Dx,
+#     # Pre-Post stuff
+#     CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+#     # RDQ
+#     rdq_coping_change:rdq_wbs_change
+#   ))
+# 
+# str(Vars_dep)
+# 
+# Vars_anx <- Mothership_post |>
+#   select( c(
+#     Anxiety_Responder,
+#     # Demographics
+#     Age_1,Some_College:Married,White, #Discharge,
+#     # Treatment info
+#     IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+#     # Disorders
+#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
+#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+#     Current_Dx,
+#     # Pre-Post stuff
+#     CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+#     # RDQ
+#     rdq_coping_change:rdq_wbs_change
+#   ))
 
@@
 ```{r}
-
-RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
-colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
+# RCI STUFF
+# RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
+# colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
+# #anxiety 
+# 
+# RCI_table[,1] = c("CUXOS", unlist(summary(Mothership_lasso$Anxiety_Responder)))
+# # Depresssion
+# RCI_table[,2] = c("CUDOS", unlist(summary(Mothership_lasso$Depression_Responder)))
+# # #Total
+# # RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
+# 
+# RCI_table
+
+# JT Table
+JT_table <- data.frame(matrix(NA,nrow = 2,ncol = 3))
+colnames(JT_table) = c("Varaibles","Responder","Non-Responder")
 #anxiety
 
-RCI_table[,1] = c("CUXOS", unlist(summary(Mothership_post$Anxiety_Responder)))
+JT_table[1,] = c("CUXOS", unlist(summary(Mothership_lasso$Anxiety_Responder)))
 # Depresssion
-RCI_table[,2] = c("CUDOS", unlist(summary(Mothership_post$Depression_Responder)))
-# #Total
-# RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
-
-RCI_table
+JT_table[2,] = c("CUDOS", unlist(summary(Mothership_lasso$Depression_Responder)))
+
+JT_table
 ```
@@
 ```{r}
-Mothership_lasso_dep <- Mothership_post |>
+Mothership_lasso_dep <- Mothership_lasso |>
     filter(
@@
     # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, Psychotic_D,  
+    Other,
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
 #The exact value of lambda can be viewed as follow:
-print(paste0("This is the minimum lambda value: ", round(cv.lasso.dep$lambda.min,5)))
+print(paste0("The minimum lambda value is: ", round(cv.lasso.dep$lambda.min,5)))
 
 #This value is called lambda.1se.
-print(paste0("This is the 1 standard error lambda value: ", round(cv.lasso.dep$lambda.1se,5)))
+print(paste0("The 1 standard error lambda value is: ", round(cv.lasso.dep$lambda.1se,5)))
 
@@
 x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
-probabilities <- model %>% predict(newx = x.test)
+probabilities <- model.min %>% predict(newx = x.test)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 lasso.model.min.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
-                      lambda = cv.lasso$lambda.min)
+                      lambda = cv.lasso.dep$lambda.min)
 
@@
 lasso.model.1se.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
-                      lambda = cv.lasso$lambda.1se)
+                      lambda = cv.lasso.dep$lambda.1se)
 coef(lasso.model.1se.dep)
@@
       # predictors
-        White + Days_complete_1 + Days_not_attended_1 + Mood_D + Substance_D + 
-        Other + Anxiety_C + Mood_C + Substance_C + CUDOS_pre + CUXOS_pre + 
-        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+        Days_complete_1 + Days_not_attended_1 + Other + Mood_C + CUDOS_pre +  
+        CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
 ```{r}
-Mothership_lasso_anx <- Mothership_post |>
+Mothership_lasso_anx <- Mothership_lasso |>
     filter(
@@
 
-citation("glmnet")
 ```
@@
 lasso.model.min.anx <- glmnet(x, y, alpha = 1, family = "binomial",
-                      lambda = cv.lasso$lambda.min)
+                      lambda = cv.lasso.anx$lambda.min)
 
@@
 lasso.model.1se.anx <- glmnet(x, y, alpha = 1, family = "binomial",
-                      lambda = cv.lasso$lambda.1se)
+                      lambda = cv.lasso.anx$lambda.1se)
 coef(lasso.model.1se.anx)
@@
       # predictors
-        Married + White + Days_complete_1 + Days_not_attended_1 + 
-        Anxiety_D + Mood_C + Substance_C + Trauma_C +  CUDOS_pre + CUXOS_pre + 
-        rdq_coping_change + rdq_pmh_change + rdq_func_change,
+        Age_1 + Married + Days_complete_1 + Days_not_attended_1 + 
+        Anxiety_D + Trauma_D + Substance_C + BPD_Co_C +
+        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
       family = "binomial")
+
 # Summary of the model
@@
 
+write_csv(FP.min.anx, "~/Downloads/FP.min.anx")
+
 ```
@@
 # Summary of the model
+
   summary.1se.anx      <- summary(glm_1se_anx)
@@
 #Create order varaible in dataset to keep it the same as the regression
-FP.min.anx$order = c(rev(seq(length(FP.min.anx$Variable),1)))
-FP.min.anx
-
-```
-
-```{r}
-FP.min.anx |>
-  ggplot(aes(y = reorder(Variable, -order))) +
+
+FP_test <- read_csv("~/Downloads/FP.min.anx")
+
+FP_test$order = c(seq(from=2, to=length(FP.min.anx$Variable) + 1,1))
+
+FP_test <- FP_test |>
+  mutate(
+    sig = ifelse(p.adjusted <= 0.05, 16,1)
+  )
+FP_test
+```
+
+```{r}
+FP_test_m <- FP_test |>
+  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
   #take away background
@@
   #make the forrest plot
-  geom_point(aes(x=OR), shape=10, size=2.5,show.legend = FALSE) +
-    geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
+  geom_point(aes(x=OR), shape= FP_test$sig,
+               # ifelse(FP_test$p.adjusted <= 0.05, 
+               #                        16, # colored ones for significant varaibles
+               #                        1), # uncolored ones for insignificant varaibles
+             size=4,show.legend = FALSE) +
   geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
-  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.5)+
+  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
+  scale_color_manual(values = c("darkgrey","red"))+
   #change x axis name
@@
     x="Odds Ratio",
-    # title = "Odds of Reporting Medical Conditions",
-    # subtitle = "Based Upon Probable TBI/concussion") +
-       ) 
+    title = "Odds of Anxiety Treatment Non-Response",
+    subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
   #adjust the dimentions. 
-  #coord_cartesian(ylim = c(1,length(FP.min.anx$Variable))) +
-  #add a line at 0 for reference
-
+  coord_cartesian(ylim = c(1,length(FP_test$Variable) + 1)) +
+  #add a line at 1 for reference 
+   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
   #add anotations to help suggests what each side means.
-  # annotate("text", x = .5, y = 14, label = "Less Likely", size= 3) +
-  # annotate("text", x = 1.5, y = 14, label = "More Likely",size= 3) +
+  annotate("text", x = .8, y = length(FP_test$Variable) + 1, label = "Less Likely", size= 3) +
+  annotate("text", x = 1.2, y = length(FP_test$Variable) + 1, label = "More Likely",size= 3) +
   #Git rid of the Y - Axis
@@
 
-```
+FP_test_m
+```
+
+```{r}
+FP_test <- FP_test |>
+  # round estimates and 95% CIs to 2 decimal places for journal specifications
+  mutate(across(
+    c(OR, OR_low, OR_high),
+    ~ str_pad(
+      round(.x, 2),
+      width = 4,
+      pad = "0",
+      side = "right"
+    )
+  ),
+  # add an "-" between HR estimate confidence intervals
+  estimate_lab = paste0(OR, " (", OR_low, "-", OR_high, ")")) |>
+  # round p-values to two decimal places, except in cases where p < .001
+  mutate(p.adjusted_fig = case_when(
+    p.adjusted < .001 ~ "<0.001",
+    round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
+    p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
+      as.character(round(p.adjusted, 3)),
+      width = 4,
+      pad = "0",
+      side = "right"
+    ),
+    TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
+      as.character(round(p.adjusted, 2)),
+      width = 4,
+      pad = "0",
+      side = "right"
+    )
+  )) |>
+  # add a row of data that are actually column names which will be shown on the plot in the next step
+  bind_rows(
+    data.frame(
+      Variable = "Variable",
+      estimate_lab = "Odd Ratio (95% CI)",
+      OR_low = "",
+      OR_high = "",
+      p.adjusted_fig = "p value"
+    )
+  )
+
+FP_test[14,8] = 1
+FP_test
+```
+
+```{r}
+#arange the labels on top
+      FP_test<-mutate(FP_test, top_row = 0)
+      FP_test[14,12] = 1
+      FP_test <- arrange(FP_test,order)
+FP_test
+    # plot the left side of the plot 
+      FP_test_L <- FP_test %>% 
+        ggplot(aes(y = reorder(Variable, -order))) +
+        geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
+        geom_text(aes(x = 1, label = estimate_lab),
+        hjust = 0,
+        fontface = ifelse(FP_test$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
+        theme_void() +
+        coord_cartesian(ylim = c(1,length(FP_test$Variable) + 1), xlim = c(0, 4))
+
+FP_test_L
+
+FP_test_R <-  
+      FP_test |>
+      ggplot() +
+        geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
+        fontface = ifelse(FP_test$p.adjusted_fig == "p value", "bold", "plain")) +
+        theme_void() +
+        coord_cartesian(ylim = c(1,length(FP_test$Variable) + 1))
+
+FP_test
+```
+
+```{r}
+library("patchwork")
+
+layout <- c(
+  patchwork::area(t = 0, l = 0, b = 30, r = 25),
+  patchwork::area(t = 0, l = 14, b = 30, r = 25),
+  patchwork::area(t = 0, l = 23, b = 30, r = 30) 
+  )
+
+FP_test_L + FP_test_m + FP_test_R + plot_layout(design = layout)
+
+```

### 2024-03-25 Lasso_RCI_Response.Rmd
MADE FP AND FINALIZED MODELS!!!!!

@@
                            ifelse(Mood_D == 1, "Mood",
-                                  #ifelse(OCD_P == 1, "Anxiety",
-                                     #felse(OCD_P == 1, "Other",
                                          ifelse(Substance_D == 1, "Other",
@@
 catVars <- c("Some_College", "Female" , "Married", "White",
-             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
+             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D", "Substance_D" ,        
              "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
@@
 # Depression Lasso 
-Preparing data for lasso - Anxiety
+Preparing data for lasso - depression
 ```{r}
@@
     # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, Psychotic_D,  
-    Other,
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, #Psychotic_D,  
+    #Other,
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
                 lambda = cv.lasso.dep$lambda.min)
-# Display regression coefficients
-coef(model.min)
 
@@
 library(broom) # for tidy regression output
-# Old model
-# ## min model
-#   glm_min_dep <-  
-#       glm(
-#       #Outcome varaible
-#         Depression_Responder ~ 
-#       # predictors
-#         Married + Days_not_attended_1 + Mood_D + Anxiety_C + Substance_C +
-#         CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + 
-#         rdq_func_change,
-#       #data
-#       data = Vars_dep, 
-#       # type of regression : logistic = binary / binomial
-#       family = "binomial")
 ```
@@
       # predictors
-        Days_complete_1 + Days_not_attended_1 + Other + Mood_C + CUDOS_pre +  
+        Days_complete_1 + Days_not_attended_1 + Mood_C + CUDOS_pre +
         CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
@@
         family = "binomial")
+
+####### JT - substance disorder seperate    
+  # glm(
+  #     #Outcome varaible
+  #       Depression_Responder ~
+  #     # predictors
+  #       Age_1 + Some_College + Married + White + Days_complete_1 +  
+  #       Mood_D + Substance_D + Mood_C + Substance_C + CUDOS_pre + 
+  #       CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+  #     #data
+  #       data = Vars_dep,
+  #     # type of regression : logistic = binary / binomial
+  #       family = "binomial")
+
+###### JT + substance in other
+      # glm(
+      # #Outcome varaible
+      #   Depression_Responder ~
+      # # predictors
+      #   Days_complete_1 + Days_not_attended_1 + Other + Mood_C + CUDOS_pre +
+      #   CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+      # #data
+      #   data = Vars_dep,
+      # # type of regression : logistic = binary / binomial
+      #   family = "binomial")
+##############
 
@@
 FP.min.dep <- left_join(FP.min.dep,ADJ.p.values.min.dep, by = join_by(p.values == p.value))
+FP.min.dep$OR = round(as.numeric(FP.min.dep$OR),3)
+FP.min.dep$OR_low = round(as.numeric(FP.min.dep$OR_low),3)
+FP.min.dep$OR_high = round(as.numeric(FP.min.dep$OR_high),3)
+FP.min.dep$p.values = round(as.numeric(FP.min.dep$p.values),3)
+FP.min.dep$p.adjusted = round(as.numeric(FP.min.dep$p.adjusted),3)
 FP.min.dep$type = c("Depression")
 FP.min.dep
+
+write_csv(FP.min.dep, "~/Downloads/FP.min.dep")
 ```
@@
     # Demographics
-    Age_1,Some_College:Married,White, #Discharge,
+    Age_1,Some_College:Married,White, 
     # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    IPT_track_1, Days_complete_1, Days_not_attended_1, 
     # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, Psychotic_D,  
-    Other,
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, 
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
         Age_1 + Married + Days_complete_1 + Days_not_attended_1 +
-        Anxiety_D + Trauma_D + Substance_C + BPD_Co_C +
+        Anxiety_D + Trauma_D +  BPD_Co_C + 
         rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
@@
 
+####### JT - wo/Substance_D
+  # glm_min_anx <-  
+  #     glm(
+  #     #Outcome varaible
+  #       Anxiety_Responder ~ 
+  #     # predictors
+  #       Age_1 + Married + Days_complete_1 + Days_not_attended_1 + 
+  #       Anxiety_D + Trauma_D + BPD_Co_C +
+  #       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+  #     #data
+  #     data = Vars_anx, 
+  #     # type of regression : logistic = binary / binomial
+  #     family = "binomial")
 # Summary of the model
@@
 
-# Left join the FDR adjusted p.value
+# Left join the FDR adjusted p.value and round
 FP.min.anx <- left_join(FP.min.anx,ADJ.p.values.min.anx, by = join_by(p.values == p.value))
@@
 
+Anxiety Plot
 ```{r}
@@
 
-FP_test <- read_csv("~/Downloads/FP.min.anx")
-
-FP_test$order = c(seq(from=2, to=length(FP.min.anx$Variable) + 1,1))
-
-FP_test <- FP_test |>
+FP_anx <- read_csv("~/Downloads/FP.min.anx")
+
+#Change the names of variables
+FP_anx$Variable
+
+FP_anx$order = c(seq(from=2, to=length(FP_anx$Variable) + 1,1))
+
+FP_anx <- FP_anx |>
   mutate(
@@
   )
-FP_test
-```
-
-```{r}
-FP_test_m <- FP_test |>
+FP_anx
+
+FP_anx$Variable = c(
+                    "Age", "Married", "Days Completed", "Days Not Attended", 
+                    "Anxiety Disorder", "Trauma Disorder", "Co-Occuring BPD",
+                    "Coping Ability", "Positive Mental Health", "Functioning", 
+                    "Sense of Well Being"
+                    )
+
+FP_anx_m <- FP_anx |>
   ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
@@
   #make the forrest plot
-  geom_point(aes(x=OR), shape= FP_test$sig,
-               # ifelse(FP_test$p.adjusted <= 0.05, 
+  geom_point(aes(x=OR), shape= FP_anx$sig,
+               # ifelse(FP_anx$p.adjusted <= 0.05, 
                #                        16, # colored ones for significant varaibles
@@
   labs(
-    x="Odds Ratio",
-    title = "Odds of Anxiety Treatment Non-Response",
-    subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
+    x="Odds Ratio") +
+    # title = "Odds of Anxiety Treatment Non-Response",
+    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
   #adjust the dimentions. 
-  coord_cartesian(ylim = c(1,length(FP_test$Variable) + 1)) +
+  coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1)) +
   #add a line at 1 for reference 
@@
   #add anotations to help suggests what each side means.
-  annotate("text", x = .8, y = length(FP_test$Variable) + 1, label = "Less Likely", size= 3) +
-  annotate("text", x = 1.2, y = length(FP_test$Variable) + 1, label = "More Likely",size= 3) +
+  annotate("text", x = .75, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
+  annotate("text", x = 1.25, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
   #Git rid of the Y - Axis
@@
 
-FP_test_m
-```
-
-```{r}
-FP_test <- FP_test |>
+FP_anx_m
+
+FP_anx <- FP_anx |>
   # round estimates and 95% CIs to 2 decimal places for journal specifications
@@
       Variable = "Variable",
-      estimate_lab = "Odd Ratio (95% CI)",
+      estimate_lab = "Odds Ratio (95% CI)",
       OR_low = "",
@@
 
-FP_test[14,8] = 1
-FP_test
-```
-
-```{r}
+FP_anx[length(FP_anx$Variable),8] = 1
+FP_anx
+
 #arange the labels on top
-      FP_test<-mutate(FP_test, top_row = 0)
-      FP_test[14,12] = 1
-      FP_test <- arrange(FP_test,order)
-FP_test
+      FP_anx<-mutate(FP_anx, top_row = 0)
+      FP_anx[length(FP_anx$Variable),12] = 1
+      FP_anx <- arrange(FP_anx,order)
+FP_anx
     # plot the left side of the plot 
-      FP_test_L <- FP_test %>% 
+      FP_anx_L <- FP_anx %>% 
         ggplot(aes(y = reorder(Variable, -order))) +
@@
         hjust = 0,
-        fontface = ifelse(FP_test$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
+        fontface = ifelse(FP_anx$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
         theme_void() +
-        coord_cartesian(ylim = c(1,length(FP_test$Variable) + 1), xlim = c(0, 4))
-
-FP_test_L
-
-FP_test_R <-  
-      FP_test |>
+        coord_cartesian(ylim = c(1,length(FP_anx$Variable)), xlim = c(0, 4))
+
+FP_anx_L
+
+FP_anx_R <-  
+      FP_anx |>
       ggplot() +
         geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
-        fontface = ifelse(FP_test$p.adjusted_fig == "p value", "bold", "plain")) +
+        fontface = ifelse(FP_anx$p.adjusted_fig == "p value", "bold", "plain")) +
         theme_void() +
-        coord_cartesian(ylim = c(1,length(FP_test$Variable) + 1))
-
-FP_test
-```
-
-```{r}
+        coord_cartesian(ylim = c(1,length(FP_anx$Variable)))
+
+FP_anx
+
 library("patchwork")
@@
 layout <- c(
-  patchwork::area(t = 0, l = 0, b = 30, r = 25),
-  patchwork::area(t = 0, l = 14, b = 30, r = 25),
-  patchwork::area(t = 0, l = 23, b = 30, r = 30) 
-  )
-
-FP_test_L + FP_test_m + FP_test_R + plot_layout(design = layout)
-
-```
+  patchwork::area(t = 0, l = 0, b = 30, r = 30),
+  patchwork::area(t = 0, l = 15, b = 30, r = 25),
+  patchwork::area(t = 0, l = 22, b = 30, r = 30) 
+  )
+
+FP_anx_L + FP_anx_m + FP_anx_R + plot_layout(design = layout)
+
+```
+## Depression Plot
+```{r}
+#Create order varaible in dataset to keep it the same as the regression
+
+FP_dep <- read_csv("~/Downloads/FP.min.dep")
+
+#rename the variables for the figure
+FP_dep$Variable = c(
+                    "Days Completed", "Days Not Attended", 
+                    "Co-Ocurring Mood Disorder", "CUXOS Pre-Score", "CUDOS Pre-Score",
+                    "Coping Ability", "Positive Mental Health", "Functioning", 
+                    "Sense of Well Being"
+                    )
+
+FP_dep$order = c(seq(from=2, to=length(FP_dep$Variable) + 1,1))
+
+FP_dep <- FP_dep |>
+  mutate(
+    sig = ifelse(p.adjusted <= 0.05, 16,1)
+  )
+FP_dep
+
+FP_dep_m <- FP_dep |>
+  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
+  #take away background
+  theme_classic() +
+  #make the forrest plot
+  geom_point(aes(x=OR), shape= FP_dep$sig,
+               # ifelse(FP_dep$p.adjusted <= 0.05, 
+               #                        16, # colored ones for significant varaibles
+               #                        1), # uncolored ones for insignificant varaibles
+             size=4,show.legend = FALSE) +
+  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
+  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
+  scale_color_manual(values = c("darkgrey","blue"))+
+  #change x axis name
+  labs(
+    x="Odds Ratio") +
+    # title = "Odds of Anxiety Treatment Non-Response",
+    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
+  #adjust the dimentions. 
+  coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1)) +
+  #add a line at 1 for reference 
+   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
+  #add anotations to help suggests what each side means.
+  annotate("text", x = .8, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
+  annotate("text", x = 1.2, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
+  #Git rid of the Y - Axis
+    theme(axis.line.y = element_blank(),
+        axis.ticks.y= element_blank(),
+        axis.text.y= element_blank(),
+        axis.title.y= element_blank())
+
+FP_dep_m
+
+FP_dep <- FP_dep |>
+  # round estimates and 95% CIs to 2 decimal places for journal specifications
+  mutate(across(
+    c(OR, OR_low, OR_high),
+    ~ str_pad(
+      round(.x, 2),
+      width = 4,
+      pad = "0",
+      side = "right"
+    )
+  ),
+  # add an "-" between HR estimate confidence intervals
+  estimate_lab = paste0(OR, " (", OR_low, "-", OR_high, ")")) |>
+  # round p-values to two decimal places, except in cases where p < .001
+  mutate(p.adjusted_fig = case_when(
+    p.adjusted < .001 ~ "<0.001",
+    round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
+    p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
+      as.character(round(p.adjusted, 3)),
+      width = 4,
+      pad = "0",
+      side = "right"
+    ),
+    TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
+      as.character(round(p.adjusted, 2)),
+      width = 4,
+      pad = "0",
+      side = "right"
+    )
+  )) |>
+  # add a row of data that are actually column names which will be shown on the plot in the next step
+  bind_rows(
+    data.frame(
+      Variable = "Variable",
+      estimate_lab = "Odds Ratio (95% CI)",
+      OR_low = "",
+      OR_high = "",
+      p.adjusted_fig = "p value"
+    )
+  )
+
+FP_dep[length(FP_dep$Variable),8] = 1
+FP_dep
+
+#arange the labels on top
+      FP_dep<-mutate(FP_dep, top_row = 0)
+      FP_dep[length(FP_dep$Variable),12] = 1
+      FP_dep <- arrange(FP_dep,order)
+FP_dep
+    # plot the left side of the plot 
+      FP_dep_L <- FP_dep %>% 
+        ggplot(aes(y = reorder(Variable, -order))) +
+        geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
+        geom_text(aes(x = 1, label = estimate_lab),
+        hjust = 0,
+        fontface = ifelse(FP_dep$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
+        theme_void() +
+        coord_cartesian(ylim = c(1,length(FP_dep$Variable)), xlim = c(0, 4))
+
+FP_dep_L
+
+FP_dep_R <-  
+      FP_dep |>
+      ggplot() +
+        geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
+        fontface = ifelse(FP_dep$p.adjusted_fig == "p value", "bold", "plain")) +
+        theme_void() +
+        coord_cartesian(ylim = c(1,length(FP_dep$Variable)))
+
+FP_dep
+
+library("patchwork")
+
+layout <- c(
+  patchwork::area(t = 0, l = 0, b = 30, r = 30),
+  patchwork::area(t = 0, l = 15, b = 30, r = 25),
+  patchwork::area(t = 0, l = 22, b = 30, r = 30) 
+  )
+
+FP_dep_L + FP_dep_m + FP_dep_R + plot_layout(design = layout)
+```

### 2024-03-25 Lasso_RCI_Response.Rmd
Updated RCI table

@@
 ```{r}
-# #Demographics Table
-# Demo_tab_df <- Mothership_post |>
-#   #Mothership_Diag_treat |>
-#   filter(!is.na(Education_1),
-#          !is.na(Race_1),
-#          !is.na(Gender_1),
-#          !is.na(Disorder_Type),
-#          !is.na(Relationship_1),
-#          !is.na(RESPONDER_FIGS)
-#         )
-
-# #Demographic tab
-# Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
-# colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
-# Demo_tab
-# 
-# Simple_Demo_tab <-data.frame(table1::table1(~Age_1 + White +IPT_track_1 + Straight + Married + Female +  Some_College + Discharge | RESPONDER_FIGS, data=Demo_tab_df))
-# colnames(Simple_Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
-# Simple_Demo_tab
-# 
-# Table
-
 Mothership_lasso <- Mothership_post |>
@@
     CUDOS_pre >= 20
-  )
-
-Vars_anx <- Mothership_lasso |>
+  ) |>
   select( c(
-    Anxiety_Responder,
+    Anxiety_Responder, Depression_Responder,
     # Demographics
@@
     # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, 
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
     # RDQ
-    rdqPOST_coping:rdqPOST_wbs
+    rdqPOST_coping:rdqPOST_wbs,
+    #For table 3 - RCI info
+    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
   ))
 
-# Mothership_lasso_dep <- Mothership_post |>
-#     filter(
-#     !is.na(Some_College),
-#     !is.na(Female),
-#     !is.na(IPT_track_1),
-#     !is.na(White),
-#     !is.na(Depression_Responder),
-#     CUXOS_pre >= 20,
-#     CUDOS_pre >= 20
-#   )
-
-Vars_dep <- Mothership_lasso |>
-  select( c(
-    Depression_Responder,
-    # Demographics
-    Age_1,Some_College:Married,White, 
-    # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, 
-    # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
-    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
-    Current_Dx,
-    # Pre-Post stuff
-    CUDOS_pre,CUXOS_pre,
-    # RDQ
-    rdqPOST_coping:rdqPOST_wbs
-  ))
-
-Vars_anx <- na.omit(Vars_anx)
-Vars_dep <- na.omit(Vars_dep)
+Mothership_lasso <- na.omit(Mothership_lasso)
+
+summary(Mothership_lasso$Anxiety_Responder)
+
+# Vars_dep <- Mothership_lasso |>
+#   select( c(
+#     Depression_Responder,
+#     # Demographics
+#     Age_1,Some_College:Married,White, 
+#     # Treatment info
+#     IPT_track_1, Days_complete_1, Days_not_attended_1, 
+#     # Disorders
+#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
+#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+#     Current_Dx,
+#     # Pre-Post stuff
+#     CUDOS_pre,CUXOS_pre,
+#     # RDQ
+#     rdqPOST_coping:rdqPOST_wbs
+#   ))
 
@@
 ## Vector of variables to summarize
-table1_vars_anx <- c(colnames(Vars_anx)[-1])
+table1_vars_anx <- c(colnames(Mothership_lasso)[-1])
 
@@
 table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
-tab1_df_anx <- data.frame(table1_tab_anx)
-tab1_df_anx
+table1_tab_anx <- data.frame(table1_tab_anx)
+write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
+table1_tab_anx
 ### next gather info based upon depression
@@
 catVars <- c("Some_College", "Female" , "Married", "White",
-             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D", "Substance_D" ,        
+             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D",        
              "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
@@
 table1_tab_dep <-data.frame(table1_tab_dep)
+write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")
 table1_tab_dep
@@
 table1_gen <-data.frame(table1_gen)
+write_csv(table1_gen,"~/Downloads/table1_gen.csv")
 table1_gen
@@
 
-JT_table[1,] = c("CUXOS", unlist(summary(Mothership_lasso$Anxiety_Responder)))
+JT_table[1,] = c("CUXOS", unlist(summary(Vars_anx$Anxiety_Responder)))
 # Depresssion
-JT_table[2,] = c("CUDOS", unlist(summary(Mothership_lasso$Depression_Responder)))
+JT_table[2,] = c("CUDOS", unlist(summary(Vars_dep$Depression_Responder)))
 
@@
 
+summary(Vars_dep$Depression_Responder)
+
 # old model
@@
 Vars_dep <- na.omit(Vars_dep)
-
 ```

### 2024-04-02 Lasso_RCI_Response.Rmd
Results + tables and fig draft 1!

@@
 
-JT_DF
+View(JT_DF)
 
@@
 #   filter(!is.na(RESPONDER_FIGS))
-
-Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
+```
+
+JT Numbers
+```{r}
+# Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
+#   mutate(
+#     Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
+#     Depression_Responder = as.factor(recode(Depression_Responder,
+#                                             "1" = "2",
+#                                             "2" = "2",
+#                                             "3" = "1",
+#                                             "4" = "1",
+#                                             "5" = "1"
+#     )),
+#     Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
+#     Depression_Responder = as.factor(recode(Depression_Responder,
+#                                             "2" = "Non-Responder",
+#                                             "1" = "Responder"
+#     )),
+#     Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
+#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+#                                          "1" = "2",
+#                                          "2" = "2",
+#                                          "3" = "1",
+#                                          "4" = "1",
+#                                          "5" = "1"
+#     )),
+#     Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
+#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+#                                          "2" = "Non-Responder",
+#                                          "1" = "Responder"
+#     ))) |>
+#   filter(
+#     !is.na(Anxiety_Responder),
+#     !is.na(Depression_Responder)
+#     )
+```
+
+RCI numbers
+```{r}
+Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
   mutate(
-    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
+    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
     Depression_Responder = as.factor(recode(Depression_Responder,
@@
     )),
-    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
+    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
@@
   select( c(
-    Anxiety_Responder, Depression_Responder,
+    Anxiety_Responder, Depression_Responder,Disorder_treat,
     # Demographics
@@
     # Disorders
-    Anxiety_D, Mood_D, BPD_P, Trauma_D, 
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
 
-summary(Mothership_lasso$Anxiety_Responder)
-
-# Vars_dep <- Mothership_lasso |>
-#   select( c(
-#     Depression_Responder,
-#     # Demographics
-#     Age_1,Some_College:Married,White, 
-#     # Treatment info
-#     IPT_track_1, Days_complete_1, Days_not_attended_1, 
-#     # Disorders
-#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
-#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
-#     Current_Dx,
-#     # Pre-Post stuff
-#     CUDOS_pre,CUXOS_pre,
-#     # RDQ
-#     rdqPOST_coping:rdqPOST_wbs
-#   ))
-
 library(tableone)
@@
 ## Vector of variables to summarize
-table1_vars_anx <- c(colnames(Mothership_lasso)[-1])
-
+table1_vars_anx <- c("Anxiety_Responder",colnames(Mothership_lasso)[-1:-3])
+table1_vars_anx <- table1_vars_anx[1:28]
+
+colnames(Mothership_lasso)[-1]
 ## Vector of categorical variables that need transformation
@@
              )
+
 ## Create a TableOne object
-table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Vars_anx,strata ="Anxiety_Responder",  factorVars = catVars)
+table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Mothership_lasso,strata ="Anxiety_Responder",  factorVars = catVars)
 table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
@@
 ## Vector of variables to summarize
-table1_vars_dep <- c(colnames(Vars_dep)[-1])
-
-## Vector of categorical variables that need transformation
-catVars <- c("Some_College", "Female" , "Married", "White",
-             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D",        
-             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
-             "Substance_C", "Other_C" , "No_Co"
-             )
+table1_vars_dep <- c("Depression_Responder",colnames(Mothership_lasso)[-1:-3])
+table1_vars_dep <- table1_vars_dep[1:28]
+
 ## Create a TableOne object
-table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Vars_dep,strata ="Depression_Responder",  factorVars = catVars)
+table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,strata ="Depression_Responder",  factorVars = catVars)
 table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
@@
 
+## Vector of variables to summarize
+table1_vars_gen <- c(colnames(Mothership_lasso)[-1:-3])
+table1_vars_gen<- table1_vars_gen[1:27]
+
 ## lastly get the overal treatment breakdown
-table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,  factorVars = catVars)
+table1_gen <- CreateTableOne(vars = table1_vars_gen, data = Mothership_lasso,  factorVars = catVars)
 table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
@@
 table1_gen
+
+mean(Mothership_lasso$CUDOS_pre)
+sd(Mothership_lasso$CUDOS_pre)
+mean(Mothership_lasso$CUDOS_post)
+sd(Mothership_lasso$CUDOS_post)
 
@@
 # Disorders by treatment response
-Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | Anxiety_Responder, 
+Dis_tab <- data.frame(table1::table1(~Disorder_treat + Current_Dx | Anxiety_Responder, 
                                      data = Mothership_lasso))
@@
 
-Dis_tab1 <- data.frame(table1::table1(~Disorder_Type + Current_Dx | Depression_Responder, 
+Dis_tab1 <- data.frame(table1::table1(~Disorder_treat + Current_Dx | Depression_Responder, 
                                      data = Mothership_lasso))
@@
 #Full demographic break down
+dim(Mothership_lasso)
 
 co_dis_tab <- Mothership_lasso |>
-  filter(
-      !is.na(rdq_func_change),
-      !is.na(rdq_pmh_change),
-      !is.na(rdq_coping_change),
-      !is.na(rdq_wbs_change)
-  ) |>
   pivot_longer(
@@
 ```{r}
-# Vars_dep <- Mothership_post |>
-#   select( c(
-#     # Demographics
-#     Age_1,Some_College:Married,White, #Discharge,
-#     # Treatment info
-#     IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
-#     # Disorders
-#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
-#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
-#     Current_Dx,
-#     # Pre-Post stuff
-#     CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
-#     # RDQ
-#     rdq_coping_change:rdq_wbs_change
-#   ))
+
+Vars_dep <- Mothership_lasso |>
+  select( c(
+    Depression_Responder,
+    # Demographics
+    Age_1,Some_College:Married,White, #Discharge,
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    # Disorders
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
+    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+    Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    # RDQ
+    rdqPOST_coping:rdqPOST_wbs  
+    ))
+
+Vars_anx <- Mothership_lasso |>
+  select( c(
+    Anxiety_Responder,
+    # Demographics
+    Age_1,Some_College:Married,White, #Discharge,
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    # Disorders
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
+    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+    Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    # RDQ
+    rdqPOST_coping:rdqPOST_wbs  
+  ))
+
+#Make a correlation table???
+
+# install.packages("ggcorrplot")
+# library(ggcorrplot)
+# model.matrix(~0+., data=Mothership_lasso) %>% 
+#   cor(use="pairwise.complete.obs") %>% 
+#   ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
 # 
-# str(Vars_dep)
-# 
-# Vars_anx <- Mothership_post |>
-#   select( c(
-#     Anxiety_Responder,
-#     # Demographics
-#     Age_1,Some_College:Married,White, #Discharge,
-#     # Treatment info
-#     IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
-#     # Disorders
-#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
-#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
-#     Current_Dx,
-#     # Pre-Post stuff
-#     CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
-#     # RDQ
-#     rdq_coping_change:rdq_wbs_change
-#   ))
-
-Vars_FULL <- na.omit(Vars_dep)
-
-# install.packages("ggcorrplot")
-library(ggcorrplot)
-model.matrix(~0+., data=Vars_dep) %>% 
-  cor(use="pairwise.complete.obs") %>% 
-  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
-
-model.matrix(~0+., data=Vars_anx) %>% 
-  cor(use="pairwise.complete.obs") %>% 
-  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
+# model.matrix(~0+., data=Vars_anx) %>% 
+#   cor(use="pairwise.complete.obs") %>% 
+#   ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
 
@@
 library(broom) # for tidy regression output
-```
-
-```{r}
+
 ## min model
@@
     # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, 
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
         Age_1 + Married + Days_complete_1 + Days_not_attended_1 +
-        Anxiety_D + Trauma_D +  BPD_Co_C + 
-        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+        Anxiety_D + Trauma_D +  BPD_Co_C + CUXOS_pre +
+        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func,
       #data
@@
       # predictors
-        Days_not_attended_1 + CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_wbs,
+        Days_complete_1 + Days_not_attended_1 + Anxiety_D +CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func,
       #data
@@
 FP.1se.anx
+
+write_csv(FP.1se.anx, "~/Downloads/FP.1se.anx")
 ```
@@
 FP_anx <- read_csv("~/Downloads/FP.min.anx")
+# FP_anx <- read_csv("~/Downloads/FP.1se.anx")
 
@@
 FP_anx$Variable = c(
-                    "Age", "Married", "Days Completed", "Days Not Attended", 
+                    "Age", "Unmarried", "Days Completed", "Days Not Attended",
                     "Anxiety Disorder", "Trauma Disorder", "Co-Occuring BPD",
-                    "Coping Ability", "Positive Mental Health", "Functioning", 
-                    "Sense of Well Being"
-                    )
+                    "CUXOS Pre-Score",
+                    "Coping Ability", "Positive Mental Health", "Functioning"
+                    )
+# FP_anx$Variable = c(                      
+#                     "Days Completed","Days Not Attended","Anxiety Disroder","CUXOS Pre-score",
+#                     "Coping Ability","Positive Mental Health", "Functioning"   
+#                     )
 

### 2024-04-08 Lasso_RCI_Response.Rmd
Discriptive Satistics

@@
 table1_tab_anx <- data.frame(table1_tab_anx)
+table1_tab_anx<- table1_tab_anx[-2,]
 write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
 table1_tab_anx
+```
+
+```{r}
 ### next gather info based upon depression
@@
 table1_tab_dep <-data.frame(table1_tab_dep)
+table1_tab_dep <- table1_tab_dep[-2,]
+
+# add discriptive statistics 
+table1_tab_dep$ef_size = c("")
+
+# age
+table1_tab_dep[2,4] <- round(t_test(Age_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_dep[2,5] <- round(cohens_d(Age_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+# Some College 
+table1_tab_dep[3,4] <- round(chisq.test(Mothership_lasso$Some_College, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[3,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Some_College))$estimate,2)
+# Female
+table1_tab_dep[4,4] <- round(chisq.test(Mothership_lasso$Female, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[4,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Female))$estimate,2)
+# Married
+table1_tab_dep[5,4] <- round(chisq.test(Mothership_lasso$Married, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[5,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Married))$estimate,2)
+# White
+table1_tab_dep[6,4] <- round(chisq.test(Mothership_lasso$White, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[6,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$White))$estimate,2)
+# Treatment track
+table1_tab_dep[7,4] <- round(chisq.test(Mothership_lasso$IPT_track_1, Mothership_lasso$Depression_Responder)$statistic,2)
+# OR general vs Trauma track
+table1_tab_dep[9,5] <- round(fisher.test(cbind(OR_IPT_Tab[,"General"],OR_IPT_Tab[,"Trauma"]))$estimate,2)
+# OR General vs Young adult track 
+table1_tab_dep[10,5] <- 
+  round(fisher.test(cbind(OR_IPT_Tab[,"General"],OR_IPT_Tab[,"Young Adult"]))$estimate,2)
+# Days Completed in program
+table1_tab_dep[11,4] <- round(t_test(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
+round(table1_tab_dep[11,5] <- cohens_d(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+# Days not attending treatment
+table1_tab_dep[12,4] <- round(t_test(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
+round(table1_tab_dep[12,5] <- cohens_d(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+# Anxiety disorder
+table1_tab_dep[13,4] <- round(chisq.test(Mothership_lasso$Anxiety_D, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[13,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Anxiety_D))$estimate,2)
+# Mood Disorders
+table1_tab_dep[14,4] <- round(chisq.test(Mothership_lasso$Mood_D, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[14,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Mood_D))$estimate,2)
+# BPD 
+table1_tab_dep[15,4] <- round(chisq.test(Mothership_lasso$BPD_P, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[15,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$BPD_P))$estimate,2)
+# Truama Related Disorders
+table1_tab_dep[16,4] <- round(chisq.test(Mothership_lasso$Trauma_D, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[16,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Trauma_D))$estimate,2)
+# Other Disorders
+table1_tab_dep[17,4] <- round(chisq.test(Mothership_lasso$Other, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[17,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Other))$estimate,2)
+# Co-occurring anxiety disorder 
+table1_tab_dep[18,4] <- round(chisq.test(Mothership_lasso$Anxiety_C, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[18,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Anxiety_C))$estimate,2)
+# Co-occurring mood disorder
+table1_tab_dep[19,4] <- round(chisq.test(Mothership_lasso$Mood_C, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[19,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Mood_C))$estimate,2)
+# Co-occurring BPD
+table1_tab_dep[20,4] <- round(chisq.test(Mothership_lasso$BPD_Co_C, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[20,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$BPD_Co_C))$estimate,2)
+# Co-occurring Trauma Related Disorder
+table1_tab_dep[21,4] <- round(chisq.test(Mothership_lasso$Trauma_C, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[21,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Trauma_C))$estimate,2)
+# Co-occurring Substance Use Disorders
+table1_tab_dep[22,4] <- round(chisq.test(Mothership_lasso$Substance_C, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[22,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Substance_C))$estimate,2)
+# Co-occurring Other Disroders
+table1_tab_dep[23,4] <- round(chisq.test(Mothership_lasso$Other_C, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[23,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Other_C))$estimate,2)
+# No Co-occurring Disorders
+table1_tab_dep[24,4] <- round(chisq.test(Mothership_lasso$No_Co, Mothership_lasso$Depression_Responder)$statistic,2)
+table1_tab_dep[24,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$No_Co))$estimate,2)
+# Number of Current diagnoses 
+table1_tab_dep[25,4] <- round(t_test(Current_Dx ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_dep[25,5] <- round(cohens_d(Current_Dx ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+# CUDOS Pre scores
+table1_tab_dep[26,4] <- round(t_test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_dep[26,5] <- round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+# CUXOS Pre scores
+table1_tab_dep[27,4] <- round(t_test(CUXOS_pre ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_dep[27,5] <- round(cohens_d(CUXOS_pre ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+# RDQ Coping post scores
+table1_tab_dep[28,4] <- round(t_test(rdqPOST_coping ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_dep[28,5] <- round(cohens_d(rdqPOST_coping ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+# RDQ Positive Mental Health post scores
+table1_tab_dep[29,4] <- round(t_test(rdqPOST_pmh ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_dep[29,5] <- round(cohens_d(rdqPOST_pmh ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+# RDQ Functioning post scores
+table1_tab_dep[30,4] <- round(t_test(rdqPOST_func ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_dep[30,5] <- round(cohens_d(rdqPOST_func ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+# RDQ Sense of Wellbeing post scores
+table1_tab_dep[31,4] <- round(t_test(rdqPOST_wbs ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_dep[31,5] <- round(cohens_d(rdqPOST_wbs ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+
+table1_tab_dep
 write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")
-table1_tab_dep
+
+```
+
+```{r}
 
@@
 table1_gen
-
-mean(Mothership_lasso$CUDOS_pre)
-sd(Mothership_lasso$CUDOS_pre)
-mean(Mothership_lasso$CUDOS_post)
-sd(Mothership_lasso$CUDOS_post)
 

### 2024-04-08 Lasso_RCI_Response.Rmd
Discriptives pt. 2

@@
              )
-
+```
+
+```{r}
 ## Create a TableOne object
@@
 table1_tab_anx<- table1_tab_anx[-2,]
+
+# add discriptive statistics 
+table1_tab_anx$ef_size = c("")
+
+# age
+table1_tab_anx[2,4] <- round(t_test(Age_1 ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_anx[2,5] <- round(cohens_d(Age_1 ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+# Some College 
+table1_tab_anx[3,4] <- round(chisq.test(Mothership_lasso$Some_College, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[3,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Some_College))$estimate,2)
+# Female
+table1_tab_anx[4,4] <- round(chisq.test(Mothership_lasso$Female, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[4,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Female))$estimate,2)
+# Married
+table1_tab_anx[5,4] <- round(chisq.test(Mothership_lasso$Married, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[5,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Married))$estimate,2)
+# White
+table1_tab_anx[6,4] <- round(chisq.test(Mothership_lasso$White, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[6,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$White))$estimate,2)
+# Treatment track
+table1_tab_anx[7,4] <- round(chisq.test(Mothership_lasso$IPT_track_1, Mothership_lasso$Anxiety_Responder)$statistic,2)
+OR_IPT_anx <- table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$IPT_track_1)
+# OR general vs Trauma track
+table1_tab_anx[9,5] <- round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Trauma"]))$estimate,2)
+table1_tab_anx[9,3] <-
+round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Trauma"]))$p,2)
+# OR General vs Young adult track 
+table1_tab_anx[10,5] <- 
+  round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Young Adult"]))$estimate,2)
+table1_tab_anx[10,3] <-
+round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Young Adult"]))$p,2)
+# Days Completed in program
+table1_tab_anx[11,4] <- round(t_test(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_anx[11,5] <- round(cohens_d(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+# Days not attending treatment
+table1_tab_anx[12,4] <- round(t_test(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_anx[12,5] <- round(cohens_d(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+# Anxiety disorder
+table1_tab_anx[13,4] <- round(chisq.test(Mothership_lasso$Anxiety_D, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[13,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Anxiety_D))$estimate,2)
+# Mood Disorders
+table1_tab_anx[14,4] <- round(chisq.test(Mothership_lasso$Mood_D, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[14,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Mood_D))$estimate,2)
+# BPD 
+table1_tab_anx[15,4] <- round(chisq.test(Mothership_lasso$BPD_P, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[15,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$BPD_P))$estimate,2)
+# Truama Related Disorders
+table1_tab_anx[16,4] <- round(chisq.test(Mothership_lasso$Trauma_D, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[16,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Trauma_D))$estimate,2)
+# Other Disorders
+table1_tab_anx[17,4] <- round(chisq.test(Mothership_lasso$Other, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[17,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Other))$estimate,2)
+# Co-occurring anxiety disorder 
+table1_tab_anx[18,4] <- round(chisq.test(Mothership_lasso$Anxiety_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[18,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Anxiety_C))$estimate,2)
+# Co-occurring mood disorder
+table1_tab_anx[19,4] <- round(chisq.test(Mothership_lasso$Mood_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[19,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Mood_C))$estimate,2)
+# Co-occurring BPD
+table1_tab_anx[20,4] <- round(chisq.test(Mothership_lasso$BPD_Co_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[20,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$BPD_Co_C))$estimate,2)
+# Co-occurring Trauma Related Disorder
+table1_tab_anx[21,4] <- round(chisq.test(Mothership_lasso$Trauma_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[21,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Trauma_C))$estimate,2)
+# Co-occurring Substance Use Disorders
+table1_tab_anx[22,4] <- round(chisq.test(Mothership_lasso$Substance_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[22,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Substance_C))$estimate,2)
+# Co-occurring Other Disroders
+table1_tab_anx[23,4] <- round(chisq.test(Mothership_lasso$Other_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[23,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Other_C))$estimate,2)
+# No Co-occurring Disorders
+table1_tab_anx[24,4] <- round(chisq.test(Mothership_lasso$No_Co, Mothership_lasso$Anxiety_Responder)$statistic,2)
+table1_tab_anx[24,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$No_Co))$estimate,2)
+# Number of Current diagnoses 
+table1_tab_anx[25,4] <- round(t_test(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_anx[25,5] <- round(cohens_d(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+# CUDOS Pre scores
+table1_tab_anx[26,4] <- round(t_test(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_anx[26,5] <- round(cohens_d(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+# CUXOS Pre scores
+table1_tab_anx[27,4] <- round(t_test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_anx[27,5] <- round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+# RDQ Coping post scores
+table1_tab_anx[28,4] <- round(t_test(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_anx[28,5] <- round(cohens_d(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+# RDQ Positive Mental Health post scores
+table1_tab_anx[29,4] <- round(t_test(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_anx[29,5] <- round(cohens_d(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+# RDQ Functioning post scores
+table1_tab_anx[30,4] <- round(t_test(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_anx[30,5] <- round(cohens_d(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+# RDQ Sense of Wellbeing post scores
+table1_tab_anx[31,4] <- round(t_test(rdqPOST_wbs ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
+table1_tab_anx[31,5] <- round(cohens_d(rdqPOST_wbs ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+
 write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
@@
 table1_tab_dep[7,4] <- round(chisq.test(Mothership_lasso$IPT_track_1, Mothership_lasso$Depression_Responder)$statistic,2)
+OR_IPT_dep <- table(Mothership_lasso$Depression_Responder,Mothership_lasso$IPT_track_1)
 # OR general vs Trauma track
-table1_tab_dep[9,5] <- round(fisher.test(cbind(OR_IPT_Tab[,"General"],OR_IPT_Tab[,"Trauma"]))$estimate,2)
+table1_tab_dep[9,5] <- round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Trauma"]))$estimate,2)
+table1_tab_dep[9,3] <-
+round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Trauma"]))$p,2)
 # OR General vs Young adult track 
 table1_tab_dep[10,5] <- 
-  round(fisher.test(cbind(OR_IPT_Tab[,"General"],OR_IPT_Tab[,"Young Adult"]))$estimate,2)
+  round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Young Adult"]))$estimate,2)
+table1_tab_dep[10,3] <-
+round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Young Adult"]))$p,2)
 # Days Completed in program
 table1_tab_dep[11,4] <- round(t_test(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-round(table1_tab_dep[11,5] <- cohens_d(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[11,5] <- round(cohens_d(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
 # Days not attending treatment
 table1_tab_dep[12,4] <- round(t_test(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-round(table1_tab_dep[12,5] <- cohens_d(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[12,5] <- round(cohens_d(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
 # Anxiety disorder
@@
 ```{r}
-
 ## Vector of variables to summarize

### 2024-04-09 Lasso_RCI_Response.Rmd
Pre-post score stats

@@
 
-RCI_DF
+head(RCI_DF)
 ```
@@
 
-View(JT_DF)
-
+head(JT_DF)
 ```
@@
 ```{r}
-# Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
+Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
+  mutate(
+    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
+    Depression_Responder = as.factor(recode(Depression_Responder,
+                                            "1" = "2",
+                                            "2" = "2",
+                                            "3" = "1",
+                                            "4" = "1",
+                                            "5" = "1"
+    )),
+    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
+    Depression_Responder = as.factor(recode(Depression_Responder,
+                                            "2" = "Non-Responder",
+                                            "1" = "Responder"
+    )),
+    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
+    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+                                         "1" = "2",
+                                         "2" = "2",
+                                         "3" = "1",
+                                         "4" = "1",
+                                         "5" = "1"
+    )),
+    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
+    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+                                         "2" = "Non-Responder",
+                                         "1" = "Responder"
+    ))) |>
+  filter(
+    !is.na(Anxiety_Responder),
+    !is.na(Depression_Responder)
+    )
+```
+
+RCI numbers
+```{r}
+# Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
 #   mutate(
-#     Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
+#     Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
 #     Depression_Responder = as.factor(recode(Depression_Responder,
@@
 #     )),
-#     Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
+#     Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
 #     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
@@
 #     )
-```
-
-RCI numbers
-```{r}
-Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
-  mutate(
-    Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
-    Depression_Responder = as.factor(recode(Depression_Responder,
-                                            "1" = "2",
-                                            "2" = "2",
-                                            "3" = "1",
-                                            "4" = "1",
-                                            "5" = "1"
-    )),
-    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
-    Depression_Responder = as.factor(recode(Depression_Responder,
-                                            "2" = "Non-Responder",
-                                            "1" = "Responder"
-    )),
-    Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
-    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
-                                         "1" = "2",
-                                         "2" = "2",
-                                         "3" = "1",
-                                         "4" = "1",
-                                         "5" = "1"
-    )),
-    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
-    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
-                                         "2" = "Non-Responder",
-                                         "1" = "Responder"
-    ))) |>
-  filter(
-    !is.na(Anxiety_Responder),
-    !is.na(Depression_Responder)
-    )
 ```
@@
 table1_tab_anx$ef_size = c("")
+
+library(rstatix)
 
@@
 ```
+Figure 1: 
+```{r}
+# t test scores for differences pre post, between and within groups. 
+Pre_Post_t_Scores <- c("")
+
+#1. Pre post score differences of anxeity and depression by treatment response:
+  #1.1 depression responders   
+    t.test(subset(Mothership_lasso,Depression_Responder == "Responder")$CUDOS_pre,
+       subset(Mothership_lasso,Depression_Responder == "Responder")$CUDOS_post,
+       paired = TRUE, alternative = "two.sided"
+       )
+  #1.2 depression non-responders   
+     t.test(subset(Mothership_lasso,Depression_Responder == "Non-Responder")$CUDOS_pre,
+       subset(Mothership_lasso,Depression_Responder == "Non-Responder")$CUDOS_post,
+       paired = TRUE, alternative = "two.sided"
+       )
+  #1.3 anxiety responders   
+    t.test(subset(Mothership_lasso,Anxiety_Responder == "Responder")$CUXOS_pre,
+       subset(Mothership_lasso,Anxiety_Responder == "Responder")$CUXOS_post,
+       paired = TRUE, alternative = "two.sided"
+       )
+  #1.2 anxiety non-responders   
+     t.test(subset(Mothership_lasso,Anxiety_Responder == "Non-Responder")$CUXOS_pre,
+       subset(Mothership_lasso,Anxiety_Responder == "Non-Responder")$CUXOS_post,
+       paired = TRUE, alternative = "two.sided"
+       )
+#So, Non-responders and responders have lower post scores than pre scores for anxiety and depression.
+
+#2. Differences between group differences for pre and post scores of anxiety and depression.
+  #2.1 Pre scores of anxiety
+     t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso)
+  #2.2 Post scores of anxiety
+     t.test(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso)
+     sd(subset(Mothership_lasso,Anxiety_Responder == "Responder")$CUXOS_post)
+     sd(subset(Mothership_lasso,Anxiety_Responder == "Non-Responder")$CUXOS_post)
+     round(cohens_d(CUXOS_post ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+  #2.3 Pre scores of depression
+     t.test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso)
+  #2.4 Post scores of depression
+     t.test(CUDOS_post ~ Depression_Responder, data = Mothership_lasso)
+     sd(subset(Mothership_lasso,Depression_Responder == "Responder")$CUDOS_post)
+     sd(subset(Mothership_lasso,Depression_Responder == "Non-Responder")$CUDOS_post)
+     round(cohens_d(CUDOS_post ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+```
+
+Take away form this is:
+1. Non-responders and responders have lower post scores than pre scores for anxiety and depression.
+2. There are no statistically significant differences in pre scores of anxiety or depression between responders and non-responders
+3. There are significantly lower scores of anxiety and depression between responders and non-responder.
 
@@
 #Simplified lasso
-lasso1_dep <- glmnet(x.dep, y.dep,family = "binomial", alpha = 1, lambda = NULL)
+lasso1_dep <- glmnet(x.dep, y.dep,family = "binomial", alpha = 1, lambda = NULL,standardize =  TRUE)
 plot(lasso1_dep, "lambda", label = TRUE)
@@
 set.seed(123) 
-cv.lasso.dep <- cv.glmnet(x.dep, y.dep, alpha = 1, family = "binomial")
+cv.lasso.dep <- cv.glmnet(x.dep, y.dep, alpha = 1, family = "binomial",standardize = TRUE)
 
@@
 model.min <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
-                lambda = cv.lasso.dep$lambda.min)
+                lambda = cv.lasso.dep$lambda.min,standardize = TRUE)
 
@@
 lasso.model.min.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
-                      lambda = cv.lasso.dep$lambda.min)
+                      lambda = cv.lasso.dep$lambda.min, standardized = TRUE)
 
@@
 lasso.model.1se.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
-                      lambda = cv.lasso.dep$lambda.1se)
+                      lambda = cv.lasso.dep$lambda.1se,standardized = TRUE)
 coef(lasso.model.1se.dep)
@@
         Days_complete_1 + Days_not_attended_1 + Mood_C + CUDOS_pre +
-        CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+        CUXOS_pre + 
+        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
       # type of regression : logistic = binary / binomial
-        family = "binomial")
-
-####### JT - substance disorder seperate    
-  # glm(
-  #     #Outcome varaible
-  #       Depression_Responder ~
-  #     # predictors
-  #       Age_1 + Some_College + Married + White + Days_complete_1 +  
-  #       Mood_D + Substance_D + Mood_C + Substance_C + CUDOS_pre + 
-  #       CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
-  #     #data
-  #       data = Vars_dep,
-  #     # type of regression : logistic = binary / binomial
-  #       family = "binomial")
-
-###### JT + substance in other
-      # glm(
-      # #Outcome varaible
-      #   Depression_Responder ~
-      # # predictors
-      #   Days_complete_1 + Days_not_attended_1 + Other + Mood_C + CUDOS_pre +
-      #   CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
-      # #data
-      #   data = Vars_dep,
-      # # type of regression : logistic = binary / binomial
-      #   family = "binomial")
-##############
+        family = "binomial",
+      )
 
@@
 #Simplified lasso
-lasso1_anx <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)
+lasso1_anx <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL, standardize = TRUE)
 plot(lasso1_anx, "lambda", label = TRUE)
@@
 set.seed(123) 
-cv.lasso.anx <- cv.glmnet(x, y, alpha = 1, family = "binomial")
+cv.lasso.anx <- cv.glmnet(x, y, alpha = 1, family = "binomial",standardize = TRUE)
 
@@
 model <- glmnet(x, y, alpha = 1, family = "binomial",
-                lambda = cv.lasso.anx$lambda.min)
+                lambda = cv.lasso.anx$lambda.min, standardized = TRUE)
 # Display regression coefficients
@@
 lasso.model.min.anx <- glmnet(x, y, alpha = 1, family = "binomial",
-                      lambda = cv.lasso.anx$lambda.min)
+                      lambda = cv.lasso.anx$lambda.min, standardized = TRUE)
 
@@
 lasso.model.1se.anx <- glmnet(x, y, alpha = 1, family = "binomial",
-                      lambda = cv.lasso.anx$lambda.1se)
+                      lambda = cv.lasso.anx$lambda.1se,
+                      standardized = TRUE)
 coef(lasso.model.1se.anx)
@@
 
-# Some_College + Married + White + Days_complete_1 + Days_not_attended_1 + 
-#         Anxiety_D + Other + Mood_C + BPD_Co_C + Substance_C + Trauma_C + Current_Dx +
-#         CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
-
 ## min model
@@
         Age_1 + Married + Days_complete_1 + Days_not_attended_1 +
-        Anxiety_D + Trauma_D +  BPD_Co_C + CUXOS_pre +
+        Anxiety_D + BPD_Co_C + 
         rdqPOST_coping + rdqPOST_pmh + rdqPOST_func,
@@
   #     family = "binomial")
+
 # Summary of the model
@@
       # predictors
-        Days_complete_1 + Days_not_attended_1 + Anxiety_D +CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func,
+         Days_not_attended_1 + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
 # Coefficients
-  coefs.1se.anx <- abs(coef(glm_1se_anx))
+  coefs.1se.anx <- round(abs(coef(glm_1se_anx)),3)
 
 # Odds ratio
-  OR.1se.anx <- exp(coef(glm_1se_anx))
+  OR.1se.anx <- round(exp(coef(glm_1se_anx)),3)
 
@@
   CI.1se.anx <- data.frame(exp(confint(glm_1se_anx)))
+  CI.1se.anx[,1] = round(CI.1se.anx[,1],3)
+  CI.1se.anx[,2] = round(CI.1se.anx[,2],3)
 
@@
 FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
+FP.1se.anx$p.values = round(as.numeric(FP.1se.anx$p.values),3)
+FP.1se.anx$p.adjusted = round(as.numeric(FP.1se.anx$p.adjusted),3)
 FP.1se.anx$type = c("Anxiety")
@@
                     "Age", "Unmarried", "Days Completed", "Days Not Attended",
-                    "Anxiety Disorder", "Trauma Disorder", "Co-Occuring BPD",
-                    "CUXOS Pre-Score",
+                    "Anxiety Disorder", "Co-Occuring BPD",
                     "Coping Ability", "Positive Mental Health", "Functioning"
@@
 #rename the variables for the figure
+# FP_dep$Variable = c(
+#                     "Days Completed", "Days Not Attended", 
+#                     "Co-Ocurring Mood Disorder", "CUXOS Pre-Score", "CUDOS Pre-Score",
+#                     "Coping Ability", "Positive Mental Health", "Functioning", 
+#                     "Sense of Well Being"
+#                     )
 FP_dep$Variable = c(
-                    "Days Completed", "Days Not Attended", 
-                    "Co-Ocurring Mood Disorder", "CUXOS Pre-Score", "CUDOS Pre-Score",
+                     "Days Not Attended",
+                    "CUDOS Pre-Score",
                     "Coping Ability", "Positive Mental Health", "Functioning",

### 2024-04-24 Lasso_RCI_Response.Rmd
seperate dfs and RCI with final analysis.

@@
 #DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
-
+dim(Mothership)
 ```
@@
     post = as.numeric(CUDOS_post),
-    Disorder = Disorder_treat
   ) |>
   select(
-    ID1,pre,post,Disorder
+    ID1,pre,post
   ) |>
@@
     post = as.numeric(CUXOS_post),
-    Disorder = Disorder_treat
   ) |>
   select(
-    ID1,pre,post,Disorder
+    ID1,pre,post
   ) |>
@@
 DEP_JT <- JTRCIdf
+colnames(DEP_JT) <- paste0(colnames(DEP_JT),"_dep")
+head(DEP_JT)
 
@@
 
-JT_DF<- ANX_JT
-
-colnames(JT_DF) <- paste0(colnames(JT_DF),"_anx")
-
-JT_DF2<- DEP_JT
-colnames(JT_DF2) <- paste0(colnames(JT_DF2),"_dep")
-
-JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
-colnames(JT_DF)[1] = "ID1"
-
-head(JT_DF)
+# JT_DF<- ANX_JT
+
+colnames(ANX_JT) <- paste0(colnames(ANX_JT),"_anx")
+
+# 
+# JT_DF2<- DEP_JT
+
+# 
+# JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
+# colnames(JT_DF)[1] = "ID1"
+
+head(ANX_JT)
+```
+
+JTRCI with less people
+```{r}
+
+RCI_df_anx2 <- Mothership_post |>
+  filter(
+    !is.na(Some_College),
+    !is.na(Female),
+    !is.na(IPT_track_1),
+    !is.na(White),
+    !is.na(CUXOS_pre),
+    !is.na(CUXOS_post),
+    CUXOS_pre > 20,
+  )|>
+  mutate(
+    ID1  = as.integer(ID1),
+    pre  = as.numeric(CUDOS_pre),
+    post = as.numeric(CUDOS_post),
+  ) |>
+  select(
+    ID1,pre,post
+  ) |>
+  filter(!is.na(pre),
+         !is.na(post),
+         pre > 20)
+
+RCI_df_dep2 <- Mothership_post |>
+  filter(
+    !is.na(Some_College),
+    !is.na(Female),
+    !is.na(IPT_track_1),
+    !is.na(White),
+    !is.na(CUDOS_pre),
+    !is.na(CUDOS_post),
+    CUDOS_pre > 20,
+  ) |>
+  mutate(
+    ID1  = as.integer(ID1),
+    pre  = as.numeric(CUXOS_pre),
+    post = as.numeric(CUXOS_post),
+  ) |>
+  select(
+    ID1,pre,post
+  ) |>
+  filter(!is.na(pre),
+         !is.na(post),
+         pre > 20)
+
+RCI_df_dep2 <- data.frame(RCI_df_dep2)
+RCI_df_anx2 <- data.frame(RCI_df_anx2)
+
+#1. JT classification for depression
+JTRCI (data = RCI_df_dep2, 
+                  pre = "pre", 
+                  post = "post", 
+                  ppid = "ID1", 
+                  reliability = .74, 
+                  indextype = "JT", 
+                  JTcrit = "auto",
+                  plottitle = "JT indices for Depression")
+
+DEP_JT_smol <- JTRCIdf
+colnames(DEP_JT_smol) <- paste0(colnames(DEP_JT_smol),"_dep")
+head(DEP_JT_smol)
+
+#2. JT classification for anxiety
+JTRCI (data = RCI_df_anx2, 
+                  pre = "pre", 
+                  post = "post", 
+                  ppid = "ID1", 
+                  reliability = .74, 
+                  indextype = "JT", 
+                  #JTcrit = "auto",
+                  plottitle = "JT Indices For Anxiety")
+
+ANX_JT_smol<- JTRCIdf
+
+colnames(ANX_JT_smol) <- paste0(colnames(ANX_JT_smol),"_anx")
+
+head(ANX_JT_smol)
+
+view(ANX_JT_smol)
 ```
@@
 ```{r}
-Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
+Mothership_post_anx <- left_join(Mothership_post,ANX_JT_smol, by = join_by(ID1 == ppid_anx)) |>
   mutate(
-    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
-    Depression_Responder = as.factor(recode(Depression_Responder,
-                                            "1" = "2",
-                                            "2" = "2",
-                                            "3" = "1",
-                                            "4" = "1",
-                                            "5" = "1"
-    )),
-    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
-    Depression_Responder = as.factor(recode(Depression_Responder,
-                                            "2" = "Non-Responder",
-                                            "1" = "Responder"
-    )),
     Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
@@
     !is.na(Anxiety_Responder),
+    )
+
+Mothership_post_dep <- left_join(Mothership_post,DEP_JT_smol, by = join_by(ID1 == ppid_dep)) |>
+  mutate(
+    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
+    Depression_Responder = as.factor(recode(Depression_Responder,
+                                            "1" = "2",
+                                            "2" = "2",
+                                            "3" = "1",
+                                            "4" = "1",
+                                            "5" = "1"
+    )),
+    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
+    Depression_Responder = as.factor(recode(Depression_Responder,
+                                            "2" = "Non-Responder",
+                                            "1" = "Responder"
+    ))) |>
+  filter(
     !is.na(Depression_Responder)
     )
+
+Mothership_post_joined <- full_join(Mothership_post_dep,Mothership_post_anx, by = join_by(ID1 == ID1), suffix = c(".x",".y")) |>
+  select(-ends_with(".y"))
+
+#It saves everything colname.x, so I'm going to remove the .x from everything
+names.x <- colnames(Mothership_post_joined)[2:248]
+colnames(Mothership_post_joined)[2:248] <- substr(names.x,1,nchar(names.x)-2)
 ```
@@
 
-AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
-                                   Mothership_post$Disorder_treat,
-                                   Mothership_post$BL_CUDOS,
-                                   Mothership_post$BL_CUXOS,
-                                   Mothership_post$CUDOS_pre,
-                                   Mothership_post$CUDOS_post,
-                                   Mothership_post$CUXOS_pre,
-                                   Mothership_post$CUXOS_post,
+AnxDep_PrePost <- data.frame(cbind(Mothership_post_joined$ID1,
+                                   Mothership_post_joined$Disorder_treat,
+                                   Mothership_post_joined$BL_CUDOS,
+                                   Mothership_post_joined$BL_CUXOS,
+                                   Mothership_post_joined$CUDOS_pre,
+                                   Mothership_post_joined$CUDOS_post,
+                                   Mothership_post_joined$CUXOS_pre,
+                                   Mothership_post_joined$CUXOS_post,
                                    #Extra stuff?
-                                   Mothership_post$Depression_Responder,
-                                   Mothership_post$Anxiety_Responder
+                                   Mothership_post_joined$Depression_Responder,
+                                   Mothership_post_joined$Anxiety_Responder
                                    #Mothership_post$RESPONDER_FIGS
 )) #%>%
-#filter(!is.na(Mothership_post$Disorder_treat))
-
-colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","Depression_Responder",
-                             "Anxiety_Responder")
-#, "RESPONDER_FIGS")
-
-#8. Create long data frame
-
-AnxDep_PrePost_Long <- AnxDep_PrePost %>% 
-  pivot_longer(
-    cols = CUDOS_pre:CUXOS_post, 
-    names_to = "Test",
-    values_to = "Score"
-  )
-AnxDep_PrePost_Long <-AnxDep_PrePost_Long %>%
-  mutate(
-    PrePost = ifelse(
-      Test == "CUDOS_pre", "Pre",
-      ifelse(Test == "CUXOS_pre" , "Pre", "Post"
-      )),
-    Score = as.integer(Score),
-    Test = as.factor(Test),
-    Test = as.factor(ifelse(Test == "CUDOS_pre",  "CUDOS",
-                            ifelse(Test == "CUDOS_post", "CUDOS", "CUXOS"
-                            ))))
-
-#9. Convert to data frame with means of values to be plotted
-AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
-  group_by(Test,PrePost) %>%
-  summarise(Score=mean(Score,na.rm=TRUE))
+
 ```
@@
 # Data analysis 
-## Part 1: Who is attending?
+## Part 1: Methods information
+```{r}
+
+```
+
+## Part 2: Who is attending?
 
@@
 - Table 4: demographic breakdown
-```{r}
-Mothership_lasso <- Mothership_post |>
+
+First greate dfs for analyses
+
+```{r}
+### Anxeity 
+Mothership_lasso_anx <- Mothership_post_anx |>
   filter(
@@
   !is.na(Anxiety_Responder),
-    !is.na(Depression_Responder),
   CUXOS_pre >= 20,
-    CUDOS_pre >= 20
   ) |>
   select( c(
-    Anxiety_Responder, Depression_Responder,Disorder_treat,
+    ID1,Anxiety_Responder,Disorder_treat,
     # Demographics
@@
   ))
-
-Mothership_lasso <- na.omit(Mothership_lasso)
-
-library(tableone)
+Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)
+
+### depression
+Mothership_lasso_dep <- Mothership_post_dep |>
+    filter(
+    !is.na(Some_College),
+    !is.na(Female),
+    !is.na(IPT_track_1),
+    !is.na(White),
+    !is.na(Depression_Responder),
+    CUDOS_pre >= 20,
+  ) |>
+  select( c(
+    ID1, Depression_Responder,Disorder_treat,
+    # Demographics
+    Age_1,Some_College:Married,White, #Discharge,
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    # Disorders
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
+    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+    Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    # RDQ
+    rdqPOST_coping:rdqPOST_wbs,
+    #For table 3 - RCI info
+    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
+  ))
+Mothership_lasso_dep <- na.omit(Mothership_lasso_dep)
+
+### joined df
+Mothership_lasso_joined <- full_join(Mothership_lasso_anx,Mothership_lasso_dep, by = join_by("ID1" == "ID1")) |> 
+    select(-ends_with(".y"))
+
+#It saves everything colname.x, so I'm going to remove the .x from everything
+names.x <- colnames(Mothership_lasso_joined)[3:34]
+colnames(Mothership_lasso_joined)[3:34] <- substr(names.x,1,nchar(names.x)-2)
+
+#Delete ID1 from dfs
+Mothership_lasso_anx <- Mothership_lasso_anx[,-1]
+Mothership_lasso_dep <- Mothership_lasso_dep[,-1]
+```
+
+```{r}
+
+library(tableone) # This can be used to grab Exporatory data analysis values
 
 ### first gather information based upon anxiety
-
 ## Vector of variables to summarize
-table1_vars_anx <- c("Anxiety_Responder",colnames(Mothership_lasso)[-1:-3])
-table1_vars_anx <- table1_vars_anx[1:28]
-
-colnames(Mothership_lasso)[-1]
+table1_vars_anx <- c(colnames(Mothership_lasso_anx)[-1:-2])
+table1_vars_anx <- table1_vars_anx[1:27]
+
 ## Vector of categorical variables that need transformation
 catVars <- c("Some_College", "Female" , "Married", "White",
-             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
-             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
+             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Other", 
+             "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
              "Substance_C", "Other_C" , "No_Co"
              )
-```
-
-```{r}
+
 ## Create a TableOne object
-table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Mothership_lasso,strata ="Anxiety_Responder",  factorVars = catVars)
+table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Mothership_lasso_anx,strata ="Anxiety_Responder",  factorVars = catVars, addOverall = T)
 table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
 table1_tab_anx <- data.frame(table1_tab_anx)
-table1_tab_anx<- table1_tab_anx[-2,]
-
+table1_tab_anx
 # add discriptive statistics 
@@
 # age
-table1_tab_anx[2,4] <- round(t_test(Age_1 ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_anx[2,5] <- round(cohens_d(Age_1 ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_anx[2,5] <- round(t_test(Age_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
+table1_tab_anx[2,6] <- round(cohens_d(Age_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
 # Some College 
-table1_tab_anx[3,4] <- round(chisq.test(Mothership_lasso$Some_College, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[3,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Some_College))$estimate,2)
+table1_tab_anx[3,5] <- round(chisq.test(Mothership_lasso_anx$Some_College, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[3,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Some_College))$estimate,2)
 # Female
-table1_tab_anx[4,4] <- round(chisq.test(Mothership_lasso$Female, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[4,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Female))$estimate,2)
+table1_tab_anx[4,5] <- round(chisq.test(Mothership_lasso_anx$Female, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[4,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Female))$estimate,2)
 # Married
-table1_tab_anx[5,4] <- round(chisq.test(Mothership_lasso$Married, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[5,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Married))$estimate,2)
+table1_tab_anx[5,5] <- round(chisq.test(Mothership_lasso_anx$Married, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[5,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Married))$estimate,2)
 # White
-table1_tab_anx[6,4] <- round(chisq.test(Mothership_lasso$White, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[6,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$White))$estimate,2)
+table1_tab_anx[6,5] <- round(chisq.test(Mothership_lasso_anx$White, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[6,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$White))$estimate,2)
 # Treatment track
-table1_tab_anx[7,4] <- round(chisq.test(Mothership_lasso$IPT_track_1, Mothership_lasso$Anxiety_Responder)$statistic,2)
-OR_IPT_anx <- table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$IPT_track_1)
+table1_tab_anx[7,5] <- round(chisq.test(Mothership_lasso_anx$IPT_track_1, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+OR_IPT_anx <- table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$IPT_track_1)
 # OR general vs Trauma track
-table1_tab_anx[9,5] <- round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Trauma"]))$estimate,2)
-table1_tab_anx[9,3] <-
+table1_tab_anx[9,6] <- round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Trauma"]))$estimate,2)
+table1_tab_anx[9,5] <-
 round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Trauma"]))$p,2)
 # OR General vs Young adult track 
+table1_tab_anx[10,6] <- 
+  round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Young Adult"]))$estimate,2)
 table1_tab_anx[10,5] <-
-  round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Young Adult"]))$estimate,2)
-table1_tab_anx[10,3] <-
 round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Young Adult"]))$p,2)
 # Days Completed in program
-table1_tab_anx[11,4] <- round(t_test(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_anx[11,5] <- round(cohens_d(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_anx[11,5] <- round(t_test(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
+table1_tab_anx[11,6] <- round(cohens_d(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
 # Days not attending treatment
-table1_tab_anx[12,4] <- round(t_test(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_anx[12,5] <- round(cohens_d(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_anx[12,5] <- round(t_test(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
+table1_tab_anx[12,6] <- round(cohens_d(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
 # Anxiety disorder
-table1_tab_anx[13,4] <- round(chisq.test(Mothership_lasso$Anxiety_D, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[13,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Anxiety_D))$estimate,2)
+table1_tab_anx[13,5] <- round(chisq.test(Mothership_lasso_anx$Anxiety_D, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[13,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Anxiety_D))$estimate,2)
 # Mood Disorders
-table1_tab_anx[14,4] <- round(chisq.test(Mothership_lasso$Mood_D, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[14,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Mood_D))$estimate,2)
+table1_tab_anx[14,5] <- round(chisq.test(Mothership_lasso_anx$Mood_D, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[14,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Mood_D))$estimate,2)
 # BPD 
-table1_tab_anx[15,4] <- round(chisq.test(Mothership_lasso$BPD_P, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[15,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$BPD_P))$estimate,2)
+table1_tab_anx[15,5] <- round(chisq.test(Mothership_lasso_anx$BPD_P, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[15,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$BPD_P))$estimate,2)
 # Truama Related Disorders
-table1_tab_anx[16,4] <- round(chisq.test(Mothership_lasso$Trauma_D, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[16,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Trauma_D))$estimate,2)
+table1_tab_anx[16,5] <- round(chisq.test(Mothership_lasso_anx$Trauma_D, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[16,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Trauma_D))$estimate,2)
 # Other Disorders
-table1_tab_anx[17,4] <- round(chisq.test(Mothership_lasso$Other, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[17,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Other))$estimate,2)
+table1_tab_anx[17,5] <- round(chisq.test(Mothership_lasso_anx$Other, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[17,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Other))$estimate,2)
 # Co-occurring anxiety disorder 
-table1_tab_anx[18,4] <- round(chisq.test(Mothership_lasso$Anxiety_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[18,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Anxiety_C))$estimate,2)
+table1_tab_anx[18,5] <- round(chisq.test(Mothership_lasso_anx$Anxiety_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[18,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Anxiety_C))$estimate,2)
 # Co-occurring mood disorder
-table1_tab_anx[19,4] <- round(chisq.test(Mothership_lasso$Mood_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[19,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Mood_C))$estimate,2)
+table1_tab_anx[19,5] <- round(chisq.test(Mothership_lasso_anx$Mood_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[19,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Mood_C))$estimate,2)
 # Co-occurring BPD
-table1_tab_anx[20,4] <- round(chisq.test(Mothership_lasso$BPD_Co_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[20,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$BPD_Co_C))$estimate,2)
+table1_tab_anx[20,5] <- round(chisq.test(Mothership_lasso_anx$BPD_Co_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[20,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$BPD_Co_C))$estimate,2)
 # Co-occurring Trauma Related Disorder
-table1_tab_anx[21,4] <- round(chisq.test(Mothership_lasso$Trauma_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[21,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Trauma_C))$estimate,2)
+table1_tab_anx[21,5] <- round(chisq.test(Mothership_lasso_anx$Trauma_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[21,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Trauma_C))$estimate,2)
 # Co-occurring Substance Use Disorders
-table1_tab_anx[22,4] <- round(chisq.test(Mothership_lasso$Substance_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[22,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Substance_C))$estimate,2)
+table1_tab_anx[22,5] <- round(chisq.test(Mothership_lasso_anx$Substance_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[22,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Substance_C))$estimate,2)
 # Co-occurring Other Disroders
-table1_tab_anx[23,4] <- round(chisq.test(Mothership_lasso$Other_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[23,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Other_C))$estimate,2)
+table1_tab_anx[23,5] <- round(chisq.test(Mothership_lasso_anx$Other_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[23,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Other_C))$estimate,2)
 # No Co-occurring Disorders
-table1_tab_anx[24,4] <- round(chisq.test(Mothership_lasso$No_Co, Mothership_lasso$Anxiety_Responder)$statistic,2)
-table1_tab_anx[24,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$No_Co))$estimate,2)
+table1_tab_anx[24,5] <- round(chisq.test(Mothership_lasso_anx$No_Co, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
+table1_tab_anx[24,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$No_Co))$estimate,2)
 # Number of Current diagnoses 
-table1_tab_anx[25,4] <- round(t_test(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_anx[25,5] <- round(cohens_d(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_anx[25,5] <- round(t_test(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
+table1_tab_anx[25,6] <- round(cohens_d(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
 # CUDOS Pre scores
-table1_tab_anx[26,4] <- round(t_test(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_anx[26,5] <- round(cohens_d(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_anx[26,5] <- round(t_test(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
+table1_tab_anx[26,6] <- round(cohens_d(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
 # CUXOS Pre scores
-table1_tab_anx[27,4] <- round(t_test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_anx[27,5] <- round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_anx[27,5] <- round(t_test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
+table1_tab_anx[27,6] <- round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
 # RDQ Coping post scores
-table1_tab_anx[28,4] <- round(t_test(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_anx[28,5] <- round(cohens_d(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_anx[28,5] <- round(t_test(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
+table1_tab_anx[28,6] <- round(cohens_d(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
 # RDQ Positive Mental Health post scores
-table1_tab_anx[29,4] <- round(t_test(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_anx[29,5] <- round(cohens_d(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_anx[29,5] <- round(t_test(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
+table1_tab_anx[29,6] <- round(cohens_d(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
 # RDQ Functioning post scores
-table1_tab_anx[30,4] <- round(t_test(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_anx[30,5] <- round(cohens_d(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_anx[30,5] <- round(t_test(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
+table1_tab_anx[30,6] <- round(cohens_d(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
 # RDQ Sense of Wellbeing post scores
-table1_tab_anx[31,4] <- round(t_test(rdqPOST_wbs ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_anx[31,5] <- round(cohens_d(rdqPOST_wbs ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_anx[31,5] <- round(t_test(rdqPOST_wbs ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
+table1_tab_anx[31,6] <- round(cohens_d(rdqPOST_wbs ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
 
@@
 table1_tab_anx
-```
-
-```{r}
-### next gather info based upon depression
+
+mean(Mothership_lasso_anx$CUXOS_post)
+sd(Mothership_lasso_anx$CUXOS_post)
+```
+
+```{r}
 
 ## Vector of variables to summarize
-table1_vars_dep <- c("Depression_Responder",colnames(Mothership_lasso)[-1:-3])
-table1_vars_dep <- table1_vars_dep[1:28]
+table1_vars_dep <- c(colnames(Mothership_lasso_dep)[-1:-2])
+table1_vars_dep <- table1_vars_dep[1:27]
 
 ## Create a TableOne object
-table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,strata ="Depression_Responder",  factorVars = catVars)
+table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso_dep,strata ="Depression_Responder",  factorVars = catVars, addOverall = T)
 table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
 table1_tab_dep <-data.frame(table1_tab_dep)
-table1_tab_dep <- table1_tab_dep[-2,]
 
@@
 
+table1_tab_dep
 # age
-table1_tab_dep[2,4] <- round(t_test(Age_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_dep[2,5] <- round(cohens_d(Age_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[2,5] <- round(t_test(Age_1 ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
+table1_tab_dep[2,6] <- round(cohens_d(Age_1 ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
 # Some College 
-table1_tab_dep[3,4] <- round(chisq.test(Mothership_lasso$Some_College, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[3,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Some_College))$estimate,2)
+table1_tab_dep[3,5] <- round(chisq.test(Mothership_lasso_dep$Some_College, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[3,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Some_College))$estimate,2)
 # Female
-table1_tab_dep[4,4] <- round(chisq.test(Mothership_lasso$Female, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[4,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Female))$estimate,2)
+table1_tab_dep[4,5] <- round(chisq.test(Mothership_lasso_dep$Female, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[4,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Female))$estimate,2)
 # Married
-table1_tab_dep[5,4] <- round(chisq.test(Mothership_lasso$Married, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[5,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Married))$estimate,2)
+table1_tab_dep[5,5] <- round(chisq.test(Mothership_lasso_dep$Married, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[5,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Married))$estimate,2)
 # White
-table1_tab_dep[6,4] <- round(chisq.test(Mothership_lasso$White, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[6,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$White))$estimate,2)
+table1_tab_dep[6,5] <- round(chisq.test(Mothership_lasso_dep$White, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[6,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$White))$estimate,2)
 # Treatment track
-table1_tab_dep[7,4] <- round(chisq.test(Mothership_lasso$IPT_track_1, Mothership_lasso$Depression_Responder)$statistic,2)
-OR_IPT_dep <- table(Mothership_lasso$Depression_Responder,Mothership_lasso$IPT_track_1)
+table1_tab_dep[7,5] <- round(chisq.test(Mothership_lasso_dep$IPT_track_1, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+OR_IPT_dep <- table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$IPT_track_1)
 # OR general vs Trauma track
 table1_tab_dep[9,5] <- round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Trauma"]))$estimate,2)
-table1_tab_dep[9,3] <-
+table1_tab_dep[9,6] <-
 round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Trauma"]))$p,2)
@@
   round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Young Adult"]))$estimate,2)
-table1_tab_dep[10,3] <-
+table1_tab_dep[10,6] <-
 round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Young Adult"]))$p,2)
 # Days Completed in program
-table1_tab_dep[11,4] <- round(t_test(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_dep[11,5] <- round(cohens_d(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[11,5] <- round(t_test(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
+table1_tab_dep[11,6] <- round(cohens_d(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
 # Days not attending treatment
-table1_tab_dep[12,4] <- round(t_test(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_dep[12,5] <- round(cohens_d(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[12,5] <- round(t_test(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
+table1_tab_dep[12,6] <- round(cohens_d(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
 # Anxiety disorder
-table1_tab_dep[13,4] <- round(chisq.test(Mothership_lasso$Anxiety_D, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[13,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Anxiety_D))$estimate,2)
+table1_tab_dep[13,5] <- round(chisq.test(Mothership_lasso_dep$Anxiety_D, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[13,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Anxiety_D))$estimate,2)
 # Mood Disorders
-table1_tab_dep[14,4] <- round(chisq.test(Mothership_lasso$Mood_D, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[14,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Mood_D))$estimate,2)
+table1_tab_dep[14,5] <- round(chisq.test(Mothership_lasso_dep$Mood_D, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[14,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Mood_D))$estimate,2)
 # BPD 
-table1_tab_dep[15,4] <- round(chisq.test(Mothership_lasso$BPD_P, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[15,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$BPD_P))$estimate,2)
+table1_tab_dep[15,5] <- round(chisq.test(Mothership_lasso_dep$BPD_P, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[15,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$BPD_P))$estimate,2)
 # Truama Related Disorders
-table1_tab_dep[16,4] <- round(chisq.test(Mothership_lasso$Trauma_D, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[16,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Trauma_D))$estimate,2)
+table1_tab_dep[16,5] <- round(chisq.test(Mothership_lasso_dep$Trauma_D, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[16,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Trauma_D))$estimate,2)
 # Other Disorders
-table1_tab_dep[17,4] <- round(chisq.test(Mothership_lasso$Other, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[17,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Other))$estimate,2)
+table1_tab_dep[17,5] <- round(chisq.test(Mothership_lasso_dep$Other, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[17,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Other))$estimate,2)
 # Co-occurring anxiety disorder 
-table1_tab_dep[18,4] <- round(chisq.test(Mothership_lasso$Anxiety_C, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[18,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Anxiety_C))$estimate,2)
+table1_tab_dep[18,5] <- round(chisq.test(Mothership_lasso_dep$Anxiety_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[18,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Anxiety_C))$estimate,2)
 # Co-occurring mood disorder
-table1_tab_dep[19,4] <- round(chisq.test(Mothership_lasso$Mood_C, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[19,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Mood_C))$estimate,2)
+table1_tab_dep[19,5] <- round(chisq.test(Mothership_lasso_dep$Mood_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[19,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Mood_C))$estimate,2)
 # Co-occurring BPD
-table1_tab_dep[20,4] <- round(chisq.test(Mothership_lasso$BPD_Co_C, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[20,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$BPD_Co_C))$estimate,2)
+table1_tab_dep[20,5] <- round(chisq.test(Mothership_lasso_dep$BPD_Co_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[20,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$BPD_Co_C))$estimate,2)
 # Co-occurring Trauma Related Disorder
-table1_tab_dep[21,4] <- round(chisq.test(Mothership_lasso$Trauma_C, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[21,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Trauma_C))$estimate,2)
+table1_tab_dep[21,5] <- round(chisq.test(Mothership_lasso_dep$Trauma_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[21,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Trauma_C))$estimate,2)
 # Co-occurring Substance Use Disorders
-table1_tab_dep[22,4] <- round(chisq.test(Mothership_lasso$Substance_C, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[22,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Substance_C))$estimate,2)
+table1_tab_dep[22,5] <- round(chisq.test(Mothership_lasso_dep$Substance_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[22,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Substance_C))$estimate,2)
 # Co-occurring Other Disroders
-table1_tab_dep[23,4] <- round(chisq.test(Mothership_lasso$Other_C, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[23,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$Other_C))$estimate,2)
+table1_tab_dep[23,5] <- round(chisq.test(Mothership_lasso_dep$Other_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[23,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Other_C))$estimate,2)
 # No Co-occurring Disorders
-table1_tab_dep[24,4] <- round(chisq.test(Mothership_lasso$No_Co, Mothership_lasso$Depression_Responder)$statistic,2)
-table1_tab_dep[24,5] <- round(fisher.test(table(Mothership_lasso$Depression_Responder,Mothership_lasso$No_Co))$estimate,2)
+table1_tab_dep[24,5] <- round(chisq.test(Mothership_lasso_dep$No_Co, Mothership_lasso_dep$Depression_Responder)$statistic,2)
+table1_tab_dep[24,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$No_Co))$estimate,2)
 # Number of Current diagnoses 
-table1_tab_dep[25,4] <- round(t_test(Current_Dx ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_dep[25,5] <- round(cohens_d(Current_Dx ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[25,5] <- round(t_test(Current_Dx ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
+table1_tab_dep[25,6] <- round(cohens_d(Current_Dx ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
 # CUDOS Pre scores
-table1_tab_dep[26,4] <- round(t_test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_dep[26,5] <- round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[26,5] <- round(t_test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
+table1_tab_dep[26,6] <- round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
 # CUXOS Pre scores
-table1_tab_dep[27,4] <- round(t_test(CUXOS_pre ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_dep[27,5] <- round(cohens_d(CUXOS_pre ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[27,5] <- round(t_test(CUXOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
+table1_tab_dep[27,6] <- round(cohens_d(CUXOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
 # RDQ Coping post scores
-table1_tab_dep[28,4] <- round(t_test(rdqPOST_coping ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_dep[28,5] <- round(cohens_d(rdqPOST_coping ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[28,5] <- round(t_test(rdqPOST_coping ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
+table1_tab_dep[28,6] <- round(cohens_d(rdqPOST_coping ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
 # RDQ Positive Mental Health post scores
-table1_tab_dep[29,4] <- round(t_test(rdqPOST_pmh ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_dep[29,5] <- round(cohens_d(rdqPOST_pmh ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[29,5] <- round(t_test(rdqPOST_pmh ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
+table1_tab_dep[29,6] <- round(cohens_d(rdqPOST_pmh ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
 # RDQ Functioning post scores
-table1_tab_dep[30,4] <- round(t_test(rdqPOST_func ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_dep[30,5] <- round(cohens_d(rdqPOST_func ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[30,5] <- round(t_test(rdqPOST_func ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
+table1_tab_dep[30,6] <- round(cohens_d(rdqPOST_func ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
 # RDQ Sense of Wellbeing post scores
-table1_tab_dep[31,4] <- round(t_test(rdqPOST_wbs ~ Depression_Responder, data = Mothership_lasso)$statistic,2)
-table1_tab_dep[31,5] <- round(cohens_d(rdqPOST_wbs ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+table1_tab_dep[31,5] <- round(t_test(rdqPOST_wbs ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
+table1_tab_dep[31,6] <- round(cohens_d(rdqPOST_wbs ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
 
@@
 ```{r}
-## Vector of variables to summarize
-table1_vars_gen <- c(colnames(Mothership_lasso)[-1:-3])
-table1_vars_gen<- table1_vars_gen[1:27]
-
-## lastly get the overal treatment breakdown
-table1_gen <- CreateTableOne(vars = table1_vars_gen, data = Mothership_lasso,  factorVars = catVars)
-table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
-table1_gen <-data.frame(table1_gen)
-write_csv(table1_gen,"~/Downloads/table1_gen.csv")
-table1_gen
+# 
+# Mothership_lasso_dep <- na.omit(Mothership_lasso_dep)
+# left_join()
+# 
+# ## Vector of variables to summarize
+# table1_vars_gen <- c(colnames(Mothership_lasso_joined)[-1:-3])
+# table1_vars_gen<- table1_vars_gen[1:27]
+# 
+# Mothership_lasso
+# 
+# ## lastly get the overal treatment breakdown
+# table1_gen <- CreateTableOne(vars = table1_vars_gen, data = Mothership_lasso,  factorVars = catVars)
+# table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
+# table1_gen <-data.frame(table1_gen)
+# write_csv(table1_gen,"~/Downloads/table1_gen.csv")
+# table1_gen
 
@@
     #make df
-      anx_rep_tab <- Mothership_lasso |>
+      anx_rep_tab <- Mothership_lasso_anx |>
         group_by(Anxiety_Responder) |>
@@
   #Make df
-    dep_rep_tab <- Mothership_lasso |>
+    dep_rep_tab <- Mothership_lasso_dep |>
       group_by(Depression_Responder) |>
@@
   #1.1 depression responders   
-    t.test(subset(Mothership_lasso,Depression_Responder == "Responder")$CUDOS_pre,
-       subset(Mothership_lasso,Depression_Responder == "Responder")$CUDOS_post,
+    t.test(subset(Mothership_lasso_dep,Depression_Responder == "Responder")$CUDOS_pre,
+       subset(Mothership_lasso_dep,Depression_Responder == "Responder")$CUDOS_post,
        paired = TRUE, alternative = "two.sided"
@@
   #1.2 depression non-responders   
-     t.test(subset(Mothership_lasso,Depression_Responder == "Non-Responder")$CUDOS_pre,
-       subset(Mothership_lasso,Depression_Responder == "Non-Responder")$CUDOS_post,
+     t.test(subset(Mothership_lasso_dep,Depression_Responder == "Non-Responder")$CUDOS_pre,
+       subset(Mothership_lasso_dep,Depression_Responder == "Non-Responder")$CUDOS_post,
        paired = TRUE, alternative = "two.sided"
@@
   #1.3 anxiety responders   
-    t.test(subset(Mothership_lasso,Anxiety_Responder == "Responder")$CUXOS_pre,
-       subset(Mothership_lasso,Anxiety_Responder == "Responder")$CUXOS_post,
+    t.test(subset(Mothership_lasso_anx,Anxiety_Responder == "Responder")$CUXOS_pre,
+       subset(Mothership_lasso_anx,Anxiety_Responder == "Responder")$CUXOS_post,
        paired = TRUE, alternative = "two.sided"
@@
   #1.2 anxiety non-responders   
-     t.test(subset(Mothership_lasso,Anxiety_Responder == "Non-Responder")$CUXOS_pre,
-       subset(Mothership_lasso,Anxiety_Responder == "Non-Responder")$CUXOS_post,
+     t.test(subset(Mothership_lasso_anx,Anxiety_Responder == "Non-Responder")$CUXOS_pre,
+       subset(Mothership_lasso_anx,Anxiety_Responder == "Non-Responder")$CUXOS_post,
        paired = TRUE, alternative = "two.sided"
@@
   #2.1 Pre scores of anxiety
-     t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso)
+     t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)
   #2.2 Post scores of anxiety
-     t.test(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso)
-     sd(subset(Mothership_lasso,Anxiety_Responder == "Responder")$CUXOS_post)
-     sd(subset(Mothership_lasso,Anxiety_Responder == "Non-Responder")$CUXOS_post)
-     round(cohens_d(CUXOS_post ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+     t.test(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)
+     sd(subset(Mothership_lasso_anx,Anxiety_Responder == "Responder")$CUXOS_post)
+     sd(subset(Mothership_lasso_anx,Anxiety_Responder == "Non-Responder")$CUXOS_post)
+     round(cohens_d(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
   #2.3 Pre scores of depression
-     t.test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso)
+     t.test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)
   #2.4 Post scores of depression
-     t.test(CUDOS_post ~ Depression_Responder, data = Mothership_lasso)
-     sd(subset(Mothership_lasso,Depression_Responder == "Responder")$CUDOS_post)
-     sd(subset(Mothership_lasso,Depression_Responder == "Non-Responder")$CUDOS_post)
-     round(cohens_d(CUDOS_post ~ Depression_Responder, data = Mothership_lasso)$effsize,2)
+     t.test(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)
+     sd(subset(Mothership_lasso_dep,Depression_Responder == "Responder")$CUDOS_post)
+     sd(subset(Mothership_lasso_dep,Depression_Responder == "Non-Responder")$CUDOS_post)
+     round(cohens_d(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
+```
+dataset visualizatoin
+```{r}
+# #install.packages("ggdist")
+# library("ggdist")
+# 
+# Mothership_lasso |> 
+#   ggplot( aes(x=Depression_Responder, y=CUDOS_pre, fill=Depression_Responder)) +
+#     geom_boxplot() +
+#    #viridis::scale_fill_viridis(discrete = TRUE, alpha=0.6) +
+#     geom_jitter(color="black", size=.6 , alpha=0.9) +
+#     theme(
+#       legend.position="none",
+#       plot.title = element_text(size=11)
+#     ) +
+# #    ggtitle("Pre scores of depression severity") +
+#     xlab("Depression Severity") +
+#     ylim(0,80)
+# 
+# Mothership_lasso|>
+# ggplot( mapping=aes(x=Trauma_C)) +
+#   geom_bar()
+# 
+# Mothership_lasso|>
+# ggplot( mapping=aes(x= Current_Dx)) +
+#         geom_histogram() +
+#     theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
+#   theme(panel.background=NULL)+
+#   theme(legend.title = element_blank()) 
+#
+
 ```
@@
 ```{r}
-# Disorders by treatment response
-Dis_tab <- data.frame(table1::table1(~Disorder_treat + Current_Dx | Anxiety_Responder, 
-                                     data = Mothership_lasso))
-colnames(Dis_tab) = c("Variables","Anxiety Non Responder", "Anxiety Responder", "Total")
-
-Dis_tab1 <- data.frame(table1::table1(~Disorder_treat + Current_Dx | Depression_Responder, 
-                                     data = Mothership_lasso))
-colnames(Dis_tab1) = c("Variables","Depression Non Responder", "Depression Responder", "Total")
-Dis_tab <- cbind(Dis_tab1[,1:3],Dis_tab[,2:4])
-Dis_tab
+
+Mothership_lasso_anx
+
+# # Disorders by treatment response
+# Dis_tab <- data.frame(table1::table1(~Disorder_treat + Current_Dx | Anxiety_Responder, 
+#                                      data = Mothership_lasso_joined))
+# colnames(Dis_tab) = c("Variables","Anxiety Non Responder", "Anxiety Responder", "Total")
+# 
+# Dis_tab1 <- data.frame(table1::table1(~Disorder_treat + Current_Dx | Depression_Responder, 
+#                                      data = Mothership_lasso))
+# colnames(Dis_tab1) = c("Variables","Depression Non Responder", "Depression Responder", "Total")
+# Dis_tab <- cbind(Dis_tab1[,1:3],Dis_tab[,2:4])
+# Dis_tab
 
 #Full demographic break down
-dim(Mothership_lasso)
-
-co_dis_tab <- Mothership_lasso |>
+
+co_dis_tab <- Mothership_lasso_joined |>
   pivot_longer(
@@
 ```{r}
-
-Vars_dep <- Mothership_lasso |>
-  select( c(
-    Depression_Responder,
-    # Demographics
-    Age_1,Some_College:Married,White, #Discharge,
-    # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
-    # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
-    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
-    Current_Dx,
-    # Pre-Post stuff
-    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
-    # RDQ
-    rdqPOST_coping:rdqPOST_wbs  
-    ))
-
-Vars_anx <- Mothership_lasso |>
-  select( c(
-    Anxiety_Responder,
-    # Demographics
-    Age_1,Some_College:Married,White, #Discharge,
-    # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
-    # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
-    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
-    Current_Dx,
-    # Pre-Post stuff
-    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
-    # RDQ
-    rdqPOST_coping:rdqPOST_wbs  
-  ))
+# 
+# Vars_dep <- Mothership_lasso |>
+#   select( c(
+#     Depression_Responder,
+#     # Demographics
+#     Age_1,Some_College:Married,White, #Discharge,
+#     # Treatment info
+#     IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+#     # Disorders
+#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
+#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+#     Current_Dx,
+#     # Pre-Post stuff
+#     CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+#     # RDQ
+#     rdqPOST_coping:rdqPOST_wbs  
+#     ))
+# 
+# Vars_anx <- Mothership_lasso |>
+#   select( c(
+#     Anxiety_Responder,
+#     # Demographics
+#     Age_1,Some_College:Married,White, #Discharge,
+#     # Treatment info
+#     IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+#     # Disorders
+#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
+#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+#     Current_Dx,
+#     # Pre-Post stuff
+#     CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+#     # RDQ
+#     rdqPOST_coping:rdqPOST_wbs  
+#   ))
 
@@
 
-JT_table[1,] = c("CUXOS", unlist(summary(Vars_anx$Anxiety_Responder)))
+JT_table[1,] = c("CUXOS", unlist(summary(Mothership_lasso_anx$Anxiety_Responder)))
 # Depresssion
-JT_table[2,] = c("CUDOS", unlist(summary(Vars_dep$Depression_Responder)))
+JT_table[2,] = c("CUDOS", unlist(summary(Mothership_lasso_dep$Depression_Responder)))
 
@@
 ```{r}
-Mothership_lasso_dep <- Mothership_lasso |>
-    filter(
-    !is.na(Some_College),
-    !is.na(Female),
-    !is.na(IPT_track_1),
-    !is.na(White),
-    !is.na(Depression_Responder)
-  )
 
@@
 
-summary(Vars_dep$Depression_Responder)
-
 # old model
@@
 
+tmp_coeffs <- coef(lasso.model.min.dep, s = "lambda.min")
+Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
+Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
+Dep_reg_coefs
+```
+
+```{r}
 ## min model
@@
       # predictors
-        Days_complete_1 + Days_not_attended_1 + Mood_C + CUDOS_pre +
-        CUXOS_pre + 
+        Some_College  + Married + White +
+        Days_not_attended_1 + Mood_C +
+        CUDOS_pre + CUXOS_pre + 
         rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
@@
    R2.min.dep <- performance::r2(glm_min_dep)
-
+  R2.min.dep
 # df for Forrest plots
@@
 ```{r}
-Mothership_lasso_anx <- Mothership_lasso |>
-    filter(
-    !is.na(Some_College),
-    !is.na(Female),
-    !is.na(IPT_track_1),
-    !is.na(White),
-    !is.na(Anxiety_Responder)
-  )
 
@@
 
+tmp_coeffs <- coef(lasso.model.min.anx, s = "lambda.min")
+Anx_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
+Anx_reg_coefs <- Anx_coefs[2:length(Anx_coefs)]
+Anx_reg_coefs
+
 ## min model
@@
       # predictors
-        Age_1 + Married + Days_complete_1 + Days_not_attended_1 +
-        Anxiety_D + BPD_Co_C + 
-        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func,
+        Age_1 + Some_College + Married + 
+        White +  Days_complete_1 +Days_not_attended_1 + 
+        Anxiety_D + Trauma_D + Other + 
+        Substance_C + CUXOS_pre + rdqPOST_coping + 
+        rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
       family = "binomial")
-
-####### JT - wo/Substance_D
-  # glm_min_anx <-
-  #     glm(
-  #     #Outcome varaible
-  #       Anxiety_Responder ~
-  #     # predictors
-  #       Age_1 + Married + Days_complete_1 + Days_not_attended_1 +
-  #       Anxiety_D + Trauma_D + BPD_Co_C +
-  #       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
-  #     #data
-  #     data = Vars_anx,
-  #     # type of regression : logistic = binary / binomial
-  #     family = "binomial")
 
@@
    R2.min.anx <- performance::r2(glm_min_anx)
-
+   R2.min.anx
 # df for Forrest plots
@@
 #Change the names of variables
-FP_anx$Variable
+FP_anx$Variable = Anx_reg_coefs
 
@@
 
-FP_anx$Variable = c(
-                    "Age", "Unmarried", "Days Completed", "Days Not Attended",
-                    "Anxiety Disorder", "Co-Occuring BPD",
-                    "Coping Ability", "Positive Mental Health", "Functioning"
-                    )
+Anx_reg_coefs[1:10] <- c("Age","Some_College","Married", "White","Days_complete","Days_not_attended", "Anxiety_D", "Trauma_D","Other", "Substance_C")
+FP_anx$Variable = Anx_reg_coefs
+
+Anx_reg_coefs
 # FP_anx$Variable = c(                      
@@
   #adjust the dimentions. 
-  coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1)) +
+  coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
+                  xlim = c(.4,2)) +
   #add a line at 1 for reference 
@@
   #add anotations to help suggests what each side means.
-  annotate("text", x = .75, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
-  annotate("text", x = 1.25, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
+  annotate("text", x = .6, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
+  annotate("text", x = 1.5, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
   #Git rid of the Y - Axis
@@
   patchwork::area(t = 0, l = 0, b = 30, r = 30),
-  patchwork::area(t = 0, l = 15, b = 30, r = 25),
+  patchwork::area(t = 0, l = 16, b = 30, r = 25),
   patchwork::area(t = 0, l = 22, b = 30, r = 30) 
@@
 #rename the variables for the figure
+FP_dep$Variable = Dep_reg_coefs
 # FP_dep$Variable = c(
-#                     "Days Completed", "Days Not Attended", 
-#                     "Co-Ocurring Mood Disorder", "CUXOS Pre-Score", "CUDOS Pre-Score",
+#                      "Days Not Attended",
+#                     "CUDOS Pre-Score",
 #                     "Coping Ability", "Positive Mental Health", "Functioning",
@@
 #                     )
-FP_dep$Variable = c(
-                     "Days Not Attended",
-                    "CUDOS Pre-Score",
-                    "Coping Ability", "Positive Mental Health", "Functioning",
-                    "Sense of Well Being"
-                    )
 
@@
   )
-FP_dep
 
@@
   #add anotations to help suggests what each side means.
-  annotate("text", x = .8, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
-  annotate("text", x = 1.2, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
+  annotate("text", x = .75, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
+  annotate("text", x = 1.25, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
   #Git rid of the Y - Axis

### 2024-04-29 Lasso_RCI_Response.Rmd
updated tables and figures!

@@
 
-RCI_df_anx2 <- Mothership_post |>
+Mothership_lasso <- Mothership_post |>
+  filter(
+  !is.na(Some_College),
+  !is.na(Female),
+  !is.na(IPT_track_1),
+  !is.na(White),
+  #!is.na(Anxiety_Responder),
+  CUXOS_pre >= 20,
+  ) |>
+  select( c(
+    ID1,Disorder_treat,
+    # Demographics
+    Age_1,Some_College:Married,White, #Discharge,
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    # Disorders
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
+    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+    Current_Dx,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    # RDQ
+    rdqPOST_coping:rdqPOST_wbs,
+    #For table 3 - RCI info
+    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
+  ))
+Mothership_lasso_1 <- na.omit(Mothership_lasso)
+
+RCI_df_anx2 <- Mothership_lasso_1 |>
   filter(
@@
 
-RCI_df_dep2 <- Mothership_post |>
+RCI_df_dep2 <- Mothership_lasso_1 |>
   filter(
@@
 
-view(ANX_JT_smol)
+view(DEP_JT_smol)
 ```
@@
     Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
+  )
     #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
-    Anx_Responder = as.factor(
-      ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
-      ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
-      )),
-    Dep_Responder = as.factor(
-      ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
-      ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
-      )),
-    Treatment_Responder = as.factor(
-      ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
-      ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
-      ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
-      ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
-      )))))))))))
+    # Anx_Responder = as.factor(
+    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  <= -50, "Responder",
+    #   ifelse(CUXOS_pre <= 20 & Percent_Anx_change  > -50,  "Unresponders", NA)   
+    #   )),
+    # Dep_Responder = as.factor(
+    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange <= -50, "Responder",
+    #   ifelse(CUDOS_pre <= 20 & Percent_Dep_Dchange > -50,   "Unresponders", NA) 
+    #   )),
+    # Treatment_Responder = as.factor(
+    #   ifelse(CUXOS_pre > 10 & CUXOS_pre > 10 & Percent_Anx_change  <= -50 & Percent_Anx_change < 0 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange <= -50, "Both_Responder", 
+    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change  <= -50, "Anx Responder",
+    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange <= -50, "Dep Responder",
+    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0 & CUXOS_pre > 10 & Percent_Anx_change > 0, "Both Worse",
+    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change > 0, "Anx Worse",
+    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange > 0, "Dep Worse",
+    #   ifelse(CUXOS_pre > 10 & CUDOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Both Unresponder",
+    #   ifelse(CUDOS_pre > 10 & Percent_Dep_Dchange < 0 & Percent_Dep_Dchange > -50, "Dep Unresponders", 
+    #   ifelse(CUXOS_pre > 10 & Percent_Anx_change < 0 & Percent_Anx_change > -50, "Anx Unresponders", "Low Baseline"
+      # )))))))))))
 
@@
     )),
-    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
+    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, NA)),
     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
@@
     )),
-    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
+    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, NA)),
     Depression_Responder = as.factor(recode(Depression_Responder,
@@
 
+table1_tab_anx[,2:7] <- table1_tab_anx
+table1_tab_anx[,1] <- rownames(table1_tab_anx)
+colnames(table1_tab_anx) <- c("Variables",colnames(table1_tab_anx)[1:6])
+
+table1_tab_anx
+
 write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
-table1_tab_anx
-
-mean(Mothership_lasso_anx$CUXOS_post)
-sd(Mothership_lasso_anx$CUXOS_post)
-```
-
-```{r}
-
+```
+
+```{r}
 ## Vector of variables to summarize
@@
 table1_tab_dep
+
 # age
@@
 
+table1_tab_dep[,2:7] <- table1_tab_dep
+table1_tab_dep[,1] <- rownames(table1_tab_dep)
+colnames(table1_tab_dep) <- c("Variables",colnames(table1_tab_dep)[1:6])
+
 table1_tab_dep
@@
 
-```{r}
-# 
-# Mothership_lasso_dep <- na.omit(Mothership_lasso_dep)
-# left_join()
-# 
-# ## Vector of variables to summarize
-# table1_vars_gen <- c(colnames(Mothership_lasso_joined)[-1:-3])
-# table1_vars_gen<- table1_vars_gen[1:27]
-# 
-# Mothership_lasso
-# 
-# ## lastly get the overal treatment breakdown
-# table1_gen <- CreateTableOne(vars = table1_vars_gen, data = Mothership_lasso,  factorVars = catVars)
-# table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
-# table1_gen <-data.frame(table1_gen)
-# write_csv(table1_gen,"~/Downloads/table1_gen.csv")
-# table1_gen
+Means and SDs of post scores
+```{r}
+
+mean(Mothership_lasso_anx$CUXOS_post)
+sd(Mothership_lasso_anx$CUXOS_post)
+
+mean(Mothership_lasso_dep$CUDOS_post)
+sd(Mothership_lasso_dep$CUDOS_post)
 
@@
 ```
-Figure 1: 
+## Part 2: RCI ANALYSIS - Treatment Response
+Anxiety & Depression = Total response
+- Table 4: RCI Analsyis results
+  + Anxiety, Depression, Total response
+- Figure 2 / Supplimetal 2: RCI Analysis figs 
+  + Anxeity & Depression
+
+Table 3
+```{r}
+# RCI_table
+
+# JT Table
+JT_table <- data.frame(matrix(NA,nrow = 3,ncol = 6))
+colnames(JT_table) = c("Instrument","Responder","Non-Responder", "Mean Pre Score", "RCI","JT Criterion A")
+#discriptor row
+
+JT_table[1,] = c(NA,"n","n", "M (SD)",NA,NA)
+summary(Mothership_lasso_anx$Anxiety_Responder)[[1]]
+
+#Anxiety
+JT_table[2,] = c("CUXOS", 
+                 summary(Mothership_lasso_anx$Anxiety_Responder)[[1]],
+                 summary(Mothership_lasso_anx$Anxiety_Responder)[[2]],
+                 paste0(round(mean(Mothership_lasso_anx$CUXOS_pre),2), " (", 
+                        round(sd(Mothership_lasso_anx$CUXOS_pre),2),")"),
+                 13,
+                 21)
+
+summary(Mothership_lasso_anx$Anxiety_Responder)[2]
+
+# Depresssion
+JT_table[3,] = c("CUDOS", 
+                 summary(Mothership_lasso_dep$Depression_Responder)[[1]],             
+                 summary(Mothership_lasso_dep$Depression_Responder)[[2]],
+                 paste0(round(mean(Mothership_lasso_dep$CUDOS_pre),2), " (", 
+                        round(sd(Mothership_lasso_dep$CUDOS_pre),2),")"),
+                 21,
+                 17)
+
+JT_table
+```
+
+###table 4A
+Between Group Differences of Anxiety at Pre and Post Timepoints by Anxiety Treatment Response
+```{r}
+#table set up
+tab4 <- data.frame(matrix(NA,nrow = 5,ncol = 5))
+colnames(tab4) = c("Instrument","Responder","Non-Responder", "Test Score", "Effect Size")
+tab4[1,] = c(NA,"M (SD)", "M (SD)", "t", "d")
+
+#anxiety
+
+t.test_pre_anx  <- t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)
+t.test_post_anx <- t.test(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)
+
+t.test_pre_dep  <- t.test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)
+t.test_post_dep <- t.test(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)
+
+##mean
+t.test_pre_anx$estimate[[1]]
+
+t.test_pre_anx$statistic[[1]]
+
+#CUXOS PRE
+tab4[2,] = c(
+  "CUXOS Pre",
+  #Responder
+  paste0(round(t.test_pre_anx$estimate[[1]],2)," (",
+         round(sd(subset(Mothership_lasso_anx,
+                         Anxiety_Responder == "Responder")$CUXOS_pre),2),
+         ")"),
+  #non-responder
+  paste0(round(t.test_pre_anx$estimate[[2]],2)," (",
+         round(sd(subset(Mothership_lasso_anx,
+                         Anxiety_Responder == "Non-Responder")$CUXOS_pre),2),
+         ")"),
+  #t-stat
+  round(t.test_pre_anx$statistic[[1]],2),
+  #effect size
+  round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
+    )
+
+#CUXOS Post
+tab4[3,] = c(
+  "CUXOS Post",
+  #Responder
+  paste0(round(t.test_post_anx$estimate[[1]],2)," (",
+         round(sd(subset(Mothership_lasso_anx,
+                         Anxiety_Responder == "Responder")$CUXOS_post),2),
+         ")"),
+  #non-responder
+  paste0(round(t.test_post_anx$estimate[[2]],2)," (",
+         round(sd(subset(Mothership_lasso_anx,
+                         Anxiety_Responder == "Non-Responder")$CUXOS_post),2),
+         ")"),
+  #t-stat
+  round(t.test_post_anx$statistic[[1]],2),
+  #effect size
+  round(cohens_d(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
+    )
+
+#CUDOS PRE
+tab4[4,] = c(
+  "CUDOS Pre",
+  #Responder
+  paste0(round(t.test_pre_dep$estimate[[1]],2)," (",
+         round(sd(subset(Mothership_lasso_dep,
+                         Depression_Responder == "Responder")$CUDOS_pre),2),
+         ")"),
+  #non-responder
+  paste0(round(t.test_pre_dep$estimate[[2]],2)," (",
+         round(sd(subset(Mothership_lasso_dep,
+                         Depression_Responder == "Non-Responder")$CUDOS_pre),2),
+         ")"),
+  #t-stat
+  round(t.test_pre_dep$statistic[[1]],2),
+  #effect size
+  round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
+    )
+
+#CUDOS Post
+tab4[5,] = c(
+  "CUDOS Post",
+  #Responder
+  paste0(round(t.test_post_dep$estimate[[1]],2)," (",
+         round(sd(subset(Mothership_lasso_dep,
+                         Depression_Responder == "Responder")$CUDOS_post),2),
+         ")"),
+  #non-responder
+  paste0(round(t.test_post_dep$estimate[[2]],2)," (",
+         round(sd(subset(Mothership_lasso_dep,
+                         Depression_Responder == "Non-Responder")$CUDOS_post),2),
+         ")"),
+  #t-stat
+  round(t.test_post_dep$statistic[[1]],2),
+  #effect size
+  round(cohens_d(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
+    )
+
+tab4
+```
+
 ```{r}
@@
      t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)
+     round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
   #2.2 Post scores of anxiety
@@
      t.test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)
+     round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
   #2.4 Post scores of depression
@@
      round(cohens_d(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-```
-dataset visualizatoin
+
+  test1  <- t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)
+
+test1$estimate[[1]] #responder pre cuxos mean
+
+```
+
+```{r}
+
+```
+
+ataset visualizatoin
 ```{r}
@@
 colnames(anx_prepost)[1] = "Responder"
+
+anx_prepost
 
@@
 
-## Part 2: RCI ANALYSIS - Treatment Response
-Anxiety & Depression = Total response
-- Table 4: RCI Analsyis results
-  + Anxiety, Depression, Total response
-- Figure 2 / Supplimetal 2: RCI Analysis figs 
-  + Anxeity & Depression
-```{r}
-# RCI STUFF
-# RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
-# colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
-# #anxiety 
-# 
-# RCI_table[,1] = c("CUXOS", unlist(summary(Mothership_lasso$Anxiety_Responder)))
-# # Depresssion
-# RCI_table[,2] = c("CUDOS", unlist(summary(Mothership_lasso$Depression_Responder)))
-# # #Total
-# # RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
-# 
-# RCI_table
-
-# JT Table
-JT_table <- data.frame(matrix(NA,nrow = 2,ncol = 3))
-colnames(JT_table) = c("Varaibles","Responder","Non-Responder")
-#anxiety
-
-JT_table[1,] = c("CUXOS", unlist(summary(Mothership_lasso_anx$Anxiety_Responder)))
-# Depresssion
-JT_table[2,] = c("CUDOS", unlist(summary(Mothership_lasso_dep$Depression_Responder)))
-
-JT_table
-```
-
 ## Part 3 Logistic lasso
@@
     Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, #Psychotic_D,  
-    #Other,
+    Other,
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
 ```{r}
-## min model
+# min model
 glm_min_dep <-
@@
     # predictors
-        Some_College  + Married + White +
-        Days_not_attended_1 + Mood_C +
-        CUDOS_pre + CUXOS_pre + 
+      Age_1  + Some_College + Married + IPT_track_1 +
+      Days_complete_1 + Days_not_attended_1 + Anxiety_D + Trauma_D +
+      Trauma_C + Substance_C +
       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
@@
 
+  # glm_min_dep <-
+  #           glm(
+  #     #Outcome varaible
+  #       Depression_Responder ~
+  #     # predictors
+  #       Age_1  +
+  #       Days_complete_1 + Days_not_attended_1 + Anxiety_D + 
+  #       BPD_Co_C + Current_Dx + CUXOS_pre+
+  #       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+  #     #data
+  #       data = Vars_dep,
+  #     # type of regression : logistic = binary / binomial
+  #       family = "binomial",
+  #     )
+
+install.packages("rempsyc")
+library(rempsyc)
+nice_table(tidy.summary.min.dep)
+
 # Summary of the model
@@
   tidy.summary.min.dep <- tidy(glm_min_dep)
-
+  tidy.summary.min.dep
 # Coefficients
@@
 ```{r}
+tmp_coeffs <- coef(lasso.model.1se.dep, s = "lambda.1se")
+Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
+Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
+Dep_reg_coefs
 
@@
 # Coefficients
-  coefs.1se.dep <- abs(coef(glm_1se_dep))
+  coefs.1se.dep <- round(abs(coef(glm_1se_dep)),2)
 
 # Odds ratio
-  OR.1se.dep <- exp(coef(glm_1se_dep))
+  OR.1se.dep <- round(exp(coef(glm_1se_dep)),2)
 
 # OR 95% CI
-  CI.1se.dep <- data.frame(exp(confint(glm_1se_dep)))
+  CI.1se.dep <- round(data.frame(exp(confint(glm_1se_dep))),2)
 
@@
 FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
+FP.1se.dep$p.adjusted <- round(FP.1se.dep$p.adjusted,2)
 FP.1se.dep$type = c("Depression")
@@
       # predictors
-        Age_1 + Some_College + Married + 
-        White +  Days_complete_1 +Days_not_attended_1 + 
-        Anxiety_D + Trauma_D + Other + 
-        Substance_C + CUXOS_pre + rdqPOST_coping + 
-        rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+        Days_complete_1 + Days_not_attended_1 + Anxiety_C + Substance_C + 
+        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
 write_csv(FP.min.anx, "~/Downloads/FP.min.anx")
-
 ```
@@
 ```{r}
+tmp_coeffs <- coef(lasso.model.1se.anx, s = "lambda.1se")
+Anx_coefs2 <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
+Anx_reg_coefs2 <- Anx_coefs[2:length(Anx_coefs)]
+Anx_reg_coefs2
 
@@
 
-FP_anx <- read_csv("~/Downloads/FP.min.anx")
+FP_anx <- read_csv("~/Downloads/FP.1se.anx")
 # FP_anx <- read_csv("~/Downloads/FP.1se.anx")
@@
 #Change the names of variables
-FP_anx$Variable = Anx_reg_coefs
+FP_anx$Variable = Anx_reg_coefs2
 
@@
 
-Anx_reg_coefs[1:10] <- c("Age","Some_College","Married", "White","Days_complete","Days_not_attended", "Anxiety_D", "Trauma_D","Other", "Substance_C")
-FP_anx$Variable = Anx_reg_coefs
+# Anx_reg_coefs[1:8] <- c("Days completed","Days not attended", "Co-Anxiety",         "Co-Substance",        "Post coping" ,     "Post pmh"     ,   
+# "Post functioning"   ,     "Post wellbeing" )
+# FP_anx$Variable = Anx_reg_coefs
 
@@
   coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
-                  xlim = c(.4,2)) +
+                  xlim = c(.5,1.5)) +
   #add a line at 1 for reference 

### 2024-04-29 Lasso_RCI_Response.Rmd
Fixed exclusion.

@@
   #!is.na(Anxiety_Responder),
-  CUXOS_pre >= 20,
   ) |>
@@
 Mothership_lasso_1 <- na.omit(Mothership_lasso)
+dim(Mothership_lasso_1)
 
@@
   filter(
-    !is.na(Some_College),
-    !is.na(Female),
-    !is.na(IPT_track_1),
-    !is.na(White),
     !is.na(CUXOS_pre),
@@
   )|>
+  mutate(
+    ID1  = as.integer(ID1),
+    pre  = as.numeric(CUXOS_pre),
+    post = as.numeric(CUXOS_post),
+  ) |>
+  select(
+    ID1,pre,post
+  ) |>
+  filter(!is.na(pre),
+         !is.na(post),
+         pre > 20)
+
+RCI_df_dep2 <- Mothership_lasso_1 |>
+  filter(
+    !is.na(CUDOS_pre),
+    !is.na(CUDOS_post),
+    CUDOS_pre > 20,
+  ) |>
   mutate(
@@
 
-RCI_df_dep2 <- Mothership_lasso_1 |>
-  filter(
-    !is.na(Some_College),
-    !is.na(Female),
-    !is.na(IPT_track_1),
-    !is.na(White),
-    !is.na(CUDOS_pre),
-    !is.na(CUDOS_post),
-    CUDOS_pre > 20,
-  ) |>
-  mutate(
-    ID1  = as.integer(ID1),
-    pre  = as.numeric(CUXOS_pre),
-    post = as.numeric(CUXOS_post),
-  ) |>
-  select(
-    ID1,pre,post
-  ) |>
-  filter(!is.na(pre),
-         !is.na(post),
-         pre > 20)
-
 RCI_df_dep2 <- data.frame(RCI_df_dep2)
@@
 
-head(ANX_JT_smol)
-
+view(ANX_JT_smol)
 view(DEP_JT_smol)
@@
     Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
-    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
+    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100
   )
@@
     )),
-    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, NA)),
+    # Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, NA)),
     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
@@
     )),
-    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, NA)),
+    # Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, NA)),
     Depression_Responder = as.factor(recode(Depression_Responder,
@@
 #     )
-```
-
-```{r}
-#############            AnxDep_PrePost                 ##################
-
-#7. create new DF with Varaibles we want
-
-AnxDep_PrePost <- data.frame(cbind(Mothership_post_joined$ID1,
-                                   Mothership_post_joined$Disorder_treat,
-                                   Mothership_post_joined$BL_CUDOS,
-                                   Mothership_post_joined$BL_CUXOS,
-                                   Mothership_post_joined$CUDOS_pre,
-                                   Mothership_post_joined$CUDOS_post,
-                                   Mothership_post_joined$CUXOS_pre,
-                                   Mothership_post_joined$CUXOS_post,
-                                   #Extra stuff?
-                                   Mothership_post_joined$Depression_Responder,
-                                   Mothership_post_joined$Anxiety_Responder
-                                   #Mothership_post$RESPONDER_FIGS
-)) #%>%
-
 ```
@@
 FP.1se.dep
+
+write_csv(FP.1se.dep, "~/Downloads/FP.1se.dep")
 ```
@@
       # predictors
-        Days_complete_1 + Days_not_attended_1 + Anxiety_C + Substance_C + 
+        Age_1 + Married + Days_complete_1 + Days_not_attended_1 + Anxiety_D + 
+        Substance_C + Trauma_D + Other + Mood_C + BPD_Co_C + Substance_C + 
+        CUXOS_pre + 
         rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
@@
 
-FP_anx <- read_csv("~/Downloads/FP.1se.anx")
+FP_anx <- read_csv("~/Downloads/FP.min.anx")
 # FP_anx <- read_csv("~/Downloads/FP.1se.anx")
@@
 #Change the names of variables
-FP_anx$Variable = Anx_reg_coefs2
+FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
+                    "Days Not Attended", "Anixety Disorder","Co-SUD", 
+                    "Trauma Disorder", "Other Disorder", "Co-Mood Disorder", 
+                    "Co-BPD", "CUXOS Pre", "Post Coping", 
+                    "Post PMH", "Post Functioning", "Post Wellbeing")
 
@@
   )
-FP_anx
-
-# Anx_reg_coefs[1:8] <- c("Days completed","Days not attended", "Co-Anxiety",         "Co-Substance",        "Post coping" ,     "Post pmh"     ,   
-# "Post functioning"   ,     "Post wellbeing" )
-# FP_anx$Variable = Anx_reg_coefs
-
-Anx_reg_coefs
-# FP_anx$Variable = c(                      
-#                     "Days Completed","Days Not Attended","Anxiety Disroder","CUXOS Pre-score",
-#                     "Coping Ability","Positive Mental Health", "Functioning"   
-#                     )
 
@@
                #                        1), # uncolored ones for insignificant varaibles
-             size=4,show.legend = FALSE) +
+             size=3.5,show.legend = FALSE) +
   geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
-  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
+  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.5, show.legend = FALSE)+
   scale_color_manual(values = c("darkgrey","red"))+
@@
   coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
-                  xlim = c(.5,1.5)) +
+                  xlim = c(.25,2.0)) +
   #add a line at 1 for reference 
@@
 
-FP_dep <- read_csv("~/Downloads/FP.min.dep")
+FP_dep <- read_csv("~/Downloads/FP.1se.dep")
 
 #rename the variables for the figure
-FP_dep$Variable = Dep_reg_coefs
-# FP_dep$Variable = c(
-#                      "Days Not Attended",
-#                     "CUDOS Pre-Score",
-#                     "Coping Ability", "Positive Mental Health", "Functioning",
-#                     "Sense of Well Being"
-#                     )
+
+FP_dep$Variable = c(
+                     "Days Not Attended",
+                    "Post Coping", 
+                    "Post PMH", "Post Functioning", "Post Wellbeing")
 

### 2024-05-11 Lasso_RCI_Response.Rmd
ACT Scores???

@@
 library(tidyr)
+library(fuzzySim) ## For FDR adjusted p values
+library(broom) # for tidy regression output
 ```
@@
 ```{r}
-Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
+Mothership1 <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
 #DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
-dim(Mothership)
+Mothership1
+
+list.files("~/Desktop/Coding/data/ACT_scores")
+# path = "~/Desktop/Coding/data/ACT_scores"
+# # 
+# length(dir(path))
+# for(i in dir(path))
+# {
+#   df_1 <- read_sav(paste0(path,"/",i))
+#   Mothership_mindful <- left_join(Mothership1,df_1, by = join_by(ID1 == ID1))
+# }
+
+df_1 <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
+Mothership1 <- left_join(Mothership1,df_1, by = join_by(ID1 == ID1))
+df_2 <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
+Mothership1 <- left_join(Mothership1,df_2, by = join_by(ID1 == ID1))
+df_3 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
+Mothership1 <- left_join(Mothership1,df_3, by = join_by(ID1 == ID1))
+df_4 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
+Mothership1 <- left_join(Mothership1,df_4, by = join_by(ID1 == ID1))
+df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
+Mothership1 <- left_join(Mothership1,df_5, by = join_by(ID1 == ID1))
+
+view(Mothership_mindful)
+```
+
+```{r}
+
 ```
@@
 Mothership_lasso_1 <- na.omit(Mothership_lasso)
-dim(Mothership_lasso_1)
 
@@
 ```{r}
-
+summary(as.factor(Mothership_post_joined$SCID_1))
 ```
@@
 ## install.packages("fuzzySim")
-library(fuzzySim) ## For FDR adjusted p values
-library(broom) # for tidy regression output
 
@@
 
-  # glm_min_dep <-
-  #           glm(
-  #     #Outcome varaible
-  #       Depression_Responder ~
-  #     # predictors
-  #       Age_1  +
-  #       Days_complete_1 + Days_not_attended_1 + Anxiety_D + 
-  #       BPD_Co_C + Current_Dx + CUXOS_pre+
-  #       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
-  #     #data
-  #       data = Vars_dep,
-  #     # type of regression : logistic = binary / binomial
-  #       family = "binomial",
-  #     )
-
-install.packages("rempsyc")
-library(rempsyc)
-nice_table(tidy.summary.min.dep)
+# install.packages("rempsyc")
+# library(rempsyc)
+# nice_table(tidy.summary.min.dep)
 
@@
       # predictors
-        Age_1 + Married + Days_complete_1 + Days_not_attended_1 + Anxiety_D + 
-        Substance_C + Trauma_D + Other + Mood_C + BPD_Co_C + Substance_C + 
-        CUXOS_pre + 
-        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+        Age_1 + Married + Days_complete_1 + 
+        Days_not_attended_1 + Anxiety_D + Trauma_D +
+        Other + Mood_C + BPD_Co_C + 
+        Substance_C + CUXOS_pre +  rdqPOST_coping + 
+        rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
    R2.min.anx
+
+#wald
+   library(aod)
+   wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:15)
+
 # df for Forrest plots
@@
 FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
-                    "Days Not Attended", "Anixety Disorder","Co-SUD", 
-                    "Trauma Disorder", "Other Disorder", "Co-Mood Disorder", 
-                    "Co-BPD", "CUXOS Pre", "Post Coping", 
+                    "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
+                    "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
+                    "Co-SUD", "CUXOS Pre", "Post Coping", 
                     "Post PMH", "Post Functioning", "Post Wellbeing")
@@
   #adjust the dimentions. 
-  coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1)) +
+  coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1),
+                  xlim = c(.5,1.5)) +
   #add a line at 1 for reference 

### 2024-05-13 Lasso_RCI_Response.Rmd
Act variables = insignificant models?

@@
 ```{r}
-Mothership1 <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
+Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
 #DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
-Mothership1
-
-list.files("~/Desktop/Coding/data/ACT_scores")
-# path = "~/Desktop/Coding/data/ACT_scores"
-# # 
-# length(dir(path))
-# for(i in dir(path))
-# {
-#   df_1 <- read_sav(paste0(path,"/",i))
-#   Mothership_mindful <- left_join(Mothership1,df_1, by = join_by(ID1 == ID1))
-# }
-
-df_1 <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
-Mothership1 <- left_join(Mothership1,df_1, by = join_by(ID1 == ID1))
-df_2 <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
-Mothership1 <- left_join(Mothership1,df_2, by = join_by(ID1 == ID1))
-df_3 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
-Mothership1 <- left_join(Mothership1,df_3, by = join_by(ID1 == ID1))
-df_4 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
-Mothership1 <- left_join(Mothership1,df_4, by = join_by(ID1 == ID1))
-df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
-Mothership1 <- left_join(Mothership1,df_5, by = join_by(ID1 == ID1))
-
-view(Mothership_mindful)
-```
-
-```{r}
-
+```
+
+```{r}
+
+AAQIIpre <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
+AAQIIpre <- AAQIIpre |>
+  mutate(
+    AAQIIpre = AAQIIpre_1_1 + AAQIIpre_2_1 + AAQIIpre_3_1 + AAQIIpre_4_1 + 
+      AAQIIpre_5_1 + AAQIIpre_6_1 + AAQIIpre_7_1
+  )
+Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))
+AAQII
+
+AAQIIpost <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
+AAQIIpost <- AAQIIpost |>
+  mutate(
+    AAQIIpost = AAQIIpost_1_1 + AAQIIpost_2_1 + AAQIIpost_3_1 + AAQIIpost_4_1 + 
+      AAQIIpost_5_1 + AAQIIpost_6_1 + AAQIIpost_7_1
+  )
+Mothership <- left_join(Mothership,AAQIIpost, by = join_by(ID1 == ID1))
+
+FMMQ_pre <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
+FMMQ_pre <- FMMQ_pre|>
+  mutate(
+    #reverse code items
+    FFMQpre_4R  = 6 - FFMQpre_4_1,
+    FFMQpre_5R  = 6 - FFMQpre_5_1,  
+    FFMQpre_7R  = 6 - FFMQpre_7_1, 
+    FFMQpre_8R  = 6 - FFMQpre_8_1, 
+    FFMQpre_11R = 6 - FFMQpre_11_1, 
+    FFMQpre_12R = 6 - FFMQpre_12_1,
+    FFMQpre_14R = 6 - FFMQpre_14_1,
+    FFMQpre_17R = 6 - FFMQpre_17_1,
+    FFMQpre_19R = 6 - FFMQpre_19_1,
+    FFMQpre_22R = 6 - FFMQpre_22_1,
+    FFMQpre_23R = 6 - FFMQpre_23_1,
+    FFMQpre_24R = 6 - FFMQpre_24_1,
+    #create scales
+    Desc_Ex_pre =
+        FFMQpre_1_1 + FFMQpre_2_1 + FFMQpre_5R + FFMQpre_11R + FFMQpre_16_1,
+    Non_react_pre = 
+        FFMQpre_3_1 + FFMQpre_9_1 + FFMQpre_13_1 + FFMQpre_18_1 + FFMQpre_21_1,
+    Observe_inner_pre = 
+        FFMQpre_6_1 + FFMQpre_10_1 + FFMQpre_15_1 + FFMQpre_20_1,
+    Self_compasion_pre = 
+        FFMQpre_4R + FFMQpre_7R + FFMQpre_14R + FFMQpre_19R + FFMQpre_24R,
+    Acting_mindful_pre = 
+        FFMQpre_8R + FFMQpre_12R + FFMQpre_17R + FFMQpre_22R + FFMQpre_23R,
+    FFMQ_pre_total = 
+        Desc_Ex_pre + Non_react_pre + Observe_inner_pre+ Self_compasion_pre + Acting_mindful_pre
+    )
+Mothership <- left_join(Mothership,FMMQ_pre, by = join_by(ID1 == ID1))
+
+FMMQ_post <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
+FMMQ_post <- FMMQ_post|>
+  mutate(
+    #reverse code items
+    FFMQpost_4R  = 6 - FFMQpost_4_1,
+    FFMQpost_5R  = 6 - FFMQpost_5_1,  
+    FFMQpost_7R  = 6 - FFMQpost_7_1, 
+    FFMQpost_8R  = 6 - FFMQpost_8_1, 
+    FFMQpost_11R = 6 - FFMQpost_11_1, 
+    FFMQpost_12R = 6 - FFMQpost_12_1,
+    FFMQpost_14R = 6 - FFMQpost_14_1,
+    FFMQpost_17R = 6 - FFMQpost_17_1,
+    FFMQpost_19R = 6 - FFMQpost_19_1,
+    FFMQpost_22R = 6 - FFMQpost_22_1,
+    FFMQpost_23R = 6 - FFMQpost_23_1,
+    FFMQpost_24R = 6 - FFMQpost_24_1,
+    #create scales
+    Desc_Ex_post =
+        FFMQpost_1_1 + FFMQpost_2_1 + FFMQpost_5R + FFMQpost_11R + FFMQpost_16_1,
+    Non_react_post = 
+        FFMQpost_3_1 + FFMQpost_9_1 + FFMQpost_13_1 + FFMQpost_18_1 + FFMQpost_21_1,
+    Observe_inner_post = 
+        FFMQpost_6_1 + FFMQpost_10_1 + FFMQpost_15_1 + FFMQpost_20_1,
+    Self_compasion_post = 
+        FFMQpost_4R + FFMQpost_7R + FFMQpost_14R + FFMQpost_19R + FFMQpost_24R,
+    Acting_mindful_post = 
+        FFMQpost_8R + FFMQpost_12R + FFMQpost_17R + FFMQpost_22R + FFMQpost_23R,
+    FFMQ_post_total = 
+        Desc_Ex_post + Non_react_post + Observe_inner_post + Self_compasion_post + Acting_mindful_post
+    )
+Mothership <- left_join(Mothership,FMMQ_post, by = join_by(ID1 == ID1))
+
+view(Mothership)
+# df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
 ```
@@
 ```{r}
+view(Mothership_post)
+```
+
+```{r}
 #Using JT citeria (recovered/improved/nonresponse/deteriorated)
@@
     CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
+    #ACT stuff
+    AAQIIpre, AAQIIpost, 
+    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
+    Acting_mindful_post, FFMQ_post_total, 
+    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    Acting_mindful_pre, FFMQ_post_total
   ))
 Mothership_lasso_1 <- na.omit(Mothership_lasso)
+
+dim(Mothership_lasso_1)
 
@@
     #For table 3 - RCI info
-    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
+    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
+        #ACT stuff
+    AAQIIpre, AAQIIpost, 
+    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
+    Acting_mindful_post, FFMQ_post_total, 
+    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    Acting_mindful_pre, FFMQ_post_total
   ))
@@
     #For table 3 - RCI info
-    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
+    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
+    #ACT stuff
+    AAQIIpre, AAQIIpost, 
+    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
+    Acting_mindful_post, FFMQ_post_total, 
+    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    Acting_mindful_pre, FFMQ_post_total
+
   ))
@@
     Age_1,Some_College:Married,White, 
-    # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, 
     # Disorders
@@
     Current_Dx,
-    # Pre-Post stuff
+# Pre variables
     CUDOS_pre,CUXOS_pre,
+    AAQIIpre,
+    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
+    Acting_mindful_pre,
+  #post stuff    
+     # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1,
     # RDQ
-    rdqPOST_coping:rdqPOST_wbs
+    # rdqPOST_coping:rdqPOST_wbs,
+    #ACT stuff
+
+    AAQIIpost,
+    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
+    Acting_mindful_post,
+
   ))
@@
 ```{r}
-# min model
+# # min model - old
+# glm_min_dep <-
+#           glm(
+#     #Outcome varaible
+#       Depression_Responder ~
+#     # predictors
+#       Age_1  + Some_College + Married + IPT_track_1 +
+#       Days_complete_1 + Days_not_attended_1 + Anxiety_D + Trauma_D +
+#       Trauma_C + Substance_C +
+#       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+#     #data
+#       data = Vars_dep,
+#     # type of regression : logistic = binary / binomial
+#       family = "binomial",
+#     )
+
+# # min model - pre
+# glm_min_dep <-
+#           glm(
+#     #Outcome varaible
+#       Depression_Responder ~
+#     # predictors
+#       White  +   Anxiety_C + BPD_Co_C+  Current_Dx + CUXOS_pre + 
+#       Self_compasion_pre,
+#     #data
+#       data = Vars_dep,
+#     # type of regression : logistic = binary / binomial
+#       family = "binomial",
+#     )
+
+# min model - pre/post
 glm_min_dep <-
@@
     # predictors
-      Age_1  + Some_College + Married + IPT_track_1 +
-      Days_complete_1 + Days_not_attended_1 + Anxiety_D + Trauma_D +
-      Trauma_C + Substance_C +
-      rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+      White  +  Days_not_attended_1 + Anxiety_C + Current_Dx + CUXOS_pre +
+      Non_react_post + AAQIIpost + Acting_mindful_post,
     #data
@@
 # install.packages("rempsyc")
-# library(rempsyc)
-# nice_table(tidy.summary.min.dep)
 
@@
   R2.min.dep
+
+  #wald
+   library(aod)
+   wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:7)
+
 # df for Forrest plots
@@
     # RDQ
-    rdqPOST_coping:rdqPOST_wbs
+    # rdqPOST_coping:rdqPOST_wbs,
+        #ACT stuff
+    AAQIIpre, AAQIIpost, 
+    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
+    Acting_mindful_post, 
+    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    Acting_mindful_pre
   ))
@@
       # predictors
-        Age_1 + Married + Days_complete_1 + 
-        Days_not_attended_1 + Anxiety_D + Trauma_D +
-        Other + Mood_C + BPD_Co_C + 
-        Substance_C + CUXOS_pre +  rdqPOST_coping + 
-        rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+        Female + Married + White + Days_not_attended_1 + 
+        Anxiety_D +  BPD_Co_C + CUXOS_pre +  
+        AAQIIpost + Non_react_post + Self_compasion_post + Acting_mindful_post,
       #data
@@
    library(aod)
-   wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:15)
+   wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:12)
 
@@
 #Change the names of variables
-FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
-                    "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
-                    "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
-                    "Co-SUD", "CUXOS Pre", "Post Coping", 
-                    "Post PMH", "Post Functioning", "Post Wellbeing")
+# FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
+#                     "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
+#                     "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
+#                     "Co-SUD", "CUXOS Pre", "Post Coping", 
+#                     "Post PMH", "Post Functioning", "Post Wellbeing")
 
@@
 
-FP_dep <- read_csv("~/Downloads/FP.1se.dep")
+FP_dep <- read_csv("~/Downloads/FP.min.dep")
 
@@
 
-FP_dep$Variable = c(
-                     "Days Not Attended",
-                    "Post Coping", 
-                    "Post PMH", "Post Functioning", "Post Wellbeing")
+# FP_dep$Variable = c(
+#                      "Days Not Attended",
+#                     "Post Coping", 
+#                     "Post PMH", "Post Functioning", "Post Wellbeing")
 

### 2024-05-21 Lasso_RCI_Response.Rmd
Mindfulness variables

@@
 Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))
-AAQII
 
@@
 
-view(Mothership)
 # df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
@@
     dummy = -99
-  ) |>
-  filter(!is.na(Disorder_treat),
-         !is.na(TxYear),
-         !is.na(Duration))
+  )
+  # filter(!is.na(Disorder_treat),
+  #        !is.na(TxYear),
+  #        !is.na(Duration))
 
@@
 )
-
+```
+
+```{r}
 # 4. RCI Analysis categorization ------------------------------------------
@@
 library(JTRCI)
-citation("JTRCI")
-
-# 
-# #devtools::install_github("zieglema/ClinicalSig")
-#1. Create df for RCI
-RCI_df_dep <- Mothership_post |>
-  mutate(
-    ID1  = as.integer(ID1),
-    pre  = as.numeric(CUDOS_pre),
-    post = as.numeric(CUDOS_post),
-  ) |>
-  select(
-    ID1,pre,post
-  ) |>
-  filter(!is.na(pre),
-         !is.na(post),
-         pre > 20)
-
-RCI_df_anx <- Mothership_post |>
-  mutate(
-    ID1  = as.integer(ID1),
-    pre  = as.numeric(CUXOS_pre),
-    post = as.numeric(CUXOS_post),
-  ) |>
-  select(
-    ID1,pre,post
-  ) |>
-  filter(!is.na(pre),
-         !is.na(post),
-         pre > 20)
-
-RCI_df_dep <- data.frame(RCI_df_dep)
-RCI_df_anx <- data.frame(RCI_df_anx)
-
-# https://awkruijt.netlify.app/plotposts/longitudinaljtrci
-
-RCI_df_anx1<-RCI_df_anx |>
-  select(ID1,pre,post)
-
-## Using RCI only (respond/nonrespond/deteriorated)
-DEP_RCI <- JTRCI (data = RCI_df_dep, 
-                  pre = "pre", 
-                  post = "post", 
-                  ppid = "ID1", 
-                  reliability = .74, 
-                  indextype = "RCI", 
-                  JTcrit = "auto",
-                  plottitle = "JT indices for anxiety")
-
-ANX_RCI <- JTRCI (data = RCI_df_anx, 
-                  pre = "pre", 
-                  post = "post", 
-                  ppid = "ID1", 
-                  reliability = .74, 
-                  indextype = "RCI", 
-                  #JTcrit = "auto",
-                  plottitle = "JT indices for depression")
-RCI_DF<- ANX_RCI$data
-colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")
-
-RCI_DF2<- DEP_RCI$data
-colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")
-
-RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
-colnames(RCI_DF)[1] = "ID1"
-
-head(RCI_DF)
-```
-
-```{r}
-view(Mothership_post)
+
+# # 
+# # #devtools::install_github("zieglema/ClinicalSig")
+# #1. Create df for RCI
+# RCI_df_dep <- Mothership_post |>
+#   mutate(
+#     ID1  = as.integer(ID1),
+#     pre  = as.numeric(CUDOS_pre),
+#     post = as.numeric(CUDOS_post),
+#   ) |>
+#   select(
+#     ID1,pre,post
+#   ) |>
+#   filter(!is.na(pre),
+#          !is.na(post),
+#          pre > 20)
+# 
+# RCI_df_anx <- Mothership_post |>
+#   mutate(
+#     ID1  = as.integer(ID1),
+#     pre  = as.numeric(CUXOS_pre),
+#     post = as.numeric(CUXOS_post),
+#   ) |>
+#   select(
+#     ID1,pre,post
+#   ) |>
+#   filter(!is.na(pre),
+#          !is.na(post),
+#          pre > 20)
+# 
+# 
+# RCI_df_dep <- data.frame(RCI_df_dep)
+# RCI_df_anx <- data.frame(RCI_df_anx)
+# 
+# # https://awkruijt.netlify.app/plotposts/longitudinaljtrci
+# 
+# RCI_df_anx1<-RCI_df_anx |>
+#   select(ID1,pre,post)
+# 
+# ## Using RCI only (respond/nonrespond/deteriorated)
+# DEP_RCI <- JTRCI (data = RCI_df_dep, 
+#                   pre = "pre", 
+#                   post = "post", 
+#                   ppid = "ID1", 
+#                   reliability = .74, 
+#                   indextype = "RCI", 
+#                   JTcrit = "auto",
+#                   plottitle = "JT indices for anxiety")
+# 
+# ANX_RCI <- JTRCI (data = RCI_df_anx, 
+#                   pre = "pre", 
+#                   post = "post", 
+#                   ppid = "ID1", 
+#                   reliability = .74, 
+#                   indextype = "RCI", 
+#                   #JTcrit = "auto",
+#                   plottitle = "JT indices for depression")
+# RCI_DF<- ANX_RCI$data
+# colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")
+# 
+# RCI_DF2<- DEP_RCI$data
+# colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")
+# 
+# RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
+# colnames(RCI_DF)[1] = "ID1"
+# 
+# head(RCI_DF)
 ```
@@
 #Using JT citeria (recovered/improved/nonresponse/deteriorated)
-
-#1. JT classification for depression
-JTRCI (data = RCI_df_dep, 
-                  pre = "pre", 
-                  post = "post", 
-                  ppid = "ID1", 
-                  reliability = .74, 
-                  indextype = "JT", 
-                  JTcrit = "auto",
-                  plottitle = "JT indices for anxiety")
-
-DEP_JT <- JTRCIdf
-colnames(DEP_JT) <- paste0(colnames(DEP_JT),"_dep")
-head(DEP_JT)
-
-#2. JT classification for anxiety
-JTRCI (data = RCI_df_anx, 
-                  pre = "pre", 
-                  post = "post", 
-                  ppid = "ID1", 
-                  reliability = .74, 
-                  indextype = "JT", 
-                  #JTcrit = "auto",
-                  plottitle = "JT indices for depression")
-
-ANX_JT<- JTRCIdf
-
-#3. Make combined JT table for anxiety and depression
-
-# JT_DF<- ANX_JT
-
-colnames(ANX_JT) <- paste0(colnames(ANX_JT),"_anx")
-
-# 
-# JT_DF2<- DEP_JT
-
-# 
-# JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
-# colnames(JT_DF)[1] = "ID1"
-
-head(ANX_JT)
+# 
+# #1. JT classification for depression
+# JTRCI (data = RCI_df_dep, 
+#                   pre = "pre", 
+#                   post = "post", 
+#                   ppid = "ID1", 
+#                   reliability = .74, 
+#                   indextype = "JT", 
+#                   JTcrit = "auto",
+#                   plottitle = "JT indices for anxiety")
+# 
+# DEP_JT <- JTRCIdf
+# colnames(DEP_JT) <- paste0(colnames(DEP_JT),"_dep")
+# head(DEP_JT)
+# 
+# #2. JT classification for anxiety
+# JTRCI (data = RCI_df_anx, 
+#                   pre = "pre", 
+#                   post = "post", 
+#                   ppid = "ID1", 
+#                   reliability = .74, 
+#                   indextype = "JT", 
+#                   #JTcrit = "auto",
+#                   plottitle = "JT indices for depression")
+# 
+# ANX_JT<- JTRCIdf
+# 
+# #3. Make combined JT table for anxiety and depression
+# 
+# # JT_DF<- ANX_JT
+# 
+# colnames(ANX_JT) <- paste0(colnames(ANX_JT),"_anx")
+# 
+# # 
+# # JT_DF2<- DEP_JT
+# 
+# # 
+# # JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
+# # colnames(JT_DF)[1] = "ID1"
+# 
+# head(ANX_JT)
 ```
@@
     # RDQ
-    rdqPOST_coping:rdqPOST_wbs,
+    # rdqPRE_coping:rdqPRE_wbs,
     #For table 3 - RCI info
@@
     #ACT stuff
-    AAQIIpre, AAQIIpost, 
+    # AAQIIpre, AAQIIpost,
+    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
+    # Acting_mindful_pre,
     Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post, FFMQ_post_total, 
-    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    Acting_mindful_pre, FFMQ_post_total
+    Acting_mindful_post,
   ))
+
 Mothership_lasso_1 <- na.omit(Mothership_lasso)
@@
 
+```
+
+```{r}
 RCI_df_anx2 <- Mothership_lasso_1 |>
@@
 colnames(ANX_JT_smol) <- paste0(colnames(ANX_JT_smol),"_anx")
-
-view(ANX_JT_smol)
-view(DEP_JT_smol)
 ```
@@
 
-Mothership_post <- Mothership_post |>
-  #1. Filter out scores for people not in the program / don't have data
-  filter(!is.na(Days_complete_1)) |>
-  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
-  filter(!is.na(CUXOS_pre),
-         !is.na(CUXOS_post),
-         CUXOS_pre > 0,
-         CUXOS_post >= 0,
-         !is.na(CUDOS_pre),
-         !is.na(CUDOS_post),
-         CUDOS_pre > 0,
-         CUDOS_post> 0
-         ) |>
-  mutate(
-    Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
-    Delta_Dep_DC = CUDOS_post - CUDOS_pre,
-    Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
-    Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100
-  )
+# Mothership_post <- Mothership_post |>
+#   #1. Filter out scores for people not in the program / don't have data
+#   filter(!is.na(Days_complete_1)) |>
+#   #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
+#   filter(!is.na(CUXOS_pre),
+#          !is.na(CUXOS_post),
+#          CUXOS_pre > 0,
+#          CUXOS_post >= 0,
+#          !is.na(CUDOS_pre),
+#          !is.na(CUDOS_post),
+#          CUDOS_pre > 0,
+#          CUDOS_post>= 0
+#          ) |>
+#   mutate(
+#     Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
+#     Delta_Dep_DC = CUDOS_post - CUDOS_pre,
+#     Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
+#     Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100
+#   )
+```
+
+```{r}
 #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
@@
 ```{r}
-summary(as.factor(Mothership_post_joined$SCID_1))
+# summary(as.factor(Mothership_post_joined$SCID_1))
 ```
@@
     # RDQ
-    rdqPOST_coping:rdqPOST_wbs,
+    rdqPOST_coping:rdqPOST_wbs,rdqPRE_coping:rdqPRE_wbs,
     #For table 3 - RCI info
@@
     Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post, FFMQ_post_total, 
+    Acting_mindful_post, 
     Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    Acting_mindful_pre, FFMQ_post_total
+    Acting_mindful_pre,
 
@@
 
+T tests
 ```{r}
@@
     # Demographics
-    Age_1,Some_College:Married,White, 
+    Age_1,Some_College:Married,White, #Discharge,
+    # Treatment info
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
     # Disorders
-    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, #Psychotic_D,  
-    Other,
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
     Current_Dx,
-# Pre variables
-    CUDOS_pre,CUXOS_pre,
-    AAQIIpre,
-    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
-    Acting_mindful_pre,
-  #post stuff    
-     # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1,
+    # Pre-Post stuff
+    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
     # RDQ
-    # rdqPOST_coping:rdqPOST_wbs,
+    #rdqPRE_coping:rdqPRE_wbs,
+    #For table 3 - RCI info
+    CUXOS_pre,CUDOS_pre, 
     #ACT stuff
-
-    AAQIIpost,
+    # AAQIIpre, AAQIIpost,
+    #  Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    # Acting_mindful_pre, 
     Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
     Acting_mindful_post,
-
   ))
-
-# old model
-# Anxiety_D, Mood_D, BPD_P,    Trauma_D,  Other,
-#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
-#     Current_Dx,
 
@@
 
+#####  CHECK THIS OUT?????????
+
 # Make predictions on the test data
 x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
-probabilities <- model.min %>% predict(newx = x.test)
+probabilities <- model.min %>% predict(newx = x.test,"response")
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 #Using lambda.min as the best lambda, gives the following regression coefficients:
-coef(cv.lasso.dep, cv.lasso.dep$lambda.min)
+#coef(cv.lasso.dep, cv.lasso.dep$lambda.min)
 
 #Using lambda.1se as the best lambda, gives the following regression coefficients:
-coef(cv.lasso.dep, cv.lasso.dep$lambda.1se)
+#coef(cv.lasso.dep, cv.lasso.dep$lambda.1se)
 ```
@@
 x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
-probabilities <- lasso.model.min.dep %>% predict(newx = x.test)
+probabilities <- lasso.model.min.dep %>% predict(newx = x.test,type ="response")
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
-probabilities <- lasso.model.1se.dep %>% predict(newx = x.test)
+probabilities <- lasso.model.1se.dep %>% predict(newx = x.test,type ="response")
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 
-# # min model - pre
+# min model - post AAQII no Mindful stuff
+glm_min_dep <-
+          glm(
+    #Outcome varaible
+      Depression_Responder ~
+    # predictors
+Days_not_attended_1 + Anxiety_C + BPD_Co_C + Current_Dx + 
+  CUXOS_pre +  Non_react_post + 
+  Self_compasion_post + Acting_mindful_post,
+    #data
+      data = Vars_dep,
+    # type of regression : logistic = binary / binomial
+      family = "binomial",
+    )
+
+# min model - pre/post
 # glm_min_dep <-
@@
 #     # predictors
-#       White  +   Anxiety_C + BPD_Co_C+  Current_Dx + CUXOS_pre + 
-#       Self_compasion_pre,
+#       White  +  Days_not_attended_1 + Anxiety_C + Current_Dx + CUXOS_pre +
+#       Non_react_post + AAQIIpost + Acting_mindful_post,
 #     #data
@@
 
-# min model - pre/post
-glm_min_dep <-
-          glm(
-    #Outcome varaible
-      Depression_Responder ~
-    # predictors
-      White  +  Days_not_attended_1 + Anxiety_C + Current_Dx + CUXOS_pre +
-      Non_react_post + AAQIIpost + Acting_mindful_post,
-    #data
-      data = Vars_dep,
-    # type of regression : logistic = binary / binomial
-      family = "binomial",
-    )
-
 # install.packages("rempsyc")
@@
    library(aod)
-   wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:7)
+   # wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:13)
 
@@
     # Demographics
-    Age_1,Some_College:Married,White, 
+    Age_1,Some_College:Married,White, #Discharge,
     # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, 
+    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
     # Disorders
@@
     # RDQ
-    # rdqPOST_coping:rdqPOST_wbs,
+    #rdqPRE_coping:rdqPRE_wbs,
+    #For table 3 - RCI info
+    CUXOS_pre,CUDOS_pre, 
     #ACT stuff
-    AAQIIpre, AAQIIpost, 
     Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
     Acting_mindful_post,
-    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    Acting_mindful_pre
   ))
@@
 x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
-probabilities <- model %>% predict(newx = x.test)
+probabilities <- model %>% predict(newx = x.test,type = "response")
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 #Using lambda.min as the best lambda, gives the following regression coefficients:
-coef(cv.lasso.anx, cv.lasso.anx$lambda.min)
+#coef(cv.lasso.anx, cv.lasso.anx$lambda.min)
 
 #Using lambda.1se as the best lambda, gives the following regression coefficients:
-coef(cv.lasso.anx, cv.lasso.anx$lambda.1se)
+#coef(cv.lasso.anx, cv.lasso.anx$lambda.1se)
 ```
@@
 x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
-probabilities <- lasso.model.min.anx %>% predict(newx = x.test)
+probabilities <- lasso.model.min.anx %>% predict(newx = x.test,)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 Anx_reg_coefs
-
+```
+
+```{r}
 ## min model
@@
       # predictors
-        Female + Married + White + Days_not_attended_1 + 
-        Anxiety_D +  BPD_Co_C + CUXOS_pre +  
-        AAQIIpost + Non_react_post + Self_compasion_post + Acting_mindful_post,
+        Age_1 + Some_College + Female + Married + White + Days_not_attended_1 + 
+        BPD_Co_C + CUXOS_pre +  
+        Non_react_post+  Self_compasion_post + Acting_mindful_post,
       #data
@@
   summary.min.anx      <- summary(glm_min_anx)
+  summary.min.anx
 
@@
   )
-
+```
+
+```{r}
 FP_anx_m <- FP_anx |>
@@
   coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
-                  xlim = c(.25,2.0)) +
+                  xlim = c(.25,3.0)) +
   #add a line at 1 for reference 
@@
 layout <- c(
-  patchwork::area(t = 0, l = 0, b = 30, r = 30),
-  patchwork::area(t = 0, l = 16, b = 30, r = 25),
-  patchwork::area(t = 0, l = 22, b = 30, r = 30) 
+  patchwork::area(t = 0, l = 0, b = 30, r = 35),
+  patchwork::area(t = 0, l = 19, b = 30, r = 30),
+  patchwork::area(t = 0, l = 30, b = 30, r = 40) 
   )
@@
   coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1),
-                  xlim = c(.5,1.5)) +
+                  xlim = c(.5,2.0)) +
   #add a line at 1 for reference 

### 2024-05-21 Lasso_RCI_Response.Rmd
Pre scores only

@@
                        )))
-
+```
+
+```{r}
 #Extract Year From Intake Date
@@
       )
-
+summary(as.factor(Mothership$Prev_AdmitID_1))
+view(Mothership)
+```
+
+```{r}
 ##### df for plots
@@
 )
+
 ```
@@
 ```{r}
-
+Mothership_Missing <- Mothership_post |>
+  select(
+    ID1, 
+    # RDQ
+    rdqPRE_coping:rdqPRE_wbs,
+    rdqPOST_coping:rdqPOST_wbs,
+    #For table 3 - RCI info
+    CUXOS_pre, CUXOS_post,CUDOS_pre, CUDOS_post, 
+    #ACT stuff
+    AAQIIpre,AAQIIpost,
+    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    Acting_mindful_pre, 
+    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post, 
+    Acting_mindful_post 
+  )
+
+#install.packages('naniar')
+library(naniar)
+vis_miss(Mothership_Missing)
+```
+
+```{r}
 Mothership_lasso <- Mothership_post |>
@@
     # RDQ
-    # rdqPRE_coping:rdqPRE_wbs,
+    rdqPRE_coping:rdqPRE_wbs,
     #For table 3 - RCI info
@@
     #ACT stuff
-    # AAQIIpre, AAQIIpost,
-    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
-    # Acting_mindful_pre,
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post,
+    AAQIIpre, #AAQIIpost,
+    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
+    Acting_mindful_pre,
+    # Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
+    # Acting_mindful_post,
   ))
@@
 ```{r}
+library(JTRCI)
 RCI_df_anx2 <- Mothership_lasso_1 |>
@@
     # RDQ
-    rdqPOST_coping:rdqPOST_wbs,rdqPRE_coping:rdqPRE_wbs,
+    rdqPRE_coping:rdqPRE_wbs,
     #For table 3 - RCI info
@@
     #ACT stuff
-    AAQIIpre, AAQIIpost, 
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post, FFMQ_post_total, 
+    AAQIIpre,
     Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    Acting_mindful_pre, FFMQ_post_total
+    Acting_mindful_pre, 
   ))
+
 Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)
 
+dim(Mothership_lasso_anx)
 ### depression
@@
     #ACT stuff
-    AAQIIpre, AAQIIpost, 
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post, 
+    AAQIIpre,
     Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
@@
 Mothership_lasso_dep <- Mothership_lasso_dep[,-1]
+
 ```
@@
 
-```{r}
-
-```
-
 ataset visualizatoin
@@
     # RDQ
-    #rdqPRE_coping:rdqPRE_wbs,
+    rdqPRE_coping:rdqPRE_wbs,
     #For table 3 - RCI info
@@
     #ACT stuff
-    # AAQIIpre, AAQIIpost,
-    #  Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    # Acting_mindful_pre, 
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post,
+    AAQIIpre,
+    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    Acting_mindful_pre,
+
   ))
@@
 Vars_dep <- na.omit(Vars_dep)
+dim(Vars_dep)
 ```
@@
 
-tmp_coeffs <- coef(lasso.model.min.dep, s = "lambda.min")
+tmp_coeffs <- coef(lasso.model.1se.dep, s = "lambda.1se")
 Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
@@
 
+Vars_dep <- Vars_dep |>
+  mutate(
+    YA_Treatment = as.factor(ifelse(IPT_track_1 == "Young Adult",1,0)),
+    Trauma_Treatment = as.factor(ifelse(IPT_track_1 == "Trauma",1,0))
+  )
+
 # min model - post AAQII no Mindful stuff
@@
     # predictors
-Days_not_attended_1 + Anxiety_C + BPD_Co_C + Current_Dx + 
-  CUXOS_pre +  Non_react_post + 
-  Self_compasion_post + Acting_mindful_post,
+      Some_College + Female + White + YA_Treatment + Trauma_Treatment + Days_complete_1 + 
+      Days_not_attended_1 + Anxiety_D + BPD_P+ Trauma_D+Other+ Anxiety_C + Mood_C+ 
+      BPD_Co_C + Substance_C + No_Co + Current_Dx + CUXOS_pre + rdqPRE_coping + 
+      rdqPRE_pmh + rdqPRE_func + AAQIIpre + Self_compasion_pre,
     #data
@@
    library(aod)
-   # wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:13)
+   wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:24)
 
@@
 ```{r}
-
 Vars_anx <- Mothership_lasso_anx |>
@@
     #ACT stuff
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post,
+    AAQIIpre,
+    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    Acting_mindful_pre, 
   ))
@@
 x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
-probabilities <- lasso.model.min.anx %>% predict(newx = x.test,)
+probabilities <- lasso.model.min.anx %>% predict(newx = x.test,type="response")
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
-probabilities <- lasso.model.1se.anx %>% predict(newx = x.test)
+probabilities <- lasso.model.1se.anx %>% predict(newx = x.test,type="response")
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 ## min model
+
+Vars_anx <- Vars_anx |>
+  mutate(
+    YA_Treatment = as.factor(ifelse(IPT_track_1 == "Young Adult",1,0)),
+    Trauma_Treatment = as.factor(ifelse(IPT_track_1 == "Trauma",1,0))
+  )
+
   glm_min_anx <-  
@@
       # predictors
-        Age_1 + Some_College + Female + Married + White + Days_not_attended_1 + 
-        BPD_Co_C + CUXOS_pre +  
-        Non_react_post+  Self_compasion_post + Acting_mindful_post,
+        Age_1 + Female + Married + White + YA_Treatment + Trauma_Treatment + 
+        Days_complete_1 + Days_not_attended_1 + Anxiety_D + Mood_C + Trauma_C + 
+        Substance_C + Current_Dx + CUDOS_pre + rdqPRE_coping + rdqPRE_func + 
+        AAQIIpre + Non_react_pre + Self_compasion_pre,
       #data
@@
    library(aod)
-   wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:12)
+   wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:20)
 
@@
   )
-```
-
-```{r}
+
 FP_anx_m <- FP_anx |>
@@
   coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
-                  xlim = c(.25,3.0)) +
+                  xlim = c(.25,2.5)) +
   #add a line at 1 for reference 
@@
   patchwork::area(t = 0, l = 0, b = 30, r = 35),
-  patchwork::area(t = 0, l = 19, b = 30, r = 30),
+  patchwork::area(t = 0, l = 19, b = 30, r = 34),
   patchwork::area(t = 0, l = 30, b = 30, r = 40) 
@@
 FP_dep_m <- FP_dep |>
-  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
+  ggplot(aes(y = reorder(Variable, -order), color =as.factor(sig))) +
   #take away background
@@
   coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1),
-                  xlim = c(.5,2.0)) +
+                  xlim = c(.25,3.0)) +
   #add a line at 1 for reference 
@@
   #add anotations to help suggests what each side means.
-  annotate("text", x = .75, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
-  annotate("text", x = 1.25, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
+  annotate("text", x = .5, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
+  annotate("text", x = 1.5, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
   #Git rid of the Y - Axis

### 2024-06-25 Lasso_RCI_Response.Rmd
Updated results,tables,figures

@@
 Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
+
 #DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
@@
 ```{r}
-
-AAQIIpre <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
-AAQIIpre <- AAQIIpre |>
-  mutate(
-    AAQIIpre = AAQIIpre_1_1 + AAQIIpre_2_1 + AAQIIpre_3_1 + AAQIIpre_4_1 + 
-      AAQIIpre_5_1 + AAQIIpre_6_1 + AAQIIpre_7_1
-  )
-Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))
-
-AAQIIpost <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
-AAQIIpost <- AAQIIpost |>
-  mutate(
-    AAQIIpost = AAQIIpost_1_1 + AAQIIpost_2_1 + AAQIIpost_3_1 + AAQIIpost_4_1 + 
-      AAQIIpost_5_1 + AAQIIpost_6_1 + AAQIIpost_7_1
-  )
-Mothership <- left_join(Mothership,AAQIIpost, by = join_by(ID1 == ID1))
-
-FMMQ_pre <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
-FMMQ_pre <- FMMQ_pre|>
-  mutate(
-    #reverse code items
-    FFMQpre_4R  = 6 - FFMQpre_4_1,
-    FFMQpre_5R  = 6 - FFMQpre_5_1,  
-    FFMQpre_7R  = 6 - FFMQpre_7_1, 
-    FFMQpre_8R  = 6 - FFMQpre_8_1, 
-    FFMQpre_11R = 6 - FFMQpre_11_1, 
-    FFMQpre_12R = 6 - FFMQpre_12_1,
-    FFMQpre_14R = 6 - FFMQpre_14_1,
-    FFMQpre_17R = 6 - FFMQpre_17_1,
-    FFMQpre_19R = 6 - FFMQpre_19_1,
-    FFMQpre_22R = 6 - FFMQpre_22_1,
-    FFMQpre_23R = 6 - FFMQpre_23_1,
-    FFMQpre_24R = 6 - FFMQpre_24_1,
-    #create scales
-    Desc_Ex_pre =
-        FFMQpre_1_1 + FFMQpre_2_1 + FFMQpre_5R + FFMQpre_11R + FFMQpre_16_1,
-    Non_react_pre = 
-        FFMQpre_3_1 + FFMQpre_9_1 + FFMQpre_13_1 + FFMQpre_18_1 + FFMQpre_21_1,
-    Observe_inner_pre = 
-        FFMQpre_6_1 + FFMQpre_10_1 + FFMQpre_15_1 + FFMQpre_20_1,
-    Self_compasion_pre = 
-        FFMQpre_4R + FFMQpre_7R + FFMQpre_14R + FFMQpre_19R + FFMQpre_24R,
-    Acting_mindful_pre = 
-        FFMQpre_8R + FFMQpre_12R + FFMQpre_17R + FFMQpre_22R + FFMQpre_23R,
-    FFMQ_pre_total = 
-        Desc_Ex_pre + Non_react_pre + Observe_inner_pre+ Self_compasion_pre + Acting_mindful_pre
-    )
-Mothership <- left_join(Mothership,FMMQ_pre, by = join_by(ID1 == ID1))
-
-FMMQ_post <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
-FMMQ_post <- FMMQ_post|>
-  mutate(
-    #reverse code items
-    FFMQpost_4R  = 6 - FFMQpost_4_1,
-    FFMQpost_5R  = 6 - FFMQpost_5_1,  
-    FFMQpost_7R  = 6 - FFMQpost_7_1, 
-    FFMQpost_8R  = 6 - FFMQpost_8_1, 
-    FFMQpost_11R = 6 - FFMQpost_11_1, 
-    FFMQpost_12R = 6 - FFMQpost_12_1,
-    FFMQpost_14R = 6 - FFMQpost_14_1,
-    FFMQpost_17R = 6 - FFMQpost_17_1,
-    FFMQpost_19R = 6 - FFMQpost_19_1,
-    FFMQpost_22R = 6 - FFMQpost_22_1,
-    FFMQpost_23R = 6 - FFMQpost_23_1,
-    FFMQpost_24R = 6 - FFMQpost_24_1,
-    #create scales
-    Desc_Ex_post =
-        FFMQpost_1_1 + FFMQpost_2_1 + FFMQpost_5R + FFMQpost_11R + FFMQpost_16_1,
-    Non_react_post = 
-        FFMQpost_3_1 + FFMQpost_9_1 + FFMQpost_13_1 + FFMQpost_18_1 + FFMQpost_21_1,
-    Observe_inner_post = 
-        FFMQpost_6_1 + FFMQpost_10_1 + FFMQpost_15_1 + FFMQpost_20_1,
-    Self_compasion_post = 
-        FFMQpost_4R + FFMQpost_7R + FFMQpost_14R + FFMQpost_19R + FFMQpost_24R,
-    Acting_mindful_post = 
-        FFMQpost_8R + FFMQpost_12R + FFMQpost_17R + FFMQpost_22R + FFMQpost_23R,
-    FFMQ_post_total = 
-        Desc_Ex_post + Non_react_post + Observe_inner_post + Self_compasion_post + Acting_mindful_post
-    )
-Mothership <- left_join(Mothership,FMMQ_post, by = join_by(ID1 == ID1))
+# AAQIIpre <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
+# AAQIIpre <- AAQIIpre |>
+#   mutate(
+#     AAQIIpre = AAQIIpre_1_1 + AAQIIpre_2_1 + AAQIIpre_3_1 + AAQIIpre_4_1 + 
+#       AAQIIpre_5_1 + AAQIIpre_6_1 + AAQIIpre_7_1
+#   )
+# Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))
+# 
+# AAQIIpost <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
+# AAQIIpost <- AAQIIpost |>
+#   mutate(
+#     AAQIIpost = AAQIIpost_1_1 + AAQIIpost_2_1 + AAQIIpost_3_1 + AAQIIpost_4_1 + 
+#       AAQIIpost_5_1 + AAQIIpost_6_1 + AAQIIpost_7_1
+#   )
+# Mothership <- left_join(Mothership,AAQIIpost, by = join_by(ID1 == ID1))
+# 
+# FMMQ_pre <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
+# FMMQ_pre <- FMMQ_pre|>
+#   mutate(
+#     #reverse code items
+#     FFMQpre_4R  = 6 - FFMQpre_4_1,
+#     FFMQpre_5R  = 6 - FFMQpre_5_1,  
+#     FFMQpre_7R  = 6 - FFMQpre_7_1, 
+#     FFMQpre_8R  = 6 - FFMQpre_8_1, 
+#     FFMQpre_11R = 6 - FFMQpre_11_1, 
+#     FFMQpre_12R = 6 - FFMQpre_12_1,
+#     FFMQpre_14R = 6 - FFMQpre_14_1,
+#     FFMQpre_17R = 6 - FFMQpre_17_1,
+#     FFMQpre_19R = 6 - FFMQpre_19_1,
+#     FFMQpre_22R = 6 - FFMQpre_22_1,
+#     FFMQpre_23R = 6 - FFMQpre_23_1,
+#     FFMQpre_24R = 6 - FFMQpre_24_1,
+#     #create scales
+#     Desc_Ex_pre =
+#         FFMQpre_1_1 + FFMQpre_2_1 + FFMQpre_5R + FFMQpre_11R + FFMQpre_16_1,
+#     Non_react_pre = 
+#         FFMQpre_3_1 + FFMQpre_9_1 + FFMQpre_13_1 + FFMQpre_18_1 + FFMQpre_21_1,
+#     Observe_inner_pre = 
+#         FFMQpre_6_1 + FFMQpre_10_1 + FFMQpre_15_1 + FFMQpre_20_1,
+#     Self_compasion_pre = 
+#         FFMQpre_4R + FFMQpre_7R + FFMQpre_14R + FFMQpre_19R + FFMQpre_24R,
+#     Acting_mindful_pre = 
+#         FFMQpre_8R + FFMQpre_12R + FFMQpre_17R + FFMQpre_22R + FFMQpre_23R,
+#     FFMQ_pre_total = 
+#         Desc_Ex_pre + Non_react_pre + Observe_inner_pre+ Self_compasion_pre + Acting_mindful_pre
+#     )
+# Mothership <- left_join(Mothership,FMMQ_pre, by = join_by(ID1 == ID1))
+# 
+# FMMQ_post <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
+# FMMQ_post <- FMMQ_post|>
+#   mutate(
+#     #reverse code items
+#     FFMQpost_4R  = 6 - FFMQpost_4_1,
+#     FFMQpost_5R  = 6 - FFMQpost_5_1,  
+#     FFMQpost_7R  = 6 - FFMQpost_7_1, 
+#     FFMQpost_8R  = 6 - FFMQpost_8_1, 
+#     FFMQpost_11R = 6 - FFMQpost_11_1, 
+#     FFMQpost_12R = 6 - FFMQpost_12_1,
+#     FFMQpost_14R = 6 - FFMQpost_14_1,
+#     FFMQpost_17R = 6 - FFMQpost_17_1,
+#     FFMQpost_19R = 6 - FFMQpost_19_1,
+#     FFMQpost_22R = 6 - FFMQpost_22_1,
+#     FFMQpost_23R = 6 - FFMQpost_23_1,
+#     FFMQpost_24R = 6 - FFMQpost_24_1,
+#     #create scales
+#     Desc_Ex_post =
+#         FFMQpost_1_1 + FFMQpost_2_1 + FFMQpost_5R + FFMQpost_11R + FFMQpost_16_1,
+#     Non_react_post = 
+#         FFMQpost_3_1 + FFMQpost_9_1 + FFMQpost_13_1 + FFMQpost_18_1 + FFMQpost_21_1,
+#     Observe_inner_post = 
+#         FFMQpost_6_1 + FFMQpost_10_1 + FFMQpost_15_1 + FFMQpost_20_1,
+#     Self_compasion_post = 
+#         FFMQpost_4R + FFMQpost_7R + FFMQpost_14R + FFMQpost_19R + FFMQpost_24R,
+#     Acting_mindful_post = 
+#         FFMQpost_8R + FFMQpost_12R + FFMQpost_17R + FFMQpost_22R + FFMQpost_23R,
+#     FFMQ_post_total = 
+#         Desc_Ex_post + Non_react_post + Observe_inner_post + Self_compasion_post + Acting_mindful_post
+#     )
+# Mothership <- left_join(Mothership,FMMQ_post, by = join_by(ID1 == ID1))
 
@@
       )
-summary(as.factor(Mothership$Prev_AdmitID_1))
-view(Mothership)
 ```
@@
                                                        ifelse(is.na(BL_CUXOS), NA, "Subclinical"
-                                                       ))))))
+                                                       )))))),
+      Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
+      Delta_Dep_DC = CUDOS_post - CUDOS_pre
 )
@@
     # RDQ
-    rdqPRE_coping:rdqPRE_wbs,
+    # rdqPRE_coping:rdqPRE_wbs,
     rdqPOST_coping:rdqPOST_wbs,
@@
     #ACT stuff
-    AAQIIpre,AAQIIpost,
-    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    Acting_mindful_pre, 
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post, 
-    Acting_mindful_post 
+    # AAQIIpre,AAQIIpost,
+    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    # Acting_mindful_pre, 
+    # Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post, 
+    # Acting_mindful_post 
   )
@@
     # RDQ
-    rdqPRE_coping:rdqPRE_wbs,
+    rdqPOST_coping:rdqPOST_wbs,
     #For table 3 - RCI info
     CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
-    #ACT stuff
-    AAQIIpre, #AAQIIpost,
-    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
-    Acting_mindful_pre,
+    # #ACT stuff
+    # AAQIIpre, #AAQIIpost,
+    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
+    # Acting_mindful_pre,
     # Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
@@
 #   mutate(
-#     Delta_Anx_DC =  CUXOS_post - CUXOS_pre,
-#     Delta_Dep_DC = CUDOS_post - CUDOS_pre,
+
 #     Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
@@
     # RDQ
-    rdqPRE_coping:rdqPRE_wbs,
+    rdqPOST_coping:rdqPOST_wbs,
     #For table 3 - RCI info
     CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
-    #ACT stuff
-    AAQIIpre,
-    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    Acting_mindful_pre, 
+    # #ACT stuff
+    # AAQIIpre,
+    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    # Acting_mindful_pre, 
   ))
-
 Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)
 
-dim(Mothership_lasso_anx)
 ### depression
@@
     # RDQ
-    rdqPRE_coping:rdqPRE_wbs,
+    rdqPOST_coping:rdqPOST_wbs,
     #For table 3 - RCI info
@@
     #ACT stuff
-    AAQIIpre,
-    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    Acting_mindful_pre,
+    # AAQIIpre,
+    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    # Acting_mindful_pre,
 
@@
 
+Mothership_lasso_anx$CUXOS
+
 #3. Get statistics for variables + Assign to table
@@
                       lambda = cv.lasso.dep$lambda.min, standardized = TRUE)
-
-coef(lasso.model.min.dep)
 # Make prediction on test data
@@
                       lambda = cv.lasso.dep$lambda.1se,standardized = TRUE)
-coef(lasso.model.1se.dep)
 # Make prediction on test data
@@
     # predictors
-      Some_College + Female + White + YA_Treatment + Trauma_Treatment + Days_complete_1 + 
-      Days_not_attended_1 + Anxiety_D + BPD_P+ Trauma_D+Other+ Anxiety_C + Mood_C+ 
-      BPD_Co_C + Substance_C + No_Co + Current_Dx + CUXOS_pre + rdqPRE_coping + 
-      rdqPRE_pmh + rdqPRE_func + AAQIIpre + Self_compasion_pre,
+      Age_1  + Some_College + Female +
+      Married + White + Trauma_Treatment + 
+      YA_Treatment + Days_complete_1 + Days_not_attended_1 + 
+      BPD_P+ Trauma_D+ Other+ 
+      Mood_C+ Trauma_C + Substance_C + 
+      Current_Dx + CUXOS_pre + CUXOS_pre +
+      rdqPOST_coping + rdqPOST_pmh + rdqPOST_func +
+      rdqPOST_wbs,
     #data
@@
 
-# min model - pre/post
+# 1se model
 # glm_min_dep <-
@@
 #     # predictors
-#       White  +  Days_not_attended_1 + Anxiety_C + Current_Dx + CUXOS_pre +
-#       Non_react_post + AAQIIpost + Acting_mindful_post,
+#        Age_1 + Days_not_attended_1 + CUXOS_pre + rdqPOST_coping + rdqPOST_pmh 
+#        + rdqPOST_func + rdqPOST_wbs
 #     #data
@@
    library(aod)
-   wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:24)
+   dep_wald  <- wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:22)
+  wald <- wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms=2)$result$chi2[1]
+  for(i in 3:22){
+      wald <- append(wald, wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms=i)$result$chi2[1])
+  }
+  wald
 
@@
 FP.min.dep$type = c("Depression")
+FP.min.dep$Beta =   round(tidy.summary.min.dep$estimate[2:22],3)
+FP.min.dep$Wald = round(wald,2)
+
 FP.min.dep
@@
 
+```{r}
+# df for Forrest plots
+FP.min.dep <- data.frame(cbind(
+  Variable = tidy.summary.min.dep$term[2:length(tidy.summary.min.dep$term)],
+  Beta =round(tidy.summary.min.dep$estimate[2:11],3),
+  Wald = round(wald,2),
+  OR = round(as.numeric(OR.min.dep[2:length(OR.min.dep)]),2),
+  OR_low  = round(as.numeric(CI.min.dep[2:length(CI.min.dep$X2.5..),1]),2),
+  OR_high = round(as.numeric(CI.min.dep[2:length(CI.min.dep$X97.5..),2]),2),
+  p.values = p.values.min.dep$X2[2:length(p.values.min.dep$X2)]
+  ))
+FP.min.dep <- left_join(FP.min.dep,ADJ.p.values.min.dep, by = join_by(p.values == p.value))
+FP.min.dep
+
+write_csv(FP.min.dep, "~/Downloads/FP.min.dep")
+
+#create FP df
+dep_df <- data.frame(rbind(
+  #Block 1
+  NA,NA,
+  arrange(FP.min.dep,desc(OR)),
+  #Top row
+  NA
+))
+
+dep_df <- mutate(dep_df,
+    OR = as.numeric(OR),
+    OR_low = as.numeric(OR_low),
+    OR_high = as.numeric(OR_high),
+    sig = ifelse(is.na(p.adjusted), NA, 
+          ifelse(p.adjusted<= 0.05, 16,1)),
+    p_fig = ifelse(
+      is.na(p.adjusted), NA,
+      ifelse(p.adjusted < 0.001, "<0.001", 
+             round(as.numeric(p.adjusted),3))),
+    order = 0
+    )
+
+#create OR label for FP
+dep_df <- mutate(dep_df,
+    label = 
+      #NAs      
+      # ifelse(is.na(OR) |is.na(CI),NA,
+      #p <.05      
+      ifelse(p.adjusted <= 0.05 & p.adjusted >= 0.01,
+                   paste0(OR," [",OR_low,"-",OR_high,"]*"),
+      #p<.01
+      ifelse(p.adjusted < 0.01 & p.adjusted >= 0.001,
+                   paste0(OR," [",OR_low,"-",OR_high,"]**"),
+      #p<.001
+      ifelse(p.adjusted < 0.001,
+                   paste0(OR," [",OR_low,"-",OR_high,"]***"),
+      # else (i.e., p > .05)
+             paste0(OR," [",OR_low,"-",OR_high,"]")
+      ))))
+
+#assign variable names
+dep_df$Variable <- c(
+    paste0("X^2 = ", round(dep_wald$result$chi2[1],2),", p<0.001"),
+    paste0("Model R^2 = ", round((R2.min.dep[[1]]*100),3),"%"),
+"Other Disorder", "Trauma Treatment", "Male","Unmarried", "Young Adult Treatment",       
+"Days Not Attended", "White", "# of Diagnosis", "Age", "Days completed", "Pre CUXOS",          
+"Post Wellbeing", "Post Positive Mental Helath", "Post Functioning", "Post Coping Ability", "Some College","BPD", "Trauma Disorder", "Co-occuring Mood Disorder", "Co-occuring Trauma Disorder", "Co-occuring SUD",  "Variable"
+    )
+
+# assign labels to top row and assign the order of varaibles
+dep_df[24,2] = "Beta"
+dep_df[24,3] = "Wald"
+dep_df[24,12] = "OR [95% CI]"
+dep_df[24,10] = "Adjusted p"
+dep_df$order = c(seq(2,length(dep_df$order),1),1)
+#Final df for FP
+dep_df
+
+write_csv(dep_df, "~/Downloads/dep_df")
+```
+
 # Anxiety Lasso 
@@
     #ACT stuff
-    AAQIIpre,
-    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    Acting_mindful_pre, 
+    # AAQIIpre,
+    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
+    # Acting_mindful_pre, 
   ))
@@
       # predictors
-        Age_1 + Female + Married + White + YA_Treatment + Trauma_Treatment + 
-        Days_complete_1 + Days_not_attended_1 + Anxiety_D + Mood_C + Trauma_C + 
-        Substance_C + Current_Dx + CUDOS_pre + rdqPRE_coping + rdqPRE_func + 
-        AAQIIpre + Non_react_pre + Self_compasion_pre,
+        Age_1 + Some_College + Days_not_attended_1 + Anxiety_D + BPD_Co_C + 
+        Substance_C + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
   tidy.summary.min.anx <- tidy(glm_min_anx)
-  tidy.summary.min.anx
 # Coefficients
@@
    library(aod)
-   wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:20)
-
+   anx_wald  <- wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:10)
+  wald <- wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms=2)$result$chi2[1]
+  for(i in 3:11){
+      wald <- append(wald, wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms=i)$result$chi2[1])
+  }
+  wald
+```
+
+```{r}
 # df for Forrest plots
@@
   Variable = tidy.summary.min.anx$term[2:length(tidy.summary.min.anx$term)],
-  OR = OR.min.anx [2:length(OR.min.anx)],
-  OR_low  = CI.min.anx [2:length(CI.min.anx$X2.5..),1],
-  OR_high = CI.min.anx [2:length(CI.min.anx$X97.5..),2],
+  Beta =round(tidy.summary.min.anx$estimate[2:11],3),
+  Wald = round(wald,2),
+  OR = round(as.numeric(OR.min.anx[2:length(OR.min.anx)]),2),
+  OR_low  = round(as.numeric(CI.min.anx[2:length(CI.min.anx$X2.5..),1]),2),
+  OR_high = round(as.numeric(CI.min.anx[2:length(CI.min.anx$X97.5..),2]),2),
   p.values = p.values.min.anx$X2[2:length(p.values.min.anx$X2)]
   ))
-
-# Left join the FDR adjusted p.value and round
 FP.min.anx <- left_join(FP.min.anx,ADJ.p.values.min.anx, by = join_by(p.values == p.value))
-FP.min.anx$p.values = round(as.numeric(FP.min.anx$p.values),3)
-FP.min.anx$p.adjusted = round(as.numeric(FP.min.anx$p.adjusted),3)
-FP.min.anx$type = c("Anxiety")
 FP.min.anx
@@
 write_csv(FP.min.anx, "~/Downloads/FP.min.anx")
-```
-1se -
-```{r}
-tmp_coeffs <- coef(lasso.model.1se.anx, s = "lambda.1se")
-Anx_coefs2 <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
-Anx_reg_coefs2 <- Anx_coefs[2:length(Anx_coefs)]
-Anx_reg_coefs2
-
-## 1se model
-  glm_1se_anx <-  
-      glm(
-      #Outcome varaible
-        Anxiety_Responder ~ 
-      # predictors
-         Days_not_attended_1 + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
-      #data
-      data = Vars_anx, 
-      # type of regression : logistic = binary / binomial
-      family = "binomial")
-# Summary of the model
-
-  summary.1se.anx      <- summary(glm_1se_anx)
-
-  tidy.summary.1se.anx <- tidy(glm_1se_anx)
-  tidy.summary.1se.anx
-# Coefficients
-  coefs.1se.anx <- round(abs(coef(glm_1se_anx)),3)
-
-# Odds ratio
-  OR.1se.anx <- round(exp(coef(glm_1se_anx)),3)
-
-# OR 95% CI
-  CI.1se.anx <- data.frame(exp(confint(glm_1se_anx)))
-  CI.1se.anx[,1] = round(CI.1se.anx[,1],3)
-  CI.1se.anx[,2] = round(CI.1se.anx[,2],3)
-
-# P values
-  p.values.1se.anx <- data.frame(cbind(tidy.summary.1se.anx$term,tidy.summary.1se.anx$p.value))
-  # FDR Adjusted P Values
-    adj.p.1se.anx <- FDR(pvalues = p.values.1se.anx)
-    ADJ.p.values.1se.anx <- data.frame(rbind(adj.p.1se.anx$exclude, adj.p.1se.anx$select))
-
-# R^2 values  
-   R2.1se.anx <- performance::r2(glm_1se_anx)
-
-# df for Forrest plots
-FP.1se.anx <- data.frame(cbind(
-  Variable = tidy.summary.1se.anx$term[2:length(tidy.summary.1se.anx$term)],
-  OR = OR.1se.anx [2:length(OR.1se.anx)],
-  OR_low  = CI.1se.anx [2:length(CI.1se.anx$X2.5..),1],
-  OR_high = CI.1se.anx [2:length(CI.1se.anx$X97.5..),2],
-  p.values = p.values.1se.anx$X2[2:length(p.values.1se.anx$X2)]
+
+#create FP df
+anx_df <- data.frame(rbind(
+  #Block 1
+  NA,NA,
+  arrange(FP.min.anx,desc(OR)),
+  #Top row
+  NA
 ))
 
-# Left join the FDR adjusted p.value
-FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
-FP.1se.anx$p.values = round(as.numeric(FP.1se.anx$p.values),3)
-FP.1se.anx$p.adjusted = round(as.numeric(FP.1se.anx$p.adjusted),3)
-FP.1se.anx$type = c("Anxiety")
-FP.1se.anx
-
-write_csv(FP.1se.anx, "~/Downloads/FP.1se.anx")
-```
-
-# Forrest Plot
+anx_df <- mutate(anx_df,
+    OR = as.numeric(OR),
+    OR_low = as.numeric(OR_low),
+    OR_high = as.numeric(OR_high),
+    sig = ifelse(is.na(p.adjusted), NA, 
+          ifelse(p.adjusted<= 0.05, 16,1)),
+    p_fig = ifelse(
+      is.na(p.adjusted), NA,
+      ifelse(p.adjusted < 0.001, "<0.001", 
+             round(as.numeric(p.adjusted),3))),
+    order = 0
+    )
+
+#create OR label for FP
+anx_df <- mutate(anx_df,
+    label = 
+      #NAs      
+      # ifelse(is.na(OR) |is.na(CI),NA,
+      #p <.05      
+      ifelse(p.adjusted <= 0.05 & p.adjusted >= 0.01,
+                   paste0(OR," [",OR_low,"-",OR_high,"]*"),
+      #p<.01
+      ifelse(p.adjusted < 0.01 & p.adjusted >= 0.001,
+                   paste0(OR," [",OR_low,"-",OR_high,"]**"),
+      #p<.001
+      ifelse(p.adjusted < 0.001,
+                   paste0(OR," [",OR_low,"-",OR_high,"]***"),
+      # else (i.e., p > .05)
+             paste0(OR," [",OR_low,"-",OR_high,"]")
+      ))))
+
+#assign variable names
+anx_df$Variable <- c(
+    paste0("X^2 = ", round(anx_wald$result$chi2[1],2),", p<0.001"),
+    paste0("Model R^2 = ", round((R2.min.anx[[1]]*100),3),"%"),
+    "Co-occuring BPD", "Days Not Attended", "Age", "Post Functioning", 
+    "Post Sense of Wellbeing", "Post PMH", "Post Coping", "Some College",
+    "Co-occuring SUD", "Anxiety Disorder",
+    "Variable"
+    )
+
+# assign labels to top row and assign the order of varaibles
+anx_df[13,2] = "Beta"
+anx_df[13,3] = "Wald"
+anx_df[13,12] = "OR [95% CI]"
+anx_df[13,10] = "Adjusted p"
+anx_df$order = c(seq(2,length(anx_df$order),1),1)
+#Final df for FP
+anx_df
+
+write_csv(anx_df, "~/Downloads/anx_df")
+
+```
 
 Anxiety Plot
+```{r}
+ANX_FP <- 
+  anx_df |>
+  ggplot(aes(y = reorder(Variable, -order))) +
+  #take away background
+  theme_classic() +
+  #make the forrest plot
+  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = 1, show.legend = FALSE,
+                color = ifelse(anx_df$p.adjusted < 0.05, "red", "darkgrey")) +
+  geom_point(aes(x=OR), shape= 16,
+             size=4,show.legend = FALSE,
+             color = ifelse(anx_df$p.adjusted < 0.05, "red", "darkgrey")) +
+  geom_point(aes(x=OR), shape= 1,
+             size=4,show.legend = FALSE, color = "white") +
+    geom_point(aes(x=OR), shape= 1,
+             size=4.1,show.legend = FALSE, color = "white")+
+# geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.6, show.legend = FALSE) +
+  #change x axis name
+  labs(
+    x="Odds Ratio",
+    # title = "    Odds of Meeting Physical Activity Guidelines",
+    subtitle ="Odds of Anxiety Non-Response")+
+  #adjust the dimentions. 
+  coord_cartesian(ylim = c(1,  length(anx_df$Variable)))+
+  #add a line at 1 for reference 
+  geom_vline(xintercept = 1,linetype="dashed",alpha = .50) + 
+  #add anotations to help suggests what each side means.
+  annotate("text", x = .6, y = length(anx_df$Variable) -1 , label = "Less Likely", size= 4) +
+  annotate("text", x = 1.4, y = length(anx_df$Variable) -1, label = "More Likely",size= 4) +
+  #Git rid of the Y - Axis
+    theme(axis.line.y = element_blank(),
+        axis.ticks.y= element_blank(),
+        axis.text.y= element_blank(),
+        axis.title.y= element_blank())
+
+ANX_text <- 
+  dep_df |>
+  ggplot(aes(y = reorder(Variable, -order))) +
+  geom_text(aes(x = 0, label = Variable), hjust = 0,
+        fontface = ifelse(dep_df$Variable == "Variable","bold","plain")) +
+  geom_text(aes(x = 1.1, label = Beta),
+        hjust = 0,
+        fontface = ifelse(dep_df$Beta == "Beta", "bold","plain")) + 
+  geom_text(aes(x = 1.5, label = Wald),
+        hjust = 0,
+        fontface = ifelse(dep_df$Wald == "Wald", "bold","plain")) +
+  geom_text(aes(x = 1.9, label = label),
+        hjust = 0,
+        fontface = ifelse(dep_df$label == "OR [95% CI]", "bold","plain")) +
+  theme_void() +     
+  coord_cartesian(ylim = c(1,length(dep_df$Variable)), xlim = c(0, 4))
+
+library("patchwork")
+
+layout <- c(
+  patchwork::area(t = 0, l = 0, b = 30, r = 25),
+  patchwork::area(t = 0, l = 17, b = 30, r = 26)
+)
+
+ANX_text + ANX_FP + plot_layout(design = layout)
+```
+
+Depression Plot
+```{r}
+DEP_FP <- 
+  dep_df |>
+  ggplot(aes(y = reorder(Variable, -order))) +
+  #take away background
+  theme_classic() +
+  #make the forrest plot
+  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = 1, show.legend = FALSE,
+                color = ifelse(dep_df$p.adjusted < 0.05, "blue", "darkgrey")) +
+  geom_point(aes(x=OR), shape= 16,
+             size=4,show.legend = FALSE,
+             color = ifelse(dep_df$p.adjusted < 0.05, "blue", "darkgrey")) +
+  geom_point(aes(x=OR), shape= 1,
+             size=4,show.legend = FALSE, color = "white") +
+    geom_point(aes(x=OR), shape= 1,
+             size=4.1,show.legend = FALSE, color = "white")+
+# geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.6, show.legend = FALSE) +
+  #change x axis name
+  labs(
+    x="Odds Ratio",
+    # title = "    Odds of Meeting Physical Activity Guidelines",
+    subtitle ="Odds of Depression Non-Response")+
+  #adjust the dimentions. 
+  coord_cartesian(ylim = c(1,  length(dep_df$Variable)),
+                  xlim = c(0,2))+
+  #add a line at 1 for reference 
+  geom_vline(xintercept = 1,linetype="dashed",alpha = .50) + 
+  #add anotations to help suggests what each side means.
+  annotate("text", x = .6, y = length(dep_df$variable) -1 , label = "Less Likely", size= 4) +
+  annotate("text", x = 1.4, y = length(dep_df$variable) -1, label = "More Likely",size= 4) +
+  #Git rid of the Y - Axis
+    theme(axis.line.y = element_blank(),
+        axis.ticks.y= element_blank(),
+        axis.text.y= element_blank(),
+        axis.title.y= element_blank())
+
+DEP_text <- 
+  dep_df |>
+  ggplot(aes(y = reorder(Variable, -order))) +
+  geom_text(aes(x = 0, label = Variable), hjust = 0,
+        fontface = ifelse(dep_df$Variable == "Variable","bold","plain")) +
+  geom_text(aes(x = 1.1, label = Beta),
+        hjust = 0,
+        fontface = ifelse(dep_df$Beta == "Beta", "bold","plain")) + 
+  geom_text(aes(x = 1.5, label = Wald),
+        hjust = 0,
+        fontface = ifelse(dep_df$Wald == "Wald", "bold","plain")) +
+  geom_text(aes(x = 1.9, label = label),
+        hjust = 0,
+        fontface = ifelse(dep_df$label == "OR [95% CI]", "bold","plain")) +
+  theme_void() +     
+  coord_cartesian(ylim = c(1,length(dep_df$Variable)), xlim = c(0, 4))
+
+library("patchwork")
+
+layout <- c(
+  patchwork::area(t = 0, l = 0, b = 30, r = 25),
+  patchwork::area(t = 0, l = 17, b = 30, r = 26)
+)
+
+DEP_text + DEP_FP + plot_layout(design = layout)
+```
+
 ```{r}
@@
   # add an "-" between HR estimate confidence intervals
-  estimate_lab = paste0(OR, " (", OR_low, "-", OR_high, ")")) |>
+  estimate_lab = paste0(OR, " [", OR_low, "-", OR_high, "]")) |>
   # round p-values to two decimal places, except in cases where p < .001
@@
 ```
+
 ## Depression Plot

### 2024-06-28 Lasso_RCI_Response.Rmd
don't need dis stuff

--- 2024-05-21 Lasso_RCI_Response.Rmd
@@
 library(tidyr)
-library(fuzzySim) ## For FDR adjusted p values
-library(broom) # for tidy regression output
 ```
@@
 #DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
-```
-
-```{r}
-
-AAQIIpre <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPre_1.sav")
-AAQIIpre <- AAQIIpre |>
-  mutate(
-    AAQIIpre = AAQIIpre_1_1 + AAQIIpre_2_1 + AAQIIpre_3_1 + AAQIIpre_4_1 + 
-      AAQIIpre_5_1 + AAQIIpre_6_1 + AAQIIpre_7_1
-  )
-Mothership <- left_join(Mothership,AAQIIpre, by = join_by(ID1 == ID1))
-
-AAQIIpost <- read_sav("~/Desktop/Coding/data/ACT_scores/AAQIIPost_1.sav")
-AAQIIpost <- AAQIIpost |>
-  mutate(
-    AAQIIpost = AAQIIpost_1_1 + AAQIIpost_2_1 + AAQIIpost_3_1 + AAQIIpost_4_1 + 
-      AAQIIpost_5_1 + AAQIIpost_6_1 + AAQIIpost_7_1
-  )
-Mothership <- left_join(Mothership,AAQIIpost, by = join_by(ID1 == ID1))
-
-FMMQ_pre <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPre_1.sav")
-FMMQ_pre <- FMMQ_pre|>
-  mutate(
-    #reverse code items
-    FFMQpre_4R  = 6 - FFMQpre_4_1,
-    FFMQpre_5R  = 6 - FFMQpre_5_1,  
-    FFMQpre_7R  = 6 - FFMQpre_7_1, 
-    FFMQpre_8R  = 6 - FFMQpre_8_1, 
-    FFMQpre_11R = 6 - FFMQpre_11_1, 
-    FFMQpre_12R = 6 - FFMQpre_12_1,
-    FFMQpre_14R = 6 - FFMQpre_14_1,
-    FFMQpre_17R = 6 - FFMQpre_17_1,
-    FFMQpre_19R = 6 - FFMQpre_19_1,
-    FFMQpre_22R = 6 - FFMQpre_22_1,
-    FFMQpre_23R = 6 - FFMQpre_23_1,
-    FFMQpre_24R = 6 - FFMQpre_24_1,
-    #create scales
-    Desc_Ex_pre =
-        FFMQpre_1_1 + FFMQpre_2_1 + FFMQpre_5R + FFMQpre_11R + FFMQpre_16_1,
-    Non_react_pre = 
-        FFMQpre_3_1 + FFMQpre_9_1 + FFMQpre_13_1 + FFMQpre_18_1 + FFMQpre_21_1,
-    Observe_inner_pre = 
-        FFMQpre_6_1 + FFMQpre_10_1 + FFMQpre_15_1 + FFMQpre_20_1,
-    Self_compasion_pre = 
-        FFMQpre_4R + FFMQpre_7R + FFMQpre_14R + FFMQpre_19R + FFMQpre_24R,
-    Acting_mindful_pre = 
-        FFMQpre_8R + FFMQpre_12R + FFMQpre_17R + FFMQpre_22R + FFMQpre_23R,
-    FFMQ_pre_total = 
-        Desc_Ex_pre + Non_react_pre + Observe_inner_pre+ Self_compasion_pre + Acting_mindful_pre
-    )
-Mothership <- left_join(Mothership,FMMQ_pre, by = join_by(ID1 == ID1))
-
-FMMQ_post <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_1.sav")
-FMMQ_post <- FMMQ_post|>
-  mutate(
-    #reverse code items
-    FFMQpost_4R  = 6 - FFMQpost_4_1,
-    FFMQpost_5R  = 6 - FFMQpost_5_1,  
-    FFMQpost_7R  = 6 - FFMQpost_7_1, 
-    FFMQpost_8R  = 6 - FFMQpost_8_1, 
-    FFMQpost_11R = 6 - FFMQpost_11_1, 
-    FFMQpost_12R = 6 - FFMQpost_12_1,
-    FFMQpost_14R = 6 - FFMQpost_14_1,
-    FFMQpost_17R = 6 - FFMQpost_17_1,
-    FFMQpost_19R = 6 - FFMQpost_19_1,
-    FFMQpost_22R = 6 - FFMQpost_22_1,
-    FFMQpost_23R = 6 - FFMQpost_23_1,
-    FFMQpost_24R = 6 - FFMQpost_24_1,
-    #create scales
-    Desc_Ex_post =
-        FFMQpost_1_1 + FFMQpost_2_1 + FFMQpost_5R + FFMQpost_11R + FFMQpost_16_1,
-    Non_react_post = 
-        FFMQpost_3_1 + FFMQpost_9_1 + FFMQpost_13_1 + FFMQpost_18_1 + FFMQpost_21_1,
-    Observe_inner_post = 
-        FFMQpost_6_1 + FFMQpost_10_1 + FFMQpost_15_1 + FFMQpost_20_1,
-    Self_compasion_post = 
-        FFMQpost_4R + FFMQpost_7R + FFMQpost_14R + FFMQpost_19R + FFMQpost_24R,
-    Acting_mindful_post = 
-        FFMQpost_8R + FFMQpost_12R + FFMQpost_17R + FFMQpost_22R + FFMQpost_23R,
-    FFMQ_post_total = 
-        Desc_Ex_post + Non_react_post + Observe_inner_post + Self_compasion_post + Acting_mindful_post
-    )
-Mothership <- left_join(Mothership,FMMQ_post, by = join_by(ID1 == ID1))
-
-# df_5 <- read_sav("~/Desktop/Coding/data/ACT_scores/FFMQPost_4250-4350.sav")
+
 ```
@@
     dummy = -99
-  )
-  # filter(!is.na(Disorder_treat),
-  #        !is.na(TxYear),
-  #        !is.na(Duration))
+  ) |>
+  filter(!is.na(Disorder_treat),
+         !is.na(TxYear),
+         !is.na(Duration))
 
@@
 ```{r}
-# 4. RCI Analysis categorization ------------------------------------------
-
-#devtools::install_github("AWKruijt/JT-RCI")
-
-library(JTRCI)
-
-# # 
-# # #devtools::install_github("zieglema/ClinicalSig")
-# #1. Create df for RCI
-# RCI_df_dep <- Mothership_post |>
-#   mutate(
-#     ID1  = as.integer(ID1),
-#     pre  = as.numeric(CUDOS_pre),
-#     post = as.numeric(CUDOS_post),
-#   ) |>
-#   select(
-#     ID1,pre,post
-#   ) |>
-#   filter(!is.na(pre),
-#          !is.na(post),
-#          pre > 20)
-# 
-# RCI_df_anx <- Mothership_post |>
-#   mutate(
-#     ID1  = as.integer(ID1),
-#     pre  = as.numeric(CUXOS_pre),
-#     post = as.numeric(CUXOS_post),
-#   ) |>
-#   select(
-#     ID1,pre,post
-#   ) |>
-#   filter(!is.na(pre),
-#          !is.na(post),
-#          pre > 20)
-# 
-# 
-# RCI_df_dep <- data.frame(RCI_df_dep)
-# RCI_df_anx <- data.frame(RCI_df_anx)
-# 
-# # https://awkruijt.netlify.app/plotposts/longitudinaljtrci
-# 
-# RCI_df_anx1<-RCI_df_anx |>
-#   select(ID1,pre,post)
-# 
-# ## Using RCI only (respond/nonrespond/deteriorated)
-# DEP_RCI <- JTRCI (data = RCI_df_dep, 
-#                   pre = "pre", 
-#                   post = "post", 
-#                   ppid = "ID1", 
-#                   reliability = .74, 
-#                   indextype = "RCI", 
-#                   JTcrit = "auto",
-#                   plottitle = "JT indices for anxiety")
-# 
-# ANX_RCI <- JTRCI (data = RCI_df_anx, 
-#                   pre = "pre", 
-#                   post = "post", 
-#                   ppid = "ID1", 
-#                   reliability = .74, 
-#                   indextype = "RCI", 
-#                   #JTcrit = "auto",
-#                   plottitle = "JT indices for depression")
-# RCI_DF<- ANX_RCI$data
-# colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")
-# 
-# RCI_DF2<- DEP_RCI$data
-# colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")
-# 
-# RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
-# colnames(RCI_DF)[1] = "ID1"
-# 
-# head(RCI_DF)
-```
-
-```{r}
-#Using JT citeria (recovered/improved/nonresponse/deteriorated)
-# 
-# #1. JT classification for depression
-# JTRCI (data = RCI_df_dep, 
-#                   pre = "pre", 
-#                   post = "post", 
-#                   ppid = "ID1", 
-#                   reliability = .74, 
-#                   indextype = "JT", 
-#                   JTcrit = "auto",
-#                   plottitle = "JT indices for anxiety")
-# 
-# DEP_JT <- JTRCIdf
-# colnames(DEP_JT) <- paste0(colnames(DEP_JT),"_dep")
-# head(DEP_JT)
-# 
-# #2. JT classification for anxiety
-# JTRCI (data = RCI_df_anx, 
-#                   pre = "pre", 
-#                   post = "post", 
-#                   ppid = "ID1", 
-#                   reliability = .74, 
-#                   indextype = "JT", 
-#                   #JTcrit = "auto",
-#                   plottitle = "JT indices for depression")
-# 
-# ANX_JT<- JTRCIdf
-# 
-# #3. Make combined JT table for anxiety and depression
-# 
-# # JT_DF<- ANX_JT
-# 
-# colnames(ANX_JT) <- paste0(colnames(ANX_JT),"_anx")
-# 
-# # 
-# # JT_DF2<- DEP_JT
-# 
-# # 
-# # JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
-# # colnames(JT_DF)[1] = "ID1"
-# 
-# head(ANX_JT)
-```
-
-JTRCI with less people
-```{r}
-
-Mothership_lasso <- Mothership_post |>
+Mothership_lasso_1 <- Mothership_post |>
     filter(
@@
     !is.na(White),
-  #!is.na(Anxiety_Responder),
+    CUXOS_pre >= 20,
+    CUDOS_pre >= 20
   ) |>
   select( c(
-    ID1,Disorder_treat,
+   # Anxiety_Responder, Depression_Responder,
     # Demographics
-    Age_1,Some_College:Married,White, #Discharge,
+    ID1, Age_1,Some_College:Married,White, #Discharge,
     # Treatment info
@@
     # Disorders
-    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
+    Anxiety_D, Mood_D, BPD_P, Trauma_D, 
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
     # RDQ
-    # rdqPRE_coping:rdqPRE_wbs,
+    rdqPOST_coping:rdqPOST_wbs,
     #For table 3 - RCI info
-    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post,
-    #ACT stuff
-    # AAQIIpre, AAQIIpost,
-    # Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre,
-    # Acting_mindful_pre,
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post,
+    CUXOS_pre, CUXOS_post, CUDOS_pre, CUDOS_post
   ))
 
-Mothership_lasso_1 <- na.omit(Mothership_lasso)
-
-dim(Mothership_lasso_1)
-
-```
-
-```{r}
-RCI_df_anx2 <- Mothership_lasso_1 |>
-  filter(
-    !is.na(CUXOS_pre),
-    !is.na(CUXOS_post),
-    CUXOS_pre > 20,
-  )|>
-  mutate(
-    ID1  = as.integer(ID1),
-    pre  = as.numeric(CUXOS_pre),
-    post = as.numeric(CUXOS_post),
-  ) |>
-  select(
-    ID1,pre,post
-  ) |>
-  filter(!is.na(pre),
-         !is.na(post),
-         pre > 20)
-
-RCI_df_dep2 <- Mothership_lasso_1 |>
-  filter(
-    !is.na(CUDOS_pre),
-    !is.na(CUDOS_post),
-    CUDOS_pre > 20,
-  ) |>
+Mothership_lasso_1 <- na.omit(Mothership_lasso_1)
+```
+
+```{r}
+# 4. RCI Analysis categorization ------------------------------------------
+
+#devtools::install_github("AWKruijt/JT-RCI")
+
+library(JTRCI)
+citation("JTRCI")
+
+# 
+# #devtools::install_github("zieglema/ClinicalSig")
+#1. Create df for RCI
+RCI_df_dep <- Mothership_lasso_1 |>
   mutate(
@@
   ) |>
+  filter(!is.na(pre),
+         !is.na(post),
+         pre > 20,
+         !is.na(Some_College),
+         !is.na(Female),
+         !is.na(IPT_track_1),
+         !is.na(White),
+         CUXOS_pre >= 20,
+         CUDOS_pre >= 20) |>
   select(
-    ID1,pre,post
+    ID1,pre,post)
+
+RCI_df_anx <- Mothership_lasso_1 |>
+  mutate(
+    ID1  = as.integer(ID1),
+    pre  = as.numeric(CUXOS_pre),
+    post = as.numeric(CUXOS_post)
   ) |>
@@
          !is.na(post),
-         pre > 20)
-
-RCI_df_dep2 <- data.frame(RCI_df_dep2)
-RCI_df_anx2 <- data.frame(RCI_df_anx2)
-
-#1. JT classification for depression
-JTRCI (data = RCI_df_dep2, 
+         pre > 20,
+         !is.na(Some_College),
+         !is.na(Female),
+         !is.na(IPT_track_1),
+         !is.na(White),
+         CUXOS_pre >= 20,
+         CUDOS_pre >= 20
+  ) |>
+  select(
+    ID1,pre,post
+  )
+
+RCI_df_dep <- data.frame(RCI_df_dep)
+RCI_df_anx <- data.frame(RCI_df_anx)
+
+# https://awkruijt.netlify.app/plotposts/longitudinaljtrci
+
+RCI_df_anx1<-RCI_df_anx |>
+  select(ID1,pre,post)
+
+## Using RCI only (respond/nonrespond/deteriorated)
+DEP_RCI <- JTRCI (data = RCI_df_dep, 
                   pre = "pre", 
@@
                   reliability = .74, 
-                  indextype = "JT", 
+                  indextype = "RCI", 
                   JTcrit = "auto",
-                  plottitle = "JT indices for Depression")
-
-DEP_JT_smol <- JTRCIdf
-colnames(DEP_JT_smol) <- paste0(colnames(DEP_JT_smol),"_dep")
-head(DEP_JT_smol)
-
-#2. JT classification for anxiety
-JTRCI (data = RCI_df_anx2, 
+                  plottitle = "JT indices for anxiety")
+
+ANX_RCI <- JTRCI (data = RCI_df_anx, 
                   pre = "pre", 
@@
                   reliability = .74, 
-                  indextype = "JT", 
+                  indextype = "RCI", 
                   #JTcrit = "auto",
-                  plottitle = "JT Indices For Anxiety")
-
-ANX_JT_smol<- JTRCIdf
-
-colnames(ANX_JT_smol) <- paste0(colnames(ANX_JT_smol),"_anx")
+                  plottitle = "JT indices for depression")
+RCI_DF<- ANX_RCI$data
+colnames(RCI_DF) <- paste0(colnames(RCI_DF),"_anx")
+
+RCI_DF2<- DEP_RCI$data
+colnames(RCI_DF2) <- paste0(colnames(RCI_DF2),"_dep")
+
+RCI_DF <- full_join(RCI_DF,RCI_DF2, by = c("ppid_anx" = "ppid_dep"))
+colnames(RCI_DF)[1] = "ID1"
+
+RCI_DF
+```
+
+```{r}
+#Using JT citeria (recovered/improved/nonresponse/deteriorated)
+
+#1. JT classification for depression
+JTRCI (data = RCI_df_dep, 
+                  pre = "pre", 
+                  post = "post", 
+                  ppid = "ID1", 
+                  reliability = .74, 
+                  indextype = "JT") 
+                  #plottitle = "JT indices for anxiety")
+
+DEP_JT <- JTRCIdf
+
+#2. JT classification for anxiety
+JTRCI (data = RCI_df_anx, 
+                  pre = "pre", 
+                  post = "post", 
+                  ppid = "ID1", 
+                  reliability = .74, 
+                  indextype = "JT") 
+                  #JTcrit = "auto",
+                 # plottitle = "JT indices for depression")
+
+ANX_JT<- JTRCIdf
+
+#3. Make combined JT table for anxiety and depression
+
+JT_DF<- ANX_JT
+
+colnames(JT_DF) <- paste0(colnames(JT_DF),"_anx")
+
+JT_DF2<- DEP_JT
+colnames(JT_DF2) <- paste0(colnames(JT_DF2),"_dep")
+
+JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
+colnames(JT_DF)[1] = "ID1"
+
+JT_DF
+
 ```
@@
 
-# Mothership_post <- Mothership_post |>
-#   #1. Filter out scores for people not in the program / don't have data
-#   filter(!is.na(Days_complete_1)) |>
-#   #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
-#   filter(!is.na(CUXOS_pre),
-#          !is.na(CUXOS_post),
-#          CUXOS_pre > 0,
-#          CUXOS_post >= 0,
-#          !is.na(CUDOS_pre),
-#          !is.na(CUDOS_post),
-#          CUDOS_pre > 0,
-#          CUDOS_post>= 0
-#          ) |>
+Mothership_post <- Mothership_post |>
+  #1. Filter out scores for people not in the program / don't have data
+  filter(!is.na(Days_complete_1)) |>
+  #Having people in the program for more than 40 days means that their scores may be a lot higher, they should be filtered out as result. 
+  filter(!is.na(CUXOS_pre),
+         !is.na(CUXOS_post),
+         CUXOS_pre > 0,
+         CUXOS_post >= 0,
+         !is.na(CUDOS_pre),
+         !is.na(CUDOS_post),
+         CUDOS_pre > 0,
+         CUDOS_post> 0
+         ) 
   # mutate(
@@
   #   Percent_Anx_change = (Delta_Anx_DC/CUXOS_pre)*100,
-#     Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100
-#   )
-```
-
-```{r}
-#Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
+  #   Percent_Dep_Dchange = (Delta_Dep_DC/CUDOS_pre)*100,
+  #   #Days_complete_W = ifelse(Days_complete_1 > 40, 40, Days_complete_1),
   #   Anx_Responder = as.factor(
@@
 
-#2. Left join data from the RCI dataset into the Mothership_post df
-# Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
-#   mutate(
-#     Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
-#     Depression_Responder = as.factor(recode(Depression_Responder,
-#                                             "1" = "2",
-#                                             "2" = "2",
-#                                             "3" = "1"
-#     )),
-#     Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
-#     Depression_Responder = as.factor(recode(Depression_Responder,
-#                                             "2" = "Non-Responder",
-#                                             "1" = "Responder"
-#     )),
-#     Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
-#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
-#                                          "1" = "2",
-#                                          "2" = "2",
-#                                          "3" = "1"
-#     )),
-#     Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
-#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
-#                                          "2" = "Non-Responder",
-#                                          "1" = "Responder"
-#     )),
-#     RESPONDER_FIGS = as.factor(
-#       ifelse(Anxiety_Responder == "Responder" | Depression_Responder == "Responder", "Responder",
-#              ifelse(Anxiety_Responder == "Non-Responder" & Depression_Responder == "Non-Responder", "Non-Responder", NA)
-#       ))) |>
-#   filter(!is.na(RESPONDER_FIGS))
-```
-
-JT Numbers
-```{r}
-Mothership_post_anx <- left_join(Mothership_post,ANX_JT_smol, by = join_by(ID1 == ppid_anx)) |>
-  mutate(
-    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
-    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
-                                         "1" = "2",
-                                         "2" = "2",
-                                         "3" = "1",
-                                         "4" = "1",
-                                         "5" = "1"
-    )),
-    # Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, NA)),
-    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
-                                         "2" = "Non-Responder",
-                                         "1" = "Responder"
-    ))) |>
-  filter(
-    !is.na(Anxiety_Responder),
-    )
-
-Mothership_post_dep <- left_join(Mothership_post,DEP_JT_smol, by = join_by(ID1 == ppid_dep)) |>
+Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
   mutate(
@@
     )),
-    # Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, NA)),
+    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
     Depression_Responder = as.factor(recode(Depression_Responder,
+                                            "2" = "Non-Responder",
+                                            "1" = "Responder"
+    )),
+    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
+    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+                                         "1" = "2",
+                                         "2" = "2",
+                                         "3" = "1",
+                                         "4" = "1",
+                                         "5" = "1"
+    )),
+    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
+    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                          "2" = "Non-Responder",
@@
   filter(
+    !is.na(Anxiety_Responder),
     !is.na(Depression_Responder)
     )
-
-Mothership_post_joined <- full_join(Mothership_post_dep,Mothership_post_anx, by = join_by(ID1 == ID1), suffix = c(".x",".y")) |>
-  select(-ends_with(".y"))
-
-#It saves everything colname.x, so I'm going to remove the .x from everything
-names.x <- colnames(Mothership_post_joined)[2:248]
-colnames(Mothership_post_joined)[2:248] <- substr(names.x,1,nchar(names.x)-2)
-```
-
-RCI numbers
-```{r}
-# Mothership_post <- left_join(Mothership_post,RCI_DF, by = join_by(ID1 == ID1)) |>
-#   mutate(
-#     Depression_Responder = ifelse(!is.na(class_RCI_dep), class_RCI_dep, NA),
-#     Depression_Responder = as.factor(recode(Depression_Responder,
-#                                             "1" = "2",
-#                                             "2" = "2",
-#                                             "3" = "1",
-#                                             "4" = "1",
-#                                             "5" = "1"
-#     )),
-#     Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
-#     Depression_Responder = as.factor(recode(Depression_Responder,
-#                                             "2" = "Non-Responder",
-#                                             "1" = "Responder"
-#     )),
-#     Anxiety_Responder = ifelse(!is.na(class_RCI_anx), class_RCI_anx, NA),
-#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
-#                                          "1" = "2",
-#                                          "2" = "2",
-#                                          "3" = "1",
-#                                          "4" = "1",
-#                                          "5" = "1"
-#     )),
-#     Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
-#     Anxiety_Responder = as.factor(recode(Anxiety_Responder,
-#                                          "2" = "Non-Responder",
-#                                          "1" = "Responder"
-#     ))) |>
-#   filter(
-#     !is.na(Anxiety_Responder),
-#     !is.na(Depression_Responder)
-#     )
+```
+
+```{r}
+#############            AnxDep_PrePost                 ##################
+
+#7. create new DF with Varaibles we want
+
+AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
+                                   Mothership_post$Disorder_treat,
+                                   Mothership_post$BL_CUDOS,
+                                   Mothership_post$BL_CUXOS,
+                                   Mothership_post$CUDOS_pre,
+                                   Mothership_post$CUDOS_post,
+                                   Mothership_post$CUXOS_pre,
+                                   Mothership_post$CUXOS_post,
+                                   #Extra stuff?
+                                   Mothership_post$Depression_Responder,
+                                   Mothership_post$Anxiety_Responder
+                                   #Mothership_post$RESPONDER_FIGS
+)) #%>%
+#filter(!is.na(Mothership_post$Disorder_treat))
+
+colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","Depression_Responder",
+                             "Anxiety_Responder")
+#, "RESPONDER_FIGS")
+
+#8. Create long data frame
+
+AnxDep_PrePost_Long <- AnxDep_PrePost %>% 
+  pivot_longer(
+    cols = CUDOS_pre:CUXOS_post, 
+    names_to = "Test",
+    values_to = "Score"
+  )
+AnxDep_PrePost_Long <-AnxDep_PrePost_Long %>%
+  mutate(
+    PrePost = ifelse(
+      Test == "CUDOS_pre", "Pre",
+      ifelse(Test == "CUXOS_pre" , "Pre", "Post"
+      )),
+    Score = as.integer(Score),
+    Test = as.factor(Test),
+    Test = as.factor(ifelse(Test == "CUDOS_pre",  "CUDOS",
+                            ifelse(Test == "CUDOS_post", "CUDOS", "CUXOS"
+                            ))))
+
+#9. Convert to data frame with means of values to be plotted
+AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
+  group_by(Test,PrePost) %>%
+  summarise(Score=mean(Score,na.rm=TRUE))
 ```
@@
 # Data analysis 
-## Part 1: Methods information
-```{r}
-# summary(as.factor(Mothership_post_joined$SCID_1))
-```
-
-## Part 2: Who is attending?
+## Part 1: Who is attending?
 
@@
 - Table 4: demographic breakdown
-
-First greate dfs for analyses
-
-```{r}
-### Anxeity 
-Mothership_lasso_anx <- Mothership_post_anx |>
+```{r}
+Mothership_lasso <- Mothership_post |>
     filter(
@@
     !is.na(Anxiety_Responder),
+    !is.na(Depression_Responder),
     CUXOS_pre >= 20,
+    CUDOS_pre >= 20
   ) |>
   select( c(
-    ID1,Anxiety_Responder,Disorder_treat,
+    Anxiety_Responder, Depression_Responder,
     # Demographics
@@
     # RDQ
-    rdqPOST_coping:rdqPOST_wbs,rdqPRE_coping:rdqPRE_wbs,
+    rdqPOST_coping:rdqPOST_wbs,
     #For table 3 - RCI info
-    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
-        #ACT stuff
-    AAQIIpre, AAQIIpost, 
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post, FFMQ_post_total, 
-    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    Acting_mindful_pre, FFMQ_post_total
+    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
   ))
-Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)
-
-### depression
-Mothership_lasso_dep <- Mothership_post_dep |>
-    filter(
-    !is.na(Some_College),
-    !is.na(Female),
-    !is.na(IPT_track_1),
-    !is.na(White),
-    !is.na(Depression_Responder),
-    CUDOS_pre >= 20,
-  ) |>
-  select( c(
-    ID1, Depression_Responder,Disorder_treat,
-    # Demographics
-    Age_1,Some_College:Married,White, #Discharge,
-    # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
-    # Disorders
-    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
-    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
-    Current_Dx,
-    # Pre-Post stuff
-    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
-    # RDQ
-    rdqPOST_coping:rdqPOST_wbs,rdqPRE_coping:rdqPRE_wbs,
-    #For table 3 - RCI info
-    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC,
-    #ACT stuff
-    AAQIIpre, AAQIIpost, 
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post, 
-    Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    Acting_mindful_pre,
-
-  ))
-Mothership_lasso_dep <- na.omit(Mothership_lasso_dep)
-
-### joined df
-Mothership_lasso_joined <- full_join(Mothership_lasso_anx,Mothership_lasso_dep, by = join_by("ID1" == "ID1")) |> 
-    select(-ends_with(".y"))
-
-#It saves everything colname.x, so I'm going to remove the .x from everything
-names.x <- colnames(Mothership_lasso_joined)[3:34]
-colnames(Mothership_lasso_joined)[3:34] <- substr(names.x,1,nchar(names.x)-2)
-
-#Delete ID1 from dfs
-Mothership_lasso_anx <- Mothership_lasso_anx[,-1]
-Mothership_lasso_dep <- Mothership_lasso_dep[,-1]
-```
-
-```{r}
-
-library(tableone) # This can be used to grab Exporatory data analysis values
+
+Mothership_lasso <- na.omit(Mothership_lasso)
+
+summary(Mothership_lasso$Anxiety_Responder)
+
+# Vars_dep <- Mothership_lasso |>
+#   select( c(
+#     Depression_Responder,
+#     # Demographics
+#     Age_1,Some_College:Married,White, 
+#     # Treatment info
+#     IPT_track_1, Days_complete_1, Days_not_attended_1, 
+#     # Disorders
+#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
+#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+#     Current_Dx,
+#     # Pre-Post stuff
+#     CUDOS_pre,CUXOS_pre,
+#     # RDQ
+#     rdqPOST_coping:rdqPOST_wbs
+#   ))
+
+library(tableone)
 
 ### first gather information based upon anxiety
+
 ## Vector of variables to summarize
-table1_vars_anx <- c(colnames(Mothership_lasso_anx)[-1:-2])
-table1_vars_anx <- table1_vars_anx[1:27]
+table1_vars_anx <- c(colnames(Mothership_lasso)[-1])
 
@@
 catVars <- c("Some_College", "Female" , "Married", "White",
-             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Other", 
-             "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
+             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
+             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
              "Substance_C", "Other_C" , "No_Co"
              )
-
 ## Create a TableOne object
-table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Mothership_lasso_anx,strata ="Anxiety_Responder",  factorVars = catVars, addOverall = T)
+table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Vars_anx,strata ="Anxiety_Responder",  factorVars = catVars)
 table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
 table1_tab_anx <- data.frame(table1_tab_anx)
+write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
 table1_tab_anx
-# add discriptive statistics 
-table1_tab_anx$ef_size = c("")
-
-library(rstatix)
-
-# age
-table1_tab_anx[2,5] <- round(t_test(Age_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
-table1_tab_anx[2,6] <- round(cohens_d(Age_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-# Some College 
-table1_tab_anx[3,5] <- round(chisq.test(Mothership_lasso_anx$Some_College, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[3,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Some_College))$estimate,2)
-# Female
-table1_tab_anx[4,5] <- round(chisq.test(Mothership_lasso_anx$Female, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[4,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Female))$estimate,2)
-# Married
-table1_tab_anx[5,5] <- round(chisq.test(Mothership_lasso_anx$Married, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[5,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Married))$estimate,2)
-# White
-table1_tab_anx[6,5] <- round(chisq.test(Mothership_lasso_anx$White, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[6,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$White))$estimate,2)
-# Treatment track
-table1_tab_anx[7,5] <- round(chisq.test(Mothership_lasso_anx$IPT_track_1, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-OR_IPT_anx <- table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$IPT_track_1)
-# OR general vs Trauma track
-table1_tab_anx[9,6] <- round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Trauma"]))$estimate,2)
-table1_tab_anx[9,5] <-
-round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Trauma"]))$p,2)
-# OR General vs Young adult track 
-table1_tab_anx[10,6] <- 
-  round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Young Adult"]))$estimate,2)
-table1_tab_anx[10,5] <-
-round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Young Adult"]))$p,2)
-# Days Completed in program
-table1_tab_anx[11,5] <- round(t_test(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
-table1_tab_anx[11,6] <- round(cohens_d(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-# Days not attending treatment
-table1_tab_anx[12,5] <- round(t_test(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
-table1_tab_anx[12,6] <- round(cohens_d(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-# Anxiety disorder
-table1_tab_anx[13,5] <- round(chisq.test(Mothership_lasso_anx$Anxiety_D, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[13,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Anxiety_D))$estimate,2)
-# Mood Disorders
-table1_tab_anx[14,5] <- round(chisq.test(Mothership_lasso_anx$Mood_D, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[14,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Mood_D))$estimate,2)
-# BPD 
-table1_tab_anx[15,5] <- round(chisq.test(Mothership_lasso_anx$BPD_P, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[15,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$BPD_P))$estimate,2)
-# Truama Related Disorders
-table1_tab_anx[16,5] <- round(chisq.test(Mothership_lasso_anx$Trauma_D, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[16,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Trauma_D))$estimate,2)
-# Other Disorders
-table1_tab_anx[17,5] <- round(chisq.test(Mothership_lasso_anx$Other, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[17,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Other))$estimate,2)
-# Co-occurring anxiety disorder 
-table1_tab_anx[18,5] <- round(chisq.test(Mothership_lasso_anx$Anxiety_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[18,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Anxiety_C))$estimate,2)
-# Co-occurring mood disorder
-table1_tab_anx[19,5] <- round(chisq.test(Mothership_lasso_anx$Mood_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[19,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Mood_C))$estimate,2)
-# Co-occurring BPD
-table1_tab_anx[20,5] <- round(chisq.test(Mothership_lasso_anx$BPD_Co_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[20,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$BPD_Co_C))$estimate,2)
-# Co-occurring Trauma Related Disorder
-table1_tab_anx[21,5] <- round(chisq.test(Mothership_lasso_anx$Trauma_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[21,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Trauma_C))$estimate,2)
-# Co-occurring Substance Use Disorders
-table1_tab_anx[22,5] <- round(chisq.test(Mothership_lasso_anx$Substance_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[22,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Substance_C))$estimate,2)
-# Co-occurring Other Disroders
-table1_tab_anx[23,5] <- round(chisq.test(Mothership_lasso_anx$Other_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[23,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Other_C))$estimate,2)
-# No Co-occurring Disorders
-table1_tab_anx[24,5] <- round(chisq.test(Mothership_lasso_anx$No_Co, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
-table1_tab_anx[24,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$No_Co))$estimate,2)
-# Number of Current diagnoses 
-table1_tab_anx[25,5] <- round(t_test(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
-table1_tab_anx[25,6] <- round(cohens_d(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-# CUDOS Pre scores
-table1_tab_anx[26,5] <- round(t_test(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
-table1_tab_anx[26,6] <- round(cohens_d(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-# CUXOS Pre scores
-table1_tab_anx[27,5] <- round(t_test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
-table1_tab_anx[27,6] <- round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-# RDQ Coping post scores
-table1_tab_anx[28,5] <- round(t_test(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
-table1_tab_anx[28,6] <- round(cohens_d(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-# RDQ Positive Mental Health post scores
-table1_tab_anx[29,5] <- round(t_test(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
-table1_tab_anx[29,6] <- round(cohens_d(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-# RDQ Functioning post scores
-table1_tab_anx[30,5] <- round(t_test(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
-table1_tab_anx[30,6] <- round(cohens_d(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-# RDQ Sense of Wellbeing post scores
-table1_tab_anx[31,5] <- round(t_test(rdqPOST_wbs ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
-table1_tab_anx[31,6] <- round(cohens_d(rdqPOST_wbs ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-
-table1_tab_anx[,2:7] <- table1_tab_anx
-table1_tab_anx[,1] <- rownames(table1_tab_anx)
-colnames(table1_tab_anx) <- c("Variables",colnames(table1_tab_anx)[1:6])
-
-table1_tab_anx
-
-write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
-```
-
-```{r}
+### next gather info based upon depression
+
 ## Vector of variables to summarize
-table1_vars_dep <- c(colnames(Mothership_lasso_dep)[-1:-2])
-table1_vars_dep <- table1_vars_dep[1:27]
-
+table1_vars_dep <- c(colnames(Vars_dep)[-1])
+
+## Vector of categorical variables that need transformation
+catVars <- c("Some_College", "Female" , "Married", "White",
+             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D",        
+             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
+             "Substance_C", "Other_C" , "No_Co"
+             )
 ## Create a TableOne object
-table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso_dep,strata ="Depression_Responder",  factorVars = catVars, addOverall = T)
+table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Vars_dep,strata ="Depression_Responder",  factorVars = catVars)
 table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
 table1_tab_dep <-data.frame(table1_tab_dep)
-
-# add discriptive statistics 
-table1_tab_dep$ef_size = c("")
-
+write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")
 table1_tab_dep
 
-# age
-table1_tab_dep[2,5] <- round(t_test(Age_1 ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
-table1_tab_dep[2,6] <- round(cohens_d(Age_1 ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-# Some College 
-table1_tab_dep[3,5] <- round(chisq.test(Mothership_lasso_dep$Some_College, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[3,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Some_College))$estimate,2)
-# Female
-table1_tab_dep[4,5] <- round(chisq.test(Mothership_lasso_dep$Female, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[4,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Female))$estimate,2)
-# Married
-table1_tab_dep[5,5] <- round(chisq.test(Mothership_lasso_dep$Married, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[5,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Married))$estimate,2)
-# White
-table1_tab_dep[6,5] <- round(chisq.test(Mothership_lasso_dep$White, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[6,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$White))$estimate,2)
-# Treatment track
-table1_tab_dep[7,5] <- round(chisq.test(Mothership_lasso_dep$IPT_track_1, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-OR_IPT_dep <- table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$IPT_track_1)
-# OR general vs Trauma track
-table1_tab_dep[9,5] <- round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Trauma"]))$estimate,2)
-table1_tab_dep[9,6] <-
-round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Trauma"]))$p,2)
-# OR General vs Young adult track 
-table1_tab_dep[10,5] <- 
-  round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Young Adult"]))$estimate,2)
-table1_tab_dep[10,6] <-
-round(fisher.test(cbind(OR_IPT_dep[,"General"],OR_IPT_dep[,"Young Adult"]))$p,2)
-# Days Completed in program
-table1_tab_dep[11,5] <- round(t_test(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
-table1_tab_dep[11,6] <- round(cohens_d(Days_complete_1 ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-# Days not attending treatment
-table1_tab_dep[12,5] <- round(t_test(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
-table1_tab_dep[12,6] <- round(cohens_d(Days_not_attended_1 ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-# Anxiety disorder
-table1_tab_dep[13,5] <- round(chisq.test(Mothership_lasso_dep$Anxiety_D, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[13,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Anxiety_D))$estimate,2)
-# Mood Disorders
-table1_tab_dep[14,5] <- round(chisq.test(Mothership_lasso_dep$Mood_D, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[14,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Mood_D))$estimate,2)
-# BPD 
-table1_tab_dep[15,5] <- round(chisq.test(Mothership_lasso_dep$BPD_P, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[15,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$BPD_P))$estimate,2)
-# Truama Related Disorders
-table1_tab_dep[16,5] <- round(chisq.test(Mothership_lasso_dep$Trauma_D, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[16,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Trauma_D))$estimate,2)
-# Other Disorders
-table1_tab_dep[17,5] <- round(chisq.test(Mothership_lasso_dep$Other, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[17,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Other))$estimate,2)
-# Co-occurring anxiety disorder 
-table1_tab_dep[18,5] <- round(chisq.test(Mothership_lasso_dep$Anxiety_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[18,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Anxiety_C))$estimate,2)
-# Co-occurring mood disorder
-table1_tab_dep[19,5] <- round(chisq.test(Mothership_lasso_dep$Mood_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[19,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Mood_C))$estimate,2)
-# Co-occurring BPD
-table1_tab_dep[20,5] <- round(chisq.test(Mothership_lasso_dep$BPD_Co_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[20,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$BPD_Co_C))$estimate,2)
-# Co-occurring Trauma Related Disorder
-table1_tab_dep[21,5] <- round(chisq.test(Mothership_lasso_dep$Trauma_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[21,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Trauma_C))$estimate,2)
-# Co-occurring Substance Use Disorders
-table1_tab_dep[22,5] <- round(chisq.test(Mothership_lasso_dep$Substance_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[22,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Substance_C))$estimate,2)
-# Co-occurring Other Disroders
-table1_tab_dep[23,5] <- round(chisq.test(Mothership_lasso_dep$Other_C, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[23,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$Other_C))$estimate,2)
-# No Co-occurring Disorders
-table1_tab_dep[24,5] <- round(chisq.test(Mothership_lasso_dep$No_Co, Mothership_lasso_dep$Depression_Responder)$statistic,2)
-table1_tab_dep[24,6] <- round(fisher.test(table(Mothership_lasso_dep$Depression_Responder,Mothership_lasso_dep$No_Co))$estimate,2)
-# Number of Current diagnoses 
-table1_tab_dep[25,5] <- round(t_test(Current_Dx ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
-table1_tab_dep[25,6] <- round(cohens_d(Current_Dx ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-# CUDOS Pre scores
-table1_tab_dep[26,5] <- round(t_test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
-table1_tab_dep[26,6] <- round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-# CUXOS Pre scores
-table1_tab_dep[27,5] <- round(t_test(CUXOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
-table1_tab_dep[27,6] <- round(cohens_d(CUXOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-# RDQ Coping post scores
-table1_tab_dep[28,5] <- round(t_test(rdqPOST_coping ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
-table1_tab_dep[28,6] <- round(cohens_d(rdqPOST_coping ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-# RDQ Positive Mental Health post scores
-table1_tab_dep[29,5] <- round(t_test(rdqPOST_pmh ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
-table1_tab_dep[29,6] <- round(cohens_d(rdqPOST_pmh ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-# RDQ Functioning post scores
-table1_tab_dep[30,5] <- round(t_test(rdqPOST_func ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
-table1_tab_dep[30,6] <- round(cohens_d(rdqPOST_func ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-# RDQ Sense of Wellbeing post scores
-table1_tab_dep[31,5] <- round(t_test(rdqPOST_wbs ~ Depression_Responder, data = Mothership_lasso_dep)$statistic,2)
-table1_tab_dep[31,6] <- round(cohens_d(rdqPOST_wbs ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-
-table1_tab_dep[,2:7] <- table1_tab_dep
-table1_tab_dep[,1] <- rownames(table1_tab_dep)
-colnames(table1_tab_dep) <- c("Variables",colnames(table1_tab_dep)[1:6])
-
-table1_tab_dep
-write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")
-
-```
-
-Means and SDs of post scores
-```{r}
-
-mean(Mothership_lasso_anx$CUXOS_post)
-sd(Mothership_lasso_anx$CUXOS_post)
-
-mean(Mothership_lasso_dep$CUDOS_post)
-sd(Mothership_lasso_dep$CUDOS_post)
+## lastly get the overal treatment breakdown
+table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso,  factorVars = catVars)
+table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
+table1_gen <-data.frame(table1_gen)
+write_csv(table1_gen,"~/Downloads/table1_gen.csv")
+table1_gen
 
@@
     #make df
-      anx_rep_tab <- Mothership_lasso_anx |>
+      anx_rep_tab <- Mothership_lasso |>
         group_by(Anxiety_Responder) |>
@@
   #Make df
-    dep_rep_tab <- Mothership_lasso_dep |>
+    dep_rep_tab <- Mothership_lasso |>
       group_by(Depression_Responder) |>
@@
 ```
-## Part 2: RCI ANALYSIS - Treatment Response
-Anxiety & Depression = Total response
-- Table 4: RCI Analsyis results
-  + Anxiety, Depression, Total response
-- Figure 2 / Supplimetal 2: RCI Analysis figs 
-  + Anxeity & Depression
-
-Table 3
-```{r}
-# RCI_table
-
-# JT Table
-JT_table <- data.frame(matrix(NA,nrow = 3,ncol = 6))
-colnames(JT_table) = c("Instrument","Responder","Non-Responder", "Mean Pre Score", "RCI","JT Criterion A")
-#discriptor row
-
-JT_table[1,] = c(NA,"n","n", "M (SD)",NA,NA)
-summary(Mothership_lasso_anx$Anxiety_Responder)[[1]]
-
-#Anxiety
-JT_table[2,] = c("CUXOS", 
-                 summary(Mothership_lasso_anx$Anxiety_Responder)[[1]],
-                 summary(Mothership_lasso_anx$Anxiety_Responder)[[2]],
-                 paste0(round(mean(Mothership_lasso_anx$CUXOS_pre),2), " (", 
-                        round(sd(Mothership_lasso_anx$CUXOS_pre),2),")"),
-                 13,
-                 21)
-
-summary(Mothership_lasso_anx$Anxiety_Responder)[2]
-
-# Depresssion
-JT_table[3,] = c("CUDOS", 
-                 summary(Mothership_lasso_dep$Depression_Responder)[[1]],             
-                 summary(Mothership_lasso_dep$Depression_Responder)[[2]],
-                 paste0(round(mean(Mothership_lasso_dep$CUDOS_pre),2), " (", 
-                        round(sd(Mothership_lasso_dep$CUDOS_pre),2),")"),
-                 21,
-                 17)
-
-JT_table
-```
-
-###table 4A
-Between Group Differences of Anxiety at Pre and Post Timepoints by Anxiety Treatment Response
-```{r}
-#table set up
-tab4 <- data.frame(matrix(NA,nrow = 5,ncol = 5))
-colnames(tab4) = c("Instrument","Responder","Non-Responder", "Test Score", "Effect Size")
-tab4[1,] = c(NA,"M (SD)", "M (SD)", "t", "d")
-
-#anxiety
-
-t.test_pre_anx  <- t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)
-t.test_post_anx <- t.test(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)
-
-t.test_pre_dep  <- t.test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)
-t.test_post_dep <- t.test(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)
-
-##mean
-t.test_pre_anx$estimate[[1]]
-
-t.test_pre_anx$statistic[[1]]
-
-#CUXOS PRE
-tab4[2,] = c(
-  "CUXOS Pre",
-  #Responder
-  paste0(round(t.test_pre_anx$estimate[[1]],2)," (",
-         round(sd(subset(Mothership_lasso_anx,
-                         Anxiety_Responder == "Responder")$CUXOS_pre),2),
-         ")"),
-  #non-responder
-  paste0(round(t.test_pre_anx$estimate[[2]],2)," (",
-         round(sd(subset(Mothership_lasso_anx,
-                         Anxiety_Responder == "Non-Responder")$CUXOS_pre),2),
-         ")"),
-  #t-stat
-  round(t.test_pre_anx$statistic[[1]],2),
-  #effect size
-  round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-    )
-
-#CUXOS Post
-tab4[3,] = c(
-  "CUXOS Post",
-  #Responder
-  paste0(round(t.test_post_anx$estimate[[1]],2)," (",
-         round(sd(subset(Mothership_lasso_anx,
-                         Anxiety_Responder == "Responder")$CUXOS_post),2),
-         ")"),
-  #non-responder
-  paste0(round(t.test_post_anx$estimate[[2]],2)," (",
-         round(sd(subset(Mothership_lasso_anx,
-                         Anxiety_Responder == "Non-Responder")$CUXOS_post),2),
-         ")"),
-  #t-stat
-  round(t.test_post_anx$statistic[[1]],2),
-  #effect size
-  round(cohens_d(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-    )
-
-#CUDOS PRE
-tab4[4,] = c(
-  "CUDOS Pre",
-  #Responder
-  paste0(round(t.test_pre_dep$estimate[[1]],2)," (",
-         round(sd(subset(Mothership_lasso_dep,
-                         Depression_Responder == "Responder")$CUDOS_pre),2),
-         ")"),
-  #non-responder
-  paste0(round(t.test_pre_dep$estimate[[2]],2)," (",
-         round(sd(subset(Mothership_lasso_dep,
-                         Depression_Responder == "Non-Responder")$CUDOS_pre),2),
-         ")"),
-  #t-stat
-  round(t.test_pre_dep$statistic[[1]],2),
-  #effect size
-  round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-    )
-
-#CUDOS Post
-tab4[5,] = c(
-  "CUDOS Post",
-  #Responder
-  paste0(round(t.test_post_dep$estimate[[1]],2)," (",
-         round(sd(subset(Mothership_lasso_dep,
-                         Depression_Responder == "Responder")$CUDOS_post),2),
-         ")"),
-  #non-responder
-  paste0(round(t.test_post_dep$estimate[[2]],2)," (",
-         round(sd(subset(Mothership_lasso_dep,
-                         Depression_Responder == "Non-Responder")$CUDOS_post),2),
-         ")"),
-  #t-stat
-  round(t.test_post_dep$statistic[[1]],2),
-  #effect size
-  round(cohens_d(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-    )
-
-tab4
-```
-
-T tests
-```{r}
-# t test scores for differences pre post, between and within groups. 
-Pre_Post_t_Scores <- c("")
-
-#1. Pre post score differences of anxeity and depression by treatment response:
-  #1.1 depression responders   
-    t.test(subset(Mothership_lasso_dep,Depression_Responder == "Responder")$CUDOS_pre,
-       subset(Mothership_lasso_dep,Depression_Responder == "Responder")$CUDOS_post,
-       paired = TRUE, alternative = "two.sided"
-       )
-  #1.2 depression non-responders   
-     t.test(subset(Mothership_lasso_dep,Depression_Responder == "Non-Responder")$CUDOS_pre,
-       subset(Mothership_lasso_dep,Depression_Responder == "Non-Responder")$CUDOS_post,
-       paired = TRUE, alternative = "two.sided"
-       )
-  #1.3 anxiety responders   
-    t.test(subset(Mothership_lasso_anx,Anxiety_Responder == "Responder")$CUXOS_pre,
-       subset(Mothership_lasso_anx,Anxiety_Responder == "Responder")$CUXOS_post,
-       paired = TRUE, alternative = "two.sided"
-       )
-  #1.2 anxiety non-responders   
-     t.test(subset(Mothership_lasso_anx,Anxiety_Responder == "Non-Responder")$CUXOS_pre,
-       subset(Mothership_lasso_anx,Anxiety_Responder == "Non-Responder")$CUXOS_post,
-       paired = TRUE, alternative = "two.sided"
-       )
-#So, Non-responders and responders have lower post scores than pre scores for anxiety and depression.
-
-#2. Differences between group differences for pre and post scores of anxiety and depression.
-  #2.1 Pre scores of anxiety
-     t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)
-     round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-  #2.2 Post scores of anxiety
-     t.test(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)
-     sd(subset(Mothership_lasso_anx,Anxiety_Responder == "Responder")$CUXOS_post)
-     sd(subset(Mothership_lasso_anx,Anxiety_Responder == "Non-Responder")$CUXOS_post)
-     round(cohens_d(CUXOS_post ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)
-  #2.3 Pre scores of depression
-     t.test(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)
-     round(cohens_d(CUDOS_pre ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-  #2.4 Post scores of depression
-     t.test(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)
-     sd(subset(Mothership_lasso_dep,Depression_Responder == "Responder")$CUDOS_post)
-     sd(subset(Mothership_lasso_dep,Depression_Responder == "Non-Responder")$CUDOS_post)
-     round(cohens_d(CUDOS_post ~ Depression_Responder, data = Mothership_lasso_dep)$effsize,2)
-
-  test1  <- t.test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)
-
-test1$estimate[[1]] #responder pre cuxos mean
-
-```
-
-```{r}
-
-```
-
-ataset visualizatoin
-```{r}
-# #install.packages("ggdist")
-# library("ggdist")
-# 
-# Mothership_lasso |> 
-#   ggplot( aes(x=Depression_Responder, y=CUDOS_pre, fill=Depression_Responder)) +
-#     geom_boxplot() +
-#    #viridis::scale_fill_viridis(discrete = TRUE, alpha=0.6) +
-#     geom_jitter(color="black", size=.6 , alpha=0.9) +
-#     theme(
-#       legend.position="none",
-#       plot.title = element_text(size=11)
-#     ) +
-# #    ggtitle("Pre scores of depression severity") +
-#     xlab("Depression Severity") +
-#     ylim(0,80)
-# 
-# Mothership_lasso|>
-# ggplot( mapping=aes(x=Trauma_C)) +
-#   geom_bar()
-# 
-# Mothership_lasso|>
-# ggplot( mapping=aes(x= Current_Dx)) +
-#         geom_histogram() +
-#     theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
-#   theme(panel.background=NULL)+
-#   theme(legend.title = element_blank()) 
-#
-
-```
-
-Take away form this is:
-1. Non-responders and responders have lower post scores than pre scores for anxiety and depression.
-2. There are no statistically significant differences in pre scores of anxiety or depression between responders and non-responders
-3. There are significantly lower scores of anxiety and depression between responders and non-responder.
 
@@
 
-anx_prepost
-
 #3. Combine dataset
@@
 #4. Plot pre post scores by treatment response
-ggplot(data=AnxDep_fig_response,
+pre_post_plot<- ggplot(data=AnxDep_fig_response,
        aes(x=factor(PrePost,level=c("Pre","Post")),y=Score,
@@
   scale_y_continuous(name="CUDOS/CUXOS Score")+
-  ggtitle("Mean Pre and Post Scores of Anxiety and Depression")+
+  #ggtitle("Mean Pre and Post Scores of Anxiety and Depression")+
   theme(panel.grid.major.y = element_line(color = "grey",size = 0.5,linetype = 2))+
@@
   facet_wrap(~Responder)
+
+pre_post_plot
 ```
@@
 ```{r}
-
-Mothership_lasso_anx
-
-# # Disorders by treatment response
-# Dis_tab <- data.frame(table1::table1(~Disorder_treat + Current_Dx | Anxiety_Responder, 
-#                                      data = Mothership_lasso_joined))
-# colnames(Dis_tab) = c("Variables","Anxiety Non Responder", "Anxiety Responder", "Total")
-# 
-# Dis_tab1 <- data.frame(table1::table1(~Disorder_treat + Current_Dx | Depression_Responder, 
-#                                      data = Mothership_lasso))
-# colnames(Dis_tab1) = c("Variables","Depression Non Responder", "Depression Responder", "Total")
-# Dis_tab <- cbind(Dis_tab1[,1:3],Dis_tab[,2:4])
-# Dis_tab
+# Disorders by treatment response
+Dis_tab <- data.frame(table1::table1(~Disorder_Type + Current_Dx | Anxiety_Responder, 
+                                     data = Mothership_lasso))
+colnames(Dis_tab) = c("Variables","Anxiety Non Responder", "Anxiety Responder", "Total")
+
+Dis_tab1 <- data.frame(table1::table1(~Disorder_Type + Current_Dx | Depression_Responder, 
+                                     data = Mothership_lasso))
+colnames(Dis_tab1) = c("Variables","Depression Non Responder", "Depression Responder", "Total")
+Dis_tab <- cbind(Dis_tab1[,1:3],Dis_tab[,2:4])
+Dis_tab
 
@@
 
-co_dis_tab <- Mothership_lasso_joined |>
+co_dis_tab <- Mothership_lasso |>
+  filter(
+      !is.na(rdq_func_change),
+      !is.na(rdq_pmh_change),
+      !is.na(rdq_coping_change),
+      !is.na(rdq_wbs_change)
+  ) |>
   pivot_longer(
@@
 ```{r}
-# 
-# Vars_dep <- Mothership_lasso |>
+# Vars_dep <- Mothership_post |>
 #   select( c(
-#     Depression_Responder,
 #     # Demographics
@@
 #     # Disorders
-#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Other,
+#     Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
 #     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
 #     # RDQ
-#     rdqPOST_coping:rdqPOST_wbs  
+#     rdq_coping_change:rdq_wbs_change
 #   ))
 # 
-# Vars_anx <- Mothership_lasso |>
+# str(Vars_dep)
+# 
+# Vars_anx <- Mothership_post |>
 #   select( c(
@@
 #     # RDQ
-#     rdqPOST_coping:rdqPOST_wbs  
+#     rdq_coping_change:rdq_wbs_change
 #   ))
 
-#Make a correlation table???
+Vars_FULL <- na.omit(Vars_dep)
 
 # install.packages("ggcorrplot")
-# library(ggcorrplot)
-# model.matrix(~0+., data=Mothership_lasso) %>% 
-#   cor(use="pairwise.complete.obs") %>% 
-#   ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
+library(ggcorrplot)
+model.matrix(~0+., data=Vars_dep) %>% 
+  cor(use="pairwise.complete.obs") %>% 
+  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
+
+model.matrix(~0+., data=Vars_anx) %>% 
+  cor(use="pairwise.complete.obs") %>% 
+  ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
+
+```
+
+## Part 2: RCI ANALYSIS - Treatment Response
+Anxiety & Depression = Total response
+- Table 4: RCI Analsyis results
+  + Anxiety, Depression, Total response
+- Figure 2 / Supplimetal 2: RCI Analysis figs 
+  + Anxeity & Depression
+```{r}
+# RCI STUFF
+# RCI_table <- data.frame(matrix(NA,nrow = 3,ncol = 3))
+# colnames(RCI_table) = c("Varaibles","Responder","Non-Responder")
+# #anxiety 
 # 
-# model.matrix(~0+., data=Vars_anx) %>% 
-#   cor(use="pairwise.complete.obs") %>% 
-#   ggcorrplot(show.diag=FALSE, type="lower", lab=TRUE, lab_size=2)
-
+# RCI_table[,1] = c("CUXOS", unlist(summary(Mothership_lasso$Anxiety_Responder)))
+# # Depresssion
+# RCI_table[,2] = c("CUDOS", unlist(summary(Mothership_lasso$Depression_Responder)))
+# # #Total
+# # RCI_table[3,] = c("Either", unlist(summary(Mothership_post$RESPONDER_FIGS))[2],unlist(summary(Mothership_post$RESPONDER_FIGS))[1])
+# 
+# RCI_table
+
+# JT Table
+JT_table <- data.frame(matrix(NA,nrow = 2,ncol = 3))
+colnames(JT_table) = c("Varaibles","Responder","Non-Responder")
+#anxiety
+
+JT_table[1,] = c("CUXOS", unlist(summary(Vars_anx$Anxiety_Responder)))
+# Depresssion
+JT_table[2,] = c("CUDOS", unlist(summary(Vars_dep$Depression_Responder)))
+
+JT_table
 ```
@@
 ```{r}
+Mothership_lasso_dep <- Mothership_lasso |>
+    filter(
+    !is.na(Some_College),
+    !is.na(Female),
+    !is.na(IPT_track_1),
+    !is.na(White),
+    !is.na(Depression_Responder)
+  )
 
@@
     # Demographics
-    Age_1,Some_College:Married,White, #Discharge,
+    Age_1,Some_College:Married,White, 
     # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    IPT_track_1, Days_complete_1, Days_not_attended_1, 
     # Disorders
-    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, #Substance_D, #Psychotic_D,  
+    #Other,
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
     # Pre-Post stuff
-    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
+    CUDOS_pre,CUXOS_pre,
     # RDQ
-    #rdqPRE_coping:rdqPRE_wbs,
-    #For table 3 - RCI info
-    CUXOS_pre,CUDOS_pre, 
-    #ACT stuff
-    # AAQIIpre, AAQIIpost,
-    #  Desc_Ex_pre, Non_react_pre, Observe_inner_pre, Self_compasion_pre, 
-    # Acting_mindful_pre, 
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post,
+    rdqPOST_coping:rdqPOST_wbs
   ))
+
+summary(Vars_dep$Depression_Responder)
+
+# old model
+# Anxiety_D, Mood_D, BPD_P,    Trauma_D,  Other,
+#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
+#     Current_Dx,
 
@@
 #Simplified lasso
-lasso1_dep <- glmnet(x.dep, y.dep,family = "binomial", alpha = 1, lambda = NULL,standardize =  TRUE)
+lasso1_dep <- glmnet(x.dep, y.dep,family = "binomial", alpha = 1, lambda = NULL)
 plot(lasso1_dep, "lambda", label = TRUE)
@@
 set.seed(123) 
-cv.lasso.dep <- cv.glmnet(x.dep, y.dep, alpha = 1, family = "binomial",standardize = TRUE)
+cv.lasso.dep <- cv.glmnet(x.dep, y.dep, alpha = 1, family = "binomial")
 
@@
 model.min <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
-                lambda = cv.lasso.dep$lambda.min,standardize = TRUE)
-
-#####  CHECK THIS OUT?????????
+                lambda = cv.lasso.dep$lambda.min)
 
@@
 x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
-probabilities <- model.min %>% predict(newx = x.test,"response")
+probabilities <- model.min %>% predict(newx = x.test)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 #Using lambda.min as the best lambda, gives the following regression coefficients:
-#coef(cv.lasso.dep, cv.lasso.dep$lambda.min)
+coef(cv.lasso.dep, cv.lasso.dep$lambda.min)
 
 #Using lambda.1se as the best lambda, gives the following regression coefficients:
-#coef(cv.lasso.dep, cv.lasso.dep$lambda.1se)
+coef(cv.lasso.dep, cv.lasso.dep$lambda.1se)
 ```
@@
 lasso.model.min.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
-                      lambda = cv.lasso.dep$lambda.min, standardized = TRUE)
+                      lambda = cv.lasso.dep$lambda.min)
 
@@
 x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
-probabilities <- lasso.model.min.dep %>% predict(newx = x.test,type ="response")
+probabilities <- lasso.model.min.dep %>% predict(newx = x.test)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 lasso.model.1se.dep <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
-                      lambda = cv.lasso.dep$lambda.1se,standardized = TRUE)
+                      lambda = cv.lasso.dep$lambda.1se)
 coef(lasso.model.1se.dep)
@@
 x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
-probabilities <- lasso.model.1se.dep %>% predict(newx = x.test,type ="response")
+probabilities <- lasso.model.1se.dep %>% predict(newx = x.test)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 ## install.packages("fuzzySim")
-
-tmp_coeffs <- coef(lasso.model.min.dep, s = "lambda.min")
-Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
-Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
-Dep_reg_coefs
-```
-
-```{r}
-# # min model - old
-# glm_min_dep <-
-#           glm(
-#     #Outcome varaible
-#       Depression_Responder ~
-#     # predictors
-#       Age_1  + Some_College + Married + IPT_track_1 +
-#       Days_complete_1 + Days_not_attended_1 + Anxiety_D + Trauma_D +
-#       Trauma_C + Substance_C +
-#       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
-#     #data
-#       data = Vars_dep,
-#     # type of regression : logistic = binary / binomial
-#       family = "binomial",
-#     )
-
-# min model - post AAQII no Mindful stuff
+library(fuzzySim) ## For FDR adjusted p values
+library(broom) # for tidy regression output
+```
+
+```{r}
+## min model
   glm_min_dep <-
@@
       # predictors
-Days_not_attended_1 + Anxiety_C + BPD_Co_C + Current_Dx + 
-  CUXOS_pre +  Non_react_post + 
-  Self_compasion_post + Acting_mindful_post,
+        Days_complete_1 + Days_not_attended_1 + Mood_C + CUDOS_pre +
+        CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
       # type of regression : logistic = binary / binomial
-      family = "binomial",
-    )
-
-# min model - pre/post
-# glm_min_dep <-
+        family = "binomial")
+
+####### JT - substance disorder seperate    
   # glm(
@@
   #     # predictors
-#       White  +  Days_not_attended_1 + Anxiety_C + Current_Dx + CUXOS_pre +
-#       Non_react_post + AAQIIpost + Acting_mindful_post,
+  #       Age_1 + Some_College + Married + White + Days_complete_1 +  
+  #       Mood_D + Substance_D + Mood_C + Substance_C + CUDOS_pre + 
+  #       CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
   #     #data
@@
   #     # type of regression : logistic = binary / binomial
-#       family = "binomial",
-#     )
-
-# install.packages("rempsyc")
+  #       family = "binomial")
+
+###### JT + substance in other
+      # glm(
+      # #Outcome varaible
+      #   Depression_Responder ~
+      # # predictors
+      #   Days_complete_1 + Days_not_attended_1 + Other + Mood_C + CUDOS_pre +
+      #   CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+      # #data
+      #   data = Vars_dep,
+      # # type of regression : logistic = binary / binomial
+      #   family = "binomial")
+##############
 
@@
   tidy.summary.min.dep <- tidy(glm_min_dep)
-  tidy.summary.min.dep
+
 # Coefficients
@@
    R2.min.dep <- performance::r2(glm_min_dep)
-  R2.min.dep
-
-  #wald
-   library(aod)
-   # wald.test(b = coef(glm_min_dep),Sigma = vcov(glm_min_dep),Terms= 2:13)
 
@@
 ```{r}
-tmp_coeffs <- coef(lasso.model.1se.dep, s = "lambda.1se")
-Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
-Dep_reg_coefs <- Dep_coefs[2:length(Dep_coefs)]
-Dep_reg_coefs
 
@@
 # Coefficients
-  coefs.1se.dep <- round(abs(coef(glm_1se_dep)),2)
+  coefs.1se.dep <- abs(coef(glm_1se_dep))
 
 # Odds ratio
-  OR.1se.dep <- round(exp(coef(glm_1se_dep)),2)
+  OR.1se.dep <- exp(coef(glm_1se_dep))
 
 # OR 95% CI
-  CI.1se.dep <- round(data.frame(exp(confint(glm_1se_dep))),2)
+  CI.1se.dep <- data.frame(exp(confint(glm_1se_dep)))
 
@@
 FP.1se.dep <- left_join(FP.1se.dep,ADJ.p.values.1se.dep, by = join_by(p.values == p.value))
-FP.1se.dep$p.adjusted <- round(FP.1se.dep$p.adjusted,2)
 FP.1se.dep$type = c("Depression")
 FP.1se.dep
-
-write_csv(FP.1se.dep, "~/Downloads/FP.1se.dep")
 ```
@@
 ```{r}
+Mothership_lasso_anx <- Mothership_lasso |>
+    filter(
+    !is.na(Some_College),
+    !is.na(Female),
+    !is.na(IPT_track_1),
+    !is.na(White),
+    !is.na(Anxiety_Responder)
+  )
 
@@
     # Demographics
-    Age_1,Some_College:Married,White, #Discharge,
+    Age_1,Some_College:Married,White, 
     # Treatment info
-    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
+    IPT_track_1, Days_complete_1, Days_not_attended_1, 
     # Disorders
-    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
+    Anxiety_D, Mood_D, BPD_P,    Trauma_D, 
     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
@@
     # RDQ
-    #rdqPRE_coping:rdqPRE_wbs,
-    #For table 3 - RCI info
-    CUXOS_pre,CUDOS_pre, 
-    #ACT stuff
-    Desc_Ex_post, Non_react_post, Observe_inner_post, Self_compasion_post,
-    Acting_mindful_post,
+    rdqPOST_coping:rdqPOST_wbs
   ))
@@
 #Simplified lasso
-lasso1_anx <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL, standardize = TRUE)
+lasso1_anx <- glmnet(x, y,family = "binomial", alpha = 1, lambda = NULL)
 plot(lasso1_anx, "lambda", label = TRUE)
@@
 set.seed(123) 
-cv.lasso.anx <- cv.glmnet(x, y, alpha = 1, family = "binomial",standardize = TRUE)
+cv.lasso.anx <- cv.glmnet(x, y, alpha = 1, family = "binomial")
 
@@
 model <- glmnet(x, y, alpha = 1, family = "binomial",
-                lambda = cv.lasso.anx$lambda.min, standardized = TRUE)
+                lambda = cv.lasso.anx$lambda.min)
 # Display regression coefficients
@@
 x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
-probabilities <- model %>% predict(newx = x.test,type = "response")
+probabilities <- model %>% predict(newx = x.test)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 #Using lambda.min as the best lambda, gives the following regression coefficients:
-#coef(cv.lasso.anx, cv.lasso.anx$lambda.min)
+coef(cv.lasso.anx, cv.lasso.anx$lambda.min)
 
 #Using lambda.1se as the best lambda, gives the following regression coefficients:
-#coef(cv.lasso.anx, cv.lasso.anx$lambda.1se)
+coef(cv.lasso.anx, cv.lasso.anx$lambda.1se)
 ```
@@
 lasso.model.min.anx <- glmnet(x, y, alpha = 1, family = "binomial",
-                      lambda = cv.lasso.anx$lambda.min, standardized = TRUE)
+                      lambda = cv.lasso.anx$lambda.min)
 
@@
 x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
-probabilities <- lasso.model.min.anx %>% predict(newx = x.test,)
+probabilities <- lasso.model.min.anx %>% predict(newx = x.test)
 predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
@@
 lasso.model.1se.anx <- glmnet(x, y, alpha = 1, family = "binomial",
-                      lambda = cv.lasso.anx$lambda.1se,
-                      standardized = TRUE)
+                      lambda = cv.lasso.anx$lambda.1se)
 coef(lasso.model.1se.anx)
@@
 
-tmp_coeffs <- coef(lasso.model.min.anx, s = "lambda.min")
-Anx_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
-Anx_reg_coefs <- Anx_coefs[2:length(Anx_coefs)]
-Anx_reg_coefs
-```
-
-```{r}
+# Some_College + Married + White + Days_complete_1 + Days_not_attended_1 + 
+#         Anxiety_D + Other + Mood_C + BPD_Co_C + Substance_C + Trauma_C + Current_Dx +
+#         CUDOS_pre + CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
+
 ## min model
@@
       # predictors
-        Age_1 + Some_College + Female + Married + White + Days_not_attended_1 + 
-        BPD_Co_C + CUXOS_pre +  
-        Non_react_post+  Self_compasion_post + Acting_mindful_post,
+        Age_1 + Married + Days_complete_1 + Days_not_attended_1 +
+        Anxiety_D + Trauma_D +  BPD_Co_C + 
+        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
       #data
@@
 
+####### JT - wo/Substance_D
+  # glm_min_anx <-  
+  #     glm(
+  #     #Outcome varaible
+  #       Anxiety_Responder ~ 
+  #     # predictors
+  #       Age_1 + Married + Days_complete_1 + Days_not_attended_1 + 
+  #       Anxiety_D + Trauma_D + BPD_Co_C +
+  #       rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+  #     #data
+  #     data = Vars_anx, 
+  #     # type of regression : logistic = binary / binomial
+  #     family = "binomial")
 # Summary of the model
   summary.min.anx      <- summary(glm_min_anx)
-  summary.min.anx
 
@@
    R2.min.anx <- performance::r2(glm_min_anx)
-   R2.min.anx
-
-#wald
-   library(aod)
-   wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:12)
 
@@
 write_csv(FP.min.anx, "~/Downloads/FP.min.anx")
+
 ```
@@
 ```{r}
-tmp_coeffs <- coef(lasso.model.1se.anx, s = "lambda.1se")
-Anx_coefs2 <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
-Anx_reg_coefs2 <- Anx_coefs[2:length(Anx_coefs)]
-Anx_reg_coefs2
 
@@
       # predictors
-         Days_not_attended_1 + rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
+        Days_not_attended_1 + CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_wbs,
       #data
@@
 # Coefficients
-  coefs.1se.anx <- round(abs(coef(glm_1se_anx)),3)
+  coefs.1se.anx <- abs(coef(glm_1se_anx))
 
 # Odds ratio
-  OR.1se.anx <- round(exp(coef(glm_1se_anx)),3)
+  OR.1se.anx <- exp(coef(glm_1se_anx))
 
@@
   CI.1se.anx <- data.frame(exp(confint(glm_1se_anx)))
-  CI.1se.anx[,1] = round(CI.1se.anx[,1],3)
-  CI.1se.anx[,2] = round(CI.1se.anx[,2],3)
 
@@
 FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
-FP.1se.anx$p.values = round(as.numeric(FP.1se.anx$p.values),3)
-FP.1se.anx$p.adjusted = round(as.numeric(FP.1se.anx$p.adjusted),3)
 FP.1se.anx$type = c("Anxiety")
 FP.1se.anx
-
-write_csv(FP.1se.anx, "~/Downloads/FP.1se.anx")
 ```
@@
 FP_anx <- read_csv("~/Downloads/FP.min.anx")
-# FP_anx <- read_csv("~/Downloads/FP.1se.anx")
 
 #Change the names of variables
-# FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
-#                     "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
-#                     "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
-#                     "Co-SUD", "CUXOS Pre", "Post Coping", 
-#                     "Post PMH", "Post Functioning", "Post Wellbeing")
+FP_anx$Variable
 
@@
   )
-```
-
-```{r}
+FP_anx
+
+FP_anx$Variable = c(
+                    "Age", "Married", "Days Completed", "Days Not Attended", 
+                    "Anxiety Disorder", "Trauma Disorder", "Co-Occuring BPD",
+                    "Coping Ability", "Positive Mental Health", "Functioning", 
+                    "Sense of Well Being"
+                    )
+
 FP_anx_m <- FP_anx |>
@@
                #                        1), # uncolored ones for insignificant varaibles
-             size=3.5,show.legend = FALSE) +
+             size=4,show.legend = FALSE) +
   geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
-  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.5, show.legend = FALSE)+
+  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
   scale_color_manual(values = c("darkgrey","red"))+
@@
   #adjust the dimentions. 
-  coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
-                  xlim = c(.25,3.0)) +
+  coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1)) +
   #add a line at 1 for reference 
@@
   #add anotations to help suggests what each side means.
-  annotate("text", x = .6, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
-  annotate("text", x = 1.5, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
+  annotate("text", x = .75, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
+  annotate("text", x = 1.25, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
   #Git rid of the Y - Axis
@@
 layout <- c(
-  patchwork::area(t = 0, l = 0, b = 30, r = 35),
-  patchwork::area(t = 0, l = 19, b = 30, r = 30),
-  patchwork::area(t = 0, l = 30, b = 30, r = 40) 
+  patchwork::area(t = 0, l = 0, b = 30, r = 30),
+  patchwork::area(t = 0, l = 15, b = 30, r = 25),
+  patchwork::area(t = 0, l = 22, b = 30, r = 30) 
   )
@@
 #rename the variables for the figure
-
-# FP_dep$Variable = c(
-#                      "Days Not Attended",
-#                     "Post Coping", 
-#                     "Post PMH", "Post Functioning", "Post Wellbeing")
+FP_dep$Variable = c(
+                    "Days Completed", "Days Not Attended", 
+                    "Co-Ocurring Mood Disorder", "CUXOS Pre-Score", "CUDOS Pre-Score",
+                    "Coping Ability", "Positive Mental Health", "Functioning", 
+                    "Sense of Well Being"
+                    )
 
@@
   )
+FP_dep
 
@@
   #adjust the dimentions. 
-  coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1),
-                  xlim = c(.5,2.0)) +
+  coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1)) +
   #add a line at 1 for reference 
@@
   #add anotations to help suggests what each side means.
-  annotate("text", x = .75, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
-  annotate("text", x = 1.25, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
+  annotate("text", x = .8, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
+  annotate("text", x = 1.2, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
   #Git rid of the Y - Axis

### 2024-06-30 Lasso_RCI_Response.Rmd
Made JT plots manually

--- 2024-06-25 Lasso_RCI_Response.Rmd
@@
 ```{r}
-Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
-
+
+#set path for working directory for PC or MAC
+wd_path <- 
+  ifelse(Sys.info()[[1]] == "Windows","C:/Users/troyh/OneDrive - University of Kentucky/Coding/R working directory/",
+         ifelse(Sys.info()[[1]] == "Darwin", "~/Desktop/Coding/R working directory/","¿¿Donde Estoy??"
+         ))
+
+#Set path for directory with data files for PC or MAC
+data_path <- 
+  ifelse(Sys.info()[[1]] == "Windows","C:/Users/troyh/OneDrive - University of Kentucky/Coding/data/",
+         ifelse(Sys.info()[[1]] == "Darwin", "~/Desktop/Coding/Data/","¿¿Donde Estoy??"
+         ))
+
+#read main File
+Mothership <- read_sav(paste0(data_path,"PHPoutcome_clean.sav"))
 #DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
@@
 ####  Export as CSV
-write.csv(Mothership,"~/Desktop/Coding/data/Mothership_paper")
+write.csv(Mothership,paste0(data_path,"Mothership_paper"))
 
@@
 ### Export as CSV
-write.csv(Mothership,"~/Desktop/Coding/data/Mothership_Diag_treat.csv")
+write.csv(Mothership,paste0(data_path,"Mothership_Diag_treat.csv"))
 
@@
 
-#install.packages('naniar')
+install.packages('naniar')
 library(naniar)
@@
                   indextype = "JT", 
-                  #JTcrit = "auto",
                   plottitle = "JT Indices For Anxiety")
@@
 ANX_JT_smol<- JTRCIdf
+view(DEP_JT_smol)
 
@@
 
-write_csv(table1_tab_anx,"~/Downloads/table1_tab_anx.csv")
+write_csv(table1_tab_anx,paste0("C:/Users/troyh/OneDrive - University of Kentucky/Coding/data/table1_tab_anx_test.csv"))
+
 ```
@@
 table1_tab_dep
-write_csv(table1_tab_dep,"~/Downloads/table1_tab_dep.csv")
+write_csv(table1_tab_dep,paste0(data_path,"table1_tab_dep_test.csv"))
 
@@
 ```{r}
-# #install.packages("ggdist")
-# library("ggdist")
-# 
-# Mothership_lasso |> 
-#   ggplot( aes(x=Depression_Responder, y=CUDOS_pre, fill=Depression_Responder)) +
-#     geom_boxplot() +
-#    #viridis::scale_fill_viridis(discrete = TRUE, alpha=0.6) +
-#     geom_jitter(color="black", size=.6 , alpha=0.9) +
-#     theme(
-#       legend.position="none",
-#       plot.title = element_text(size=11)
-#     ) +
-# #    ggtitle("Pre scores of depression severity") +
-#     xlab("Depression Severity") +
-#     ylim(0,80)
+# install.packages("ggdist")
+library("ggdist")
+
+anx_fig <- Mothership_lasso_anx |>
+  mutate(
+      Anxiety_Responder = as.factor(recode(Anxiety_Responder,
+        "Non-Responder" = paste0("Non-Responder (n=",summary(Mothership_lasso_anx$Anxiety_Responder)[[2]],")"),
+        "Responder" = paste0("Responder (n=",summary(Mothership_lasso_anx$Anxiety_Responder)[[1]],")")
+      )))
+
+dep_fig <- Mothership_lasso_dep |>
+  mutate(
+      Depression_Responder = as.factor(recode(Depression_Responder,
+        "Non-Responder" = paste0("Non-Responder (n=",summary(Mothership_lasso_dep$Depression_Responder)[[2]],")"),
+        "Responder" = paste0("Responder (n=",summary(Mothership_lasso_dep$Depression_Responder)[[1]],")")
+      )))
+
+subset(dep_fig, !is.na(Depression_Responder)) |>
+  ggplot(aes(x=CUDOS_pre, y=CUDOS_post, color=Depression_Responder)) +
+  geom_point(position = position_jitter(.3),size=2,alpha=.75)+
+  # geom_jitter(size=2,alpha=.75)+
+  theme_classic()+
+  scale_color_manual(values=c("darkgrey","#23c4cc"))+
+  geom_abline(intercept = 0, slope = 1,linetype='dotted',size=.75)+
+  geom_abline(intercept = 13, slope = 1, col = 'black',size=1)+
+  geom_abline(intercept = -13, slope = 1, col = 'black',size=1)+
+  geom_hline(yintercept =21, linetype = 'dashed',size = 1) +
+    labs(
+    title="         RCI Analysis of Depression Treatment Response\n",
+    color = "  Depression Response",
+    x = "Pre CUDOS",
+    y= " Post CUDOS"
+  )
+
+subset(anx_fig, !is.na(Anxiety_Responder)) |>
+  ggplot(aes(x=CUXOS_pre, y=CUXOS_post, color=Anxiety_Responder)) +
+  geom_point(position = position_jitter(.3),size=2,alpha=.75)+
+  # geom_jitter(size=2,alpha=.75)+
+  theme_classic()+
+  scale_color_manual(values=c("darkgrey","#e6402e"))+
+  geom_abline(intercept = 0, slope = 1,linetype='dotted',size=.75)+
+  geom_abline(intercept = 21, slope = 1, col = 'black',size=1)+
+  geom_abline(intercept = -21, slope = 1, col = 'black',size=1)+
+  geom_hline(yintercept =16.6, linetype = 'dashed',size = 1)+
+  labs(
+    title="           RCI Analysis of Anxiety Treatment Response\n",
+    color = " Anxiety Response",
+    x = "Pre CUXOS",
+    y= " Post CUXOS"
+  )
+
+```
+
+```{r}
 # 
@@
   facet_wrap(~Responder)
+```
+
+```{r}
+# 
+# 
+# FP_dep_m <- FP_dep |>
+#   ggplot(aes(y = reorder(Variable, -order), color =as.factor(sig))) +
+#   #take away background
+#   theme_classic() +
+#   #make the forrest plot
+#   geom_point(aes(x=OR), shape= FP_dep$sig,
+#                # ifelse(FP_dep$p.adjusted <= 0.05, 
+#                #                        16, # colored ones for significant varaibles
+#                #                        1), # uncolored ones for insignificant varaibles
+#              size=4,show.legend = FALSE) +
+#   geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
+#   geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
+#   scale_color_manual(values = c("darkgrey","blue"))+
+#   #change x axis name
+#   labs(
+#     x="Odds Ratio") +
+#     # title = "Odds of Anxiety Treatment Non-Response",
+#     # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
+#   #adjust the dimentions. 
+#   coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1),
+#                   xlim = c(.25,3.0)) +
+#   #add a line at 1 for reference 
+#    geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
+#   #add anotations to help suggests what each side means.
+#   annotate("text", x = .5, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
+#   annotate("text", x = 1.5, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
+#   #Git rid of the Y - Axis
+#     theme(axis.line.y = element_blank(),
+#         axis.ticks.y= element_blank(),
+#         axis.text.y= element_blank(),
+#         axis.title.y= element_blank())
+#
+
 ```
@@
 x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
-probabilities <- lasso.model.1se.dep %>% predict(newx = x.test,type ="response")
-predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
+probabilities.1se <- lasso.model.1se.dep %>% predict(newx = x.test,type ="response")
+predicted.classes.1se <- ifelse(probabilities.1se > 0.5, "Responder", "Non-Responder")
 
@@
 observed.classes <- test.data$Depression_Responder
-Mean.predict.1se.dep <- mean(predicted.classes == observed.classes)
+Mean.predict.1se.dep <- mean(predicted.classes.1se == observed.classes)
 
@@
 # Make predictions
-probabilities <- full.model.dep %>% predict(test.data, type = "response")
-predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
+probabilities.full <- full.model.dep %>% predict(test.data, type = "response")
+predicted.classes.full <- ifelse(probabilities.full > 0.5, "Responder", "Non-Responder")
 # Model accuracy
-observed.classes <- test.data$Depression_Responder
-Mean.predict.full.model.dep <- mean(predicted.classes == observed.classes)
+observed.classes.full <- test.data$Depression_Responder
+Mean.predict.full.model.dep <- mean(predicted.classes.full == observed.classes)
 
@@
 
-tmp_coeffs <- coef(lasso.model.1se.dep, s = "lambda.1se")
+tmp_coeffs <- coef(lasso.model.min.dep, s = "lambda.min")
 Dep_coefs <-tmp_coeffs@Dimnames[[1]][tmp_coeffs@i + 1]
@@
 
-write_csv(FP.min.dep, "~/Downloads/FP.min.dep")
+write_csv(FP.min.dep, paste0(data_path,"FP.min.dep"))
 ```
@@
 
-write_csv(FP.1se.dep, "~/Downloads/FP.1se.dep")
+write_csv(FP.1se.dep, paste0(data_path,"FP.1se.dep"))
 ```
@@
 
-write_csv(FP.min.dep, "~/Downloads/FP.min.dep")
+write_csv(FP.min.dep, paste0(data_path,"FP.min.dep"))
 
@@
 
-write_csv(dep_df, "~/Downloads/dep_df")
+write_csv(dep_df, paste0(data_path,"dep_df"))
 ```
@@
 
-write_csv(FP.min.anx, "~/Downloads/FP.min.anx")
+write_csv(FP.min.anx, paste0(data_path,"FP.min.anx"))
 
@@
 
-write_csv(anx_df, "~/Downloads/anx_df")
+# write_csv(anx_df, "~/Downloads/anx_df")
 
@@
   geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = 1, show.legend = FALSE,
-                color = ifelse(anx_df$p.adjusted < 0.05, "red", "darkgrey")) +
+                color = ifelse(anx_df$p.adjusted < 0.05, "#e6402e", "darkgrey")) +
+  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.3, show.legend = FALSE,
+                color = ifelse(anx_df$p.adjusted < 0.05, "#e6402e", "darkgrey"))+
+      geom_point(aes(x=OR), shape= 16,
+             size=5,show.legend = FALSE, color = "white")+
     geom_point(aes(x=OR), shape= 16,
              size=4,show.legend = FALSE,
-             color = ifelse(anx_df$p.adjusted < 0.05, "red", "darkgrey")) +
-  geom_point(aes(x=OR), shape= 1,
-             size=4,show.legend = FALSE, color = "white") +
-    geom_point(aes(x=OR), shape= 1,
-             size=4.1,show.legend = FALSE, color = "white")+
+             color = ifelse(anx_df$p.adjusted < 0.05, "#e6402e", "darkgrey")) +
 # geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.6, show.legend = FALSE) +
@@
         axis.title.y= element_blank())
-
+```
+
+```{r}
 ANX_text <- 
-  dep_df |>
+  anx_df |>
   ggplot(aes(y = reorder(Variable, -order))) +
   geom_text(aes(x = 0, label = Variable), hjust = 0,
-        fontface = ifelse(dep_df$Variable == "Variable","bold","plain")) +
+        fontface = ifelse(anx_df$Variable == "Variable","bold","plain")) +
   geom_text(aes(x = 1.1, label = Beta),
         hjust = 0,
-        fontface = ifelse(dep_df$Beta == "Beta", "bold","plain")) + 
+        fontface = ifelse(anx_df$Beta == "Beta", "bold","plain")) + 
   geom_text(aes(x = 1.5, label = Wald),
         hjust = 0,
-        fontface = ifelse(dep_df$Wald == "Wald", "bold","plain")) +
+        fontface = ifelse(anx_df$Wald == "Wald", "bold","plain")) +
   geom_text(aes(x = 1.9, label = label),
         hjust = 0,
-        fontface = ifelse(dep_df$label == "OR [95% CI]", "bold","plain")) +
+        fontface = ifelse(anx_df$label == "OR [95% CI]", "bold","plain")) +
   theme_void() +     
-  coord_cartesian(ylim = c(1,length(dep_df$Variable)), xlim = c(0, 4))
+  coord_cartesian(ylim = c(1,length(anx_df$Variable)), xlim = c(0, 4))
 
@@
     geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = 1, show.legend = FALSE,
-                color = ifelse(dep_df$p.adjusted < 0.05, "blue", "darkgrey")) +
+                color = ifelse(dep_df$p.adjusted < 0.05, "#23c4cc", "darkgrey")) +
+    geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.4, show.legend = FALSE,
+                color = ifelse(dep_df$p.adjusted < 0.05, "#23c4cc", "darkgrey")) +
+  # geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE,
+                # color = ifelse(dep_df$p.adjusted < 0.05, "#23c4cc", "darkgrey"))+
+      geom_point(aes(x=OR), shape= 16,
+             size=5,show.legend = FALSE, color = "white")+
     geom_point(aes(x=OR), shape= 16,
              size=4,show.legend = FALSE,
-             color = ifelse(dep_df$p.adjusted < 0.05, "blue", "darkgrey")) +
-  geom_point(aes(x=OR), shape= 1,
-             size=4,show.legend = FALSE, color = "white") +
-    geom_point(aes(x=OR), shape= 1,
-             size=4.1,show.legend = FALSE, color = "white")+
-# geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.6, show.legend = FALSE) +
+             color = ifelse(dep_df$p.adjusted < 0.05, "#23c4cc", "darkgrey")) +
+
   #change x axis name
@@
     # title = "    Odds of Meeting Physical Activity Guidelines",
-    subtitle ="Odds of Depression Non-Response")+
+    subtitle ="Odds of Depression Non-Response") +
   #adjust the dimentions. 
   coord_cartesian(ylim = c(1,  length(dep_df$Variable)),
-                  xlim = c(0,2))+
+                  xlim = c(0.4,2)) +
   #add a line at 1 for reference 
@@
   #add anotations to help suggests what each side means.
-  annotate("text", x = .6, y = length(dep_df$variable) -1 , label = "Less Likely", size= 4) +
-  annotate("text", x = 1.4, y = length(dep_df$variable) -1, label = "More Likely",size= 4) +
+  annotate("text", x = .6, y = length(dep_df$Variable) -1 , label = "Less Likely", size= 4) +
+  annotate("text", x = 1.4, y = length(dep_df$Variable) -1, label = "More Likely",size= 4) +
   #Git rid of the Y - Axis
@@
 ```{r}
-#Create order varaible in dataset to keep it the same as the regression
-
-FP_anx <- read_csv("~/Downloads/FP.min.anx")
-# FP_anx <- read_csv("~/Downloads/FP.1se.anx")
-
-#Change the names of variables
-# FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
-#                     "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
-#                     "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
-#                     "Co-SUD", "CUXOS Pre", "Post Coping", 
-#                     "Post PMH", "Post Functioning", "Post Wellbeing")
-
-FP_anx$order = c(seq(from=2, to=length(FP_anx$Variable) + 1,1))
-
-FP_anx <- FP_anx |>
-  mutate(
-    sig = ifelse(p.adjusted <= 0.05, 16,1)
-  )
-
-FP_anx_m <- FP_anx |>
-  ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
-  #take away background
-  theme_classic() +
-  #make the forrest plot
-  geom_point(aes(x=OR), shape= FP_anx$sig,
-               # ifelse(FP_anx$p.adjusted <= 0.05, 
-               #                        16, # colored ones for significant varaibles
-               #                        1), # uncolored ones for insignificant varaibles
-             size=3.5,show.legend = FALSE) +
-  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
-  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.5, show.legend = FALSE)+
-  scale_color_manual(values = c("darkgrey","red"))+
-  #change x axis name
-  labs(
-    x="Odds Ratio") +
-    # title = "Odds of Anxiety Treatment Non-Response",
-    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
-  #adjust the dimentions. 
-  coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
-                  xlim = c(.25,2.5)) +
-  #add a line at 1 for reference 
-   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
-  #add anotations to help suggests what each side means.
-  annotate("text", x = .6, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
-  annotate("text", x = 1.5, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
-  #Git rid of the Y - Axis
-    theme(axis.line.y = element_blank(),
-        axis.ticks.y= element_blank(),
-        axis.text.y= element_blank(),
-        axis.title.y= element_blank())
-
-FP_anx_m
-
-FP_anx <- FP_anx |>
-  # round estimates and 95% CIs to 2 decimal places for journal specifications
-  mutate(across(
-    c(OR, OR_low, OR_high),
-    ~ str_pad(
-      round(.x, 2),
-      width = 4,
-      pad = "0",
-      side = "right"
-    )
-  ),
-  # add an "-" between HR estimate confidence intervals
-  estimate_lab = paste0(OR, " [", OR_low, "-", OR_high, "]")) |>
-  # round p-values to two decimal places, except in cases where p < .001
-  mutate(p.adjusted_fig = case_when(
-    p.adjusted < .001 ~ "<0.001",
-    round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
-    p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
-      as.character(round(p.adjusted, 3)),
-      width = 4,
-      pad = "0",
-      side = "right"
-    ),
-    TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
-      as.character(round(p.adjusted, 2)),
-      width = 4,
-      pad = "0",
-      side = "right"
-    )
-  )) |>
-  # add a row of data that are actually column names which will be shown on the plot in the next step
-  bind_rows(
-    data.frame(
-      Variable = "Variable",
-      estimate_lab = "Odds Ratio (95% CI)",
-      OR_low = "",
-      OR_high = "",
-      p.adjusted_fig = "p value"
-    )
-  )
-
-FP_anx[length(FP_anx$Variable),8] = 1
-FP_anx
-
-#arange the labels on top
-      FP_anx<-mutate(FP_anx, top_row = 0)
-      FP_anx[length(FP_anx$Variable),12] = 1
-      FP_anx <- arrange(FP_anx,order)
-FP_anx
-    # plot the left side of the plot 
-      FP_anx_L <- FP_anx %>% 
-        ggplot(aes(y = reorder(Variable, -order))) +
-        geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
-        geom_text(aes(x = 1, label = estimate_lab),
-        hjust = 0,
-        fontface = ifelse(FP_anx$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
-        theme_void() +
-        coord_cartesian(ylim = c(1,length(FP_anx$Variable)), xlim = c(0, 4))
-
-FP_anx_L
-
-FP_anx_R <-  
-      FP_anx |>
-      ggplot() +
-        geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
-        fontface = ifelse(FP_anx$p.adjusted_fig == "p value", "bold", "plain")) +
-        theme_void() +
-        coord_cartesian(ylim = c(1,length(FP_anx$Variable)))
-
-FP_anx
-
-library("patchwork")
-
-layout <- c(
-  patchwork::area(t = 0, l = 0, b = 30, r = 35),
-  patchwork::area(t = 0, l = 19, b = 30, r = 34),
-  patchwork::area(t = 0, l = 30, b = 30, r = 40) 
-  )
-
-FP_anx_L + FP_anx_m + FP_anx_R + plot_layout(design = layout)
+# #Create order varaible in dataset to keep it the same as the regression
+# 
+# FP_anx <- read_csv("~/Downloads/FP.min.anx")
+# # FP_anx <- read_csv("~/Downloads/FP.1se.anx")
+# 
+# #Change the names of variables
+# # FP_anx$Variable = c("Age", "Unmarried", "Days Completed", 
+# #                     "Days Not Attended", "Anixety Disorder","Trauma Disorder", 
+# #                     "Other Disorder", "Co-Mood Disorder",  "Co-BPD", 
+# #                     "Co-SUD", "CUXOS Pre", "Post Coping", 
+# #                     "Post PMH", "Post Functioning", "Post Wellbeing")
+# 
+# FP_anx$order = c(seq(from=2, to=length(FP_anx$Variable) + 1,1))
+# 
+# FP_anx <- FP_anx |>
+#   mutate(
+#     sig = ifelse(p.adjusted <= 0.05, 16,1)
+#   )
+# 
+# FP_anx_m <- FP_anx |>
+#   ggplot(aes(y = reorder(Variable, -order), color = as.factor(sig))) +
+#   #take away background
+#   theme_classic() +
+#   #make the forrest plot
+#   geom_point(aes(x=OR), shape= FP_anx$sig,
+#                # ifelse(FP_anx$p.adjusted <= 0.05, 
+#                #                        16, # colored ones for significant varaibles
+#                #                        1), # uncolored ones for insignificant varaibles
+#              size=3.5,show.legend = FALSE) +
+#   geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
+#   geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.5, show.legend = FALSE)+
+#   scale_color_manual(values = c("darkgrey","red"))+
+#   #change x axis name
+#   labs(
+#     x="Odds Ratio") +
+#     # title = "Odds of Anxiety Treatment Non-Response",
+#     # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
+#   #adjust the dimentions. 
+#   coord_cartesian(ylim = c(1,length(FP_anx$Variable) + 1),
+#                   xlim = c(.25,2.5)) +
+#   #add a line at 1 for reference 
+#    geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
+#   #add anotations to help suggests what each side means.
+#   annotate("text", x = .6, y = length(FP_anx$Variable) + 1, label = "Less Likely", size= 3) +
+#   annotate("text", x = 1.5, y = length(FP_anx$Variable) + 1, label = "More Likely",size= 3) +
+#   #Git rid of the Y - Axis
+#     theme(axis.line.y = element_blank(),
+#         axis.ticks.y= element_blank(),
+#         axis.text.y= element_blank(),
+#         axis.title.y= element_blank())
+# 
+# FP_anx_m
+# 
+# FP_anx <- FP_anx |>
+#   # round estimates and 95% CIs to 2 decimal places for journal specifications
+#   mutate(across(
+#     c(OR, OR_low, OR_high),
+#     ~ str_pad(
+#       round(.x, 2),
+#       width = 4,
+#       pad = "0",
+#       side = "right"
+#     )
+#   ),
+#   # add an "-" between HR estimate confidence intervals
+#   estimate_lab = paste0(OR, " [", OR_low, "-", OR_high, "]")) |>
+#   # round p-values to two decimal places, except in cases where p < .001
+#   mutate(p.adjusted_fig = case_when(
+#     p.adjusted < .001 ~ "<0.001",
+#     round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
+#     p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
+#       as.character(round(p.adjusted, 3)),
+#       width = 4,
+#       pad = "0",
+#       side = "right"
+#     ),
+#     TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
+#       as.character(round(p.adjusted, 2)),
+#       width = 4,
+#       pad = "0",
+#       side = "right"
+#     )
+#   )) |>
+#   # add a row of data that are actually column names which will be shown on the plot in the next step
+#   bind_rows(
+#     data.frame(
+#       Variable = "Variable",
+#       estimate_lab = "Odds Ratio (95% CI)",
+#       OR_low = "",
+#       OR_high = "",
+#       p.adjusted_fig = "p value"
+#     )
+#   ) 
+# 
+# FP_anx[length(FP_anx$Variable),8] = 1
+# FP_anx
+# 
+# #arange the labels on top
+#       FP_anx<-mutate(FP_anx, top_row = 0)
+#       FP_anx[length(FP_anx$Variable),12] = 1
+#       FP_anx <- arrange(FP_anx,order)
+# FP_anx
+#     # plot the left side of the plot 
+#       FP_anx_L <- FP_anx %>% 
+#         ggplot(aes(y = reorder(Variable, -order))) +
+#         geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
+#         geom_text(aes(x = 1, label = estimate_lab),
+#         hjust = 0,
+#         fontface = ifelse(FP_anx$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
+#         theme_void() +
+#         coord_cartesian(ylim = c(1,length(FP_anx$Variable)), xlim = c(0, 4))
+# 
+# FP_anx_L
+# 
+# FP_anx_R <-  
+#       FP_anx |>
+#       ggplot() +
+#         geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
+#         fontface = ifelse(FP_anx$p.adjusted_fig == "p value", "bold", "plain")) +
+#         theme_void() +
+#         coord_cartesian(ylim = c(1,length(FP_anx$Variable)))
+#         
+# FP_anx
+# 
+# library("patchwork")
+# 
+# layout <- c(
+#   patchwork::area(t = 0, l = 0, b = 30, r = 35),
+#   patchwork::area(t = 0, l = 19, b = 30, r = 34),
+#   patchwork::area(t = 0, l = 30, b = 30, r = 40) 
+#   )
+# 
+# FP_anx_L + FP_anx_m + FP_anx_R + plot_layout(design = layout)
 
@@
 ```{r}
-#Create order varaible in dataset to keep it the same as the regression
-
-FP_dep <- read_csv("~/Downloads/FP.min.dep")
-
-#rename the variables for the figure
-
-# FP_dep$Variable = c(
-#                      "Days Not Attended",
-#                     "Post Coping", 
-#                     "Post PMH", "Post Functioning", "Post Wellbeing")
-
-FP_dep$order = c(seq(from=2, to=length(FP_dep$Variable) + 1,1))
-
-FP_dep <- FP_dep |>
-  mutate(
-    sig = ifelse(p.adjusted <= 0.05, 16,1)
-  )
-
-FP_dep_m <- FP_dep |>
-  ggplot(aes(y = reorder(Variable, -order), color =as.factor(sig))) +
-  #take away background
-  theme_classic() +
-  #make the forrest plot
-  geom_point(aes(x=OR), shape= FP_dep$sig,
-               # ifelse(FP_dep$p.adjusted <= 0.05, 
-               #                        16, # colored ones for significant varaibles
-               #                        1), # uncolored ones for insignificant varaibles
-             size=4,show.legend = FALSE) +
-  geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
-  geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
-  scale_color_manual(values = c("darkgrey","blue"))+
-  #change x axis name
-  labs(
-    x="Odds Ratio") +
-    # title = "Odds of Anxiety Treatment Non-Response",
-    # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
-  #adjust the dimentions. 
-  coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1),
-                  xlim = c(.25,3.0)) +
-  #add a line at 1 for reference 
-   geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
-  #add anotations to help suggests what each side means.
-  annotate("text", x = .5, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
-  annotate("text", x = 1.5, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
-  #Git rid of the Y - Axis
-    theme(axis.line.y = element_blank(),
-        axis.ticks.y= element_blank(),
-        axis.text.y= element_blank(),
-        axis.title.y= element_blank())
-
-FP_dep_m
-
-FP_dep <- FP_dep |>
-  # round estimates and 95% CIs to 2 decimal places for journal specifications
-  mutate(across(
-    c(OR, OR_low, OR_high),
-    ~ str_pad(
-      round(.x, 2),
-      width = 4,
-      pad = "0",
-      side = "right"
-    )
-  ),
-  # add an "-" between HR estimate confidence intervals
-  estimate_lab = paste0(OR, " (", OR_low, "-", OR_high, ")")) |>
-  # round p-values to two decimal places, except in cases where p < .001
-  mutate(p.adjusted_fig = case_when(
-    p.adjusted < .001 ~ "<0.001",
-    round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
-    p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
-      as.character(round(p.adjusted, 3)),
-      width = 4,
-      pad = "0",
-      side = "right"
-    ),
-    TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
-      as.character(round(p.adjusted, 2)),
-      width = 4,
-      pad = "0",
-      side = "right"
-    )
-  )) |>
-  # add a row of data that are actually column names which will be shown on the plot in the next step
-  bind_rows(
-    data.frame(
-      Variable = "Variable",
-      estimate_lab = "Odds Ratio (95% CI)",
-      OR_low = "",
-      OR_high = "",
-      p.adjusted_fig = "p value"
-    )
-  )
-
-FP_dep[length(FP_dep$Variable),8] = 1
-FP_dep
-
-#arange the labels on top
-      FP_dep<-mutate(FP_dep, top_row = 0)
-      FP_dep[length(FP_dep$Variable),12] = 1
-      FP_dep <- arrange(FP_dep,order)
-FP_dep
-    # plot the left side of the plot 
-      FP_dep_L <- FP_dep %>% 
-        ggplot(aes(y = reorder(Variable, -order))) +
-        geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
-        geom_text(aes(x = 1, label = estimate_lab),
-        hjust = 0,
-        fontface = ifelse(FP_dep$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
-        theme_void() +
-        coord_cartesian(ylim = c(1,length(FP_dep$Variable)), xlim = c(0, 4))
-
-FP_dep_L
-
-FP_dep_R <-  
-      FP_dep |>
-      ggplot() +
-        geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
-        fontface = ifelse(FP_dep$p.adjusted_fig == "p value", "bold", "plain")) +
-        theme_void() +
-        coord_cartesian(ylim = c(1,length(FP_dep$Variable)))
-
-FP_dep
-
-library("patchwork")
-
-layout <- c(
-  patchwork::area(t = 0, l = 0, b = 30, r = 30),
-  patchwork::area(t = 0, l = 15, b = 30, r = 25),
-  patchwork::area(t = 0, l = 22, b = 30, r = 30) 
-  )
-
-FP_dep_L + FP_dep_m + FP_dep_R + plot_layout(design = layout)
-```
+# #Create order varaible in dataset to keep it the same as the regression
+# 
+# 
+# 
+# FP_dep <- read_csv("~/Downloads/FP.min.dep")
+# 
+# #rename the variables for the figure
+# 
+# # FP_dep$Variable = c(
+# #                      "Days Not Attended",
+# #                     "Post Coping", 
+# #                     "Post PMH", "Post Functioning", "Post Wellbeing")
+# 
+# 
+# FP_dep$order = c(seq(from=2, to=length(FP_dep$Variable) + 1,1))
+# 
+# FP_dep <- FP_dep |>
+#   mutate(
+#     sig = ifelse(p.adjusted <= 0.05, 16,1)
+#   )
+# 
+# FP_dep_m <- FP_dep |>
+#   ggplot(aes(y = reorder(Variable, -order), color =as.factor(sig))) +
+#   #take away background
+#   theme_classic() +
+#   #make the forrest plot
+#   geom_point(aes(x=OR), shape= FP_dep$sig,
+#                # ifelse(FP_dep$p.adjusted <= 0.05, 
+#                #                        16, # colored ones for significant varaibles
+#                #                        1), # uncolored ones for insignificant varaibles
+#              size=4,show.legend = FALSE) +
+#   geom_linerange(aes(xmin=OR_low, xmax=OR_high),size = .4, show.legend = FALSE) +
+#   geom_errorbar(aes(xmin=OR_low, xmax=OR_high),width =.35, show.legend = FALSE)+
+#   scale_color_manual(values = c("darkgrey","blue"))+
+#   #change x axis name
+#   labs(
+#     x="Odds Ratio") +
+#     # title = "Odds of Anxiety Treatment Non-Response",
+#     # subtitle = "Based on Pre/Post CUXOS Scores in PHP program") +
+#   #adjust the dimentions. 
+#   coord_cartesian(ylim = c(1,length(FP_dep$Variable) + 1),
+#                   xlim = c(.25,3.0)) +
+#   #add a line at 1 for reference 
+#    geom_vline(xintercept = 1, linetype="dashed", alpha = .5) +
+#   #add anotations to help suggests what each side means.
+#   annotate("text", x = .5, y = length(FP_dep$Variable) + 1, label = "Less Likely", size= 4) +
+#   annotate("text", x = 1.5, y = length(FP_dep$Variable) + 1, label = "More Likely",size= 4) +
+#   #Git rid of the Y - Axis
+#     theme(axis.line.y = element_blank(),
+#         axis.ticks.y= element_blank(),
+#         axis.text.y= element_blank(),
+#         axis.title.y= element_blank())
+# 
+# FP_dep_m
+# 
+# FP_dep <- FP_dep |>
+#   # round estimates and 95% CIs to 2 decimal places for journal specifications
+#   mutate(across(
+#     c(OR, OR_low, OR_high),
+#     ~ str_pad(
+#       round(.x, 2),
+#       width = 4,
+#       pad = "0",
+#       side = "right"
+#     )
+#   ),
+#   # add an "-" between HR estimate confidence intervals
+#   estimate_lab = paste0(OR, " (", OR_low, "-", OR_high, ")")) |>
+#   # round p-values to two decimal places, except in cases where p < .001
+#   mutate(p.adjusted_fig = case_when(
+#     p.adjusted < .001 ~ "<0.001",
+#     round(p.adjusted, 2) == .05 ~ as.character(round(p.adjusted,3)),
+#     p.adjusted < .01 ~ str_pad( # if less than .01, go one more decimal place
+#       as.character(round(p.adjusted, 3)),
+#       width = 4,
+#       pad = "0",
+#       side = "right"
+#     ),
+#     TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
+#       as.character(round(p.adjusted, 2)),
+#       width = 4,
+#       pad = "0",
+#       side = "right"
+#     )
+#   )) |>
+#   # add a row of data that are actually column names which will be shown on the plot in the next step
+#   bind_rows(
+#     data.frame(
+#       Variable = "Variable",
+#       estimate_lab = "Odds Ratio (95% CI)",
+#       OR_low = "",
+#       OR_high = "",
+#       p.adjusted_fig = "p value"
+#     )
+#   ) 
+# 
+# FP_dep[length(FP_dep$Variable),8] = 1
+# FP_dep
+# 
+# #arange the labels on top
+#       FP_dep<-mutate(FP_dep, top_row = 0)
+#       FP_dep[length(FP_dep$Variable),12] = 1
+#       FP_dep <- arrange(FP_dep,order)
+# FP_dep
+#     # plot the left side of the plot 
+#       FP_dep_L <- FP_dep %>% 
+#         ggplot(aes(y = reorder(Variable, -order))) +
+#         geom_text(aes(x = 0, label = Variable), hjust = 0, fontface = "bold")+
+#         geom_text(aes(x = 1, label = estimate_lab),
+#         hjust = 0,
+#         fontface = ifelse(FP_dep$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
+#         theme_void() +
+#         coord_cartesian(ylim = c(1,length(FP_dep$Variable)), xlim = c(0, 4))
+# 
+# FP_dep_L
+# 
+# FP_dep_R <-  
+#       FP_dep |>
+#       ggplot() +
+#         geom_text(aes(x = 0, y = reorder(Variable, -order), label = p.adjusted_fig), hjust = 0,
+#         fontface = ifelse(FP_dep$p.adjusted_fig == "p value", "bold", "plain")) +
+#         theme_void() +
+#         coord_cartesian(ylim = c(1,length(FP_dep$Variable)))
+#         
+# FP_dep
+# 
+# library("patchwork")
+# 
+# layout <- c(
+#   patchwork::area(t = 0, l = 0, b = 30, r = 30),
+#   patchwork::area(t = 0, l = 15, b = 30, r = 25),
+#   patchwork::area(t = 0, l = 22, b = 30, r = 30) 
+#   )
+# 
+# FP_dep_L + FP_dep_m + FP_dep_R + plot_layout(design = layout)
+```

### 2024-06-30 Lasso_RCI_Response.Rmd
Fixing Anx LASSO

@@
    library(aod)
-   anx_wald  <- wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:10)
+   anx_wald  <- wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms= 2:11)
   wald <- wald.test(b = coef(glm_min_anx),Sigma = vcov(glm_min_anx),Terms=2)$result$chi2[1]
@@
     paste0("Model R^2 = ", round((R2.min.anx[[1]]*100),3),"%"),
-    "Co-occuring BPD", "Days Not Attended", "Age", "Post Functioning", 
-    "Post Sense of Wellbeing", "Post PMH", "Post Coping", "Some College",
-    "Co-occuring SUD", "Anxiety Disorder",
+    "Co-occuring BPD",
+    "Days Not Attended", 
+    "Age", 
+    "Post Functioning", 
+    "Post Sense of Wellbeing", 
+    "Post Positive Mental Health", 
+    "Post Coping Ability", 
+    "Some College",  
+    "Anxiety Disorder", 
+    "Co-occuring SUD", 
     "Variable"
